### 2017-09-25 draft1.1.tex
new project

%\documentclass[11pt]{article}
\documentclass[%
%reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
preprint,
showpacs,
%preprintnumbers,
nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
%aps,
%pra,
%prb,
prc,
%paper,
%rmp,
%prstab,
%prstper,
%twocolumn,
floatfix ]%
{revtex4-1}

\usepackage{comment}
%\usepackage[dvips]{graphicx}
%\usepackage{amsmath,amssymb}
%\usepackage{mathrsfs}
%\usepackage{txfonts}
\usepackage{braket}
%\usepackage{latexsym}
%\usepackage{ascmac}
%\usepackage{fancybox}
%\usepackage{type1cm}
\usepackage{cases}
\usepackage{caption}
\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}

  \makeatletter
    \renewcommand{\theequation}{%
    \thesection.\arabic{equation}}
    \@addtoreset{equation}{section}
  \makeatother

\begin{document}

\title{Comparative study of requantization of time-dependent mean-field
for pairing dynamics}
\author{Fang Ni}
 \affiliation{Faculty of Pure and Applied Sciences,
              University of Tsukuba, Tsukuba 305-8571, Japan}
\author{Takashi Nakatsukasa}
 \affiliation{Center for Computational Sciences,
              University of Tsukuba, Tsukuba 305-8577, Japan}
 \affiliation{Faculty of Pure and Applied Sciences,
              University of Tsukuba, Tsukuba 305-8571, Japan}
 \affiliation{iTHES Research Group, RIKEN, Wako 351-0198, Japan}

\begin{abstract}
In order to obtain quantal information, such as enegy eigenvalues
and transition matrix elements,
it is useful to requantize the mean-field dynamics.
We study the two-level pairing model to compare different
requantization methods and their accuracy.
Among the different methods, the one constructing microscopic
wave functions, using the TDHFB trajectories fulfilling the
Einstein-Brillouin-Keller quantization condition,
is the most accurate.
We also examine the performance of the collective model,
analogous to the Bohr model of the quadrupole vibrations and rotation,
assuming the pairing gap parameter as the collective coordinate.
It turns out that the applicability of such a model is very limited
for the pairing case.
\end{abstract}

\maketitle

\section{Introduction}

Pairing correlation is important 
in the ground state of open-shell nuclei.
Many evidences of the pairing correlation were observed in experiment,
including odd-even mass difference, moments of inertia of rotational bands,
and quasi-particle spectra in odd nuclei.
Even in closed-shell nuclei, the pairing dynamically plays an important
role in elementary modes of excitation, such as pairing vibrations
\cite{BM75, RS80, BB05}.
Properties of low-lying modes of excitation in even-even nuclei are
expected to be determined by interplay between
the pairing and the quadrupole correlations.
However, the true nature of the low-lying excitations is still unclear,
especilly for excited $J^\pi=0^+$ states \cite{garrett,HW11}.
Understanding the pairing dynamics is a key ingredient for solving
mysteries of excited $0^+$ states.

The ground states in many of even-even nuclei are well
described by the Bardeen-Cooper-Schriefer (BCS)
and the Hartree-Fock-Bogoliubov (HFB) theories \cite{RS80,BHR03}.
Its time-dependent version, 
the time-dependent HFB (TDHFB) theory \cite{BR86,NMMY16},
is a natural extension of the static HFB theory.
The small-amplitude limit of the TDHFB is known to be 
the quasiparticle random phase approximation (QRPA).
%Because of the improvement of computational power,
%dynamics and reaction process in nuclei have been investigated
%based on QRPA.
The QRPA has been extensively utilized and successfully
describe properties of giant resonances.
In contrast, many of low-lying excited states
cannot be well reproduced by QRPA \cite{NMMY16}.
This may be due to their slowly moving large-amplitude nature.

%Because the energy scale of pairing correlation is a few MeV, not only quadrupole deformation, but also pairing correlation play significant role in low-lying excited states. The importance of pairing in low-lying excited states is especially mentioned in rare earth region\cite{garrett}. The competition between quadrupole and pairing is considerable, hence the motion is expected to be large amplitude. \par
%The most conventional approach to describe large amplitude collective motion (LACM) in many-body system is time dependent Hartree-Fock(-Bogoliubov) TDHF(B) theory.

The Bohr Hamiltonian was introduced to describe low-energy
nuclear collective motion in quadrupole degrees of freedom with
the deformation parameters $(\beta, \gamma)$ and the Euler angles
$(\alpha,\beta,\gamma)$.
For the pairing motion, the collective coordinates are analogously
chosen as the pair deformation (gap) $\Delta$ and the gauge angle $\Phi$
\cite{BBPK70}.
Based on the pairing collective Hamiltonian, 
effects of the pair motion on the quadrupole vibrations %and fission half lives
have been discussed in literatures \cite{delta1,delta3}.
%\cite{delta1,delta2,delta3}. 
However, it is not trivial whether the pair deformation is really a suitable
choice for the collective coordinate,
which should be investigated in a microscopic approach based on
the TDHFB dynamics.

In principle, the TDHFB dynamics can be large amplitude motion.
The problem is that it is not easy to determine quantum mechanical 
quantities, such as energy eigenvalues and transition matrix elements,
from the TDHFB trajectories.
For this purpose,
since the TDHF(B) trajectory corresponds to a classical limit of the path
integral formulation,
the requantization of the mean-field dynamics was
proposed \cite{Neg80,path,path2,Rei80}.
It recovers quantum fluctuations missing in the mean-field
level, and possibly enables us to describe large-amplitude collective
tunneling phenomena such as spontaneous fission \cite{Neg80}.
The requantization of the TDHFB is particularly feasible
for integrable systems, because the system is described by separable
action-angle variables $(I_k, \phi_k)$, leading to
the Einstein-Brillouin-Keller (EBK) quantization condition.
However, for nonintegrable systems in general, it is difficult to find
suitable periodic orbits to quantize.
A possible solution to this difficulty is to find a decoupled collective
subspace spanned by
a single coordinate and its conjugate momentum \cite{NMMY16}.
Since the one-dimensional system is integrable, the quantization is
practicable.

Our final goal is to study the role of dynamical pairing effects
and to reveal nature of the mysterious excited $0^+$ states.
As the first step Toward this goal, we investigate accuracy and
applicability of the requantized TDHFB model for a two-level pairing model
with equal degeneracy $\Omega$ \cite{HF60},
especially on the calculation of two-particle-transfer matrix elements.
In Ref.~\cite{CDS84},
the two-particle-transfer matrix elements were eveluated as
Fourier components of the time-dependent mean values of the pair
creation operators,
which demonstrates nice agreement with the exact results at
large $\Omega$ values ($\Omega=40$).
However, in the realistic values of $\Omega$, we will show that
the deviation is prominent.
The collective model of the pairing motion, which assumes the pair deformation
as the collective coordinate, has a similar tendency, namely, 
applicability limited to large $\Omega$ cases \cite{BBPK70}.
This deficiency is mainly due to the small collectivity in the pairing motion
in realistic situations.
In this paper, in order to improve the quantitative estimate of the matrix
elements, we construct microscopic wave functions
based on the EBK quantization for the integrable systems.
The wave functions are obtained
from the stationary phase approximation for the path-integral form \cite{SM88}.
Its superiority to the other methods
becomes more evident for smaller values of $\Omega$.

%Nuclear collective model has the advantage to deal with the requantization. The collective coordinates can be easily quantized. Also, the mass parameters and collective potential with respect to the collective coordinates can be derived from microscopic theory (e.g. constrained HFB). For example, Bohr Hamiltonian, which can describe nuclear collective motion in quadrupole degrees of freedom, is written by collective coordinates of quadrupole deformation parameter $\beta, \gamma$ and Euler angle $\theta_i \ (i=1,2,3)$. For pairing LACM (PLACM), the collective coordinates are gauge angle $\Phi$ and pairing gap $\Delta$. $\Delta$ corresponds to deformation and $\Phi$ corresponds to rotation in U(1) gauge space. The concept of pairing collective coordinates is firstly introduced in Ref. \cite{first}. Based on pairing collective Hamiltonian, the pairing degrees of freedom influence not only the value of pairing gap in ground state, but also transition probability and spontaneous fission half-lives\cite{delta1,delta2,delta3}. On the other hand, without pairing collective Hamiltonian, there is little study about PLACM in requantization of TDHFB. Because the pairing collective coordinates are chosen ``by hand'', we need to investigate the validity of such collective coordinates.\par

%The main purpose of this paper is elucidate PLACM in two-level system of a simple nuclear pairing model -- Richardson model.  We consider all of the canonical coordinates in TDHFB trajectory. Such canonical coordinates can be generated from Thouless' theorem. In realistic nuclear system, we have huge number of canonical coordinates. However, the number of canonical coordinates is limited in Richardson model, which has advantage to be studied for the requantization of TDHFB without collective model. Especially, two-level system contains the least degrees of freedom for discussing about pairing rotation and pairing vibration. We also transform the canonical coordinates to $\Delta$ and $\Phi$, to discuss whether the pairing collecitve Hamiltonian is validity. \par
%To describe LACM from microscopic picture, the major approach is constrained Hartree-Fock(-Bogoliubov) (CHFB) or constrained BCS (CBCS) method by assuming collective coordinates as the constraint condition. \par
%Because the collective of gauge angle $\Phi$ and pairing gap $\Delta$ is chosen ``by hand'', it is suspective whether the system prefers the motion along artificial collective coordinates. We need to consider some more ``natural'' collective coordinates.\par

The paper is organized as follows. 
In Sec. \ref{sec:TDHFB},
we derive a TDHFB classical Hamiltonian for the pairing model.
In Sec. \ref{sec:requantization}, 
the requantization of the TDHFB is performed using different methods,
based on the canonical and the EBK quantizations.
In Sec. \ref{sec:results}, 
the numerical results for the two-level model are shown and compared with
exact results.
Properties of the pairing collective coordinate is also discussed.
We give a conclusion in Sec. \ref{sec:conclusion}.

%\section{Classical picture}
\section{Classical form of TDHFB Hamiltonian}
\label{sec:TDHFB}

The Hamiltonian of the pairing model is given in terms of
single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{equation}
%  H &= \sum_l \epsilon_l n_l - \frac{g}{4} \sum_{ll'} P_l^{\dag}P_{l'}
	H = \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^-
    = \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
\end{equation}
where we use the SU(2) quasispin operators,
$\boldsymbol{S}=\sum_l \boldsymbol{S}_l$, with
\begin{eqnarray}
        S_l^0 &=& \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l) ,\\
        S_l^{+} &=& \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
degeneracy ($\Omega_l=j_l+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,\Omega_l-1/2$.
The occupation number of each level $l$ is given by
$
	n_l = \sum_m a^{\dag}_{lm}a_{lm} = 2S_l^0+\Omega_l ,
$.
%The first term giving a spherical single particle energy $\epsilon_l$ for each j-shell, which 
The quasispin operators satisfy the commutation relations
\begin{equation}
  [S_l^0,S_{l'}^{\pm}] = \pm\delta_{ll'}S_{l}^{\pm},
	\quad [S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0} .
\end{equation}
The magnitude of quasispin for each level is
$S_l=\frac{1}{2}(\Omega_l-\nu_l)$, where $\nu_l$ is the seniority
quantum number, namely the number of unpaired particle at each level $l$.
%We call $\nu=\sum_l \nu_l=0$ excited states as pairing collective excited states. The pairing collective excited states can be simple $2p2h, 4p4h\cdots$ excitation or the complex combination of $2p2h, 4p4h\cdots$ components.
In the present study, we only consider seniority zero states with
$\nu=\sum_l \nu_l=0$.
The residual two-body interaction only consists of monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain exact solutions either by solving Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasispin symmetry.

%\subsection{Coherent state}
\subsection{Coherent-state representation of the TDHFB Hamiltonian}

The coherent state for the seniority $\nu=0$ states
($S_l=\Omega_l/2$) is constructed as
\begin{equation}
	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-\Omega_l/2}
	\exp (Z_l(t) S_l^{+}) \ket{0}
 \label{coherent}
\end{equation}
where $\ket{0}$ is the vacuum (zero particle) state,
$Z_l(t)$ are time-dependent complex variables which describe
motion of the system. 
In the SU(2) quasispin representation,
$\ket{0}=\prod_l \ket{S_l,-S_l}$.
The coherent state $\ket{Z(t)}$ is a superposition of
states with different particle numbers
without unpaired particles.
%If $Z_l$ are all real,
In the present pairing model,
the coherent state is the same as the time-dependent BCS wave function
with $Z_l(t)=v_l(t)/u_l(t)$,
where $(u_l(t),v_l(t))$ are the time-dependent BCS $u,v$ factors.

The TDHFB equation can be derived from the tiem-dependent variational
principle,
\begin{equation}
	\delta \mathcal{S} = 0,
	\quad
%  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
	\mathcal{S}\equiv
	\int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt,
  \label{TDHFB}
\end{equation}
where $\ket{\phi(t)}$ is the time-dependent generalized Slater determinant.
In the present case, we adopt the coherent state of Eq. (\ref{coherent}),
$\ket{\phi(t)}=\ket{Z(t)}$.
%Keeping the time-dependent state vector fulfills normalization $\braket{Z|Z}=1$, 
The action $\mathcal{S}$ is
\begin{equation}
	\mathcal{S}  = \int \mathcal{L}(t) dt
	%&= \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt \\
	= \int dt \left\{ \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{Z|H|Z} \right\} ,
\label{S}
\end{equation}
and
\begin{align}
%  \braket{Z|H|Z} &= \sum_l \epsilon_l \left\{ 2S_l\left( 1-\frac{2}{1+|Z_l|^2} \right) + \Omega_l \right\}
%  -g \sum_l \frac{2S_l|Z_l|^2(2S_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
%  -g \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
  \braket{Z|H|Z} &= \sum_l \epsilon_l \frac{2\Omega_l |Z_l|^2}{1+|Z_l|^2}
  -g \sum_l \frac{\Omega_l|Z_l|^2(\Omega_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
  -g \sum_{l_1 \neq l_2} \frac{\Omega_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{\Omega_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
	\label{TDHFB_Hamiltonian_1}
\end{align}
We transform the complex variables $Z_l$ into real variables $(q_l,\chi_l)$
by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ and $q_l=\cos{\theta_l}$.
The Lagrangian $\mathcal{L}$ and the expectation value of Hamiltonian become
\begin{align}
\mathcal{L}(t) &= \sum_l \frac{\Omega_l}{2}
	(1-q_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
	\mathcal{H}(Z,Z^*)&\equiv \braket{Z|H|Z} = \sum_l \epsilon_l\Omega_l(1- q_l) - \frac{g}{4}\sum_l \Omega_l (\Omega_l(1-q_l^2)+(1-q_l)^2) \nonumber \\
&- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}\sqrt{(1-q_{l_1}^2)(1-q_{l_2}^2)}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
\label{TDHFB_Hamiltonian_2}
\end{align}
Here, $\chi_l$ represent the gauge angle of each level,
and $q_l$ are related to the occupation probability, $q_l=|u_l|^2-|v_l|^2$.
Since the Hamiltonian (\ref{TDHFB_Hamiltonian_2}) depends only on
relative difference in the gauge angles,
the ``global'' gauge angles, $\Phi\propto\sum_l \chi_l$,
is a cyclic variable.

\subsection{Two-level case}

In a two-level system,
it is convenient to define global and relative gauge angles,
$\Phi$ and $\phi$, respectively.
\begin{align}
  \Phi &\equiv \frac{\chi_1 + \chi_2}{2}, \quad\quad
\phi\equiv \chi_2 - \chi_1,
\label{phi}
\end{align}
whose ranges are $0\leq \Phi \leq 2\pi$ and $-2\pi \leq \phi \leq 2\pi$.
Their conjugate momenta $(J,j)$ are given by
\begin{align}
	J &= \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} =  \sum_{l=1}^2 \frac{\Omega_l}{2}(1-q_l), 
\quad\quad
j = \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \frac{\Omega_2(1-q_2) - \Omega_1(1-q_1)}{4}. \label{pi} .
\end{align}
Calculating the occupation number $n_l$ in the level $l$,
the physical meaning of these conjugate momenta becomes obvious.
\begin{equation}
   n_l = \braket{Z|n_l|Z} % = -2S_lq_l+\Omega_l \nonumber  \\
	= \Omega_l(1-q_l) .
\end{equation}
Therefore, $J$ corresponds to the total particle number
$N=\sum_l n_l$,
while $j$ corresponds to the difference of occupation number
between upper level and lower level. 
\begin{align}
  J &= \frac{N}{2}, \hspace{5mm} j = \frac{n_{2}-n_{1}}{4} .
  \label{momentum}
\end{align}
Since the coherent states (\ref{coherent}) contains only even number of
particles in each level,
we assume that $n_l$ are even numbers.
%The expectation value of total particle number is
%\begin{align}
%   N &= \braket{Z|N|Z} = \sum_l (-2S_lq_l+\Omega_l) \nonumber  \\
%	&= 2\sum_l S_l(1-q_l)+\nu .
%\end{align}
%Also, the expectation value of occupation number in each level is
The Hamiltonian in terms of these canonical variables
$(\phi,j;\Phi,J)$ is given by
\begin{equation}
\mathcal{H}(\phi,j;J)
	= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
- \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} \cos\phi .
\label{TDHFB_Hamiltonian_3}
\end{equation}
with
\begin{equation}
	q_l=\frac{\Omega_l - J -2(-1)^l j}{\Omega_l} 
	\quad \mbox{ for } l=1,2.
	\label{q_l}
\end{equation}
Note that the Hamiltonian does not depend on the global gauge angle $\Phi$.
This leads to the particle number conservation, $dN/dt=0$.

%\begin{align}
%  \mathcal{H}(\phi(t),\pi(t);\Phi(t),\Pi(t)) =& \braket{Z|H|Z} \nonumber \\
%  =& \sum_{l=1,2} \epsilon_l(-2S_lq_l+\Omega_l) - g\sum_{l=1,2} \frac{S_l}{2}(2S_l(1-q_l^2)+(1-q_l)^2) \nonumber \\
%  &- 2g S_{1}S_{2}\sqrt{(1-q_{1}^2)(1-q_{2}^2)}\cos{\phi}.
%\label{hamiltonian}  
%\end{align}
%In (\ref{hamiltonian}), there is no $\Phi$ dependence in Hamiltonian, hence the expectation value of total particle number is conserved. The dependence of classical Hamiltonian becomes
%\begin{align}
%  \mathcal{H}(\phi(t)\},\pi(t);\Phi(t),\Pi(t))=\mathcal{H}(\phi(t),\pi(t),\Pi) .
%\end{align}
%\par

%The motion on $\Phi$ direction corresponds to pairing rotation. In quantum state, pairing rotational mode is labeled by quantum number $N$. The excitation states emerges in $N+2, N-2,\cdots$ system. In single-j system, the energy spectra is completely parabolic with respect to $N$. However, it contains higher order of $N$ from (\ref{hamiltonian}) in general system. \par
%Excluding the cyclic variable, all we have to study is the one dimensional motion on $\phi$ direction, which corresponds to pairing vibration. The excitation states in pairing vibrational mode emerges in the same $N$ system. We can understand the classical picture of pairing vibration in two dimensional phase space. The classical trajectory fulfills

The TDHFB equation can be written in a form of
the classical equations of motion:
\begin{eqnarray}
	&&\frac{d\Phi}{dt} = \frac{\partial\mathcal{H}}{\partial J} ,\quad\quad
\frac{dJ}{dt} = -\frac{\partial\mathcal{H}}{\partial \Phi} , \\
	&&\frac{d\phi}{dt} = \frac{\partial\mathcal{H}}{\partial j} ,\quad\quad
\frac{dj}{dt} = -\frac{\partial\mathcal{H}}{\partial \phi} .
\label{TDHFB_equation}
\end{eqnarray}
Since the $J=N/2$ and the total energy $E$ are constants of motion,
the TDHFB trajectories with given $N$ and $E$ are determined
in the two-dimensional phase space $(\phi,j)$ with the condition
\begin{equation}
  \mathcal{H}(\phi(t),j(t);J=N/2) = E.
\end{equation}
Examples of the classical trajectories in the phase space
$(\phi,j)$ are shown in Fig.~\ref{fig:phase_space}.
The figure shows contour lines of energy for systems,
which correspond to the TDHFB trajectories,
with $\Omega_1=\Omega_2=8$ and $N=16$ with different values of $g$.
%$N=16$ system with energy contour lines fulfilling (\ref{Sommerfeld}). 
The transition from normal to superfluid phase takes place at
$g=\Delta\epsilon(2\Omega)^{-1}$ with $\Delta\epsilon=\epsilon_2-\epsilon_1$.
Using a dimensionless parameter
$
  x = 2g\Omega/\Delta\epsilon,
$
at $x<1$, the ground state is normal with fully occupied
lower level $n_1=N$ and empty upper level ($n_2=0$).
All the TDHFB trajectories represent rotational behavior with respect to
relative angle $\phi$.
At $g=x=0$, the Hamiltonian becomes independent from $(\Phi,\phi)$, then,
the occupation numbers, $n_1$ and $n_2$, are constants of motion.
At $x>1$, the energy-minimum point and the closed trajectories appear around
%$-N/4 < \pi < N/4$ and $\phi=0$,
$j=j_0$ ($-N/4 < j_0 < N/4$) and $\phi=0$,
which suggests the vibrational behavior for $\phi$.
At higher energies, the trajectories become open (rotational-like),
which suggests a phase transition from super to normal phases
as a function of excitation energy.
%We have two types of trajectory, opened trajectory and closed trajectory. With BCS ground state, the closed trajectory which corresponds to a kind of condensed state may emerge in low-lying region. There is a phase transition point from closed trajectory to opened trajectory. Near the phase transition point, the fluctuation is important to deal with quantum states. The fluctuation causes the difficulty of the description by TDHFB theory.

In the single-$j$ model, since the second term in the Hamiltonian
(\ref{TDHFB_Hamiltonian_3}) is absent,
the Hamiltonian is exactly quadratic with respect to $N$,
$\mathcal{H}(N) = \mathcal{H}_0+(N-N_0)^2/(2\cal{J})$.
The moment of inertia for the pair rotation is 
$\mathcal{J}=2/g\times\Omega/(\Omega-1)\approx 2/g$
at $\Omega\rightarrow\infty$.
In the multi-$j$ case, the Hamiltonian contains higher-order
terms in general.

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
 \end{center}
 \caption{Energy contour plot for $\Omega_1=\Omega_2=8$ and $N=16$.
	The lines indicate the TDHFB trajectories fulfilling
	the EBK quantization condition of Eq. (\ref{EBK}).
	}
 \label{fig:phase_space}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Requantization of TDHFB for the two-level pair model}
\label{sec:requantization}

In order to determine energy eigenstates,
we need to requantize the TDHFB trajectories.
%The straightforward method is canonical quantization.  However, the canonical quantization has problem to deal with two-particle transition (see section 4).  To solve the problem, we also consider semiclassical approach, which is the approximation of path integral.
Since the present two-level model is integrable (Sec.~\ref{sec:TDHFB}),
it is feasible to apply the stationary-phase approximation to
the path integral expression.
In addition, we also study the canonical quantization of the TDHFB
Hamiltonian, and the matrix elements extracted by the Fourier components
\cite{CDS84}.
We show results of these different approaches to the pairing model.

\subsection{Stationary phase approximation to the path integral}
\label{sec:SPA}

Starting an arbitrary state $\ket{\psi(0)}$ at time $t=0$,
the time-dependent full quantum state can be written in the path integral form
\begin{equation}
\ket{\psi(t)}
	= e^{-iHt} \ket{\psi(0)}
	= \int d\mu(Z'') \ket{Z''} \int d\mu(Z')
	\int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)])
	e^{i\mathcal{S}[Z(\tau)]} \psi(Z') ,
\label{path_integral_expression}
\end{equation}
where $\psi(Z)\equiv \braket{Z|\psi(0)}$ and
the invariant measure $d\mu(Z)$ is defiend by 
the unity condition,
\begin{equation}
  \int d\mu(Z) \ket{Z}\bra{Z} = 1 .
  \label{unity}
\end{equation}
In Eq. (\ref{path_integral_expression}),
$\mathcal{S}[Z(\tau)]$ is the action (\ref{S}) along a given path $Z(\tau)$
with the initial coherent state $\ket{Z(0)}=\ket{Z'}$ and
the final state $\ket{Z(t)}=\ket{Z''}$,
then, the integration $\int \mathcal {D}\mu[Z(\tau)]$
is performed over all possible paths $\ket{Z(\tau)}$ between them.
Among all trajectories in the path integral,
the lowest stationary phase approximation selects
the TDHFB (classical) trajectories.
%\begin{align}
%	\int \mathcal{D}\mu(Z) e^{i\mathcal{S}(Z,Z_0)} \approx e^{i\mathcal{S}_{\rm cl}(Z,Z_0)} .
%\end{align}
\begin{equation}
	\ket{\psi(t)} \approx \int d\mu(Z') \ket{Z'_{\rm cl}(t)}
	e^{i\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z')} \psi(Z') ,
	\label{SPA}
\end{equation}
where the TDHFB trajectory starting from $\ket{Z'}$
ends at $\ket{Z'_{\rm cl}(t)}$ at time $t$.
The action $\mathcal{S}_{\rm cl}(Z_f,Z_i)$ is calculated along this
classical trajectory
connecting $Z_i=Z'_{\rm cl}(0)=Z'$ and $Z_f=Z'_{\rm cl}(t)$.
\begin{equation}
	\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z') \equiv \int_{0}^{t}
\braket{Z_{\rm cl}(t)|
	i\hbar\frac{\partial}{\partial t} - H
	|Z_{\rm cl}(t)} dt
	= \mathcal{T}[Z_{\rm cl}] - \mathcal{H}(Z',Z'^*) t 
	,
	\label{S_cl}
\end{equation}
with
\begin{equation}
\mathcal{T}[Z_{\rm cl}]\equiv
\int_{0}^{t} \braket{Z_{\rm cl}(t)| i\hbar\frac{\partial}{\partial t}
	|Z_{\rm cl}(t)} dt 
	= \int_{Z'}^{Z'_{\rm cl}(t)}
	\frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
  (Z_l^* dZ_l - Z_l dZ_l^*) .
\end{equation}
In the last equation of Eq. (\ref{S_cl}),
we used the fact that the TDHFB trajectory conserves the energy,
$\mathcal{H}(Z_{\rm cl}(t),Z_{\rm cl}^*(t))= \mathcal{H}(Z',Z'^*)$.
%We assume that only classical (TDHFB) trajectory contributes to the time dependent wave function

The energy eigenstates correspond to stationary states,
$\braket{Z|\psi(t)} \propto \braket{Z|\psi(0)}=\psi(Z)$,
which can be constructed by superposing the coherent states along
a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{path,path2,SM88}.
\begin{equation}
	\ket{\phi_k} = \oint d\mu(Z_{\rm cl}^{(k)}) \ket{Z_{\rm cl}^{(k)}}
	e^{i\mathcal{T}[Z_{\rm cl}^{(k)}]} .
\end{equation}
The single-valuedness of the wave function leads to
the quantization condition ($k$: integer)
\begin{equation}
	\mathcal{T}_\circ[Z_{\rm cl}^{(k)}]=
	\oint \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l^{(k)}|^2}
	\left(Z_l^{(k)*} dZ_l^{(k)} - Z_l^{(k)} dZ_l^{(k)*}\right) = 2k\pi .
	\label{EBK}
\end{equation}
The state evolves in time as $\ket{\phi(t)}=\ket{\phi}e^{-iE_k t}$,
with the energy of the $k$-th periodic trajectory,
$E_k=\mathcal{H}(Z_{\rm cl}^{(k)},Z_{\rm cl}^{(k)*})$.

Finding TDHFB trajectories satisfying the quantization condition
(\ref{EBK}) is an extremenly difficult task in general.
It is better founded and more practical
if the classical system is completely integrable.
In integrable systems, $M$ complex variables $Z(t)$ can be transformed into
the action-angle variables;
\begin{equation}
	Z(t) = \{Z_l(t);l=1,\cdots,M \} \rightarrow
	\{E; v_1,\cdots,v_{M-1}; \theta_1(t),\cdots,\theta_M(t)\} ,
\end{equation}
where the variables $E$ and $v$ define an invariant torus,
while $\theta(t)$ parameterize the coordinates on the torus.
The integration path of Eq. (\ref{EBK}) is now taken as topologically
independent closed path on the torus,
namely the EBK quantization condition.
There are $M$ independent closed paths and $M$ quantum numbers,
$k=(k_1,\cdots,k_M)$, to specify the stationary energy eigenstate.
These are associated with $M$ invariant variables,
$\{E_k;v_1^{(k)},\cdots,v_{M-1}^{(k)}\}$.
Using the invariant measure
\begin{align}
%  d\mu(Z) = \rho(Z)dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
  d\mu(Z) = \rho(E,v,\theta) dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
\end{align}
the $k$-th semiclassical wave function can be calculated as
\begin{equation}
  \ket{\phi_k} \propto \oint d\theta_1\cdots \oint d\theta_M \ 
	\rho(E_k,v^{(k)},\theta)
	\ket{E_k,v^{(k)},\theta} e^{i\mathcal{T}[E_k,v^{(k)},\theta]/\hbar} .
  \label{semi_wave_func}
\end{equation}
Here, we omit the integration with respect to the invariant variables,
$E$ and $v$.

%The wave function can be obtained after summing over whole phase space. In integrable system, we can write down the coordinates in $2M$ dimensional phase space as
%\begin{align}
%  Z = \{Z_{\mu}\} = \{E; v_1,\cdots,v_{M-1}; \theta_1(t),\cdots,\theta_M(t)\}
%\end{align}
%where $E$ is total energy, $v_i$ are invariant physical numbers and $\theta_i(t)$ are coordinates in torus. Having coordinate $q$ and conjugate momentum $p$, the Einstein-Brillouin-Keller (EBK) quantization condition is
%\begin{align}
%  \oint_{H(p,q)=E} \sum_i p_i dq_i = (n+\frac{\nu}{4})h  \hspace{2em} (n=1,2,\cdots)
%\end{align}
%where $h$ is plank constant and $\nu$ is the number of turning points in the trajectory. The EBK quantization condition attributes to Sommerfeld quantization
%\begin{equation}
%  \oint_{H(p,q)=E} p dq = (n+\frac{\nu}{4})h \hspace{2em} (n=1,2,\cdots),
%  \label{Sommerfeld}
%\end{equation}
%in one dimensional dynamics.

We apply semiclassical approach to the two-level pairing model.
The invariant measure in SU(2)$\otimes$SU(2) is 
\begin{align}
%	d\mu(Z) &= \prod_{l=1,2} \frac{S_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
%  &= \prod_l \frac{S_l+1}{4\pi}\sin{\theta_l}d\theta_ld\phi_l \\
%  &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi .
d\mu(Z) &= \prod_l \frac{\Omega_l+2}{2\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
  &= \prod_l \frac{\Omega_l+2}{8\pi}\sin{\theta_l}d\theta_ld\phi_l \\
	&= \left(\prod_{l=1,2} \frac{1+2\Omega_l^{-1}}{4\pi}\right)
             d\Phi dJ d\phi dj .
\end{align}
In the last equation, we transform the canonical coordinates
by Eqs. (\ref{phi}) and (\ref{pi}).
%In two-level system, we can transform the canonical coordinates by (\ref{phi}) and (\ref{pi}).
%After coordinate transformation, the Hamilton's equations are
%\begin{align}
%\left\{
%\begin{array}{c}
%  \dot{\Phi} = \frac{\partial\mathcal{H}}{\partial \Pi} \\
%  \dot{\Pi} = -\frac{\partial\mathcal{H}}{\partial \Phi} 
%\end{array}
%\right. \hspace{10mm} \left\{
%\begin{array}{c}
%  \dot{\phi} = \frac{\partial\mathcal{H}}{\partial \pi} \\
%  \dot{\pi} = -\frac{\partial\mathcal{H}}{\partial \phi} 
%\end{array}
%\right. , \label{Hamilton}
%\end{align}
%and the measure and action integral become
%\begin{align}
%  d\mu(Z) &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi \\
%  \mathcal{T}(Z) &=  \int (\Pi d\Phi+\pi d\phi) = \Pi\Phi + \int \pi d\phi.
%\end{align}
%The above canonical variables contain an invariant number $\Pi$. Because two-level system has 2*2 dimensional phase space, we need to find another conservative number before applying (\ref{semi_wave_func}). This task can be accomplished by canonical transformation 
Since the particle number $J=N/2$ and the total energy $E$ are invariant,
the two-level pairing model is integrable.
Thus, we can construct the semiclassical wave function using
Eq. (\ref{semi_wave_func}).
%This task can be accomplished by canonical transformation 
%\begin{align}
%  (\phi, \pi)  \to (t, E)
%\end{align}
%where $E$ is total energy in classical system.
The action integral is given by
\begin{equation}
	\mathcal{T}_k(\Phi,\phi;J)
%	= \Pi\Phi + \int \pi(t) \frac{d\phi}{dt} dt .
	= J\Phi + \int^\phi_{-\pi} j' d\phi' 
	= \frac{N}{2}\Phi + \int^t_0   %_{\mathcal{H}(\phi,\pi)=E_k}
	j(t') \frac{d\phi}{dt'} dt' 
\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
\end{equation}
where the integration $\int j d\phi$ is performed on the $k$-th
closed trajectory of Eq. (\ref{EBK}), and
the variables $(\phi,j)$ are transformed into $(t,E)$.
%where $\pi(t)$ can be solved from the right side of (\ref{TDHFB_equation}). (i.e. 2D Runge-Kutta method) \par
The semiclassical wave function fulfilling the EBK quantization condition
becomes
\begin{align}
	\ket{\phi_k^N} &\propto \oint d\Phi \oint dt
	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
	\ket{\Phi,t}_{N,E_k} \nonumber \\
%  &\propto \sum_k \frac{1}{k!}\int_0^{2\pi}d\Phi e^{i(\Pi-k)\Phi}\sum_{j=0}^{k}C_j^{(E,k)}\ket{S_1,-S_1+j;S_2,-S_2+(k-j)} \label{semi_wave_func1}
  &\propto \sum_{m=0}^{J}C_m^{(E_k,J)}\ket{S_1,-S_1+m;S_2,-S_2+(J-m)} ,
	\label{semi_wave_func1}
\end{align}
with $S_l=\Omega_l/2$, $J=N/2$, and the coefficients
\begin{align}
  C_m^{(E_k,J)} &= {}_J C_m\int_0^T dt \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
  & \hspace{5mm} A(q,S,m) = \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
\end{align}
where $T$ is the period of the closed trajectory.
The TDHFB-requantized wave functions (\ref{semi_wave_func1}) are
eigenstates of the total particle number.
This is due to the integration over the global gauge angle $\Phi$,
which makes the particle number projection not only for the ground state
but also for excited states.
See Appendix for detailed derivation of Eq.~(\ref{semi_wave_func1}).

Since we obtain the microscopic wave function of every eigenstate,
the expectation values and the transition matrix elements for any operator
can be calculated in a straightforward manner.
In Sec.~\ref{sec:results}, we show those of the pair-addition operator
$S^+$ which characterize properties of the pair condensates.

% In our system, we have two types of trajectory (Figure \ref{trajectory}). For opened trajectory, we define the size which is surrounded by one periodic trajectory and horizontal axis. Under this definition, the size changes smoothly when the trajectory changes from closed to opened. 
%
%\begin{figure}[htbp]
% \begin{minipage}{0.5\hsize}
% \begin{center}
%%  \includegraphics[bb=0 0 120 120]{images/Sommerfeld1.png}
% \end{center}
% \end{minipage}
% \begin{minipage}{0.5\hsize}
% \begin{center}
%%  \includegraphics[bb=0 0 120 120]{images/Sommerfeld2.png}
% \end{center}
% \end{minipage}
%  \caption{The painted parts correspond to the left side of (\ref{Sommerfeld}). Left figure shows the size surrounded by closed trajectory, right figure shows the size surrounded by one periodic opened trajectory and horizontal axis.}
%  \label{trajectory}
%\end{figure}

Before ending this section, let us note the periodic conditions
of the coordinates and the quantization condition.
Since the two original variables, $(\chi_1,\chi_2)$,
are independent periodic variables of the period $2\pi$,
in addition to the trivial periodicity of $2\pi$ for $\Phi$ and of $4\pi$
for $\phi$,
we have periodic conditions for
$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\pm 2\pi)$ and
$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\mp 2\pi)$.
The former (latter) corresponds to $\chi_2\pm 2\pi$ ($\chi_1\pm 2\pi$)
with $\chi_1$ ($\chi_2$) being fixed.
For open TDHFB trajectory (e.g., Fig.~\ref{fig:phase_space}),
the quantization condition becomes
\begin{equation}
 \mathcal{T}_{N,E_k}(\Phi,T/2)
	= \pm \frac{N}{2} \pi + \int_{-\pi}^\pi j d\phi
	= 2k\pi .
\end{equation}
This leads to the following:
\begin{equation}
	\int_{-\pi}^\pi j d\phi = 
	\begin{cases}
		2k\pi & \mbox{ for } N=4n ,\\
		(2k+1)\pi & \mbox{ for } N=4n+2 ,
	\end{cases}
	\label{EBK_2}
\end{equation}
where $k$ and $n>0$ are integer numbers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Canonical quantization}
\label{sec:canonical}

The most common approach to the quantization of the nuclear collective model
is the canonical quantization \cite{BM75}.
In the pairing collective model, the canonical quantization
was adopted in previous studies \cite{BBPK70,delta1,delta3}.
Assuming magnitude and phase of the pairing gap as collective coordinates,
a collective Hamiltonian was constructed in the second order in momenta.
Then, the Hamiltonian was quantized by the canonical quantization
with the Pauli's prescription.
In this section, we apply similar quantization method to
the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
The main difference is that the collective canonical variables are
not assumed in the present case, but are obtained from the TDHFB dynamics
itself.
%The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation

The quantization method is not unique.
A common choice in the nuclear collective model is the Pauli's prescription.
However, it is not straightforward to apply it to the present case, 
because the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3})
is not limited to the second order in momenta.
In the present study, we adopt a simple symmetrized ordering, as
\begin{align}
	H(\hat{\phi},\hat{j},\hat{J})
	&= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l (1-q_l) 
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
	\nonumber \\
	&- \frac{g}{4}\Omega_{1}\Omega_{2}
	\left\{ \sqrt{(1-q_{1}^2)(1-q_{2}^2)}\cos{\hat{\phi}}
	+ \cos{\hat{\phi}}\sqrt{(1-q_{1}^2)(1-q_{2}^2)} \right\} .
\label{canonical_quantized_H}
\end{align}
As in Eq. (\ref{q_l}), $q_l$ contain $J$ and $j$ which
are replaced by
\begin{equation}
%  [\hat{\Phi},\hat{\Pi}] = i, \hspace{2em} [\hat{\phi},\hat{\pi}] = i .
	\hat{J} = -i\frac{\partial}{\partial\Phi},\quad\quad
	\hat{j} = -i\frac{\partial}{\partial\phi} .
\end{equation}
%Because quantized Hamiltonian must be Hermitian, 
%the ordering in mixing term of $\phi$ and $\pi$ is not unique. 
%However, we apply the quantization procedure of Hamiltonian in (\ref{2level}) as follows
Since $\Phi$ is a cyclic variable, 
we write the collective wave function $\Psi(\Phi,\phi)$ as eigenstates
of the particle number $N$ in a separable form
\begin{equation}
  \Psi_k^{(N)}(\Phi,\phi) = 
	\frac{1}{\sqrt{2\pi}}e^{i\frac{N}{2}\Phi}\psi_k^{(N)}(\phi) .
\end{equation}
Then, the problem is reduced to the one-dimensional Schr\"{o}dinger
equation for the motion in the relative angle $\phi$.
%pairing vibrational mode can be obtained by solving the Schrodinger equation
\begin{equation}
	H\left( \phi,-i\frac{d}{d\phi},\frac{N}{2} \right)
	\psi_k^{(N)}(\phi) = E_k^{(N)}\psi_k^{(N)}(\phi),
	\label{Schroedinger_eq}
\end{equation}
%where $i$ is the excitation index under the system of fixed total particle number $N$. To solve the Schrodinger equation, the wave function can be expanded as
%we consider two different methods, which are classified by Type I and Type II.\par
%Type I: periodic boundary condition.

The wave function should have a periodic property with respect to
the variable $\phi$;
$\psi_k(\phi)=\psi_k(\phi+4\pi)$.
For the adopted simple ordering of Eq. (\ref{canonical_quantized_H}),
it is convenient to use the eigenstates of $\hat{j}$ as the basis
to diagonalize the Hamiltonian.
They are
\begin{equation}
%  \hat{\pi}\chi_\nu(\phi) = \nu \chi_\nu(\phi) \\
	\chi_p(\phi) = \frac{1}{\sqrt{4\pi}} e^{ip\phi} ,
	\quad\quad\mbox{with $p$: integer or half integer} .
\end{equation}
Since the Hamiltonian (\ref{canonical_quantized_H}) contains only
terms linearly proportional to $e^{\pm i\phi}$,
the basis states $\chi_p$ with half-integer difference in $p$
are not coupled with each other.
Thus, the eigenstates of Eq. (\ref{Schroedinger_eq}) can be expanded as
\begin{equation}
	\psi_k^{(N)}(\phi) = 
	\sum_{p=p_{\rm min},p_{\rm min}+1,\cdots}^{p_{\rm max}}
	c_{k,p}^{(N)} \chi_p^{(N)}(\phi) .
	\label{CQ_eigenstate}
\end{equation}
According to the relation $j=(n_2-n_1)/4=(N-2n_1)/4$ in Eq. (\ref{momentum}),
we adopt the (half-)integer values of $p$ for $N=4n$ ($N=4n+2$)
with integer $n$.
This is consistent with the quantization condition (\ref{EBK_2}).
The coupling term with different $p$
in Eq. (\ref{canonical_quantized_H}) vanishes
for $n_l=0$ and $n_l=2\Omega_l$,
which restricts values of $p$ in a finite range of
$p_{\rm min}\leq p \leq p_{\rm max}$.

%where $\nu_0$ is the minimum value of $\nu$.
%$\chi_m(\phi)$ is the eigenfunction of momentum operator fulfills
%\begin{align}
%  \hat{\pi}\chi_m(\phi) = p_m \chi_m(\phi) \\
%  \chi_m(\phi) \propto e^{ip_m\phi} .
%\end{align}
%Due to the periodic boundary condition in coordinate space of Hamiltonian
%\begin{equation}
%  H(\phi) = H(\phi+2\pi)
%\end{equation}
%and the integer or half-integer number of $p_m$ in maximum and minimum value, the wave function fulfills
%\begin{equation}
%  \psi_i(\phi) = 
%  \left\{ 
%  \begin{array}{c}
% \psi_i(\phi+2\pi) \hspace{2em} ({\rm for} \hspace{1em} p_m=m) \\    
% -\psi_i(\phi+2\pi) \hspace{2em} ({\rm for} \hspace{1em}  p_m=m/2) \\    
%  \end{array}
%  \right.  
%\end{equation}
%and $p_m$ must increase or decrease in increments of one 
%\begin{align}
%  p_{min}, p_{min}+1, \cdots ,p_{max}-1, p_{max} .
%\end{align}
%Therefore, we can easily diagonalize the Hamiltonian in the basis of momentum eigenfuction.\par
\begin{comment}
Type II: adiabatic solution. We employ a canonical transformation
\begin{align}
  Q = Q(\phi,\pi) = \pi, \hspace{2em} P = P(\phi,\pi) = -\phi
\end{align}
assuming $\pi$ as a coordinate and $\phi$ as a conjugate momentum. Because wave function is expected to be localized in $\phi$ space when pairing correlation is strong, we expand $\phi$ up to second order. The change in Hamiltonian is only
\begin{align}
  \cos{\phi} = \cos{P} \to 1 + \frac{1}{2}\frac{\partial^2}{\partial Q^2} .
\end{align}
In this solution, there is no periodic boundary condition, which opposite to Type I. \par
\end{comment}

In order to estimate the two-particle transfer matrix elements,
we construct the corresponding operators as follows.
The classical form of matrix elements are obtained as
\begin{align}
  S_+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_+|Z} = \left( S_1\sqrt{1-q_1^2}e^{-i\phi/2}+S_2\sqrt{1-q_2^2}e^{i\phi/2} \right) e^{i\Phi}
	\label{Sp_mean_value} \\
  S_-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_-|Z} = \left( S_1\sqrt{1-q_1^2}e^{i\phi/2}+S_2\sqrt{1-q_2^2}e^{-i\phi/2} \right) e^{-i\Phi} .
	\label{Sm_mean_value}
\end{align}
%For simplicity, we ignore the part of off-diagonal element (e.g. $\braket{Z'|\hat{S}_+|Z}$). 
%To requantize the two-particle transition operators, 
Again, we adopt a simple symmetrized ordering for the quantization:
\begin{eqnarray}
%  &S_+(\Phi,\Pi;\phi,\pi) \to S_+(\hat{\Phi},\hat{\Pi};\hat{\phi},\hat{\pi}) \nonumber \\
  S_\pm (\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
	&=& \frac{1}{4}\left( \Omega_1\sqrt{1-q_1^2}e^{\mp i\hat{\phi}/2}
+\Omega_2\sqrt{1-q_2^2}e^{\pm i\hat{\phi}/2} \right) e^{\pm i\hat{\Phi}} 
	\nonumber \\
&+ & \frac{1}{4}e^{\pm i\hat{\Phi}}\left( 
e^{\mp i\hat{\phi}/2}\Omega_1\sqrt{1-q_1^2}
+e^{\pm i\hat{\phi}/2}\Omega_2\sqrt{1-q_2^2} \right) .
\end{eqnarray}
The exponential factors $e^{\pm i\Phi}$ change
the total particle number $N\rightarrow N\pm 2$,
while $e^{\pm i\phi/2}$ change the relative numbers,
$n_2-n_1 \rightarrow n_2-n_1 \pm 2$.
%For example, the pair-additional transition strength in requantized form is
Using these operators,
the pair-addition transition strengths are calculated as
\begin{align}
B(P_{\rm ad};k\rightarrow k') &=
|\braket{N',k'|S_+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})|N,k}|^2
	\nonumber \\
&= \left| \int_{0}^{2\pi}d\Phi \int_{-2\pi}^{2\pi}d\phi 
	\psi^{(N')*}_{k'}(\phi) e^{-i\frac{N'}{2}\Phi}
	S_+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
	\psi^{(N)}_{k}(\phi)e^{i\frac{N}{2}\Phi} \right|^2,
\end{align}
which automatically vanishes for $N'\neq N+2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fourier decomposition of time-dependent matrix elements}
\label{sec:Fourier}

The requantization and calculation of the matrix elements can be also
performed using the time-dependent solutions of the TDHFB.
It was proposed and applied to the two-level pairing model \cite{CDS84},
which we recapitulate in this section.

The TDHFB provides a time-dependent solution $Z(t)$ starting from
a given initial state $Z(0)$.
The energy eigenvalues and the corresponding closed trajectories
are determined from the EBK quantization condition (\ref{EBK}).
The pair transfer matrix elements are evaluated as the Fourier components
of the time-dependent mean values $S_\pm(t)=S_\pm(Z(t))$,
Eqs. (\ref{Sp_mean_value}) and (\ref{Sm_mean_value}).
%In the ground state, the motion in the global gauge angle $\Phi$
%is independent from the $\phi$ motion.
Since the global gauge angle $\Phi$ is a cyclic variable,
the motion in the relative gauge angle $\phi$ is independent from $\Phi$.
Thus, we calculate the time evolution of $\phi(t)$, and
find the period of the $k$-th closed trajectory $T$
satisfying Eq. (\ref{EBK}).
Then, the Fourier component,
\begin{equation}
	\tilde{S}_\pm(E_k; \omega) = \frac{1}{T}\int_0^T dt
	e^{i\omega t} S_\pm(t) ,
\label{Fourier_decomposition}
\end{equation}
corresponds to the pair transfer matrix element from the state $k$ to $k'$
when $\omega=2\pi (k'-k)/T$.
The pair-addition transition strengths are calculated as
\begin{equation}
	B(P_{\rm ad};k\rightarrow k') 
	= \left|\tilde{S}_+\left(E_k;\frac{2\pi}{T}\Delta k \right) \right|^2 ,
\end{equation}
with $\Delta k=k'-k$.
In this approach, the transition between the ground states of
neighboring nuclei ($N\rightarrow N+2$) corresponds to
the stationary component ($k=0$ and $\Delta k=0$),
namely the expectation value in the BCS approximation.

The derivation  of Eq. (\ref{Fourier_decomposition})
is based on the wave packet in the
classical limit \cite{LL65}.
The TDHFB state is assumed to be a superposition of eigenstates
in a narrow range of energy $E_{k_0}-\Delta E<E_k<E_{k_0}+\Delta E$,
\begin{equation}
	\ket{Z(t)} = \sum_N \sum_k c_k^N \ket{\phi_k^N} e^{-iE_k t} ,
	\label{superposition}
\end{equation}
where the eigenenergies are evenly spaced and
the coefficients $c_k^N$ slowly vary with respect to $k$ and $N$.
The expectation value of $S_\pm$ is
\begin{equation}
	S_\pm(t) = \sum_{N} \sum_{k,k'} c_{k'}^{N+2*} c_k^N 
	\braket{\phi_{k'}^{N+2}|S_\pm|\phi_k^N} e^{i(E_{k'}-E_k)t} .
\end{equation}
The matrix element $\braket{\phi_{k'}^{N+2}|S_\pm|\phi_k^N}$
quickly disappears as $|k'-k|$ increases, while it stays almost constant
for the small change of $k$ and $N$ with $|k'-k|$ being fixed.
Thus, we may approximate $c_{k'}^{N+2}\approx c_k^N$,
$E_{k'}-E_k\approx \omega_0 \Delta k$, and
that $\braket{\phi_{k'}^{N+2}|S_\pm|\phi_k^N}\approx
\braket{\phi_{k_0+\Delta k}^{N+2}|S_\pm|\phi_{k_0}^N}$ 
\begin{equation}
	S_\pm(t) \approx \sum_{N} \sum_{k} \left|c_k^N\right|^2
	\sum_{\Delta k}
	\braket{\phi_{k_0+\Delta k}^{N+2}|S_\pm|\phi_{k_0}^N}
	e^{i\omega_0 \Delta k t} 
	= \sum_{\Delta k}
	\braket{\phi_{k_0+\Delta k}^{N+2}|S_\pm|\phi_{k_0}^N}
	e^{i\omega_0 \Delta k t}  ,
\end{equation}
where $k_0$ is a representative index value of the superposition in 
Eq. (\ref{superposition}).
From this classical wave packet approximation,
we obtain Eq. (\ref{Fourier_decomposition}).
It is not trivial to justify the approximation for small values of $\Omega$
and for transitions around the ground state.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

In this section, we study the seniority-zero states ($\nu_1=\nu_2=0$) in
the two-level system with equal degeneracy, $\Omega_1=\Omega_2=\Omega$.
Since all the properties are scaled with the ratio, $g/\Delta\epsilon$,
where $\Delta\epsilon$ is the level spacing
$\Delta\epsilon=\epsilon_2-\epsilon_1$,
we define a dimensionless parameter to control the strength of
the pairing correlation;
\begin{align}
  x = 2\Omega\frac{g}{\Delta\epsilon} .
\end{align}
For sub-shell-closed systems with $N=2\Omega$ system,
the transition from normal ($x<1$) to superfluid ($x>1$) states
takes place at $x=1$

%We consider two types of system: [1. Ideal type] $\Omega$ is large, which causes BCS approximation works very well for $x>>1$; [2. Realistic type] $\Omega$ is comparable to the capacity of single particle level between neighborhood magic numbers in nuclei. For each type, we consider the dynamics for $N=\Omega$ (half-filled) and $N=2\Omega$ (closed shell) system.\par

%In excitation energy spectra, we also used harmonic approximation to compare with both requantization methods. The excitation energy in harmonic approximation is expressed by mass parameter and second derivative of potential
%\begin{align}
%  \omega = \sqrt{\frac{V''(\pi)}{B(\pi)}}
%\end{align}
%where
%\begin{align}
%\left\{
%\begin{array}{c}
%  V(\pi) = \sum_{l=1,2} \epsilon_l(-2S_lq_l+\Omega_l) - g\sum_{l=1,2} \frac{S_l}{2}(2S_l(1-q_l^2)+(1-q_l)^2) - 2gS_{1}S_{2}\sqrt{(1-q_{1}^2)(1-q_{2}^2)} \\
%  B^{-1}(\pi) = 2gS_{1}S_{2}\sqrt{(1-q_{1}^2)(1-q_{2}^2)}
%\end{array}
%\right. .
%\end{align}
%Because of one-dimensional system, we only obtain the lowest excitation energy from harmonic approximation.

%The two-nucleon transfer reaction is a specific probe of pairing correlation. We define pair additional transition strength as
%\begin{align}
%  B(Pad) \equiv |\braket{N+2,\beta|S_+|N,\alpha}|^2
%  \label{Pad}
%\end{align}
%where $\alpha,\beta$ are the excitation index in fixed particle number system. 
%\begin{comment}
%To estimate the requantization method, we also define the ratio of transition strength
%\begin{align}
%  r \equiv \frac{B(Pad)_{req}}{B(Pad)_{exact}}.
%  \label{ratio}
%\end{align}
%$B(Pad)_{req}$ indicates the result from canonical quantization or semiclassical approach. The requantization result is perfect when $r=1$.
%\end{comment}

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
and the canonical quantization (Sec.~\ref{sec:canonical}) as ``CQ''.
In addition, the harmonic approximation at the ground state is
called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.

\subsection{Large-$\Omega$ cases}

In the limit of $\Omega\rightarrow\infty$,
we expect that the classical approximation becomes exact.
Here, we adopt $\Omega=50$ with $N=100$ (closed-shell configuration)
and $N=50$ (mid-shell configuration).

%The system consists of $\Omega=50$ and $\Delta\epsilon=1$(MeV). We show the results in $N=50$ system, which is always superfluidity in ground state.\par
Calulated excitation energies are shown in Figs.~\ref{fig:N50energy}
and \ref{fig:N100energy}.
The results of SPA/FD and CQ are compared with the exact values.
At the weak pairing limit of $x\rightarrow 0$,
the excitation energies are multiples of $2\Delta\epsilon$, 
which correspond to pure $2n$-particle-$2n$-hole excitations.
Both the weak and the strong pairing limits
are nicely reproduced by all the calculations,
while the CQ method produces excitation energies slightly lower than the
exact values in an intermediate region around $x=1$.
It is somewhat surprising to see that the deviation is larger for
the case of the mid-shell configuration ($N=50$) than the closed shell
($N=100$).

%Both requantization methods converge to exact solution in no pairing and strong pairing limit. However, we can see the result from canonical quantization is under estimated around $x=1$, while semiclassical approach is almost perfect in all region. The lowest excitation energy obtained from harmonic approximation well reproduces exact result.

The deviation in the CQ method is mainly due to the zero-point energy
in the ground state.
Since we solve the collective Schr\"odinger equation (\ref{Schroedinger_eq})
with the quantized Hamiltonian of Eq. (\ref{canonical_quantized_H}),
the zero-point energy $\Delta E>0$ is inevitable in the CQ method.
The $\Delta E$ is associated with the degree of localization of
the wave function.
Thus, the magnitude of $\Delta E$ for ``bound'' states are different
from that for ``unbound'' states.
See Fig.~\ref{fig:phase_space}.
In the strong pairing limit, the potential minimum is deep enough to bound
both ground and excited states.
Conversely, all the states are unbound in the weak limit.
In both limits, $\Delta E$ for ground and excited states are similar,
and they are canceled for the excitation energy.
However, near $x=1$, the ground state is bound,
while the excited states are unbound.
In this case, $\Delta E$ is larger in the ground state than in the
excited states, which makes the excitation energy smaller.
This also explains the difference between the mid-shell and closed-shell
configurations.
In the closed shell, all the states are unbound for $x<1$,
while, in the mid-shell,
there is a region in $x<1$ where the ground state is bound but
the excited state is unbound.

The obtained wave functions in the SPA and the CQ can be decomposed in the
$2n$-particle-$2n$-hole components in Fig.~\ref{fig:N50_occ}.
In the SPA, it is done as Eq. (\ref{semi_wave_func1}) and
the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
in Fig~\ref{fig:N50_occ}.
For the CQ, $|c_{k,p}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
Here, $m$ and $p$ are related to each other, $2p=J-2m$.
They show excellent agreement with the exact results, not only for the
ground state but for excited states.
We find the SPA is even more precise than the CQ.

Next, let us discuss the transition matrix elements.
The calculated pair-addition strengths $B(P_{\rm ad})$ are shown in
Fig.~\ref{fig:N50Pad} for $N=98\rightarrow 100$ and $N=48\rightarrow 50$.
In this paper, we discuss only $k=0$ (ground state) and $k=1$
(1st excited $\nu=0$ state).
The FD calculation is based on the time evolution of the expectation 
value $S_+(t)$ with fixed $(J,\Phi)$ in Eq. (\ref{Fourier_decomposition}).
%There is some ambiguity for the calculation of $S_+(t)$,
%namely, for which trajectory we should calculate $S_+(t)$.
For $(N,k)\rightarrow (N+2,k')$ transitions,
we basically adopt the trajectories for the initial state, namely,
the one with $J=N/2$ satisfying the $k$-th EBK quantization condition.
The $k\rightarrow k$ ($\Delta k = 0$)  transitions
correspond to the intraband transitions of the
pair-rotational band, when the state is deformed in the
gauge space (pair deformation).
For the ground-state band ($k=0$),
this is nothing but the expectation value at the BCS wave function.
The calculation trivially leads to vanishing interband transitions for 
$k=0\rightarrow k'$ ($k'\neq 0$), because the $S_+(t)$ is stationary
in the ground state.
Thus, for the interband transition of $(N,k=0)\rightarrow (N+2,k=1)$
transitions, the trajectory satisfying the EBK condition of $k=1$ is used to
perform the Fourier decomposition (\ref{Fourier_decomposition})
of $\omega=2\pi/T$.

Near the closed-shell configuration ($N=98\rightarrow 100$),
the pair-addition strengths for the intraband transitions ($\Delta k=0$)
drastically increase around $x=1$.
This reflects a character change from the pair vibration ($x\lesssim 1$)
to the pair rotation ($x\gtrsim 1$).
The $B(P_{\rm ad}; k\rightarrow k)$ in the pair-rotational transitions
are about 20 times larger than those in the vibrational transitions.
The interband $B(P_{\rm ad}; 0\rightarrow 1)$ are similar to
the $B(P_{\rm ad}; 0\rightarrow 0)$ in the vibrational region
($x\lesssim 1$), because they both change the number of pair-phonon quanta
by one unit.
In contrast, $B(P_{\rm ad}; 1\rightarrow 0)$, which change the phonon
quanta by two, are almost zero.
In the pair-rotational region ($x \gg 1$),
$B(P_{\rm ad}; 1\rightarrow 0)$ and $B(P_{\rm ad}; 0\rightarrow 1)$
are roughly identical,
while their magnitude is significantly smaller than
$B(P_{\rm ad}; 0\rightarrow 1)$ at $x\lesssim 1$.
This indicates the character change of the $k=1$ states
from the vibration around the ``spherical'' ground state
to that around the ``deformed'' ground state.
This is analogous to the quadrupole vibrations in spherical nuclei
and the beta vibrations in deformed nuclei, respectively.
The latter may correspond to the Higgs amplitude mode.

In the mid-shell region ($N=48\rightarrow 50$),
the intraband $B(P_{\rm ad}; k\rightarrow k)$ are smoothly increase as
$x$ increases.
Their values are larger than the interband strengths by about one order
of magnitude, indicating the pair-rotational character.
The interband $B(P_{\rm ad}; 0\rightarrow 1)$ shows a gradual decrease
as a function of $x$, while
$B(P_{\rm ad}; 1\rightarrow 0)$ are negligibly small,
even at $x\gg 1$.
This present a prominent difference from the closed-shell case.

All the features are nicely reproduced in the SPA method,
for both the closed- and mid-shell configurations.
The CQ method qualitatively agree with the exact calculation.
For instance, the order-of-magnitude difference between intraband
and interband transitions.
However, the precision of the CQ method is not so good,
especiallyaround $x=1$.
The FD method properly describes the main features
in the superflud phase, while it fails for the normal phase
($x\lesssim 1$). 
In the mid-shell configuration, the ground state is always
in the superfluid phase at $x>0$,
while the $k=1$ excited state corresponds to
the open (closed) trajectory at $0<x\lesssim 1$ ($x\gtrsim 1$).
For the open trajectory, the FD produces wrong values.
However, somewhat surprisingly,
the SPA results, which use these open trajectories for the construction
of wave functions,
reproduce main features of the exact results.

%The two-particle transition strength from $N=48$ to $N=50$ is shown in Figure \ref{fig:N50Pad}. We plotted four types of transition, $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$. $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ correspond to pairing rotational transition, while $\ket{0_1^+}\to\ket{0_2^+}$ and $\ket{0_2^+}\to\ket{0_1^+}$ correspond to pairing vibrational transition. We can find the pairing rotational transition are much stronger than pairing vibrational transition in whole region. The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system. In canonical quantization, the pairing rotational transition is quantitatively reproduced, while the pairing vibrational transition is under estimated in $x<1.5$. In semiclassical approach, not only the pairing rotational transition is almost perfectly reproduced, but also the pairing rotational transition has the same tendency with exact solution. Because $\ket{0_2^+}$ has one node, in $\ket{0_1^+}\to\ket{0_2^+}$, most of component of matrix element are canceled with each other, causing weak transition strength. Hence the under estimation of $\ket{0_1^+}\to\ket{0_2^+}$ in semiclassical approach is not serious.\par
%From numerical results in ideal case, even though semiclassical approach is better than canonical quantization, canonical quantization is still able to describe physical values quantitatively. This is due to high collectivity of pairing in large $\Omega$ system.

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_woType2.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_woType2.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N50Pad}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Small-$\Omega$ cases}

Next, we discuss systems with smaller degeneracy $\Omega=8$.
Again, we study systems near the closed-shell and the mid-shell configurations.
%$N=8$ system, which is always superfluidity in ground state; (2) $N=16$ system, which has phase transition at $x=1$ in ground state.\par

\subsubsection{Mid-shell configuration}

The calculated excitation energies are shown in Fig.~\ref{fig:N8energy}
for the $N=8$ case.
The SPA/FD reproduces the exact calculation in the entire region of $x$,
not only for the lowest but also for higher excited states.
The CQ reproduces the exact result in a weak pairing region ($x\lesssim 1$),
while it underestimates the excitation energies at $x\gtrsim 1$.
Analogous to the case of $\Omega=50$,
this is mainly due to effect of the zero-point energy $\Delta E$.
The ground-state energy in the CQ calculation 
is bound at $x\gtrsim 1$ ({\bf need to check}).
However, because of the weak collectivity with $N=8$,
the first excited state stays unbound even at the maximum $x$ in 
Fig.~\ref{fig:N8energy}.
Therefore, the energy shift $\Delta E>0$ is larger in the ground state,
which makes the excitation energy smaller.

The wave functions are plotted in Fig.~\ref{fig:N8_occ}. 
At the weak pairing case of $x=0.5$,
both the SPA and the CQ reproduce the exact result.
At $x=2$, the squared coefficients of the ground state is peaked at the
lowest $p$, which suggests that the state is not deeply bound in the
potential.
It is in contrast to the symmetric shape in Fig.~\ref{fig:N50_occ}.
The wave functions obtained by the CQ method has noticeable deviation
from the exact result.
On the other hand, the SPA wave functions are almost identical to the
exact ones.

%At no pairing limit, the excitation energies are multiples of $2\Delta\epsilon$. Both requantization methods converge to exact solution in no pairing limit. However, we can see the result from canonical quantization is under estimated after $x=1$, while semiclassical approach is almost perfect in all region. The lowest excitation energy obtained from harmonic approximation well reproduces exact result. 
%We can find both requantization methods reproduce well in $x=0.5$, and semiclassical approach is better than canonical quantization in $x=2$.

The pair-addition transition strengths from $N=6$ to $N=8$ are
shown in Fig.~\ref{fig:N8Pad}.
The intraband $k\rightarrow k$ transitions increase and 
the interband $k\rightarrow k\pm1$ transitions decrease as
functions of $x$.
Their relative difference becomes
more than one order of magnitude at $x\gtrsim 2$.
Thus, even at relatively small $\Omega$ and $N$,
the intraband transitions in the pair rotation is qualitatively different
from the interband transitions.

We find the excellent agreement between the SPA and the exact calculations.
The first excited state corresponds to the open trajectory which
turns out to almost perfectly reproduces the exact wave function.
In contrast, this open trajectory produces results far from the exact
result in the FD method.
It produces almost vanishing the intraband
$B(P_{\rm ad}; 1\rightarrow 1)$ and the interband transitions.
The $B(P_{\rm ad}; 0\rightarrow 0)$ shows a qualitative agreement for
its behavior, but is significantly underestimated.
The CQ method also underestimates the intraband transitions.

%The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system. In canonical quantization, all transition strengths are failed to reproduce quantitatively. In semiclassical approach, however, both pairing rotational transition and pairing vibrational transition are reproduced quantitatively in all region. \par
%In above case, semiclassical approach is much better than canonical quantization. The low collectivity of pairing in small $\Omega$ system influences significantly the methods of requantization. Nevertheless, semiclassical approach can still describe physical values quantitatively as in ideal case.

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=8$ system.}
 \label{fig:N8energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ_woType2.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ_woType2.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-2$ corresponds to 0p8h configuration, $-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=6$ to $N=8$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N8Pad}
\end{figure}

\subsubsection{Closed-shell configuration}

In the closed shell with $N=16$,
the minimum-energy trajectory changes at $x=1$ from
$p=-4$ (normal phase) to
the BCS minimum $p>-4$ and $\phi=0$ (superfluid phase).
At the transitional point ($x=1$), the harmonic approximation is
known to collapse, namely to produce zero excitation energy.
In Fig.~\ref{fig:N16energy},
this collapsing is avoided in all the calculations (SPA/FD and CQ).
The behaviors of the lowest excitation agree with the exact calculations,
while the CQ method substantially underestimates those for higher states.
This is again due to the difference in the zero-point energy in
the ground and the excited states.
In the CQ calculation, the first excited state is bound at $x\gtrsim 1.?$,
but the second excited state is unbound for $x\lesssim 3.?$.

Near the transition point from the open to closed trajectories,
the wave functions calculated with the SPA and CQ methods somewhat differ
from the exact ones.
In Fig.~\ref{fig:N16_occ}, the wave functions at $x=0.5$ and 2 are presented.
They agree with exact calculation at $x=0.5$.
In contrast, we find some deviations for the first excited state ($k=1$)
at $x=2$.
This is because the $k=1$ trajectory corresponding to the first excited state
changes its character from open to closed at $x\approx 1.8$ {\bf need to check}.
Therefore, the first excited wave function is difficult to reproduce in
the SPA, although the wave functions for
the ground and higher excited states show reasonable agreement.
The similar disagreement is observed for the ground state near $x=1$.

%The excitation energy is shown in Figure \ref{fig:N16energy}. At no pairing limit, the excitation energies are multiples of $2\Delta\epsilon$. Both requantization methods converge to exact solution in no pairing limit, while under estimate the exact solution after $x=1$. However, semiclassical approach is close to exact solution. The lowest excitation energy obtained from harmonic approximation emerges after $x>1$, and well reproduces exact result in strong pairing limit. 
%The occupation probability in such excited states is plotted in Figure \ref{fig:N16_occ}. We can find both requantization methods reproduce well in $x=0.5$, and both methods have some disagreement of $\ket{0_2^+}$ and $\ket{0_3^+}$ in $x=2$. 
%This disagreement is caused by large fluctuation close to phase transition point (in Figure \ref{phase_space}, the changing from closed trajectory to opened trajectory). After the phase transition, the occupation probability of $\ket{0_4^+}$ is also well reproduced in semiclassical approach.

Singular behaviors near the transition points can be also observed in
the pair-addition transition strengths ($N=14\rightarrow 16$) shown
in Fig.~\ref{fig:N16Pad}. 
At $x=1$, the intraband $B(P_{\rm ad}; 0\rightarrow 0)$ shows a kink
in the SPA,
and $B(P_{\rm ad}; 1\rightarrow 1)$ shows another kink at $x\approx 1.8$.
These exactly correspond to the transition points from open to closed
trajectories.
Nevertheless, the overall behaviors are well reproduced and
the values at the weak and strong pairing limit are well reproduced
in the SPA.
The CQ calculation also shows smoothed kink-like behaviors near the
transition points.
The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
because $S_+(t)$ is calculated for a $N=14$ system.
Both intraband and interband transitions reasonably agree with
the exact results at $x\gtrsim 1.8$,
while the $k=1$ state is not properly reproduced at $x\lesssim 1.8$
with the open trajectory.

%Between pairing rotational transition and pairing vibrational transition, we can find the transition strength are compareable in $x<1$, and pairing rotational transition are dominant in $x>1$. The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system.  In canonical quantization, even though the tendency of $\ket{0_1^+}\to\ket{0_1^+}$ are reproduced, all transition strengths are failed to reproduce quantitatively. In semiclassical approach, the strengths have disagreement around phase transition region, but are recovering toward no pairing and strong pairing limit. \par
%In closed shell system, the phase transition is semiclassical approach is more quantitative than canonical approach except phase transition region.

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=16$ system.}
 \label{fig:N16energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ_woType2.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ_woType2.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=14$ to $N=16$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N16Pad}
\end{figure}
%In realistic type, semiclassical approach is much better than canonical quantization in every physical values, especially in two-particle transition. The most difficult case is closed shell system with BCS phase transition. However, semiclassical approach works well in closed shell system except phase transition region.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Collective model treatment}

In literatures, the collective model has been proposed
and utilized for the nuclear pairing dynamics.
For those studies, the pairing gap parameter is assumed to be the
collective coordinates.
This is analogous to the five-dimensional (5D) collective (Bohr) model,
in which the collective coordinates are assumed to be the
quadrupole deformation parameters, $\alpha_{2\mu}$.
The 5D collective model has been extensively studied and
successfully applied to analysis on numerous experimental data.
On the contrary, the collective model for the pairing was not so
successful in comparison with experimental data.
In this section, we examine the collective treatment of the pairing.

%The most popular collective coordinate to describe pairing vibration is pairing gap, which is the order parameter in U(1) gauge space. The algebra form of pairing vibration is analogous the vibration in real three-dimensional space which suppose to be the swinging in quadrupole deformation parameters $\beta,\gamma$. In two-level system, the pairing gap becomes
%\begin{align}
%\Delta &= g\braket{Z|\hat{S}_-|Z} \nonumber \\
%	&= g\sum_{l=1}^2 S_l\sqrt{1-q_l^2}e^{-i\chi_l} \nonumber \\
%	&= g \left( S_1\sqrt{1-q_1^2}e^{i\frac{\phi_1}{2}}+S_2\sqrt{1-q_2^2}e^{-i\frac{\phi_2}{2}} \right) e^{-i\Phi}.
%\end{align}
%. Without total gauge angle part $e^{i\Phi}$, $\Delta$ is still complex number in general. However, the pairing gap is real number with the definition by BCS wave function

In the superfluid phase, the energy minimization always lead to $\phi=0$.
Although the global gauge angle $\Phi$ is arbitrary,
the gap parameter is usually taken as real value ($\Phi=0$).
\begin{align}
\Delta(j,J) = g\braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
	= g\sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
 \label{Delta_BCS}
\end{align}
The relation between $j$ and $\Delta$ 
and that between $j$ and $E=\cal{H}(\phi=0,j;J)$
are shown for $\Omega=8$
in Figs. \ref{fig:p_Delta1} ($N=8$) and \ref{p_Delta2} ($N=16$).
%These results correspond to the system in Section 4.2. 
The gap $\Delta$ is largest at $j=0$ (equal filling in both levels),
and smallest at end points of $j$.
The constrained minimization with respect to $\Delta$ cannot 
produce the states corresponding to $j>0$.
Apparently, we cannot map the entire region of $j$ to $\Delta$,
since there is no one-to-one correspondence between $j$ and $\Delta$.

If the system has a deep potential at $j<0$ to prevent the wave function
from spreading toward the region of $j<0$,
we may justify the use of $\Delta$ as a coordinate in
the collective model.
For very large $\Omega$, this is the case.
However, for $\Omega=8$, the treatment can be justified only for
a very limited region of $x$, namely in the weak pairing limit.
For instance, we show the potential energy curves as functions of $\Delta$
in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
In the weak pairing case ($x=0.5$),
assuming the Neumann boundary condition at $\Delta=0$,
we may obtain the colletive wave functions up to the third excited states.
On the other hand, in the strong pairing case ($x=3.2$), 
even the ground state may not be bound in the region of $j<0$.

%We also consider the behavior of energy surface.  After mapping, the energy surface at $\phi=0$
%\begin{align}
%  \left\{
%  \begin{array}{c}
%    E = E(\phi=0,\pi) \\
%    \Delta = \Delta(\pi)
%  \end{array}
%  \right. \hspace{1em} \to \hspace{1em} f(E,\Delta) = 0
%  \label{mapping}
%\end{align}
%can be connected with pairing gap $\Delta$. The implicit function form is necessary. On the other hand, we consider pairing gap as a collective coordinate ``by hand''. The collective coordinate can be derived from CBCS equation
%\begin{align}
% &\delta\braket{BCS|\hat{H}'|BCS} = 0, \hspace{1em} \hat{H}' = \hat{H} - \mu \hat{N} - \lambda \hat{S}_-
% \label{CBCS}
%\end{align}
%where $\lambda$ is Lagrange multiplier with respect to $\Delta$. In CBCS case, the energy surface is the explicit function of $\Delta$. The examples of energy surface from both mapping and CBCS are shown in Figure \ref{fig:Delta_E}. The results correspond to the system in Section 4.2, $N=16$ case. We found that both mapping and CBCS results are the same up to the turning point, which is infinite gradient point with respect to $\Delta$. However, CBCS cannot reproduce the upper surface after turning point because of no one-to-one correspondence between $\pi$ and $\Delta$. The pairing gap can only describe a part of the collective path. In two-level system, from \ref{Delta_BCS}, the gradient of $\Delta$ with respect to $\pi$ is 
%\begin{align}
% \frac{\partial\Delta}{\partial\pi} = \frac{q_2}{\sqrt{1-q_2^2}} - \frac{q_1}{\sqrt{1-q_1^2}} .
%\end{align}
%It represents, in $\pi$ space, the gradient goes to $+\infty$ at the left end and $-\infty$ at the right end. Hence the turning point $\frac{\partial\Delta}{\partial\pi}=0$ must exist on the way of $\pi$. Therefore, paining gap is not suitable collective coordinate to describe pairing vibration in two-level system.\par
%However, the effect of the turning point is not expected to be important in some cases. In the top panel of Figure \ref{fig:Delta_E}, we found that the low-lying energy spectra are located below the turning point. Because the energy of turning point is high, the collective path below the turning point is sufficient to describe the low-lying excited states. Therefore, the collective coordinate $\Delta$ is available to describe low-lying pairing vibration in weak pairing correlation system.

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
 \label{fig:p_Delta2}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=130mm,angle=-90]{images/Delta_compare.eps}
 \end{center}
 \caption{Energy surface with respect to $\Delta$. The results correspond to Section 4.2, $N=16$ system. Purple lines are obtained from (\ref{mapping}) and green dashed lines are obtained from (\ref{CBCS}). The blue lines are excitation energy spectra until 3rd excitation obtained from (\ref{Sommerfeld}). The top, middle and bottom panels display the energy surfaces with various pairing strength.}
 \label{fig:Delta_E}
\end{figure}

\newpage

\section{Conclusion}

The different methods of the requantization of the TDHFB dynamics
was studied for the two-level pairing model;
the stationary phase approximation (SPA) of the path integral,
the canonical quantization (CQ), and the Fourier decomposiion (FD)
of the time-dependent observables.
In this model, since the global gauge angle $\Phi$ is a cyclic variable,
the TDHFB dynamics can be described by the integrable classical dynamics.
After the pair-rotation variables $(\Phi,J)$ are separated,
the remaining degrees of freedom, $(\phi,j)$, describe
the pair-vibrational motion.

In systems with large degeneracy $\Omega$ and number of particles $N$,
all the quantization methods reasonably reproduce the results of the
exact calculation for excitation spectra.
It is more difficult to reproduce the two-particle transfer matrix elements.
Nevertheless, for the large $\Omega$ and $N$,
we obtain qualitative agreement with the exact results.
These are ideal cases,
but realistic situations may have smaller $\Omega$ and $N$
in the valence space.

In systems with relatively small $\Omega$ and $N$,
the agreement is less quantitative for the CQ and the FD,
especially for the two-particle transfer matrix elements.
In contrast, the SPA keeps its accuracy in the entire range of
pairing strengths.
One of the reasons of its sucess is due to the inclusion of the off-diagonal 
parts of the pair transfer operator,
by the explicit construction of the microscopic wave functions.
The CQ and FD calculate the pair transfer matrix elements using only
the diagonal part (expectation value) of the operator $\hat{S}_\pm$,
based on Eqs. (\ref{Sp_mean_value}) and (\ref{Sm_mean_value}).
This is a good approximation when the collectivity is so large that the
diagonal parts dominate.
However, the pairing collecitivity may not be too weak to justify this
treatment.

%To describe pairing collective motion by using collective coordinates, we applied requantization of TDHFB method. In classical picture of two-level system, we have two degrees of freedom. The total gauge angle describing pairing rotational mode is a cyclic variable in classical Hamiltonian. The intrinsic time dependent coordinate which is only one-dimensional  corresponds to pairing vibrational mode. 
%We discussed two requantization method, canonical quantization and semiclassical approach. In ideal type of system, both methods are reasonable even though semiclassical approach is better. In realistic type of system, the semiclassical approach is more quantitative than canonical quantization in excitation energy and wave function. 
%Especially, the transition strength of pair transfer has significant difference between two methods. 
%The off-diagonal part of pair transfer operator is important, causing requantization procedure lose a lot of information. 
%The advantage of semiclassical approach is that the wave function is microscopic, so that we can use original operator to calculate transition strength. Even though the system is as small as realistic case, the semiclassical approach works well except phase transition region.\par

We also investigated the conventional treatment of
the collective model which assumes that the collective coordinate is
the paring gap parameter.
As we mentioned before, the present two-level pairing Hamiltonian has
only one pair of collective variables $(\phi,j)$, in addition to the
pair rotational varialbles $(\Phi,J)$.
Even for such a simple system, we find that it is difficult to justify
the use of $\Delta$ as the collective coordinate,
especially for relatively small-$\Omega$ cases.
Basically, there is no one-to-one correspondence between $\Delta$ and $j$.
The collective wave functions are not necessarily bound in the region
where the variable $\Delta$ can represent.

% coordinate describing pairing vibration. We found that the collective path has significant difference compared with CBCS which use pairing gap as a constraint condition. The turning point must exist in energy surface, causing the collective path from CBCS only a part of the collective path in original coordinate. Hence pairing gap is not suitable collective coordinate to describe pairing collective motion in two-level system. However, if the energy of the turning point is much higher than low-lying excitation energy, pairing gap is available as a collective coordinate. In weak pairing correlation system, we expect that the low-lying excited states are able to be described by the coordinate of pairing gap. \par

Among the different requantization methods,
the SPA is the most accurate tool for desciption of
the pairing large amplitude collective motion in realistic nuclear system.
The weak point of this approach is that it is applicable only to the
integrable TDHFB system.
In order to solve this problem, we plan to first extract the
integrable collective submanifold in the many-dimensional TDHFB phase space.
For this purpose, the adiabatic self-consistent collective coordinate (ASCC)
method \cite{NMMY16} is a promising tool.
The combined study of the ASCC and the SPA for multi-level systems is our
next target under progress.

\bibliographystyle{unsrt}
\bibliography{ref}

\end{document}

### 2017-09-28 draft1.1.tex
テスト
updated 4.B, added adiabatic approximation

@@
 
+%aaa
 \usepackage{comment}
@@
 not assumed in the present case, but are obtained from the TDHFB dynamics
-itself.
+itself.\par
+In this section, we consider two separated methods to solve the quantum mechanics: periodic boundary condition and adiabatic approximation. 
 %The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation
+
+\subsubsection{Periodic boundary condition}
 
@@
 which automatically vanishes for $N'\neq N+2$.
+
+\subsubsection{Adiabatic approximation}
+We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
+The adiabatic approximation means $\phi$ in Hamiltonian can be
+ expanded up to second order
+\begin{align}
+ \mathcal{H}(\phi,j;J)
+	\approx V(j:J) + \frac{1}{2B(j;J)}j^2
+\end{align}
+where
+\begin{align}
+ V(j:J) &\equiv \mathcal{H}(\phi=0,j;J) \nonumber \\
+  &= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
+	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
+- \frac{g}{2}\Omega_1\Omega_2
+	\sqrt{(1-q_1^2)(1-q_2^2)} \\
+ B(j;J)^{-1} &\equiv \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2}\right|_{\phi=0} \nonumber \\
+ &= \frac{g}{2}\Omega_1\Omega_2
+	\sqrt{(1-q_1^2)(1-q_2^2)} .
+\end{align}
+We transform the carved space into plain space
+ which keeps the mass parameter equals one
+\begin{align}
+ \mathcal{H}(\phi,j;J) \to \mathcal{\bar{H}}(p,q;J) = \bar{V}(q;J) + \frac{1}{2}p^2 .
+\end{align}
+The relation between both coordinates fulfills
+\begin{align}
+ \frac{\partial q(j)}{\partial j} = \sqrt{B(j;J)} .
+\end{align}
+Instead of Pauli prescription, we solve the Schr\"{o}dinger equation in plain space
+\begin{equation}
+	\bar{H}\left( q,-i\frac{d}{dq},\frac{N}{2} \right)
+	u_k^{(N)}(q) = E_k^{(N)}u_k^{(N)}(q).
+	\label{Schroedinger_eq2}
+\end{equation}
+At weak pairing limit in ground state, most of the component of wave function is expected to occupy around the minimum value of $j$.
+We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, where $q_{min}$ corresponds to the minimum value of $j$.
 

### 2017-09-29 draft1.1.tex
test
added some figures, changed 5.C a little

@@
 \usepackage{comment}
-%\usepackage[dvips]{graphicx}
+\usepackage[dvips]{graphicx}
 %\usepackage{amsmath,amssymb}
@@
 Although the global gauge angle $\Phi$ is arbitrary,
-the gap parameter is usually taken as real value ($\Phi=0$).
-\begin{align}
-\Delta(j,J) = g\braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
-	= g\sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
+the deformation parameter $\alpha$ in gauge space is usually taken as real value ($\Phi=0$).
+\begin{align}
+\alpha(j,J) = \braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
+	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
  \label{Delta_BCS}
 \end{align}
-The relation between $j$ and $\Delta$ 
-and that between $j$ and $E=\cal{H}(\phi=0,j;J)$
+The relation between $j$ and $\alpha$ 
+and that between $j$ and $E=\mathcal{H}(\phi=0,j;J)$
 are shown for $\Omega=8$
@@
 %These results correspond to the system in Section 4.2. 
-The gap $\Delta$ is largest at $j=0$ (equal filling in both levels),
+The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
 and smallest at end points of $j$.
-The constrained minimization with respect to $\Delta$ cannot 
+The constrained minimization with respect to $\alpha$ cannot 
 produce the states corresponding to $j>0$.
-Apparently, we cannot map the entire region of $j$ to $\Delta$,
-since there is no one-to-one correspondence between $j$ and $\Delta$.
+Apparently, we cannot map the entire region of $j$ to $\alpha$,
+since there is no one-to-one correspondence between $j$ and $\alpha$.
 
@@
 from spreading toward the region of $j<0$,
-we may justify the use of $\Delta$ as a coordinate in
+we may justify the use of $\alpha$ as a coordinate in
 the collective model.
@@
 a very limited region of $x$, namely in the weak pairing limit.
-For instance, we show the potential energy curves as functions of $\Delta$
+For instance, we show the potential energy curves as functions of $\alpha$
 in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
 In the weak pairing case ($x=0.5$),
-assuming the Neumann boundary condition at $\Delta=0$,
+assuming the Neumann boundary condition at $\alpha=0$,
 we may obtain the colletive wave functions up to the third excited states.
@@
  \begin{center}
-%  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
+  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
+  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
  \end{center}

### 2017-10-06 draft1.1.tex
added some figures

@@
 \subsubsection{Periodic boundary condition}
+\label{subsec:canonical1}
 
@@
 \subsubsection{Adiabatic approximation}
+\label{subsec:canonical2}
+
 We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
@@
 the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
-and the canonical quantization (Sec.~\ref{sec:canonical}) as ``CQ''.
+ the canonical quantization with periodic boundary condition 
+(Sec.~\ref{subsec:canonical1}) as ``CQ1'', and the canonical quantization 
+with adiabatic approximation (Sec.~\ref{subsec:canonical2})  as ``CQ2''.
 In addition, the harmonic approximation at the ground state is
@@
 and $N=50$ (mid-shell configuration).
+
+\subsubsection{Mid-shell configuration}
 
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_woType2.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_woType2.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ.eps}
  \end{center}
@@
 %  \includegraphics[width=70mm,angle=-90]{images/N50Pad_semiclassical.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}).
+The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown.
+Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
+ \label{fig:N50Pad}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
+ \label{fig:N50energy}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ.eps}
+ \end{center}
+ \end{minipage}
+ \begin{minipage}{1\hsize}
+ \begin{center}
+  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ.eps}
+ \end{center}
+ \end{minipage}
+ \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system.
+The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
+From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
+ \label{fig:N50_occ}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{minipage}{0.33\hsize}
+ \begin{center}
+%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_exact.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.33\hsize}
+ \begin{center}
+%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_Type1.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.33\hsize}
+ \begin{center}
+%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_semiclassical.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ_woType2.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ_woType2.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ_woType2.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ_woType2.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
+  \includegraphics[width=50mm,angle=-90]{images/N8p_E.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
+  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
  \end{center}

### 2017-10-11 draft1.1.tex
updated figures, added appendix

@@
  \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
+  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
  \end{center}
@@
 	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
-	\ket{\Phi,t}_{N,E_k} \nonumber \\
+	\ket{\Phi,t}_{N,E_k} \label{semi_wave_func0} \\
 %  &\propto \sum_k \frac{1}{k!}\int_0^{2\pi}d\Phi e^{i(\Pi-k)\Phi}\sum_{j=0}^{k}C_j^{(E,k)}\ket{S_1,-S_1+j;S_2,-S_2+(k-j)} \label{semi_wave_func1}
@@
  \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy2.eps}
  \end{center}
@@
  \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system.
-The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
-From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
+ \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=50$ system.
+The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively.
+From (\ref{momentum}), $j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.}
  \label{fig:N50_occ}
@@
 \begin{figure}[htbp]
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_exact.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_CQ.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_Type1.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_FD.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_semiclassical.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_SPA.eps}
  \end{center}
@@
  \end{minipage}
- \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}).
-The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown.
-Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
+ \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=48$ to $N=50$ system.
+Dashed lines are exact solution.
+Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
+Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
  \label{fig:N50Pad}
@@
  \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy.eps}
- \end{center}
- \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
- \label{fig:N50energy}
+  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy2.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=100$ system.}
+ \label{fig:N100energy}
 \end{figure}
@@
  \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system.
-The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
-From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
- \label{fig:N50_occ}
+ \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=100$ system.
+The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively.
+From (\ref{momentum}), $j=-25$ corresponds to 0p0h configuration, $j=-24$ corresponds to 2p2h configuration, and so on.}
+ \label{fig:N100_occ}
 \end{figure}
@@
 \begin{figure}[htbp]
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_exact.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_CQ.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_Type1.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_FD.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_semiclassical.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_SPA.eps}
  \end{center}
@@
  \end{minipage}
- \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}).
-The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown.
-Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
- \label{fig:N50Pad}
+ \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=98$ to $N=100$ system.
+Dashed lines are exact solution.
+Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
+Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
+ \label{fig:N100Pad}
 \end{figure}
@@
  \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy2.eps}
  \end{center}
@@
  \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=8$ system.
+ \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system.
 The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
-From the physical meaning of $\pi$, $-2$ corresponds to 0p8h configuration, $-1$ corresponds to 2p10h configuration, and so on.}
+From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.}
  \label{fig:N8_occ}
@@
 \begin{figure}[htbp]
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_exact.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N8Pad_CQ.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_Type1.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N8Pad_FD.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_semiclassical.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N8Pad_SPA.eps}
  \end{center}
@@
  \end{minipage}
- \caption{The strength of pair additional transition from $N=6$ to $N=8$ system defined in (\ref{Pad}).
-The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown.
-Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
+ \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=6$ to $N=8$ system.
+Dashed lines are exact solution.
+Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
+Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
  \label{fig:N8Pad}
@@
  \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy2.eps}
  \end{center}
@@
  \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system.
-The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
-From the physical meaning of $\pi$, $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
+ \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=16$ system.
+The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.From (\ref{momentum}), $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
  \label{fig:N16_occ}
@@
 \begin{figure}[htbp]
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_exact.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N16Pad_CQ.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_Type1.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N16Pad_FD.eps}
  \end{center}
@@
  \end{minipage}
- \begin{minipage}{0.33\hsize}
- \begin{center}
-%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_semiclassical.eps}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N16Pad_SPA.eps}
  \end{center}
@@
  \end{minipage}
- \caption{The strength of pair additional transition from $N=14$ to $N=16$ system defined in (\ref{Pad}).
-The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown.
-Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
+ \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=14$ to $N=16$ system.
+Dashed lines are exact solution.
+Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
+Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
  \label{fig:N16Pad}
@@
  \end{center}
- \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
+ \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=8$ system.
+ Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
  \label{fig:p_Delta1}
@@
  \end{center}
- \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
+ \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=16$ system.
+ Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
  \label{fig:p_Delta2}
@@
 \begin{figure}[htbp]
- \begin{center}
-%  \includegraphics[width=130mm,angle=-90]{images/Delta_compare.eps}
- \end{center}
- \caption{Energy surface with respect to $\Delta$.
-The results correspond to Section 4.2, $N=16$ system.
-Purple lines are obtained from (\ref{mapping}) and green dashed lines are obtained from (\ref{CBCS}).
-The blue lines are excitation energy spectra until 3rd excitation obtained from (\ref{Sommerfeld}).
-The top, middle and bottom panels display the energy surfaces with various pairing strength.}
+ \begin{minipage}{0.45\hsize}
+ \begin{center}
+  \includegraphics[width=130mm,angle=-90]{images/N50gap_E.eps}
+ \end{center}
+ \end{minipage}
+ \begin{minipage}{0.45\hsize}
+ \begin{center}
+  \includegraphics[width=130mm,angle=-90]{images/N16gap_E.eps}
+ \end{center}
+\end{minipage}
+ \caption{Energy surface with respect to $\alpha$ in $x=0.5$, $x=1$ and $x=2$. 
+Green lines are energy spectra until 3rd excitation obtained from CQ2 
+(Sec.~\ref{subsec:canonical2}). Left panels: $\Omega=50$, $N=50$ system;
+ Right panels: $\Omega=8$, $N=16$ system.}
  \label{fig:Delta_E}
@@
 
+\appendix
+\section{Derivation of semiclassical wave function}
+
+We give the detail derivation of semiclassical wave function 
+discussed in Sec \ref{sec:SPA}. The explicit form of coherent state is
+\begin{align}
+  \ket{Z} &= \prod_{l=1}^2(1+|Z_l|^2)^{-\Omega_l/2}e^{Z_lS_l^{\dag}}\ket{0} \nonumber \\
+  &= \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
+  {}_kC_m \left(
+  \tan{\frac{\theta_1}{2}}e^{-i\phi_1}S_1^{\dag} \right)^m \left(
+  \tan{\frac{\theta_2}{2}}e^{-i\phi_2}S_2^{\dag} \right)^{k-m} \ket{0} \nonumber \\
+  &= \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
+  {}_kC_m \tan^m{\frac{\theta_1}{2}}\tan^{k-m}{\frac{\theta_2}{2}}e^{-ik\Phi}e^{-i(k/2-m)\phi}
+  (S_1^{\dag})^m(S_2^{\dag})^{k-m} \ket{0}
+  \label{ZZ}
+\end{align} 
+Inserting (\ref{ZZ}) into (\ref{semi_wave_func0}) under fixed $N$ and $E_k$, The classical wave function becomes
+\begin{align}
+	\ket{\phi_k^N} \propto& \oint d\Phi \oint dt
+	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
+	\ket{\Phi,t}_{N,E_k} \nonumber \\
+  \propto& \sum_k \frac{1}{k!} \sum_{m=0}^k{}_kC_m \int_0^{2\pi} d\Phi e^{i(N/2-k)\Phi} 
+  \int_0^T dt e^{i\int \pi(t') \dot{\phi}(t') dt'-i(k/2-m)\phi} \nonumber \\
+  &\times \left\{ \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \right\}
+\tan^m{\frac{\theta_1}{2}}\tan^{k-m}\frac{\theta_2}{2}(S_1^{\dag})^m(S_2^{\dag})^{k-m} \ket{0} \nonumber \\
+  \propto& \sum_{m=0}^{N/2}{}_{N/2}C_m  \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(N/4-m)\phi \right)} \nonumber \\
+  &\times \left\{ \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \right\} 
+\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{\dag})^m(S_2^{\dag})^{N/2-m} \ket{0} \label{semi_wave_func_b}
+\end{align}
+From 2nd line to 3rd line, we can find that it is nothing but number projection. In SU(2) quasispin representation, the vacuum state becomes $\ket{0}=\ket{S_1,-S_1;S_2,-S_2}$, which leads
+\begin{align}
+  (S_1^{\dag})^m(S_2^{\dag})^{N/2-m} \ket{0} 
+  = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(N/2-m)!}{(2S_2-(N/2-m))!}}
+  \ket{S_1,-S_1+m;S_2,-S_2+(N/2-m)}.
+\end{align}
+For convenience, we define a coefficient 
+\begin{align}
+  A(q,S,m) &\equiv 
+  \frac{\tan^m{\frac{\theta}{2}}}{\left(1+\tan^2{\frac{\theta}{2}}\right)^{-S}}
+  \sqrt{\frac{(2S)!m!}{(2S-m)!}}  \nonumber \\
+  &= \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2} \sqrt{\frac{(2S)!m!}{(2S-m)!}}
+\label{tan}
+\end{align}
+where $q=\cos{\theta}$. Inserting (\ref{tan}) into (\ref{semi_wave_func_b}) and using $N/2=J$, the semiclassical wave function attributes to (\ref{semi_wave_func1}).
+%\begin{align}
+ % \sum_{m=0}^{J}{}_J C_m\int_0^T dt \exp{\left( i\int^t \pi(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) (S_1^{\dag})^m(S_2^{\dag})^{J-m}\ket{0}
+%\end{align}
+
 \bibliographystyle{unsrt}

### 2017-10-31 draft1.1.tex
removed adiabatic approximation, changed IV C

@@
 the requantization of the mean-field dynamics was
-proposed \cite{Neg80,path,path2,Rei80}.
+proposed \cite{Neg80,KS80,K81,Rei80}.
 It recovers quantum fluctuations missing in the mean-field
@@
 which can be constructed by superposing the coherent states along
-a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{path,path2,SM88}.
+a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{KS80,K81,SM88}.
 \begin{equation}
@@
 itself.\par
-In this section, we consider two separated methods to solve the quantum mechanics: periodic boundary condition and adiabatic approximation. 
+
+%In this section, we consider two separated methods to solve the quantum mechanics: periodic boundary condition and adiabatic approximation. 
 %The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation
 
-\subsubsection{Periodic boundary condition}
-\label{subsec:canonical1}
+%\subsubsection{Periodic boundary condition}
+%\label{subsec:canonical1}
 
@@
 
+\begin{comment}
+
 \subsubsection{Adiabatic approximation}
@@
 
+We hope that the pairing large amplitude collective motion can be 
+described in adiabatic approximation. 
 We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
-The adiabatic approximation means $\phi$ in Hamiltonian can be
+The adiabatic approximation means the conjugate momentum in Hamiltonian can be
  expanded up to second order
@@
  \mathcal{H}(\phi,j;J)
-	\approx V(j:J) + \frac{1}{2B(j;J)}j^2
+	\approx V(j:J) + \frac{1}{2B(j;J)}\phi^2
 \end{align}
@@
 \end{align}
-We transform the carved space into plain space
- which keeps the mass parameter equals one
+Because $B(j;J)$ diverges at both end points in $j$ space, it has advantage 
+to transform the carved space into plain space which keeps the mass parameter equals one
 \begin{align}
@@
 \end{align}
-The relation between both coordinates fulfills
+The relation between both coordinate systems fulfills
 \begin{align}
@@
 \end{equation}
-At weak pairing limit in ground state, most of the component of wave function is expected to occupy around the minimum value of $j$.
-We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, where $q_{min}$ corresponds to the minimum value of $j$.
+At weak pairing ($x<1$) in ground state, most of the component of wave function is 
+expected to occupy around the minimum value of $j$. 
+We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, 
+where $q_{min}$ corresponds to the minimum value of $j$. Under such boundary condition, 
+the occupation probability in $j$ space approaches to $\delta(j)$ in $x\to 0$ limit.
+
+\end{comment}
 
@@
 the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
- the canonical quantization with periodic boundary condition 
-(Sec.~\ref{subsec:canonical1}) as ``CQ1'', and the canonical quantization 
-with adiabatic approximation (Sec.~\ref{subsec:canonical2})  as ``CQ2''.
-In addition, the harmonic approximation at the ground state is
-called ''HA''.
+and the canonical quantization with periodic boundary condition 
+(Sec.~\ref{subsec:canonical1}) as ``CQ''.
+%In addition, the harmonic approximation at the ground state is called ''HA''.
 Note that the SPA and the FD produce the same eigenenergies which
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy2.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy2.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy2.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy2.eps}
+  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ.eps}
+  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
 \end{align}
+Using $\alpha$ as a coordinate is equivalent to using pairing gap $\Delta$ as a coordinate because the relation
+\begin{align}
+  \alpha = \frac{1}{2}\sum_{k>0}\frac{\Delta}{\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}}
+\end{align}
+guarantees one-to-one correspondence between $\alpha$ and $\Delta$.
 The relation between $j$ and $\alpha$ 
@@
 are shown for $\Omega=8$
-in Figs. \ref{fig:p_Delta1} ($N=8$) and \ref{p_Delta2} ($N=16$).
+in Fig. \ref{fig:p_Delta1} ($N=8$) and Fig. \ref{fig:p_Delta2} ($N=16$).
 %These results correspond to the system in Section 4.2. 
@@
 the collective model.
-For very large $\Omega$, this is the case.
+For very large $\Omega$, this is the case (See Fig. \ref{fig:Delta_E}, left panels).
 However, for $\Omega=8$, the treatment can be justified only for
@@
  \begin{center}
-  \includegraphics[width=130mm,angle=-90]{images/N50gap_E.eps}
+  \includegraphics[width=50mm,angle=-90]{images/N50Xeq2p4gap_E.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=130mm,angle=-90]{images/N16gap_E.eps}
- \end{center}
-\end{minipage}
- \caption{Energy surface with respect to $\alpha$ in $x=0.5$, $x=1$ and $x=2$. 
-Green lines are energy spectra until 3rd excitation obtained from CQ2 
-(Sec.~\ref{subsec:canonical2}). Left panels: $\Omega=50$, $N=50$ system;
+  \includegraphics[width=50mm,angle=-90]{images/N16Xeq2p4gap_E.eps}
+ \end{center}
+\end{minipage}
+ \caption{Energy surface with respect to $\alpha$ in $x=2.4$. 
+Green lines are energy spectra until 3rd excitation obtained from CQ 
+(Sec.~\ref{sec:canonical}). Left panels: $\Omega=50$, $N=50$ system;
  Right panels: $\Omega=8$, $N=16$ system.}
@@
 \section{Conclusion}
+\label{sec:conclusion}
 

### 2017-11-13 draft1.1.tex
updated some figures, rewrited 4.C

@@
 
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
 \title{Comparative study of requantization of time-dependent mean-field
@@
 \begin{abstract}
-In order to obtain quantal information, such as enegy eigenvalues
+In order to obtain quantal information, such as energy eigenvalues
 and transition matrix elements,
@@
 However, the true nature of the low-lying excitations is still unclear,
-especilly for excited $J^\pi=0^+$ states \cite{garrett,HW11}.
+especially for excited $J^\pi=0^+$ states \cite{garrett,HW11}.
 Understanding the pairing dynamics is a key ingredient for solving
@@
 and to reveal nature of the mysterious excited $0^+$ states.
-As the first step Toward this goal, we investigate accuracy and
+As the first step, toward this goal, we investigate accuracy and
 applicability of the requantized TDHFB model for a two-level pairing model
@@
 In Ref.~\cite{CDS84},
-the two-particle-transfer matrix elements were eveluated as
+the two-particle-transfer matrix elements were evaluated as
 Fourier components of the time-dependent mean values of the pair
@@
 \braket{Z_{\rm cl}(t)|
-	i\hbar\frac{\partial}{\partial t} - H
+	i\frac{\partial}{\partial t} - H
 	|Z_{\rm cl}(t)} dt
@@
 \mathcal{T}[Z_{\rm cl}]\equiv
-\int_{0}^{t} \braket{Z_{\rm cl}(t)| i\hbar\frac{\partial}{\partial t}
+\int_{0}^{t} \braket{Z_{\rm cl}(t)| i\frac{\partial}{\partial t}
 	|Z_{\rm cl}(t)} dt 
@@
 	\rho(E_k,v^{(k)},\theta)
-	\ket{E_k,v^{(k)},\theta} e^{i\mathcal{T}[E_k,v^{(k)},\theta]/\hbar} .
+	\ket{E_k,v^{(k)},\theta} e^{i\mathcal{T}[E_k,v^{(k)},\theta]} .
   \label{semi_wave_func}
@@
 we define a dimensionless parameter to control the strength of
-the pairing correlation;
+the pairing correlation
 \begin{align}
@@
 the transition from normal ($x<1$) to superfluid ($x>1$) states
-takes place at $x=1$
+takes place at $x=1$.\footnote{$x$ is common definition of dimensionless coupling constant. Strictly, the exact phase transition point is $x=2\Omega/(2\Omega-1)$. }
 
@@
 and $N=50$ (mid-shell configuration).
-
-\subsubsection{Mid-shell configuration}
 
@@
 In contrast, $B(P_{\rm ad}; 1\rightarrow 0)$, which change the phonon
-quanta by two, are almost zero.
+quanta by three, are almost zero.
 In the pair-rotational region ($x \gg 1$),
@@
 However, the precision of the CQ method is not so good,
-especiallyaround $x=1$.
+especially around $x=1$.
 The FD method properly describes the main features
-in the superflud phase, while it fails for the normal phase
+in the superfluid phase, while it fails for the normal phase
 ($x\lesssim 1$). 
@@
 The ground-state energy in the CQ calculation 
-is bound at $x\gtrsim 1$ ({\bf need to check}).
+is bound at $x\gtrsim 1$.
 However, because of the weak collectivity with $N=8$,
@@
 the ground and the excited states.
-In the CQ calculation, the first excited state is bound at $x\gtrsim 1.?$,
-but the second excited state is unbound for $x\lesssim 3.?$.
+In the CQ calculation, the first excited state is bound at $x\gtrsim 2$,
+but the second excited state is unbound for $x\lesssim 3.2$.
 
@@
 This is because the $k=1$ trajectory corresponding to the first excited state
-changes its character from open to closed at $x\approx 1.8$ {\bf need to check}.
+changes its character from open to closed at $x\approx 1.8$.
 Therefore, the first excited wave function is difficult to reproduce in
@@
 \end{align}
-Using $\alpha$ as a coordinate is equivalent to using pairing gap $\Delta$ as a coordinate because the relation
+$\alpha$ is equivalent to pairing gap $\Delta$ as a coordinate because the gap equation
 \begin{align}
@@
 the collective model.
-For very large $\Omega$, this is the case (See Fig. \ref{fig:Delta_E}, left panels).
-However, for $\Omega=8$, the treatment can be justified only for
-a very limited region of $x$, namely in the weak pairing limit.
-For instance, we show the potential energy curves as functions of $\alpha$
-in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
-In the weak pairing case ($x=0.5$),
-assuming the Neumann boundary condition at $\alpha=0$,
-we may obtain the colletive wave functions up to the third excited states.
-On the other hand, in the strong pairing case ($x=3.2$), 
-even the ground state may not be bound in the region of $j<0$.
+The importance of the region of $j<0$ is considerable in strong pairing case.
+Fig. \ref{fig:Delta_E} shows two examples of the relationship 
+between excitation energies and energy surface.
+In the left panel ($\Omega=50$, $N=50$, $x=2.4$), the excited $0^+$ states are bound up to second excitation.
+For very large degeneracy, the pocket of energy surface is deep, 
+hence the low-lying excited states can be described by $\alpha$. 
+However, in the right panel ($\Omega=8$, $N=16$, $x=2.4$), 
+only the ground state is bound, and all excited $0^+$ states are unbound.
+For small degeneracy, the shallow pocket of energy surface allows 
+the excited $0^+$ states to be unbound. Therefore, pairing deformation parameter
+is not proper collective coordinate in small $\Omega$ and strong pairing case.
+
+%the treatment can be justified only for
+%a very limited region of $x$, namely in the weak pairing limit.
+%For instance, we show the potential energy curves as functions of $\alpha$
+%in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
+%In the weak pairing case ($x=0.5$),
+%assuming the Neumann boundary condition at $\alpha=0$,
+%we may obtain the collective wave functions up to the third excited states.
+%On the other hand, in the strong pairing case ($x=3.2$), 
+%even the ground state may not be bound in the region of $j<0$.
 
@@
 the stationary phase approximation (SPA) of the path integral,
-the canonical quantization (CQ), and the Fourier decomposiion (FD)
+the canonical quantization (CQ), and the Fourier decomposition (FD)
 of the time-dependent observables.
@@
 pairing strengths.
-One of the reasons of its sucess is due to the inclusion of the off-diagonal 
+One of the reasons of its success is due to the inclusion of the off-diagonal 
 parts of the pair transfer operator,
@@
 diagonal parts dominate.
-However, the pairing collecitivity may not be too weak to justify this
+However, the pairing collectivity may not be too weak to justify this
 treatment.
@@
 only one pair of collective variables $(\phi,j)$, in addition to the
-pair rotational varialbles $(\Phi,J)$.
+pair rotational variables $(\Phi,J)$.
 Even for such a simple system, we find that it is difficult to justify
@@
 Among the different requantization methods,
-the SPA is the most accurate tool for desciption of
+the SPA is the most accurate tool for description of
 the pairing large amplitude collective motion in realistic nuclear system.

### 2017-11-24 draft1.2.tex
new file:   draft1.2.tex 	modified:   ref.bib

--- 2017-11-13 draft1.1.tex
@@
 \begin{abstract}
-In order to obtain quantal information, such as energy eigenvalues
-and transition matrix elements,
-it is useful to requantize the mean-field dynamics.
-We study the two-level pairing model to compare different
-requantization methods and their accuracy.
-Among the different methods, the one constructing microscopic
-wave functions, using the TDHFB trajectories fulfilling the
+%The time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory is useful
+%to study large amplitude collective motion with nuclear superfluidity.
+%However, in order to obtain quantal information,
+%such as energy eigenvalues and transition matrix elements,
+%it is necessary to requantize the mean-field dynamics.
+To describe quantal collective phenomena, it is useful
+to requantize the time-dependent mean-field dynamics.
+We study the time-dependent Hartree-Fock-Boboliubov (TDHFB) theory
+for the two-level pairing Hamiltonian, and compare results
+of different quantization methods.
+The one constructing microscopic wave functions,
+using the TDHFB trajectories fulfilling the
 Einstein-Brillouin-Keller quantization condition,
-is the most accurate.
-We also examine the performance of the collective model,
-analogous to the Bohr model of the quadrupole vibrations and rotation,
-assuming the pairing gap parameter as the collective coordinate.
-It turns out that the applicability of such a model is very limited
-for the pairing case.
+turns out to be the most accurate.
+The method is based on the stationary-phase approximation
+to the path integral.
+We also examine the performance of the collective model
+%analogous to the Bohr model of the quadrupole vibrations and rotation,
+which assumes that the pairing gap parameter is the collective coordinate.
+The applicability of the collective model is limited
+for the nuclear pairing with a small number of
+single-particle levels,
+because the pairing gap parameter represents only a half of the
+pairing collective space.
 \end{abstract}
@@
 
-Pairing correlation is important 
-in the ground state of open-shell nuclei.
+Pairing correlation plays a decisive role in a number of nuclear phenomena,
+which is especially important in open-shell nuclei.
 Many evidences of the pairing correlation were observed in experiment,
@@
 Properties of low-lying modes of excitation in even-even nuclei are
-expected to be determined by interplay between
+expected to be determined dominantly by interplay between
 the pairing and the quadrupole correlations.
@@
 
-The Bohr Hamiltonian was introduced to describe low-energy
+In principle, the TDHFB dynamics can be applicable to large amplitude motion.
+The problem is that it is not easy to determine quantum mechanical 
+quantities, such as energy eigenvalues and transition matrix elements,
+from the TDHFB trajectories.
+In addition, the TDHFB lacks a part of quantum fluctuation
+associated with low-eneryg
+large amplitude collective motion,
+which leads to difficutlties in description of the quantum tunneling
+processes, such as spontaneous fission and sub-barrier fusion reaction.
+For this purpose,
+since the TDHF(B) trajectory corresponds to a classical limit of the path
+integral formulation,
+the requantization of the mean-field dynamics was
+proposed \cite{Neg82,KS80,K81,Rei80}.
+It recovers quantum fluctuations missing in the mean-field
+level, and possibly enables us to describe large-amplitude collective
+tunneling phenomena such as spontaneous fission \cite{Neg82}.
+The requantization of the TDHFB is particularly feasible
+for integrable systems, because the system is described by separable
+action-angle variables $(I_k, \phi_k)$, leading to
+the Einstein-Brillouin-Keller (EBK) quantization condition.
+However, for nonintegrable systems in general, it is difficult to find
+suitable periodic orbits to quantize.
+A possible solution to this difficulty is to find a decoupled collective
+subspace spanned by
+a single coordinate and its conjugate momentum \cite{NMMY16}.
+Since the one-dimensional system is integrable, the quantization is
+practicable.
+
+Another somewhat phenomenological approach
+to nuclear collective dynamics is the collective model.
+In this approach, the collective Hamiltonian is constructed by choosing
+collective coordinates intuitively.
+The nuclear energy density functional model is often used as a tool for
+a microscopic derivation of the collective Hamiltonian \cite{NMMY16}.
+The most well-known and successful model is the Bohr model \cite{BM75},
+which was introduced to describe low-energy
 nuclear collective motion in quadrupole degrees of freedom with
@@
 
-In principle, the TDHFB dynamics can be large amplitude motion.
-The problem is that it is not easy to determine quantum mechanical 
-quantities, such as energy eigenvalues and transition matrix elements,
-from the TDHFB trajectories.
-For this purpose,
-since the TDHF(B) trajectory corresponds to a classical limit of the path
-integral formulation,
-the requantization of the mean-field dynamics was
-proposed \cite{Neg80,KS80,K81,Rei80}.
-It recovers quantum fluctuations missing in the mean-field
-level, and possibly enables us to describe large-amplitude collective
-tunneling phenomena such as spontaneous fission \cite{Neg80}.
-The requantization of the TDHFB is particularly feasible
-for integrable systems, because the system is described by separable
-action-angle variables $(I_k, \phi_k)$, leading to
-the Einstein-Brillouin-Keller (EBK) quantization condition.
-However, for nonintegrable systems in general, it is difficult to find
-suitable periodic orbits to quantize.
-A possible solution to this difficulty is to find a decoupled collective
-subspace spanned by
-a single coordinate and its conjugate momentum \cite{NMMY16}.
-Since the one-dimensional system is integrable, the quantization is
-practicable.
-
-Our final goal is to study the role of dynamical pairing effects
+Our final goal is to study the role of large-amplitude pairing dynamics
 and to reveal nature of the mysterious excited $0^+$ states.
@@
 large $\Omega$ values ($\Omega=40$).
-However, in the realistic values of $\Omega$, we will show that
-the deviation is prominent.
+However, in realistic values of $\Omega$, we will show that
+the deviation is substantial.
 The collective model of the pairing motion, which assumes the pair deformation
@@
 \end{align}
-Here, $\chi_l$ represent the gauge angle of each level,
+Here, $\chi_l$ represent a kind of gauge angle of each level,
 and $q_l$ are related to the occupation probability, $q_l=|u_l|^2-|v_l|^2$.
+If we choose $\chi_l$ as canonical coordinates, their conjugate momenta
+are given by
+$p_l\equiv \partial\mathcal{H}/\partial\dot{\chi}_l=\Omega_l(1-q_l)/2$.
 Since the Hamiltonian (\ref{TDHFB_Hamiltonian_2}) depends only on
@@
 \quad\quad
-j = \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \frac{\Omega_2(1-q_2) - \Omega_1(1-q_1)}{4}. \label{pi} .
+j = \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \frac{\Omega_2(1-q_2) - \Omega_1(1-q_1)}{4}.
+	\label{pi}
 \end{align}
@@
 relative angle $\phi$.
+Here, the ``rotational behavior'' means that the motion span the whole
+region of the angle $\phi$,
+while we use ``vibrational'' for the classical motion in a bound region of
+$\phi$ ($-\pi<\phi<\pi$).
 At $g=x=0$, the Hamiltonian becomes independent from $(\Phi,\phi)$, then,
@@
 
-The quantization method is not unique.
-A common choice in the nuclear collective model is the Pauli's prescription.
-However, it is not straightforward to apply it to the present case, 
+%The quantization method is not unique.
+%A common choice in the nuclear collective model is the Pauli's prescription.
+%However, 
+It is not straightforward to apply the Pauli's prescription
+to the present case, 
 because the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3})
 is not limited to the second order in momenta.
-In the present study, we adopt a simple symmetrized ordering, as
+In the present study, 
+we adopt a simple symmetrized ordering, as
 \begin{align}
@@
 \begin{equation}
-	H\left( \phi,-i\frac{d}{d\phi},\frac{N}{2} \right)
+	H\left( \phi,-i\frac{d}{d\phi};\frac{N}{2} \right)
 	\psi_k^{(N)}(\phi) = E_k^{(N)}\psi_k^{(N)}(\phi),
@@
 %  \hat{\pi}\chi_\nu(\phi) = \nu \chi_\nu(\phi) \\
-	\chi_p(\phi) = \frac{1}{\sqrt{4\pi}} e^{ip\phi} ,
-	\quad\quad\mbox{with $p$: integer or half integer} .
+	\chi_j(\phi) = \frac{1}{\sqrt{4\pi}} e^{i\phi j} ,
+	\quad\quad\mbox{with $j$: integer or half integer} .
 \end{equation}
@@
 terms linearly proportional to $e^{\pm i\phi}$,
-the basis states $\chi_p$ with half-integer difference in $p$
+the basis states $\chi_j$ with half-integer difference in $j$
 are not coupled with each other.
@@
 	\psi_k^{(N)}(\phi) = 
-	\sum_{p=p_{\rm min},p_{\rm min}+1,\cdots}^{p_{\rm max}}
-	c_{k,p}^{(N)} \chi_p^{(N)}(\phi) .
+	\sum_{j=j_{\rm min},j_{\rm min}+1,\cdots}^{j_{\rm max}}
+	c_{k,j}^{(N)} \chi_j^{(N)}(\phi) .
 	\label{CQ_eigenstate}
@@
 According to the relation $j=(n_2-n_1)/4=(N-2n_1)/4$ in Eq. (\ref{momentum}),
-we adopt the (half-)integer values of $p$ for $N=4n$ ($N=4n+2$)
+we adopt the (half-)integer values of $j$ for $N=4n$ ($N=4n+2$)
 with integer $n$.
 This is consistent with the quantization condition (\ref{EBK_2}).
-The coupling term with different $p$
+The coupling term with different $j$
 in Eq. (\ref{canonical_quantized_H}) vanishes
 for $n_l=0$ and $n_l=2\Omega_l$,
-which restricts values of $p$ in a finite range of
-$p_{\rm min}\leq p \leq p_{\rm max}$.
+which restricts values of $j$ in a finite range of
+$j_{\rm min}\leq j \leq j_{\rm max}$.
 
@@
   x = 2\Omega\frac{g}{\Delta\epsilon} .
+\label{x}
 \end{align}
@@
 the transition from normal ($x<1$) to superfluid ($x>1$) states
-takes place at $x=1$.\footnote{$x$ is common definition of dimensionless coupling constant. Strictly, the exact phase transition point is $x=2\Omega/(2\Omega-1)$. }
+takes place at $x=1$.\footnote{
+Strictly speaking, the phase transition takes place at $x=2\Omega/(2\Omega-1)$. }
 
@@
 
+\begin{figure}[t]
+ \begin{center}
+%  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
+%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
+	 (a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
+	 (b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and
+$\ket{0_4^+}$ for $\Omega=50$ systems with (a) $N=50$ and (b) $N=100$
+	as functions of the dimensionless parameter $x$ of Eq. (\ref{x}).
+}
+ \label{fig:N50energy}
+\end{figure}
+
 In the limit of $\Omega\rightarrow\infty$,
@@
 %The system consists of $\Omega=50$ and $\Delta\epsilon=1$(MeV). We show the results in $N=50$ system, which is always superfluidity in ground state.\par
-Calulated excitation energies are shown in Figs.~\ref{fig:N50energy}
-and \ref{fig:N100energy}.
+Calulated excitation energies are shown in Figs.~\ref{fig:N50energy}.
+%and \ref{fig:N100energy}.
 The results of SPA/FD and CQ are compared with the exact values.
@@
 For the CQ, $|c_{k,p}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
-Here, $m$ and $p$ are related to each other, $2p=J-2m$.
+Here, $m$ and $j$ are related to each other, $2j=J-2m$.
 They show excellent agreement with the exact results, not only for the
@@
 We find the SPA is even more precise than the CQ.
+\begin{figure}[t]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
+(a1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
+(b1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+ \begin{minipage}{1\hsize}
+ \begin{center}
+%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+(a2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
+(b2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+ \caption{
+Occupation probability in excited $0^+$ states
+as a function of $j$ for $\Omega=50$ systems
+with (a) $N=50$ and (b) $N=100$.
+The upper and lower panels display the results for $x=0.5$ and $x=2$,
+respectively. 
+The three vertical bars at each $j$ from the left to the right represents
+the squared components of the wave functions
+from exact, SPA, and CQ calculations, respectively.
+The left end of the horizontal axis at $j=j_{\rm min}$
+corresponds to a component with $(n_1,n_2)=(N,0)$.
+The next at $j=j_{\rm min}+1$ corresponds to the one with
+$(n_1,n_2)=(N-2,2)$, and so on.
+%From Eq. (\ref{momentum}),
+%$j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.
+}
+ \label{fig:N50_occ}
+\end{figure}
 
 Next, let us discuss the transition matrix elements.
-The calculated pair-addition strengths $B(P_{\rm ad})$ are shown in
-Fig.~\ref{fig:N50Pad} for $N=98\rightarrow 100$ and $N=48\rightarrow 50$.
 In this paper, we discuss only $k=0$ (ground state) and $k=1$
@@
 For the ground-state band ($k=0$),
-this is nothing but the expectation value at the BCS wave function.
-The calculation trivially leads to vanishing interband transitions for 
-$k=0\rightarrow k'$ ($k'\neq 0$), because the $S_+(t)$ is stationary
-in the ground state.
-Thus, for the interband transition of $(N,k=0)\rightarrow (N+2,k=1)$
+this is nothing but the expectation value at the BCS wave function,
+with the constant value of $S_+$.
+Since the constant $S_+$ provides only $\Delta k=0$ intraband transitions,
+for the interband transition of $(N,k=0)\rightarrow (N+2,k=1)$
 transitions, the trajectory satisfying the EBK condition of $k=1$ is used to
@@
 
+\begin{figure}[t]
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_CQ.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_FD.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_SPA.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \caption{The strength of pair additional transition
+$B(P_{\rm ad};k\rightarrow k')$ for $\Omega=50$ systems
+from $N=48$ to 50.
+Left panels: results of the CQ method; Middle panels: FD; Right panels: SPA.
+Dashed lines represent exact calculation.
+Upper panels show the intraband transitions of
+$\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$,
+while lower panels show the interband transition of
+$\ket{0_1^+}\to\ket{0_2^+}$ and $\ket{0_2^+}\to\ket{0_1^+}$.
+}
+ \label{fig:N50Pad}
+\end{figure}
+
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
+% \end{center}
+% \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=100$ system.}
+% \label{fig:N100energy}
+%\end{figure}
+
+%\begin{figure}[htbp]
+% \begin{minipage}{1\hsize}
+% \begin{center}
+%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
+% \end{center}
+% \end{minipage}
+% \begin{minipage}{1\hsize}
+% \begin{center}
+%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+% \end{center}
+% \end{minipage}
+% \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=100$ system.
+The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively.
+From (\ref{momentum}), $j=-25$ corresponds to 0p0h configuration, $j=-24$ corresponds to 2p2h configuration, and so on.}
+% \label{fig:N100_occ}
+%\end{figure}
+
+\begin{figure}[htbp]
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_CQ.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_FD.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_SPA.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \caption{
+The same as Fig.~\ref{fig:N50Pad} but for $N=98\rightarrow 100$.
+%The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=98$ to $N=100$ system.
+Dashed lines are exact solution.
+Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
+Left panels: CQ1; Middle panels: FD; Right panels: SPA.
+}
+ \label{fig:N100Pad}
+\end{figure}
+
+The calculated pair-addition strengths $B(P_{\rm ad})$ are shown in
+Fig.~\ref{fig:N50Pad} for $N=48\rightarrow 50$,
+and in Fig.~\ref{fig:N100Pad} for $N=98\rightarrow 100$.
 Near the closed-shell configuration ($N=98\rightarrow 100$),
@@
 and the beta vibrations in deformed nuclei, respectively.
-The latter may correspond to the Higgs amplitude mode.
+%The latter may correspond to the Higgs amplitude mode.
 
@@
 $x$ increases.
-Their values are larger than the interband strengths by about one order
-of magnitude, indicating the pair-rotational character.
+Their values are larger than the interband strengths by about one (two) order
+of magnitude at $x\sim 0$ ($x\sim 2.5$),
+indicating the pair-rotational character.
 The interband $B(P_{\rm ad}; 0\rightarrow 1)$ shows a gradual decrease
@@
 even at $x\gg 1$.
-This present a prominent difference from the closed-shell case.
-
-All the features are nicely reproduced in the SPA method,
+This presents a prominent difference from the closed-shell case.
+
+All the features of the pair-transfer strengths
+are nicely reproduced in the SPA method,
 for both the closed- and mid-shell configurations.
@@
 However, somewhat surprisingly,
-the SPA results, which use these open trajectories for the construction
+the SPA, which uses these open trajectories for the construction
 of wave functions,
-reproduce main features of the exact results.
+reproduces main features of the exact results.
 
@@
 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
- \end{center}
- \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
- \label{fig:N50energy}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=50$ system.
-The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively.
-From (\ref{momentum}), $j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.}
- \label{fig:N50_occ}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{0.3\hsize}
- \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N50Pad_CQ.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
- \end{minipage}
- \begin{minipage}{0.3\hsize}
- \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N50Pad_FD.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
- \end{minipage}
- \begin{minipage}{0.3\hsize}
- \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N50Pad_SPA.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
- \end{minipage}
- \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=48$ to $N=50$ system.
-Dashed lines are exact solution.
-Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
-Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
- \label{fig:N50Pad}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
- \end{center}
- \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=100$ system.}
- \label{fig:N100energy}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=100$ system.
-The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively.
-From (\ref{momentum}), $j=-25$ corresponds to 0p0h configuration, $j=-24$ corresponds to 2p2h configuration, and so on.}
- \label{fig:N100_occ}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{0.3\hsize}
- \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N100Pad_CQ.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
- \end{minipage}
- \begin{minipage}{0.3\hsize}
- \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N100Pad_FD.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
- \end{minipage}
- \begin{minipage}{0.3\hsize}
- \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N100Pad_SPA.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
- \end{minipage}
- \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=98$ to $N=100$ system.
-Dashed lines are exact solution.
-Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
-Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
- \label{fig:N100Pad}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 %$N=8$ system, which is always superfluidity in ground state; (2) $N=16$ system, which has phase transition at $x=1$ in ground state.\par
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy_wo_adiabatic.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and
+$\ket{0_4^+}$ for $\Omega=N=8$ systems as functions of $x$.
+}
+ \label{fig:N8energy}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+ (a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N8Xeq0p5occ_wo_adiabatic.eps}
+ (b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N8Xeq2occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+ \caption{
+%Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system.
+The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
+From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.
+Occupation probability in excited $0^+$ states
+as a function of $j$ for $\Omega=N=8$ systems.
+The panels (a) and (b) display the results for $x=0.5$ and $x=2$,
+respectively. 
+See the caption of Fig.~\ref{fig:N50_occ}.
+%The left end at $j=j_{\rm min}$ corresponds to a component with
+%$(n_1,n_2)=(N,0)$.
+%The next at $j=j_{\rm min}+1$ corresponds to the one with
+%$(n_1,n_2)=(N-2,2)$, and so on.
+}
+ \label{fig:N8_occ}
+\end{figure}
 
@@
 both the SPA and the CQ reproduce the exact result.
-At $x=2$, the squared coefficients of the ground state is peaked at the
-lowest $p$, which suggests that the state is not deeply bound in the
+At $x=2$, the squared coefficients of the ground state has an
+asymmetric shape peaked at the
+lowest $j$, which suggests that the state is not deeply bound in the
 potential.
@@
 The wave functions obtained by the CQ method has noticeable deviation
-from the exact result.
+from the exact results.
 On the other hand, the SPA wave functions are almost identical to the
@@
 The intraband $k\rightarrow k$ transitions increase and 
-the interband $k\rightarrow k\pm1$ transitions decrease as
+the interband $k=1\rightarrow 0$ transitions decrease as
 functions of $x$.
@@
 
+For the mid-shell configurations, the SPA is dominantly superior to the
+CQ and the FD methods.
+
 %The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system.
@@
 \begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy_wo_adiabatic.eps}
- \end{center}
- \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=8$ system.}
- \label{fig:N8energy}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system.
-The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.
-From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.}
- \label{fig:N8_occ}
-\end{figure}
-
-\begin{figure}[htbp]
  \begin{minipage}{0.3\hsize}
@@
  \end{minipage}
- \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=6$ to $N=8$ system.
-Dashed lines are exact solution.
-Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
-Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
+	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=6\rightarrow 8$
+	with $\Omega=16$.
+}
  \label{fig:N8Pad}
@@
 
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy_wo_adiabatic.eps}
+ \end{center}
+	\caption{The same as Fig.~\ref{fig:N8energy} but for
+	$N=2\Omega=16$.
+}
+ \label{fig:N16energy}
+\end{figure}
+
+\begin{figure}[thb]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+(a) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq0p5occ_wo_adiabatic.eps}
+(b) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+	\caption{The same as Fig.~\ref{fig:N8_occ} but for
+	$N=2\Omega=16$.
+}
+ \label{fig:N16_occ}
+\end{figure}
+
 \subsubsection{Closed-shell configuration}
@@
 the minimum-energy trajectory changes at $x=1$ from
-$p=-4$ (normal phase) to
-the BCS minimum $p>-4$ and $\phi=0$ (superfluid phase).
+$j=-4$ (normal phase) to
+the BCS minimum $j>-4$ and $\phi=0$ (superfluid phase).
 At the transitional point ($x=1$), the harmonic approximation is
@@
 Nevertheless, the overall behaviors are well reproduced and
-the values at the weak and strong pairing limit are well reproduced
+the values at the weak and strong pairing limit are reasonably reproduced
 in the SPA.
@@
 transition points.
+However, it underestimates the intraband $B(P_{\rm ad}; k\rightarrow k)$.
 The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
 because $S_+(t)$ is calculated for a $N=14$ system.
-Both intraband and interband transitions reasonably agree with
-the exact results at $x\gtrsim 1.8$,
-while the $k=1$ state is not properly reproduced at $x\lesssim 1.8$
+Both intraband and interband transitions in the FD calculations
+reasonably agree with the exact results at $x\gtrsim 1.8$.
+The $k=1$ state is not properly reproduced at $x\lesssim 1.8$
 with the open trajectory.
+
+For the closed-shell configurations,
+the SPA and the FD methods provide reasonable description for the
+pair-transfer transition strengths.
 
@@
 \begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy_wo_adiabatic.eps}
- \end{center}
- \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=16$ system.}
- \label{fig:N16energy}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \begin{minipage}{1\hsize}
- \begin{center}
-  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=16$ system.
-The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.From (\ref{momentum}), $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
- \label{fig:N16_occ}
-\end{figure}
-
-\begin{figure}[htbp]
  \begin{minipage}{0.3\hsize}
@@
  \end{minipage}
- \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=14$ to $N=16$ system.
-Dashed lines are exact solution.
-Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$.
-Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
+	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
+	with $\Omega=16$.
+}
  \label{fig:N16Pad}

### 2017-11-26 draft1.2.tex
modified:   draft1.2.tex 	modified:   ref.bib

@@
 amsmath,amssymb,
-%aps,
+aps,
 %pra,
@@
 to requantize the time-dependent mean-field dynamics.
-We study the time-dependent Hartree-Fock-Boboliubov (TDHFB) theory
+We study the time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory
 for the two-level pairing Hamiltonian, and compare results
@@
 In addition, the TDHFB lacks a part of quantum fluctuation
-associated with low-eneryg
+associated with low-energy
 large amplitude collective motion,
-which leads to difficutlties in description of the quantum tunneling
+which leads to difficulties in description of the quantum tunneling
 processes, such as spontaneous fission and sub-barrier fusion reaction.
@@
 effects of the pair motion on the quadrupole vibrations %and fission half lives
-have been discussed in literatures \cite{delta1,delta3}.
+have been discussed in literature \cite{delta1,delta3}.
 %\cite{delta1,delta2,delta3}. 
@@
 the requantization of the TDHFB is performed using different methods,
-based on the canonical and the EBK quantizations.
+based on the canonical and the EBK quantization.
 In Sec. \ref{sec:results}, 
@@
 \end{equation}
-where we use the SU(2) quasispin operators,
+where we use the SU(2) quasi-spin operators,
 $\boldsymbol{S}=\sum_l \boldsymbol{S}_l$, with
@@
 %The first term giving a spherical single particle energy $\epsilon_l$ for each j-shell, which 
-The quasispin operators satisfy the commutation relations
+The quasi-spin operators satisfy the commutation relations
 \begin{equation}
@@
 \end{equation}
-The magnitude of quasispin for each level is
+The magnitude of quasi-spin for each level is
 $S_l=\frac{1}{2}(\Omega_l-\nu_l)$, where $\nu_l$ is the seniority
@@
 \cite{Richardson,Richardson2,Richardson3} or
-by diagonalizing the Hamiltonian using the quasispin symmetry.
+by diagonalizing the Hamiltonian using the quasi-spin symmetry.
 
@@
 motion of the system. 
-In the SU(2) quasispin representation,
+In the SU(2) quasi-spin representation,
 $\ket{0}=\prod_l \ket{S_l,-S_l}$.
@@
 
-The TDHFB equation can be derived from the tiem-dependent variational
+The TDHFB equation can be derived from the time-dependent variational
 principle,
@@
 where $\psi(Z)\equiv \braket{Z|\psi(0)}$ and
-the invariant measure $d\mu(Z)$ is defiend by 
+the invariant measure $d\mu(Z)$ is defined by 
 the unity condition,
@@
 Finding TDHFB trajectories satisfying the quantization condition
-(\ref{EBK}) is an extremenly difficult task in general.
+(\ref{EBK}) is an extremely difficult task in general.
 It is better founded and more practical
@@
 \begin{align}
-  S_+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_+|Z} = \left( S_1\sqrt{1-q_1^2}e^{-i\phi/2}+S_2\sqrt{1-q_2^2}e^{i\phi/2} \right) e^{i\Phi}
+  S_+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_+|Z}
+ = \frac{1}{2}
+\left( \Omega_1\sqrt{1-q_1^2}e^{-i\phi/2}+\Omega_2\sqrt{1-q_2^2}e^{i\phi/2} \right) e^{i\Phi}
 	\label{Sp_mean_value} \\
-  S_-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_-|Z} = \left( S_1\sqrt{1-q_1^2}e^{i\phi/2}+S_2\sqrt{1-q_2^2}e^{-i\phi/2} \right) e^{-i\Phi} .
+  S_-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_-|Z}
+ = \frac{1}{2}
+\left( \Omega_1\sqrt{1-q_1^2}e^{i\phi/2}+\Omega_2\sqrt{1-q_2^2}e^{-i\phi/2} \right) e^{-i\Phi} .
 	\label{Sm_mean_value}
@@
 and the canonical quantization with periodic boundary condition 
-(Sec.~\ref{subsec:canonical1}) as ``CQ''.
+(Sec.~\ref{sec:canonical}) as ``CQ''.
 %In addition, the harmonic approximation at the ground state is called ''HA''.
@@
 %The system consists of $\Omega=50$ and $\Delta\epsilon=1$(MeV). We show the results in $N=50$ system, which is always superfluidity in ground state.\par
-Calulated excitation energies are shown in Figs.~\ref{fig:N50energy}.
+Calculated excitation energies are shown in Figs.~\ref{fig:N50energy}.
 %and \ref{fig:N100energy}.
@@
 respectively. 
-See the caption of Fig.~\ref{fig:N50_occ}.
+See also the caption of Fig.~\ref{fig:N50_occ}.
 %The left end at $j=j_{\rm min}$ corresponds to a component with
@@
 	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=6\rightarrow 8$
-	with $\Omega=16$.
+	with $\Omega=8$.
 }
@@
 
-In literatures, the collective model has been proposed
-and utilized for the nuclear pairing dynamics.
-For those studies, the pairing gap parameter is assumed to be the
-collective coordinates.
+%In literatures, the collective model has been proposed
+The collective model has been proposed
+and utilized for the nuclear pairing dynamics
+\cite{BBPK70,delta1,delta3}.
+For those studies, the pairing gap parameter (or equivalent quantities)
+is assumed to be the collective coordinates.
 This is analogous to the five-dimensional (5D) collective (Bohr) model,
@@
 quadrupole deformation parameters, $\alpha_{2\mu}$.
-The 5D collective model has been extensively studied and
-successfully applied to analysis on numerous experimental data.
-On the contrary, the collective model for the pairing was not so
-successful in comparison with experimental data.
-In this section, we examine the collective treatment of the pairing.
+The 5D collective model has been 
+extensively applied to analysis on numerous experimental data.
+On the contrary, there have been very few applications of
+the pairing collective model
+in comparison with experimental data.
+In this section, we examine the validity of
+the collective treatment of the pairing.
 
@@
 
-In the superfluid phase, the energy minimization always lead to $\phi=0$.
 Although the global gauge angle $\Phi$ is arbitrary,
-the deformation parameter $\alpha$ in gauge space is usually taken as real value ($\Phi=0$).
+The deformation parameter $\alpha\equiv \braket{ \hat{S}_- }$
+in the gauge space is
+usually taken as real value ($\Phi=0$).
+%In the superfluid phase, 
+The energy minimization with a fixed value of real $\alpha$ always
+leads to $\phi=0$.
 \begin{align}
 \alpha(j,J) = \braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
-	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
+%	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
+	= \frac{\Omega}{2} \left(\sqrt{1-q_1^2} +\sqrt{1-q_2^2} \right).
  \label{Delta_BCS}
 \end{align}
-$\alpha$ is equivalent to pairing gap $\Delta$ as a coordinate because the gap equation
-\begin{align}
-  \alpha = \frac{1}{2}\sum_{k>0}\frac{\Delta}{\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}}
-\end{align}
+The parameter $\alpha$ is equivalent to pairing gap $\Delta$,
+% as a coordinate because the gap equation
+%\begin{align}
+%  \alpha = \frac{1}{2}\sum_{k>0}\frac{\Delta}{\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}}
+%\end{align}
+since the relation, $\Delta=G\alpha$,
 guarantees one-to-one correspondence between $\alpha$ and $\Delta$.
+In Sec.~\ref{sec:canonical}, we treat $\phi$ as a collective coordinate
+and $j$ as its conjugate momentum.
+The collective model treatment is based on the opposite choice,
+$j$ as a coordinate and $\phi$ as a momentum.
+
+\begin{figure}[tb]
+ \begin{center}
+(a) \includegraphics[height=0.46\textwidth,angle=-90]{images/N8p_E.eps}
+(b) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16p_E.eps}
+ \end{center}
+ \caption{Energy surface as functions of $j$
+ for $x=0.5$, $x=2$ and $x=3.2$.
+ Dashed line is the pairing deformation parameter $\alpha$
+ of Eq.~(\ref{Delta_BCS}) as a function of $j$.
+ (a) mid-shell ($\Omega=N=8$) and (b) closed-shell ($2\Omega=N=16$).
+}
+ \label{fig:p_Delta}
+\end{figure}
+
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
+% \end{center}
+% \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=16$ system.
+% Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
+% \label{fig:p_Delta2}
+%\end{figure}
+
+The problem is that
+there is no one-to-one correspondence between $j$ and $\alpha$.
 The relation between $j$ and $\alpha$ 
-and that between $j$ and $E=\mathcal{H}(\phi=0,j;J)$
-are shown for $\Omega=8$
-in Fig. \ref{fig:p_Delta1} ($N=8$) and Fig. \ref{fig:p_Delta2} ($N=16$).
-%These results correspond to the system in Section 4.2. 
+are shown by dashed lines in Fig.~\ref{fig:p_Delta}
+for $\Omega=8$ mid-shell (a) and closed-shell (b) configurations.
 The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
@@
 produce the states corresponding to $j>0$.
-Apparently, we cannot map the entire region of $j$ to $\alpha$,
-since there is no one-to-one correspondence between $j$ and $\alpha$.
-
-If the system has a deep potential at $j<0$ to prevent the wave function
-from spreading toward the region of $j<0$,
-we may justify the use of $\alpha$ as a coordinate in
-the collective model.
-The importance of the region of $j<0$ is considerable in strong pairing case.
-Fig. \ref{fig:Delta_E} shows two examples of the relationship 
+Apparently, we cannot map the entire region of $j$ to $\alpha$.
+%since there is no one-to-one correspondence between $j$ and $\alpha$.
+
+The collective model treatment
+requires the collective wave functions to be well localized
+in the $j<0$ region.
+The potential energy, $E=\mathcal{H}(\phi=0,j;J)$, is also shown in
+Fig.~\ref{fig:p_Delta}.
+The restriction becomes more serious for the stronger pairing cases.
+For instance, the potential with $x=3.2$ in Fig.~\ref{fig:p_Delta}(a)
+has only about 1 MeV depth at the minimum point, relative to the value
+at the boundary point ($j=0$) with the maximum value of $\alpha$ ($\Delta$).
+
+%If the system has a deep potential at $j<0$ to prevent the wave function
+%from spreading toward the region of $j<0$,
+%we may justify the use of $\alpha$ as a coordinate in
+%the collective model.
+%The importance of the region of $j<0$ is considerable in strong pairing case.
+Figure~\ref{fig:Delta_E} shows two examples of the relationship 
 between excitation energies and energy surface.
-In the left panel ($\Omega=50$, $N=50$, $x=2.4$), the excited $0^+$ states are bound up to second excitation.
+In the panel (a), we show the case of large $\Omega$
+($\Omega=50$, $N=50$, $x=2.4$),
+in which
+the excited $0^+$ states are bound up to second excitation.
 For very large degeneracy, the pocket of energy surface is deep, 
-hence the low-lying excited states can be described by $\alpha$. 
-However, in the right panel ($\Omega=8$, $N=16$, $x=2.4$), 
-only the ground state is bound, and all excited $0^+$ states are unbound.
-For small degeneracy, the shallow pocket of energy surface allows 
-the excited $0^+$ states to be unbound. Therefore, pairing deformation parameter
-is not proper collective coordinate in small $\Omega$ and strong pairing case.
+hence the low-lying excited states may be described by $\alpha$. 
+However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
+of the panel (b), no excited states are bound.
+This shallow pocket of potential energy is a consequence of the
+choice of the collective coordinate
+which represents only the $j<0$ region.
+Therefore, the collective model treatment assuming
+$\alpha$ ($\Delta$) as the collective coordinate
+is not applicable to small-$\Omega$ and strong-pairing cases.
 
@@
 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=50mm,angle=-90]{images/N8p_E.eps}
- \end{center}
- \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=8$ system.
- Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
- \label{fig:p_Delta1}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
- \end{center}
- \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=16$ system.
- Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
- \label{fig:p_Delta2}
-\end{figure}
-
-\begin{figure}[htbp]
- \begin{minipage}{0.45\hsize}
- \begin{center}
-  \includegraphics[width=50mm,angle=-90]{images/N50Xeq2p4gap_E.eps}
- \end{center}
- \end{minipage}
- \begin{minipage}{0.45\hsize}
- \begin{center}
-  \includegraphics[width=50mm,angle=-90]{images/N16Xeq2p4gap_E.eps}
- \end{center}
-\end{minipage}
- \caption{Energy surface with respect to $\alpha$ in $x=2.4$. 
-Green lines are energy spectra until 3rd excitation obtained from CQ 
-(Sec.~\ref{sec:canonical}). Left panels: $\Omega=50$, $N=50$ system;
- Right panels: $\Omega=8$, $N=16$ system.}
+\begin{figure}[tb]
+% \begin{minipage}{0.45\hsize}
+ \begin{center}
+(a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50Xeq2p4gap_E.eps}
+% \end{center}
+% \end{minipage}
+% \begin{minipage}{0.45\hsize}
+% \begin{center}
+(b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2p4gap_E.eps}
+ \end{center}
+%\end{minipage}
+\caption{Potential energy surface as functions of $\alpha$ with $x=2.4$;
+(a) $\Omega=N=50$,
+(b) $2\Omega=N=16$.
+Horizontal (green) lines indicate
+ energy spectra obtained with the CQ method
+(Sec.~\ref{sec:canonical}).
+%Left panels: $\Omega=50$, $N=50$ system;
+% Right panels: $\Omega=8$, $N=16$ system.
+}
  \label{fig:Delta_E}
@@
 diagonal parts dominate.
-However, the pairing collectivity may not be too weak to justify this
+However, the pairing collectivity may be too weak to justify this
 treatment.
@@
 
-We give the detail derivation of semiclassical wave function 
-discussed in Sec \ref{sec:SPA}. The explicit form of coherent state is
+We give a derivation of the semiclassical wave function
+of Eq. (\ref{semi_wave_func1}).
+The explicit form of coherent state is
 \begin{align}
@@
 \end{align} 
-Inserting (\ref{ZZ}) into (\ref{semi_wave_func0}) under fixed $N$ and $E_k$, The classical wave function becomes
+Inserting (\ref{ZZ}) into (\ref{semi_wave_func0}) under fixed $N$ and $E_k$,
+it becomes
 \begin{align}
@@
 \end{align}
-From 2nd line to 3rd line, we can find that it is nothing but number projection. In SU(2) quasispin representation, the vacuum state becomes $\ket{0}=\ket{S_1,-S_1;S_2,-S_2}$, which leads
+We find that the integration over $\Phi$ is nothing but the number projection.
+In SU(2) quasi-spin representation, the vacuum state is written as
+$\ket{0}=\ket{S_1,-S_1;S_2,-S_2}$, which leads to
 \begin{align}
@@
 \end{align}
-For convenience, we define a coefficient 
+For convenience, we define coefficients
 \begin{align}
@@
 \end{align}
-where $q=\cos{\theta}$. Inserting (\ref{tan}) into (\ref{semi_wave_func_b}) and using $N/2=J$, the semiclassical wave function attributes to (\ref{semi_wave_func1}).
+where $q=\cos{\theta}$.
+Inserting Eq. (\ref{tan}) into Eq. (\ref{semi_wave_func_b}) with $N/2=J$,
+we reach Eq. (\ref{semi_wave_func1}).
 %\begin{align}
@@
 
-\bibliographystyle{unsrt}
+\bibliographystyle{apsrev4-1}
 \bibliography{ref}

### 2017-11-27 draft1.2.tex
modified:   draft1.2.tex

@@
  \end{center}
- \caption{Energy surface as functions of $j$
+ \caption{Energy surface as functions of $j$,
+ Eq. (\ref{TDHFB_Hamiltonian_3}) with $\phi=0$,
  for $x=0.5$, $x=2$ and $x=3.2$.
@@
 in the $j<0$ region.
-The potential energy, $E=\mathcal{H}(\phi=0,j;J)$, is also shown in
+The potential energy, $E(j)=\mathcal{H}(\phi=0,j;J=N/2)$ of
+Eq. (\ref{TDHFB_Hamiltonian_3}), is also shown in
 Fig.~\ref{fig:p_Delta}.
@@
 has only about 1 MeV depth at the minimum point, relative to the value
-at the boundary point ($j=0$) with the maximum value of $\alpha$ ($\Delta$).
+at the boundary point ($j=0$) corresponding to
+the maximum value of $\alpha$ ($\Delta$).
 
@@
 %The importance of the region of $j<0$ is considerable in strong pairing case.
+To simulate the result of the collective model, we expand the Hamiltonian
+(\ref{TDHFB_Hamiltonian_3}) up to the second order in $\phi$,
+then, quantize it by $\hat{\phi}=i\partial/\partial j$ with
+the ordering given by the Pauli's prescription.
+The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
+with the vanishing boundary condition $\psi(j_{\rm min})=\psi(0)=0$.
 Figure~\ref{fig:Delta_E} shows two examples of the relationship 
-between excitation energies and energy surface.
+between excitation energies and the potential energy surface.
 In the panel (a), we show the case of large $\Omega$

### 2017-12-06 draft1.2.tex
Modified 4.C

@@
 in Fig~\ref{fig:N50_occ}.
-For the CQ, $|c_{k,p}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
+For the CQ, $|c_{k,j}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
 Here, $m$ and $j$ are related to each other, $2j=J-2m$.
@@
 the excited $0^+$ states are bound up to second excitation.
+From the collective model, the energies of ground state and first excited state are
+well described, while the deviation of the energies from second excitation
+becomes larger and larger.
 For very large degeneracy, the pocket of energy surface is deep, 
@@
 of the panel (b), no excited states are bound.
+We can see the excited $0^+$ states from collective model 
+are not described correctly.
 This shallow pocket of potential energy is a consequence of the
@@
  \begin{center}
-(a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50Xeq2p4gap_E.eps}
+(a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50Xeq2p4gap_E(2).eps}
 % \end{center}
@@
 % \begin{center}
-(b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2p4gap_E.eps}
+(b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2p4gap_E(2).eps}
  \end{center}
@@
 (b) $2\Omega=N=16$.
-Horizontal (green) lines indicate
- energy spectra obtained with the CQ method
+Horizontal lines 
+indicate energy spectra. Black lines are obtained
+from the potential energy surface, and green lines are 
+obtained with the CQ method
 (Sec.~\ref{sec:canonical}).

### 2017-12-07 draft1.2.tex
Modified the trivial mistakes

@@
 the deformation parameters $(\beta, \gamma)$ and the Euler angles
-$(\alpha,\beta,\gamma)$.
+$(\phi,\theta,\psi)$.
 For the pairing motion, the collective coordinates are analogously
@@
 \end{align}
-Since the coherent states (\ref{coherent}) contains only even number of
-particles in each level,
-we assume that $n_l$ are even numbers.
 %The expectation value of total particle number is
@@
 relative angle $\phi$.
-Here, the ``rotational behavior'' means that the motion span the whole
+Here, the ``rotational behavior'' means that the motion spans the whole
 region of the angle $\phi$,
@@
 \begin{equation}
-	\ket{\phi_k} = \oint d\mu(Z_{\rm cl}^{(k)}) \ket{Z_{\rm cl}^{(k)}}
+	\ket{\psi_k} = \oint d\mu(Z_{\rm cl}^{(k)}) \ket{Z_{\rm cl}^{(k)}}
 	e^{i\mathcal{T}[Z_{\rm cl}^{(k)}]} .
@@
 \begin{equation}
-  \ket{\phi_k} \propto \oint d\theta_1\cdots \oint d\theta_M \ 
+  \ket{\psi_k} \propto \oint d\theta_1\cdots \oint d\theta_M \ 
 	\rho(E_k,v^{(k)},\theta)
@@
 \begin{align}
-	\ket{\phi_k^N} &\propto \oint d\Phi \oint dt
+	\ket{\psi_k^N} &\propto \oint d\Phi \oint dt
 	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
@@
 	= \pm \frac{N}{2} \pi + \int_{-\pi}^\pi j d\phi
-	= 2k\pi .
+	= 2m\pi .
 \end{equation}
@@
 \end{equation}
-where $k$ and $n>0$ are integer numbers.
+where $m$, $k$ and $n>0$ are integer numbers.
 
@@
 \begin{align}
-  S_+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_+|Z}
+  S^+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}^+|Z}
  = \frac{1}{2}
@@
 	\label{Sp_mean_value} \\
-  S_-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}_-|Z}
+  S^-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}^-|Z}
  = \frac{1}{2}
@@
 %  &S_+(\Phi,\Pi;\phi,\pi) \to S_+(\hat{\Phi},\hat{\Pi};\hat{\phi},\hat{\pi}) \nonumber \\
-  S_\pm (\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
+  S^\pm (\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
 	&=& \frac{1}{4}\left( \Omega_1\sqrt{1-q_1^2}e^{\mp i\hat{\phi}/2}
@@
 B(P_{\rm ad};k\rightarrow k') &=
-|\braket{N',k'|S_+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})|N,k}|^2
+|\braket{N',k'|S^+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})|N,k}|^2
 	\nonumber \\
@@
 	\psi^{(N')*}_{k'}(\phi) e^{-i\frac{N'}{2}\Phi}
-	S_+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
+	S^+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
 	\psi^{(N)}_{k}(\phi)e^{i\frac{N}{2}\Phi} \right|^2,
@@
 The pair transfer matrix elements are evaluated as the Fourier components
-of the time-dependent mean values $S_\pm(t)=S_\pm(Z(t))$,
+of the time-dependent mean values $S^\pm(t)=S^\pm(Z(t))$,
 Eqs. (\ref{Sp_mean_value}) and (\ref{Sm_mean_value}).
@@
 \begin{equation}
-	\tilde{S}_\pm(E_k; \omega) = \frac{1}{T}\int_0^T dt
-	e^{i\omega t} S_\pm(t) ,
+	\tilde{S}^\pm(E_k; \omega) = \frac{1}{T}\int_0^T dt
+	e^{i\omega t} S^\pm(t) ,
 \label{Fourier_decomposition}
@@
 	B(P_{\rm ad};k\rightarrow k') 
-	= \left|\tilde{S}_+\left(E_k;\frac{2\pi}{T}\Delta k \right) \right|^2 ,
+	= \left|\tilde{S}^+\left(E_k;\frac{2\pi}{T}\Delta k \right) \right|^2 ,
 \end{equation}
@@
 classical limit \cite{LL65}.
-The TDHFB state is assumed to be a superposition of eigenstates
+The TDHFB state is assumed to be a superposition of eigenstates $\ket{\phi_k^N}$
 in a narrow range of energy $E_{k_0}-\Delta E<E_k<E_{k_0}+\Delta E$,
@@
 the coefficients $c_k^N$ slowly vary with respect to $k$ and $N$.
-The expectation value of $S_\pm$ is
-\begin{equation}
-	S_\pm(t) = \sum_{N} \sum_{k,k'} c_{k'}^{N+2*} c_k^N 
-	\braket{\phi_{k'}^{N+2}|S_\pm|\phi_k^N} e^{i(E_{k'}-E_k)t} .
-\end{equation}
-The matrix element $\braket{\phi_{k'}^{N+2}|S_\pm|\phi_k^N}$
+The expectation value of $S^\pm$ is
+\begin{equation}
+	S^\pm(t) = \sum_{N} \sum_{k,k'} c_{k'}^{N+2*} c_k^N 
+	\braket{\phi_{k'}^{N+2}|S^\pm|\phi_k^N} e^{i(E_{k'}-E_k)t} .
+\end{equation}
+The matrix element $\braket{\phi_{k'}^{N+2}|S^\pm|\phi_k^N}$
 quickly disappears as $|k'-k|$ increases, while it stays almost constant
@@
 $E_{k'}-E_k\approx \omega_0 \Delta k$, and
-that $\braket{\phi_{k'}^{N+2}|S_\pm|\phi_k^N}\approx
-\braket{\phi_{k_0+\Delta k}^{N+2}|S_\pm|\phi_{k_0}^N}$ 
-\begin{equation}
-	S_\pm(t) \approx \sum_{N} \sum_{k} \left|c_k^N\right|^2
+that $\braket{\phi_{k'}^{N+2}|S^\pm|\phi_k^N}\approx
+\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}$ 
+\begin{equation}
+	S^\pm(t) \approx \sum_{N} \sum_{k} \left|c_k^N\right|^2
 	\sum_{\Delta k}
-	\braket{\phi_{k_0+\Delta k}^{N+2}|S_\pm|\phi_{k_0}^N}
+	\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}
 	e^{i\omega_0 \Delta k t} 
 	= \sum_{\Delta k}
-	\braket{\phi_{k_0+\Delta k}^{N+2}|S_\pm|\phi_{k_0}^N}
+	\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}
 	e^{i\omega_0 \Delta k t}  ,
@@
 %  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
-(a2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
-(b2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+(a2)\includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
+(b2)\includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
 The FD calculation is based on the time evolution of the expectation 
-value $S_+(t)$ with fixed $(J,\Phi)$ in Eq. (\ref{Fourier_decomposition}).
+value $S^+(t)$ with fixed $(J,\Phi)$ in Eq. (\ref{Fourier_decomposition}).
 %There is some ambiguity for the calculation of $S_+(t)$,
@@
 this is nothing but the expectation value at the BCS wave function,
-with the constant value of $S_+$.
-Since the constant $S_+$ provides only $\Delta k=0$ intraband transitions,
+with the constant value of $S^+$.
+Since the constant $S^+$ provides only $\Delta k=0$ intraband transitions,
 for the interband transition of $(N,k=0)\rightarrow (N+2,k=1)$
@@
 $B(P_{\rm ad}; 1\rightarrow 0)$ and $B(P_{\rm ad}; 0\rightarrow 1)$
-are roughly identical,
-while their magnitude is significantly smaller than
-$B(P_{\rm ad}; 0\rightarrow 1)$ at $x\lesssim 1$.
-This indicates the character change of the $k=1$ states
-from the vibration around the ``spherical'' ground state
-to that around the ``deformed'' ground state.
-This is analogous to the quadrupole vibrations in spherical nuclei
-and the beta vibrations in deformed nuclei, respectively.
-%The latter may correspond to the Higgs amplitude mode.
+are roughly identical. This is because both $B(P_{\rm ad}; 1\rightarrow 0)$ 
+and $B(P_{\rm ad}; 0\rightarrow 1)$ correspond to one-phonon excitation
+in ``deformed'' cases ($x \gg 1$).
 
@@
 The intraband $k\rightarrow k$ transitions increase and 
-the interband $k=1\rightarrow 0$ transitions decrease as
+the interband $k=0\rightarrow 1$ transitions decrease as
 functions of $x$.
@@
 The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
-because $S_+(t)$ is calculated for a $N=14$ system.
+because $S^+(t)$ is calculated for a $N=14$ system.
 Both intraband and interband transitions in the FD calculations
@@
 Although the global gauge angle $\Phi$ is arbitrary,
-The deformation parameter $\alpha\equiv \braket{ \hat{S}_- }$
+The deformation parameter $\alpha\equiv \braket{ \hat{S}^- }$
 in the gauge space is
@@
 \begin{align}
-\alpha(j,J) = \braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
+\alpha(j,J) = \braket{Z_0|\hat{S}^-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
 %	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
@@
 The CQ and FD calculate the pair transfer matrix elements using only
-the diagonal part (expectation value) of the operator $\hat{S}_\pm$,
+the diagonal part (expectation value) of the operator $\hat{S}^\pm$,
 based on Eqs. (\ref{Sp_mean_value}) and (\ref{Sm_mean_value}).
@@
 \begin{align}
-  \ket{Z} &= \prod_{l=1}^2(1+|Z_l|^2)^{-\Omega_l/2}e^{Z_lS_l^{\dag}}\ket{0} \nonumber \\
+  \ket{Z} &= \prod_{l=1}^2(1+|Z_l|^2)^{-\Omega_l/2}e^{Z_lS_l^{+}}\ket{0} \nonumber \\
   &= \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
   {}_kC_m \left(
-  \tan{\frac{\theta_1}{2}}e^{-i\phi_1}S_1^{\dag} \right)^m \left(
-  \tan{\frac{\theta_2}{2}}e^{-i\phi_2}S_2^{\dag} \right)^{k-m} \ket{0} \nonumber \\
+  \tan{\frac{\theta_1}{2}}e^{-i\phi_1}S_1^{+} \right)^m \left(
+  \tan{\frac{\theta_2}{2}}e^{-i\phi_2}S_2^{+} \right)^{k-m} \ket{0} \nonumber \\
   &= \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
   {}_kC_m \tan^m{\frac{\theta_1}{2}}\tan^{k-m}{\frac{\theta_2}{2}}e^{-ik\Phi}e^{-i(k/2-m)\phi}
-  (S_1^{\dag})^m(S_2^{\dag})^{k-m} \ket{0}
+  (S_1^{+})^m(S_2^{+})^{k-m} \ket{0}
   \label{ZZ}
@@
   &\times \left\{ \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \right\}
-\tan^m{\frac{\theta_1}{2}}\tan^{k-m}\frac{\theta_2}{2}(S_1^{\dag})^m(S_2^{\dag})^{k-m} \ket{0} \nonumber \\
+\tan^m{\frac{\theta_1}{2}}\tan^{k-m}\frac{\theta_2}{2}(S_1^{+})^m(S_2^{+})^{k-m} \ket{0} \nonumber \\
   \propto& \sum_{m=0}^{N/2}{}_{N/2}C_m  \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(N/4-m)\phi \right)} \nonumber \\
   &\times \left\{ \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \right\} 
-\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{\dag})^m(S_2^{\dag})^{N/2-m} \ket{0} \label{semi_wave_func_b}
+\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} \label{semi_wave_func_b}
 \end{align}
@@
 \begin{align}
-  (S_1^{\dag})^m(S_2^{\dag})^{N/2-m} \ket{0} 
+  (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} 
   = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(N/2-m)!}{(2S_2-(N/2-m))!}}
@@
 %\begin{align}
- % \sum_{m=0}^{J}{}_J C_m\int_0^T dt \exp{\left( i\int^t \pi(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) (S_1^{\dag})^m(S_2^{\dag})^{J-m}\ket{0}
+ % \sum_{m=0}^{J}{}_J C_m\int_0^T dt \exp{\left( i\int^t \pi(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) (S_1^{+})^m(S_2^{+})^{J-m}\ket{0}
 %\end{align}

### 2017-12-08 draft1.3.tex
submitted draft1.3.tex to arxiv

--- 2017-12-07 draft1.2.tex
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
+  \includegraphics[width=60mm,angle=-90]{phase.eps}
  \end{center}
@@
 % \begin{center}
-%%  \includegraphics[bb=0 0 120 120]{images/Sommerfeld1.png}
+%%  \includegraphics[bb=0 0 120 120]{Sommerfeld1.png}
 % \end{center}
@@
 % \begin{center}
-%%  \includegraphics[bb=0 0 120 120]{images/Sommerfeld2.png}
+%%  \includegraphics[bb=0 0 120 120]{Sommerfeld2.png}
 % \end{center}
@@
 equation for the motion in the relative angle $\phi$.
-%pairing vibrational mode can be obtained by solving the Schrodinger equation
+%pairing vibrational mode can be obtained by solving
+the Schr\"{o}dinger equation
 \begin{equation}
@@
 \end{equation}
-%where $i$ is the excitation index under the system of fixed total particle number $N$. To solve the Schrodinger equation, the wave function can be expanded as
+%where $i$ is the excitation index under the system of fixed total particle number $N$. To solve the Schr\"{o}dinger equation, the wave function can be expanded as
 %we consider two different methods, which are classified by Type I and Type II.\par
@@
 expected to occupy around the minimum value of $j$. 
-We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, 
+We choose the Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, 
 where $q_{min}$ corresponds to the minimum value of $j$. Under such boundary condition, 
@@
  \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
-%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
-	 (a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
-	 (b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
+%  \includegraphics[width=60mm,angle=-90]{N50ex_energy_wo_adiabatic.eps}
+%  \includegraphics[width=60mm,angle=-90]{N100ex_energy_wo_adiabatic.eps}
+	 (a)  \includegraphics[height=0.46\textwidth,angle=-90]{N50ex_energy_wo_adiabatic.eps}
+	 (b)  \includegraphics[height=0.46\textwidth,angle=-90]{N100ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
-%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
-(a1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
-(b1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
+(a)\includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
+(b)\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
-%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
-(a2)\includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
-(b2)\includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
+\hspace{13pt}
+\includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
+\hspace{13pt}\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N50Pad_CQ.eps}
+  \includegraphics[width=70mm,angle=-90]{N50Pad_CQ.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N50Pad_FD.eps}
+  \includegraphics[width=70mm,angle=-90]{N50Pad_FD.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N50Pad_SPA.eps}
+  \includegraphics[width=70mm,angle=-90]{N50Pad_SPA.eps}
  \end{center}
@@
 % \begin{center}
-%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
+%  \includegraphics[width=60mm,angle=-90]{N100ex_energy_wo_adiabatic.eps}
 % \end{center}
@@
 % \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
 % \end{center}
@@
 % \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
 % \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N100Pad_CQ.eps}
+  \includegraphics[width=70mm,angle=-90]{N100Pad_CQ.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N100Pad_FD.eps}
+  \includegraphics[width=70mm,angle=-90]{N100Pad_FD.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N100Pad_SPA.eps}
+  \includegraphics[width=70mm,angle=-90]{N100Pad_SPA.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy_wo_adiabatic.eps}
+  \includegraphics[width=60mm,angle=-90]{N8ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
- (a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N8Xeq0p5occ_wo_adiabatic.eps}
- (b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N8Xeq2occ_wo_adiabatic.eps}
+ (a)  \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
+ (b)  \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N8Pad_CQ.eps}
+  \includegraphics[width=70mm,angle=-90]{N8Pad_CQ.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N8Pad_FD.eps}
+  \includegraphics[width=70mm,angle=-90]{N8Pad_FD.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N8Pad_SPA.eps}
+  \includegraphics[width=70mm,angle=-90]{N8Pad_SPA.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy_wo_adiabatic.eps}
+  \includegraphics[width=60mm,angle=-90]{N16ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-(a) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq0p5occ_wo_adiabatic.eps}
-(b) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2occ_wo_adiabatic.eps}
+(a) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
+(b) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N16Pad_CQ.eps}
+  \includegraphics[width=70mm,angle=-90]{N16Pad_CQ.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N16Pad_FD.eps}
+  \includegraphics[width=70mm,angle=-90]{N16Pad_FD.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=70mm,angle=-90]{images/N16Pad_SPA.eps}
+  \includegraphics[width=70mm,angle=-90]{N16Pad_SPA.eps}
  \end{center}
@@
  \begin{center}
-(a) \includegraphics[height=0.46\textwidth,angle=-90]{images/N8p_E.eps}
-(b) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16p_E.eps}
+(a) \includegraphics[height=0.46\textwidth,angle=-90]{N8p_E.eps}
+(b) \includegraphics[height=0.46\textwidth,angle=-90]{N16p_E.eps}
  \end{center}
@@
 % \begin{center}
-%  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
+%  \includegraphics[width=50mm,angle=-90]{N16p_E.eps}
 % \end{center}
@@
 the excited $0^+$ states are bound up to second excitation.
-From the collective model, the energies of ground state and first excited state are
-well described, while the deviation of the energies from second excitation
-becomes larger and larger.
+From the collective model, the energies of ground and first excited states
+are well described, while the deviation becomes larger for
+higher excited states.
 For very large degeneracy, the pocket of energy surface is deep, 
@@
 However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
-of the panel (b), no excited states are bound.
-We can see the excited $0^+$ states from collective model 
-are not described correctly.
-This shallow pocket of potential energy is a consequence of the
-choice of the collective coordinate
+of the panel (b), no excited states are bound by the potential
+as a function of $\alpha$.
+None of the excited $0^+$ states
+are properly described in the collective model.
+This shallow potential is a consequence of the improper
+choice of the collective coordinate $\alpha$
 which represents only the $j<0$ region.
@@
  \begin{center}
-(a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50Xeq2p4gap_E(2).eps}
+(a)  \includegraphics[height=0.46\textwidth,angle=-90]{N50Xeq2p4gap_E.eps}
 % \end{center}
@@
 % \begin{center}
-(b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2p4gap_E(2).eps}
+(b)  \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2p4gap_E.eps}
  \end{center}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Acknowledgments
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgments}
+This work is supported in part
+by Interdisciplinary Computational Science Program in CCS,
+University of Tsukuba,
+and
+by JSPS-NSFC Bilateral Program for Joint Research Project
+on Nuclear mass and life for unravelling mysteries of r-process.
+%and by ImPACT Program of Council for Science,
+%Technology and Innovation (Cabinet Office, Government of Japan).
+\end{acknowledgments}
+
 \appendix
@@
 \begin{align}
-	\ket{\phi_k^N} \propto& \oint d\Phi \oint dt
+	\ket{\psi_k^N} \propto& \oint d\Phi \oint dt
 	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}

### 2018-02-06 draft2.1.tex
draft 2.1

--- 2017-12-08 draft1.3.tex
@@
 The QRPA has been extensively utilized and successfully
-describe properties of giant resonances.
+describes properties of giant resonances.
 In contrast, many of low-lying excited states
@@
 which leads to difficulties in description of the quantum tunneling
-processes, such as spontaneous fission and sub-barrier fusion reaction.
+processes, such as spontaneous fission and sub-barrier fusion reaction \cite{S12}.
 For this purpose,
@@
 the requantization of the mean-field dynamics was
-proposed \cite{Neg82,KS80,K81,Rei80}.
+proposed \cite{Neg82,L80,LNP80,KS80,K81,Rei80}.
 It recovers quantum fluctuations missing in the mean-field
@@
 the two-particle-transfer matrix elements were evaluated as
-Fourier components of the time-dependent mean values of the pair
-creation operators,
+Fourier components of the time-dependent mean values of the pair-creation operators,
 which demonstrates nice agreement with the exact results at
@@
 The wave functions are obtained
-from the stationary phase approximation for the path-integral form \cite{SM88}.
+from the stationary-phase approximation for the path-integral form \cite{SM88}.
 Its superiority to the other methods
@@
 degeneracy ($\Omega_l=j_l+1/2$)
-and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,\Omega_l-1/2$.
+and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_l-1/2$.
 The occupation number of each level $l$ is given by
@@
 	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-\Omega_l/2}
-	\exp (Z_l(t) S_l^{+}) \ket{0}
+	\exp [Z_l(t) S_l^{+}] \ket{0}
  \label{coherent}
@@
 We transform the complex variables $Z_l$ into real variables $(q_l,\chi_l)$
-by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ and $q_l=\cos{\theta_l}$.
+by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ and $q_l=\cos{\theta_l}$ ($0\leq\theta\leq\pi$).
 The Lagrangian $\mathcal{L}$ and the expectation value of Hamiltonian become
@@
 	(1-q_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
-	\mathcal{H}(Z,Z^*)&\equiv \braket{Z|H|Z} = \sum_l \epsilon_l\Omega_l(1- q_l) - \frac{g}{4}\sum_l \Omega_l (\Omega_l(1-q_l^2)+(1-q_l)^2) \nonumber \\
+	\mathcal{H}(Z,Z^*) \equiv \braket{Z|H|Z} =& \sum_l \epsilon_l\Omega_l(1- q_l) - \frac{g}{4}\sum_l \Omega_l [\Omega_l(1-q_l^2)+(1-q_l)^2] \nonumber \\
 &- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}\sqrt{(1-q_{l_1}^2)(1-q_{l_2}^2)}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
@@
 \end{align}
-Here, $\chi_l$ represent a kind of gauge angle of each level,
+Here, $\chi_l$ represents a kind of gauge angle of each level,
 and $q_l$ are related to the occupation probability, $q_l=|u_l|^2-|v_l|^2$.
@@
 \end{align}
-Calculating the occupation number $n_l$ in the level $l$,
-the physical meaning of these conjugate momenta becomes obvious.
+By calculating the occupation number $n_l$ in the level $l$,
+the physical meaning of these conjugate momenta becomes obvious
 \begin{equation}
@@
 	= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
-	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
+	- \frac{g}{4} [\Omega_l(1-q_l^2)+(1-q_l)^2] \right\}
 - \frac{g}{2}\Omega_1\Omega_2
-	\sqrt{(1-q_1^2)(1-q_2^2)} \cos\phi .
+	\sqrt{(1-q_1^2)(1-q_2^2)} \cos\phi
 \label{TDHFB_Hamiltonian_3}
@@
 All the TDHFB trajectories represent rotational behavior with respect to
-relative angle $\phi$.
+the relative angle $\phi$.
 Here, the ``rotational behavior'' means that the motion spans the whole
@@
 	= \int d\mu(Z'') \ket{Z''} \int d\mu(Z')
-	\int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)])
+	\int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)]
 	e^{i\mathcal{S}[Z(\tau)]} \psi(Z') ,
@@
 Among all trajectories in the path integral,
-the lowest stationary phase approximation selects
+the lowest stationary-phase approximation selects
 the TDHFB (classical) trajectories.
@@
 which can be constructed by superposing the coherent states along
-a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{KS80,K81,SM88}.
+a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{KS80,K81,SM88}
 \begin{equation}
@@
 \begin{align}
-  C_m^{(E_k,J)} &= {}_J C_m\int_0^T dt \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
+  C_m^{(E_k,J)} &= \binom{J}{m}\int_0^T dt \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
   & \hspace{5mm} A(q,S,m) = \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
@@
 %The system consists of $\Omega=50$ and $\Delta\epsilon=1$(MeV). We show the results in $N=50$ system, which is always superfluidity in ground state.\par
-Calculated excitation energies are shown in Figs.~\ref{fig:N50energy}.
+Calculated excitation energies are shown in Fig.~\ref{fig:N50energy}.
 %and \ref{fig:N100energy}.
@@
 the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
-in Fig~\ref{fig:N50_occ}.
+in Fig.~\ref{fig:N50_occ}.
 For the CQ, $|c_{k,j}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
@@
 respectively. 
-The three vertical bars at each $j$ from the left to the right represents
+The three vertical bars at each $j$ from the left to the right represent
 the squared components of the wave functions
@@
 indicating the pair-rotational character.
-The interband $B(P_{\rm ad}; 0\rightarrow 1)$ shows a gradual decrease
+The interband $B(P_{\rm ad}; 0\rightarrow 1)$ show a gradual decrease
 as a function of $x$, while
@@
 for both the closed- and mid-shell configurations.
-The CQ method qualitatively agree with the exact calculation.
+The CQ method qualitatively agrees with the exact calculation.
 For instance, the order-of-magnitude difference between intraband
@@
 The first excited state corresponds to the open trajectory which
-turns out to almost perfectly reproduces the exact wave function.
+turns out to almost perfectly reproduce the exact wave function.
 In contrast, this open trajectory produces results far from the exact
-result in the FD method.
+one in the FD method.
 It produces almost vanishing the intraband
-$B(P_{\rm ad}; 1\rightarrow 1)$ and the interband transitions.
+$B(P_{\rm ad}; 1\rightarrow 1)$.
 The $B(P_{\rm ad}; 0\rightarrow 0)$ shows a qualitative agreement for
@@
 The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
-because $S^+(t)$ is calculated for a $N=14$ system.
+because $S^+(t)$ is calculated for an $N=14$ system.
 Both intraband and interband transitions in the FD calculations
@@
 Although the global gauge angle $\Phi$ is arbitrary,
-The deformation parameter $\alpha\equiv \braket{ \hat{S}^- }$
+the deformation parameter $\alpha\equiv \braket{ \hat{S}^- }$
 in the gauge space is
-usually taken as real value ($\Phi=0$).
+usually taken as a real value ($\Phi=0$).
 %In the superfluid phase, 
@@
 \end{align}
-The parameter $\alpha$ is equivalent to pairing gap $\Delta$,
+The parameter $\alpha$ is equivalent to the pairing gap $\Delta$,
 % as a coordinate because the gap equation
@@
  \end{center}
- \caption{Energy surface as functions of $j$,
+ \caption{Energy surfaces as functions of $j$,
  Eq. (\ref{TDHFB_Hamiltonian_3}) with $\phi=0$,
- for $x=0.5$, $x=2$ and $x=3.2$.
+ for $x=0.5$, $2$, and $3.2$.
  Dashed line is the pairing deformation parameter $\alpha$
@@
 The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
-and smallest at end points of $j$.
+and smallest at the end points of $j$.
 The constrained minimization with respect to $\alpha$ cannot 
@@
 In the panel (a), we show the case of large $\Omega$
-($\Omega=50$, $N=50$, $x=2.4$),
+($\Omega=50$, $N=50$, and $x=2.4$),
 in which
 the excited $0^+$ states are bound up to second excitation.
-From the collective model, the energies of ground and first excited states
+From the collective model, the energies of the ground and the first excited states
 are well described, while the deviation becomes larger for
@@
 hence the low-lying excited states may be described by $\alpha$. 
-However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
+However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, and $x=2.4$)
 of the panel (b), no excited states are bound by the potential
@@
 was studied for the two-level pairing model;
-the stationary phase approximation (SPA) of the path integral,
+the stationary-phase approximation (SPA) of the path integral,
 the canonical quantization (CQ), and the Fourier decomposition (FD)
@@
 only one pair of collective variables $(\phi,j)$, in addition to the
-pair rotational variables $(\Phi,J)$.
+pair-rotational variables $(\Phi,J)$.
 Even for such a simple system, we find that it is difficult to justify
@@
 the SPA is the most accurate tool for description of
-the pairing large amplitude collective motion in realistic nuclear system.
+the pairing large amplitude collective motion in realistic nuclear systems.
 The weak point of this approach is that it is applicable only to the
@@
   &= \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
-  {}_kC_m \left(
+  \binom{k}{m} \left(
   \tan{\frac{\theta_1}{2}}e^{-i\phi_1}S_1^{+} \right)^m \left(
@@
   &= \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
-  {}_kC_m \tan^m{\frac{\theta_1}{2}}\tan^{k-m}{\frac{\theta_2}{2}}e^{-ik\Phi}e^{-i(k/2-m)\phi}
+  \binom{k}{m} \tan^m{\frac{\theta_1}{2}}\tan^{k-m}{\frac{\theta_2}{2}}e^{-ik\Phi}e^{-i(k/2-m)\phi}
   (S_1^{+})^m(S_2^{+})^{k-m} \ket{0}
@@
 	\ket{\Phi,t}_{N,E_k} \nonumber \\
-  \propto& \sum_k \frac{1}{k!} \sum_{m=0}^k{}_kC_m \int_0^{2\pi} d\Phi e^{i(N/2-k)\Phi} 
+  \propto& \sum_k \frac{1}{k!} \sum_{m=0}^k \binom{k}{m} \int_0^{2\pi} d\Phi e^{i(N/2-k)\Phi} 
   \int_0^T dt e^{i\int \pi(t') \dot{\phi}(t') dt'-i(k/2-m)\phi} \nonumber \\
@@
 \tan^m{\frac{\theta_1}{2}}\tan^{k-m}\frac{\theta_2}{2}(S_1^{+})^m(S_2^{+})^{k-m} \ket{0} \nonumber \\
-  \propto& \sum_{m=0}^{N/2}{}_{N/2}C_m  \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(N/4-m)\phi \right)} \nonumber \\
+  \propto& \sum_{m=0}^{N/2} \binom{N/2}{m} \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(N/4-m)\phi \right)} \nonumber \\
   &\times \left\{ \prod_{l=1}^2\left(1+\tan^2{\frac{\theta_l}{2}}\right)^{-\Omega_l/2} \right\} 
-\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} \label{semi_wave_func_b}
+\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} . \label{semi_wave_func_b}
 \end{align}
@@
   (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} 
-  = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(N/2-m)!}{(2S_2-(N/2-m))!}}
+  = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(N/2-m)!}{[2S_2-(N/2-m)]!}}
   \ket{S_1,-S_1+m;S_2,-S_2+(N/2-m)}.

### 2018-02-07 draft2.2.tex
Revision on 2018.2.7

--- 2018-02-06 draft2.1.tex
@@
 is a natural extension of the static HFB theory.
+Thanks to increasing computational power,
+realistic applications of the TDHFB calculations in real time
+become available for studies of linear response properties
+\cite{Eba10,SBMR11,Has12,SL13-2,ENI14}
+and of various nuclear dynamics
+\cite{SL13-1,SBBMR15,SSL15,WSMBF16,MSW17,HS17}.
 The small-amplitude limit of the TDHFB is known to be 
@@
 describes properties of giant resonances.
+Recently, the QRPA calculations with modern energy density functionals
+for giant resonances in deformed nuclei have become available
+\cite{Nes06,YG08,PG08,AKR09,Los10,TE10,YN11,YN13}.
 In contrast, many of low-lying excited states
@@
 which leads to difficulties in description of the quantum tunneling
-processes, such as spontaneous fission and sub-barrier fusion reaction \cite{S12}.
+processes, such as spontaneous fission and sub-barrier fusion reaction.
+% \cite{S12}.
 For this purpose,
-since the TDHF(B) trajectory corresponds to a classical limit of the path
+since the TDHF(B) trajectory corresponds to a stationary-phase limit of the path
 integral formulation,
@@
 level, and possibly enables us to describe large-amplitude collective
-tunneling phenomena such as spontaneous fission \cite{Neg82}.
+tunneling phenomena.
+%such as spontaneous fission \cite{Neg82}.
 The requantization of the TDHFB is particularly feasible
@@
 the lowest stationary-phase approximation selects
-the TDHFB (classical) trajectories.
+the TDHFB (classical) trajectories\footnote{
+n this formulation, the stationary-phase approximation agrees with
+the TDHF(B) trajectories, while that to the auxiliary-field path
+integral of Refs. \cite{Neg82,L80}
+leads to the TDH(B) without the Fock potentials.
+}.
 %\begin{align}
@@
 	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
-	with $\Omega=16$.
+	with $\Omega=8$.
 }
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{ref}
+%\bibliography{ref}
+\bibliography{ref2}
 

### 2018-02-07 draft2.2.tex
corrected trivial mistakes

@@
 the TDHFB (classical) trajectories\footnote{
-n this formulation, the stationary-phase approximation agrees with
+In this formulation, the stationary-phase approximation agrees with
 the TDHF(B) trajectories, while that to the auxiliary-field path

### 2018-03-23 draft3.1.tex
draft3.1

--- 2018-02-07 draft2.2.tex
@@
 %  \includegraphics[width=67mm,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
-(a)\includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
-(b)\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
  \end{center}
@@
 %  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
-\hspace{13pt}
+
 \includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
-\hspace{13pt}\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
+\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
- (a)  \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
- (b)  \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
+   \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
+   \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-(a) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
-(b) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
+   \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
+   \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
 %In closed shell system, the phase transition is semiclassical approach is more quantitative than canonical approach except phase transition region.
-
 \begin{figure}[htbp]

### 2018-03-26 draft3.1.tex
revised draft3.1

@@
 %frontmatterverbose,
-preprint,
+%preprint,
 showpacs,
@@
 %prstper,
-%twocolumn,
+twocolumn,
 floatfix ]%
@@
 
-\title{Comparative study of requantization of time-dependent mean-field
-for pairing dynamics}
+\title{Comparative study of the requantization of the time-dependent mean
+field for the dynamics of nuclear pairing}
 \author{Fang Ni}
@@
 The ground states in many of even-even nuclei are well
-described by the Bardeen-Cooper-Schriefer (BCS)
+described by the Bardeen-Cooper-Schrieffer (BCS)
 and the Hartree-Fock-Bogoliubov (HFB) theories \cite{RS80,BHR03}.
@@
 single-particle energies $\epsilon_l$ and the pairing strength $g$ as
-\begin{equation}
+\begin{align}
 %  H &= \sum_l \epsilon_l n_l - \frac{g}{4} \sum_{ll'} P_l^{\dag}P_{l'}
-	H = \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^-
-    = \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
-\end{equation}
+	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- \nonumber \\
+    &= \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
+\end{align}
 where we use the SU(2) quasi-spin operators,
@@
 The action $\mathcal{S}$ is
-\begin{equation}
-	\mathcal{S}  = \int \mathcal{L}(t) dt
+\begin{align}
+	\mathcal{S}  &= \int \mathcal{L}(t) dt \nonumber \\
 	%&= \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt \\
-	= \int dt \left\{ \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
+	&= \int dt \left\{ \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
   (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{Z|H|Z} \right\} ,
 \label{S}
-\end{equation}
+\end{align}
 and
@@
 %  -g \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
-  \braket{Z|H|Z} &= \sum_l \epsilon_l \frac{2\Omega_l |Z_l|^2}{1+|Z_l|^2}
-  -g \sum_l \frac{\Omega_l|Z_l|^2(\Omega_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
-  -g \sum_{l_1 \neq l_2} \frac{\Omega_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{\Omega_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
+  \braket{Z|H|Z} =& \sum_l \epsilon_l \frac{2\Omega_l |Z_l|^2}{1+|Z_l|^2}
+  -g \sum_l \frac{\Omega_l|Z_l|^2(\Omega_l+|Z_l|^2)}{(1+|Z_l|^2)^2} \nonumber \\
+  &-g \sum_{l_1 \neq l_2} \frac{\Omega_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{\Omega_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
 	\label{TDHFB_Hamiltonian_1}
@@
 \begin{align}
-\mathcal{L}(t) &= \sum_l \frac{\Omega_l}{2}
-	(1-q_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
-	\mathcal{H}(Z,Z^*) \equiv \braket{Z|H|Z} =& \sum_l \epsilon_l\Omega_l(1- q_l) - \frac{g}{4}\sum_l \Omega_l [\Omega_l(1-q_l^2)+(1-q_l)^2] \nonumber \\
-&- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}\sqrt{(1-q_{l_1}^2)(1-q_{l_2}^2)}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
+\mathcal{L}(t) = \sum_l \frac{\Omega_l}{2}
+	(1&-q_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
+	\mathcal{H}(Z,Z^*) \equiv \braket{Z|H|Z}& \nonumber \\
+  = \sum_l \epsilon_l\Omega_l(1- q_l)& - \frac{g}{4}\sum_l \Omega_l [\Omega_l(1-q_l^2)+(1-q_l)^2] \nonumber \\
+- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}&\sqrt{(1-q_{l_1}^2)(1-q_{l_2}^2)}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
 \label{TDHFB_Hamiltonian_2}
@@
 	J &= \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} =  \sum_{l=1}^2 \frac{\Omega_l}{2}(1-q_l), 
-\quad\quad
-j = \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \frac{\Omega_2(1-q_2) - \Omega_1(1-q_1)}{4}.
+\nonumber \\
+j &= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \frac{\Omega_2(1-q_2) - \Omega_1(1-q_1)}{4}.
 	\label{pi}
@@
 while $j$ corresponds to the difference of occupation number
-between upper level and lower level. 
+between upper level and lower level 
 \begin{align}
@@
 $(\phi,j;\Phi,J)$ is given by
-\begin{equation}
+\begin{align}
 \mathcal{H}(\phi,j;J)
-	= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
-	- \frac{g}{4} [\Omega_l(1-q_l^2)+(1-q_l)^2] \right\}
-- \frac{g}{2}\Omega_1\Omega_2
+	=& \sum_{l=1,2} \Omega_l \epsilon_l(1- q_l) \nonumber \\
+	&- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-q_l^2)+(1-q_l)^2] \nonumber \\
+&- \frac{g}{2}\Omega_1\Omega_2
 	\sqrt{(1-q_1^2)(1-q_2^2)} \cos\phi
 \label{TDHFB_Hamiltonian_3}
-\end{equation}
+\end{align}
 with
@@
 The classical trajectory fulfills
+
+\begin{figure*}[tp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{phase.eps}
+ \end{center}
+ \caption{Energy contour plot for $\Omega_1=\Omega_2=8$ and $N=16$.
+	The lines indicate the TDHFB trajectories fulfilling
+	the EBK quantization condition of Eq. (\ref{EBK}).
+	}
+ \label{fig:phase_space}
+\end{figure*}
 
@@
 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{phase.eps}
- \end{center}
- \caption{Energy contour plot for $\Omega_1=\Omega_2=8$ and $N=16$.
-	The lines indicate the TDHFB trajectories fulfilling
-	the EBK quantization condition of Eq. (\ref{EBK}).
-	}
- \label{fig:phase_space}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the time-dependent full quantum state can be written in the path integral form
-\begin{equation}
+\begin{align}
 \ket{\psi(t)}
-	= e^{-iHt} \ket{\psi(0)}
-	= \int d\mu(Z'') \ket{Z''} \int d\mu(Z')
-	\int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)]
+	=& e^{-iHt} \ket{\psi(0)} \nonumber \\
+	=& \int d\mu(Z'') \ket{Z''} \int d\mu(Z') \nonumber \\
+	&\times \int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)]
 	e^{i\mathcal{S}[Z(\tau)]} \psi(Z') ,
 \label{path_integral_expression}
-\end{equation}
+\end{align}
 where $\psi(Z)\equiv \braket{Z|\psi(0)}$ and
@@
 connecting $Z_i=Z'_{\rm cl}(0)=Z'$ and $Z_f=Z'_{\rm cl}(t)$.
-\begin{equation}
-	\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z') \equiv \int_{0}^{t}
+\begin{align}
+	\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z') &\equiv \int_{0}^{t}
 \braket{Z_{\rm cl}(t)|
 	i\frac{\partial}{\partial t} - H
-	|Z_{\rm cl}(t)} dt
-	= \mathcal{T}[Z_{\rm cl}] - \mathcal{H}(Z',Z'^*) t 
+	|Z_{\rm cl}(t)} dt \nonumber \\
+	&= \mathcal{T}[Z_{\rm cl}] - \mathcal{H}(Z',Z'^*) t 
 	,
 	\label{S_cl}
-\end{equation}
+\end{align}
 with
-\begin{equation}
-\mathcal{T}[Z_{\rm cl}]\equiv
+\begin{align}
+\mathcal{T}[Z_{\rm cl}] &\equiv
 \int_{0}^{t} \braket{Z_{\rm cl}(t)| i\frac{\partial}{\partial t}
-	|Z_{\rm cl}(t)} dt 
-	= \int_{Z'}^{Z'_{\rm cl}(t)}
+	|Z_{\rm cl}(t)} dt \nonumber \\
+	&= \int_{Z'}^{Z'_{\rm cl}(t)}
 	\frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
   (Z_l^* dZ_l - Z_l dZ_l^*) .
-\end{equation}
+\end{align}
 In the last equation of Eq. (\ref{S_cl}),
@@
 the quantization condition ($k$: integer)
-\begin{equation}
-	\mathcal{T}_\circ[Z_{\rm cl}^{(k)}]=
-	\oint \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l^{(k)}|^2}
-	\left(Z_l^{(k)*} dZ_l^{(k)} - Z_l^{(k)} dZ_l^{(k)*}\right) = 2k\pi .
+\begin{align}
+	\mathcal{T}_\circ[Z_{\rm cl}^{(k)}]=&
+	\oint \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l^{(k)}|^2} \nonumber \\
+	&\times \left(Z_l^{(k)*} dZ_l^{(k)} - Z_l^{(k)} dZ_l^{(k)*}\right) \nonumber \\
+	=& 2k\pi .
 	\label{EBK}
-\end{equation}
-The state evolves in time as $\ket{\phi(t)}=\ket{\phi}e^{-iE_k t}$,
+\end{align}
+The state evolves in time as $\ket{\psi_k(t)}=\ket{\psi_k}e^{-iE_k t}$,
 with the energy of the $k$-th periodic trajectory,
@@
 the action-angle variables;
-\begin{equation}
-	Z(t) = \{Z_l(t);l=1,\cdots,M \} \rightarrow
+\begin{align}
+	Z(t) &= \{Z_l(t);l=1,\cdots,M \} \nonumber \\
+	&\rightarrow
 	\{E; v_1,\cdots,v_{M-1}; \theta_1(t),\cdots,\theta_M(t)\} ,
-\end{equation}
+\end{align}
 where the variables $E$ and $v$ define an invariant torus,
@@
 the $k$-th semiclassical wave function can be calculated as
-\begin{equation}
-  \ket{\psi_k} \propto \oint d\theta_1\cdots \oint d\theta_M \ 
+\begin{align}
+  \ket{\psi_k} \propto \oint d\theta_1\cdots \oint d\theta_M &\ 
 	\rho(E_k,v^{(k)},\theta)
-	\ket{E_k,v^{(k)},\theta} e^{i\mathcal{T}[E_k,v^{(k)},\theta]} .
+	\ket{E_k,v^{(k)},\theta} \nonumber \\
+	&\times e^{i\mathcal{T}[E_k,v^{(k)},\theta]} .
   \label{semi_wave_func}
-\end{equation}
+\end{align}
 Here, we omit the integration with respect to the invariant variables,
@@
 The action integral is given by
-\begin{equation}
+\begin{align}
 	\mathcal{T}_k(\Phi,\phi;J)
 %	= \Pi\Phi + \int \pi(t) \frac{d\phi}{dt} dt .
-	= J\Phi + \int^\phi_{-\pi} j' d\phi' 
+	&= J\Phi + \int^\phi_{-\pi} j' d\phi' 
 	= \frac{N}{2}\Phi + \int^t_0   %_{\mathcal{H}(\phi,\pi)=E_k}
-	j(t') \frac{d\phi}{dt'} dt' 
-\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
-\end{equation}
+	j(t') \frac{d\phi}{dt'} dt' \nonumber \\
+	&\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
+\end{align}
 where the integration $\int j d\phi$ is performed on the $k$-th
@@
 \begin{align}
-  C_m^{(E_k,J)} &= \binom{J}{m}\int_0^T dt \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
-  & \hspace{5mm} A(q,S,m) = \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
+  C_m^{(E_k,J)} =& \binom{J}{m}\int_0^T dt \nonumber \\
+ &\times \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)} \nonumber \\ 
+ &\times A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
+  A(q,S,m) &= \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
 \end{align}
@@
 the quantization condition becomes
-\begin{equation}
- \mathcal{T}_{N,E_k}(\Phi,T/2)
-	= \pm \frac{N}{2} \pi + \int_{-\pi}^\pi j d\phi
-	= 2m\pi .
-\end{equation}
+\begin{align}
+ \mathcal{T}_{N,E_k}(\Phi\pm\pi,\phi\pm 2\pi;J) &= \mathcal{T}_{N,E_k}(\Phi,\phi;J) + 2m\pi \nonumber \\
+	 \Leftrightarrow \quad\quad \pm \frac{N}{2} \pi + \int_{-\pi}^\pi j d\phi
+	&= 2m\pi .
+\end{align}
 This leads to the following:
@@
 Then, the Hamiltonian was quantized by the canonical quantization
-with the Pauli's prescription.
+with Pauli's prescription.
 In this section, we apply similar quantization method to
@@
 %However, 
-It is not straightforward to apply the Pauli's prescription
+It is not straightforward to apply Pauli's prescription
 to the present case, 
@@
 	H(\hat{\phi},\hat{j},\hat{J})
-	&= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l (1-q_l) 
-	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
+	=& \sum_{l=1,2} \Omega_l \epsilon_l (1-q_l) \nonumber \\
+	&- \frac{g}{4} \sum_{l=1,2} \Omega_l (\Omega_l(1-q_l^2)+(1-q_l)^2)
 	\nonumber \\
 	&- \frac{g}{4}\Omega_{1}\Omega_{2}
-	\left\{ \sqrt{(1-q_{1}^2)(1-q_{2}^2)}\cos{\hat{\phi}}
-	+ \cos{\hat{\phi}}\sqrt{(1-q_{1}^2)(1-q_{2}^2)} \right\} .
+	\left\{ \sqrt{(1-q_{1}^2)(1-q_{2}^2)}\cos{\hat{\phi}} \right. \nonumber \\
+	&\left. + \cos{\hat{\phi}}\sqrt{(1-q_{1}^2)(1-q_{2}^2)} \right\} .
 \label{canonical_quantized_H}
@@
 \begin{align}
-  S^+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}^+|Z}
- = \frac{1}{2}
+  S^+&(\Phi,J;\phi,j) = \braket{Z|\hat{S}^+|Z} \nonumber \\
+ &= \frac{1}{2}
 \left( \Omega_1\sqrt{1-q_1^2}e^{-i\phi/2}+\Omega_2\sqrt{1-q_2^2}e^{i\phi/2} \right) e^{i\Phi}
 	\label{Sp_mean_value} \\
-  S^-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}^-|Z}
- = \frac{1}{2}
+  S^-&(\Phi,J;\phi,j) = \braket{Z|\hat{S}^-|Z} \nonumber \\
+ &= \frac{1}{2}
 \left( \Omega_1\sqrt{1-q_1^2}e^{i\phi/2}+\Omega_2\sqrt{1-q_2^2}e^{-i\phi/2} \right) e^{-i\Phi} .
@@
 Again, we adopt a simple symmetrized ordering for the quantization:
-\begin{eqnarray}
+\begin{widetext}
+\begin{align}
 %  &S_+(\Phi,\Pi;\phi,\pi) \to S_+(\hat{\Phi},\hat{\Pi};\hat{\phi},\hat{\pi}) \nonumber \\
   S^\pm (\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
-	&=& \frac{1}{4}\left( \Omega_1\sqrt{1-q_1^2}e^{\mp i\hat{\phi}/2}
+	= \frac{1}{4}\left( \Omega_1\sqrt{1-q_1^2}e^{\mp i\hat{\phi}/2}
 +\Omega_2\sqrt{1-q_2^2}e^{\pm i\hat{\phi}/2} \right) e^{\pm i\hat{\Phi}} 
-	\nonumber \\
-&+ & \frac{1}{4}e^{\pm i\hat{\Phi}}\left( 
++ \frac{1}{4}e^{\pm i\hat{\Phi}}\left( 
 e^{\mp i\hat{\phi}/2}\Omega_1\sqrt{1-q_1^2}
 +e^{\pm i\hat{\phi}/2}\Omega_2\sqrt{1-q_2^2} \right) .
-\end{eqnarray}
+\end{align}
+\end{widetext}
 The exponential factors $e^{\pm i\Phi}$ change
@@
 the pair-addition transition strengths are calculated as
+\begin{widetext}
 \begin{align}
@@
 \end{align}
+\end{widetext}
 which automatically vanishes for $N'\neq N+2$.
@@
 \braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}$ 
-\begin{equation}
-	S^\pm(t) \approx \sum_{N} \sum_{k} \left|c_k^N\right|^2
+\begin{align}
+	S^\pm(t) &\approx \sum_{N} \sum_{k} \left|c_k^N\right|^2
 	\sum_{\Delta k}
 	\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}
-	e^{i\omega_0 \Delta k t} 
-	= \sum_{\Delta k}
+	e^{i\omega_0 \Delta k t}  \nonumber \\
+	&= \sum_{\Delta k}
 	\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}
 	e^{i\omega_0 \Delta k t}  ,
-\end{equation}
+\end{align}
 where $k_0$ is a representative index value of the superposition in 
@@
 %  \includegraphics[width=60mm,angle=-90]{N100ex_energy_wo_adiabatic.eps}
-(a)	 \includegraphics[height=0.46\textwidth,angle=-90]{N50ex_energy_wo_adiabatic.eps}
-(b)	 \includegraphics[height=0.46\textwidth,angle=-90]{N100ex_energy_wo_adiabatic.eps}
+(a)	 \includegraphics[height=0.44\textwidth,angle=-90]{N50ex_energy_wo_adiabatic.eps}
+\\
+(b)	 \includegraphics[height=0.44\textwidth,angle=-90]{N100ex_energy_wo_adiabatic.eps}
  \end{center}
@@
 We find the SPA is even more precise than the CQ.
-\begin{figure}[t]
+\begin{figure*}[t]
  \begin{minipage}{1\hsize}
@@
   \includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
- \end{center}
- \end{minipage}
- \begin{minipage}{1\hsize}
- \begin{center}
-%  \includegraphics[width=67mm,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
-%  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
-
   \includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
@@
  \end{minipage}
+% \begin{minipage}{1\hsize}
+% \begin{center}
+%  \includegraphics[width=67mm,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
+%  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
+% \end{center}
+% \end{minipage}
  \caption{
@@
  \label{fig:N50_occ}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
  \begin{minipage}{0.3\hsize}
@@
  \label{fig:N50Pad}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure*}[t]
  \begin{minipage}{0.3\hsize}
@@
  \label{fig:N100Pad}
-\end{figure}
+\end{figure*}
 
@@
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{N8ex_energy_wo_adiabatic.eps}
+  \includegraphics[height=0.46\textwidth,angle=-90]{N8ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-   \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
-   \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
+   \includegraphics[height=0.9\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
+   \includegraphics[height=0.9\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
  \label{fig:N8Pad}
-\end{figure}
-
-\begin{figure}[t]
+\end{figure*}
+
+\begin{figure}[htb]
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{N16ex_energy_wo_adiabatic.eps}
+  \includegraphics[height=0.46\textwidth,,angle=-90]{N16ex_energy_wo_adiabatic.eps}
  \end{center}
@@
  \begin{center}
-   \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
-   \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
+   \includegraphics[height=0.9\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
+   \includegraphics[height=0.9\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
  \end{center}
@@
 After the phase transition, the occupation probability of $\ket{0_4^+}$ is also well reproduced in semiclassical approach.
-
-Singular behaviors near the transition points can be also observed in
-the pair-addition transition strengths ($N=14\rightarrow 16$) shown
-in Fig.~\ref{fig:N16Pad}. 
-At $x=1$, the intraband $B(P_{\rm ad}; 0\rightarrow 0)$ shows a kink
-in the SPA,
-and $B(P_{\rm ad}; 1\rightarrow 1)$ shows another kink at $x\approx 1.8$.
-These exactly correspond to the transition points from open to closed
-trajectories.
-Nevertheless, the overall behaviors are well reproduced and
-the values at the weak and strong pairing limit are reasonably reproduced
-in the SPA.
-The CQ calculation also shows smoothed kink-like behaviors near the
-transition points.
-However, it underestimates the intraband $B(P_{\rm ad}; k\rightarrow k)$.
-The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
-because $S^+(t)$ is calculated for an $N=14$ system.
-Both intraband and interband transitions in the FD calculations
-reasonably agree with the exact results at $x\gtrsim 1.8$.
-The $k=1$ state is not properly reproduced at $x\lesssim 1.8$
-with the open trajectory.
-
-For the closed-shell configurations,
-the SPA and the FD methods provide reasonable description for the
-pair-transfer transition strengths.
-
-%Between pairing rotational transition and pairing vibrational transition, we can find the transition strength are compareable in $x<1$, and pairing rotational transition are dominant in $x>1$.
-The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system.
-In canonical quantization, even though the tendency of $\ket{0_1^+}\to\ket{0_1^+}$ are reproduced, all transition strengths are failed to reproduce quantitatively.
-In semiclassical approach, the strengths have disagreement around phase transition region, but are recovering toward no pairing and strong pairing limit.
-\par
-%In closed shell system, the phase transition is semiclassical approach is more quantitative than canonical approach except phase transition region.
-\begin{figure}[htbp]
+\begin{figure*}[t]
  \begin{minipage}{0.3\hsize}
@@
  \label{fig:N16Pad}
-\end{figure}
+\end{figure*}
+
+Singular behaviors near the transition points can be also observed in
+the pair-addition transition strengths ($N=14\rightarrow 16$) shown
+in Fig.~\ref{fig:N16Pad}. 
+At $x=1$, the intraband $B(P_{\rm ad}; 0\rightarrow 0)$ shows a kink
+in the SPA,
+and $B(P_{\rm ad}; 1\rightarrow 1)$ shows another kink at $x\approx 1.8$.
+These exactly correspond to the transition points from open to closed
+trajectories.
+Nevertheless, the overall behaviors are well reproduced and
+the values at the weak and strong pairing limit are reasonably reproduced
+in the SPA.
+The CQ calculation also shows smoothed kink-like behaviors near the
+transition points.
+However, it underestimates the intraband $B(P_{\rm ad}; k\rightarrow k)$.
+The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
+because $S^+(t)$ is calculated for an $N=14$ system.
+Both intraband and interband transitions in the FD calculations
+reasonably agree with the exact results at $x\gtrsim 1.8$.
+The $k=1$ state is not properly reproduced at $x\lesssim 1.8$
+with the open trajectory.
+
+For the closed-shell configurations,
+the SPA and the FD methods provide reasonable description for the
+pair-transfer transition strengths.
+
+%Between pairing rotational transition and pairing vibrational transition, we can find the transition strength are compareable in $x<1$, and pairing rotational transition are dominant in $x>1$.
+The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system.
+In canonical quantization, even though the tendency of $\ket{0_1^+}\to\ket{0_1^+}$ are reproduced, all transition strengths are failed to reproduce quantitatively.
+In semiclassical approach, the strengths have disagreement around phase transition region, but are recovering toward no pairing and strong pairing limit.
+\par
+%In closed shell system, the phase transition is semiclassical approach is more quantitative than canonical approach except phase transition region.
+
 %In realistic type, semiclassical approach is much better than canonical quantization in every physical values, especially in two-particle transition.
@@
  \begin{center}
-(a) \includegraphics[height=0.46\textwidth,angle=-90]{N8p_E.eps}
-(b) \includegraphics[height=0.46\textwidth,angle=-90]{N16p_E.eps}
+(a) \includegraphics[height=0.44\textwidth,angle=-90]{N8p_E.eps}
+\\
+(b) \includegraphics[height=0.44\textwidth,angle=-90]{N16p_E.eps}
  \end{center}
@@
 then, quantize it by $\hat{\phi}=i\partial/\partial j$ with
-the ordering given by the Pauli's prescription.
+the ordering given by Pauli's prescription.
 The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
@@
  \begin{center}
-(a) \includegraphics[height=0.46\textwidth,angle=-90]{N50Xeq2p4gap_E.eps}
+(a) \includegraphics[height=0.4\textwidth,angle=-90]{N50Xeq2p4gap_E.eps}
+\\
 % \end{center}
@@
 % \begin{center}
-(b) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2p4gap_E.eps}
+(b) \includegraphics[height=0.4\textwidth,angle=-90]{N16Xeq2p4gap_E.eps}
  \end{center}
@@
 \appendix
+\begin{widetext}
 \section{Derivation of semiclassical wave function}
@@
 The explicit form of coherent state is
+
 \begin{align}
@@
 we reach Eq. (\ref{semi_wave_func1}).
+\end{widetext} 
 %\begin{align}

### 2018-08-31 paper2/draft1-1.tex
new directory

\documentclass[%
%reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
showpacs,
%preprintnumbers,
nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
prc,
%paper,
%rmp,
%prstab,
%prstper,
twocolumn,
floatfix ]%
{revtex4-1}

%\usepackage{acrofont}%NOTE: Comment out this line for the release version!
\newcommand{\revtex}{REV\TeX\ }
\newcommand{\classoption}[1]{\texttt{#1}}
\newcommand{\macro}[1]{\texttt{\textbackslash#1}}
\newcommand{\m}[1]{\macro{#1}}
\newcommand{\env}[1]{\texttt{#1}}
\setlength{\textheight}{9.5in}

\usepackage{comment}
\usepackage[dvips]{graphicx}
%\usepackage{amsmath,amssymb}
%\usepackage{mathrsfs}
%\usepackage{txfonts}
\usepackage{braket}
%\usepackage{latexsym}
%\usepackage{ascmac}
%\usepackage{fancybox}
%\usepackage{type1cm}
\usepackage{cases}
\usepackage{caption}
%\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}

  \makeatletter
    \renewcommand{\theequation}{%
    \thesection.\arabic{equation}}
    \@addtoreset{equation}{section}
  \makeatother

\begin{document}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\title{Low-lying collective excited states in non-integrable system based on stationary phase approximation to the path integral}%

\author{Fang Ni}
 \affiliation{Faculty of Pure and Applied Sciences,
              University of Tsukuba, Tsukuba 305-8571, Japan}
\author{Takashi Nakatsukasa}
 \affiliation{Center for Computational Sciences,
              University of Tsukuba, Tsukuba 305-8577, Japan}
 \affiliation{Faculty of Pure and Applied Sciences,
              University of Tsukuba, Tsukuba 305-8571, Japan}
 \affiliation{iTHES Research Group, RIKEN, Wako 351-0198, Japan}

\begin{abstract}
\begin{description}
\item[Background] This part would describe the
context needed to understand what the paper
is about.
\item[Purpose] This part would state the purpose
of the present paper.
\item[Method] This part describe the methods
used in the paper.
\item[Results] This part would summarize the
results.
\item[Conclusions] This part would state the
conclusions of the paper.
\end{description}
\end{abstract}

\maketitle

\section{Introduction}

\section{Theoretical framework}

\subsection{One-dimensional adiabatic self-consistent collective coordinate method}
\label{ASCC}

We review the one-dimensional adiabatic self-consistent collective coordinate method (ASCC) briefly. The classical Hamilton's equation which is identical to the TDHFB equation is described by canonical variables $\{\xi^{\alpha},\pi_{\alpha}\}$. If we assume the collective motion is slow motion, it allows us to expand momenta $\pi$ up to second order. The multi-dimensional Hamiltonian is
\begin{align}
  \mathcal{H} &= V(\xi) + \frac{1}{2}B^{\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}
\end{align}
with potential $V(\xi)$ and reciprocal mass parameter $B^{\alpha\beta}(\xi)$ defined by
\begin{align}
  V(\xi) &= \mathcal{H}(\xi,\pi=0) \\
  B^{\alpha\beta}(\xi) &= \left. \frac{\partial^2\mathcal{H}(\xi,\pi)}{\partial\pi_{\alpha}\partial\pi_{\beta}} \right|_{\pi=0}.
\end{align}
 If there is a one-dimensional collective motion which is decoupled from other intrinsic motions, the collective motion can be described by a set of canonical variable $\{q,p\}$, the one dimensional collective Hamiltonian is
\begin{align}
  \mathcal{H}_{coll} &= \bar{V}(q) + \frac{1}{2}\bar{B}^{-1}(q)p^2.
  \label{coll}
\end{align}
To obtain the collective Hamiltonian, we need to consider extended adiabatic transformation
\begin{align}
  q = q^1 &= f^1(\xi) + \frac{1}{2}f^{(1)1\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}  \label{point}\\
 \xi^{\alpha} &= g^{\alpha}(q) + \frac{1}{2}g^{(1)\alpha 1 1}(\xi)p_{1}p_{1}
\end{align}
and
\begin{align}
  p_1 &= g_{,1}^{\alpha}\pi_{\alpha} \\
 \pi_{\alpha} &= f^1_{,\alpha}p_1 ,
  \label{momenta}
\end{align}
where the index $1$ indicates the collective degree of freedom, and the comma indicates the partial derivative $(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
With these relations, collective potential $\bar{V}(q)$ and collective mass parameter $\bar{B}(q)$ can be transformed by
\begin{align}
  \bar{V}(q) &= V(\xi) \\
  \bar{B}^{-1}(q) &= f^1_{,\alpha}B^{\alpha\beta}(\xi)f^1_{,\beta} ,
  \label{coll_mass}
\end{align}

Before showing the ASCC basic equations, we consider the constants of motion in TDHFB dynamics. Since nuclei is self-bound systems without external potential, the ground state obtained from mean-field theory violates the symmetry (e.g. deformation, pairing). In such system, the constants of motion corresponding the Nambu-Goldstone (NG) mode emerges in TDHFB dynamics. Therefore, we are mostly interested in the systems with collective motion separated from NG mode.\par
We know that the most of conserved quantities, such as total angular momentum $J$ and total particle number $N$, are not only expressed by one-body Hermitian operators, but also has real matrix elements in the quasi-particle basis. Such classical variable $\mathcal{P}$ corresponding to the conserved quantity can be expanded as
\begin{align}
  \mathcal{P}(\xi,\pi) = f^I(\xi) + \frac{1}{2}f^{(1)I\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta} . \label{P}
\end{align}
The index $I$ indicates the degree of freedom for NG mode. Since the conserved quantity must fulfill $\{\mathcal{P},\mathcal{H}\}_{PB}=0$, it leads
\begin{align}
  f^{I}_{,\alpha}B^{\alpha\beta} - f^{(1)I\alpha\beta}V_{,\alpha} = 0.
  \label{P_PB}
\end{align}

Including the NG mode, $f^1(\xi)$ and $g^{\alpha}(q)$ are obtained by solving ASCC basic equations 
\begin{align}
  &\delta H_M(\xi,\pi) = 0 \label{mfHFB} \\ 
  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
  \label{mfQRPA}
\end{align}
The first equation (\ref{mfHFB}) is called moving-frame HFB equation. The moving-frame Hamiltonian $\mathcal{H}_M$ with constraints on collective coordinate and constant of motion is
\begin{align}
  \mathcal{H}_M(\xi,\pi) &= \mathcal{H}(\xi,\pi) -\lambda_1 q^1(\xi,\pi) - \lambda_I \mathcal{P}(\xi,\pi) .
\end{align}
The second equation (\ref{mfQRPA}) is called moving-frame QRPA equation. $\tilde{B}^{\alpha\beta}$ is the modified mass parameter
\begin{align}
  \tilde{B}^{\alpha\beta}(\xi) &= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
&= B^{\alpha\beta}(\xi) - \lambda_I f^{(1)I\alpha\beta}(\xi) - \lambda_1 f^{(1)1\alpha\beta}(\xi) \label{tildeB}.
\end{align} 
and the covariant derivative $V_{;\gamma\alpha}$ is defined by
\begin{align}
 V_{;\alpha\beta} = V_{,\alpha\beta} - \Gamma^{\gamma}_{\alpha\beta}V_{,\gamma} , \label{covariant}
\end{align}
where the affine connection is $\Gamma^{\alpha}_{\beta\gamma}=\frac{1}{2}B^{\alpha\delta}(B_{\delta\beta,\gamma}+B_{\delta\gamma,\beta}-B_{\beta\gamma,\delta})$. If we assume that the collective coordinate $q$ is geodesic, $\tilde{B}^{\beta\gamma}V_{;\gamma\alpha}$ can be simplified after several steps
 \begin{align}
\tilde{B}^{\alpha\gamma}V_{;\gamma\beta} = \tilde{B}^{\alpha\gamma}(V_{,\gamma\beta}-\lambda_If^I_{,\gamma\beta}) + \frac{1}{2}\tilde{B}^{\alpha\gamma}_{,\beta}V_{,\gamma} 
\label{M}.
\end{align}

We discuss the practical solution to derive the one-dimensional collective coordinate. We neglect $f^{(1)1\alpha\beta}(\xi)$ because it is supposed to be negligibly small in the previous study. On the other hand, from (\ref{P_PB}) and (\ref{mfQRPA}), $f^{(1)I\alpha\beta}(\xi)$ is necessary information to promise $\tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^I_{,\beta}=0$, which means zero mode. In most of case, we know the explicit form of $\mathcal{P}(\xi,\pi)$. The procedures to obtain the collective path are (see Figure \ref{scc}): 
\begin{enumerate}
\item Find the energy minimum point in energy surface by solving (\ref{mfHFB}) (normal HFB equation). We usually set $q^1=0$ at the energy minimum point.
\item Using (\ref{M}), diagonalize (\ref{mfQRPA}) and choose the lowest mode basically\footnote{
When eigenvalues cross on the collective path, the choice of adiabatic path or diabatic path is a critical problem}. 
\item The right eigenvector $g^{\alpha}_{,1}$ tell us the direction which system moves in energy surface. Use the relation $d\xi^{\alpha}=g^{\alpha}_{,1}dq^1$ to decide the neighborhood point $q^1\to q^1+dq^1$ in the collective path. 
\item Find the non-equilibrium energy minimum point by solving (\ref{mfHFB}) at the neighborhood point, and obtain the chemical potential $\lambda_I(q)$. 
\item Iterate (2)$\sim$(4) under the same direction in energy surface. 
\item Do (2)$\sim$(5) for the opposite direction of the collective path in energy surface. 
\end{enumerate}
The scale of the collective coordinate is not unique because of the uncertainty of the eigenvectors in (\ref{mfQRPA}). To unify the scale, the simplest procedure is to keep the collective mass parameter $\bar{B}^{-1}(q)=1$ by renormalizing eigenvectors in (\ref{coll_mass}).

\subsection{Stationary-phase approximation to the path integral}

In integrable system, we can apply the stationary phase approximation to the path integral (SPA) to obtain collective excited states. The concept of SPA is introduced in the previous study. Because the one-dimensional collective path extracted from TDHFB degrees of freedom is integrable system, SPA is supposed to be available for non-integrable system via ASCC. \par
Based on SPA, the $k$-th excited state $\ket{\psi_k}$ can be constructed by a periodic TDHFB trajectory
\begin{equation}
	\ket{\psi_k} = \oint d\mu(Z^{(k)}) \ket{Z^{(k)}}
	e^{i\mathcal{T}[Z^{(k)}]/\hbar} .
	\label{SPA}
\end{equation}
The integration indicates we integrate a periodic TDHFB trajecotry for one period in TDHFB phase space. The invariant measure $d\mu(Z)$ is defined by the unity condition $\int d\mu(Z) \ket{Z}\bra{Z} = 1$. The action integral $\mathcal{T}$ is defined by
\begin{align}
\mathcal{T}[Z] &\equiv
\int_{0}^{t} \braket{Z(t')| i\hbar\frac{\partial}{\partial t'}
	|Z(t')} dt' .
\label{tau}
\end{align}

We try to combine SPA with ASCC. The key point is to find the correspondence between TDHFB phase space and collective subspace in a TDHFB trajectory (See Fig. \ref{correspondence}). We consider the time-dependent state vector $\ket{Z(t)}$ is in a collective subspace. With pairing correlation, $\ket{Z(t)}$ can be expressed as
\begin{align}
 \ket{Z(t)} &= \ket{\Phi,J;q,p} = e^{-i\Phi \hat{J}} \ket{J;q,p} ,
 \label{GCS}
\end{align}
where $\Phi$ is the total gauge angle and $J=N/2$ is the conjugate momentum corresponding total particle number. The second equal sign indicates an intrinsic state $\ket{J;q,p}$ rotates in the gauge space. Since $[H,J]=0$, the classical Hamiltonian 
becomes
\begin{align}
 \mathcal{H} &= \braket{\Phi,J;q,p|H|\Phi,J;q,p} \nonumber \\
 &= \braket{J;q,p|H|J;q,p} \equiv \mathcal{H}_J(q,p)
\end{align}  
has no dependence of $\Phi$. Therefore, the classical Hamiltonian is the function of $(q,p)$ in a fixed particle number system, and correspond to (\ref{coll}). From ASCC, we can obtain the static state vector at each point of $q$, namely $\ket{J;q,p=0}$. To construct $\ket{J;q,p}$, we use (\ref{momenta}) at $(q,p)$ which we want to know in the collective phase space. Usually, we are interested in the points $(q^{(k)},p^{(k)})$ at the $k$-th TDHFB trajectory. Such $k$-th TDHFB trajectory is obtained from EBK quantization condition ($k$: integer)
\begin{align}
	\mathcal{T}_\circ[Z^{(k)}]=&
	\oint \braket{Z^{(k)}(t')| i\hbar\frac{\partial}{\partial t'} |Z^{(k)}(t')} dt' \nonumber \\
	=& \oint p^{(k)} dq^{(k)} = 2k\pi .
	\label{EBK}
\end{align}

\begin{figure}[htbp]
 \begin{center}
    \includegraphics[width=80mm, bb=0 0 550 180]{SPA.png}
 \end{center}
  \caption{For a TDHFB trajectory, the correspondence between TDHFB phase space and collective subspace.}
  \label{correspondence}
\end{figure}

The procedures to obtain excited states from SPA via ASCC are:
\begin{enumerate}
\item Obtain the one-dimensional collective coordinate from ASCC.
\item Using collective Hamiltonian, obtain $k$-th excitation energy and TDHFB trajectory under EBK quantization condition (\ref{EBK}).
\item For $k$-th TDHFB trajectory, construct the state vector $\ket{J;q,p}$ by using (\ref{momenta}).
\item Calculate action integral (\ref{tau}) in $k$-th TDHFB trajectory.
\item Using (\ref{SPA}), obtain $k$-th excited state.
\end{enumerate}

\section{Application in pairing model}
We study the low-lying excited $0^+$ states in multi-level pairing model by applying SPA via ASCC. 
The Hamiltonian of the pairing model is given in terms of
single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{align}
	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- \nonumber \\
    &= \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
\end{align}
where we use the SU(2) quasi-spin operators,
$\boldsymbol{S}=\sum_l \boldsymbol{S}_l$, with
\begin{eqnarray}
        S_l^0 &=& \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l) ,\\
        S_l^{+} &=& \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
degeneracy ($\Omega_l=j_l+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_l-1/2$.
The occupation number of each level $l$ is given by
$
	n_l = \sum_m a^{\dag}_{lm}a_{lm} = 2S_l^0+\Omega_l ,
$.
The quasi-spin operators satisfy the commutation relations
\begin{equation}
  [S_l^0,S_{l'}^{\pm}] = \pm\delta_{ll'}S_{l}^{\pm},
	\quad [S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0} .
\end{equation}
The magnitude of quasi-spin for each level is
$S_l=\frac{1}{2}(\Omega_l-\nu_l)$, where $\nu_l$ is the seniority
quantum number, namely the number of unpaired particle at each level $l$.
In the present study, we only consider seniority zero states with
$\nu=\sum_l \nu_l=0$.
The residual two-body interaction only consists of monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain exact solutions either by solving Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasi-spin symmetry.

\subsection{Classical form of TDHFB Hamiltonian}
The coherent state for the seniority $\nu=0$ states
($S_l=\Omega_l/2$) is constructed as
\begin{equation}
	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-\Omega_l/2}
	\exp [Z_l(t) S_l^{+}] \ket{0}
 \label{coherent}
\end{equation}
where $\ket{0}$ is the vacuum (zero particle) state,
$Z_l(t)$ are time-dependent complex variables which describe
motion of the system. 
In the SU(2) quasi-spin representation,
$\ket{0}=\prod_l \ket{S_l,-S_l}$.
The coherent state $\ket{Z(t)}$ is a superposition of
states with different particle numbers
without unpaired particles.
%If $Z_l$ are all real,
In the present pairing model,
the coherent state is the same as the time-dependent BCS wave function
with $Z_l(t)=v_l(t)/u_l(t)$,
where $(u_l(t),v_l(t))$ are the time-dependent BCS $u,v$ factors.

The TDHFB equation can be derived from the time-dependent variational
principle (we set $\hbar=1$),
\begin{equation}
	\delta \mathcal{S} = 0,
	\quad
%  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
	\mathcal{S}\equiv \int \mathcal{L}(t) dt =
	\int \braket{Z(t)|i\frac{\partial}{\partial t}-H|Z(t)}dt.
  \label{TDHFB}
\end{equation}
After transformation of the complex variables $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$  ($0\leq\theta\leq\pi$) and several steps of the derivation, the Lagrangian $\mathcal{L}$ and the expectation value of Hamiltonian become
\begin{align}
\mathcal{L}(t) = \sum_l \frac{\Omega_l}{2}
	(1&-\cos{\theta}_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
	\mathcal{H}(Z,Z^*) \equiv \braket{Z|H|Z}& \nonumber \\
  = \sum_l \epsilon_l\Omega_l(1- \cos{\theta}_l)& - \frac{g}{4}\sum_l \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
\label{TDHFB_Hamiltonian_2}
\end{align}
Here, we choose $\chi_l$ as canonical coordinates. Their conjugate momenta
are given by
\begin{align}
  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=\frac{\Omega_l}{2}
	(1-\cos{\theta}_l) .
\end{align}
$\chi_l$ represent a kind of gauge angle of each level,
and $j_l$ are related to the occupation number of each level, $2j_l=n_l$. Therefore, the TDHFB Hamiltonian can be represented by canonical variables $\mathcal{H}(Z,Z^*) = \mathcal{H}(\{\chi_l\},\{j_l\})$, and the TDHFB equation is equivalent to the Hamilton's equation
\begin{equation}
	\dot{\chi_l} = \frac{\partial\mathcal{H}}{\partial j_l}, \quad
	\dot{j_l} = -\frac{\partial\mathcal{H}}{\partial \chi_l} .
\end{equation}
.

\subsection{Application into ASCC}
We construct 1D collective subspace from ASCC theory. Because the first order with respect to $\chi_l$ is zero in TDHFB Hamiltonian, we assume $j_l$ as coordinates and $\chi_l$ as conjugate momenta. The canonical variables are $(j_l,-\chi_l)$ and fulfill $\{j_l,-\chi_l'\}_{PB}=\delta_{ll'}$. We expand the classical Hamiltonian up to second order with respect to $\chi_l$. 
The classical Hamiltonian becomes
\begin{align}
  \mathcal{H}(\{\chi_l\},\{\pi_l\}) \approx& V(j) + \frac{1}{2}B^{\alpha\beta}(j)\chi_{\alpha}\chi_{\beta},
\end{align}
where potential $V(j)$ and reciprocal mass parameter $B^{\alpha\beta}(j)$ are defined as
\begin{align}
  V(j) =& \mathcal{H}(\chi=0,j) \nonumber \\
	=& \sum_l 2\epsilon_lj_l - g\sum_l \left( \Omega_lj_l - j_l^2 +\frac{j_l^2}{\Omega_l} \right) \nonumber \\
  &- g\sum_{l_1\ne l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-j_{l_1})(\Omega_{l_2}-j_{l_2})} 	
\end{align}
\begin{align}
  B^{\alpha\beta}(j) =& \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \nonumber \\
	=& \left\{
	\begin{array}{c}
	2g\sum_{l\ne \alpha} \sqrt{j_{l}j_{\alpha}(\Omega_{l}-j_{l})(\Omega_{\alpha}-j_{\alpha})} \hspace{2em} (\alpha=\beta) \\
	-2g\sqrt{j_{\alpha}j_{\beta}(\Omega_{\alpha}-j_{\alpha})(\Omega_{\beta}-j_{\beta})} \hspace{2em} (\alpha\ne\beta)
	\end{array}
	\right. .
 \label{mass}
\end{align}
Using the TDHFB Hamiltonian, we can apply ASCC explained in Sec. \ref{ASCC} by replacing $\xi\to j$ and $\pi\to-\chi$.

We consider the treatment for the constant of motion in pairing model. In the TDHFB Hamiltonian, there is no dependence about the total gauge angle
\begin{align}
  \Phi = \frac{1}{L}\sum_l \chi_l.
  \label{total_gauge}
\end{align}
It indicates the conjugate momentum 
\begin{align}
  J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}}=\sum_l j_l = \frac{N}{2}
  \label{J}
\end{align}
is conserved quantity. From this equation, we can find $J$ is not dependent of $\chi$, which means $f^{(1)I\alpha\beta}$ in (\ref{P}) is zero. Therefore, $B^{\beta\gamma}V_{;\gamma\alpha}f^I_{,\beta}=0$ is promised exactly. Also, the second derivative of $J$ with respect to $j$ vanishes, which indicates $f^{I}_{,\gamma\beta}$ in (\ref{M}) is zero. It indicates the chemical potential $\lambda_I(q)$ is not necessary information to calculate the matrix element in moving-frame QRPA equation.

With the properties of the constant of motion, we discuss the practical solution of ASCC in pairing model. If we ignore the higher order term $f^{(1)1\alpha\beta}$, we can practice local harmonic equation (LHE)
\begin{align}
  B^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
  B^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1},
  \label{LHE}
\end{align}
which simplifies the moving-frame QRPA equation (\ref{mfQRPA}) by replacing $\tilde{B}^{\beta\gamma}$ into $B^{\beta\gamma}$. Under (\ref{LHE}), the eigenvalue of spurious mode corresponding pairing rotation is exact zero. Moreover, we can skip the Step. 4 in Sec. \ref{ASCC}. After obtain the energy minimum point by solving normal HFB equation, we only use (\ref{LHE}) one after another to construct the one-dimensional collective Hamiltonian without moving-frame HFB equation (\ref{mfHFB}). It arises the uncertainty of the total gauge angle $\Phi$ during obtaining the collective path. To arrange the eigenvectors with $\Phi(q)=-\frac{1}{L} p_1\sum_l f^1_{,l}=0$, we correct the eigenvectors by
\begin{align}
  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_l f^1_{,l} 
  \label{f}
\end{align}
after solving (\ref{LHE}) at each point of $q$.

\subsection{Application into SPA}
We derive the explicit form of excited states in (\ref{SPA}). From (\ref{GCS}) and (\ref{J}), the state vector $\ket{\Phi,J;q,p}$ becomes
\begin{align}
  \ket{\Phi,J;q,p} &= \sum_{\{j_l\}} e^{-i\Phi \sum_l j_l} \ket{J;q,p} .
\end{align}
Here, $\ket{J;q,p}$ can be expanded in SU(2) quasispin basis
\begin{align}
  \ket{J;q,p} &= \sum_{\{j_l\}} A_{j_l}(q,p) \ket{\cdots;S_l,-S_l+k_l,\cdots}, 
\end{align}
where 
\begin{align}
  A_{j_l}(q,p) =& \prod_l \left(\frac{1-\cos{\theta}_l}{2}\right)^{j_l/2}\left(\frac{1+\cos{\theta}_l}{2}\right)^{(\Omega_l-j_l)/2}
  \nonumber \\
  &\times\sqrt{\frac{(\Omega_l)!}{j_l!(\Omega_l-j_l)!}} e^{-ij_l\chi_l} 
\end{align}
is in fixed gauge angle ($\Phi=0$).

Due to $J$ is conserved quantity, the action integral can be divided into two terms
\begin{align}
  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
\end{align}
where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
\begin{align}
  \mathcal{T}_{\rm intr}(t) &= \int \braket{J;q,p|i\frac{\partial}{\partial t}|J;q,p} dt
	 \nonumber \\
	&= \int \sum_l j_l d\chi_l .
	\label{tau}
\end{align}
The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.
In SU(2) representation, the invariant measure is
\begin{align}
  d\mu(Z) &= \prod_l \frac{\Omega_l+1}{\pi} (1+|Z_l|^2)^{-2} d{\rm Re}Z d{\rm Im}Z \nonumber \\
 =& \prod_l \frac{\Omega_l+1}{4\pi} d \cos{\theta_l} d\chi_l \nonumber \\
 =& \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} d\chi_l dj_l \nonumber \\
 =& \left[ \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} \right] d\Phi dJ dqdp \nonumber \\
 &\times dQ_1\cdots dQ_{l-2}dP_1\cdots dP_{l-2}
% d\Phi dJ dq dp = d\Phi dJ dE dt 
\end{align}
where $(Q_i,P_i)$ are the other canonical variables decoupled from the collective coordinates. From the third line to the forth line, we used that Jacobian equals one in canonical transformation. The part of the invariant measure which contributes to the excited states is
\begin{align}
d\mu(\Phi,J;q,p) \propto d\Phi dJ dqdp = d\Phi dJ dE dt. 
\end{align}
Under EBK quantization condition (\ref{EBK}),
the $k$-th excited state becomes
\begin{align}
 \ket{\tilde{\phi}_k} \propto& \oint d\Phi \oint dt \ket{\Phi,J;q,p} e^{i\mathcal{T}(\Phi,J;q,p)}
 \nonumber \\
 =& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \nonumber \\
 &\times \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q,p) \ket{\cdots;S_l,-S_l+j_l,\cdots} \nonumber \\
 \equiv& \sum_{\{j_l\}\in (\sum_{j_l}=J)} C_{j_l} \ket{\cdots;S_l,-S_l+j_l,\cdots}
\end{align}
where
\begin{align}
  C_{j_l} = \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q(t),p(t)).
  \label{coef}
\end{align}

\section{Results}
\subsection{Confirmation in one-dimensional TDHFB system}

\subsection{Three-level system}

\subsection{Realistic single-particle level system}

\begin{table}
\caption{\label{tab:fonts}\LaTeXe\ and AMS-\LaTeX\ font summary.}
\begin{ruledtabular}
\begin{tabular}{lp{2in}}
\m{textit} & Italics. Replaces \m{it}\\
\m{textbf} & Bold face. Replaces \m{bf}\\
\m{textrm} & Roman. Replaces \m{rm}\\
\m{textsl} & Slanted. Replaces \m{sl}\\
\m{textsc} & Small caps. Replaces \m{sc}\\
\m{textsf} & Sans serif. Replaces \m{sf}\\
\m{texttt} & Typewriter. Replaces \m{tt}\\
\m{textmd} & Medium series\\
\m{textnormal} & Normal\\
\m{textup} & Upright\\
\m{mathbf} & Bold face\\
\m{mathcal} & Replaces \m{cal}\\
\m{mathit} & Italics\\
\m{mathnormal} & Replaces \m{mit}\\
\m{mathsf} & Sans serif\\
\m{mathtt} & Typewriter\\
\m{mathfrak} & Fraktur: Requires \classoption{amsfonts} or \classoption{amssymb} class option\\
\m{mathbb} & Bold blackboard: Requires \classoption{amsfonts} or \classoption{amssymb} class option\\
\m{bm} & Bold Greek and other math symbols: Requires
\verb+\usepackage{bm}+ and may require the \classoption{amsfonts} class
option
\end{tabular}
\end{ruledtabular}
\end{table}

\section{Conclusion}

\end{document}

### 2018-09-11 paper2/draft1-1.tex
draft1-1

@@
 \section{Results}
+We apply ASCC + SPA to study the multi-level system in pairing model.
+The TDHFB degrees of freedom equals the number of single particle levels, including the constant of motion (pairing rotation).
+First, we confirm the dynamics is identical between ASCC + SPA and adiabatic TDHFB in two-level (one-dimensional TDHFB) system.
+Next, we discuss the dynamics in non-integrable (more than three-level) system.
+
 \subsection{Confirmation in one-dimensional TDHFB system}
+In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
+\begin{align}
+\mathcal{H} 
+  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
+ &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
+- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
+\end{align}
+If we define the canonical coordinate $\phi=\chi_2-\chi_1$, it attributes to one-dimensional system.
+The conjugate momentum is $j= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \{\Omega_2(1-\cos{\theta}_2) - \Omega_1(1-\cos{\theta}_1)\}/4$.
+The adiabatic TDHFB (ATDHFB) means that we expand the Hamiltonian with respect to $\chi$ up to second order
+\begin{align}
+  \mathcal{H}(\phi,j) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
+\end{align}
+where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
+Because the time-dependent pairing vibrational mode is explicitly decoupled from pairing rotational mode, ASCC must be identical with ATDHFB.
+Furthermore, the excited states from SPA are also identical from both approaches.
+
+We study the system with equal degeneracy $\Omega_1=\Omega_2=50$, $g/(\epsilon_2-\epsilon_1)=0.02$, and $N=100$.
+In ASCC calculation, we set the mesh size of collective coordinate $dq=0.02$.
+We compared the excited $0^+$ states from one-dimensional ATDHFB and ASCC with each other.
+Fig.
+\ref{fig:N100_traj} and Fig.
+\ref{fig:N100_tau} show the TDHFB trajectory in phase space and  action integral $\mathcal{T}$ as a function of time $t$, corresponding to $\ket{0_2^+}$, respectively.
+All of the mesh points obtained from ASCC are on the trajectory obtained from ATDHFB.
+The obtained excited $0^+$ states from SPA are shown in Fig.
+\ref{fig:N100_occ}.
+The occupation probability can be decomposed into $2n$-particle-$2n$-hole components.
+We can find the results from ATDHFB and ASCC are identical for all states.
+Therefore, the theoretical framework of ASCC + SPA has no problem.
+
+\begin{figure}[thb]
+ \begin{center}
+   \includegraphics[height=0.5\textwidth,angle=-90]{N100Xeq2trajectory.eps}
+ \end{center}
+\caption{aa}
+\label{fig:N100_traj}
+\end{figure}
+\begin{figure}[thb]
+ \begin{center}
+   \includegraphics[height=0.5\textwidth,angle=-90]{N100Xeq2tau.eps}
+ \end{center}
+\caption{aa}
+\label{fig:N100_tau}
+\end{figure}
+\begin{figure}[thb]
+ \begin{center}
+   \includegraphics[height=0.5\textwidth,angle=-90]{N100Xeq2occ.eps}
+ \end{center}
+	\caption{Occupation probability in excited $0^+$ states
+as a function of $j$ for $\Omega_1=\Omega_2=50$, $N=100$, and $x=2$ system.
+The two vertical bars at each $j$ from the left to the right represent
+the squared components of the wave functions
+from ATDHFB+SPA and ASCC+SPA calculations, respectively.
+The left end of the horizontal axis at $j=j_{\rm min}$
+corresponds to a component with $(n_1,n_2)=(N,0)$.
+The next at $j=j_{\rm min}+1$ corresponds to the one with
+$(n_1,n_2)=(N-2,2)$, and so on.
+}
+ \label{fig:N100_occ}
+\end{figure}
 
 \subsection{Three-level system}
+The simplest non-integrable system is three-level system.
+We have one trivial motion and two time-dependent degrees of freedom.
+We study the system with $\Omega_1=\Omega_2=\Omega_3=8$, $\epsilon_1=-1$, $\epsilon_2=0$, $\epsilon_3=1.5$, and $g=0.2$.
 
 \subsection{Realistic single-particle level system}
-
-\begin{table}
-\caption{\label{tab:fonts}\LaTeXe\ and AMS-\LaTeX\ font summary.}
-\begin{ruledtabular}
-\begin{tabular}{lp{2in}}
-\m{textit} & Italics. Replaces \m{it}\\
-\m{textbf} & Bold face. Replaces \m{bf}\\
-\m{textrm} & Roman. Replaces \m{rm}\\
-\m{textsl} & Slanted. Replaces \m{sl}\\
-\m{textsc} & Small caps. Replaces \m{sc}\\
-\m{textsf} & Sans serif. Replaces \m{sf}\\
-\m{texttt} & Typewriter. Replaces \m{tt}\\
-\m{textmd} & Medium series\\
-\m{textnormal} & Normal\\
-\m{textup} & Upright\\
-\m{mathbf} & Bold face\\
-\m{mathcal} & Replaces \m{cal}\\
-\m{mathit} & Italics\\
-\m{mathnormal} & Replaces \m{mit}\\
-\m{mathsf} & Sans serif\\
-\m{mathtt} & Typewriter\\
-\m{mathfrak} & Fraktur: Requires \classoption{amsfonts} or \classoption{amssymb} class option\\
-\m{mathbb} & Bold blackboard: Requires \classoption{amsfonts} or \classoption{amssymb} class option\\
-\m{bm} & Bold Greek and other math symbols: Requires
-\verb+\usepackage{bm}+ and may require the \classoption{amsfonts} class
-option
-\end{tabular}
-\end{ruledtabular}
-\end{table}
 

### 2018-09-14 paper2/draft1-1.tex
draft1.1

@@
 Under (\ref{LHE}), the eigenvalue of spurious mode corresponding pairing rotation is exact zero.
-Moreover, we can skip the Step.
-4 in Sec.
-\ref{ASCC}.
-After obtain the energy minimum point by solving normal HFB equation, we only use (\ref{LHE}) one after another to construct the one-dimensional collective Hamiltonian without moving-frame HFB equation (\ref{mfHFB}).
-It arises the uncertainty of the total gauge angle $\Phi$ during obtaining the collective path.
-To arrange the eigenvectors with $\Phi(q)=-\frac{1}{L} p_1\sum_l f^1_{,l}=0$, we correct the eigenvectors by
+To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_l f^1_{,l}=0$, we correct the eigenvectors by
 \begin{align}
@@
 We study the system with $\Omega_1=\Omega_2=\Omega_3=8$, $\epsilon_1=-1$, $\epsilon_2=0$, $\epsilon_3=1.5$, and $g=0.2$.
+The phase transition occurs at $g_c=0.058$ when $N=2\Omega_1=16$.
+We consider the even particle number chain from $N=14$ to $N=24$.
+
+The pairing correlation is strong enough for low-lying $0^+$ states to have closed TDHFB trajectories.
+
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{potential.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{fig:N8Pad}
+\end{figure*}
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{fig:N8Pad}
+\end{figure*}
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{fig:N8Pad}
+\end{figure*}
+
+\begin{table}
+\begin{ruledtabular}
+\begin{tabular}{c|c|cccccc}
+            & $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
+$0_2^+$ & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
+&ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
+$0_4^+$& Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
+&ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.94$ & $8.26$ & $8.47$\\
+\end{tabular}
+\end{ruledtabular}
+\caption{\label{ex}Excitation energy.}
+\end{table}
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{intra_trans.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{3levelPad}
+\end{figure}
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{inter_trans.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{3levelPad}
+\end{figure}
 

### 2018-09-14 paper2/draft1-1.tex
draft1.1

@@
 
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{Pbomega_sq.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{fig:N8Pad}
+\end{figure*}
+
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{Pbocc_number.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{fig:N8Pad}
+\end{figure*}
+
+\begin{table}
+\begin{ruledtabular}
+\begin{tabular}{c|cccccc}
+   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
+ Exact & $$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $$\\
+ASCC+SPA & unbound & $2.31$ & $2.21$ & $2.12$ & $2.04$ & unbound \\ 
+\end{tabular}
+\end{ruledtabular}
+\caption{\label{ex}Excitation energy.}
+\end{table}
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{PbPad}
+\end{figure}
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+	\caption{aa.
+}
+ \label{PbPad}
+\end{figure}
+
+\subsection{Realistic single-particle level system}
+
 \section{Conclusion}

### 2018-09-20 paper2/draft1-1.tex
draft1.1

--- 2018-09-14 paper2/draft1-1.tex
@@
  \begin{center}
-   \includegraphics[height=0.5\textwidth,angle=-90]{N100Xeq2trajectory.eps}
+   \includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2trajectory.eps}
  \end{center}
-\caption{aa}
+\caption{TDHFB trajectory of $\ket{0_2^+}$ in two-dimensional phase space.
+Solid line is obtained from one-dimensional ATDHFB+SPA calculation and cross points corresponding to each mesh point are obtained from ASCC+SPA.
+}
 \label{fig:N100_traj}
@@
  \end{center}
-\caption{aa}
+\caption{Action integral of  $\ket{0_2^+}$ with respect to time $t$.
+Solid line is obtained from one-dimensional ATDHFB+SPA calculation and cross points corresponding to each mesh point are obtained from ASCC+SPA.
+Dashed line is $2\pi$ corresponding to $\ket{0_2^+}$ in EBK quantization condition.
+Based on Fig.
+\ref{fig:N100_traj}, we calculated the action integral from $(\phi,j)=(0,-8)$ in clockwise direction.
+}
 \label{fig:N100_tau}
@@
 
-The pairing correlation is strong enough for low-lying $0^+$ states to have closed TDHFB trajectories.
+From moving-frame QRPA equation, we obtain three modes along the collective path (Fig.
+\ref{omega_sq}).
+Except zero mode, we choose the lowest mode as collective motion.
+Fig.
+\ref{occ_number} and Fig.
+\ref{potential} are occupation number in each single-particle level and collective potential in the collective path, respectively.
+We can find the occupation numbers become to integer at both end points.
+Furthermore, Hartree-Fock states always emerge at one of the end point.
 
-\begin{figure*}[t]
- \begin{center}
-  \includegraphics[width=40mm,angle=-90]{potential.eps}
- \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
-	\caption{aa.
-}
- \label{fig:N8Pad}
-\end{figure*}
 \begin{figure*}[t]
@@
  \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
-	\caption{aa.
+	\caption{Eigenvalues of moving-frame QRPA equation with respect to the collective coordinate $q$, from $N=14$ to $N=24$.
+Purple lines are spurious modes and green lines are chosen modes corresponding to the collective coordinate.
+In each panel, both edges correspond to the end points of the collective coordinate.
 }
- \label{fig:N8Pad}
+ \label{omega_sq}
 \end{figure*}
@@
  \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
-	\caption{aa.
+	\caption{Occupation numbers in each single-particle level with respect to the collective coordinate $q$, from $N=14$ to $N=24$.
+At the left end point of the collective coordinate in each panel, the configurations correspond to Hartree-Fock states.
 }
- \label{fig:N8Pad}
+ \label{occ_number}
 \end{figure*}
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{potential.eps}
+ \end{center}
+	\caption{Collective potential obtained from ASCC. We adjusted the energy minimum point as $V=0$.
+}
+ \label{potential}
+\end{figure}
 
-\begin{table}
+Based on the information from ASCC calculation, we can obtain the excited states from SPA.
+Table \ref{ex} shows the excitation energies of first and second excited states in the collective subspace.
+Up to the second excitation, all of the energies are in their energy pockets shown in Fig.
+\ref{potential}.
+Compare the result from ASCC+SPA with exact solution, we can find all of the values are nicely reproduced.
+The slightly difference is that the values from ASCC+SPA are about $5\%$ smaller than exact solution.
+\begin{table}[htbp]
 \begin{ruledtabular}
@@
             & $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
-$0_2^+$ & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
-&ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
-$0_4^+$& Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
-&ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.94$ & $8.26$ & $8.47$\\
+$0_2^+$ one & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
+phonon &ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
+$0_4^+$ two & Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
+phonon &ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
 \end{tabular}
 \end{ruledtabular}
-\caption{\label{ex}Excitation energy.}
+\caption{Excitation energies of one-phonon and two-phonon states from exact solution and ASCC+SPA calculation.
+In a chosen collective subspace, one-phonon and two-phonon states correspond to the first and second excitation, respectively.
+In the whole Hilbert space, one-phonon and two-phonon states correspond to $\ket{0_2^+}$ and $\ket{0_4^+}$, respectively.}
+\label{ex}
 \end{table}
 
-\begin{figure}[t]
+\begin{figure}[htbp]
  \begin{center}
@@
  \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
-	\caption{aa.
-}
- \label{3levelPad}
-\end{figure}
-
-\begin{figure}[t]
  \begin{center}
@@
  \end{center}
- \captionsetup{labelformat=empty,labelsep=none}
-	\caption{aa.
+	\caption{The strength of pair additional transition
+$B(P_{\rm ad};k\rightarrow k')=|\braket{N+2,k'|S^+|N,k}|^2$, from $N=14$ to $N=22$.
+Dashed lines are exact solution and solid lines are ASCC+SPA calculation.
+Horizontal line shows the particle number of the initial states.
+Upper panel shows the intraband transitions of
+$\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$,
+while lower panel shows the interband transition of
+$\ket{0_1^+}\to\ket{0_2^+}$ and $\ket{0_2^+}\to\ket{0_1^+}$.
 }
@@
 
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{Pbomega_sq.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
+}
+ \label{Pb_omega_sq}
+\end{figure*}
+
+\begin{figure*}[t]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{Pbocc_number.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
+}
+ \label{Pb_occ_number}
+\end{figure*}
+
+\begin{table}[htbp]
+\begin{ruledtabular}
+\begin{tabular}{c|cccccc}
+   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
+ Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$\\
+ASCC+SPA & unbound & $2.31$ & $2.21$ & $2.12$ & $2.04$ & unbound \\ 
+\end{tabular}
+\end{ruledtabular}
+\caption{The same as Fig. \ref{ex} but for Pb isotopes.}
+\label{Pb_ex}
+\end{table}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
+ \end{center}
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
+}
+ \label{PbPad}
+\end{figure}
+
 \section{Conclusion}

### 2018-09-21 paper2/draft1-1.tex
draft1.1

@@
  \equiv& \sum_{\{j_l\}\in (\sum_{j_l}=J)} C_{j_l} \ket{\cdots;S_l,-S_l+j_l,\cdots}
+ \label{SPA2}
 \end{align}
@@
 \end{align}
+
+The definition of wave function in SPA can also be extended into ground state.
+The ground state is constructed by only energy minimum point in TDHFB phase space.
+In the energy minimum point, $\ket{\Phi,J;q,p}=\ket{\rm HFB}$.
+Therefore, (\ref{SPA2}) becomes
+\begin{align}
+ \ket{\tilde{\phi}_{g.s.}} \propto& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \ket{\rm HFB},  
+\end{align}
+which is identical to the wave function of the particle number projection for HFB state.
 
@@
 \ref{potential}.
-Compare the result from ASCC+SPA with exact solution, we can find all of the values are nicely reproduced.
+Comparing the result from ASCC+SPA with exact solution, we can find all of the values are nicely reproduced.
 The slightly difference is that the values from ASCC+SPA are about $5\%$ smaller than exact solution.
+Using the wave function of excited states, the pair additional transition strength is shown in Fig.
+\ref{3levelPad}.
+For intraband transition, comparing ASCC+SPA with exact solution, $B(P_{\rm ad};0\rightarrow 0)$ are almost identical and $B(P_{\rm ad};1\rightarrow 1)$ are about $10\%\sim20\%$ small.
+For interband transition, the strength from ASCC+SPA is much smaller than exact solution.
+However, because the pairing correlation is enough strong in this case, the strength of intraband transition is dominant compared with interband transition.
+We can find that $B(P_{\rm ad};0\rightarrow 1)$ and $B(P_{\rm ad};1\rightarrow 0)$ are only about $1\%$ of $B(P_{\rm ad};0\rightarrow 0)$ and $B(P_{\rm ad};1\rightarrow 1)$.
+Therefore, the interband transition can be regarded as reasonable.
+From all above results, we can conclude that ASCC+SPA reproduces exact solution quantitatively.
 \begin{table}[htbp]
@@
 
-\subsection{Realistic single-particle level system}
+\subsection{Pb isotopes}
+With pairing model, we study neutron's pairing vibration in Pb isotope.
+We prepare the neutron's single-particle level between the magic number 82 and 126 (Table \ref{Pb}).
+The coupling constant $g=0.138$ is determined to reproduce the experimental pairing gap $\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb.
+We consider the even-even system from ${}^{188}$Pb to ${}^{194}$Pb.
+\begin{table}[htbp]
+\begin{ruledtabular}
+\begin{tabular}{c|cccccc}
+  orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
+  energy& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
+\end{tabular}
+\end{ruledtabular}
+\caption{Single-particle levels of Pb isotopes used in the calculation. The orbits are obtained from spherical Woods-Saxon potential with spin-orbit coupling. }
+\label{Pb}
+\end{table}
+
+We have six TDHFB degrees of freedom in the system.
+Fig.
+\ref{Pb_omega_sq} shows the eigenvalue of moving-frame QRPA equation.
+We can find there are one spurious mode and five vibrational modes.
+Even though the degrees of freedom increase compared with three-level system, the collective modes we focus on did not cross with other modes in all panels.
+It means that the collective mode is nicely decoupled from other degrees of freedom.
+Under the chosen mode, the occupation number is shown in Fig.
+\ref{Pb_occ_number}.
+As with three-level system, the left end points correspond to HF state in all panels.
+The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
+In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ changes significantly, while other orbits are almost constant.
 
@@
 \end{ruledtabular}
-\caption{The same as Fig. \ref{ex} but for Pb isotopes.}
+\caption{The same as Table. \ref{ex} but for Pb isotopes.}
 \label{Pb_ex}

### 2018-09-30 paper2/draft1-1.tex
draft1.1

@@
 \section{Results}
-We apply ASCC + SPA to study the multi-level system in pairing model.
+We apply ASCC+SPA to study the multi-level system in pairing model.
 The TDHFB degrees of freedom equals the number of single particle levels, including the constant of motion (pairing rotation).
-First, we confirm the dynamics is identical between ASCC + SPA and adiabatic TDHFB in two-level (one-dimensional TDHFB) system.
+We consider various systems, two-level system, three-level system, and Pb isotope system in each subsection respectively.
 Next, we discuss the dynamics in non-integrable (more than three-level) system.
@@
 \subsection{Confirmation in one-dimensional TDHFB system}
+The two-level system corresponds to one-dimensional TDHFB system after decoupling the global gauge angle $\Phi$.
+We can obtain the obvious collective path from ASCC.
+The dynamics is exactly identical with adiabatic TDHFB (ATDHFB).
+We confirm that whether ASCC is identical to one-dimensional ATDHFB, and compare the difference with TDHFB, in numerical calculation.
+
 In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
@@
 The conjugate momentum is $j= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \{\Omega_2(1-\cos{\theta}_2) - \Omega_1(1-\cos{\theta}_1)\}/4$.
-The adiabatic TDHFB (ATDHFB) means that we expand the Hamiltonian with respect to $\chi$ up to second order
+The ATDHFB indicates that the Hamiltonian can be expanded up to second order with respect to $\phi$
 \begin{align}
@@
 where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
-Because the time-dependent pairing vibrational mode is explicitly decoupled from pairing rotational mode, ASCC must be identical with ATDHFB.
-Furthermore, the excited states from SPA are also identical from both approaches.
+We know that the BCS ground state corresponds to the potential minimum point with $\phi=0$.
+If the pairing correlation is strong enough to bind the excited states in the collective potential,  the adiabatic approximation is expected to be well because the states are localized in small $\phi$ region.
 
-We study the system with equal degeneracy $\Omega_1=\Omega_2=50$, $g/(\epsilon_2-\epsilon_1)=0.02$, and $N=100$.
-In ASCC calculation, we set the mesh size of collective coordinate $dq=0.02$.
-We compared the excited $0^+$ states from one-dimensional ATDHFB and ASCC with each other.
+We study the system with equal degeneracy $\Omega_1=\Omega_2=8$, $g/(\epsilon_2-\epsilon_1)=0.2$, and $N=16$.
+In ASCC calculation, we set the mesh size of collective coordinate $dq=0.01$.
+We compared the results of $\ket{0_2^+}$ and $\ket{0_3^+}$ in three different calculations.
 Fig.
-\ref{fig:N100_traj} and Fig.
-\ref{fig:N100_tau} show the TDHFB trajectory in phase space and  action integral $\mathcal{T}$ as a function of time $t$, corresponding to $\ket{0_2^+}$, respectively.
-All of the mesh points obtained from ASCC are on the trajectory obtained from ATDHFB.
+\ref{fig:N16_traj} and Fig.
+\ref{fig:N16_tau} correspond to the classical informations, which are classical trajectories in phase space and action integral $\mathcal{T}$ as a function of time $t$.
+All of the mesh points obtained from ASCC are on the trajectories obtained from ATDHFB.
+For $\ket{0_2^+}$, the closed trajectory is well localized in the phase space and TDHFB calculation is almost the same as ASCC and ATDHFB calculations.
+For $\ket{0_3^+}$, the trajectory is still closed but near the transition point between closed trajectory and open trajectory.
+We can find ASCC and ATDHFB calculations have a small deviation from TDHFB calculation.
 The obtained excited $0^+$ states from SPA are shown in Fig.
-\ref{fig:N100_occ}.
-The occupation probability can be decomposed into $2n$-particle-$2n$-hole components.
-We can find the results from ATDHFB and ASCC are identical for all states.
-Therefore, the theoretical framework of ASCC + SPA has no problem.
+\ref{fig:N16_occ}.
+We show the occupation probability which is decomposed into $2n$-particle-$2n$-hole components.
+The results from ATDHFB and ASCC are identical within numerical error.
+Also, TDHFB calculation is very close to other two calculations.
 
@@
  \begin{center}
-   \includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2trajectory.eps}
+   \includegraphics[height=0.45\textwidth,angle=-90]{N16X3p2trajectory.eps}
  \end{center}
-\caption{TDHFB trajectory of $\ket{0_2^+}$ in two-dimensional phase space.
-Solid line is obtained from one-dimensional ATDHFB+SPA calculation and cross points corresponding to each mesh point are obtained from ASCC+SPA.
+\caption{Classical trajectories of $\ket{0_2^+}$ and $\ket{0_3^+}$ in two-dimensional phase space.
+The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$.
+Cross points, solid lines, and dashed lines correspond to the results from ASCC+SPA, one-dimensional ATDHFB+SPA, and one-dimensional TDHFB+SPA, respectively.
+In ASCC+SPA calculation, each cross point corresponds to each mesh point from ASCC calculation.
 }
-\label{fig:N100_traj}
+\label{fig:N16_traj}
 \end{figure}
@@
  \begin{center}
-   \includegraphics[height=0.5\textwidth,angle=-90]{N100Xeq2tau.eps}
+   \includegraphics[height=0.5\textwidth,angle=-90]{N16X3p2action.eps}
  \end{center}
-\caption{Action integral of  $\ket{0_2^+}$ with respect to time $t$.
-Solid line is obtained from one-dimensional ATDHFB+SPA calculation and cross points corresponding to each mesh point are obtained from ASCC+SPA.
-Dashed line is $2\pi$ corresponding to $\ket{0_2^+}$ in EBK quantization condition.
+\caption{Action integrals of $\ket{0_2^+}$ and $\ket{0_3^+}$ with respect to time $t$.Cross points, solid lines, and dashed lines correspond to the results from ASCC+SPA, one-dimensional ATDHFB+SPA, and one-dimensional TDHFB+SPA, respectively.
+Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$.
 Based on Fig.
-\ref{fig:N100_traj}, we calculated the action integral from $(\phi,j)=(0,-8)$ in clockwise direction.
+\ref{fig:N16_traj}, we calculated the action integrals on each trajectory from $(\phi,j)=(0,j_{\rm max})$ in clockwise direction.
 }
-\label{fig:N100_tau}
+\label{fig:N16_tau}
 \end{figure}
@@
  \begin{center}
-   \includegraphics[height=0.5\textwidth,angle=-90]{N100Xeq2occ.eps}
+   \includegraphics[height=0.5\textwidth,angle=-90]{N16X3p2occ.eps}
  \end{center}
-	\caption{Occupation probability in excited $0^+$ states
-as a function of $j$ for $\Omega_1=\Omega_2=50$, $N=100$, and $x=2$ system.
+	\caption{Occupation probabilities of $\ket{0_2^+}$ and $\ket{0_3^+}$
+as a function of $j$.
 The two vertical bars at each $j$ from the left to the right represent
 the squared components of the wave functions
-from ATDHFB+SPA and ASCC+SPA calculations, respectively.
+from ASCC+SPA, ATDHFB+SPA and TDHFB+SPA calculations, respectively.
 The left end of the horizontal axis at $j=j_{\rm min}$
@@
 }
- \label{fig:N100_occ}
+ \label{fig:N16_occ}
 \end{figure}
+
+Comparing with one-dimensional TDHFB calculation, we confirmed we succeed to describe the bound collective excited states by ASCC+SPA.
+For the bound states, whether the adiabatic approximation included or not hardly has influence.
+Even for the weakly bound states, the adiabatic approximation is reasonable approximation.
 
@@
 \ref{3levelPad}.
-For intraband transition, comparing ASCC+SPA with exact solution, $B(P_{\rm ad};0\rightarrow 0)$ are almost identical and $B(P_{\rm ad};1\rightarrow 1)$ are about $10\%\sim20\%$ small.
+For intraband transition, comparing ASCC+SPA with exact solution, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$ are almost identical and $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are about $10\%\sim20\%$ small.
 For interband transition, the strength from ASCC+SPA is much smaller than exact solution.
+It is difficult to reproduce the absolute value of exact solution.
 However, because the pairing correlation is enough strong in this case, the strength of intraband transition is dominant compared with interband transition.
-We can find that $B(P_{\rm ad};0\rightarrow 1)$ and $B(P_{\rm ad};1\rightarrow 0)$ are only about $1\%$ of $B(P_{\rm ad};0\rightarrow 0)$ and $B(P_{\rm ad};1\rightarrow 1)$.
+We can find that $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_1^+)$ are only about $1\%$ of $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$.
 Therefore, the interband transition can be regarded as reasonable.
 From all above results, we can conclude that ASCC+SPA reproduces exact solution quantitatively.
+
+%We skipped the result about $\ket{0_3^+}$.
+ We need to discuss about the second excited state in the collective path corresponds to not $\ket{0_3^+}$ and others, but $\ket{0_4^+}$.
+In pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from exact solution, $B(P_{\rm ad};0_2^+\rightarrow 0_3^+)$ is $10\sim100$ times smaller than $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$, and $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ is in the same order with $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$.
+It indicates that $\ket{0_3^+}$ is also one-phonon state which belongs to the other collective path (black line in Fig.
+\ref{omega_sq}).
+About two-phonon states, we can easily find the candidates of two-phonon states from excitation energies and $B(P_{\rm ad};0_1^+\rightarrow 0_{ex}^+)$.
+In the candidates, $\ket{0_4^+}$ is the lowest two-phonon state and $B(P_{\rm ad};0_2^+\rightarrow 0_4^+)$ is much larger than $B(P_{\rm ad};0_3^+\rightarrow 0_4^+)$.
+Therefore, $\ket{0_4^+}$ is considered to be most appropriate corresponding to the second excited state in ASCC+SPA calculation.
 \begin{table}[htbp]
@@
 We prepare the neutron's single-particle level between the magic number 82 and 126 (Table \ref{Pb}).
-The coupling constant $g=0.138$ is determined to reproduce the experimental pairing gap $\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb.
+The coupling constant $g=0.138$(MeV) is determined to reproduce the experimental pairing gap $\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb.
 We consider the even-even system from ${}^{188}$Pb to ${}^{194}$Pb.
@@
   orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
-  energy& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
+  energy(MeV)& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
 \end{tabular}
@@
 We can find there are one spurious mode and five vibrational modes.
-Even though the degrees of freedom increase compared with three-level system, the collective modes we focus on did not cross with other modes in all panels.
-It means that the collective mode is nicely decoupled from other degrees of freedom.
-Under the chosen mode, the occupation number is shown in Fig.
+The collective modes we focus on did not cross with other modes in all panels, while the spacings of the collective modes and the second vibrational modes are small, especially for ${}^{194}$Pb.
+Under the chosen collective modes, the occupation number is shown in Fig.
 \ref{Pb_occ_number}.
@@
 The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
-In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ changes significantly, while other orbits are almost constant.
-
+In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ changes significantly, while other orbits don't change so much.
+The collective potential for each isotope is shown in Fig.
+\ref{Pb_potential}.
+The depths of them are about $2.5\sim3.5$(MeV) only enough to bind $\ket{0_2^+}$, one-phonon states.
+We can consider that the collectivity of pairing is small for excited states, even though their ground states are superfluid states.
 \begin{figure*}[t]
@@
 \end{figure*}
-
 \begin{figure*}[t]
@@
 \end{figure*}
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbpotential.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{potential} but for Pb isotopes.
+}
+ \label{Pb_potential}
+\end{figure}
+
+We show the results of $\ket{0_2^+}$, one-phonon state in the collective coordinate, from SPA.
+Table \ref{Pb} shows the excitation energy.
+The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction.
+We are only interested in the comparison between exact solution and ASCC+SPA.
+We can find the excitation energy from ASCC+SPA reproduce the exact solution as well as in three-level system.
+The pair additional transition strength is shown in Fig.
+\ref{PbPad}.
+In this case, intraband transition is also dominant compared with interband transition.
+ASCC+SPA reproduces the tendency of exact solution and somewhat smaller than exact solution in all transition.
+However, the largest deviation, $B(P_{\rm ad};1\rightarrow 1)$, only has about $25\%$ deficiency compared with exact solution.
+Therefore, ASCC+SPA is supposed to be available into complex realistic system.
+
+In Pb isotope system, there are some problems remaining.
+Up to now, ASCC+SPA is only available when the excited states are bound in the collective potential.
+For example, we cannot calculate $\ket{0_2^+}$ in ${}^{186}$Pb because the potential is too shallow to bound the excited state.
+Also, the whole collective path in ${}^{196}$Pb cannot be obtained due to the complex eigenvalue of moving-frame QRPA equation in the collective path.
 
@@
 \end{ruledtabular}
-\caption{The same as Table. \ref{ex} but for Pb isotopes.}
+\caption{The same as Table. \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
 \label{Pb_ex}
 \end{table}
-
 \begin{figure}[htbp]
@@
 
+Finally, we discuss about whether the collective coordinate can be described by other physical quantities.
+The pairing gap $\Delta$ is the candidate of the collective coordinate, which is similar with $\alpha_{2\mu}$ in 5D Bohr Hamiltonian.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
+ \end{center}
+	\caption{Pairing gap as a function of collective coordinate in ${}^{192}$Pb. 
+}
+ \label{192Pb_gap}
+\end{figure}
+
 \section{Conclusion}
+Based on the previous work which demonstrated the accuracy of SPA for the requantization of TDHFB dynamics, we combined ASCC with SPA to apply non-integrable system.
+We constructed the theoretical framework of ASCC+SPA for bound state, which is bound in the collective potential from ASCC.
+Besides the collective Hamiltonian, $Q$ operator at each point of collective path is also necessary input information from ASCC.
+
+We applied ASCC+SPA into multi-level pairing model.
+Because the global gauge angle $\Phi$ is a cyclic variable, the simplest non-integrable system is three level system.
+We investigated three level system and more realistic system, neutron's single particle levels from Pb isotope.
+In both cases, the low-lying excited $0^+$ states reproduce exact solution well not only excitation energies but also wave functions.
+The pair transition calculation has no difficulty because we don't need to requantize the pair transition operators.
+This point overcomes the disadvantage in canonical requantization.
+
+While the basic theoretical framework of ASCC+SPA was constructed, there are some problems remaining.
 

### 2018-10-01 paper2/draft1-1.tex
draft1.1

@@
               University of Tsukuba, Tsukuba 305-8571, Japan}
-\author{Takashi Nakatsukasa}
+\author{Nobuo Hinohara}
+ \affiliation{Faculty of Pure and Applied Sciences,
+              University of Tsukuba, Tsukuba 305-8571, Japan}
  \affiliation{Center for Computational Sciences,
               University of Tsukuba, Tsukuba 305-8577, Japan}
+\author{Takashi Nakatsukasa}
  \affiliation{Faculty of Pure and Applied Sciences,
               University of Tsukuba, Tsukuba 305-8571, Japan}
+ \affiliation{Center for Computational Sciences,
+              University of Tsukuba, Tsukuba 305-8577, Japan}
  \affiliation{iTHES Research Group, RIKEN, Wako 351-0198, Japan}
@@
 \begin{abstract}
-\begin{description}
-\item[Background] This part would describe the
-context needed to understand what the paper
-is about.
-\item[Purpose] This part would state the purpose
-of the present paper.
-\item[Method] This part describe the methods
-used in the paper.
-\item[Results] This part would summarize the
-results.
-\item[Conclusions] This part would state the
-conclusions of the paper.
-\end{description}
+To describe the large amplitude collective motion in nuclear pairing, stationary phase approximation to the path integral (SPA) is supposed to be the most reliable requantization approach of time-dependent mean-field dynamics.
+The disadvantage of SPA is that it only available in integrable system.
+However, we overcome the disadvantage by combining SPA with adiabatic self-consistent collective coordinate method (ASCC).
+We construct the theoretical framework of  ASCC+SPA and demonstrate the application to the multi-level pairing model which is non-integrable system.
+As with the performance in integrable system, we find that SPA also gives reasonable information about low-lying excited $0^+$ states in non-integrable system.
+%\begin{description}
+%\item[Background] This part would describe the
+%context needed to understand what the paper
+%is about.
+%\item[Purpose] This part would state the purpose
+%of the present paper.
+%\item[Method] This part describe the methods
+%used in the paper.
+%\item[Results] This part would summarize the
+%results.
+%\item[Conclusions] This part would state the
+%conclusions of the paper.
+%\end{description}
 \end{abstract}
@@
 The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
-In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ changes significantly, while other orbits don't change so much.
+In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ orbits change significantly, while other orbits don't change so much.
 The collective potential for each isotope is shown in Fig.
@@
 \ref{PbPad}.
-In this case, intraband transition is also dominant compared with interband transition.
-ASCC+SPA reproduces the tendency of exact solution and somewhat smaller than exact solution in all transition.
-However, the largest deviation, $B(P_{\rm ad};1\rightarrow 1)$, only has about $25\%$ deficiency compared with exact solution.
-Therefore, ASCC+SPA is supposed to be available into complex realistic system.
-
-In Pb isotope system, there are some problems remaining.
-Up to now, ASCC+SPA is only available when the excited states are bound in the collective potential.
-For example, we cannot calculate $\ket{0_2^+}$ in ${}^{186}$Pb because the potential is too shallow to bound the excited state.
-Also, the whole collective path in ${}^{196}$Pb cannot be obtained due to the complex eigenvalue of moving-frame QRPA equation in the collective path.
-
+The feature is similar to the case in three-level system, dominant intraband transition and the accuracy from ASCC+SPA.
+The deviation of $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ has about $25\%$ deficiency compared with exact solution.
+Therefore, ASCC+SPA gives reasonable results in realistic single-particle level systems.
 \begin{table}[htbp]
@@
 
-Finally, we discuss about whether the collective coordinate can be described by other physical quantities.
-The pairing gap $\Delta$ is the candidate of the collective coordinate, which is similar with $\alpha_{2\mu}$ in 5D Bohr Hamiltonian.
-
+Finally, we discuss about the validity of the collective treatment of the pairing.
+We know that the 5D collective model described by the quadrupole deformation parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,0)$ is widely applied to analyze experimental data.
+As with the 5D collective model, pairing can also be supposed as a sort of deformation.
+The collective model is described by the pair deformation parameters pairing gap $\Delta$ and global gauge angle $\Phi$.
+The utilization of the collective model for nuclear pairing dynamics was done in several references\cite{}.
+In our previous study, however, we find that the pairing gap $\Delta$ is not proper to be the collective coordinate in two-level pairing model \cite{}.
+In multi-level system, we can investigate the relations between the pairing gap and the collective coordinate.
+The pairing gap $\Delta$ is defined as
+\begin{align}
+  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|S^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
+  &= g\sum_l \sqrt{j_l(\Omega_l-j_l)} .
+\end{align}
+Fig.
+\ref{192Pb_gap} shows the pairing gap of $\Delta$ in ${}^{192}$Pb as a function of the collective coordinate $q$.
+We can see that the peak is near $q=0$ and both end points have small values.
+Because only one orbit near the Fermi energy ($i_{13/2}$ orbit for both end points) contributes the value of pairing gap, the value at both end points are small compared with the value around the ground state.
+There is no one-to-one correspondence between $\Delta$ and $q$ not only in ${}^{192}$Pb, but also in all multi-level systems.
+Therefore, the pairing gap $\Delta$ cannot properly describe the pairing dynamics.
 \begin{figure}[htbp]
@@
 
-\section{Conclusion}
-Based on the previous work which demonstrated the accuracy of SPA for the requantization of TDHFB dynamics, we combined ASCC with SPA to apply non-integrable system.
-We constructed the theoretical framework of ASCC+SPA for bound state, which is bound in the collective potential from ASCC.
-Besides the collective Hamiltonian, $Q$ operator at each point of collective path is also necessary input information from ASCC.
+\section{Conclusion and discussion}
+Based on our previous work which demonstrated the accuracy of SPA for the requantization of TDHFB dynamics, we considered the application of SPA to non-integrable system.
+The one of the possible way to extend SPA into non-integrable system is to combine with ASCC.
+We constructed the theoretical framework of ASCC+SPA for bound states, which is bound in the collective potential from ASCC.
+%Besides the collective Hamiltonian, $Q$ operator at each point of collective path is also necessary input information.
 
@@
 Because the global gauge angle $\Phi$ is a cyclic variable, the simplest non-integrable system is three level system.
-We investigated three level system and more realistic system, neutron's single particle levels from Pb isotope.
-In both cases, the low-lying excited $0^+$ states reproduce exact solution well not only excitation energies but also wave functions.
-The pair transition calculation has no difficulty because we don't need to requantize the pair transition operators.
+We investigated three level system and more realistic system, neutron's single-particle levels from Pb isotope.
+In both cases, the low-lying excited $0^+$ states from ASCC+SPA reproduce exact solution well not only for excitation energies but also for wave functions.
+In ASCC+SPA, the pair transition calculation has no difficulty because we don't need to requantize the pair transition operators.
 This point overcomes the disadvantage in canonical requantization.
 
-While the basic theoretical framework of ASCC+SPA was constructed, there are some problems remaining.
+While the basic theoretical framework of ASCC+SPA was constructed, there are several problems remaining.
+Up to now, ASCC+SPA is only available when the excited states are bound in the pocket of collective potential (See Fig.
+\ref{potential} and \ref{Pb_potential}).
+For example, we cannot calculate $\ket{0_2^+}$ in ${}^{186}$Pb because the potential is too shallow to bound the excited state.
+The difficulty for the application to the unbound states is that the wave function from SPA is not stationary state because the classical trajectory in phase space is not periodic.
+It is necessary to find some proper boundary conditions in the collective subspace.
+Another problem is about the crossing of the eigenvalues from moving-frame QRPA equation in the collective path.
+No problem occurs when two completely orthogonal modes crossing, such as rotational mode and vibrational mode (e.g.
+N=14,16,18,20 in Fig.
+\ref{omega_sq}).
+However, if two vibrational modes not orthogonal with each other become the same eigenvalues, the ASCC calculation stops.
+Actually, the two eigenvalues become complex conjugate values and the next mesh point of collective path cannot be decided properly.
+Such case is occurred in ${}^{196}$Pb.
+The eigenvalues crossing problem supposed to be the rare case because ${}^{196}$Pb system is the only case including the previous studies about the application of ASCC \cite{}.
 

### 2018-10-03 paper2/draft1-1.tex
draft1.1

@@
 \section{Introduction}
+%pairing in nuclei
+Pairing correlation plays an important role around the surface in open-shell nuclei.
+The properties of pairing for the ground states are well known such as odd-even mass difference, moment of inertia of rotational bands, and the quantum numbers for spin and parity.
+The elementary excitations of pairing, pairing vibrations and pairing rotations, are fascinating phenomena not only for open-shell nuclei, but also for closed-shell nuclei.
+However, the pairing dynamics still has unclear features in low-energy region (a few MeV excitation) of nuclei, especially for excited $J^{\pi}=0^+$ states.
+We aim to understand the dynamics from pairing correlation in nuclei from microscopic many-body theory.\par
+%TDMF theory for pairing
+Time-dependent mean-field (TDMF) theory is the common theory to describe the dynamics of nuclei from the microscopic degrees of freedom.
+Including pairing correlation, time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, corresponding to TDMF theory, is utilized for plenty of studies for both nuclear reaction and nuclear structure fields.
+In nuclear structure aspect, the harmonic approximation of TDHFB, quasiparticle random phase approximation (QRPA), can well describe the giant resonance of nuclei.
+Recently, the adiabatic approximations of TDHFB, such as adiabatic TDHFB (ATDHFB), adiabatic self-consistent collective coordinate method (ASCC), and 5D Bohr Hamiltonian constructed from microscopic degrees of freedom, is developed and start to be applied to low-lying excited states.
+They are expected to elucidate the large amplitude collective motions occurred in the structure, such as shape coexistence and anharmonic vibration.
+\par
+%previous work
+TDMF (TDHFB) theory corresponds to a stationary-limit in the path integral formulation.
+It lacks a part of the information about quantum fluctuation, which is remarkable in the large amplitude dynamics.
+To introduce the quantum fluctuation based on the TDHFB theory, the requantization process is necessary.
+The straightforward requantization method is canonical quantization.
+In 5D Bohr Hamiltonian, the canonical quantization was formulated and employed for the study of low-lying excited states in nuclei.
+In additional, it was also utilized to describe the large amplitude dynamics for pairing in pairing model.
+However, the Hilbert space which the wave function obtained from canonical quantization belongs to is quite different from the Hilbert space which the original wave function belongs to.
+It may cause the deviation for the requantized states.
+In our previous work, we studied the requantization of the TDHFB.
+We investigated the low-lying excited $0^+$ states in two-level pairing model by various requantization methods \cite{NN18}.
+Comparing with exact solution, we found that stationary phase approximation to the path integral (SPA) can give quantitatively results not only for the excitation energies, but also for the wave functions.
+We confirmed that SPA is superior to canonical requantization, especially for the calculation of two-particle transitional strength.
+The wave function obtained from SPA has two advantages: first, it is written in the (quasi)particle's degrees of freedom; second, it has good quantum number because the projection of the conservation quantities (e.g.
+total particle number, total angular momentum) are automatically contained.
+On the other hand, the disadvantage is that SPA only works in integrable systems.
+Due to the nuclear system is non-integrable system in general, we cannot employ SPA straightforward for the realistic system.
+\par
+%this work
+We discuss the application of SPA for the non-integrable system in this paper.
+We know that the one-dimensional system is integrable system.
+It is desirable that a collective motion can be described by one collective coordinate.
+To obtain the one-dimensional subspace, adiabatic self-consistent collective coordinate method (ASCC) is powerful tool.
+``Adiabatic'' indicates that the collective motion is slow compared with the single-particle motion.
+The collective degree of freedom is determined self-consistently from the TDHFB degrees of freedom without any assumption.
+The ASCC, which was developed from the basic idea of self-consistent collective coordinate method (SCC) \cite{MMSK80}, is flexible to deal with various collective potential, such as shape coexistence \cite{KNMM05, HNMM07, HNMM08}.
+A state in the collective subspace corresponds to a microscopic state in TDHFB phase space connected by $Q$ and $P$ operators in ASCC.
+This correspondence make us possible to apply SPA to non-integrable system.
+We construct the theoretical framework of ASCC+SPA, which implements SPA to non-integrable system by combing with ASCC.
+The first study of ASCC+SPA give us a new landscape about the large-amplitude dynamics in low-energy region.
+
+%organization of paper
+The paper is organized as follows.
+Sec.
+\ref{sec2} introduces the theoretical framework of ASCC and the combination, ASCC+SPA.
+Sec.
+\ref{sec3} is the application of ASCC+SPA in multi-level pairing model.
+We give the numerical results in Sec.
+\ref{sec4}, including two-level systems, three-level systems, and Pb isotope systems.
+The conclusion and the remaining problems are shown in Sec.
+\ref{sec5}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Theoretical framework}
+\label{sec2}
 
@@
 \label{ASCC}
-
-We review the one-dimensional adiabatic self-consistent collective coordinate method (ASCC) briefly.
+To discuss the application of ASCC+SPA in the later subsection, we review the one-dimensional adiabatic self-consistent collective coordinate method (ASCC) briefly \cite{N2012}.
 The classical Hamilton's equation which is identical to the TDHFB equation is described by canonical variables $\{\xi^{\alpha},\pi_{\alpha}\}$.
-If we assume the collective motion is slow motion, it allows us to expand momenta $\pi$ up to second order.
+If we apply the adiabatic approximation which assume that the collective motion is slow compared with the single-particle motion, we can  expand the momenta $\pi$ up to second order.
 The multi-dimensional Hamiltonian is
@@
 where the index $1$ indicates the collective degree of freedom, and the comma indicates the partial derivative $(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$.
+The canonical coordinates fulfill the canonicity
+\begin{align}
+  f^1_{,\alpha}g_{,1}^{\beta} = \delta^{\beta}_{\alpha}, \quad f^1_{,\alpha}g_{,1}^{\alpha} = 1.
+  \label{canonicity}
+\end{align}
 With these relations, collective potential $\bar{V}(q)$ and collective mass parameter $\bar{B}(q)$ can be transformed by
@@
 In most of case, we know the explicit form of $\mathcal{P}(\xi,\pi)$.
-The procedures to obtain the collective path are (see Figure \ref{scc}):
+The procedures to obtain the collective path are:
 \begin{enumerate}
 \item Find the energy minimum point in energy surface by solving (\ref{mfHFB}) (normal HFB equation). We usually set $q^1=0$ at the energy minimum point.
-\item Using (\ref{M}), diagonalize (\ref{mfQRPA}) and choose the lowest mode basically\footnote{
-When eigenvalues cross on the collective path, the choice of adiabatic path or diabatic path is a critical problem}. 
+\item Using (\ref{M}), diagonalize (\ref{mfQRPA}) and choose the lowest mode basically.%\footnote{
+%When eigenvalues cross on the collective path, the choice of adiabatic path or diabatic path is a critical problem}. 
 \item The right eigenvector $g^{\alpha}_{,1}$ tell us the direction which system moves in energy surface.
 Use the relation $d\xi^{\alpha}=g^{\alpha}_{,1}dq^1$ to decide the neighborhood point $q^1\to q^1+dq^1$ in the collective path.
-\item Find the non-equilibrium energy minimum point by solving (\ref{mfHFB}) at the neighborhood point, and obtain the chemical potential $\lambda_I(q)$. 
-\item Iterate (2)$\sim$(4) under the same direction in energy surface. 
-\item Do (2)$\sim$(5) for the opposite direction of the collective path in energy surface. 
+\item Using $f^1_{,\alpha}$, find the non-equilibrium energy minimum point by solving (\ref{mfHFB}) at the neighborhood point.
+We usually use the constraint condition $dq=f^1_{,\alpha}(\xi^{\alpha}(q)-\xi^{\alpha}(q-dq))$ from the canonicity (\ref{canonicity}).
+After convergence, we diagonalize (\ref{mfQRPA}) and obtain the corrected $f^1_{,\alpha}$.
+\item Iterate (4) until the convergence of $f^1_{,\alpha}$.  
+\item Iterate (2)$\sim$(5) to decide the collective path under the same direction in the energy surface. 
+\item Implement (2)$\sim$(6) for the opposite direction of the collective path in energy surface. 
 \end{enumerate}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Application in pairing model}
+\label{sec3}
+
 We study the low-lying excited $0^+$ states in multi-level pairing model by applying SPA via ASCC. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Results}
+\label{sec4}
 We apply ASCC+SPA to study the multi-level system in pairing model.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion and discussion}
+\label{sec5}
 Based on our previous work which demonstrated the accuracy of SPA for the requantization of TDHFB dynamics, we considered the application of SPA to non-integrable system.
@@
 It is necessary to find some proper boundary conditions in the collective subspace.
-Another problem is about the crossing of the eigenvalues from moving-frame QRPA equation in the collective path.
+The second problem is about the crossing of the eigenvalues from moving-frame QRPA equation in the collective path.
 No problem occurs when two completely orthogonal modes crossing, such as rotational mode and vibrational mode (e.g.
@@
 Such case is occurred in ${}^{196}$Pb.
-The eigenvalues crossing problem supposed to be the rare case because ${}^{196}$Pb system is the only case including the previous studies about the application of ASCC \cite{}.
+The eigenvalues crossing problem supposed to be the rare case because ${}^{196}$Pb system is the only case including the previous studies about the application of ASCC.
+In addition, we need to consider the multi energy minimum pockets in the collective potential \cite{HNMM07, HNMM08}.
+Such case doesn't appear in pairing model.
+When the excitation energy is below the multi minimum pocket, the EBK quantization condition is not unique.
+With these problems, the theoretical framework of ASCC+SPA need to be developed in the next step.
+
+\begin{acknowledgments}
+This work is supported in part
+by Interdisciplinary Computational Science Program in CCS,
+University of Tsukuba,
+and
+by JSPS-NSFC Bilateral Program for Joint Research Project
+on Nuclear mass and life for unravelling mysteries of r-process.
+%and by ImPACT Program of Council for Science,
+%Technology and Innovation (Cabinet Office, Government of Japan).
+\end{acknowledgments}
+
+\bibliographystyle{apsrev4-1}
+\bibliography{ref}
 

### 2018-10-04 thesis/thesis.tex
thesis

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{book} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margins=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsmath,amssymb}

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{Thesis}
\author{Fang Ni}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\tableofcontents

\chapter{Introduction}
\section{First section}

Your text goes here.

\subsection{A subsection}

More text.

\chapter{Pairing model}

Pairing correlation plays important role near the Fermi energy. To examine the pairing dynamics influencing the structure of nuclei, we can only concentrate the nucleons near the Fermi energy. The Hamiltonian of pairing model is
\begin{align}
	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
\end{align}
where
\begin{align}
	n_l &= \sum_m a^{\dag}_{lm}a_{lm} \\
        S_l^{+} &= \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} 
\end{align}

\section{Exact solution}

\section{TDHFB dynamics}

\chapter{Requantization of TDHFB in integrable system}

\section{Canonical quantization}

\section{Fourier decomposition}

\section{Stationary phase to the path integral}

\section{Result}

\chapter{Requantization of TDHFB in non-integrable system}

\section{Derivation of the collective subspace in adiabatic self-consistent collective coordinate method}

\section{Application of SPA in non-integrable system}

\section{Result}

\chapter{Discussion}

\chapter{Conclusion}

\end{document}

### 2018-10-05 thesis/thesis.tex
draft1.1

@@
 \chapter{Introduction}
-\section{First section}
 
-Your text goes here.
+\section{Pairing interaction in nuclei}
+
+Pairing correlation plays an important role near the Fermi energy.
+Pairing correlation is the two-body interaction which couples two identical nucleons into $J^{\pi}=0^+$ state.
+There are many evidences of pairing correlation detected from experiment.
+The most clear evidence is shown in Fig.
+\ref{Sn_isotope}.
+All of the ground states of even-even Sn isotopes are $J^{\pi}=0^+$ states  It indicates that the ground states consist of the $J^{\pi}=0^+$ pairs is more stable than other configurations.
+In addition, the ground states between even-even nuclei and neighborhood odd nuclei has large gaps of binding energy.
+In odd nuclei, the unpaired last neutron is the last single-particle level.
+The odd-even mass difference  To break the $J^{\pi}=0^+$ pair, we need large energy which is about $2\Delta \approx 24A^{-1/2}$ MeV.
+\begin{figure}[htbp]
+ \begin{center}
+    \includegraphics[width=100mm, bb=0 0 400 300]{images/Sn_isotope.png}
+ \end{center}
+  \caption{Low-lying excited states in Sn isotopes \cite{}. The absolute values of binding energy are adjusted at 0 MeV in the ground state of ${}^{116}$Sn.}
+  \label{Sn_isotope}
+\end{figure}
 
@@
 
-Pairing correlation plays important role near the Fermi energy.
-To examine the pairing dynamics influencing the structure of nuclei, we can only concentrate the nucleons near the Fermi energy.
-The Hamiltonian of pairing model is
+To examine the pairing dynamics influencing the structure of nuclei, we can only concentrate the nucleons near the Fermi energy. The Hamiltonian of pairing model is
 \begin{align}

### 2018-10-12 paper2/draft1-1.tex
draft1.1

@@
 Pairing correlation plays an important role around the surface in open-shell nuclei.
-The properties of pairing for the ground states are well known such as odd-even mass difference, moment of inertia of rotational bands, and the quantum numbers for spin and parity.
-The elementary excitations of pairing, pairing vibrations and pairing rotations, are fascinating phenomena not only for open-shell nuclei, but also for closed-shell nuclei.
-However, the pairing dynamics still has unclear features in low-energy region (a few MeV excitation) of nuclei, especially for excited $J^{\pi}=0^+$ states.
+The properties of pairing for the ground states are well known such as odd-even mass difference, moment of inertia of rotational bands, and the quantum numbers for spin and parity \cite{RS80}.
+The elementary excitations of pairing, pairing vibrations and pairing rotations, are fascinating phenomena not only for open-shell nuclei, but also for closed-shell nuclei \cite{BB05}.
+However, the pairing dynamics still has unclear features in low-energy region (a few MeV excitation) of nuclei, especially for excited $J^{\pi}=0^+$ states \cite{HW11, G01}.
 We aim to understand the dynamics from pairing correlation in nuclei from microscopic many-body theory.\par
@@
 Time-dependent mean-field (TDMF) theory is the common theory to describe the dynamics of nuclei from the microscopic degrees of freedom.
-Including pairing correlation, time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, corresponding to TDMF theory, is utilized for plenty of studies for both nuclear reaction and nuclear structure fields.
+Including pairing correlation, time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, corresponding to TDMF theory, is utilized for plenty of studies for both nuclear reaction and nuclear structure fields \cite{NMMY16}.
 In nuclear structure aspect, the harmonic approximation of TDHFB, quasiparticle random phase approximation (QRPA), can well describe the giant resonance of nuclei.
@@
 It lacks a part of the information about quantum fluctuation, which is remarkable in the large amplitude dynamics.
-To introduce the quantum fluctuation based on the TDHFB theory, the requantization process is necessary.
+To introduce the quantum fluctuation based on the TDHFB theory, the requantization process is necessary \cite{Neg82, L80, LNP80, Rei80, KS80, K81}.
 The straightforward requantization method is canonical quantization.
 In 5D Bohr Hamiltonian, the canonical quantization was formulated and employed for the study of low-lying excited states in nuclei.
-In additional, it was also utilized to describe the large amplitude dynamics for pairing in pairing model.
+In additional, it was also utilized to describe the large amplitude dynamics for pairing in pairing model \cite{BBPK70, GPBW85, ZPPRS99, P07}.
 However, the Hilbert space which the wave function obtained from canonical quantization belongs to is quite different from the Hilbert space which the original wave function belongs to.
@@
 We investigated the low-lying excited $0^+$ states in two-level pairing model by various requantization methods \cite{NN18}.
-Comparing with exact solution, we found that stationary phase approximation to the path integral (SPA) can give quantitatively results not only for the excitation energies, but also for the wave functions.
+Comparing with exact solution, we found that stationary phase approximation to the path integral (SPA) \cite{SM88} can give quantitatively results not only for the excitation energies, but also for the wave functions.
 We confirmed that SPA is superior to canonical requantization, especially for the calculation of two-particle transitional strength.
@@
 It is desirable that a collective motion can be described by one collective coordinate.
-To obtain the one-dimensional subspace, adiabatic self-consistent collective coordinate method (ASCC) is powerful tool.
+To obtain the one-dimensional subspace, adiabatic self-consistent collective coordinate method (ASCC) is powerful tool \cite{MNM00}.
 ``Adiabatic'' indicates that the collective motion is slow compared with the single-particle motion.
@@
 \label{ASCC}
-To discuss the application of ASCC+SPA in the later subsection, we review the one-dimensional adiabatic self-consistent collective coordinate method (ASCC) briefly \cite{N2012}.
+To discuss the application of ASCC+SPA in the later subsection, we review the one-dimensional adiabatic self-consistent collective coordinate method (ASCC) briefly using the notation in Ref.
+\cite{N2012}.
 The classical Hamilton's equation which is identical to the TDHFB equation is described by canonical variables $\{\xi^{\alpha},\pi_{\alpha}\}$.
@@
 \subsection{Application into ASCC}
+In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec. \ref{ASCC}. 
 We construct 1D collective subspace from ASCC theory.
-Because the first order with respect to $\chi_l$ is zero in TDHFB Hamiltonian, we assume $j_l$ as coordinates and $\chi_l$ as conjugate momenta.
-The canonical variables are $(j_l,-\chi_l)$ and fulfill $\{j_l,-\chi_l'\}_{PB}=\delta_{ll'}$.
-We expand the classical Hamiltonian up to second order with respect to $\chi_l$.
+Because the first order with respect to $\chi_{\alpha}$ is zero in TDHFB Hamiltonian, we assume $j^{\alpha}$ as coordinates and $\chi_{\alpha}$ as conjugate momenta.
+The canonical variables are $(j^{\alpha},-\chi_{\alpha})$ and fulfill $\{j^{\alpha},-\chi_{\beta}\}_{PB}=\delta^{\alpha}_{\beta}$.
+We expand the classical Hamiltonian up to second order with respect to $\chi_{\alpha}$.
 The classical Hamiltonian becomes
 \begin{align}
-  \mathcal{H}(\{\chi_l\},\{\pi_l\}) \approx& V(j) + \frac{1}{2}B^{\alpha\beta}(j)\chi_{\alpha}\chi_{\beta},
+  \mathcal{H}(j,\chi) \approx& V(j) + \frac{1}{2}B^{\alpha\beta}(j)\chi_{\alpha}\chi_{\beta},
 \end{align}
@@
   V(j) =& \mathcal{H}(\chi=0,j) \nonumber \\
-	=& \sum_l 2\epsilon_lj_l - g\sum_l \left( \Omega_lj_l - j_l^2 +\frac{j_l^2}{\Omega_l} \right) \nonumber \\
-  &- g\sum_{l_1\ne l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-j_{l_1})(\Omega_{l_2}-j_{l_2})} 	
+	=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left( \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right) \nonumber \\
+  &- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})} 	
 \end{align}
@@
 	\begin{array}{c}
-	2g\sum_{l\ne \alpha} \sqrt{j_{l}j_{\alpha}(\Omega_{l}-j_{l})(\Omega_{\alpha}-j_{\alpha})} \hspace{2em} (\alpha=\beta) \\
-	-2g\sqrt{j_{\alpha}j_{\beta}(\Omega_{\alpha}-j_{\alpha})(\Omega_{\beta}-j_{\beta})} \hspace{2em} (\alpha\ne\beta)
+	2g\sum_{\gamma\ne \alpha} \sqrt{j^{\gamma}j^{\alpha}(\Omega_{\gamma}-j^{\gamma})(\Omega_{\alpha}-j^{\alpha})} \hspace{2em} (\alpha=\beta) \\
+	-2g\sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})} \hspace{2em} (\alpha\ne\beta)
 	\end{array}
@@
 \begin{align}
-  \Phi = \frac{1}{L}\sum_l \chi_l.
+  \Phi = \frac{1}{L}\sum_{\alpha} \chi_{\alpha}.
   \label{total_gauge}
@@
 \begin{align}
-  J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}}=\sum_l j_l = \frac{N}{2}
+  J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}}=\sum_{\alpha} j^{\alpha} = \frac{N}{2}
   \label{J}
@@
 Under (\ref{LHE}), the eigenvalue of spurious mode corresponding pairing rotation is exact zero.
-To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_l f^1_{,l}=0$, we correct the eigenvectors by
+To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_{\alpha} f^1_{,\alpha}=0$, we correct the eigenvectors by
 \begin{align}
-  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_l f^1_{,l} 
+  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_{\beta} f^1_{,\beta} 
   \label{f}

### 2018-10-15 thesis/thesis.tex
thesis

@@
 %%% PAGE DIMENSIONS
-\usepackage{geometry} % to change the page dimensions
+%\usepackage{geometry} % to change the page dimensions
+\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}
 \geometry{a4paper} % or letterpaper (US) or a5paper or....
@@
 \usepackage{amsmath,amssymb}
+\usepackage{framed}
+\usepackage{braket}
 
@@
 \begin{align}
-	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
+	H &= \sum_{l=1}^L \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
 \end{align}
@@
         S_l^{+} &= \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
-\quad   S_l^{-} = S_l^{+\dag} 
+\quad   S_l^{-} = S_l^{+\dag} .
+\label{S_+}
 \end{align}
+In $L$ single-particle level system, each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
+degeneracy ($\Omega_l=j_l+1/2$)
+and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_l-1/2$.
+$\overline{m}$ indicates the time reversal quantum number with respect to $m$.
+The strength of pairing correlation is represented by coupling constant $g$.
+We also define a seniority $\nu_l$, which is the number of unpaired particles in each level.
+The unpaired particles have no pairing interaction, and play a part in Pauli blocking effect.\par
+In one-level system ($L=1$), the pairing dynamics is well understood. The analytic solution of the total energy is
+\begin{align}
+	E_{\nu}(N) = \epsilon N - \frac{1}{4}g(N-\nu)(2\Omega-N-\nu+2) .
+\end{align}
+The pairing rotational band created by the pairing correlation is completely parabolic with the moment of inertia $2/g$.
+Also, the excited states in a specified $N$ is only described by the quantum number $\nu$.
+For example, the first excited state in even particle system is $\nu=2$ state, which correspond to one $J^{\pi}=0^+$ pair broken state.\par
+The profound dynamics occurs in multi-level pairing model ($L\ge 2$).
+The pairing rotational mode becomes complex due to the shell effect.
+In addition, several pairing vibrational modes emerge.
+The pairing vibration is not single particle motion specified by $\nu_l$, but a collective motion with the excitation of $J^{\pi}=0^+$ pairs.
+In this chapter, we explain the numerical exact solution and derive the TDHFB dynamics in multi-level pairing Hamiltonian.
 
 \section{Exact solution}
+The eigenvalues and eigenvectors can be solved exactly in pairing model. There are two major methods to obtain the exact solutions, diagonalization in quasispin space and Richardson equation.
+
+\subsection{Diagonalization in quasispin space}
+We introduce SU(2) quasispin operators fulfilling the follows commutation relation
+\begin{equation}
+  [S_l^0,S_{l'}^{+}] = \delta_{ll'}S_{l}^{+},\hspace{20pt}[S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0}. 
+  \label{SU2commu}
+\end{equation}
+If we set 
+\begin{align}
+  S_l^0 &= \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l)
+  \label{S0}
+\end{align}
+and $S_l^+, S_l^-$ are the same as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
+\begin{align}
+	H &= \sum_l \epsilon_l (2S_l^0+\Omega_l) - g \sum_{l,l'} S_l^+ S_{l'}^- .
+\end{align}
+Therefore, any states $\ket{\psi}$ belong to SU(2)$\otimes\cdots\otimes$SU(2) Hilbert space, and can be expanded in the basis $\ket{S_1,S_1^0;\cdots;S_l,S_l^0;\cdots}$
+\begin{equation}
+  \ket{\psi} = \sum_{S_1^0,\cdots\,S_l^0,\cdots}c_{S_1^0,\cdots\,S_l^0,\cdots}\ket{S_1,S_1^0;\cdots;S_l,S_l^0;\cdots} .
+\end{equation}
+
+We discuss the physical meaning of the quasispin space.
+Because $S_l^+$ and $S_l^-$ correspond to the creation and annihilation operators with respect to the $J^{\pi}=0^+$ pairs in each level, the quasispin space is decoupled from the space which the unpaired particles belong to.
+Also, $S_l^0$ is related to the occupation number in each level.
+$S_l^0=-S_l$ is the minimum value corresponding no $J^{\pi}=0^+$ pair in the level and $S_l^0=S_l$ is the maximum value corresponding full of $J^{\pi}=0^+$ pairs in the level.
+Because $\nu_l$ plays a part in Pauli blocking effect in the level, the absolute value of quasispin $S_l$ is
+\begin{equation}
+  S_l = \frac{1}{2}(\Omega_l-\nu_l).
+\end{equation}
+
+The dimension of the model space is $D=\prod_l(2S_l+1)$.
+However, $[H,N]=0$ indicates that the Hamiltonian is block diagonal with respect to the total particle number $N$.
+The model space can be reduced after we extract the combination of $\{S_l^0\}$ fulfilling
+\begin{equation}
+  N = \sum_l (2S_l^0+2S_l+\nu_l) .
+\end{equation} 
+For example, we consider the dimension of the single particle levels between the magic number 50 and 82.
+Under spherical symmetry, we have five single particle levels, $d_{5/2}$, $g_{7/2}$, $s_{1/2}$, $d_{3/2}$, and $h_{11/2}$.
+The corresponding degeneracy is $\{\Omega_l\}=\{3,4,1,2,6\}$.
+If we only consider the case for$\nu_l=0$, the dimension for the system is $D=840$.
+On the other hand, under a specified $N$, the dimensions are 105 for $N=14$ and 91 for $N=20$.
+
+\subsection{Richardson equation}
+As mentioned above, diagonalizing the Hamiltonian is simple method to obtain the exact solution.
+However, diagonalization is time consuming when the model space becomes large.
+The calculation time is proportional to the cubes of the dimension of the model space For example, there are 16 single particle levels between the magic number 50 and 82 in deformed nuclei.
+Because the dimension for the system is $D=2^{16}=65536$, the calculation time in deformed system is $\sim 10^5$ times as much as the case in spherical system.
+\par
+The alternative method to obtain the exact solution is to solve Richardson equation.
+The idea was introduced by R.
+W.
+Richardson \cite{Richardson1, Richardson2, Richardson3}.
+We divide the total energy into two parts
+\begin{align}
+  E &= \braket{\psi|H|\psi} \\
+  &= \sum_l \epsilon_l \nu_l + \sum_{\alpha=1}^M E_{\alpha} .
+\end{align}
+The first term is the energy of unpaird particle, and the second term is the total energy of $J^{\pi}=0^+$ pairs. The pair-energy $E_{\alpha}$ is derived from the non-linear equations
+\begin{equation}
+  1 - g\sum_l \frac{\Omega_l-\nu_l}{2\epsilon_l-E_{\alpha}} + 2g\sum_{\beta(\neq\alpha)}^M \frac{1}{E_{\beta}-E_{\alpha}} = 0 .
+\end{equation}
+$M$ indicates the number of $J^{\pi}=0^+$ pairs in the system, and equals to the numbers of the non-linear equations.
+$E_{\alpha}$ can become not only real numbers, but also complex conjugate pairs when $M\ge 2$.
 
 \section{TDHFB dynamics}
+%In realistic nuclear system with nuclear effective interaction, the necessary model space is huge.
+To diagonalize the effective Hamiltonian is extremely difficult task.
+Such study is done by shell model calculation.
+In alternative way, we only prepare a limited model space, which supposed to be reproduce the important parts of nuclear properties.
+The time-dependent mean-field theory
+To understand the classical picture of the pairing dynamics, time-dependent mean-field (TDMF) theory is useful tool. With pairing correlation, TDMF theory attributes to TDHFB theory.
+The TDHFB equation can be derived from the time-dependent variational principle,
+\begin{equation}
+  \delta\mathcal{S}=0, \quad 
+  \mathcal{S} \equiv \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
+\end{equation}
+where $\ket{\phi(t)}$ is the time-dependent generalized Slater determinant (coherent state) obtained from Thouless' theorem
+\begin{equation}
+  \ket{\phi(t)} = \mathcal{R}\exp{\left( \sum_{k<k'}Z_{kk'}(t)\beta_k^{\dag}\beta_{k'}^{\dag}
+    \right)}\ket{\Phi_0} .
+\end{equation}
+$\beta_k^{\dag}$ is quasiparticle creation operator and $\mathcal{R}$ is normalization factor.
+$\ket{\Phi_0}$ is generally chosen as ground state or vacuum state.
+$Z_{kk'}(t)$ is time-dependent complex number determined by TDHFB equation.\par
+We derive the TDHFB equation in pairing model.
+First, we consider the time-dependent coherent state.
+Because the noticeable phenomenon is the dynamics for $J^{\pi}=0^+$ pairs in pairing model, we can describe the time-dependent coherent state in SU(2) quasispin space.
+Using Thouless' theorem, the time-dependent coherent state becomes
+\begin{equation}
+	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-S_l}
+	\exp [Z_l(t) S_l^{+}] \ket{0} .
+ \label{coherent}
+\end{equation}
+Here, we choose $\ket{\Phi_0}=\ket{0}$ which is vacuum (zero particle) state. In the quasispin representation, $\ket{0}=\prod_l \ket{S_l,-S_l}$.
 
@@
 
-\section{Canonical quantization}
+\section{TDHFB dynamics in two-level system}
 
-\section{Fourier decomposition}
+\section{Requantization methods}
+\subsection{Canonical quantization}
 
-\section{Stationary phase to the path integral}
+\subsection{Fourier decomposition}
+
+\subsection{Stationary phase to the path integral}
 
 \section{Result}
+
+\section{Collective model treatment}
 
@@
 
+\appendix
+
+\chapter{Detailed derivation of the action in pairing model}
+To obtain the TDHFB dynamics in pairing model, We need to derive the action $\mathcal{S}$ in explicit form. We give the detailed derivation in this chapter.
+
+\section{Properties of the spin-coherent state}
+The time-dependent coherent state classified into the spin-coherent state is employed in (\ref{coherent}). We derive the necessary formula for the spin-coherent state in this subsection. \par
+First, we consider the single-level case.
+With the commutation relation in (\ref{SU2commu}), the SU(2) quasispin operators fulfill the following relations
+\begin{align}
+  \hat{S}^{\pm}\ket{S,S^0} &= \sqrt{(S\mp S^0)(S\pm S^0+1)} \ket{S,S^0\pm 1}
+  \label{S_pm} \\
+  \hat{S}^0\ket{S,S^0} &= S^0\ket{S,S^0} .
+  \label{S_0}
+\end{align}
+Using above relations, the coherent state can be expanded as 
+\begin{align}
+  \ket{Z} &= (1+|Z|^2)^{-S}e^{Z \hat{S}^+}\ket{S,S^0=-S} \nonumber \\
+  &= (1+|Z|^2)^{-S}\sum_{n=0}^{2S}\sqrt{\frac{(2S)!}{n!(2S-n)!}}Z^n\ket{S,-S+n} .
+\end{align}
+We can find the normalization condition is fulfilled
+\begin{align}
+  \braket{Z|Z} &= (1+|Z|^2)^{-2S}\sum_{n=0}^{2S}\frac{(2S)!}{n!(2S-n)!}|Z|^{2n} \nonumber \\
+  &= (1+|Z|^2)^{-2S}\sum_{n=0}^{2S} {}_{2S}\mathrm{C}_n(|Z|^2)^n \nonumber \\
+  &= (1+|Z|^2)^{-2S}\times(1+|Z|^2)^{2S} \nonumber \\
+  &= 1 .
+\end{align}
+The overlap is
+\begin{align}
+  \braket{\eta|Z} &= \frac{(1+\eta^*Z)^{2S}}{(1+|\eta|^2)^S(1+|Z|^2)^S} .
+\end{align}
+
+We also calculate the expectation values of the operators. For $\hat{S}^0$,
+\begin{align}
+  \hat{S}^0e^{Z \hat{S}^+}\ket{S,S^0=-S} &= \sum_{n=0}^{2S}(-S+n)\sqrt{\frac{(2S)!}{n!(2S-n)!}}Z^n\ket{S,-S+n} ,
+\end{align}
+hence,
+\begin{align}
+  \braket{Z|\hat{S}^0|Z} &= (1+|Z|^2)^{-2S}\sum_{n=0}^{2S}(-S+n)\frac{(2S)!}{n!(2S-n)!}|Z|^{2n} \nonumber \\
+  &= -S + 2S\left( 1-\frac{1}{1+|Z|^2} \right) \nonumber \\
+  &= S\left( 1-\frac{2}{1+|Z|^2} \right) .
+  \label{S0}
+\end{align}
+From the first line to the second line, we used the differentiation for the both sides of
+\begin{align}
+  (1+|Z|^2)^{2S} &= \sum_{n=0}^{2S} {}_{2S}\mathrm{C}_n(|Z|^2)^n
+\end{align}
+with respect to $|Z|^2$. With (\ref{S0}), the expectation values of occupation number is
+\begin{align}
+  \braket{Z|\hat{n}|Z} &= \braket{Z|2\hat{S}^0+\Omega|Z} \nonumber \\
+	&= 2S\left( 1-\frac{2}{1+|Z|^2} \right) + \Omega .
+\end{align}
+The expectation values for $\hat{S}^+$ and $\hat{S}^-$ are the complex conjugate pair. For $\hat{S}^+$,
+\begin{align}
+  \hat{S}^+e^{Z \hat{S}^+}\ket{S,S^0=-S} &= \sum_{n=0}^{2S}\sqrt{(2S-n)(n+1)}\sqrt{\frac{(2S)!}{n!(2S-n)!}}Z^n\ket{S,-S+n+1}.
+\end{align}
+hence, 
+\begin{align}
+  \braket{Z|\hat{S}^+|Z} &= (1+|Z|^2)^{-2S}\sum_{n=0}^{2S}Z^n\sqrt{(2S-n)(n+1)}\sqrt{\frac{(2S)!}{n!(2S-n)!}}
+  \times(Z^*)^{n+1}\sqrt{\frac{(2S)!}{(n+1)!(2S-n-1)!}} \nonumber \\
+    &= (1+|Z|^2)^{-2S} Z^*\sum_{n=0}^{2S}|Z|^{2n}\frac{(2S)!}{n!(2S-n-1)!} \nonumber \\
+    &= \frac{2SZ^*}{1+|Z|^2} ,
+   \label{S+}
+\end{align} 
+and
+\begin{align}
+  \braket{Z|\hat{S}^-|Z} &= \braket{Z|\hat{S}^+|Z}^* = \frac{2SZ}{1+|Z|^2} .
+  \label{S-}
+\end{align}
+For the expectation value of $\hat{S}^+\hat{S}^-$,
+\begin{align}
+  \braket{Z|\hat{S}^+\hat{S}^-|Z} &= (1+|Z|^2)^{-2S}\|\hat{S}^-e^{Z \hat{S}^+}\ket{S,S^0=-S}\|^2 \nonumber \\
+  &= (1+|Z|^2)^{-2S}\sum_{n=0}^{2S}n(2S-n+1){}_{2S}\mathrm{C}_n|Z|^{2n} \nonumber \\
+  &= (1+|Z|^2)^{-2S} \left\{ (2S+1)2S(1+|Z|^2)^{2S-1}|Z|^2 - 2S(1+|Z|^2)^{2S}
+  \left( \frac{(2S-1)|Z|^4}{(1+|Z|^2)^2}+\frac{|Z|^2}{1+|Z|^2} \right) \right\} \nonumber \\
+  &= 2S|Z|^2\frac{2S+|Z|^2}{(1+|Z|^2)^2} .
+  \label{S+S-}
+\end{align}
+From the second line to the third line, we need to calculate the term $\sum_{n=0}^{2S}n^2{}_{2S}\mathrm{C}_n|Z|^{2n}$. It can be obtained from the following relation
+\begin{align}
+  |Z|^2\frac{\partial}{\partial |Z|^2}|Z|^2\frac{\partial}{\partial |Z|^2}
+  (1+|Z|^2)^{2S} &= \sum_{n=0}^{2S}n^2{}_{2S}\mathrm{C}_n|Z|^{2n} .
+\end{align}
+
+Next, we consider the multi-level case.
+For one-body operators, the extension from the single-level case is simple because we only sum over the index $l$ for the single-particle levels.
+For two-body operators, we need to give the new derivations basically.
+For the expectation value of $\hat{S}^+\hat{S}^-$,
+\begin{align}
+  \braket{Z|\hat{S}^+\hat{S}^-|Z} &= \sum_{l_1l_2}\braket{Z|\hat{S}_{l_2}^+\hat{S}_{l_1}^-|Z} .
+\end{align}
+When $l_2=l_1$, the form is the same as in (\ref{S+S-}). When $l_2\ne l_1$, from (\ref{S+}) and (\ref{S-}),
+\begin{align}
+  \braket{Z|S_{l_2}^+S_{l_1}^-|Z} = \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2} .
+\end{align}
+Therefore,
+\begin{align}
+    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_l 2S_l|Z_l|^2\frac{2S_l+|Z_l|^2}{(1+|Z_l|^2)^2}
+    + \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2} .
+\end{align}
+
+We conclude the useful formula for the spin-coherent state as follows.
+\begin{framed}
+  \begin{itemize}
+ \item Spin-coherent state 
+\begin{equation}
+	\ket{Z} = \prod_{l} \left(1+|Z_l|^2\right)^{-S_l}
+	e^{Z_l \hat{S}_l^{+}} \ket{S_l, S_l^0=-S_l} .
+ \label{coherent}
+\end{equation}
+ \item Normalization
+\begin{equation}
+	\braket{Z|Z} = 1
+\end{equation}
+ \item Overlap
+\begin{equation}
+	  \braket{\eta|Z} = \prod_l \frac{(1+\eta_l^*Z_l)^{2S_l}}{(1+|\eta_l|^2)^{S_l}(1+|Z_l|^2)^{S_l}} .
+  \label{overlap}
+\end{equation}
+ \item Expectation value of $\hat{S}^0$
+\begin{equation}
+     \braket{Z|\hat{S}^0|Z} = \sum_l S_l\left( 1-\frac{2}{1+|Z_l|^2} \right)
+\end{equation}
+ \item Expectation value of $\hat{S}^+$
+\begin{equation}
+     \braket{Z|\hat{S}^+|Z} = \sum_l \frac{2S_lZ_l^*}{1+|Z_l|^2}
+\end{equation}
+ \item Expectation value of $\hat{S}^-$
+\begin{equation}
+     \braket{Z|\hat{S}^-|Z} = \sum_l \frac{2S_lZ_l}{1+|Z_l|^2}
+\end{equation}
+ \item Expectation value of $\hat{S}^+\hat{S}^-$
+\begin{equation}
+    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_l 2S_l|Z_l|^2\frac{2S_l+|Z_l|^2}{(1+|Z_l|^2)^2}
+    + \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}
+\end{equation}
+\end{itemize}
+\end{framed}
+
+\section{Derivation of the path integral in spin-coherent state}
+We derive the path integral formulation for SU(2) spin-coherent state.
+First, we consider the case of one degree of freedom corresponding single-level system.
+Using the coherent state $\ket{Z}$, the time development from $t'$ to $t''$ of the system is described by the propagator
+\begin{align}
+  K(Z'',t'';Z',t') &= \braket{Z''|\exp \left\{-\frac{i}{\hbar}H(t''-t')\right\}|Z'} \\
+  &= \lim_{n \to \infty} \int \prod_{k=1}^{n-1}d\mu(Z_k)\prod_{k=1}^{n}
+  \braket{Z_k|\exp \left\{-\frac{i}{\hbar}H\epsilon\right\}|Z_{k-1}} ,
+  \label{propagator}
+\end{align}
+where we set $Z_n=Z''$, $Z_0=Z'$, and $\epsilon=\frac{t''-t'}{n}$.
+Because $\epsilon$ is infinitesimal quantity, we can expand (\ref{propagator}) with respect to $\epsilon$ up to first order
+\begin{align}
+  \braket{Z_k|\exp \left\{-\frac{i}{\hbar}H\epsilon\right\}|Z_{k-1}}
+  &\approx \braket{Z_k|1-\frac{i}{\hbar}\epsilon H|Z_{k-1}} \nonumber \\
+  &\approx \braket{Z_k|Z_{k-1}}\exp\left\{\frac{i}{\hbar}\epsilon
+  \frac{\braket{Z_k|H|Z_{k-1}}}{\braket{Z_k|Z_{k-1}}}\right\} \nonumber \\
+  &\approx \braket{Z_k|Z_{k-1}}\exp\left\{\frac{i}{\hbar}\epsilon
+  \braket{Z_k|H|Z_{k-1}}\right\} .
+\end{align}
+In addition, we expand the overlap up to first order
+\begin{align}
+  \braket{Z_k|Z_{k-1}} &= \exp (\log \kappa(Z_k,Z_k^*;Z_{k-1},Z_{k-1}^*)) \nonumber \\
+  &\approx \exp \left\{ \frac{i}{\hbar} \left(\frac{\hbar}{i} \left( 
+  \frac{\partial \kappa}{\partial Z_k}\Delta Z_k + \frac{\partial \kappa}{\partial Z_k^*}\Delta Z_k^*
+  \right) \right) \right\} ,
+\end{align}
+where we set $\Delta Z_k = Z_k - Z_{k-1} = \dot{Z_k}\epsilon$.
+Using (\ref{overlap}), the differentiations of $\kappa$ become
+\begin{align}
+  \left. \frac{\partial \kappa}{\partial Z_k} \right|_{Z_k=Z_{k-1}} &= -\frac{SZ_k^*}{1+|Z_k|^2}\\
+  \left. \frac{\partial \kappa}{\partial Z_k^*} \right|_{Z_k^*=Z_{k-1}^*} &= \frac{SZ_k}{1+|Z_k|^2}
+\end{align}
+Therefore, the propagator is written in path integral formulation
+\begin{align}
+    K(Z'',t'';Z',t') &= \int \mathcal{D}\mu(Z(t))e^{\frac{i}{\hbar}\mathcal{S}} \\
+     \mathcal{D}\mu(Z(t)) &= \lim_{n \to \infty} \prod_{k=1}^{n-1}d\mu(Z_k) \\
+    \mathcal{S} &= \int dt \left\{ \frac{i\hbar S}{1+|Z|^2}(Z^*\dot{Z}-Z\dot{Z^*})
+    -\braket{Z|H|Z} \right\}
+\end{align}
+
+The extension to the multi-level system is straightforward. The action $\mathcal{S}$ becomes
+\begin{equation}
+  \mathcal{S} = \int dt \left\{ i\hbar \sum_l \frac{S_l}{1+|Z_l|^2}
+  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{{\bf Z}|H|{\bf Z}} \right\} .
+\end{equation}
+
+\section{Action in canonical coordinates representation}
+
+\bibliographystyle{plain}
+\bibliography{ref}
+
 \end{document}

### 2018-10-17 thesis/thesis.tex
thesis

@@
 
-\title{Thesis}
+\title{Requantization of time-dependent mean field
+ for pairing collective motion in superfluid nuclei}
 \author{Fang Ni}
@@
 	E_{\nu}(N) = \epsilon N - \frac{1}{4}g(N-\nu)(2\Omega-N-\nu+2) .
+	\label{onelevel}
 \end{align}
@@
   S_l^0 &= \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l)
-  \label{S0}
+  \label{S_0}
 \end{align}
@@
 $\ket{\Phi_0}$ is generally chosen as ground state or vacuum state.
-$Z_{kk'}(t)$ is time-dependent complex number determined by TDHFB equation.\par
+$Z_{kk'}(t)$ is time-dependent complex number determined by TDHFB equation.
+
+\subsection{Hamilton's equation}
 We derive the TDHFB equation in pairing model.
@@
 \end{equation}
-Here, we choose $\ket{\Phi_0}=\ket{0}$ which is vacuum (zero particle) state. In the quasispin representation, $\ket{0}=\prod_l \ket{S_l,-S_l}$.
+Here, we choose $\ket{\Phi_0}=\ket{0}$ which is vacuum (zero particle) state.
+In the quasispin representation, $\ket{0}=\prod_l \ket{S_l,-S_l}$.
+The coherent state is the extension of BCS trail wave function, which consists of the superposition of different particle number states.
+$Z_l$ are complex numbers.
+$|Z_l|=0$ corresponds to empty occupation and $|Z_l|=\infty$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.\par
+ With the transformation $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$), the Lagrangian and the expectation value of Hamiltonian become
+\begin{align}
+	\mathcal{L}(t) =& \braket{Z(t)|i\hbar\frac{\partial}{\partial t}-H|Z(t)}
+	=\sum_l j_l\dot{\chi_l} - \mathcal{H}(\chi,j) ,\\
+	\mathcal{H}(\chi,j) \equiv& \braket{Z(t)|H|Z(t)} \nonumber \\
+	=& \sum_l \epsilon_l\nu_l + \sum_l 2\epsilon_lj_l - g\sum_l \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	&- 2g\sum_{l_1<l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   ,
+	\label{Hamiltonian}
+\end{align}
+where $\chi_l$ are the canonical coordinates and $j_l$ are the conjugate momenta defined in
+\begin{align}
+  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=S_l(1-\cos{\theta}_l) .
+  \label{momenta}
+\end{align}
+The detailed derivations are written in Appendix \ref{derivation}.
+The canonical variables $(\chi,j)$ have clear physical meaning.
+$\chi_l$ represent a kind of gauge angle of each level, and $j_l$ correspond to the occupation number of each level
+\begin{align}
+  \braket{Z|n_l|Z} = \nu_l + 2j_l .
+  \label{occ}
+\end{align}
+From (\ref{momenta}), we can find that $0\le j_l\le 2S_l$, where $j_l=0$ corresponds to empty occupation and $j_l=2S_l$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.
+Using canonical variables, the TDHFB equations attribute to the Hamilton's equations
+\begin{equation}
+	\dot{\chi_l} = \frac{\partial\mathcal{H}}{\partial j_l}, \quad
+	\dot{j_l} = -\frac{\partial\mathcal{H}}{\partial \chi_l} .
+\end{equation}
+
+\subsection{Constant of motion}
+\label{constant}
+The number of the TDHFB degrees of freedom is same as the number of the single-particle levels.
+However, because the Hamiltonian depends only on the relative difference in the gauge angles, the global gauge angle
+\begin{align}
+	\Phi = \frac{1}{L}\sum_l \chi_l
+\end{align}
+is a cyclic variable. With the definition for relative gauge angle (e.g. $\phi_l = \chi_l-\chi_1$), we can find that the conjugate momentum of $\Phi$ is the sum of $j_l$
+\begin{align}
+	J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} = \sum_l j_l .
+\end{align}
+From (\ref{occ}), $J$ is related to the total particle number
+\begin{align}
+	N = \sum_l \nu_l + 2J .
+\end{align}
+The Hamilton's equation for $J$
+\begin{align}
+	\dot{J} = -\frac{\partial\mathcal{H}}{\partial \dot{\Phi}} = 0, \quad J = {\rm const}
+\end{align}
+indicates that the total particle number is conserved in time evolution.
+The canonical variable $(\Phi,J)$ describes the pairing rotation.
+The pairing rotational band emerges in the particle number chain ($\cdots,N-2,N,N+2,\cdots$).
+The last term in (\ref{Hamiltonian}) contains the higher order terms with respect to $N$.
+It related to the shell effect.
+In single-level system, the last term in (\ref{Hamiltonian}) disappears and (\ref{Hamiltonian}) attributes to (\ref{onelevel}).
+The pairing rotational band is exactly parabolic.
+In multi-level system, the coupling constant $g$ and single-particle energy $\epsilon_l$ affects significantly to the last term in (\ref{Hamiltonian}).
+The parabolic structure can be broken when the shell effect is strong.
+
+In the analysis of TDHFB classical Hamiltonian, we can decouple the pairing rotational mode.
+The degrees of freedom is $L-1$ in $L$ level system.
+Therefore, the dynamics is integrable for $L=2$ and non-integrable for $L\le 3$ in multi-level pairing model.
+We discuss the integrable system and non-integrable system in Chapter \ref{integrable} and \ref{non-integrable}, respectively.
 
 \chapter{Requantization of TDHFB in integrable system}
+\label{integrable}
+As discussed in Sec. \ref{constant}, the TDHFB dynamics in two-level system is one-dimensional motion. We know that one-dimensional system must be integrable system. 
+There are two new discoveries obtained from the study of the integrable system.
+First, the requantization method, stationary phase approximation to the path integral, can be applied straightforward to describe the collective excited $0^+$ states.
+We find that SPA is superior to the other requantization methods, especially for the calculation of two-particle transition strength.
+Second, the collective coordinates are explicit in integrable system.
+Using the explicit collective coordinates, we can examine the performance of the collective model which assumes the pairing gap parameter as the collective coordinate.
+The conclusion is the pairing gap parameter can only describe a part of collective space, and the applicability of the collective model is limited.
 
 \section{TDHFB dynamics in two-level system}
+To describe the one-dimensional motion, we use the global gauge angle $\Phi$ and the relative gauge angle $\phi$ as canonical coordinates
+\begin{align}
+  \Phi &\equiv \frac{\chi_1 + \chi_2}{2}, \quad\quad
+  \phi\equiv \chi_2 - \chi_1.
+\label{phi}
+\end{align}
+These ranges are $0\leq \Phi \leq 2\pi$ and $-2\pi \leq \phi \leq 2\pi$. 
+Their conjugate momenta $(J,j)$ are given by
+\begin{align}
+	J = \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} =  \sum_{l=1}^2 j_l, 
+ \quad\quad
+j = \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \frac{j_2 - j_1}{2}.
+	\label{pi}
+\end{align}
+As in (\ref{occ}), $j$ corresponds to relative occupation number
+\begin{align}
+  j = \frac{\nu_{2}-\nu_{1}}{2} + \frac{n_{2}-n_{1}}{4}
+\end{align}
+The Hamiltonian in terms of these canonical variables
+$(\phi,j;\Phi,J)$ is given by
+\begin{align}
+	\mathcal{H}(\phi,j;J)
+	=& \sum_{l=1,2} \epsilon_l\nu_l + \sum_{l=1,2} 2\epsilon_lj_l - g\sum_{l=1,2} \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	&- 2g\sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})}\cos{\phi} , 
+\label{Hamiltonian2}
+\end{align}
+with 
+\begin{align}
+	j_1 = \frac{J}{2} - j, \quad\quad j_2 = \frac{J}{2} + j .
+\end{align}
+Because $J$ and the total energy $E$ constants of motion, the TDHFB trajectories with given $J$ and $E$ are determined
+in the two-dimensional phase space $(\phi,j)$ with the condition
+\begin{equation}
+  \mathcal{H}(\phi(t),j(t);J) = E.
+\end{equation}
+
+For convenience, we also define a dimensionless coupling constant in two-level system
+\begin{align}
+	x = \frac{\epsilon_2 - \epsilon_1}{2\Omega}
+\end{align}.
 
@@
 \chapter{Requantization of TDHFB in non-integrable system}
+\label{non-integrable}
 
@@
 \chapter{Detailed derivation of the action in pairing model}
+\label{derivation}
 To obtain the TDHFB dynamics in pairing model, We need to derive the action $\mathcal{S}$ in explicit form. We give the detailed derivation in this chapter.
@@
 \section{Properties of the spin-coherent state}
+\label{formula}
 The time-dependent coherent state classified into the spin-coherent state is employed in (\ref{coherent}). We derive the necessary formula for the spin-coherent state in this subsection. \par
@@
 \end{align}
+When $Z$ is time-dependent, the expectation value of $\frac{\partial}{\partial t}$ is also important quantity.
+\begin{align}
+   \braket{Z|\frac{\partial}{\partial t}|Z} &= \braket{Z|\dot{Z}\frac{\partial}{\partial Z}+\dot{Z}^*\frac{\partial}{\partial Z^*}|Z} \nonumber \\
+   &= -\frac{S}{1+|Z|^2}(Z^*\dot{Z}+Z\dot{Z^*}) + \dot{Z}\braket{Z|\hat{S}^+|Z} \nonumber \\
+   &= \frac{S}{1+|Z|^2}(Z^*\dot{Z}-Z\dot{Z^*})
+\end{align}
+From the second line to the third line, we used (\ref{S+}).
 
@@
 \end{equation}
+ \item Expectation value of $\frac{\partial}{\partial t}$
+\begin{equation}
+       \braket{Z|\frac{\partial}{\partial t}|Z} = \sum_l \frac{S_l}{1+|Z_l|^2}(Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*})
+	\label{ddt}
+\end{equation}
 \end{itemize}
@@
 \end{align}
+Of course, the action $\mathcal{S}$ is identical to the definition
+\begin{align}
+  \mathcal{S} = \int dt \braket{Z|i\hbar\frac{\partial}{\partial t}-H|Z} .
+\end{align}
+It can be easily checked by using (\ref{ddt}).
 
@@
 \begin{equation}
-  \mathcal{S} = \int dt \left\{ i\hbar \sum_l \frac{S_l}{1+|Z_l|^2}
-  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{{\bf Z}|H|{\bf Z}} \right\} .
+  \mathcal{S} = \int \mathcal{L}(t) dt, \quad 
+  \mathcal{L}(t) =i\hbar \sum_l \frac{S_l}{1+|Z_l|^2}
+  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{Z|H|Z}
 \end{equation}
 
-\section{Action in canonical coordinates representation}
+\section{Action in canonical variables representation}
+We derived the action in the previous section. Using the formula in Sec. \ref{formula}, the expectation value of pairing Hamiltonian is
+\begin{align}
+  \braket{Z|H|Z} =& \sum_l \epsilon_l \left\{ 2S_l\left( 1-\frac{2}{1+|Z_l|^2} \right) + \Omega_l \right\} \nonumber \\
+   &- g\sum_l 2S_l|Z_l|^2\frac{2S_l+|Z_l|^2}{(1+|Z_l|^2)^2}
+    + \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2} .
+\end{align}
+To obtain more tractable form of the action, we transform the complex variables $Z_l$ into real variables $(\theta_l,\chi_l)$
+by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$). The Lagrangian becomes
+\begin{align}
+\mathcal{L}(t) = \sum_l S_l
+	(1-\cos{\theta_l})\dot{\chi_l} - \braket{Z|H|Z} .
+\end{align}
+If we choose the $\chi_l$ as canonical coordinates, the conjugate momenta $j_l$ are given by
+\begin{align}
+  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=S_l(1-\cos{\theta}_l) .
+\end{align}
+Therefore, the Lagrangian in canonical variables representation becomes
+\begin{align}
+	\mathcal{L}(t) =& \sum_l j_l\dot{\chi_l} - \mathcal{H}(\chi,j) ,\\
+	\mathcal{H}(\chi,j) \equiv& \braket{Z|H|Z} \nonumber \\
+	=& \sum_l \epsilon_l\nu_l + \sum_l 2\epsilon_lj_l - g\sum_l \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	&- g\sum_{l_1\le l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   .
+\end{align}
 

### 2018-10-18 paper2/draft1-2.tex
darft1-2

--- 2018-10-12 paper2/draft1-1.tex
@@
 
-\title{Low-lying collective excited states in non-integrable system based on stationary phase approximation to the path integral}%
+\title{Low-lying collective excited states in non-integrable pairing models
+based on stationary phase approximation to the path integral}%
 
@@
 \begin{abstract}
-To describe the large amplitude collective motion in nuclear pairing, stationary phase approximation to the path integral (SPA) is supposed to be the most reliable requantization approach of time-dependent mean-field dynamics.
-The disadvantage of SPA is that it only available in integrable system.
-However, we overcome the disadvantage by combining SPA with adiabatic self-consistent collective coordinate method (ASCC).
-We construct the theoretical framework of  ASCC+SPA and demonstrate the application to the multi-level pairing model which is non-integrable system.
-As with the performance in integrable system, we find that SPA also gives reasonable information about low-lying excited $0^+$ states in non-integrable system.
+For a description of large amplitude collective motion associated with
+nuclear pairing, requantization of time-dependent mean-field dynamics
+is performed using the stationary phase approximation (SPA) to the path
+integral.
+A disadvantage of the SPA is that it is applicable only to integrable systems.
+We overcome this difficulty by developing a requantization approach
+combining the SPA with the adiabatic
+self-consistent collective coordinate method (ASCC+SPA).
+We apply the theoretical framework of ASCC+SPA to 
+a multi-level pairing models, which is non-integrable systems,
+to study the nuclear pairing dynamics.
+The ASCC+SPA gives a reasonable description of low-lying excited $0^+$
+states in non-integrable pairing systems.
 %\begin{description}
@@
 %pairing in nuclei
-Pairing correlation plays an important role around the surface in open-shell nuclei.
-The properties of pairing for the ground states are well known such as odd-even mass difference, moment of inertia of rotational bands, and the quantum numbers for spin and parity \cite{RS80}.
-The elementary excitations of pairing, pairing vibrations and pairing rotations, are fascinating phenomena not only for open-shell nuclei, but also for closed-shell nuclei \cite{BB05}.
-However, the pairing dynamics still has unclear features in low-energy region (a few MeV excitation) of nuclei, especially for excited $J^{\pi}=0^+$ states \cite{HW11, G01}.
-We aim to understand the dynamics from pairing correlation in nuclei from microscopic many-body theory.\par
-%TDMF theory for pairing
-Time-dependent mean-field (TDMF) theory is the common theory to describe the dynamics of nuclei from the microscopic degrees of freedom.
-Including pairing correlation, time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, corresponding to TDMF theory, is utilized for plenty of studies for both nuclear reaction and nuclear structure fields \cite{NMMY16}.
-In nuclear structure aspect, the harmonic approximation of TDHFB, quasiparticle random phase approximation (QRPA), can well describe the giant resonance of nuclei.
-Recently, the adiabatic approximations of TDHFB, such as adiabatic TDHFB (ATDHFB), adiabatic self-consistent collective coordinate method (ASCC), and 5D Bohr Hamiltonian constructed from microscopic degrees of freedom, is developed and start to be applied to low-lying excited states.
-They are expected to elucidate the large amplitude collective motions occurred in the structure, such as shape coexistence and anharmonic vibration.
-\par
+Pairing correlation plays an important role in open-shell nuclei.
+Effect of the pairing is prominent in many observables for the ground states,
+such as odd-even mass difference, moment of inertia of rotational bands,
+and common quantum number $J^\pi=0^+$ for even-even nuclei \cite{RS80}.
+Elementary excitations associated with the pairing,
+pairing vibrations and pairing rotations,
+have been observed in a number of nuclei \cite{BB05}.
+Most of these states, ``excited'' from neghboring even-even systems,
+are associated with the ground $J^\pi=0^+$ states in even-even nuclei.
+In contrast, properties of excited $J^{\pi}=0^+$ states are not clearly
+understood yet \cite{HW11, G01}, for which the pairing dynamics plays
+an important role in a low-energy region (a few MeV excitation) of nuclei. 
+In this paper,
+we aim to understand the dynamics from pairing correlation in nuclei
+from microscopic view point.
+
+%TDMF theory and ASCC
+The time-dependent mean-field (TDMF) theory is a standard theory to describe
+the dynamics of nuclei from the microscopic degrees of freedom.
+Inclusion of the pairing dynamcs leads to the
+time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory,
+which has been utilized for a number of studies of nuclear reaction
+and structure \cite{NMMY16}.
+The small-amplitude approximation of TDHFB with modern energy density
+functionals, quasiparticle random phase approximation (QRPA), 
+has successfully reproduced properties of giant resonances in nuclei.
+In contrast, the QRPA description of low-lying quadrupole vibrations
+is not as good as the giant resonances \cite{NMMY16}.
+A large-amplitude nature of the quantum shape fluctuation is supposed to
+be important for these low-lying collective states.
+Five-dimensional collective Hamiltonian (5DCH) approaches
+have been developed for studies of low-lying quadrupole states,
+in which the collective Hamiltonian is constructed from
+microscopic degrees of freedom using the mean-field calculation and
+the cranking inertia formula \cite{???}.
+The 5DCH model is able to take into account fluctuations of
+the quadrupole shape degrees of freedom which are important in many
+nuclear low-energy phenomena, such as
+shape coexistence and anharmonic quadrupole vibration.
+However, the calculated inertia is often too small to reproduce
+experimental data, due to the lack of time-odd components
+in the cranking formula \cite{RS80}.
+This deficiency can be remedied in the adiabatic self-consistent collective
+coordinate (ASCC) method \cite{MNM00},
+in which the time-odd effect is properly treated.
+In addition, the ASCC method enables us to identify a collective subspace
+of interest.
+The ASCC was developed from the basic idea of self-consistent
+collective coordinate method (SCC) by Marumori and coworkers \cite{MMSK80}.
+It has been applied to the nuclear quadrupole dynamics including
+the shape coexistence \cite{KNMM05, HNMM07, HNMM08}.
+%A state in the collective subspace corresponds to a microscopic state
+%in TDHFB phase space connected by $Q$ and $P$ operators in ASCC.
+
 %previous work
-TDMF (TDHFB) theory corresponds to a stationary-limit in the path integral formulation.
-It lacks a part of the information about quantum fluctuation, which is remarkable in the large amplitude dynamics.
-To introduce the quantum fluctuation based on the TDHFB theory, the requantization process is necessary \cite{Neg82, L80, LNP80, Rei80, KS80, K81}.
-The straightforward requantization method is canonical quantization.
-In 5D Bohr Hamiltonian, the canonical quantization was formulated and employed for the study of low-lying excited states in nuclei.
-In additional, it was also utilized to describe the large amplitude dynamics for pairing in pairing model \cite{BBPK70, GPBW85, ZPPRS99, P07}.
-However, the Hilbert space which the wave function obtained from canonical quantization belongs to is quite different from the Hilbert space which the original wave function belongs to.
+TDMF (TDHFB) theory corresponds to an SPA solution in the path integral
+formulation \cite{Neg82}.
+It lacks a part of quantum fluctuation
+important in the large amplitude dynamics.
+To introduce the quantum fluctuation based on the TDHFB theory,
+the requantization is necessary \cite{Neg82,L80,LNP80,Rei80,KS80,K81}.
+A simple and straightforward way of requantization is
+the canonical quantization.
+This is extensively utilized for collective models in nuclear physics.
+For instance,
+the canonical quantization of the 5DCH was employed for the study of low-lying
+excited states in nuclei \cite{???}.
+The similar quantization was also utilized for the pairing collective
+Hamiltonian \cite{BBPK70, GPBW85, ZPPRS99, P07}.
+%However, the Hilbert space which the wave function obtained from canonical quantization belongs to is quite different from the Hilbert space which the original wave function belongs to.
 It may cause the deviation for the requantized states.
-In our previous work, we studied the requantization of the TDHFB.
-We investigated the low-lying excited $0^+$ states in two-level pairing model by various requantization methods \cite{NN18}.
-Comparing with exact solution, we found that stationary phase approximation to the path integral (SPA) \cite{SM88} can give quantitatively results not only for the excitation energies, but also for the wave functions.
-We confirmed that SPA is superior to canonical requantization, especially for the calculation of two-particle transitional strength.
-The wave function obtained from SPA has two advantages: first, it is written in the (quasi)particle's degrees of freedom; second, it has good quantum number because the projection of the conservation quantities (e.g.
-total particle number, total angular momentum) are automatically contained.
-On the other hand, the disadvantage is that SPA only works in integrable systems.
-Due to the nuclear system is non-integrable system in general, we cannot employ SPA straightforward for the realistic system.
-\par
+In our previous work \cite{NN18},
+we studied various requantization methods for the two-level pair model,
+to investigate low-lying excited $0^+$ states.
+Since the collectivity is rather low in the pairing motion in nuclei,
+the canonical quantization often fails to produce an approximate answer
+to the exact solution.
+In contrast,
+the stationary phase approximation (SPA) to the path integral \cite{SM88} 
+can give quantitative results not only for the excitation energies, 
+but also for the wave functions and two-particle-transfer strengths.
+%We confirmed that SPA is superior to canonical requantization, especially for the calculation of two-particle transitional strength. 
+The quantized states obtained in the SPA has two advantages:
+First, the wave functions are given directly in terms of
+the microscopic degrees of freedom.
+Second, the restoration of broken symmetries are automatic.
+In the pair model, the quantized states are eigenstates of the particle number
+operator.
+On the other hand, applications of the SPA has been limited to
+integrable systems.
+This is because we need to find separable periodic trajectories on a classical
+torus.
+Since the nuclear systems, of course, correspond to non-integrable systems,
+a straightforward application of the SPA is not possible.
+
 %this work
-We discuss the application of SPA for the non-integrable system in this paper.
-We know that the one-dimensional system is integrable system.
-It is desirable that a collective motion can be described by one collective coordinate.
-To obtain the one-dimensional subspace, adiabatic self-consistent collective coordinate method (ASCC) is powerful tool \cite{MNM00}.
-``Adiabatic'' indicates that the collective motion is slow compared with the single-particle motion.
-The collective degree of freedom is determined self-consistently from the TDHFB degrees of freedom without any assumption.
-The ASCC, which was developed from the basic idea of self-consistent collective coordinate method (SCC) \cite{MMSK80}, is flexible to deal with various collective potential, such as shape coexistence \cite{KNMM05, HNMM07, HNMM08}.
-A state in the collective subspace corresponds to a microscopic state in TDHFB phase space connected by $Q$ and $P$ operators in ASCC.
-This correspondence make us possible to apply SPA to non-integrable system.
-We construct the theoretical framework of ASCC+SPA, which implements SPA to non-integrable system by combing with ASCC.
-The first study of ASCC+SPA give us a new landscape about the large-amplitude dynamics in low-energy region.
+In this paper,
+we propose a new approach of SPA applicable to the non-integrable systems,
+which is based on the extraction of the one-dimensional (1D)
+collective coordinate
+using the ASCC method.
+Since the 1D system is integrable,
+the collective subspace can be quantized with the SPA.
+%It is desirable that a collective motion can be described by one collective coordinate. 
+%To obtain the one-dimensional subspace, adiabatic self-consistent collective coordinate method (ASCC) is powerful tool \cite{MNM00}.
+%``Adiabatic'' indicates that the collective motion is slow compared with the single-particle motion. 
+The optimal degree of freedom associated with a slow collective motion
+is determined self-consistently
+inside the TDHFB space, without any assumption. 
+Thus, our approach of ASCC+SPA to the pairing model
+basically consists of two steps:
+(1) Find a decoupled 1D collective coordinate of the pair vibration,
+in addition to the pair rotational degrees of freedom.
+(2) Apply the SPA separately to each collective mode.
+%which implements SPA to non-integrable system by combing with ASCC. 
+%The first study of ASCC+SPA give us a new landscape about
+%the large-amplitude dynamics in low-energy region.
 
@@
 The paper is organized as follows. 
-Sec.
-\ref{sec2} introduces the theoretical framework of ASCC and the combination, ASCC+SPA.
-Sec.
-\ref{sec3} is the application of ASCC+SPA in multi-level pairing model.
-We give the numerical results in Sec.
-\ref{sec4}, including two-level systems, three-level systems, and Pb isotope systems.
-The conclusion and the remaining problems are shown in Sec.
-\ref{sec5}.
+Sec. \ref{sec2} introduces the theoretical framework of ASCC, SPA,
+and their combination, ASCC+SPA. 
+In Sec. \ref{sec3}, we provide some details in the application
+of ASCC+SPA to the multi-level pairing model.
+We give the numerical results in Sec. \ref{sec4}, including
+neutron pair vibrations in Pb isotopes.
+The conclusion and future perspectives are given in Sec. \ref{sec5}.
 
@@
 
-\subsection{One-dimensional adiabatic self-consistent collective coordinate method}
+\subsection{Adiabatic self-consistent collective coordinate method and
+1D collective subspace}
 \label{ASCC}
-To discuss the application of ASCC+SPA in the later subsection, we review the one-dimensional adiabatic self-consistent collective coordinate method (ASCC) briefly using the notation in Ref.
-\cite{N2012}.
-The classical Hamilton's equation which is identical to the TDHFB equation is described by canonical variables $\{\xi^{\alpha},\pi_{\alpha}\}$.
-If we apply the adiabatic approximation which assume that the collective motion is slow compared with the single-particle motion, we can  expand the momenta $\pi$ up to second order.
-The multi-dimensional Hamiltonian is
+%To discuss the application of ASCC+SPA in the later subsection, 
+In this section,
+we first recapitulate the ASCC method to find a 1D collective coordinate,
+following the notation of Ref. \cite{N2012}.
+
+As is seen in Sec.~\ref{sec3}, the TDHFB equations can be
+interpreted as the classical Hamilton's equations of motion
+%The classical Hamilton's equation which is identical to the TDHFB equation is described by
+with canonical variables $\{\xi^{\alpha},\pi_{\alpha}\}$. 
+Each point in the phase space $(\xi^{\alpha},\pi_{\alpha})$
+corresponds to a generalized Slater determinant (coherent state).
+Assuming slow collective motion,
+we expand the Hamiltonian $\mathcal{H}(\xi,\pi)$ with respect to
+momenta $\pi$ up to second order.
+The TDHFB Hamiltonian is
 \begin{align}
@@
 \end{align}
-with potential $V(\xi)$ and reciprocal mass parameter $B^{\alpha\beta}(\xi)$ defined by
-\begin{align}
-  V(\xi) &= \mathcal{H}(\xi,\pi=0) \\
+with the potential $V(\xi)$ and
+the reciprocal mass parameter $B^{\alpha\beta}(\xi)$ defined by
+\begin{align}
+  V(\xi) &= \mathcal{H}(\xi,\pi=0) , \\
   B^{\alpha\beta}(\xi) &= \left. \frac{\partial^2\mathcal{H}(\xi,\pi)}{\partial\pi_{\alpha}\partial\pi_{\beta}} \right|_{\pi=0}.
 \end{align}
- If there is a one-dimensional collective motion which is decoupled from other intrinsic motions, the collective motion can be described by a set of canonical variable $\{q,p\}$, the one dimensional collective Hamiltonian is
-\begin{align}
-  \mathcal{H}_{coll} &= \bar{V}(q) + \frac{1}{2}\bar{B}^{-1}(q)p^2.
+
+For multi-level pairing models in Sec.~\ref{sec3}, 
+there is a constant of motion in the TDHFB dynamics,
+namely the average particle number $q^n\equiv \langle N \rangle/2$.
+Since the particle number $N$ is time-even Hermitian operator, we treat
+this as a coordinate, and its conjugate gauge angle, $p_n$,
+as a momentum.
+Since $q^n$ is a constant of motion, the Hamiltonian does not
+depend on $p_n$.
+On the other hand, the gauge angle $p_n$ changes in time,
+which corresponds to the pair rotation, a Nambu-Goldstone (NG) mode
+associated with the breaking of the gauge (particle-number) symmetry.
+We assume the existence of 2D collective subspace $\Sigma_2$,
+described by a set of canonical variable $(q^1,q^n;p_1,p_n)$,
+which is well decoupled from the rest of degrees of freedom,
+$\{q^a,p_a\}$ with $a=2,\cdots$.
+The collective Hamiltonian is given by imposing $q^a=p_a=0$,
+namely by restricing the space into the collective subspace.
+\begin{equation}
+%\mathcal{H}_{\rm coll}(q,p) &= \bar{V}(q) + \frac{1}{2}\bar{B}^{-1}(q)p^2 .
+\mathcal{H}_{\rm coll}(q,p;q^n)
+= \bar{V}(q^1;q^n) + \frac{1}{2}\bar{B}^{11}(q^1,q^n)p_1^2 .
   \label{coll}
-\end{align}
-To obtain the collective Hamiltonian, we need to consider extended adiabatic transformation
-\begin{align}
-  q = q^1 &= f^1(\xi) + \frac{1}{2}f^{(1)1\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}  \label{point}\\
- \xi^{\alpha} &= g^{\alpha}(q) + \frac{1}{2}g^{(1)\alpha 1 1}(\xi)p_{1}p_{1}
-\end{align}
-and
-\begin{align}
-  p_1 &= g_{,1}^{\alpha}\pi_{\alpha} \\
- \pi_{\alpha} &= f^1_{,\alpha}p_1 ,
+\end{equation}
+Since there exist two conserved quantities, $q^n$ and $\mathcal{H}_{\rm coll}$,
+this 2D system is integrable.
+We can treat the collective motion of $(q^1,p_1)$ separately from
+the pair rotation $(q^n, p_n)$.
+
+In the collective Hamiltonian (\ref{coll}), the variable $q^n$ is
+trivially given as the particle number, which is expanded up to the
+second order in momenta $\pi$,
+\begin{equation}
+q^n=\frac{\langle N \rangle}{2} = f^n(\xi)
+	+\frac{1}{2}f^{(1)n\alpha\beta}\pi_\alpha\pi_\beta .
+	\label{q^n}
+\end{equation}
+To obtain the non-trivial collective variables
+$(q^1,p_1)$, we assume the point transformation\footnote{
+We may lift the restriction to the point transformation,
+as Eq. (\ref{q^n}) \cite{Sat18}.
+In this paper, we neglect these higher-order terms, such as
+$f^{(1)1\alpha\beta}\pi_\alpha\pi_\beta/2$.
+},
+\begin{equation}
+%  q = q^1 &= f^1(\xi) + \frac{1}{2}f^{(1)1\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}  \label{point}\\
+  q^1 = f^1(\xi) \label{point} ,
+% \xi^{\alpha} &= g^{\alpha}(q) + \frac{1}{2}g^{(1)\alpha 1 1}(\xi)p_{1}p_{1}
+\end{equation}
+and $\xi^\alpha$ on the subspace $\Sigma_2$ is given as
+$\xi^{\alpha} = g^{\alpha}(q^1,q_n,q^a=0)$.
+The momenta on $\Sigma_2$ are transformed as
+\begin{align}
+p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha \\
+\pi_{\alpha} &= f^1_{,\alpha}p_1 +f^n_{,\alpha}p_n,
  \label{momenta}
 \end{align}
-where the index $1$ indicates the collective degree of freedom, and the comma indicates the partial derivative $(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$.
-The canonical coordinates fulfill the canonicity
-\begin{align}
-  f^1_{,\alpha}g_{,1}^{\beta} = \delta^{\beta}_{\alpha}, \quad f^1_{,\alpha}g_{,1}^{\alpha} = 1.
+where the comma indicates the partial derivative
+$(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
+The Einstein's convention for summation with respect to repeated
+upper and lower indices is assumed hereafter.
+The canonical variable condition leads to
+\begin{align}
+ %f^1_{,\alpha}g_{,1}^{\beta} = \delta^{\beta}_{\alpha}, \quad 
+f^i_{,\alpha}g_{,j}^{\alpha} = \delta^i_j,
   \label{canonicity}
 \end{align}
-With these relations, collective potential $\bar{V}(q)$ and collective mass parameter $\bar{B}(q)$ can be transformed by
-\begin{align}
-  \bar{V}(q) &= V(\xi) \\
-  \bar{B}^{-1}(q) &= f^1_{,\alpha}B^{\alpha\beta}(\xi)f^1_{,\beta} ,
+where $i,j=1$ and $n$.
+The collective potential $\bar{V}(q^1,q^n)$ and
+the collective mass parameter
+$\bar{B}_{11}(q^1,q^n)=(\bar{B}^{11}(q^1,q^n))^{-1}$ can be given by
+\begin{align}
+\bar{V}(q^1,q^n) &= V(\xi=g(q^1,q^n,q^a=0)) \\
+\bar{B}^{11}(q^1,q^n) &= f^1_{,\alpha}\tilde{B}^{\alpha\beta}(\xi)f^1_{,\beta} ,
   \label{coll_mass}
 \end{align}
-
-Before showing the ASCC basic equations, we consider the constants of motion in TDHFB dynamics.
+where $\tilde{B}^{\alpha\beta}$ are defined as
+\begin{align}
+ \tilde{B}^{\alpha\beta}(\xi)
+%&= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
+&= B^{\alpha\beta}(\xi) - \bar{V}_{,n} f^{(1)n\alpha\beta}(\xi)
+%- \lambda_1 f^{(1)1\alpha\beta}(\xi) 
+\label{tildeB}.
+\end{align}
+
+%Before showing the ASCC basic equations, we consider the constants of motion in TDHFB dynamics.
 Since nuclei is self-bound systems without external potential, the ground state obtained from mean-field theory violates the symmetry (e.g.
@@
 Therefore, we are mostly interested in the systems with collective motion separated from NG mode.\par
-We know that the most of conserved quantities, such as total angular momentum $J$ and total particle number $N$, are not only expressed by one-body Hermitian operators, but also has real matrix elements in the quasi-particle basis.
+%We know that the most of conserved quantities, such as total angular momentum $J$ and total particle number $N$, are not only expressed by one-body Hermitian operators, but also has real matrix elements in the quasi-particle basis.
 Such classical variable $\mathcal{P}$ corresponding to the conserved quantity can be expanded as
-\begin{align}
-  \mathcal{P}(\xi,\pi) = f^I(\xi) + \frac{1}{2}f^{(1)I\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta} . \label{P}
-\end{align}
-The index $I$ indicates the degree of freedom for NG mode. Since the conserved quantity must fulfill $\{\mathcal{P},\mathcal{H}\}_{PB}=0$, it leads
-\begin{align}
-  f^{I}_{,\alpha}B^{\alpha\beta} - f^{(1)I\alpha\beta}V_{,\alpha} = 0.
-  \label{P_PB}
-\end{align}
-
-Including the NG mode, $f^1(\xi)$ and $g^{\alpha}(q)$ are obtained by solving ASCC basic equations 
+%\begin{align}
+%  \mathcal{P}(\xi,\pi) = f^I(\xi) + \frac{1}{2}f^{(1)I\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta} . \label{P}
+%\end{align}
+%The index $I$ indicates the degree of freedom for NG mode. Since the conserved quantity must fulfill $\{\mathcal{P},\mathcal{H}\}_{PB}=0$, it leads
+%\begin{align}
+%  f^{I}_{,\alpha}B^{\alpha\beta} - f^{(1)I\alpha\beta}V_{,\alpha} = 0.
+%  \label{P_PB}
+%\end{align}
+
+Decoupling conditions for the collective subspace $\Sigma_2$ lead to
+the basic equations of ASCC method \cite{MNM00,N2012},
+which determine tangential vectors,
+$f^1_{,\alpha}(\xi)$ and $g_{,1}^{\alpha}(q)$.
 \begin{align}
   &\delta H_M(\xi,\pi) = 0 \label{mfHFB} \\ 
-  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
-  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
+%  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
+%  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
+\mathcal{M}^\beta_\alpha f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
+\mathcal{M}^\beta_\alpha g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
   \label{mfQRPA}
 \end{align}
-The first equation (\ref{mfHFB}) is called moving-frame HFB equation. The moving-frame Hamiltonian $\mathcal{H}_M$ with constraints on collective coordinate and constant of motion is
-\begin{align}
-  \mathcal{H}_M(\xi,\pi) &= \mathcal{H}(\xi,\pi) -\lambda_1 q^1(\xi,\pi) - \lambda_I \mathcal{P}(\xi,\pi) .
-\end{align}
-The second equation (\ref{mfQRPA}) is called moving-frame QRPA equation. $\tilde{B}^{\alpha\beta}$ is the modified mass parameter
-\begin{align}
-  \tilde{B}^{\alpha\beta}(\xi) &= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
-&= B^{\alpha\beta}(\xi) - \lambda_I f^{(1)I\alpha\beta}(\xi) - \lambda_1 f^{(1)1\alpha\beta}(\xi) \label{tildeB}.
-\end{align} 
-and the covariant derivative $V_{;\gamma\alpha}$ is defined by
-\begin{align}
- V_{;\alpha\beta} = V_{,\alpha\beta} - \Gamma^{\gamma}_{\alpha\beta}V_{,\gamma} , \label{covariant}
-\end{align}
-where the affine connection is $\Gamma^{\alpha}_{\beta\gamma}=\frac{1}{2}B^{\alpha\delta}(B_{\delta\beta,\gamma}+B_{\delta\gamma,\beta}-B_{\beta\gamma,\delta})$.
-If we assume that the collective coordinate $q$ is geodesic, $\tilde{B}^{\beta\gamma}V_{;\gamma\alpha}$ can be simplified after several steps
- \begin{align}
-\tilde{B}^{\alpha\gamma}V_{;\gamma\beta} = \tilde{B}^{\alpha\gamma}(V_{,\gamma\beta}-\lambda_If^I_{,\gamma\beta}) + \frac{1}{2}\tilde{B}^{\alpha\gamma}_{,\beta}V_{,\gamma} 
+The first equation (\ref{mfHFB}) is called moving-frame HFB equation.
+The moving-frame Hamiltonian $\mathcal{H}_M$
+%with constraints on collective coordinate and constant of motion
+is
+\begin{align}
+\mathcal{H}_M(\xi,\pi) &= \mathcal{H}(\xi,\pi)
+	-\lambda_{1} q^1(\xi) - \lambda_{n} q^n(\xi,\pi) .
+\end{align}
+The second equation (\ref{mfQRPA}) is called moving-frame QRPA equation.
+%$\tilde{B}^{\alpha\beta}$ is the modified mass parameter
+%\begin{align}
+% \tilde{B}^{\alpha\beta}(\xi) &= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
+%&= B^{\alpha\beta}(\xi) - \bar{V}_{,n} f^{(1)n\alpha\beta}(\xi)
+%- \lambda_1 f^{(1)1\alpha\beta}(\xi) 
+%\label{tildeB}.
+%\end{align} 
+%and the covariant derivative $V_{;\gamma\alpha}$ is defined by
+%\begin{align}
+% V_{;\alpha\beta} = V_{,\alpha\beta} - \Gamma^{\gamma}_{\alpha\beta}V_{,\gamma} , \label{covariant}
+%\end{align}
+%where the affine connection is
+%\begin{equation}
+%\Gamma^{\alpha}_{\beta\gamma}=\frac{1}{2}B^{\alpha\delta}(B_{\delta\beta,\gamma}+B_{\delta\gamma,\beta}-B_{\beta\gamma,\delta}).
+%\end{equation}
+%If we assume that the collective coordinate $q$ is geodesic, 
+The matrix $\mathcal{M}^\beta_\alpha$ in the moving-frame QRPA
+equation (\ref{mfQRPA}) can be rewritten as 
+ \begin{align}
+\mathcal{M}^{\beta}_{\alpha} =
+	 \tilde{B}^{\beta\gamma}
+	 \left(V_{,\gamma\alpha}-\lambda_{n}f^n_{,\gamma\alpha}\right)
+	+ \frac{1}{2}\tilde{B}^{\beta\gamma}_{,\alpha}V_{,\gamma} 
 \label{M}.
 \end{align}
-
-We discuss the practical solution to derive the one-dimensional collective coordinate.
+The NG mode, $f^n_{,\alpha}$ and $g^\alpha_{,n}$, corresponds to
+the zero mode with $\omega^2=0$.
+Therefore, the collective mode of our interest corresponds to
+the mode with the lowest frequency except for the zero mode.
+
+%We discuss the practical solution to derive the one-dimensional collective coordinate.
 We neglect $f^{(1)1\alpha\beta}(\xi)$ because it is supposed to be negligibly small in the previous study.
@@
 In most of case, we know the explicit form of $\mathcal{P}(\xi,\pi)$.
-The procedures to obtain the collective path are:
+In practice, we obtain the collective path according to the following procedure:
 \begin{enumerate}
-\item Find the energy minimum point in energy surface by solving (\ref{mfHFB}) (normal HFB equation). We usually set $q^1=0$ at the energy minimum point.
-\item Using (\ref{M}), diagonalize (\ref{mfQRPA}) and choose the lowest mode basically.%\footnote{
+\item Find the HFB minimum point $\xi^\alpha_n$ ($n=0$)
+	by solving Eq. (\ref{mfHFB}) with $\lambda_1=0$.
+	Let us assume that this corresponds to $q^1_n=0$.
+\item \label{step-2}
+	Diagonalize the matrix $\mathcal{M}^{\beta}_{\alpha}$
+to solve Eq.~(\ref{mfQRPA}) using Eq.~(\ref{M}).
+%Then, choose a mode with the lowest frequency $\omega^2$
+%as $f^1_{,\alpha}$ and $g^\alpha_{,1}$.
+%\footnote{
 %When eigenvalues cross on the collective path, the choice of adiabatic path or diabatic path is a critical problem}. 
-\item The right eigenvector $g^{\alpha}_{,1}$ tell us the direction which system moves in energy surface.
-Use the relation $d\xi^{\alpha}=g^{\alpha}_{,1}dq^1$ to decide the neighborhood point $q^1\to q^1+dq^1$ in the collective path.
-\item Using $f^1_{,\alpha}$, find the non-equilibrium energy minimum point by solving (\ref{mfHFB}) at the neighborhood point.
-We usually use the constraint condition $dq=f^1_{,\alpha}(\xi^{\alpha}(q)-\xi^{\alpha}(q-dq))$ from the canonicity (\ref{canonicity}).
-After convergence, we diagonalize (\ref{mfQRPA}) and obtain the corrected $f^1_{,\alpha}$.
-\item Iterate (4) until the convergence of $f^1_{,\alpha}$.  
-\item Iterate (2)$\sim$(5) to decide the collective path under the same direction in the energy surface. 
-\item Implement (2)$\sim$(6) for the opposite direction of the collective path in energy surface. 
+\item \label{step-3}
+%The right eigenvector $g^{\alpha}_{,1}$ tell us the direction which system moves in energy surface. 
+Move to the next meighboring point
+$\xi^\alpha_{n+1}=\xi^\alpha_{n}+d\xi^\alpha$
+with $d\xi^{\alpha}=g^{\alpha}_{,1}dq^1$.
+This corresponds to the collective coordinate, $q^1_{n+1}=q^1_n+dq^1$.
+\item \label{step-4}
+At $\xi_{n+1}^\alpha$ $(q^1_{n+1})$,
+obtain a self-consistent solution of
+Eqs. (\ref{mfQRPA}) and (\ref{mfHFB}),
+to determine
+$\xi^\alpha_{n+1}$, $f^1_{,\alpha}$, and $g^\alpha_{,1}$.
+\item Go back to \ref{step-3} to determine the next point
+on the collective path.
+%\item Iterate (2)$\sim$(5) to decide the collective path under the same direction in the energy surface. 
+%\item Implement (2)$\sim$(6) for the opposite direction of the collective path in energy surface. 
 \end{enumerate}
-The scale of the collective coordinate is not unique because of the uncertainty of the eigenvectors in (\ref{mfQRPA}).
+We repeat this procedure with $dq^1 > 0$ and $dq^1<0$, and
+construct the collective path.
+In Step~\ref{step-2} and \ref{step-4}, we choose a mode
+with the lowest frequency $\omega^2$.
+Note that $\omega^2$ can be negative.
+In Step \ref{step-4}, when we solve Eq.~(\ref{mfHFB}), we use
+a constraint on the magnitude of $dq^1=f^1_{,\alpha}d\xi^{\alpha}$.
+Since the normalization of $f^1_{,\alpha}$ and $g^\alpha_{,1}$ is
+arbitrary as far as they satisfy Eq. (\ref{canonicity}).
+We fix this scale by an additional condition of $\bar{B}^{11}(q^1)=1$.
+
+%The scale of the collective coordinate is not unique because of the uncertainty of the eigenvectors in (\ref{mfQRPA}).
 To unify the scale, the simplest procedure is to keep the collective mass parameter $\bar{B}^{-1}(q)=1$ by renormalizing eigenvectors in (\ref{coll_mass}).
@@
 
-In integrable system, we can apply the stationary phase approximation to the path integral (SPA) to obtain collective excited states.
-The concept of SPA is introduced in the previous study.
-Because the one-dimensional collective path extracted from TDHFB degrees of freedom is integrable system, SPA is supposed to be available for non-integrable system via ASCC.
-\par
-Based on SPA, the $k$-th excited state $\ket{\psi_k}$ can be constructed by a periodic TDHFB trajectory
+For quantization of integrable systems,
+we can apply the stationary phase approximation (SPA)
+to the path integral.
+In our former study \cite{NN18},
+we have proposed and tested the SPA for an integrable pairing model.
+Since the collective Hamiltonian (\ref{coll}),
+extracted from TDHFB degrees of freedom, is integrable,
+kthe SPA is applicable to it.
+In this manner, we may apply the ASCC+SPA to
+non-integrable systems in general.
+
+Since the Hamiltonian $\mathcal{H}_{\rm coll}$ of Eq.~(\ref{coll})
+is separable,
+it is easy to find periodic trajectories on invariant tori.
+Since the pairing rotation corresponds to the motion of $p_n$
+with a constant $q^n$,
+all we need to do is to find classical periodic trajectories $C_k$ in
+the $(q^1,p_1)$ space (with a fixed $q^n$) which satisfy
+the Einstein-Brillouin-Keller (EBK) quantization rule
+with a unit of $\hbar=1$,
 \begin{equation}
-	\ket{\psi_k} = \oint d\mu(Z^{(k)}) \ket{Z^{(k)}}
-	e^{i\mathcal{T}[Z^{(k)}]/\hbar} .
+	\oint_{C_k} p_1dq^1 = 2\pi k ,
+\end{equation}
+where $k$ is an integer number.
+
+At each point in the 4D space $(q^1,q_n; p_1,p_n)$ corresponds to
+a generalized Slater determinant
+$\ket{q^1,q^n;p_1,p_n}=\ket{\xi,\pi}$
+where $(\xi,\pi)$ are given as
+$\xi^\alpha=g^\alpha(q^1,q_n,q^a=0)$ and
+$\pi_\alpha=f^1_{,\alpha}p_1+f^n_{,\alpha}p_n$.
+According to the SPA, the $k$-th excited state $\ket{\psi_k}$
+is constructed from the $k$-th periodic trajectory $C_k$,
+given by $(q^1(t),p_1(t))$,
+of the Hamiltonian $\mathcal{H}_{\rm coll}$.
+\begin{equation}
+%\ket{\psi_k} = \oint_{C_k} d\mu(q,p) \ket{q,p}
+\ket{\psi_k} = \oint dp_n \oint_{C_k} \rho(q,p) dt \ket{q,p}
+	e^{i\mathcal{T}[q,p]} ,
 	\label{SPA}
 \end{equation}
-The integration indicates we integrate a periodic TDHFB trajecotry for one period in TDHFB phase space.
-The invariant measure $d\mu(Z)$ is defined by the unity condition $\int d\mu(Z) \ket{Z}\bra{Z} = 1$.
+where $(q,p)$ means $(q^1,q^n;p_1, p_n)$ and a weight function
+$\rho(q,p)$ is given through an invariant meaure $d\mu(q,p)$ as
+\begin{equation}
+d\mu(q,p)=\rho(q,p) dE dt dq^n dp_n .
+\end{equation}
+The invariant measure $d\mu(q,p)$ is defined by the unity condition
+$\int d\mu(q,p) \ket{q,p}\bra{q,p} = 1$.
 The action integral $\mathcal{T}$ is defined by
 \begin{align}
-\mathcal{T}[Z] &\equiv
-\int_{0}^{t} \braket{Z(t')| i\hbar\frac{\partial}{\partial t'}
-	|Z(t')} dt' .
+\mathcal{T}[q,p] &\equiv
+\int_{0}^{t} \braket{q(t'),p(t')| i\hbar\frac{\partial}{\partial t'}
+	|q(t'),p(t')} dt' .
 \label{tau}
@@
 The collective model is described by the pair deformation parameters pairing gap $\Delta$ and global gauge angle $\Phi$.
-The utilization of the collective model for nuclear pairing dynamics was done in several references\cite{}.
-In our previous study, however, we find that the pairing gap $\Delta$ is not proper to be the collective coordinate in two-level pairing model \cite{}.
+The utilization of the collective model for nuclear pairing dynamics was done in several references\cite{??}.
+In our previous study, however, we find that the pairing gap $\Delta$ is not proper to be the collective coordinate in two-level pairing model \cite{??}.
 In multi-level system, we can investigate the relations between the pairing gap and the collective coordinate.

### 2018-10-19 paper2/draft1-2.tex
draft1-2 small change

@@
 1D collective subspace}
-\label{ASCC}
+\label{sec:ASCC}
 %To discuss the application of ASCC+SPA in the later subsection, 
@@
 associated with the breaking of the gauge (particle-number) symmetry.
-We assume the existence of 2D collective subspace $\Sigma_2$,
-described by a set of canonical variable $(q^1,q^n;p_1,p_n)$,
+We assume the existence of 2D collective subspace $\Sigma_2$
+(4D phase space),
+described by a set of canonical variable $(q^1,q^2;p_1,p_2)$,
 which is well decoupled from the rest of degrees of freedom,
-$\{q^a,p_a\}$ with $a=2,\cdots$.
+$\{q^a,p_a\}$ with $a=3,\cdots$.
 The collective Hamiltonian is given by imposing $q^a=p_a=0$,
@@
 \begin{align}
-p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha \\
+p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha
+	\label{coll_momenta}\\
 \pi_{\alpha} &= f^1_{,\alpha}p_1 +f^n_{,\alpha}p_n,
@@
 \end{align}
-The first equation (\ref{mfHFB}) is called moving-frame HFB equation.
+The first equation (\ref{mfHFB}) is called moving-frame
+Hartree-Fock-Bogoliubov (HFB) equation.
 The moving-frame Hamiltonian $\mathcal{H}_M$
@@
 \subsection{Stationary-phase approximation to the path integral}
+\label{sec:SPA}
 
@@
 non-integrable systems in general.
+
+\subsubsection{Basic idea of ASCC+SPA}
 
@@
 	\oint_{C_k} p_1dq^1 = 2\pi k ,
+	\label{EBK}
 \end{equation}
@@
 
-At each point in the 4D space $(q^1,q_n; p_1,p_n)$ corresponds to
+At each point in the space $(q^1,q_n; p_1,p_n)$ corresponds to
 a generalized Slater determinant
@@
 \end{equation}
-where $(q,p)$ means $(q^1,q^n;p_1, p_n)$ and a weight function
+where $(q,p)$ means $(q^1,q^n;p_1, p_n)$ and the weight function
 $\rho(q,p)$ is given through an invariant meaure $d\mu(q,p)$ as
@@
 $\int d\mu(q,p) \ket{q,p}\bra{q,p} = 1$.
+An explicit form of $d\mu(q,p)$ for the present pairing model is presented
+in Eq. (\ref{dmu}).
 The action integral $\mathcal{T}$ is defined by
@@
 
-We try to combine SPA with ASCC.
+The SPA quantization is able to provide a wave function $\ket{\psi_k}$
+in microscopic degrees of freedom, which is given as a superposition
+of generalized Slater determinants $\ket{q,p}$.
+In addition, the integration with respect to $p_n$ over a circuit on torus
+automatically recover the broken symmetry, namely the good particle number.
+However, it relies on the existence of invariant tori.
+In the present approach of ASCC+SPA,
+we first derive a decoupled collective subspace $\Sigma_2$ and identify
+canonical varialbles $(q,p)$.
+Because of the cyclic nature of $(q^n,p_n)$, it is basically a 1D system
+and becomes integrable.
+In other words, we perform the torus quantization on
+approximate tori in the TDHFB phase space $(\xi,\pi)$,
+which is mapped from tori in the 2D collective subspace $(q,p)$.
+
+%\begin{figure}[tb]
+% \begin{center}
+%    \includegraphics[width=80mm, bb=0 0 550 180]{SPA.png}
+% \end{center}
+%  \caption{For a TDHFB trajectory, the correspondence between TDHFB phase space and collective subspace.}
+%  \label{fig:correspondence}
+%\end{figure}
+%We try to combine SPA with ASCC.
 The key point is to find the correspondence between TDHFB phase space and collective subspace in a TDHFB trajectory (See Fig.
-\ref{correspondence}).
+\ref{fig:correspondence}).
 We consider the time-dependent state vector $\ket{Z(t)}$ is in a collective subspace.
 With pairing correlation, $\ket{Z(t)}$ can be expressed as
-\begin{align}
- \ket{Z(t)} &= \ket{\Phi,J;q,p} = e^{-i\Phi \hat{J}} \ket{J;q,p} ,
- \label{GCS}
-\end{align}
-where $\Phi$ is the total gauge angle and $J=N/2$ is the conjugate momentum corresponding total particle number.
+
+\subsubsection{Notation and practical procedure for quantization}
+\label{sec:notation}
+
+For application of the ASCC+SPA method to the pairing model in Sec.~\ref{sec3},
+we summarize some notations and procedures to obtain quantized states.
+
+In Sec.~\ref{sec3}, the time-dependent generalized Slater determinants
+(coherent states) are written as $\ket{Z}$ with complex variables
+$Z_\alpha(t)$.
+The variables $Z_\alpha$ are transformed into real variables
+$(j^\alpha, -\chi_\alpha)$ that correspond to $(\xi^\alpha,\pi_\alpha)$
+in Sec.~\ref{sec2}.
+$\chi_\alpha$ and $j^\alpha$ correspond to
+the ``angle'' and the ``number'' variables, respectively.
+Although it is customary to take the angle as a coordinate,
+since the angle $\chi_\alpha$ is time-odd quantities, 
+we switch the coordinates and the momenta with minus signs
+in front of variables $\chi$.
+Similarly, the gauge angle $\Phi$ and the total particle number $J$
+correspond to variables of the pair rotation, $-p_n$ and $q^n$, respectively.
+%The collective variables $(q^1,p_1)$ in Sec.~\ref{sec2} are
+%written as $(q,p)$ in Sec.~\ref{sec3} for simplicity.
+
+%\begin{align}
+% \ket{Z(t)} &= \ket{\Phi,J;q,p} = e^{-i\Phi \hat{J}} \ket{J;q,p} ,
+% \label{GCS}
+%\end{align}
+%where $\Phi$ is the total gauge angle and $J=N/2$ is the conjugate momentum corresponding total particle number.
 The second equal sign indicates an intrinsic state $\ket{J;q,p}$ rotates in the gauge space.
 Since $[H,J]=0$, the classical Hamiltonian
-becomes
-\begin{align}
- \mathcal{H} &= \braket{\Phi,J;q,p|H|\Phi,J;q,p} \nonumber \\
- &= \braket{J;q,p|H|J;q,p} \equiv \mathcal{H}_J(q,p)
-\end{align}  
-has no dependence of $\Phi$.
+%becomes
+%\begin{align}
+% \mathcal{H} &= \braket{\Phi,J;q,p|H|\Phi,J;q,p} \nonumber \\
+% &= \braket{J;q,p|H|J;q,p} \equiv \mathcal{H}_J(q,p)
+%\end{align}  
+%has no dependence of $\Phi$.
 Therefore, the classical Hamiltonian is the function of $(q,p)$ in a fixed particle number system, and correspond to (\ref{coll}).
@@
 Such $k$-th TDHFB trajectory is obtained from EBK quantization condition ($k$: integer)
-\begin{align}
-	\mathcal{T}_\circ[Z^{(k)}]=&
-	\oint \braket{Z^{(k)}(t')| i\hbar\frac{\partial}{\partial t'} |Z^{(k)}(t')} dt' \nonumber \\
-	=& \oint p^{(k)} dq^{(k)} = 2k\pi .
-	\label{EBK}
-\end{align}
-
-\begin{figure}[htbp]
- \begin{center}
-    \includegraphics[width=80mm, bb=0 0 550 180]{SPA.png}
- \end{center}
-  \caption{For a TDHFB trajectory, the correspondence between TDHFB phase space and collective subspace.}
-  \label{correspondence}
-\end{figure}
-
-The procedures to obtain excited states from SPA via ASCC are:
+%\begin{align}
+%	\mathcal{T}_\circ[Z^{(k)}]=&
+%	\oint \braket{Z^{(k)}(t')| i\hbar\frac{\partial}{\partial t'} |Z^{(k)}(t')} dt' \nonumber \\
+%	=& \oint p^{(k)} dq^{(k)} = 2k\pi .
+%	\label{EBK}
+%\end{align}
+
+According to the EBK quantization rule (\ref{EBK}),
+the ground state with $k=0$ corresponds to nothing but the HFB state
+with a fixed particle number $J(=q^n)$.
+For the $k$-th excited states, we perform the following calculations:
 \begin{enumerate}
-\item Obtain the one-dimensional collective coordinate from ASCC.
-\item Using collective Hamiltonian, obtain $k$-th excitation energy and TDHFB trajectory under EBK quantization condition (\ref{EBK}).
-\item For $k$-th TDHFB trajectory, construct the state vector $\ket{J;q,p}$ by using (\ref{momenta}).
-\item Calculate action integral (\ref{tau}) in $k$-th TDHFB trajectory.
-\item Using (\ref{SPA}), obtain $k$-th excited state.
+\item Obtain the 1D collective subspace with canonical variables $(q^1,p_1)$
+	according to the ASCC in Sec.~\ref{sec:ASCC}.
+\item Find a trajectory $(q^1(t),p_1(t))$ which satisfies
+the $k$-th EBK quantization condition (\ref{EBK}).
+\item Calculate the action integral (\ref{tau}) for the $k$-th trajectory.
+\item Using Eq.~(\ref{SPA}), construct the $k$-th excited state.
 \end{enumerate}
+The ASCC provides the 2D collective subspace $(q^1,J)$
+and the generalized coherent states $\ket{\Phi=0,J;q,p=0}$.
+For finite values of momenta, we use Eq.~(\ref{momenta})
+to obtain the state $\ket{\Phi,J;q,p}$.
 
@@
 
-\section{Application in pairing model}
+\section{Pairing model}
 \label{sec3}
 
-We study the low-lying excited $0^+$ states in multi-level pairing model by applying SPA via ASCC. 
+We study low-lying excited $0^+$ states
+in multi-level pairing model by applying the ASCC+SPA.
 The Hamiltonian of the pairing model is given in terms of
@@
 \begin{align}
-	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- \nonumber \\
-    &= \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
+	H &= \sum_\alpha \epsilon_\alpha n_\alpha - g \sum_{\alpha,\beta} S_\alpha^+ S_{\beta}^- \nonumber \\
+    &= \sum_\alpha\epsilon_\alpha(2S_\alpha^0+\Omega_\alpha) - g S^+ S^{-} ,
 \end{align}
 where we use the SU(2) quasi-spin operators,
-$\boldsymbol{S}=\sum_l \boldsymbol{S}_l$, with
+$\boldsymbol{S}=\sum_\alpha \boldsymbol{S}_\alpha$, with
 \begin{eqnarray}
-        S_l^0 &=& \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l) ,\\
-        S_l^{+} &=& \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
-\quad   S_l^{-} = S_l^{+\dag} .
+        S_\alpha^0 &=& \frac{1}{2}(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_\alpha) ,\\
+        S_\alpha^{+} &=& \sum_{m>0}a_{j_\alpha m}^{\dag}a_{j_\alpha\overline{m}}^{\dag} ,
+\quad   S_\alpha^{-} = S_\alpha^{+\dag} .
 \end{eqnarray}
-Each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
-degeneracy ($\Omega_l=j_l+1/2$)
-and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_l-1/2$.
-The occupation number of each level $l$ is given by
+Each single-particle energy $\epsilon_\alpha$ possesses $(2\Omega_\alpha)$-fold
+degeneracy ($\Omega_\alpha=j_\alpha+1/2$)
+and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$
+and $\Omega_\alpha-1/2$.
+The occupation number of each level $\alpha$ is given by
 $
-	n_l = \sum_m a^{\dag}_{lm}a_{lm} = 2S_l^0+\Omega_l ,
+\hat{n}_\alpha = \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m}
+=2S_\alpha^0+\Omega_\alpha
 $.
@@
 \begin{equation}
-  [S_l^0,S_{l'}^{\pm}] = \pm\delta_{ll'}S_{l}^{\pm},
-	\quad [S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0} .
+  [S_\alpha^0,S_\beta^{\pm}] = \pm\delta_{\alpha\beta}S_{\alpha}^{\pm},
+\quad [S_{\alpha}^{+},S_{\beta}^{-}] = 2\delta_{\alpha\beta}S_{\alpha}^{0} .
 \end{equation}
 The magnitude of quasi-spin for each level is
-$S_l=\frac{1}{2}(\Omega_l-\nu_l)$, where $\nu_l$ is the seniority
-quantum number, namely the number of unpaired particle at each level $l$.
+$S_\alpha=\frac{1}{2}(\Omega_\alpha-\nu_\alpha)$, where $\nu_\alpha$
+is the seniority
+quantum number, namely the number of unpaired particle at the level $\alpha$.
 In the present study, we only consider seniority zero states with
-$\nu=\sum_l \nu_l=0$.
+$\nu=\sum_\alpha \nu_\alpha=0$.
 The residual two-body interaction only consists of monopole pairing
@@
 \subsection{Classical form of TDHFB Hamiltonian}
-The coherent state for the seniority $\nu=0$ states
-($S_l=\Omega_l/2$) is constructed as
+
+The time-dependent coherent state for the seniority $\nu=0$ states
+($S_\alpha=\Omega_\alpha/2$) is constructed with
+time-dependent complex variables $Z_\alpha(t)$, as
 \begin{equation}
-	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-\Omega_l/2}
-	\exp [Z_l(t) S_l^{+}] \ket{0}
+	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_\alpha(t)|^2\right)^{-\Omega_\alpha/2}
+	\exp [Z_\alpha(t) S_\alpha^{+}] \ket{0}
  \label{coherent}
 \end{equation}
-where $\ket{0}$ is the vacuum (zero particle) state,
-$Z_l(t)$ are time-dependent complex variables which describe
-motion of the system. 
+where $\ket{0}$ is the vacuum (zero particle) state.
+The TDHFB motion is given by the time dependence of $Z_\alpha(t)$.
 In the SU(2) quasi-spin representation,
-$\ket{0}=\prod_l \ket{S_l,-S_l}$.
+$\ket{0}=\prod_\alpha \ket{S_\alpha,-S_\alpha}$.
 The coherent state $\ket{Z(t)}$ is a superposition of
@@
 the coherent state is the same as the time-dependent BCS wave function
-with $Z_l(t)=v_l(t)/u_l(t)$,
-where $(u_l(t),v_l(t))$ are the time-dependent BCS $u,v$ factors.
+with $Z_\alpha(t)=v_\alpha(t)/u_\alpha(t)$,
+where $(u_\alpha(t),v_\alpha(t))$ are the time-dependent BCS $u,v$ factors.
 
 The TDHFB equation can be derived from the time-dependent variational
-principle (we set $\hbar=1$),
+principle ($\hbar=1$), $\delta \mathcal{S} = 0$, where
 \begin{equation}
-	\delta \mathcal{S} = 0,
-	\quad
 %  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
@@
 \end{equation}
-After transformation of the complex variables $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$  ($0\leq\theta\leq\pi$) and several steps of the derivation, the Lagrangian $\mathcal{L}$ and the expectation value of Hamiltonian become
-\begin{align}
-\mathcal{L}(t) = \sum_l \frac{\Omega_l}{2}
-	(1&-\cos{\theta}_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
-	\mathcal{H}(Z,Z^*) \equiv \braket{Z|H|Z}& \nonumber \\
-  = \sum_l \epsilon_l\Omega_l(1- \cos{\theta}_l)& - \frac{g}{4}\sum_l \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
-- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
+After transformation of the complex into real variables,
+$Z_\alpha = \tan{\frac{\theta_\alpha}{2}}e^{-i\chi_\alpha}$
+($0\leq\theta\leq\pi$),
+the Lagrangian $\mathcal{L}$ and the expectation value of the Hamiltonian
+are written as
+\begin{equation}
+\mathcal{L}(t) = \sum_\alpha \frac{\Omega_\alpha}{2}
+	(1-\cos{\theta}_\alpha)\dot{\chi_\alpha} - \mathcal{H}(Z,Z^*) ,
+\end{equation}
+with
+\begin{align}
+	\mathcal{H}(Z,Z^*) &\equiv \braket{Z|H|Z}& \nonumber \\
+	&= \sum_\alpha \epsilon_\alpha\Omega_\alpha(1- \cos{\theta}_\alpha)
+	\nonumber \\
+	&- \frac{g}{4}\sum_\alpha \Omega_\alpha [\Omega_\alpha(1-\cos^2{\theta}_\alpha)+(1-\cos{\theta}_\alpha)^2] \nonumber \\
+	- \frac{g}{4}\sum_{\alpha\neq \beta} \Omega_{\alpha}\Omega_{\beta}&\sqrt{(1-\cos^2{\theta}_{\alpha})(1-\cos^2{\theta}_{\beta})}e^{-i(\chi_{\alpha}-\chi_{\beta})}   .
 \label{TDHFB_Hamiltonian_2}
 \end{align}
-Here, we choose $\chi_l$ as canonical coordinates. Their conjugate momenta
+Choose $\chi_\alpha$ as canonical coordinates, their conjugate momenta
 are given by
 \begin{align}
-  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=\frac{\Omega_l}{2}
-	(1-\cos{\theta}_l) .
-\end{align}
-$\chi_l$ represent a kind of gauge angle of each level,
-and $j_l$ are related to the occupation number of each level, $2j_l=n_l$.
-Therefore, the TDHFB Hamiltonian can be represented by canonical variables $\mathcal{H}(Z,Z^*) = \mathcal{H}(\{\chi_l\},\{j_l\})$, and the TDHFB equation is equivalent to the Hamilton's equation
+  j^\alpha\equiv
+	\frac{\partial\mathcal{L}}{\partial\dot{\chi}_\alpha}=\frac{\Omega_\alpha}{2}
+	(1-\cos{\theta}_\alpha) .
+\end{align}
+$\chi_\alpha$ represent a kind of gauge angle of each level,
+and $j^\alpha$ correspond to the occupation number of each level,
+$2j^\alpha=\bra{Z} \hat{n}_\alpha\ket{Z}$. 
+As we mention in Sec.~\ref{sec:notation},
+we switch the coordinates and momenta,
+$(\chi_\alpha,j^\alpha) \rightarrow (j^\alpha,-\chi_\alpha)$,
+to make the coordinates time even.
+%Therefore, the TDHFB Hamiltonian can be represented by canonical variables
+%$\mathcal{H}(Z,Z^*) = \mathcal{H}(\{\chi_l\},\{j_l\})$, and 
+The TDHFB equation is equivalent to the classical Hamilton's equation
 \begin{equation}
-	\dot{\chi_l} = \frac{\partial\mathcal{H}}{\partial j_l}, \quad
-	\dot{j_l} = -\frac{\partial\mathcal{H}}{\partial \chi_l} .
+	-\dot{\chi_\alpha} = -\frac{\partial\mathcal{H}}{\partial j^\alpha}, \quad
+	\dot{j^\alpha} = \frac{\partial\mathcal{H}}{\partial (-\chi_\alpha)} .
 \end{equation}
-.
-
-\subsection{Application into ASCC}
-In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec. \ref{ASCC}. 
-We construct 1D collective subspace from ASCC theory.
-Because the first order with respect to $\chi_{\alpha}$ is zero in TDHFB Hamiltonian, we assume $j^{\alpha}$ as coordinates and $\chi_{\alpha}$ as conjugate momenta.
+
+\subsection{Application of ASCC}
+
+%In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec. \ref{ASCC}. 
+We construct a 2D collective subspace $\Sigma_2$ from ASCC theory.
+%Because the first order with respect to $\chi_{\alpha}$ is zero in TDHFB Hamiltonian, we assume $j^{\alpha}$ as coordinates and $\chi_{\alpha}$ as conjugate momenta.
 The canonical variables are $(j^{\alpha},-\chi_{\alpha})$ and fulfill $\{j^{\alpha},-\chi_{\beta}\}_{PB}=\delta^{\alpha}_{\beta}$.
-We expand the classical Hamiltonian up to second order with respect to $\chi_{\alpha}$.
-The classical Hamiltonian becomes
+We expand the classical Hamiltonian up to second order with respect to
+momenta, $-\chi_{\alpha}$. 
 \begin{align}
@@
 \end{align}
-where potential $V(j)$ and reciprocal mass parameter $B^{\alpha\beta}(j)$ are defined as
-\begin{align}
-  V(j) =& \mathcal{H}(\chi=0,j) \nonumber \\
+where potential $V(j)$ and the reciprocal mass parameter
+$B^{\alpha\beta}(j)$ are given as
+\begin{align}
+  V(j) =& \mathcal{H}(j,\chi=0) \nonumber \\
 	=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left( \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right) \nonumber \\
@@
 \end{align}
-\begin{align}
-  B^{\alpha\beta}(j) =& \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \nonumber \\
-	=& \left\{
-	\begin{array}{c}
-	2g\sum_{\gamma\ne \alpha} \sqrt{j^{\gamma}j^{\alpha}(\Omega_{\gamma}-j^{\gamma})(\Omega_{\alpha}-j^{\alpha})} \hspace{2em} (\alpha=\beta) \\
-	-2g\sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})} \hspace{2em} (\alpha\ne\beta)
-	\end{array}
-	\right. .
+%\begin{align}
+\begin{eqnarray}
+&&B^{\alpha\beta}(j) = \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \\
 \label{mass}
-\end{align}
-Using the TDHFB Hamiltonian, we can apply ASCC explained in Sec. \ref{ASCC} by replacing $\xi\to j$ and $\pi\to-\chi$.
-
-We consider the treatment for the constant of motion in pairing model. In the TDHFB Hamiltonian, there is no dependence about the total gauge angle
-\begin{align}
-  \Phi = \frac{1}{L}\sum_{\alpha} \chi_{\alpha}.
+&&=
+	\begin{cases}
+2g\sum_{\gamma\ne \alpha} \sqrt{j^{\gamma}j^{\alpha}(\Omega_{\gamma}-j^{\gamma})(\Omega_{\alpha}-j^{\alpha})}
+		& \text{for $\alpha=\beta$} \\
+-2g\sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}
+		& \text{for $\alpha\ne\beta$}
+	\end{cases} \nonumber
+\end{eqnarray}
+%\end{align}
+We may apply the ASCC method in Sec. \ref{sec:ASCC}
+by regarding $\xi\to j$ and $\pi\to-\chi$.
+
+The TDHFB conserves the average total particle number $N$.
+We adopt 
+\begin{equation}
+	J\equiv N/2=\sum_\alpha j^\alpha ,
+  \label{J}
+\end{equation}
+as a coordinate $q^n$.
+Since this is explicitly given as the expectation value of the particle
+number operator, curvature quantities,
+such as $f^n_{,\alpha\beta}$ and $f^{(1)n\alpha\beta}$,
+are explicitly calculable.
+On the other hand, the gauge angle $\Phi=-p_n$ is not given a priori.
+Since the ASCC solution provides $g^\alpha_{,n}$ as an eigenvector of
+Eq. (\ref{mfQRPA}),
+we may construct it as Eq. (\ref{coll_momenta}) in the first order
+in $\pi=-\chi$.
+We confirm that the pairing rotation corresponds to an eigenvector
+of Eq. (\ref{mfQRPA}) with the zero frequency $\omega^2=0$.
+
+%With the properties of the constant of motion, we discuss the practical solution of ASCC in pairing model.
+If we ignore the higher order term $f^{(1)1\alpha\beta}$, we can practice local harmonic equation (LHE)
+%\begin{align}
+%  B^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
+%  B^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1},
+%  \label{LHE}
+%\end{align}
+%which simplifies the moving-frame QRPA equation (\ref{mfQRPA}) by replacing $\tilde{B}^{\beta\gamma}$ into $B^{\beta\gamma}$. Under (\ref{LHE}),
+
+%%%%%% I guess this is automatic. Check %%%%%%%%
+%To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_{\alpha} f^1_{,\alpha}=0$, we correct the eigenvectors by
+%\begin{align}
+%  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_{\beta} f^1_{,\beta} 
+%  \label{f}
+%\end{align}
+%after solving (\ref{LHE}) at each point of $q$.
+
+In the present pairing model, 
+from Eq. (\ref{total_gauge}), we find $J$ does not dependent on $\chi$.
+This means $f^{(1)n\alpha\beta}=0$ in Eq. (\ref{P}),
+thus, $\tilde{B}^{\beta\gamma}=B^{\beta\gamma}$.
+The second derivative of $J$ with respect to $j$ also vanishes,
+which indicates $f^{I}_{,\gamma\beta}$ in Eq.~(\ref{M}) is zero. 
+%It indicates the chemical potential $\lambda_I(q)$ is not necessary information to calculate the matrix element in moving-frame QRPA equation.
+In the present model, it is easy to find an explicit expression
+for the gauge angle $\Phi$.
+\begin{align}
+  \Phi = \frac{1}{L}\sum_{\alpha} \chi_{\alpha},
   \label{total_gauge}
 \end{align}
-It indicates the conjugate momentum 
-\begin{align}
-  J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}}=\sum_{\alpha} j^{\alpha} = \frac{N}{2}
-  \label{J}
-\end{align}
-is conserved quantity.
-From this equation, we can find $J$ is not dependent of $\chi$, which means $f^{(1)I\alpha\beta}$ in (\ref{P}) is zero.
-Therefore, $B^{\beta\gamma}V_{;\gamma\alpha}f^I_{,\beta}=0$ is promised exactly.
-Also, the second derivative of $J$ with respect to $j$ vanishes, which indicates $f^{I}_{,\gamma\beta}$ in (\ref{M}) is zero.
-It indicates the chemical potential $\lambda_I(q)$ is not necessary information to calculate the matrix element in moving-frame QRPA equation.
-
-With the properties of the constant of motion, we discuss the practical solution of ASCC in pairing model.
-If we ignore the higher order term $f^{(1)1\alpha\beta}$, we can practice local harmonic equation (LHE)
-\begin{align}
-  B^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
-  B^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1},
-  \label{LHE}
-\end{align}
-which simplifies the moving-frame QRPA equation (\ref{mfQRPA}) by replacing $\tilde{B}^{\beta\gamma}$ into $B^{\beta\gamma}$.
-Under (\ref{LHE}), the eigenvalue of spurious mode corresponding pairing rotation is exact zero.
-To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_{\alpha} f^1_{,\alpha}=0$, we correct the eigenvectors by
-\begin{align}
-  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_{\beta} f^1_{,\beta} 
-  \label{f}
-\end{align}
-after solving (\ref{LHE}) at each point of $q$.
-
-\subsection{Application into SPA}
-We derive the explicit form of excited states in (\ref{SPA}). From (\ref{GCS}) and (\ref{J}), the state vector $\ket{\Phi,J;q,p}$ becomes
+where $L$ is the number of available shells $\alpha=1,\cdots,L$.
+Its conjugate variable
+${\partial\mathcal{L}}/{\partial\dot{\Phi}}$
+is indeed given by $J$ of Eq. (\ref{J}).
+Again, exchanging coordinate and momentum,
+we have $q^n=J$ and $p_n=-\Phi$.
+
+%We consider the treatment for the constant of motion in pairing model. In the TDHFB Hamiltonian, there is no dependence about the total gauge angle
+%\begin{align}
+%  J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}}=\sum_{\alpha} j^{\alpha} = \frac{N}{2}
+%\end{align}
+%is conserved quantity.
+
+\subsection{Application of SPA}
+
+After deriving the collective subspace states $\Sigma_2$, 
+we perform the quantization according to the SPA in Sec.~\ref{sec:SPA}.
+Calculating a trajectory in the $(q^1,p_1)$ space,
+we can identify a series of states $\{\ket{\Phi,J;q^1(t),p_1(t)}\}$
+in the form of Eq. (\ref{coherent}) on the trajectory.
+
+derive the explicit form of excited states in (\ref{SPA}). From (\ref{GCS}) and (\ref{J}), the state vector $\ket{\Phi,J;q,p}$ becomes
 \begin{align}
@@
 % d\Phi dJ dq dp = d\Phi dJ dE dt 
+	\label{dmu}
 \end{align}

### 2018-10-20 paper2/draft1-2.tex
Still under progress

@@
 we can identify a series of states $\{\ket{\Phi,J;q^1(t),p_1(t)}\}$
-in the form of Eq. (\ref{coherent}) on the trajectory.
-
-derive the explicit form of excited states in (\ref{SPA}). From (\ref{GCS}) and (\ref{J}), the state vector $\ket{\Phi,J;q,p}$ becomes
-\begin{align}
-  \ket{\Phi,J;q,p} &= \sum_{\{j_l\}} e^{-i\Phi \sum_l j_l} \ket{J;q,p} .
-\end{align}
-Here, $\ket{J;q,p}$ can be expanded in SU(2) quasispin basis
-\begin{align}
-  \ket{J;q,p} &= \sum_{\{j_l\}} A_{j_l}(q,p) \ket{\cdots;S_l,-S_l+k_l,\cdots}, 
-\end{align}
-where 
-\begin{align}
-  A_{j_l}(q,p) =& \prod_l \left(\frac{1-\cos{\theta}_l}{2}\right)^{j_l/2}\left(\frac{1+\cos{\theta}_l}{2}\right)^{(\Omega_l-j_l)/2}
+on the trajectory,
+in the form of Eq. (\ref{coherent})
+with parameters $Z_\alpha$ given at $(\Phi,J,q^1,p_1)$ and $q^a=p_a=0$ for
+$a\geq 3$.
+%Due to $J$ is conserved quantity, the action integral can be divided into two terms
+Since the variables$(\Phi,J)$ and $(q^1,p_1)$ are separable,
+we may take closed trajectories independently in $(\Phi,J)$ and $(q^1,p_1)$
+sectors, which we denote here as $C_\Phi$ and $C_1$, respectively.
+The action integral is given by
+\begin{align}
+\mathcal{T}(\Phi,J;q^1,p_1)
+&= \int_{C_\Phi} \braket{\Phi(t),J;q^1,p_1|i\frac{\partial}{\partial t}|\Phi(t),J;q^1,p_1} dt \nonumber \\
++ \int_{C_1} &\braket{\Phi,J;q^1(t),p_1(t)|i\frac{\partial}{\partial t}|\Phi,J;q^1(t),p_1(t)} dt
  \nonumber \\
-  &\times\sqrt{\frac{(\Omega_l)!}{j_l!(\Omega_l-j_l)!}} e^{-ij_l\chi_l} 
-\end{align}
-is in fixed gauge angle ($\Phi=0$).
-
-Due to $J$ is conserved quantity, the action integral can be divided into two terms
-\begin{align}
-  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
-\end{align}
-where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
-\begin{align}
-  \mathcal{T}_{\rm intr}(t) &= \int \braket{J;q,p|i\frac{\partial}{\partial t}|J;q,p} dt
+	&=J\Phi + \int_{C_1} \sum_\alpha j^\alpha d\chi_\alpha
 	\nonumber \\
-	&= \int \sum_l j_l d\chi_l .
+	&\equiv \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
 	\label{tau}
 \end{align}
-The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.
-In SU(2) representation, the invariant measure is
-\begin{align}
-  d\mu(Z) &= \prod_l \frac{\Omega_l+1}{\pi} (1+|Z_l|^2)^{-2} d{\rm Re}Z d{\rm Im}Z \nonumber \\
- =& \prod_l \frac{\Omega_l+1}{4\pi} d \cos{\theta_l} d\chi_l \nonumber \\
- =& \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} d\chi_l dj_l \nonumber \\
- =& \left[ \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} \right] d\Phi dJ dqdp \nonumber \\
- &\times dQ_1\cdots dQ_{l-2}dP_1\cdots dP_{l-2}
+In fact, the gauge-angle dependence is formally given as
+\begin{equation}
+\ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_q} .
+\end{equation}
+Then, the action for the trajectory $C_1$ can be also expressed as
+$\mathcal{T}(q^1,p_1;J)=
+ \int_{C_1} \braket{J;q^1,p_1|i\frac{\partial}{\partial t}|J;q^1,p_1} dt$.
+%\begin{align}
+%  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
+%\end{align}
+%%where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
+%The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.
+
+In the su(2) representation, the invariant measure is
+\begin{align}
+  d\mu(Z) &= \prod_\alpha \frac{\Omega_\alpha+1}{\pi} (1+|Z_\alpha|^2)^{-2} d{\rm Re}Z d{\rm Im}Z \nonumber \\
+=& \prod_\alpha \frac{-(\Omega_\alpha+1)}{4\pi} d \cos{\theta_\alpha} d\chi_\alpha \nonumber \\
+ =& \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} d\chi_\alpha dj^\alpha \nonumber \\
+ =& \left[ \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} \right] d\Phi dJ dq^1 dp_1 %\nonumber \\
+  \prod_a dq^a dp_a
 % d\Phi dJ dq dp = d\Phi dJ dE dt 
@@
 \end{align}
-where $(Q_i,P_i)$ are the other canonical variables decoupled from the collective coordinates.
-From the third line to the forth line, we used that Jacobian equals one in canonical transformation.
-The part of the invariant measure which contributes to the excited states is
-\begin{align}
-d\mu(\Phi,J;q,p) \propto d\Phi dJ dqdp = d\Phi dJ dE dt. 
-\end{align}
-Under EBK quantization condition (\ref{EBK}),
-the $k$-th excited state becomes
-\begin{align}
- \ket{\tilde{\phi}_k} \propto& \oint d\Phi \oint dt \ket{\Phi,J;q,p} e^{i\mathcal{T}(\Phi,J;q,p)}
+where $(q^a,p_a)$ are the intrinsic canonical variables
+decoupled from the collective subspace $\Sigma_2$.
+For the last equation in Eq. (\ref{dmu}),
+we used the invariance of the phase space volume element
+in canonical transformation.
+%The part of the invariant measure which contributes to the excited states is
+According to (\ref{dmu}),
+the weight function $\rho(q,p)$ in Eq. (\ref{SPA}) is just a constant,
+thus, treated as the normalization of the wave function.
+%\begin{align}
+%d\mu(\Phi,J;q,p) \propto d\Phi dJ dqdp = d\Phi dJ dE dt. 
+%\end{align}
+%Under EBK quantization condition (\ref{EBK}),
+
+%derive the explicit form of excited states in (\ref{SPA}). From (\ref{GCS}) and (\ref{J}), the state vector $\ket{\Phi,J;q,p}$ becomes
+%\begin{align}
+%  \ket{\Phi,J;q,p} &= \sum_{\{j_l\}} e^{-i\Phi \sum_l j_l} \ket{J;q,p} .
+%\end{align}
+The coherent state $\ket{\Phi,J;q^1,p_1}=\ket{Z}$ is
+expanded in the su(2) quasispin basis as
+\begin{align}
+\ket{Z} &= 
+\sum_{\{m_\alpha\}} A_m(Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots}, \nonumber\\
+\end{align}
+where the summation is taken over all possible combinations
+of integer values of $\{ m_\alpha\}$.
+\begin{align}
+A_m(Z) =& \prod_\alpha 
+\frac{Z_\alpha^{m_\alpha}}
+	{\left(1+|Z_\alpha|^2\right)^{\Omega_\alpha/2}m_\alpha!}
+\sqrt{\frac{(\Omega_\alpha)! m_\alpha!}{(\Omega_\alpha-m_\alpha)!}} \nonumber\\
+ =& \prod_\alpha \left(\frac{1-\cos{\theta}_\alpha}{2}\right)^{m_\alpha/2}\left(\frac{1+\cos{\theta}_\alpha}{2}\right)^{(\Omega_\alpha-m_\alpha)/2}
   \nonumber \\
- =& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \nonumber \\
- &\times \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q,p) \ket{\cdots;S_l,-S_l+j_l,\cdots} \nonumber \\
- \equiv& \sum_{\{j_l\}\in (\sum_{j_l}=J)} C_{j_l} \ket{\cdots;S_l,-S_l+j_l,\cdots}
+  &\times\sqrt{\frac{(\Omega_\alpha)!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
+	\label{A_m}
+\end{align}
+where the lower index $m$ indicates a combination of $\{ m_\alpha \}$.
+The integer numbers $m_\alpha$ correspond to the number of pairs
+in the level $\alpha$.
+%is in fixed gauge angle ($\Phi=0$).
+%
+
+Using Eq.~(\ref{A_m}),
+now, the $k$-th excited state is calculated as
+\begin{align}
+\ket{\psi_k} \propto& \oint_{C_\Phi} d\Phi \oint_{C_1} dt
+\ket{\Phi,J;q^1,p_1} e^{i\mathcal{T}(\Phi,J;q^1,p_1)}
+ \nonumber \\
+	=& \sum_{\{m_\alpha\}}
+	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \nonumber \\
+&\times \oint dt e^{i\mathcal{T}_1}(t) B_m (Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots} \nonumber \\
+ \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots}
  \label{SPA2}
 \end{align}
-where
-\begin{align}
-  C_{j_l} = \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q(t),p(t)).
+where $B_m(Z)$ are indentical to $A_m$ in Eq.~(\ref{A_m}) but
+replacing $\chi_\alpha$ by the relative angles
+$\phi_\alpha\equiv\chi_\alpha-\Phi$.
+The coefficients $C_m$ are
+\begin{align}
+C_m = \oint_{C_1} dt e^{i\mathcal{T}_1(t)} B_m(Z(t))
   \label{coef}
 \end{align}
-
-The definition of wave function in SPA can also be extended into ground state.
-The ground state is constructed by only energy minimum point in TDHFB phase space.
-In the energy minimum point, $\ket{\Phi,J;q,p}=\ket{\rm HFB}$.
-Therefore, (\ref{SPA2}) becomes
-\begin{align}
- \ket{\tilde{\phi}_{g.s.}} \propto& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \ket{\rm HFB},  
+In the last line of Eq. (\ref{SPA2}), the summation is restricted to
+$\{m_\alpha\}$ that satisfy $\sum_\alpha m_\alpha=J$.
+It is easy to find that $J$ must be integer,
+according to the quantization rule (\ref{EBK}) for the $(J,\Phi)$ sector.
+
+The SPA for the ground state ($k=0$) is given by the stationary point
+in the $(q^1,p_1)$ sector,
+namely, the HFB state $\ket{\Phi,J;q,p}=e^{-i\Phi\hat{N}/2}\ket{\rm HFB}$.
+Nevertheless, the rotational motion in $\Phi(t)$ is present,
+which leads to the number quantization (projection).
+Therefore, Eq.~(\ref{SPA2}) becomes
+\begin{align}
+	\ket{\psi_{g.s.}} \propto& \sum_{\{m_\alpha\}}
+	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \ket{\rm HFB},  
 \end{align}

### 2018-10-24 paper2/draft1-3.tex
draft1-3

--- 2018-10-20 paper2/draft1-2.tex
@@
 microscopic degrees of freedom using the mean-field calculation and
-the cranking inertia formula \cite{???}.
+the cranking inertia formula \cite{Bar11,Del10,Fu13}.
 The 5DCH model is able to take into account fluctuations of
@@
 the canonical quantization of the 5DCH was employed for the study of low-lying
-excited states in nuclei \cite{???}.
+excited states in nuclei \cite{PR09,HSNMM10,NMMY16}.
 The similar quantization was also utilized for the pairing collective
@@
 	\ket{\psi_{g.s.}} \propto& \sum_{\{m_\alpha\}}
-	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \ket{\rm HFB},  
+	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi}
+	\ket{\rm HFB},  
+	\label{SPA3}
 \end{align}
@@
 \label{sec4}
-We apply ASCC+SPA to study the multi-level system in pairing model.
-The TDHFB degrees of freedom equals the number of single particle levels, including the constant of motion (pairing rotation).
+
+%We apply ASCC+SPA to study the multi-level system in pairing model. 
+In the pairing model in Sec.~\ref{sec3},
+the number of TDHFB degrees of freedom equals that of single particle levels.
+% including the constant of motion (pairing rotation).
 We consider various systems, two-level system, three-level system, and Pb isotope system in each subsection respectively.
 Next, we discuss the dynamics in non-integrable (more than three-level) system.
-
-\subsection{Confirmation in one-dimensional TDHFB system}
-The two-level system corresponds to one-dimensional TDHFB system after decoupling the global gauge angle $\Phi$.
-We can obtain the obvious collective path from ASCC.
-The dynamics is exactly identical with adiabatic TDHFB (ATDHFB).
-We confirm that whether ASCC is identical to one-dimensional ATDHFB, and compare the difference with TDHFB, in numerical calculation.
-
-In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
-\begin{align}
-\mathcal{H} 
-  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
- &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
-- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
-\end{align}
-If we define the canonical coordinate $\phi=\chi_2-\chi_1$, it attributes to one-dimensional system.
+Since there is a constant of motion, the particle number, in addition to
+the energy, the system is integrable for one- and two-level models.
+We first apply the ASCC+SPA method to an integrable two-level model,
+then, to non-integrable multi-level models.
+
+\subsection{Integrable case: Two-level pairing model}
+
+The two-level pairing model corresponds to the 2D TDHFB system.
+Explicitly separating the gauge angle $\Phi$ and
+fixing the particle number $J$,
+the 2D TDHFB is reduced to the 1D system,
+with the relative angle $\phi\equiv \chi_2-\chi_1$ and the relative
+occupation $j\equiv (j_2-j_1)/2$ as canonical variables.
+In Ref.~\cite{NN18}, using the explicit transformation to these
+separable variables,
+we examined performance of the SPA requantization
+for the two-level model.
+In this section, we apply the ASCC+SPA method to the same model.
+In other words, the ASCC method finds the transformation.
+
+Here, we study the system with equal degeneracy,
+$\Omega_1=\Omega_2=8$, 
+the pairing strength $g/(\epsilon_2-\epsilon_1)=0.2$,
+and the particle number $N=16$. 
+The moving-frame QRPA produces the zero mode and another eigenvector
+with finite frequency $\omega^2\neq 0$.
+We follow the latter mode to construct the collective path.
+In the ASCC calculation, we set the increment of the
+collective coordinate, $dq=0.01$,
+in units of $1/\sqrt{\epsilon_2-\epsilon_1}$.
+We confirm that the pair rotation always has zero frequency
+on the collective path.
+On the obtained collective path, we calculate classical trajectory
+for the Hamiltonian
+\begin{equation}
+\mathcal{H}_{\rm coll}(q^1,p_1;J)=\frac{1}{2} p_1^2 + V(q^1,J) ,
+\end{equation}
+with $J=N/2=8$.
+Calculated trajectories, satisfying the EBK quantization condition
+(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$),
+are mapped onto the $(\phi,j)$ plane and
+shown in Fig. \ref{fig:N16_traj}.
+We also calculate the trajectories using explicit transformation
+of variables to $(\Phi,J;\phi,j)$, which
+are shown by dashed lines in Fig. \ref{fig:N16_traj}.
+We call this ``TDHFB trajectories''.
+Small deviation in large $\phi$ is due to the neglect of higher-order
+terms in $\chi_\alpha$ in the ASCC.
+In fact, if we calculate the trajectories in the variables
+$(\Phi,J;\phi,j)$ using the Hamiltonian truncated up to the
+second order in $\chi_\alpha$ (``ATDHFB trajectories''),
+we obtain the solid lines in Fig. \ref{fig:N16_traj},
+which perfectly agree with the ASCC trajectories.
+
+The action integrals $\mathcal{T}(t)$ corresponding to
+these closed trajectories are shown in Fig. \ref{fig:N16_tau}.
+For the $0_2^+$ state,
+all three calculations well agree
+with each other, while we see small deviation between the full TDHFB
+and the ASCC/ATDHFB calculations for the $0_3^+$ state.
+
+The calculated wave functions for excited $0^+$ states 
+are shown in Fig. \ref{fig:N16_occ}. 
+We show the occupation probability which is decomposed 
+into $2n$-particle-$2n$-hole components. 
+The left end of the horizontal axis at $j=j_{\rm min}$
+corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
+are in the lower level $\epsilon_1$.
+The next at $j=j_{\rm min}+1$ corresponds to the one with
+$(m_1,m_2)=(N-2/2,1)$, and so on.
+The results from ATDHFB+SPA and ASCC+SPA are identical to each other
+within numerical error, which well reproduces
+the TDHFB+SPA calculation.
+(How about exact cal.?)
+
+%we can obtain the obvious collective path from ASCC.
+%The dynamics is exactly identical with adiabatic TDHFB (ATDHFB). We confirm that whether ASCC is identical to one-dimensional ATDHFB, and compare the difference with TDHFB, in numerical calculation.
+%
+%In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
+%\begin{align}
+%\mathcal{H} 
+%  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
+% &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
+%- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
+%\end{align}
+%If we define the canonical coordinate $\phi=\chi_2-\chi_1$, it attributes to one-dimensional system.
 The conjugate momentum is $j= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \{\Omega_2(1-\cos{\theta}_2) - \Omega_1(1-\cos{\theta}_1)\}/4$.
 The ATDHFB indicates that the Hamiltonian can be expanded up to second order with respect to $\phi$
-\begin{align}
-  \mathcal{H}(\phi,j) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
-\end{align}
-where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
-We know that the BCS ground state corresponds to the potential minimum point with $\phi=0$.
+%\begin{align}
+%  \mathcal{H}(\phi,j) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
+%\end{align}
+%where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
+%We know that the BCS ground state corresponds to the potential minimum point with $\phi=0$.
 If the pairing correlation is strong enough to bind the excited states in the collective potential,  the adiabatic approximation is expected to be well because the states are localized in small $\phi$ region.
-
-We study the system with equal degeneracy $\Omega_1=\Omega_2=8$, $g/(\epsilon_2-\epsilon_1)=0.2$, and $N=16$.
-In ASCC calculation, we set the mesh size of collective coordinate $dq=0.01$.
-We compared the results of $\ket{0_2^+}$ and $\ket{0_3^+}$ in three different calculations.
-Fig.
-\ref{fig:N16_traj} and Fig.
-\ref{fig:N16_tau} correspond to the classical informations, which are classical trajectories in phase space and action integral $\mathcal{T}$ as a function of time $t$.
-All of the mesh points obtained from ASCC are on the trajectories obtained from ATDHFB.
-For $\ket{0_2^+}$, the closed trajectory is well localized in the phase space and TDHFB calculation is almost the same as ASCC and ATDHFB calculations.
-For $\ket{0_3^+}$, the trajectory is still closed but near the transition point between closed trajectory and open trajectory.
-We can find ASCC and ATDHFB calculations have a small deviation from TDHFB calculation.
-The obtained excited $0^+$ states from SPA are shown in Fig.
-\ref{fig:N16_occ}.
-We show the occupation probability which is decomposed into $2n$-particle-$2n$-hole components.
-The results from ATDHFB and ASCC are identical within numerical error.
-Also, TDHFB calculation is very close to other two calculations.
+%
 
@@
  \end{center}
-\caption{Classical trajectories of $\ket{0_2^+}$ and $\ket{0_3^+}$ in two-dimensional phase space.
-The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$.
-Cross points, solid lines, and dashed lines correspond to the results from ASCC+SPA, one-dimensional ATDHFB+SPA, and one-dimensional TDHFB+SPA, respectively.
-In ASCC+SPA calculation, each cross point corresponds to each mesh point from ASCC calculation.
+\caption{Classical trajectories satisfying the EBK condition
+(\ref{EBK}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
+%The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$. 
+Crosses, solid and dashed lines correspond to the results
+of ASCC+SPA, ATDHFB+SPA, and TDHFB+SPA, respectively. 
+For the ASCC+SPA trajectories, we plot the crosses
+every ten(?) points of the calculation,
+namely $\delta q=0.1/\sqrt{\epsilon_2-\epsilon_1}$.
 }
@@
  \end{center}
-\caption{Action integrals of $\ket{0_2^+}$ and $\ket{0_3^+}$ with respect to time $t$.Cross points, solid lines, and dashed lines correspond to the results from ASCC+SPA, one-dimensional ATDHFB+SPA, and one-dimensional TDHFB+SPA, respectively.
-Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$.
-Based on Fig.
-\ref{fig:N16_traj}, we calculated the action integrals on each trajectory from $(\phi,j)=(0,j_{\rm max})$ in clockwise direction.
+\caption{Calculated action integrals for the $\ket{0_2^+}$ and $\ket{0_3^+}$ states as functions of time $t$.
+Crosses, solid and dashed lines correspond to the ASCC+SPA,
+the ATDHFB+SPA, and the TDHFB+SPA, respectively. 
+%Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
+We calculated the action integrals on each trajectory
+from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction
+in Fig. \ref{fig:N16_traj}.
 }
@@
  \end{center}
-	\caption{Occupation probabilities of $\ket{0_2^+}$ and $\ket{0_3^+}$
-as a function of $j$.
-The two vertical bars at each $j$ from the left to the right represent
-the squared components of the wave functions
-from ASCC+SPA, ATDHFB+SPA and TDHFB+SPA calculations, respectively.
-The left end of the horizontal axis at $j=j_{\rm min}$
-corresponds to a component with $(n_1,n_2)=(N,0)$.
-The next at $j=j_{\rm min}+1$ corresponds to the one with
-$(n_1,n_2)=(N-2,2)$, and so on.
+\caption{
+Occupation probabilities for the $0_2^+$ and $0_3^+$ states.
+The horizontal line indicates the $m_2-m_1$ of the quasi-spin basis
+in Eq. (\ref{SPA2}).
+The vertical bars at each $m_2-m_1$
+represent the ASCC+SPA, ATDHFB+SPA and TDHFB+SPA calculations,
+respectively, from left to right.
 }
@@
 
-Comparing with one-dimensional TDHFB calculation, we confirmed we succeed to describe the bound collective excited states by ASCC+SPA.
+Comparing with the full TDHFB calculation with the ASCC+SPA approach
+in the two-level pairing model,
+we conclude that the ASCC is reliable for description of low-lying
+collective states, for which the adiabatic approximation is justifiable.
+In addition, the pair rotation is properly separated.
+%we succeed to describe the bound collective excited states by ASCC+SPA.
 For the bound states, whether the adiabatic approximation included or not hardly has influence.
@@
 
-\subsection{Three-level system}
-The simplest non-integrable system is three-level system.
-We have one trivial motion and two time-dependent degrees of freedom.
-We study the system with $\Omega_1=\Omega_2=\Omega_3=8$, $\epsilon_1=-1$, $\epsilon_2=0$, $\epsilon_3=1.5$, and $g=0.2$.
-The phase transition occurs at $g_c=0.058$ when $N=2\Omega_1=16$.
-We consider the even particle number chain from $N=14$ to $N=24$.
-
-From moving-frame QRPA equation, we obtain three modes along the collective path (Fig.
-\ref{omega_sq}).
-Except zero mode, we choose the lowest mode as collective motion.
-Fig.
-\ref{occ_number} and Fig.
-\ref{potential} are occupation number in each single-particle level and collective potential in the collective path, respectively.
-We can find the occupation numbers become to integer at both end points.
-Furthermore, Hartree-Fock states always emerge at one of the end point.
+\subsection{Non-integrable case (1): Three-level pairing model}
+\label{sec:three-level-model}
+
+In contrast to the two-level model,
+the TDHFB for the three-level model is non-integrable.
+%The simplest non-integrable system is three-level system. We have one trivial motion and two time-dependent degrees of freedom. 
+We set parameters of the system as follows:
+$\Omega_1=\Omega_2=\Omega_3=\Omega=\Omega=8$,
+$\epsilon_1=-\epsilon_0$, $\epsilon_2=0$, $\epsilon_3=1.5\epsilon_0$,
+and $g=0.2\epsilon_0$.
+We use the parameter $\epsilon_0$ as the unit energy.
+For the sub-shell closed configuration of $N=2\Omega=16$,
+the HFB ground state changes from the normal phase to
+the superfluid phase at $g_c=0.058\epsilon_0$.
+We calculate a chain of systems with even particle number
+from $N=14$ to $N=24$.
+
+We obtain three eigen-frequencies for the moving-frame QRPA equation, 
+on the collective path (Fig. \ref{omega_sq}). 
+First of all, we clearly identify the zero mode with $\omega^2=0$
+everywhere along the collective path.
+This means that the pair rotation is separated from the other
+degrees of freedom in the ASCC.
+The frequency could become imaginary ($\omega^2<0$).
+Except for the case of sub-shell closure ($N=2\Omega_1=16$),
+the frequency rapidly increases near the end points.
+The end points are given by points where search for the next point
+on the collective path in Sec.~\ref{sec:ASCC} fails.
+
+We choose the lowest mode, except for the zero mode,
+as a generator for the collective path ($q^1$).
+Figure~\ref{occ_number} shows variation of the occupation probability
+of each single-particle state, as functions of the collective
+coordinate $q^1$ on the collective path.
+The most striking feature is that the collective path is terminates
+with special configurations which are given by the integer number
+of occupation.
+This is a reason why the search for the collective path fails
+at the both ends.
+The occupation of the level 3 ($\epsilon_3$) vanishes, while
+those of the levels 1 and 2 become either maximum or minimum.
+The left end of each panel in Fig.~\ref{occ_number} corresponds to 
+a kind of ``Hartree-Fock'' state which minimizes
+the single-particle-energiy sum, $\sum_\alpha 2j_\alpha \epsilon_\alpha$.
+The pairing correlation is weakened in both ends of the
+collective path.
+
+The collective mass with respect to the coordinate $q^1$ is normalized
+to unity.
+The collective potential is shown in Fig.~\ref{potential}.
+The range of $q^1$ is the largest for the system with $N=16$.
+This is because the varition of $j^1$ and $j^2$ is the largest in
+this case.
 
@@
 	\caption{Occupation numbers in each single-particle level with respect to the collective coordinate $q$, from $N=14$ to $N=24$.
-At the left end point of the collective coordinate in each panel, the configurations correspond to Hartree-Fock states.
+At the left end point of the collective coordinate in each panel, the configurations correspond to Hartree-Fock (HF) states.
 }
@@
 
-Based on the information from ASCC calculation, we can obtain the excited states from SPA.
-Table \ref{ex} shows the excitation energies of first and second excited states in the collective subspace.
-Up to the second excitation, all of the energies are in their energy pockets shown in Fig.
-\ref{potential}.
-Comparing the result from ASCC+SPA with exact solution, we can find all of the values are nicely reproduced.
-The slightly difference is that the values from ASCC+SPA are about $5\%$ smaller than exact solution.
-Using the wave function of excited states, the pair additional transition strength is shown in Fig.
-\ref{3levelPad}.
-For intraband transition, comparing ASCC+SPA with exact solution, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$ are almost identical and $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are about $10\%\sim20\%$ small.
-For interband transition, the strength from ASCC+SPA is much smaller than exact solution.
-It is difficult to reproduce the absolute value of exact solution.
-However, because the pairing correlation is enough strong in this case, the strength of intraband transition is dominant compared with interband transition.
-We can find that $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_1^+)$ are only about $1\%$ of $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$.
-Therefore, the interband transition can be regarded as reasonable.
-From all above results, we can conclude that ASCC+SPA reproduces exact solution quantitatively.
-
-%We skipped the result about $\ket{0_3^+}$.
- We need to discuss about the second excited state in the collective path corresponds to not $\ket{0_3^+}$ and others, but $\ket{0_4^+}$.
-In pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from exact solution, $B(P_{\rm ad};0_2^+\rightarrow 0_3^+)$ is $10\sim100$ times smaller than $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$, and $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ is in the same order with $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$.
-It indicates that $\ket{0_3^+}$ is also one-phonon state which belongs to the other collective path (black line in Fig.
+Based on the collective path determined by the ASCC calculation,
+we perform the requantization according to the SPA.
+Table \ref{ex} shows the excitation energies of the first and the second
+excited states, determined by the EBK quantization condition (\ref{EBK}).
+Comparing the result of the ASCC+SPA with those of the exact calculation,
+we find the excitation energies are reasonably well reproduced. 
+The ASCC+SPA underestimates the excitation energies by about 5 \%.
+%The difference is that the values from ASCC+SPA are 
+%about $5\%$ smaller than exact solution.
+
+It should be noted that the second excited state in the collective path
+corresponds to the $0_4^+$ state,
+not to the $0_3^+$ state, in the exact calculation. 
+We examine the interband $(k\neq k')$ pair addition transition,
+\begin{equation}
+B(P_{\rm ad};k\rightarrow k') \equiv 
+	\left|\bra{0_{k'}^+;N+2} S^+ \ket{0_k^+;N}\right|^2 ,
+\label{BPad}
+\end{equation}
+in the exact solution.
+$B(P_{\rm ad};0_2^+\rightarrow 0_3^+)$ 
+is $10\sim100$ times smaller than $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$,
+while $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and
+$B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$ are in the same order.
+The ASCC+SPA produces states in the same family,
+namely, those belonging to the same collective subspace (path).
+In the phonon-like picture,
+we expect similar magnitude of strengths for
+$B(P_{\rm ad};{\rm g.s.}\rightarrow i{\rm 1 phonon})$
+and
+$B(P_{\rm ad};{\rm 1 phonon}\rightarrow i{\rm 2 phonon})$,
+but smaller values of
+$B(P_{\rm ad};{\rm g.s.}\rightarrow i{\rm 2 phonon})$.
+Thus, the $0_4^+$ state in the exact calculation
+corresponds to the two-phonon state in the ASCC+SPA.
+The $0_3^+$ state in the exact calculation may correspond to
+a collective path associated with another solution of the moving-frame QRPA
+(thin black line in Fig.~\ref{omega_sq}).
+
+%It indicates that $\ket{0_3^+}$ is also one-phonon state which belongs to the other collective path (black line in Fig.
 \ref{omega_sq}).
@@
 Therefore, $\ket{0_4^+}$ is considered to be most appropriate corresponding to the second excited state in ASCC+SPA calculation.
+
+Next, we calculate the wave functions,
+according to Eqs.~(\ref{SPA2}) and (\ref{SPA3}).
+The ground state corresponds to the number-projected HFB state
+(variation before projection).
+In contrast, excited states are given as superposition of
+generalized Slater determinants in the collective subspace,
+Using these wave function of excited states, 
+the pair addition transition strengths
+are shown in Fig. \ref{3levelPad}.
+For the intraband transition ($k=k'$ in Eq. (\ref{BPad}),
+the ASCC+SPA method well reproduces the strengths of the exact calculation.
+The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
+are perfectly reproduced, while
+$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are underestimated 
+by about $10\%\sim20\%$.
+
+It is more difficult to reproduce the absolute magnitude of
+interband transitions ($k\neq k'$), 
+which are far smaller than the intraband transitions.
+Although the increasing (decreasing) trend for
+$B(P_{\rm ad};0_2^+\rightarrow 0_1^+)$
+($B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$)
+as a function of the particle number is properly reproduced,
+the absolute magnitude is signiicantely underestimated in the ASCC+SPA.
+This is due to extremely small collectivity in the interband transitions.
+Almost all the strengths are absorbed in the intraband transitions.
+Even in the exact calculation, the pair addition strength is
+about two orders of magnitude smaller than the intraband strength.
+Remember that the non-collective limit ($g\rightarrow 0$) of this
+value is $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)=\Omega$.
+Therefore, the pairing correlation hinders the interband transitions
+by about one order of magnitude.
+For such tiny quantities, perhaps, 
+the reduction to the 1D collective path is not well justified.
+%In our previous study on the two-level case, we found that
+%the SPA reasonably well reproduces interband transitions \cite{NN18}.
+%The present case corresponds to a strong pairing case with
+%the strongly hindered interband transitions.
+
+%It is difficult to reproduce the absolute value of exact solution.
+%However, because the pairing correlation is enough strong in this case, the strength of intraband transition is dominant compared with interband transition.
+%We can find that 
+%$B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_1^+)$ are only about $1\%$ of $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$.
+Therefore, the interband transition can be regarded as reasonable.
+From all above results, we can conclude that ASCC+SPA reproduces exact solution quantitatively.
+
+We should remark here that there is a difficulty in the present ASCC+SPA
+requantization for weak paring cases.
+In such cases, the potential minimum is close to the left end 
+($q^1=q_L$) of the collective path, and the potential height
+at $q^1=q_L$, $V(q_L) - V(0)$, becomes small.
+Then, a classical trajectory at $E>V(q_L)$ hit this boundary ($q^1=q_L$).
+In construction of wave functions,
+the boundary condition at $q^1=q_L$ significantly influences the result.
+In the present study, we choose a strong pairing case to avoid
+such a situation.
+As in Feb.~\ref{potential}, the potential height at $q^1=q_L$ has
+about $10\epsilon_0$ which is larger than the excitation energies
+of the second excitation.
+Therefore, all the trajectories are ``closed'' in the usual sense.
+
+%We skipped the result about $\ket{0_3^+}$.
 \begin{table}[htbp]
 \begin{ruledtabular}
-\begin{tabular}{c|c|cccccc}
-            & $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
-$0_2^+$ one & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
-phonon &ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
-$0_4^+$ two & Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
-phonon &ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
+\begin{tabular}{c|cccccc}
+            $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
+ASCC+SPA (1st exc.) & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\
+    Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\ \hline
+ASCC+SPA (2nd exc.)& $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
+Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$
 \end{tabular}
 \end{ruledtabular}
-\caption{Excitation energies of one-phonon and two-phonon states from exact solution and ASCC+SPA calculation.
-In a chosen collective subspace, one-phonon and two-phonon states correspond to the first and second excitation, respectively.
-In the whole Hilbert space, one-phonon and two-phonon states correspond to $\ket{0_2^+}$ and $\ket{0_4^+}$, respectively.}
+\caption{Calculated excitation energies of the first and the second
+excited states in units of $\epsilon_0$.
+In the exact calculation, the second excited state in the ASCC+SPA
+corresponds to the $0_4^+$ state.
+See text for details.}
 \label{ex}
@@
  \end{center}
-	\caption{The strength of pair additional transition
-$B(P_{\rm ad};k\rightarrow k')=|\braket{N+2,k'|S^+|N,k}|^2$, from $N=14$ to $N=22$.
-Dashed lines are exact solution and solid lines are ASCC+SPA calculation.
-Horizontal line shows the particle number of the initial states.
-Upper panel shows the intraband transitions of
+\caption{Calculated strength of pair-addition transition (\ref{BPad})
+from $N=14$ to $N=22$. 
+The solid (dashed) lines correspond to the ASCC+SPA (exact) calculation.
+The horizontal line indicates the particle number of the initial states.
+The upper panel shows the intraband transitions,
 $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$,
-while lower panel shows the interband transition of
+while lower panel shows the interband transitions,
 $\ket{0_1^+}\to\ket{0_2^+}$ and $\ket{0_2^+}\to\ket{0_1^+}$.
@@
 
-\subsection{Pb isotopes}
-With pairing model, we study neutron's pairing vibration in Pb isotope.
-We prepare the neutron's single-particle level between the magic number 82 and 126 (Table \ref{Pb}).
-The coupling constant $g=0.138$(MeV) is determined to reproduce the experimental pairing gap $\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb.
-We consider the even-even system from ${}^{188}$Pb to ${}^{194}$Pb.
+\subsection{Non-integrable case (2): Pb isotopes}
+\label{sec:Pb_isotopes}
+
+Finally, we apply our method to neutrons' pairing dynamics in 
+neutron-deficient Pb isotopes.
+The spherical single-particle levels of neutrons
+between the magic number 82 and 126 are adopted and
+their energies are presented in Table \ref{Pb}. 
+The coupling constant $g=0.138$ MeV is determined to reproduce
+the experimental pairing gap given by the even-odd mass difference,
+$\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb.
+The even-even nuclei from ${}^{188}$Pb to ${}^{194}$Pb
+are studied.
 \begin{table}[htbp]
@@
 \end{ruledtabular}
-\caption{Single-particle levels of Pb isotopes used in the calculation. The orbits are obtained from spherical Woods-Saxon potential with spin-orbit coupling. }
+\caption{Single-particle energies of Pb isotopes used in the calculation
+in units of MeV.
+These are obtained from spherical Woods-Saxon potential
+with the universal parameters(?) \cite{??}. }
 \label{Pb}
@@
 
-We have six TDHFB degrees of freedom in the system.
-Fig.
-\ref{Pb_omega_sq} shows the eigenvalue of moving-frame QRPA equation.
-We can find there are one spurious mode and five vibrational modes.
-The collective modes we focus on did not cross with other modes in all panels, while the spacings of the collective modes and the second vibrational modes are small, especially for ${}^{194}$Pb.
-Under the chosen collective modes, the occupation number is shown in Fig.
-\ref{Pb_occ_number}.
-As with three-level system, the left end points correspond to HF state in all panels.
-The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
-In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ orbits change significantly, while other orbits don't change so much.
-The collective potential for each isotope is shown in Fig.
-\ref{Pb_potential}.
-The depths of them are about $2.5\sim3.5$(MeV) only enough to bind $\ket{0_2^+}$, one-phonon states.
-We can consider that the collectivity of pairing is small for excited states, even though their ground states are superfluid states.
+The TDHFB dynamics is described by six degrees of freedom.
+Figure \ref{Pb_omega_sq} shows eigenvalues of the
+moving-frame QRPA equation.
+Again, we find that there is a zero mode corresponding to
+the neutron pair rotation.
+Among the five vibrational modes, we choose the lowest one to
+construct the collective path in the ASCC.
+This lowest mode never crosses with other modes,
+though the spacing between the lowest to the next lowest mode
+can be very small, especially for ${}^{194}$Pb.
+The evolution of the occupation numbers along the collective path
+is shown in Fig. \ref{Pb_occ_number}.
+Similarly to the three-level model, 
+the end points of the collective path indicate exactly
+the integer numbers, and
+the left end of each panel corresponds to the ``HF''-like state.
+On the collective path, the occupation of $i_{13/2}$, $p_{3/2}$, and
+$f_{5/2}$ mainly changes.
+%The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
+
+The collective potentials for these isotopes are shown
+in Fig. \ref{Pb_potential}.
+The heights of the potentials at the left end, $V(q_L)-V(0)$,
+are $2\sim3.5$ MeV.
+For $^{186}$Pb, the height of the potential is not
+enough to satisfy the condition, $E<V(q_L)$,
+to have a closed trajectory for the first excited state
+(See the last paragraph in Sec.~\ref{sec:three-level-model}).
+We encounter another kind of problem for $^{196}$Pb,
+which will be discussed in Sec.~\ref{sec5}.
+Therefore, in this paper, we calculate the first excited states
+in $^{188,190,192,194}$Pb.
+
 \begin{figure*}[t]
@@
 
-We show the results of $\ket{0_2^+}$, one-phonon state in the collective coordinate, from SPA.
-Table \ref{Pb} shows the excitation energy.
-The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction.
-We are only interested in the comparison between exact solution and ASCC+SPA.
-We can find the excitation energy from ASCC+SPA reproduce the exact solution as well as in three-level system.
-The pair additional transition strength is shown in Fig.
-\ref{PbPad}.
-The feature is similar to the case in three-level system, dominant intraband transition and the accuracy from ASCC+SPA.
-The deviation of $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ has about $25\%$ deficiency compared with exact solution.
-Therefore, ASCC+SPA gives reasonable results in realistic single-particle level systems.
+We show the calculated excitation energy of the first excited state
+in Table~\ref{Pb}.
+Experimentally, this pairing vibrational excited $0^+$ state is
+fragmented into several $0^+$ states due to other correlations,
+such as quadrupole correlation, not taken into account in the present model.
+%The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction. 
+We make a comparison with the exact solution of the multi-level
+pairing model.
+The ASCC+SPA method quantitatively reproduces the excitation energy of
+the exact solution.
+
+The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
+The feature similar to the three-level case is observed;
+dominant intraband transition and very weak interband transitions.
+the accuracy from 
+The ASCC+SPA method well reproduces
+$B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$,
+and qualitatively reproduces
+$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ as well.
+The deviation for the latter is about $25\%$.
+The interband transitions are smaller than the intraband transitions
+by more than two orders of magnitude.
+This is also similar to the three-level model discussed
+in Sec.~\ref{sec:three-level-model}.
+For such weak transitions, the ASCC+SPA significantly
+underestimates the strengths.
+We may say that the ASCC+SPA gives reasonable results for the intraband
+transitions in realistic values of pairing coupling constant $g$ and
+single-particle levels.
+
 \begin{table}[htbp]
@@
    & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
- Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$\\
-ASCC+SPA & unbound & $2.31$ & $2.21$ & $2.12$ & $2.04$ & unbound \\ 
+ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
+Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
 \end{tabular}
@@
 
-Finally, we discuss about the validity of the collective treatment of the pairing.
-We know that the 5D collective model described by the quadrupole deformation parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,0)$ is widely applied to analyze experimental data.
-As with the 5D collective model, pairing can also be supposed as a sort of deformation.
-The collective model is described by the pair deformation parameters pairing gap $\Delta$ and global gauge angle $\Phi$.
-The utilization of the collective model for nuclear pairing dynamics was done in several references\cite{??}.
+Finally, we discuss the validity of the collective model approach
+assuming the pairing gap as a collective coordinate.
+The 5D collective Hamiltonian assuming the quadrupole deformation
+parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,0)$ as the collective coordinates
+is widely utilized to analyze experimental data of quadrupole states.
+Similarly, we may construct the pairing collective Hamiltonian
+in terms of the pairing gap $\Delta$ and the gauge angle $\Phi$. 
+As far as there is one-to-one correspondence between $\Delta$ 
+and the collective variable $q^1$ we obtained in the present study,
+we can transform the collective Hamiltonian in $(q^1,\Phi)$
+into the one in $(\Delta,\Phi)$.
+The pairing gap $\Delta$ is defined as
+\begin{align}
+  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|S^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
+  &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
+\end{align}
+Figure \ref{192Pb_gap} shows the pairing gap $\Delta$ in ${}^{192}$Pb
+as a function of the collective coordinate $q^1$.
+The peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
+function of $q^1$, thus, no one-to-one correspondence exists.
+The same behavior is observed for other Pb isotopes too.
+Therefore, the pairing gap $\Delta$ is not suitable collective coordinate
+to describe the pairing dynamics in the multi-level model.
+
+%Because only one orbit near the Fermi energy ($i_{13/2}$ orbit for both end points) contributes the value of pairing gap, the value at both end points are small compared with the value around the ground state.
+There is no one-to-one correspondence between $\Delta$ and $q$ not only in ${}^{192}$Pb, but also in all multi-level systems.
+
+%As with the 5D collective model, pairing can also be supposed as a sort of deformation. The collective model is described by
+%the pair deformation parameters pairing gap $\Delta$ and global gauge angle $\Phi$. 
+%The utilization of the collective model for nuclear pairing dynamics was done in several references\cite{??}.
 In our previous study, however, we find that the pairing gap $\Delta$ is not proper to be the collective coordinate in two-level pairing model \cite{??}.
 In multi-level system, we can investigate the relations between the pairing gap and the collective coordinate.
-The pairing gap $\Delta$ is defined as
-\begin{align}
-  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|S^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
-  &= g\sum_l \sqrt{j_l(\Omega_l-j_l)} .
-\end{align}
-Fig.
-\ref{192Pb_gap} shows the pairing gap of $\Delta$ in ${}^{192}$Pb as a function of the collective coordinate $q$.
-We can see that the peak is near $q=0$ and both end points have small values.
-Because only one orbit near the Fermi energy ($i_{13/2}$ orbit for both end points) contributes the value of pairing gap, the value at both end points are small compared with the value around the ground state.
-There is no one-to-one correspondence between $\Delta$ and $q$ not only in ${}^{192}$Pb, but also in all multi-level systems.
-Therefore, the pairing gap $\Delta$ cannot properly describe the pairing dynamics.
+
 \begin{figure}[htbp]
@@
 \label{sec5}
-Based on our previous work which demonstrated the accuracy of SPA for the requantization of TDHFB dynamics, we considered the application of SPA to non-integrable system.
-The one of the possible way to extend SPA into non-integrable system is to combine with ASCC.
-We constructed the theoretical framework of ASCC+SPA for bound states, which is bound in the collective potential from ASCC.
+
+Extending our former work \cite{NN18},
+which demonstrated the accuracy of SPA for the requantization
+of TDHFB dynamics in the two-level pairing model, 
+we propose the ASCC+SPA method for non-integrable systems.
+In this approach, we use the ASCC method to extract the 2D
+collective subspace including the pair rotation.
+In other words, we map the non-integrable system to an approximate
+integrable system described by $(q^1,p_1;J,\Phi)$.
+
+%to extend SPA into non-integrable system is to combine with ASCC. We constructed the theoretical framework of ASCC+SPA for bound states, which is bound in the collective potential from ASCC. 
 %Besides the collective Hamiltonian, $Q$ operator at each point of collective path is also necessary input information.
 
-We applied ASCC+SPA into multi-level pairing model.
-Because the global gauge angle $\Phi$ is a cyclic variable, the simplest non-integrable system is three level system.
-We investigated three level system and more realistic system, neutron's single-particle levels from Pb isotope.
-In both cases, the low-lying excited $0^+$ states from ASCC+SPA reproduce exact solution well not only for excitation energies but also for wave functions.
-In ASCC+SPA, the pair transition calculation has no difficulty because we don't need to requantize the pair transition operators.
-This point overcomes the disadvantage in canonical requantization.
-
-While the basic theoretical framework of ASCC+SPA was constructed, there are several problems remaining.
-Up to now, ASCC+SPA is only available when the excited states are bound in the pocket of collective potential (See Fig.
-\ref{potential} and \ref{Pb_potential}).
-For example, we cannot calculate $\ket{0_2^+}$ in ${}^{186}$Pb because the potential is too shallow to bound the excited state.
-The difficulty for the application to the unbound states is that the wave function from SPA is not stationary state because the classical trajectory in phase space is not periodic.
-It is necessary to find some proper boundary conditions in the collective subspace.
-The second problem is about the crossing of the eigenvalues from moving-frame QRPA equation in the collective path.
-No problem occurs when two completely orthogonal modes crossing, such as rotational mode and vibrational mode (e.g.
-N=14,16,18,20 in Fig.
-\ref{omega_sq}).
-However, if two vibrational modes not orthogonal with each other become the same eigenvalues, the ASCC calculation stops.
-Actually, the two eigenvalues become complex conjugate values and the next mesh point of collective path cannot be decided properly.
-Such case is occurred in ${}^{196}$Pb.
-The eigenvalues crossing problem supposed to be the rare case because ${}^{196}$Pb system is the only case including the previous studies about the application of ASCC.
-In addition, we need to consider the multi energy minimum pockets in the collective potential \cite{HNMM07, HNMM08}.
-Such case doesn't appear in pairing model.
-When the excitation energy is below the multi minimum pocket, the EBK quantization condition is not unique.
-With these problems, the theoretical framework of ASCC+SPA need to be developed in the next step.
+We apply the ASCC+SPA method to the multi-level pairing model.
+%Because the gauge angle $\Phi$ is a cyclic variable, 
+%the simplest non-integrable system is three level system. 
+We investigate the three-level model and 
+the multi-level model simulating Pb isotopes
+with realistic pairing coupling constant $g$ and single-particle levels.
+In both cases, the low-lying excited $0^+$ states obtained with
+the ASCC+SPA well reproduce the exact solutions
+not only of excitation energies but also of wave functions.
+In the ASCC+SPA, the pair-transition calculation is straightforward,
+because we have a microscopic wave function for every quantized state.
+This overcomes a disadvantage in the conventional canonical requantization
+in which we need to construct the pair-transition operator
+in terms of the collective variables only.
+
+Although the overall agreement between the ASCC+SPA and the exact
+calculations is good in general,
+we have encountered several problems remaining to be solved.
+First, we can calculate a classical trajectory bound by the
+pocket of a potential, however, it is not trivial how to treat
+``unbound'' trajectories that hit the end point of the collective path.
+See the potentials in Figs. \ref{potential} and \ref{Pb_potential}.
+This happens in the calculation of ${}^{186}$Pb
+(Sec.~\ref{sec:Pb_isotopes}).
+Probably, it is necessary to find a proper boundary condition
+in the collective subspace.
+For instance, the 5D quadrupole collective model has
+such boundary conditions imposed by the symmetry property of
+the quadrupole degrees of freedom \cite{KB67}.
+
+The second problem occured in the calculation of $^{196}$Pb,
+in which we have encountered complex eigenvalues and eigenvectors
+of the moving-frame QRPA equation.
+This happens at a point where the two eigenenegies become
+identical, $\omega_1^2=\omega_2^2$, namely at a crossing point.
+We do not have a problem for the crossing between the pair rotational
+mode and the other modes.
+Currently, we do not know exactly when the complex solutions emerge.
+
+Another problem we need to solve is a description of the
+quantum tunneling.
+The tunneling plays an essential role in
+spontaneous fission, sub-barrier fusion reaction, and
+shape coexistence phenomena \cite{NMMY16,WN16,WN17,HNMM07,HNMM08}.
+In the present ASCC+SPA, the classical trajectory
+cannot penetrate the potential barrier.
+Since the ASCC is able to provide the 1D collective coordinate,
+the imaginary-time TDHF is feasible and may be a solution
+to this problem \cite{Neg82}.
+These remaining issues in the ASCC+SPA approach should be
+addressed in future.
+
+%The crossing of the eigenvalues from the moving-frame QRPA equation
+%in the collective path.
+%No problem occurs when two completely orthogonal modes crossing, such as rotational mode and vibrational mode (e.g. N=14,16,18,20 in Fig. \ref{omega_sq}).
+%However, if two vibrational modes not orthogonal with each other become the same eigenvalues, the ASCC calculation stops.
+%Actually, the two eigenvalues become complex conjugate values and the next mesh point of collective path cannot be decided properly. Such case is occurred in ${}^{196}$Pb.
+%The eigenvalues crossing problem supposed to be the rare case because ${}^{196}$Pb system is the only case including the previous studies about the application of ASCC.
+
+%The difficulty for the application to the unbound states is that the wave function from SPA is not stationary state because the classical trajectory in phase space is not periodic.
 
 \begin{acknowledgments}
-This work is supported in part
-by Interdisciplinary Computational Science Program in CCS,
-University of Tsukuba,
+This work is supported in part by JSPS KAKENHI Grants No. ????
 and
@@
 on Nuclear mass and life for unravelling mysteries of r-process.
+Numerical calculations were performed in part using COMA at the CCS,
+University of Tsukuba.
 %and by ImPACT Program of Council for Science,

### 2018-10-25 paper2/draft1-3.tex
small change

@@
 we expect similar magnitude of strengths for
-$B(P_{\rm ad};{\rm g.s.}\rightarrow i{\rm 1 phonon})$
+$B(P_{\rm ad};{\rm g.s.}\rightarrow {\rm 1-phonon})$
 and
-$B(P_{\rm ad};{\rm 1 phonon}\rightarrow i{\rm 2 phonon})$,
+$B(P_{\rm ad};{\rm 1-phonon}\rightarrow i{\rm 2-phonon})$,
 but smaller values of
-$B(P_{\rm ad};{\rm g.s.}\rightarrow i{\rm 2 phonon})$.
+$B(P_{\rm ad};{\rm g.s.}\rightarrow {\rm 2-phonon})$.
 Thus, the $0_4^+$ state in the exact calculation
@@
 are shown in Fig. \ref{3levelPad}.
-For the intraband transition ($k=k'$ in Eq. (\ref{BPad}),
+For the intraband transition ($k=k'$ in Eq. (\ref{BPad})),
 the ASCC+SPA method well reproduces the strengths of the exact calculation.

### 2018-10-25 paper2/draft1-3.tex
Small change again

@@
 we expect similar magnitude of strengths for
-$B(P_{\rm ad};{\rm g.s.}\rightarrow {\rm 1-phonon})$
+$B(P_{\rm ad};{\rm g.s.}\rightarrow \omega_{\rm phon})$
 and
-$B(P_{\rm ad};{\rm 1-phonon}\rightarrow i{\rm 2-phonon})$,
+$B(P_{\rm ad};\omega_{\rm phon}\rightarrow 2\omega_{\rm phon})$,
 but smaller values of
-$B(P_{\rm ad};{\rm g.s.}\rightarrow {\rm 2-phonon})$.
+$B(P_{\rm ad};{\rm g.s.}\rightarrow 2\omega_{\rm phon})$.
 Thus, the $0_4^+$ state in the exact calculation

### 2018-11-01 paper2/draft1-4.tex

--- 2018-10-25 paper2/draft1-3.tex
@@
 	-\lambda_{1} q^1(\xi) - \lambda_{n} q^n(\xi,\pi) .
+\label{H_M}
 \end{align}
@@
 
-%%%%%% I guess this is automatic. Check %%%%%%%%
-%To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_{\alpha} f^1_{,\alpha}=0$, we correct the eigenvectors by
-%\begin{align}
-%  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_{\beta} f^1_{,\beta} 
-%  \label{f}
-%\end{align}
-%after solving (\ref{LHE}) at each point of $q$.
-
 In the present pairing model, 
 from Eq. (\ref{total_gauge}), we find $J$ does not dependent on $\chi$.
-This means $f^{(1)n\alpha\beta}=0$ in Eq. (\ref{P}),
+This means $f^{(1)n\alpha\beta}=0$ in Eq. (\ref{q^n}),
 thus, $\tilde{B}^{\beta\gamma}=B^{\beta\gamma}$.
 The second derivative of $J$ with respect to $j$ also vanishes,
-which indicates $f^{I}_{,\gamma\beta}$ in Eq.~(\ref{M}) is zero. 
+which indicates $f^n_{,\gamma\beta}$ in Eq.~(\ref{M}) is zero. 
 %It indicates the chemical potential $\lambda_I(q)$ is not necessary information to calculate the matrix element in moving-frame QRPA equation.
-In the present model, it is easy to find an explicit expression
-for the gauge angle $\Phi$.
-\begin{align}
-  \Phi = \frac{1}{L}\sum_{\alpha} \chi_{\alpha},
+The gauge angle $\Phi$ is locally determined
+by the solution of Eq. (\ref{mfQRPA}).
+\begin{align}
+%  \Phi = \frac{1}{L}\sum_{\alpha} \chi_{\alpha},
+\Phi = g^\alpha_{,n} \chi_{\alpha},
   \label{total_gauge}
 \end{align}
-where $L$ is the number of available shells $\alpha=1,\cdots,L$.
-Its conjugate variable
-${\partial\mathcal{L}}/{\partial\dot{\Phi}}$
-is indeed given by $J$ of Eq. (\ref{J}).
-Again, exchanging coordinate and momentum,
-we have $q^n=J$ and $p_n=-\Phi$.
+%where $L$ is the number of available shells $\alpha=1,\cdots,L$.
+%Its conjugate variable
+%${\partial\mathcal{L}}/{\partial\dot{\Phi}}$
+%is indeed given by $J$ of Eq. (\ref{J}).
+%Again, exchanging coordinate and momentum,
+%we have $q^n=J$ and $p_n=-\Phi$.
 
@@
 %is conserved quantity.
+
+%%%%%% Gauge fixing %%%%%%
+It should be noted \cite{N2012} that the definition of the collective
+variables $(q^1,p_1)$ are not unique, because it can be arbitrarily mixed
+with the pair rotation $(q^n,p_n)$ as
+\begin{equation}
+	q^1 \rightarrow q^1 + c q^n,  \quad
+	p_n \rightarrow p_n -c p_1
+\end{equation}
+with an arbitrary constant $c$.
+Numerically, this arbitrariness sometimes leads to a problematic bahavior 
+in iterative procedure of the ASCC.
+In order to fix the parameter $c$, we adopt a condition
+called ``ETOP'' in Ref.~\cite{HNMM07}.
+\begin{align}
+\sum_\alpha f^1_{,\alpha} = 0 ,
+\end{align}
+with 
+\begin{align}
+{f}^1_{,\alpha} \to f^1_{,\alpha} + c f^n_{,\alpha} .
+  \label{f}
+\end{align}
+%after solving (\ref{LHE}) at each point of $q$.
 
@@
 \begin{equation}
-\ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_q} .
+\ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1} .
 \end{equation}
@@
 These are obtained from spherical Woods-Saxon potential
-with the universal parameters(?) \cite{??}. }
+with the parameters of Ref.~\cite{BM69}.
+}
 \label{Pb}
@@
 \begin{acknowledgments}
-This work is supported in part by JSPS KAKENHI Grants No. ????
+This work is supported in part by JSPS KAKENHI Grants No. 18H01209
 and

### 2018-11-01 paper2/draft1-4.tex
draft 1-4

@@
 called ``ETOP'' in Ref.~\cite{HNMM07}.
-\begin{align}
-\sum_\alpha f^1_{,\alpha} = 0 ,
-\end{align}
-with 
+We require the following condition to determine $c$:
+\begin{align}
+\sum_\alpha 
+	f^1_{,\alpha} = 0 ,
+\end{align}
+where $f^1_{,\alpha}$ is replaced as
 \begin{align}
@@
 	&\equiv \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
-	\label{tau}
+%	\label{tau}
 \end{align}
@@
 $\Omega_1=\Omega_2=8$, 
-the pairing strength $g/(\epsilon_2-\epsilon_1)=0.2$,
+the pairing strength $g/\epsilon_0=0.2$,
 and the particle number $N=16$. 
+In this two-level case, we use the level spacing,
+$\epsilon_0\equiv \epsilon_2-\epsilon_1$,
+as the unit of energy.
 The moving-frame QRPA produces the zero mode and another eigenvector
@@
 collective coordinate, $dq=0.01$,
-in units of $1/\sqrt{\epsilon_2-\epsilon_1}$.
+in units of $1/\sqrt{\epsilon_0}$.
 We confirm that the pair rotation always has zero frequency
@@
 $(\Phi,J;\phi,j)$ using the Hamiltonian truncated up to the
-second order in $\chi_\alpha$ (``ATDHFB trajectories''),
+second order in $\chi_\alpha$ (``TDHFB2 trajectories''),
 we obtain the solid lines in Fig. \ref{fig:N16_traj},
@@
 with each other, while we see small deviation between the full TDHFB
-and the ASCC/ATDHFB calculations for the $0_3^+$ state.
+and the ASCC/TDHFB2 calculations for the $0_3^+$ state.
 
@@
 into $2n$-particle-$2n$-hole components. 
-The left end of the horizontal axis at $j=j_{\rm min}$
+The left end of the horizontal axis at $m_2-m_1=-8$
 corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
-are in the lower level $\epsilon_1$.
-The next at $j=j_{\rm min}+1$ corresponds to the one with
-$(m_1,m_2)=(N-2/2,1)$, and so on.
-The results from ATDHFB+SPA and ASCC+SPA are identical to each other
+are in the lower level $\alpha=1$.
+The next at $m_2-m_1=-6$ corresponds to the one with
+$(m_1,m_2)=((N-2)/2,1)$, and so on.
+The results from TDHFB2+SPA and ASCC+SPA are identical to each other
 within numerical error, which well reproduces
@@
 Crosses, solid and dashed lines correspond to the results
-of ASCC+SPA, ATDHFB+SPA, and TDHFB+SPA, respectively. 
+of ASCC+SPA, TDHFB2+SPA, and TDHFB+SPA, respectively. 
 For the ASCC+SPA trajectories, we plot the crosses
@@
 Crosses, solid and dashed lines correspond to the ASCC+SPA,
-the ATDHFB+SPA, and the TDHFB+SPA, respectively. 
+the TDHFB2+SPA, and the TDHFB+SPA, respectively. 
 %Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
-We calculated the action integrals on each trajectory
+We calculate the action integrals on each trajectory
 from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction
@@
 The vertical bars at each $m_2-m_1$
-represent the ASCC+SPA, ATDHFB+SPA and TDHFB+SPA calculations,
+represent $|C_m|^2$ of Eq. (\ref{coef}) in
+ASCC+SPA, TDHFB2+SPA and TDHFB+SPA calculations,
 respectively, from left to right.
@@
 The left end of each panel in Fig.~\ref{occ_number} corresponds to 
-a kind of ``Hartree-Fock'' state which minimizes
+a kind of ``Hartree-Fock'' (HF) state which minimizes
 the single-particle-energiy sum, $\sum_\alpha 2j_\alpha \epsilon_\alpha$.
@@
  \end{center}
-	\caption{Eigenvalues of moving-frame QRPA equation with respect to the collective coordinate $q$, from $N=14$ to $N=24$.
-Purple lines are spurious modes and green lines are chosen modes corresponding to the collective coordinate.
-In each panel, both edges correspond to the end points of the collective coordinate.
+\caption{Eigenvalues of moving-frame QRPA equation with respect
+to the collective coordinate $q^1$, from $N=14$ to $N=24$.
+The thick (green) lines are the modes we choose as
+the collective coordinate $q^1$,
+while the dashed lines correspond to the zero modes ($q^n$).
+In each panel, both ends of the horizontal axis corresponds
+to the ending points of the collective path $q^1$.
 }
@@
  \end{center}
-	\caption{Occupation numbers in each single-particle level with respect to the collective coordinate $q$, from $N=14$ to $N=24$.
-At the left end point of the collective coordinate in each panel, the configurations correspond to Hartree-Fock (HF) states.
+\caption{Occupation numbers in each single-particle level
+with respect to the collective coordinate $q$,
+from $N=14$ to $N=24$.
+The purple, green, and blue lines correpsond to
+$\alpha=1$, 2, and 3, respectively.
+At the left end point of the collective coordinate in each panel,
+the configurations correspond to the ``HF-like'' states.
+See text for details.
 }
@@
  \end{center}
-	\caption{Collective potential obtained from ASCC. We adjusted the energy minimum point as $V=0$.
+	\caption{Collective potential $V(q^1)$ obtained from ASCC.
+	We adjust the energy minimum point as $q^1=0$ and $V=0$.
 }
@@
 %We skipped the result about $\ket{0_3^+}$.
-\begin{table}[htbp]
+\begin{table}[tb]
 \begin{ruledtabular}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tb]
  \begin{center}
@@
 The upper panel shows the intraband transitions,
-$\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$,
+$0_1^+\to 0_1^+$ and $0_2^+\to 0_2^+$,
 while lower panel shows the interband transitions,
-$\ket{0_1^+}\to\ket{0_2^+}$ and $\ket{0_2^+}\to\ket{0_1^+}$.
+$0_1^+ \to 0_2^+$ and $0_2^+\to 0_1^+$.
 }
@@
 the integer numbers, and
-the left end of each panel corresponds to the ``HF''-like state.
+the left end of each panel corresponds to the
+``Hartree-Fock''-like state.
 On the collective path, the occupation of $i_{13/2}$, $p_{3/2}$, and
@@
  \end{center}
-	\caption{Pairing gap as a function of collective coordinate in ${}^{192}$Pb. 
+	\caption{Pairing gap as a function of collective coordinate $q^1$
+	in ${}^{192}$Pb. 
 }

### 2018-11-05 paper2/draft1-5.tex
Add files via upload

--- 2018-11-01 paper2/draft1-4.tex
@@
     \renewcommand{\theequation}{%
-    \thesection.\arabic{equation}}
+    \arabic{section}.\arabic{equation}}
+      %\thesection.\arabic{equation}}
     \@addtoreset{equation}{section}
@@
 \title{Low-lying collective excited states in non-integrable pairing models
-based on stationary phase approximation to the path integral}%
+based on stationary-phase approximation to path integral}%
 
@@
 \author{Nobuo Hinohara}
+ \affiliation{Center for Computational Sciences,
+              University of Tsukuba, Tsukuba 305-8577, Japan}
   \affiliation{Faculty of Pure and Applied Sciences,
               University of Tsukuba, Tsukuba 305-8571, Japan}
- \affiliation{Center for Computational Sciences,
-              University of Tsukuba, Tsukuba 305-8577, Japan}
 \author{Takashi Nakatsukasa}
@@
 \begin{abstract}
-For a description of large amplitude collective motion associated with
+For a description of large-amplitude collective motion associated with
 nuclear pairing, requantization of time-dependent mean-field dynamics
-is performed using the stationary phase approximation (SPA) to the path
+is performed using the stationary-phase approximation (SPA) to the path
 integral.
-A disadvantage of the SPA is that it is applicable only to integrable systems.
-We overcome this difficulty by developing a requantization approach
-combining the SPA with the adiabatic
-self-consistent collective coordinate method (ASCC+SPA).
-We apply the theoretical framework of ASCC+SPA to 
-a multi-level pairing models, which is non-integrable systems,
+We overcome the difficulty of the SPA, which is known to be applicable to integrable systems only,
+by developing a requantization approach combining the SPA with the adiabatic self-consistent collective coordinate method (ASCC+SPA).
+%A disadvantage of the SPA is that it is applicable only to integrable systems.
+%We overcome this difficulty by developing a requantization approach
+%combining the SPA with the adiabatic
+%self-consistent collective coordinate method (ASCC+SPA).
+We apply the theoretical framework of the ASCC+SPA to 
+multi-level pairing models, which are non-integrable systems,
 to study the nuclear pairing dynamics.
@@
 Effect of the pairing is prominent in many observables for the ground states,
-such as odd-even mass difference, moment of inertia of rotational bands,
+such as the odd-even mass difference, moment of inertia of rotational bands,
 and common quantum number $J^\pi=0^+$ for even-even nuclei \cite{RS80}.
-Elementary excitations associated with the pairing,
-pairing vibrations and pairing rotations,
+Collective excitations associated with the pairing, such as
+pair vibrations and pair rotations,
 have been observed in a number of nuclei \cite{BB05}.
-Most of these states, ``excited'' from neghboring even-even systems,
+Most of these states that are ``excited'' from neighboring even-even systems
 are associated with the ground $J^\pi=0^+$ states in even-even nuclei.
@@
 In this paper,
-we aim to understand the dynamics from pairing correlation in nuclei
-from microscopic view point.
+we aim to understand the dynamics associated with pairing correlation in nuclei
+from a microscopic view point.
 
@@
 the dynamics of nuclei from the microscopic degrees of freedom.
-Inclusion of the pairing dynamcs leads to the
+Inclusion of the pairing dynamics leads to the
 time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory,
@@
 and structure \cite{NMMY16}.
-The small-amplitude approximation of TDHFB with modern energy density
-functionals, quasiparticle random phase approximation (QRPA), 
-has successfully reproduced properties of giant resonances in nuclei.
+The small-amplitude approximation of the TDHFB with modern energy density
+functionals, the quasiparticle random-phase approximation (QRPA), 
+has successfully reproduced the properties of giant resonances in nuclei.
 In contrast, the QRPA description of low-lying quadrupole vibrations
-is not as good as the giant resonances \cite{NMMY16}.
+is not as good as that of giant resonances \cite{NMMY16}.
 A large-amplitude nature of the quantum shape fluctuation is supposed to
@@
 microscopic degrees of freedom using the mean-field calculation and
-the cranking inertia formula \cite{Bar11,Del10,Fu13}.
+the cranking formula for the inertial masses \cite{Bar11,Del10,Fu13}.
 The 5DCH model is able to take into account fluctuations of
@@
 of interest.
-The ASCC was developed from the basic idea of self-consistent
-collective coordinate method (SCC) by Marumori and coworkers \cite{MMSK80}.
+The ASCC was developed from the basic idea of the self-consistent
+collective coordinate (SCC) method by Marumori and coworkers \cite{MMSK80}.
 It has been applied to the nuclear quadrupole dynamics including
-the shape coexistence \cite{KNMM05, HNMM07, HNMM08}.
+the shape coexistence \cite{KNMM05, HNMM08, HNMM09}.
 %A state in the collective subspace corresponds to a microscopic state
@@
 %previous work
-TDMF (TDHFB) theory corresponds to an SPA solution in the path integral
+The TDMF (TDHFB) theory corresponds to an SPA solution in the path integral
 formulation \cite{Neg82}.
-It lacks a part of quantum fluctuation
-important in the large amplitude dynamics.
+It lacks a part of quantum fluctuation that is
+important in the large-amplitude dynamics.
 To introduce the quantum fluctuation based on the TDHFB theory,
@@
 In our previous work \cite{NN18},
-we studied various requantization methods for the two-level pair model,
+we studied various requantization methods for the two-level pairing model,
 to investigate low-lying excited $0^+$ states.
 Since the collectivity is rather low in the pairing motion in nuclei,
-the canonical quantization often fails to produce an approximate answer
+the canonical quantization often fails to produce an approximate value %answer
 to the exact solution.
 In contrast,
-the stationary phase approximation (SPA) to the path integral \cite{SM88} 
+the stationary-phase approximation (SPA) to the path integral \cite{SM88} 
 can give quantitative results not only for the excitation energies, 
@@
 %We confirmed that SPA is superior to canonical requantization, especially for the calculation of two-particle transitional strength. 
-The quantized states obtained in the SPA has two advantages:
-First, the wave functions are given directly in terms of
-the microscopic degrees of freedom.
-Second, the restoration of broken symmetries are automatic.
-In the pair model, the quantized states are eigenstates of the particle number
+The quantized states obtained in the SPA have two advantages;
+first, the wave functions are given directly in terms of
+the microscopic degrees of freedom, and second,
+the restoration of the broken symmetries are automatic.
+In the pairing model, the quantized states are eigenstates of the particle-number
 operator.
-On the other hand, applications of the SPA has been limited to
+On the other hand, applications of the SPA have been limited to
 integrable systems.
@@
 In this paper,
-we propose a new approach of SPA applicable to the non-integrable systems,
+we propose a new approach of the SPA applicable to the non-integrable systems,
 which is based on the extraction of the one-dimensional (1D)
@@
 inside the TDHFB space, without any assumption. 
-Thus, our approach of ASCC+SPA to the pairing model
+Thus, our approach of the ASCC+SPA to the pairing model
 basically consists of two steps:
-(1) Find a decoupled 1D collective coordinate of the pair vibration,
+(1) find a decoupled 1D collective coordinate of the pair vibration,
 in addition to the pair rotational degrees of freedom.
-(2) Apply the SPA separately to each collective mode.
+(2) apply the SPA independently to each collective mode.
 %which implements SPA to non-integrable system by combing with ASCC. 
@@
 The paper is organized as follows. 
-Sec. \ref{sec2} introduces the theoretical framework of ASCC, SPA,
+Section \ref{sec2} introduces the theoretical framework of the ASCC, SPA,
 and their combination, ASCC+SPA. 
 In Sec. \ref{sec3}, we provide some details in the application
-of ASCC+SPA to the multi-level pairing model.
+of the ASCC+SPA to the multi-level pairing model.
 We give the numerical results in Sec. \ref{sec4}, including
@@
 we expand the Hamiltonian $\mathcal{H}(\xi,\pi)$ with respect to
-momenta $\pi$ up to second order.
-The TDHFB Hamiltonian is
+the momenta $\pi$ up to second order.
+The TDHFB Hamiltonian is written as
 \begin{align}
@@
 (4D phase space),
-described by a set of canonical variable $(q^1,q^2;p_1,p_2)$,
+described by a set of canonical variable $(q^1,q^2=q^n;p_1,p_2=p_n)$,
 which is well decoupled from the rest of degrees of freedom,
@@
 The collective Hamiltonian is given by imposing $q^a=p_a=0$,
-namely by restricing the space into the collective subspace.
+namely by restricting the space into the collective subspace
 \begin{equation}
@@
 \mathcal{H}_{\rm coll}(q,p;q^n)
-= \bar{V}(q^1;q^n) + \frac{1}{2}\bar{B}^{11}(q^1,q^n)p_1^2 .
+= \bar{V}(q^1,q^n) + \frac{1}{2}\bar{B}^{11}(q^1,q^n)p_1^2 .
   \label{coll}
@@
 In the collective Hamiltonian (\ref{coll}), the variable $q^n$ is
-trivially given as the particle number, which is expanded up to the
-second order in momenta $\pi$,
+trivially given as the particle number, which is expanded up to
+second order in the momenta $\pi$,
 \begin{equation}
@@
 and $\xi^\alpha$ on the subspace $\Sigma_2$ is given as
-$\xi^{\alpha} = g^{\alpha}(q^1,q_n,q^a=0)$.
+$\xi^{\alpha} = g^{\alpha}(q^1,q^n,q^a=0)$.
 The momenta on $\Sigma_2$ are transformed as
 \begin{align}
-p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha
+p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha,
 	\label{coll_momenta}\\
@@
 $(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
-The Einstein's convention for summation with respect to repeated
+The Einstein's convention for summation with respect to the repeated
 upper and lower indices is assumed hereafter.
@@
 the collective mass parameter
-$\bar{B}_{11}(q^1,q^n)=(\bar{B}^{11}(q^1,q^n))^{-1}$ can be given by
-\begin{align}
-\bar{V}(q^1,q^n) &= V(\xi=g(q^1,q^n,q^a=0)) \\
+$\bar{B}_{11}(q^1,q^n)=[\bar{B}^{11}(q^1,q^n)]^{-1}$ can be given by
+\begin{align}
+\bar{V}(q^1,q^n) &= V(\xi=g(q^1,q^n,q^a=0)), \\
 \bar{B}^{11}(q^1,q^n) &= f^1_{,\alpha}\tilde{B}^{\alpha\beta}(\xi)f^1_{,\beta} ,
@@
 Decoupling conditions for the collective subspace $\Sigma_2$ lead to
-the basic equations of ASCC method \cite{MNM00,N2012},
+the basic equations of the ASCC method \cite{MNM00,N2012},
 which determine tangential vectors,
@@
 \begin{align}
-  &\delta H_M(\xi,\pi) = 0 \label{mfHFB} \\ 
+  \delta H_M(\xi,\pi) = 0, \label{mfHFB}
+  \end{align}\begin{align}
 %  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
 %  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
-\mathcal{M}^\beta_\alpha f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
+ \mathcal{M}^\beta_\alpha f^1_{,\beta}  = \omega^2 f^1_{,\alpha},\hspace{2em} 
 \mathcal{M}^\beta_\alpha g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
@@
 Therefore, the collective mode of our interest corresponds to
-the mode with the lowest frequency except for the zero mode.
+the mode with the lowest frequency squared except for the zero mode.
 
@@
 \begin{enumerate}
-\item Find the HFB minimum point $\xi^\alpha_n$ ($n=0$)
+\item Find the HFB minimum point $\xi^\alpha_i$ ($i=0$)
 	by solving Eq. (\ref{mfHFB}) with $\lambda_1=0$.
-	Let us assume that this corresponds to $q^1_n=0$.
+	Let us assume that this corresponds to $q^1_i=0$.
 \item \label{step-2}
@@
 %The right eigenvector $g^{\alpha}_{,1}$ tell us the direction which system moves in energy surface. 
-Move to the next meighboring point
-$\xi^\alpha_{n+1}=\xi^\alpha_{n}+d\xi^\alpha$
+Move to the next neighboring point
+$\xi^\alpha_{i+1}=\xi^\alpha_{i}+d\xi^\alpha$
 with $d\xi^{\alpha}=g^{\alpha}_{,1}dq^1$.
-This corresponds to the collective coordinate, $q^1_{n+1}=q^1_n+dq^1$.
+This corresponds to the collective coordinate, $q^1_{i+1}=q^1_i+dq^1$.
 \item \label{step-4}
-At $\xi_{n+1}^\alpha$ $(q^1_{n+1})$,
+At $\xi_{i+1}^\alpha$ $(q^1_{i+1})$,
 obtain a self-consistent solution of
-Eqs. (\ref{mfQRPA}) and (\ref{mfHFB}),
+Eqs. (\ref{mfHFB}) and (\ref{mfQRPA})
 to determine
-$\xi^\alpha_{n+1}$, $f^1_{,\alpha}$, and $g^\alpha_{,1}$.
-\item Go back to \ref{step-3} to determine the next point
+$\xi^\alpha_{i+1}$, $f^1_{,\alpha}$, and $g^\alpha_{,1}$.
+\item Go back to Step \ref{step-3} to determine the next point
 on the collective path.
@@
 construct the collective path.
-In Step~\ref{step-2} and \ref{step-4}, we choose a mode
-with the lowest frequency $\omega^2$.
+In Steps~\ref{step-2} and \ref{step-4}, we choose a mode
+with the lowest frequency squared $\omega^2$.
 Note that $\omega^2$ can be negative.
@@
 Since the normalization of $f^1_{,\alpha}$ and $g^\alpha_{,1}$ is
-arbitrary as far as they satisfy Eq. (\ref{canonicity}).
-We fix this scale by an additional condition of $\bar{B}^{11}(q^1)=1$.
+arbitrary as far as they satisfy Eq. (\ref{canonicity}),
+we fix this scale by an additional condition of $\bar{B}^{11}(q^1)=1$.
 
@@
 
-\subsection{Stationary-phase approximation to the path integral}
+\subsection{Stationary-phase approximation to path integral}
 \label{sec:SPA}
@@
 For quantization of integrable systems,
-we can apply the stationary phase approximation (SPA)
+we can apply the stationary-phase approximation (SPA)
 to the path integral.
@@
 we have proposed and tested the SPA for an integrable pairing model.
-Since the collective Hamiltonian (\ref{coll}),
-extracted from TDHFB degrees of freedom, is integrable,
-kthe SPA is applicable to it.
+Since the collective Hamiltonian (\ref{coll}) that is
+extracted from the TDHFB degrees of freedom is integrable,
+the SPA is applicable to it.
 In this manner, we may apply the ASCC+SPA to
@@
 
-Since the Hamiltonian $\mathcal{H}_{\rm coll}$ of Eq.~(\ref{coll})
+Because the Hamiltonian $\mathcal{H}_{\rm coll}$ of Eq.~(\ref{coll})
 is separable,
 it is easy to find periodic trajectories on invariant tori.
-Since the pairing rotation corresponds to the motion of $p_n$
+Since the pair rotation corresponds to the motion of $p_n$
 with a constant $q^n$,
@@
 
-At each point in the space $(q^1,q_n; p_1,p_n)$ corresponds to
+At each point in the space $(q^1,q^n; p_1,p_n)$ corresponds to
 a generalized Slater determinant
@@
 where $(\xi,\pi)$ are given as
-$\xi^\alpha=g^\alpha(q^1,q_n,q^a=0)$ and
+$\xi^\alpha=g^\alpha(q^1,q^n,q^a=0)$ and
 $\pi_\alpha=f^1_{,\alpha}p_1+f^n_{,\alpha}p_n$.
@@
 \end{equation}
-where $(q,p)$ means $(q^1,q^n;p_1, p_n)$ and the weight function
-$\rho(q,p)$ is given through an invariant meaure $d\mu(q,p)$ as
+where $(q,p)$ means $(q^1,q^n;p_1, p_n)$, and the weight function
+$\rho(q,p)$ is given through an invariant measure $d\mu(q,p)$ as
 \begin{equation}
@@
 $\int d\mu(q,p) \ket{q,p}\bra{q,p} = 1$.
-An explicit form of $d\mu(q,p)$ for the present pairing model is presented
+An explicit form of $d\mu(q,p)$ for the present pairing model is shown
 in Eq. (\ref{dmu}).
@@
 of generalized Slater determinants $\ket{q,p}$.
-In addition, the integration with respect to $p_n$ over a circuit on torus
-automatically recover the broken symmetry, namely the good particle number.
+In addition, the integration with respect to $p_n$ over a circuit on a torus
+automatically recovers the broken symmetry, namely the good particle number.
 However, it relies on the existence of invariant tori.
-In the present approach of ASCC+SPA,
+In the present approach of the ASCC+SPA,
 we first derive a decoupled collective subspace $\Sigma_2$ and identify
-canonical varialbles $(q,p)$.
+canonical variables $(q,p)$.
 Because of the cyclic nature of $(q^n,p_n)$, it is basically a 1D system
@@
 
-For application of the ASCC+SPA method to the pairing model in Sec.~\ref{sec3},
+For the application of the ASCC+SPA method to the pairing model in Sec.~\ref{sec3},
 we summarize some notations and procedures to obtain quantized states.
@@
 the ``angle'' and the ``number'' variables, respectively.
-Although it is customary to take the angle as a coordinate,
-since the angle $\chi_\alpha$ is time-odd quantities, 
-we switch the coordinates and the momenta with minus signs
-in front of variables $\chi$.
+%Although it is customary to take the angle as a coordinate,
+%since the angle $\chi_\alpha$ is time-odd quantities, 
+%we switch the coordinates and the momenta with minus signs
+%in front of variables $\chi$.
+Although it is customary to take the time-odd angle $\chi_\alpha$ as a coordinate,
+we take the number $j^\alpha$ as a coordinate and the angle $-\chi_\alpha$ as a momentum with an additional minus sign.
 Similarly, the gauge angle $\Phi$ and the total particle number $J$
@@
 \item Calculate the action integral (\ref{tau}) for the $k$-th trajectory.
-\item Using Eq.~(\ref{SPA}), construct the $k$-th excited state.
+\item Construct the $k$-th excited state using Eq.~(\ref{SPA}).
 \end{enumerate}
@@
 
-We study low-lying excited $0^+$ states
-in multi-level pairing model by applying the ASCC+SPA.
+We study the low-lying excited $0^+$ states
+in the multi-level pairing model by applying the ASCC+SPA.
 The Hamiltonian of the pairing model is given in terms of
-single-particle energies $\epsilon_l$ and the pairing strength $g$ as
+the single-particle energies $\epsilon_l$ and the pairing strength $g$ as
 \begin{align}
@@
 \begin{eqnarray}
-        S_\alpha^0 &=& \frac{1}{2}(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_\alpha) ,\\
+        S_\alpha^0 &=& \frac{1}{2}\left(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_\alpha\right) ,\\
         S_\alpha^{+} &=& \sum_{m>0}a_{j_\alpha m}^{\dag}a_{j_\alpha\overline{m}}^{\dag} ,
@@
 \end{eqnarray}
-Each single-particle energy $\epsilon_\alpha$ possesses $(2\Omega_\alpha)$-fold
+Each single-particle energy $\epsilon_\alpha$ possesses $2\Omega_\alpha$-fold
 degeneracy ($\Omega_\alpha=j_\alpha+1/2$)
@@
 The occupation number of each level $\alpha$ is given by
-$
-\hat{n}_\alpha = \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m}
+$n_\alpha = \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m}
 =2S_\alpha^0+\Omega_\alpha
@@
 \end{equation}
-The magnitude of quasi-spin for each level is
+The magnitude of quasi-spin for each level is given by
 $S_\alpha=\frac{1}{2}(\Omega_\alpha-\nu_\alpha)$, where $\nu_\alpha$
 is the seniority
-quantum number, namely the number of unpaired particle at the level $\alpha$.
-In the present study, we only consider seniority zero states with
+quantum number, namely the number of unpaired particles at the level $\alpha$.
+In the present study, we consider only seniority-zero states with
 $\nu=\sum_\alpha \nu_\alpha=0$.
-The residual two-body interaction only consists of monopole pairing
+The residual two-body interaction consists of the monopole pairing
 interaction which couples two particles to zero angular momentum.
-We obtain exact solutions either by solving Richardson equation
+We obtain the exact solutions either by solving the Richardson equation
 \cite{Richardson,Richardson2,Richardson3} or
@@
 ($S_\alpha=\Omega_\alpha/2$) is constructed with
-time-dependent complex variables $Z_\alpha(t)$, as
+time-dependent complex variables $Z_\alpha(t)$ as
 \begin{equation}
 	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_\alpha(t)|^2\right)^{-\Omega_\alpha/2}
-	\exp [Z_\alpha(t) S_\alpha^{+}] \ket{0}
+	\exp [Z_\alpha(t) S_\alpha^{+}] \ket{0},
  \label{coherent}
 \end{equation}
-where $\ket{0}$ is the vacuum (zero particle) state.
-The TDHFB motion is given by the time dependence of $Z_\alpha(t)$.
+where $\ket{0}$ is the vacuum (zero-particle) state.
+The TDHFB motion is given by the time development of $Z_\alpha(t)$.
 In the SU(2) quasi-spin representation,
@@
 The coherent state $\ket{Z(t)}$ is a superposition of
-states with different particle numbers
+the states with different particle numbers
 without unpaired particles.
@@
 The TDHFB equation can be derived from the time-dependent variational
-principle ($\hbar=1$), $\delta \mathcal{S} = 0$, where
+principle, $\delta \mathcal{S} = 0$, where
 \begin{equation}
@@
 	\mathcal{S}\equiv \int \mathcal{L}(t) dt =
-	\int \braket{Z(t)|i\frac{\partial}{\partial t}-H|Z(t)}dt.
+	\int \braket{Z(t)|i\frac{\partial}{\partial t}-H|Z(t)}dt
   \label{TDHFB}
 \end{equation}
-After transformation of the complex into real variables,
+($\hbar=1$ applies hereafter).
+After the transformation of the complex variables into the real ones with
 $Z_\alpha = \tan{\frac{\theta_\alpha}{2}}e^{-i\chi_\alpha}$
-($0\leq\theta\leq\pi$),
+($0\leq\theta_\alpha\leq\pi$),
 the Lagrangian $\mathcal{L}$ and the expectation value of the Hamiltonian
@@
 \begin{align}
-	\mathcal{H}(Z,Z^*) &\equiv \braket{Z|H|Z}& \nonumber \\
-	&= \sum_\alpha \epsilon_\alpha\Omega_\alpha(1- \cos{\theta}_\alpha)
+	\mathcal{H}( &Z,Z^*) \equiv \braket{Z|H|Z}& \nonumber \\
+	=& \sum_\alpha \epsilon_\alpha\Omega_\alpha(1- \cos{\theta}_\alpha)
 	\nonumber \\
 	&- \frac{g}{4}\sum_\alpha \Omega_\alpha [\Omega_\alpha(1-\cos^2{\theta}_\alpha)+(1-\cos{\theta}_\alpha)^2] \nonumber \\
-	- \frac{g}{4}\sum_{\alpha\neq \beta} \Omega_{\alpha}\Omega_{\beta}&\sqrt{(1-\cos^2{\theta}_{\alpha})(1-\cos^2{\theta}_{\beta})}e^{-i(\chi_{\alpha}-\chi_{\beta})}   .
+& - \frac{g}{4}\sum_{\alpha\neq \beta} \Omega_{\alpha}\Omega_{\beta} \sqrt{(1-\cos^2{\theta}_{\alpha})(1-\cos^2{\theta}_{\beta})}e^{-i(\chi_{\alpha}-\chi_{\beta})}   .
 \label{TDHFB_Hamiltonian_2}
 \end{align}
-Choose $\chi_\alpha$ as canonical coordinates, their conjugate momenta
+We choose $\chi_\alpha$ as canonical coordinates, and their conjugate momenta
 are given by
@@
 \end{align}
-$\chi_\alpha$ represent a kind of gauge angle of each level,
-and $j^\alpha$ correspond to the occupation number of each level,
-$2j^\alpha=\bra{Z} \hat{n}_\alpha\ket{Z}$. 
+$\chi_\alpha$ represents a kind of gauge angle of each level,
+and $j^\alpha$ corresponds to the occupation number of each level,
+$2j^\alpha=\bra{Z} n_\alpha\ket{Z}$. 
 As we mention in Sec.~\ref{sec:notation},
@@
 %$\mathcal{H}(Z,Z^*) = \mathcal{H}(\{\chi_l\},\{j_l\})$, and 
-The TDHFB equation is equivalent to the classical Hamilton's equation
+The TDHFB equation is equivalent to classical Hamilton's equations
 \begin{equation}
@@
 %In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec. \ref{ASCC}. 
-We construct a 2D collective subspace $\Sigma_2$ from ASCC theory.
+We construct a 2D collective subspace $\Sigma_2$ from the ASCC method.
 %Because the first order with respect to $\chi_{\alpha}$ is zero in TDHFB Hamiltonian, we assume $j^{\alpha}$ as coordinates and $\chi_{\alpha}$ as conjugate momenta.
@@
 We expand the classical Hamiltonian up to second order with respect to
-momenta, $-\chi_{\alpha}$. 
+the momenta, $-\chi_{\alpha}$
 \begin{align}
@@
 \end{align}
-where potential $V(j)$ and the reciprocal mass parameter
+where the potential $V(j)$ and the reciprocal mass parameter
 $B^{\alpha\beta}(j)$ are given as
@@
   V(j) =& \mathcal{H}(j,\chi=0) \nonumber \\
-	=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left( \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right) \nonumber \\
-  &- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})} 	
+	=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left[ \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right] \nonumber \\
+  &- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}, 	
 \end{align}
@@
 		& \text{for $\alpha\ne\beta$}
-	\end{cases} \nonumber
+	\end{cases}. \nonumber
 \end{eqnarray}
@@
 \begin{equation}
-	J\equiv N/2=\sum_\alpha j^\alpha ,
+	J\equiv N/2=\sum_\alpha j^\alpha, 
   \label{J}
@@
 as a coordinate $q^n$.
-Since this is explicitly given as the expectation value of the particle
-number operator, curvature quantities,
+Since this is explicitly given as the expectation value of the particle-number
+operator, curvature quantities,
 such as $f^n_{,\alpha\beta}$ and $f^{(1)n\alpha\beta}$,
@@
 in $\pi=-\chi$.
-We confirm that the pairing rotation corresponds to an eigenvector
+We confirm that the pair rotation corresponds to an eigenvector
 of Eq. (\ref{mfQRPA}) with the zero frequency $\omega^2=0$.
@@
 In the present pairing model, 
-from Eq. (\ref{total_gauge}), we find $J$ does not dependent on $\chi$.
+from Eq. (\ref{J}), we find $J$ does not depend on $\chi$.
 This means $f^{(1)n\alpha\beta}=0$ in Eq. (\ref{q^n}),
-thus, $\tilde{B}^{\beta\gamma}=B^{\beta\gamma}$.
+thus, $\tilde{B}^{\alpha\beta}=B^{\alpha\beta}$.
 The second derivative of $J$ with respect to $j$ also vanishes,
-which indicates $f^n_{,\gamma\beta}$ in Eq.~(\ref{M}) is zero. 
+which indicates $f^n_{,\gamma\alpha}$ in Eq.~(\ref{M}) is zero. 
 %It indicates the chemical potential $\lambda_I(q)$ is not necessary information to calculate the matrix element in moving-frame QRPA equation.
@@
 It should be noted \cite{N2012} that the definition of the collective
-variables $(q^1,p_1)$ are not unique, because it can be arbitrarily mixed
+variables $(q^1,p_1)$ is not unique, because it can be arbitrarily mixed
 with the pair rotation $(q^n,p_n)$ as
@@
 	q^1 \rightarrow q^1 + c q^n,  \quad
-	p_n \rightarrow p_n -c p_1
+	p_n \rightarrow p_n -c p_1 \label{eq:pairrotmix}
 \end{equation}
 with an arbitrary constant $c$.
-Numerically, this arbitrariness sometimes leads to a problematic bahavior 
+Numerically, this arbitrariness sometimes leads to a problematic behavior 
 in iterative procedure of the ASCC.
@@
 \begin{align}
-{f}^1_{,\alpha} \to f^1_{,\alpha} + c f^n_{,\alpha} .
+{f}^1_{,\alpha} \to f^1_{,\alpha} + c f^n_{,\alpha}
   \label{f}
 \end{align}
+with Eq. (\ref{eq:pairrotmix}).
 %after solving (\ref{LHE}) at each point of $q$.
@@
 
-After deriving the collective subspace states $\Sigma_2$, 
+After deriving the collective subspace $\Sigma_2$, 
 we perform the quantization according to the SPA in Sec.~\ref{sec:SPA}.
@@
 %Due to $J$ is conserved quantity, the action integral can be divided into two terms
-Since the variables$(\Phi,J)$ and $(q^1,p_1)$ are separable,
+Since the variables $(\Phi,J)$ and $(q^1,p_1)$ are separable,
 we may take closed trajectories independently in $(\Phi,J)$ and $(q^1,p_1)$
@@
 \begin{equation}
-\ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1} .
+  \ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1},
 \end{equation}
+where $\hat{N}=\sum_\alpha n_\alpha$.
 Then, the action for the trajectory $C_1$ can be also expressed as
@@
 
-In the su(2) representation, the invariant measure is
-\begin{align}
-  d\mu(Z) &= \prod_\alpha \frac{\Omega_\alpha+1}{\pi} (1+|Z_\alpha|^2)^{-2} d{\rm Re}Z d{\rm Im}Z \nonumber \\
-=& \prod_\alpha \frac{-(\Omega_\alpha+1)}{4\pi} d \cos{\theta_\alpha} d\chi_\alpha \nonumber \\
+In the SU(2) representation, the invariant measure is
+\begin{align}
+  d\mu(Z) &= \prod_\alpha \frac{\Omega_\alpha+1}{\pi} (1+|Z_\alpha|^2)^{-2} d({\rm Re}\,Z) d({\rm Im}\,Z) \nonumber \\
+=& \prod_\alpha \frac{-(\Omega_\alpha+1)}{4\pi} d(\cos{\theta_\alpha}) d\chi_\alpha \nonumber \\
  =& \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} d\chi_\alpha dj^\alpha \nonumber \\
  =& \left[ \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} \right] d\Phi dJ dq^1 dp_1 %\nonumber \\
-  \prod_a dq^a dp_a
+  \prod_a dq^a dp_a,
 % d\Phi dJ dq dp = d\Phi dJ dE dt 
@@
 decoupled from the collective subspace $\Sigma_2$.
-For the last equation in Eq. (\ref{dmu}),
-we used the invariance of the phase space volume element
-in canonical transformation.
+In the last line in Eq. (\ref{dmu}),
+we used the invariance of the phase-space volume element
+in the canonical transformation.
 %The part of the invariant measure which contributes to the excited states is
-According to (\ref{dmu}),
+According to Eq. (\ref{dmu}),
 the weight function $\rho(q,p)$ in Eq. (\ref{SPA}) is just a constant,
@@
 The coherent state $\ket{\Phi,J;q^1,p_1}=\ket{Z}$ is
-expanded in the su(2) quasispin basis as
+expanded in the SU(2) quasispin basis as
 \begin{align}
@@
 where the summation is taken over all possible combinations
-of integer values of $\{ m_\alpha\}$.
+of integer values of $\{ m_\alpha\}$ with
 \begin{align}
@@
 	{\left(1+|Z_\alpha|^2\right)^{\Omega_\alpha/2}m_\alpha!}
-\sqrt{\frac{(\Omega_\alpha)! m_\alpha!}{(\Omega_\alpha-m_\alpha)!}} \nonumber\\
+\sqrt{\frac{\Omega_\alpha! m_\alpha!}{(\Omega_\alpha-m_\alpha)!}} \nonumber\\
  =& \prod_\alpha \left(\frac{1-\cos{\theta}_\alpha}{2}\right)^{m_\alpha/2}\left(\frac{1+\cos{\theta}_\alpha}{2}\right)^{(\Omega_\alpha-m_\alpha)/2}
   \nonumber \\
-  &\times\sqrt{\frac{(\Omega_\alpha)!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
+  &\times\sqrt{\frac{\Omega_\alpha!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
 	\label{A_m}
@@
 where the lower index $m$ indicates a combination of $\{ m_\alpha \}$.
-The integer numbers $m_\alpha$ correspond to the number of pairs
+The integer number $m_\alpha$ corresponds to the number of pairs
 in the level $\alpha$.
@@
 Using Eq.~(\ref{A_m}),
-now, the $k$-th excited state is calculated as
+the $k$-th excited state is calculated as
 \begin{align}
@@
 &\times \oint dt e^{i\mathcal{T}_1}(t) B_m (Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots} \nonumber \\
- \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots}
+ \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
  \label{SPA2}
 \end{align}
-where $B_m(Z)$ are indentical to $A_m$ in Eq.~(\ref{A_m}) but
-replacing $\chi_\alpha$ by the relative angles
+where $B_m(Z)$ are identical to $A_m$ in Eq.~(\ref{A_m}) except for
+replacing $\chi_\alpha$ with the relative angles
 $\phi_\alpha\equiv\chi_\alpha-\Phi$.
-The coefficients $C_m$ are
-\begin{align}
-C_m = \oint_{C_1} dt e^{i\mathcal{T}_1(t)} B_m(Z(t))
+The coefficients $C_m$ are given by
+\begin{align}
+C_m = \oint_{C_1} dt e^{i\mathcal{T}_1(t)} B_m(Z(t)).
   \label{coef}
@@
 \begin{align}
-	\ket{\psi_{g.s.}} \propto& \sum_{\{m_\alpha\}}
+	\ket{\psi_{\rm g.s.}} \propto& \sum_{\{m_\alpha\}}
 	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi}
@@
 \end{align}
-which is identical to the wave function of the particle number projection for HFB state.
+which is identical to the wave function of the particle-number projected HFB state.
 
@@
 In the pairing model in Sec.~\ref{sec3},
-the number of TDHFB degrees of freedom equals that of single particle levels.
-% including the constant of motion (pairing rotation).
+the number of TDHFB degrees of freedom equals that of single-particle levels.
+% including the constant of motion (pair rotation).
 We consider various systems, two-level system, three-level system, and Pb isotope system in each subsection respectively.
 Next, we discuss the dynamics in non-integrable (more than three-level) system.
-Since there is a constant of motion, the particle number, in addition to
+As there are two constants of motion, that is, the particle number and 
 the energy, the system is integrable for one- and two-level models.
@@
 fixing the particle number $J$,
-the 2D TDHFB is reduced to the 1D system,
+the 2D TDHFB is reduced to the 1D system
 with the relative angle $\phi\equiv \chi_2-\chi_1$ and the relative
@@
 separable variables,
-we examined performance of the SPA requantization
+we examined the performance of the SPA requantization
 for the two-level model.
-In this section, we apply the ASCC+SPA method to the same model.
-In other words, the ASCC method finds the transformation.
-
-Here, we study the system with equal degeneracy,
+In this section, we discuss the same model as in Ref.~\cite{NN18},
+but we determine the transformation using the ASCC method and then apply the
+SPA (ASCC+SPA).
+%In this section, we apply the ASCC+SPA method to the same model.
+%In other words, the ASCC method finds the transformation.
+
+Here, we study the system with the equal degeneracy,
 $\Omega_1=\Omega_2=8$, 
@@
 The moving-frame QRPA produces the zero mode and another eigenvector
-with finite frequency $\omega^2\neq 0$.
+with a finite frequency squared $\omega^2\neq 0$.
 We follow the latter mode to construct the collective path.
@@
 in units of $1/\sqrt{\epsilon_0}$.
-We confirm that the pair rotation always has zero frequency
+We confirm that the pair rotation always has a zero frequency
 on the collective path.
-On the obtained collective path, we calculate classical trajectory
+On the obtained collective path, we calculate a classical trajectory
 for the Hamiltonian
 \begin{equation}
-\mathcal{H}_{\rm coll}(q^1,p_1;J)=\frac{1}{2} p_1^2 + V(q^1,J) ,
+\mathcal{H}_{\rm coll}(q^1,p_1;J)=\frac{1}{2} p_1^2 + V(q^1,J)
 \end{equation}
 with $J=N/2=8$.
-Calculated trajectories, satisfying the EBK quantization condition
-(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$),
+Calculated trajectories that satisfy the EBK quantization condition
+(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$)
 are mapped onto the $(\phi,j)$ plane and
 shown in Fig. \ref{fig:N16_traj}.
-We also calculate the trajectories using explicit transformation
-of variables to $(\Phi,J;\phi,j)$, which
+We also calculate the trajectories using the explicit transformation
+of the variables to $(\Phi,J;\phi,j)$, which
 are shown by dashed lines in Fig. \ref{fig:N16_traj}.
 We call this ``TDHFB trajectories''.
-Small deviation in large $\phi$ is due to the neglect of higher-order
+Small deviation in large $\phi$ is due to the absence of the higher-order
 terms in $\chi_\alpha$ in the ASCC.
@@
 For the $0_2^+$ state,
-all three calculations well agree
+all three calculations agree well
 with each other, while we see small deviation between the full TDHFB
@@
 
-The calculated wave functions for excited $0^+$ states 
+The calculated wave functions for the excited $0^+$ states 
 are shown in Fig. \ref{fig:N16_occ}. 
-We show the occupation probability which is decomposed 
-into $2n$-particle-$2n$-hole components. 
-The left end of the horizontal axis at $m_2-m_1=-8$
+We show the occupation probabilities which are decomposed 
+into the $2n$-particle-$2n$-hole components. 
+The left end of the horizontal axis at $m_2-m_1=-8$ $(j=-4)$
 corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
 are in the lower level $\alpha=1$.
-The next at $m_2-m_1=-6$ corresponds to the one with
+The next one at $m_2-m_1=-6$ $(j=-3)$ corresponds to the one with
 $(m_1,m_2)=((N-2)/2,1)$, and so on.
-The results from TDHFB2+SPA and ASCC+SPA are identical to each other
-within numerical error, which well reproduces
-the TDHFB+SPA calculation.
-(How about exact cal.?)
+The results from the TDHFB2+SPA and the ASCC+SPA are identical to each other
+within numerical error, and they reproduce
+the TDHFB+SPA calculation well.
+{\bf (How about exact cal.?)}
 
@@
  \end{center}
-\caption{Classical trajectories satisfying the EBK condition
+\caption{Classical trajectories satisfying the EBK quantization condition
 (\ref{EBK}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
 %The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$. 
-Crosses, solid and dashed lines correspond to the results
-of ASCC+SPA, TDHFB2+SPA, and TDHFB+SPA, respectively. 
-For the ASCC+SPA trajectories, we plot the crosses
-every ten(?) points of the calculation,
-namely $\delta q=0.1/\sqrt{\epsilon_2-\epsilon_1}$.
+The crosses, solid and dashed lines correspond to the results
+of the ASCC+SPA, TDHFB2+SPA, and TDHFB+SPA, respectively.
+The crosses for the ASCC+SPA trajectories are plotted every ten calculations
+($\delta q = 10dq =0.1/\sqrt{\epsilon_2-\epsilon_1}$). 
+%For the ASCC+SPA trajectories, we plot the crosses
+%every ten(?) points of the calculation,
+%namely $\delta q=0.1/\sqrt{\epsilon_2-\epsilon_1}$.
 }
@@
 \caption{Calculated action integrals for the $\ket{0_2^+}$ and $\ket{0_3^+}$ states as functions of time $t$.
-Crosses, solid and dashed lines correspond to the ASCC+SPA,
+The crosses, solid and dashed lines correspond to the ASCC+SPA,
 the TDHFB2+SPA, and the TDHFB+SPA, respectively. 
 %Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
-We calculate the action integrals on each trajectory
-from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction
-in Fig. \ref{fig:N16_traj}.
+The action integrals are calculated on each trajectory in Fig. \ref{fig:N16_traj}
+from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction.
 }
@@
 Occupation probabilities for the $0_2^+$ and $0_3^+$ states.
-The horizontal line indicates the $m_2-m_1$ of the quasi-spin basis
+The horizontal line indicates the $j=(m_2-m_1)/2$ of the quasi-spin basis
 in Eq. (\ref{SPA2}).
-The vertical bars at each $m_2-m_1$
+The vertical bars at each $m_2-m_1$ from left to right
 represent $|C_m|^2$ of Eq. (\ref{coef}) in
-ASCC+SPA, TDHFB2+SPA and TDHFB+SPA calculations,
-respectively, from left to right.
+the ASCC+SPA, TDHFB2+SPA and TDHFB+SPA calculations,
+respectively.
 }
@@
 
-Comparing with the full TDHFB calculation with the ASCC+SPA approach
+By comparing with the full TDHFB calculation with the ASCC+SPA approach
 in the two-level pairing model,
@@
 collective states, for which the adiabatic approximation is justifiable.
-In addition, the pair rotation is properly separated.
+In addition to that, we should note that the pair rotation is properly separated.
 %we succeed to describe the bound collective excited states by ASCC+SPA.
@@
 In contrast to the two-level model,
-the TDHFB for the three-level model is non-integrable.
+the TDHFB for the three-level model is non integrable.
 %The simplest non-integrable system is three-level system. We have one trivial motion and two time-dependent degrees of freedom. 
-We set parameters of the system as follows:
-$\Omega_1=\Omega_2=\Omega_3=\Omega=\Omega=8$,
+We set the parameters of the system as follows:
+$\Omega_1=\Omega_2=\Omega_3=\Omega=8$,
 $\epsilon_1=-\epsilon_0$, $\epsilon_2=0$, $\epsilon_3=1.5\epsilon_0$,
@@
 the superfluid phase at $g_c=0.058\epsilon_0$.
-We calculate a chain of systems with even particle number
+We calculate a chain of systems with even particle numbers
 from $N=14$ to $N=24$.
 
-We obtain three eigen-frequencies for the moving-frame QRPA equation, 
+We obtain three eigen frequencies for the moving-frame QRPA equation, 
 on the collective path (Fig. \ref{omega_sq}). 
@@
 the frequency rapidly increases near the end points.
-The end points are given by points where search for the next point
+The end points are given by points where the search for the next point
 on the collective path in Sec.~\ref{sec:ASCC} fails.
 
-We choose the lowest mode, except for the zero mode,
-as a generator for the collective path ($q^1$).
+We choose the lowest frequency squared mode, except for the zero mode,
+as a generator of the collective path ($q^1$).
 Figure~\ref{occ_number} shows variation of the occupation probability
@@
 coordinate $q^1$ on the collective path.
-The most striking feature is that the collective path is terminates
+The most striking feature is that the collective path terminates
 with special configurations which are given by the integer number
 of occupation.
-This is a reason why the search for the collective path fails
-at the both ends.
-The occupation of the level 3 ($\epsilon_3$) vanishes, while
+This is the reason why the search for the collective path fails
+at both the ends.
+At the end points,
+the occupation of the level 3 ($\epsilon_3$) vanishes, while
 those of the levels 1 and 2 become either maximum or minimum.
@@
 a kind of ``Hartree-Fock'' (HF) state which minimizes
-the single-particle-energiy sum, $\sum_\alpha 2j_\alpha \epsilon_\alpha$.
+the single-particle-energy sum, $\sum_\alpha 2j_\alpha \epsilon_\alpha$.
 The pairing correlation is weakened in both ends of the
@@
 The range of $q^1$ is the largest for the system with $N=16$.
-This is because the varition of $j^1$ and $j^2$ is the largest in
+This is because the variation of $j^1$ and $j^2$ is the largest in
 this case.
@@
  \end{center}
-\caption{Eigenvalues of moving-frame QRPA equation with respect
-to the collective coordinate $q^1$, from $N=14$ to $N=24$.
+ \caption{Eigenvalues of moving-frame QRPA equation as a function of
+the collective coordinate $q^1$, from $N=14$ to $N=24$.
 The thick (green) lines are the modes we choose as
@@
 \caption{Occupation numbers in each single-particle level
-with respect to the collective coordinate $q$,
+as a function of the collective coordinate $q^1$,
 from $N=14$ to $N=24$.
-The purple, green, and blue lines correpsond to
+The purple, green, and blue lines correspond to
 $\alpha=1$, 2, and 3, respectively.
@@
  \end{center}
-	\caption{Collective potential $V(q^1)$ obtained from ASCC.
+	\caption{Collective potential $V(q^1)$ obtained from the ASCC.
 	We adjust the energy minimum point as $q^1=0$ and $V=0$.
@@
 we perform the requantization according to the SPA.
-Table \ref{ex} shows the excitation energies of the first and the second
+Table \ref{ex} shows the excitation energies of the first and second
 excited states, determined by the EBK quantization condition (\ref{EBK}).
-Comparing the result of the ASCC+SPA with those of the exact calculation,
-we find the excitation energies are reasonably well reproduced. 
-The ASCC+SPA underestimates the excitation energies by about 5 \%.
+Comparing the result of the ASCC+SPA with that of the exact calculation,
+we find that the excitation energies are reasonably well reproduced. 
+The ASCC+SPA underestimates the excitation energies only by about 5 \%.
 %The difference is that the values from ASCC+SPA are 
@@
 not to the $0_3^+$ state, in the exact calculation. 
-We examine the interband $(k\neq k')$ pair addition transition,
+We examine the interband $(k\neq k')$ pair-addition transition,
 \begin{equation}
@@
 In the phonon-like picture,
-we expect similar magnitude of strengths for
+we expect similar magnitude of the strengths for
 $B(P_{\rm ad};{\rm g.s.}\rightarrow \omega_{\rm phon})$
@@
 (variation before projection).
-In contrast, excited states are given as superposition of
+In contrast, the excited states are given as superposition of
 generalized Slater determinants in the collective subspace,
-Using these wave function of excited states, 
-the pair addition transition strengths
+The pair-addition transition strengths
+computed using these wave functions of the excited states
 are shown in Fig. \ref{3levelPad}.
@@
 the ASCC+SPA method well reproduces the strengths of the exact calculation.
-The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
+The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$, 
 are perfectly reproduced, while
@@
 as a function of the particle number is properly reproduced,
-the absolute magnitude is signiicantely underestimated in the ASCC+SPA.
+the absolute magnitude is significantly underestimated in the ASCC+SPA.
 This is due to extremely small collectivity in the interband transitions.
@@
 at $q^1=q_L$, $V(q_L) - V(0)$, becomes small.
-Then, a classical trajectory at $E>V(q_L)$ hit this boundary ($q^1=q_L$).
+Then, a classical trajectory with $E>V(q_L)$ hits this boundary ($q^1=q_L$).
 In construction of wave functions,
@@
 such a situation.
-As in Feb.~\ref{potential}, the potential height at $q^1=q_L$ has
+As in Fig.~\ref{potential}, the potential height at $q^1=q_L$ has
 about $10\epsilon_0$ which is larger than the excitation energies
@@
 \begin{table}[tb]
+\caption{Calculated excitation energies of the first and the second
+excited states in units of $\epsilon_0$.
+In the exact calculation, the second excited state in the ASCC+SPA
+corresponds to the $0_4^+$ state.
+See text for details.}
+\label{ex}
 \begin{ruledtabular}
@@
 \end{ruledtabular}
-\caption{Calculated excitation energies of the first and the second
-excited states in units of $\epsilon_0$.
-In the exact calculation, the second excited state in the ASCC+SPA
-corresponds to the $0_4^+$ state.
-See text for details.}
-\label{ex}
 \end{table}
@@
 $0_1^+\to 0_1^+$ and $0_2^+\to 0_2^+$,
-while lower panel shows the interband transitions,
+while the lower panel shows the interband transitions,
 $0_1^+ \to 0_2^+$ and $0_2^+\to 0_1^+$.
@@
 The spherical single-particle levels of neutrons
-between the magic number 82 and 126 are adopted and
+between the magic numbers 82 and 126 are adopted and
 their energies are presented in Table \ref{Pb}. 
 The coupling constant $g=0.138$ MeV is determined to reproduce
-the experimental pairing gap given by the even-odd mass difference,
-$\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb.
+the experimental pairing gap given by the odd-even mass difference,
+$\Delta(N)=\frac{(-1)^{N+1}}{2}[B(N+1)-2B(N)+B(N-1)]$ of ${}^{192}$Pb.
 The even-even nuclei from ${}^{188}$Pb to ${}^{194}$Pb
@@
 \begin{table}[htbp]
+\caption{Single-particle energies of Pb isotopes used in the calculation
+in units of MeV.
+These are obtained from the spherical Woods-Saxon potential
+with the parameters of Ref.~\cite{BM69}.
+}
 \begin{ruledtabular}
@@
 \end{ruledtabular}
-\caption{Single-particle energies of Pb isotopes used in the calculation
-in units of MeV.
-These are obtained from spherical Woods-Saxon potential
-with the parameters of Ref.~\cite{BM69}.
-}
 \label{Pb}
@@
 ``Hartree-Fock''-like state.
-On the collective path, the occupation of $i_{13/2}$, $p_{3/2}$, and
-$f_{5/2}$ mainly changes.
+On the collective path, the occupation numbers of $i_{13/2}$, $p_{3/2}$, and
+$f_{5/2}$ mainly change.
 %The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
@@
 are $2\sim3.5$ MeV.
-For $^{186}$Pb, the height of the potential is not
+{\bf For $^{186}$Pb, the height of the potential is not
 enough to satisfy the condition, $E<V(q_L)$,
 to have a closed trajectory for the first excited state
-(See the last paragraph in Sec.~\ref{sec:three-level-model}).
+(See the last paragraph in Sec.~\ref{sec:three-level-model}). }
 We encounter another kind of problem for $^{196}$Pb,
@@
  \begin{center}
-  \includegraphics[width=40mm,angle=-90]{Pbomega_sq.eps}
+  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
  \end{center}
@@
  \begin{center}
-  \includegraphics[width=40mm,angle=-90]{Pbocc_number.eps}
+  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
  \end{center}
@@
 We show the calculated excitation energy of the first excited state
-in Table~\ref{Pb}.
-Experimentally, this pairing vibrational excited $0^+$ state is
+in Table~\ref{Pb_ex}.
+Experimentally, this pair vibrational excited $0^+$ state is
 fragmented into several $0^+$ states due to other correlations,
@@
 The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
-The feature similar to the three-level case is observed;
+The feature that is similar to the three-level case is observed:
 dominant intraband transition and very weak interband transitions.
-the accuracy from 
-The ASCC+SPA method well reproduces
-$B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$,
+The accuracy from the ASCC+SPA method well reproduces
+$B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
 and qualitatively reproduces
@@
 We may say that the ASCC+SPA gives reasonable results for the intraband
-transitions in realistic values of pairing coupling constant $g$ and
+transitions in the realistic values of the pairing coupling constant $g$ and
 single-particle levels.
@@
 \begin{table}[htbp]
+\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
   \begin{ruledtabular}
@@
 \end{ruledtabular}
-\caption{The same as Table. \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
 \label{Pb_ex}
@@
 The 5D collective Hamiltonian assuming the quadrupole deformation
-parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,0)$ as the collective coordinates
+parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,$ and $0)$ as the collective coordinates
 is widely utilized to analyze experimental data of quadrupole states.
@@
 in terms of the pairing gap $\Delta$ and the gauge angle $\Phi$. 
-As far as there is one-to-one correspondence between $\Delta$ 
+As far as there is a one-to-one correspondence between $\Delta$ 
 and the collective variable $q^1$ we obtained in the present study,
@@
 The peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
-function of $q^1$, thus, no one-to-one correspondence exists.
+function of $q^1$, thus no one-to-one correspondence exists.
 The same behavior is observed for other Pb isotopes too.
-Therefore, the pairing gap $\Delta$ is not suitable collective coordinate
+Therefore, the pairing gap $\Delta$ is not a suitable collective coordinate
 to describe the pairing dynamics in the multi-level model.
@@
 Extending our former work \cite{NN18},
-which demonstrated the accuracy of SPA for the requantization
-of TDHFB dynamics in the two-level pairing model, 
+which demonstrated the accuracy of the SPA for the requantization
+of the TDHFB dynamics in the two-level pairing model, 
 we propose the ASCC+SPA method for non-integrable systems.
@@
 the multi-level model simulating Pb isotopes
-with realistic pairing coupling constant $g$ and single-particle levels.
+with a realistic pairing coupling constant $g$ and single-particle levels.
 In both cases, the low-lying excited $0^+$ states obtained with
 the ASCC+SPA well reproduce the exact solutions
-not only of excitation energies but also of wave functions.
+not only of the excitation energies but also of the wave functions.
 In the ASCC+SPA, the pair-transition calculation is straightforward,
@@
 This overcomes a disadvantage in the conventional canonical requantization
-in which we need to construct the pair-transition operator
+in which we need to construct a pair-transition operator
 in terms of the collective variables only.
@@
 First, we can calculate a classical trajectory bound by the
-pocket of a potential, however, it is not trivial how to treat
+pocket of a potential. However, it is not trivial how to treat
 ``unbound'' trajectories that hit the end point of the collective path.
-See the potentials in Figs. \ref{potential} and \ref{Pb_potential}.
+{\bf See the potentials in Figs. \ref{potential} and \ref{Pb_potential}.
 This happens in the calculation of ${}^{186}$Pb
-(Sec.~\ref{sec:Pb_isotopes}).
+(Sec.~\ref{sec:Pb_isotopes}).}
 Probably, it is necessary to find a proper boundary condition
@@
 
-The second problem occured in the calculation of $^{196}$Pb,
+The second problem occurred in the calculation of $^{196}$Pb,
 in which we have encountered complex eigenvalues and eigenvectors
 of the moving-frame QRPA equation.
-This happens at a point where the two eigenenegies become
+This happens at a point where the two eigen frequencies become
 identical, $\omega_1^2=\omega_2^2$, namely at a crossing point.
@@
 \begin{acknowledgments}
-This work is supported in part by JSPS KAKENHI Grants No. 18H01209
+This work is supported in part by JSPS KAKENHI Grants No. 18H01209, 17H05194, and 16K17680,
 and

### 2018-11-06 paper2/draft1-5.tex
revised draft1.5

@@
 there is a constant of motion in the TDHFB dynamics,
-namely the average particle number $q^n\equiv \langle N \rangle/2$.
-Since the particle number $N$ is time-even Hermitian operator, we treat
+namely the average particle number $q^n\equiv \langle \hat{N} \rangle/2$.
+Since the particle number $\hat{N}$ is time-even Hermitian operator, we treat
 this as a coordinate, and its conjugate gauge angle, $p_n$,
@@
 \begin{equation}
-q^n=\frac{\langle N \rangle}{2} = f^n(\xi)
+q^n=\frac{\langle \hat{N} \rangle}{2} = f^n(\xi)
 	+\frac{1}{2}f^{(1)n\alpha\beta}\pi_\alpha\pi_\beta .
@@
 %\ket{\psi_k} = \oint_{C_k} d\mu(q,p) \ket{q,p}
-\ket{\psi_k} = \oint dp_n \oint_{C_k} \rho(q,p) dt \ket{q,p}
+\ket{\psi_k} \propto \oint dp_n \oint_{C_k} \rho(q,p) dt \ket{q,p}
 	e^{i\mathcal{T}[q,p]} ,
@@
 \mathcal{T}[q,p] &\equiv
-\int_{0}^{t} \braket{q(t'),p(t')| i\hbar\frac{\partial}{\partial t'}
+\int_{0}^{t} \braket{q(t'),p(t')| i\frac{\partial}{\partial t'}
 	|q(t'),p(t')} dt' .
@@
 \begin{align}
-	H &= \sum_\alpha \epsilon_\alpha n_\alpha - g \sum_{\alpha,\beta} S_\alpha^+ S_{\beta}^- \nonumber \\
-    &= \sum_\alpha\epsilon_\alpha(2S_\alpha^0+\Omega_\alpha) - g S^+ S^{-} ,
+	\hat{H} &= \sum_\alpha \epsilon_\alpha \hat{n}_\alpha - g \sum_{\alpha,\beta} \hat{S}_\alpha^+ \hat{S}_{\beta}^- \nonumber \\
+    &= \sum_\alpha\epsilon_\alpha(2\hat{S}_\alpha^0+\Omega_\alpha) - g \hat{S}^+ \hat{S}^{-} ,
 \end{align}
@@
 \begin{eqnarray}
-        S_\alpha^0 &=& \frac{1}{2}\left(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_\alpha\right) ,\\
-        S_\alpha^{+} &=& \sum_{m>0}a_{j_\alpha m}^{\dag}a_{j_\alpha\overline{m}}^{\dag} ,
-\quad   S_\alpha^{-} = S_\alpha^{+\dag} .
+        \hat{S}_\alpha^0 &=& \frac{1}{2}\left(\sum_m\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha m}-\Omega_\alpha\right) ,\\
+        \hat{S}_\alpha^{+} &=& \sum_{m>0}\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha\overline{m}}^{\dag} ,
+\quad   \hat{S}_\alpha^{-} = \hat{S}_\alpha^{+\dag} .
 \end{eqnarray}
@@
 The occupation number of each level $\alpha$ is given by
-$n_\alpha = \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m}
-=2S_\alpha^0+\Omega_\alpha
+$\hat{n}_\alpha = \sum_m \hat{a}^{\dag}_{j_\alpha m}\hat{a}_{j_\alpha m}
+=2\hat{S}_\alpha^0+\Omega_\alpha
 $.
@@
 \begin{equation}
-  [S_\alpha^0,S_\beta^{\pm}] = \pm\delta_{\alpha\beta}S_{\alpha}^{\pm},
-\quad [S_{\alpha}^{+},S_{\beta}^{-}] = 2\delta_{\alpha\beta}S_{\alpha}^{0} .
+  [\hat{S}_\alpha^0,\hat{S}_\beta^{\pm}] = \pm\delta_{\alpha\beta}\hat{S}_{\alpha}^{\pm},
+\quad [\hat{S}_{\alpha}^{+},\hat{S}_{\beta}^{-}] = 2\delta_{\alpha\beta}\hat{S}_{\alpha}^{0} .
 \end{equation}
@@
 	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_\alpha(t)|^2\right)^{-\Omega_\alpha/2}
-	\exp [Z_\alpha(t) S_\alpha^{+}] \ket{0},
+	\exp [Z_\alpha(t) \hat{S}_\alpha^{+}] \ket{0},
  \label{coherent}
@@
 	\mathcal{S}\equiv \int \mathcal{L}(t) dt =
-	\int \braket{Z(t)|i\frac{\partial}{\partial t}-H|Z(t)}dt
+	\int \braket{Z(t)|i\frac{\partial}{\partial t}-\hat{H}|Z(t)}dt
   \label{TDHFB}
@@
 \mathcal{L}(t) = \sum_\alpha \frac{\Omega_\alpha}{2}
-	(1-\cos{\theta}_\alpha)\dot{\chi_\alpha} - \mathcal{H}(Z,Z^*) ,
+	(1-\cos{\theta}_\alpha)\dot{\chi}_\alpha - \mathcal{H}(Z,Z^*) ,
 \end{equation}
@@
 \begin{align}
-	\mathcal{H}( &Z,Z^*) \equiv \braket{Z|H|Z}& \nonumber \\
+	\mathcal{H}( &Z,Z^*) \equiv \braket{Z|\hat{H}|Z}& \nonumber \\
 	=& \sum_\alpha \epsilon_\alpha\Omega_\alpha(1- \cos{\theta}_\alpha)
@@
 and $j^\alpha$ corresponds to the occupation number of each level,
-$2j^\alpha=\bra{Z} n_\alpha\ket{Z}$. 
+$2j^\alpha=\bra{Z} \hat{n}_\alpha\ket{Z}$. 
 As we mention in Sec.~\ref{sec:notation},
@@
 \begin{equation}
-	-\dot{\chi_\alpha} = -\frac{\partial\mathcal{H}}{\partial j^\alpha}, \quad
-	\dot{j^\alpha} = \frac{\partial\mathcal{H}}{\partial (-\chi_\alpha)} .
+	-\dot{\chi}_\alpha = -\frac{\partial\mathcal{H}}{\partial j^\alpha}, \quad
+	\dot{j}^\alpha = \frac{\partial\mathcal{H}}{\partial (-\chi_\alpha)} .
 \end{equation}
@@
 \end{equation}
-where $\hat{N}=\sum_\alpha n_\alpha$.
+where $\hat{N}=\sum_\alpha \hat{n}_\alpha$.
 Then, the action for the trajectory $C_1$ can be also expressed as
@@
 \subsection{Integrable case: Two-level pairing model}
-
-The two-level pairing model corresponds to the 2D TDHFB system.
-Explicitly separating the gauge angle $\Phi$ and
-fixing the particle number $J$,
-the 2D TDHFB is reduced to the 1D system
-with the relative angle $\phi\equiv \chi_2-\chi_1$ and the relative
-occupation $j\equiv (j_2-j_1)/2$ as canonical variables.
-In Ref.~\cite{NN18}, using the explicit transformation to these
-separable variables,
-we examined the performance of the SPA requantization
-for the two-level model.
-In this section, we discuss the same model as in Ref.~\cite{NN18},
-but we determine the transformation using the ASCC method and then apply the
-SPA (ASCC+SPA).
-%In this section, we apply the ASCC+SPA method to the same model.
-%In other words, the ASCC method finds the transformation.
-
-Here, we study the system with the equal degeneracy,
-$\Omega_1=\Omega_2=8$, 
-the pairing strength $g/\epsilon_0=0.2$,
-and the particle number $N=16$. 
-In this two-level case, we use the level spacing,
-$\epsilon_0\equiv \epsilon_2-\epsilon_1$,
-as the unit of energy.
-The moving-frame QRPA produces the zero mode and another eigenvector
-with a finite frequency squared $\omega^2\neq 0$.
-We follow the latter mode to construct the collective path.
-In the ASCC calculation, we set the increment of the
-collective coordinate, $dq=0.01$,
-in units of $1/\sqrt{\epsilon_0}$.
-We confirm that the pair rotation always has a zero frequency
-on the collective path.
-On the obtained collective path, we calculate a classical trajectory
-for the Hamiltonian
-\begin{equation}
-\mathcal{H}_{\rm coll}(q^1,p_1;J)=\frac{1}{2} p_1^2 + V(q^1,J)
-\end{equation}
-with $J=N/2=8$.
-Calculated trajectories that satisfy the EBK quantization condition
-(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$)
-are mapped onto the $(\phi,j)$ plane and
-shown in Fig. \ref{fig:N16_traj}.
-We also calculate the trajectories using the explicit transformation
-of the variables to $(\Phi,J;\phi,j)$, which
-are shown by dashed lines in Fig. \ref{fig:N16_traj}.
-We call this ``TDHFB trajectories''.
-Small deviation in large $\phi$ is due to the absence of the higher-order
-terms in $\chi_\alpha$ in the ASCC.
-In fact, if we calculate the trajectories in the variables
-$(\Phi,J;\phi,j)$ using the Hamiltonian truncated up to the
-second order in $\chi_\alpha$ (``TDHFB2 trajectories''),
-we obtain the solid lines in Fig. \ref{fig:N16_traj},
-which perfectly agree with the ASCC trajectories.
-
-The action integrals $\mathcal{T}(t)$ corresponding to
-these closed trajectories are shown in Fig. \ref{fig:N16_tau}.
-For the $0_2^+$ state,
-all three calculations agree well
-with each other, while we see small deviation between the full TDHFB
-and the ASCC/TDHFB2 calculations for the $0_3^+$ state.
-
-The calculated wave functions for the excited $0^+$ states 
-are shown in Fig. \ref{fig:N16_occ}. 
-We show the occupation probabilities which are decomposed 
-into the $2n$-particle-$2n$-hole components. 
-The left end of the horizontal axis at $m_2-m_1=-8$ $(j=-4)$
-corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
-are in the lower level $\alpha=1$.
-The next one at $m_2-m_1=-6$ $(j=-3)$ corresponds to the one with
-$(m_1,m_2)=((N-2)/2,1)$, and so on.
-The results from the TDHFB2+SPA and the ASCC+SPA are identical to each other
-within numerical error, and they reproduce
-the TDHFB+SPA calculation well.
-{\bf (How about exact cal.?)}
-
-%we can obtain the obvious collective path from ASCC.
-%The dynamics is exactly identical with adiabatic TDHFB (ATDHFB). We confirm that whether ASCC is identical to one-dimensional ATDHFB, and compare the difference with TDHFB, in numerical calculation.
-%
-%In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
-%\begin{align}
-%\mathcal{H} 
-%  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
-% &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
-%- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
-%\end{align}
-%If we define the canonical coordinate $\phi=\chi_2-\chi_1$, it attributes to one-dimensional system.
-The conjugate momentum is $j= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \{\Omega_2(1-\cos{\theta}_2) - \Omega_1(1-\cos{\theta}_1)\}/4$.
-The ATDHFB indicates that the Hamiltonian can be expanded up to second order with respect to $\phi$
-%\begin{align}
-%  \mathcal{H}(\phi,j) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
-%\end{align}
-%where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
-%We know that the BCS ground state corresponds to the potential minimum point with $\phi=0$.
-If the pairing correlation is strong enough to bind the excited states in the collective potential,  the adiabatic approximation is expected to be well because the states are localized in small $\phi$ region.
-%
 
@@
 
+The two-level pairing model corresponds to the 2D TDHFB system.
+Explicitly separating the gauge angle $\Phi$ and
+fixing the particle number $J$,
+the 2D TDHFB is reduced to the 1D system
+with the relative angle $\phi\equiv \chi_2-\chi_1$ and the relative
+occupation $j\equiv (j_2-j_1)/2$ as canonical variables.
+In Ref.~\cite{NN18}, using the explicit transformation to these
+separable variables,
+we examined the performance of the SPA requantization
+for the two-level model.
+In this section, we discuss the same model as in Ref.~\cite{NN18},
+but we determine the transformation using the ASCC method and then apply the
+SPA (ASCC+SPA).
+%In this section, we apply the ASCC+SPA method to the same model.
+%In other words, the ASCC method finds the transformation.
+
+Here, we study the system with the equal degeneracy,
+$\Omega_1=\Omega_2=8$, 
+the pairing strength $g/\epsilon_0=0.2$,
+and the particle number $N=16$. 
+In this two-level case, we use the level spacing,
+$\epsilon_0\equiv \epsilon_2-\epsilon_1$,
+as the unit of energy.
+The moving-frame QRPA produces the zero mode and another eigenvector
+with a finite frequency squared $\omega^2\neq 0$.
+We follow the latter mode to construct the collective path.
+In the ASCC calculation, we set the increment of the
+collective coordinate, $dq=0.01$,
+in units of $1/\sqrt{\epsilon_0}$.
+We confirm that the pair rotation always has a zero frequency
+on the collective path.
+On the obtained collective path, we calculate a classical trajectory
+for the Hamiltonian
+\begin{equation}
+\mathcal{H}_{\rm coll}(q^1,p_1;J)=\frac{1}{2} p_1^2 + V(q^1,J)
+\end{equation}
+with $J=N/2=8$.
+Calculated trajectories that satisfy the EBK quantization condition
+(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$)
+are mapped onto the $(\phi,j)$ plane and
+shown in Fig. \ref{fig:N16_traj}.
+We also calculate the trajectories using the explicit transformation
+of the variables to $(\Phi,J;\phi,j)$, which
+are shown by dashed lines in Fig. \ref{fig:N16_traj}.
+We call this ``TDHFB trajectories''.
+Small deviation in large $\phi$ is due to the absence of the higher-order
+terms in $\chi_\alpha$ in the ASCC.
+In fact, if we calculate the trajectories in the variables
+$(\Phi,J;\phi,j)$ using the Hamiltonian truncated up to the
+second order in $\chi_\alpha$ (``TDHFB2 trajectories''),
+we obtain the solid lines in Fig. \ref{fig:N16_traj},
+which perfectly agree with the ASCC trajectories.
+
+The action integrals $\mathcal{T}(t)$ corresponding to
+these closed trajectories are shown in Fig. \ref{fig:N16_tau}.
+For the $0_2^+$ state,
+all three calculations agree well
+with each other, while we see small deviation between the full TDHFB
+and the ASCC/TDHFB2 calculations for the $0_3^+$ state.
+
+The calculated wave functions for the excited $0^+$ states 
+are shown in Fig. \ref{fig:N16_occ}. 
+We show the occupation probabilities which are decomposed 
+into the $2n$-particle-$2n$-hole components. 
+The left end of the horizontal axis at $m_2-m_1=-8$ $(j=-4)$
+corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
+are in the lower level $\alpha=1$.
+The next one at $m_2-m_1=-6$ $(j=-3)$ corresponds to the one with
+$(m_1,m_2)=((N-2)/2,1)$, and so on.
+The results from the TDHFB2+SPA and the ASCC+SPA are identical to each other
+within numerical error, and they reproduce
+the TDHFB+SPA calculation well.
+
+%we can obtain the obvious collective path from ASCC.
+%The dynamics is exactly identical with adiabatic TDHFB (ATDHFB). We confirm that whether ASCC is identical to one-dimensional ATDHFB, and compare the difference with TDHFB, in numerical calculation.
+%
+%In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
+%\begin{align}
+%\mathcal{H} 
+%  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
+% &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
+%- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
+%\end{align}
+%If we define the canonical coordinate $\phi=\chi_2-\chi_1$, it attributes to one-dimensional system.
+The conjugate momentum is $j= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \{\Omega_2(1-\cos{\theta}_2) - \Omega_1(1-\cos{\theta}_1)\}/4$.
+The ATDHFB indicates that the Hamiltonian can be expanded up to second order with respect to $\phi$
+%\begin{align}
+%  \mathcal{H}(\phi,j) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
+%\end{align}
+%where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
+%We know that the BCS ground state corresponds to the potential minimum point with $\phi=0$.
+If the pairing correlation is strong enough to bind the excited states in the collective potential,  the adiabatic approximation is expected to be well because the states are localized in small $\phi$ region.
+%
+
 By comparing with the full TDHFB calculation with the ASCC+SPA approach
@@
 
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
+ \end{center}
+ \caption{Eigenvalues of moving-frame QRPA equation as a function of
+the collective coordinate $q^1$, from $N=14$ to $N=24$.
+The thick (green) lines are the modes we choose as
+the collective coordinate $q^1$,
+while the dashed lines correspond to the zero modes ($q^n$).
+In each panel, both ends of the horizontal axis corresponds
+to the ending points of the collective path $q^1$.
+}
+ \label{omega_sq}
+\end{figure*}
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
+ \end{center}
+\caption{Occupation numbers in each single-particle level
+as a function of the collective coordinate $q^1$,
+from $N=14$ to $N=24$.
+The purple, green, and blue lines correspond to
+$\alpha=1$, 2, and 3, respectively.
+At the left end point of the collective coordinate in each panel,
+the configurations correspond to the ``HF-like'' states.
+See text for details.
+}
+ \label{occ_number}
+\end{figure*}
 \subsection{Non-integrable case (1): Three-level pairing model}
@@
 
-\begin{figure*}[t]
- \begin{center}
-  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
- \end{center}
- \caption{Eigenvalues of moving-frame QRPA equation as a function of
-the collective coordinate $q^1$, from $N=14$ to $N=24$.
-The thick (green) lines are the modes we choose as
-the collective coordinate $q^1$,
-while the dashed lines correspond to the zero modes ($q^n$).
-In each panel, both ends of the horizontal axis corresponds
-to the ending points of the collective path $q^1$.
-}
- \label{omega_sq}
-\end{figure*}
-\begin{figure*}[t]
- \begin{center}
-  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
- \end{center}
-\caption{Occupation numbers in each single-particle level
-as a function of the collective coordinate $q^1$,
-from $N=14$ to $N=24$.
-The purple, green, and blue lines correspond to
-$\alpha=1$, 2, and 3, respectively.
-At the left end point of the collective coordinate in each panel,
-the configurations correspond to the ``HF-like'' states.
-See text for details.
-}
- \label{occ_number}
-\end{figure*}
 \begin{figure}[htbp]
@@
 \end{figure}
+\begin{table}[htbp]
+\caption{Calculated excitation energies of the first and the second
+excited states in units of $\epsilon_0$.
+In the exact calculation, the second excited state in the ASCC+SPA
+corresponds to the $0_4^+$ state.
+See text for details.}
+\label{ex}
+\begin{ruledtabular}
+\begin{tabular}{c|cccccc}
+            $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
+ASCC+SPA (1st exc.) & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\
+    Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\ \hline
+ASCC+SPA (2nd exc.)& $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
+Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$
+\end{tabular}
+\end{ruledtabular}
+\end{table}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{intra_trans.eps}
+ \end{center}
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{inter_trans.eps}
+ \end{center}
+\caption{Calculated strength of pair-addition transition (\ref{BPad})
+from $N=14$ to $N=22$. 
+The solid (dashed) lines correspond to the ASCC+SPA (exact) calculation.
+The horizontal line indicates the particle number of the initial states.
+The upper panel shows the intraband transitions,
+$0_1^+\to 0_1^+$ and $0_2^+\to 0_2^+$,
+while the lower panel shows the interband transitions,
+$0_1^+ \to 0_2^+$ and $0_2^+\to 0_1^+$.
+}
+ \label{3levelPad}
+\end{figure}
 
@@
 B(P_{\rm ad};k\rightarrow k') \equiv 
-	\left|\bra{0_{k'}^+;N+2} S^+ \ket{0_k^+;N}\right|^2 ,
+	\left|\bra{0_{k'}^+;N+2} \hat{S}^+ \ket{0_k^+;N}\right|^2 ,
 \label{BPad}
@@
 We should remark here that there is a difficulty in the present ASCC+SPA
-requantization for weak paring cases.
+requantization for weak pairing cases.
 In such cases, the potential minimum is close to the left end 
@@
 %We skipped the result about $\ket{0_3^+}$.
-\begin{table}[tb]
-\caption{Calculated excitation energies of the first and the second
-excited states in units of $\epsilon_0$.
-In the exact calculation, the second excited state in the ASCC+SPA
-corresponds to the $0_4^+$ state.
-See text for details.}
-\label{ex}
-\begin{ruledtabular}
-\begin{tabular}{c|cccccc}
-            $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
-ASCC+SPA (1st exc.) & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\
-    Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\ \hline
-ASCC+SPA (2nd exc.)& $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
-Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$
-\end{tabular}
-\end{ruledtabular}
-\end{table}
-
-\begin{figure}[tb]
+
+\begin{figure*}[tb]
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{intra_trans.eps}
+  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
  \end{center}
+	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
+}
+ \label{Pb_omega_sq}
+\end{figure*}
+
+\begin{figure*}[tb]
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{inter_trans.eps}
+  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
  \end{center}
-\caption{Calculated strength of pair-addition transition (\ref{BPad})
-from $N=14$ to $N=22$. 
-The solid (dashed) lines correspond to the ASCC+SPA (exact) calculation.
-The horizontal line indicates the particle number of the initial states.
-The upper panel shows the intraband transitions,
-$0_1^+\to 0_1^+$ and $0_2^+\to 0_2^+$,
-while the lower panel shows the interband transitions,
-$0_1^+ \to 0_2^+$ and $0_2^+\to 0_1^+$.
+	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
 }
- \label{3levelPad}
-\end{figure}
-
+ \label{Pb_occ_number}
+\end{figure*}
 \subsection{Non-integrable case (2): Pb isotopes}
@@
 
-The collective potentials for these isotopes are shown
-in Fig. \ref{Pb_potential}.
-The heights of the potentials at the left end, $V(q_L)-V(0)$,
-are $2\sim3.5$ MeV.
-{\bf For $^{186}$Pb, the height of the potential is not
-enough to satisfy the condition, $E<V(q_L)$,
-to have a closed trajectory for the first excited state
-(See the last paragraph in Sec.~\ref{sec:three-level-model}). }
-We encounter another kind of problem for $^{196}$Pb,
-which will be discussed in Sec.~\ref{sec5}.
-Therefore, in this paper, we calculate the first excited states
-in $^{188,190,192,194}$Pb.
-
-\begin{figure*}[t]
- \begin{center}
-  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
- \end{center}
-	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
-}
- \label{Pb_omega_sq}
-\end{figure*}
-\begin{figure*}[t]
- \begin{center}
-  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
- \end{center}
-	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
-}
- \label{Pb_occ_number}
-\end{figure*}
 \begin{figure}[htbp]
@@
 \end{figure}
-
+The collective potentials for these isotopes are shown
+in Fig. \ref{Pb_potential}.
+The heights of the potentials at the left end, $V(q_L)-V(0)$,
+are $2\sim3.5$ MeV.
+For $^{186}$Pb, the height of the potential is not
+enough to satisfy the condition, $E<V(q_L)$,
+to have a closed trajectory for the first excited state
+(See the last paragraph in Sec.~\ref{sec:three-level-model}).
+We encounter another kind of problem for $^{196}$Pb,
+which will be discussed in Sec.~\ref{sec5}.
+Therefore, in this paper, we calculate the first excited states
+in $^{188,190,192,194}$Pb.
+
+\begin{table}[htbp]
+\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
+  \begin{ruledtabular}
+\begin{tabular}{c|cccccc}
+   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
+ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
+Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
+\end{tabular}
+\end{ruledtabular}
+\label{Pb_ex}
+\end{table}
 We show the calculated excitation energy of the first excited state
@@
 
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
+ \end{center}
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
+}
+ \label{PbPad}
+\end{figure}
 The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
@@
 
-\begin{table}[htbp]
-\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
-  \begin{ruledtabular}
-\begin{tabular}{c|cccccc}
-   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
-ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
-Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
-\end{tabular}
-\end{ruledtabular}
-\label{Pb_ex}
-\end{table}
 \begin{figure}[htbp]
  \begin{center}
-  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
+  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
  \end{center}
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
- \end{center}
-	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
+	\caption{Pairing gap as a function of collective coordinate $q^1$
+	in ${}^{192}$Pb. 
 }
- \label{PbPad}
+ \label{192Pb_gap}
 \end{figure}
-
 Finally, we discuss the validity of the collective model approach
@@
 \begin{align}
-  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|S^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
+  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|\hat{S}^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
   &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
@@
 In multi-level system, we can investigate the relations between the pairing gap and the collective coordinate.
-
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
- \end{center}
-	\caption{Pairing gap as a function of collective coordinate $q^1$
-	in ${}^{192}$Pb. 
-}
- \label{192Pb_gap}
-\end{figure}
 
@@
 ``unbound'' trajectories that hit the end point of the collective path.
-{\bf See the potentials in Figs. \ref{potential} and \ref{Pb_potential}.
+See the potentials in Figs. \ref{potential} and \ref{Pb_potential}.
 This happens in the calculation of ${}^{186}$Pb
-(Sec.~\ref{sec:Pb_isotopes}).}
+(Sec.~\ref{sec:Pb_isotopes}).
 Probably, it is necessary to find a proper boundary condition

### 2018-11-06 paper2/draft1-5.tex
revised draft1.5
revised draft1.5 after submission to PRC

@@
 %self-consistent collective coordinate method (ASCC+SPA).
-We apply the theoretical framework of the ASCC+SPA to 
+We apply the ASCC+SPA to 
 multi-level pairing models, which are non-integrable systems,
@@
 where we use the SU(2) quasi-spin operators,
-$\boldsymbol{S}=\sum_\alpha \boldsymbol{S}_\alpha$, with
+$\boldsymbol{\hat{S}}=\sum_\alpha \boldsymbol{\hat{S}}_\alpha$, with
 \begin{eqnarray}
@@
 The crosses for the ASCC+SPA trajectories are plotted every ten calculations
-($\delta q = 10dq =0.1/\sqrt{\epsilon_2-\epsilon_1}$). 
+($\delta q = 10dq =0.1/\sqrt{\epsilon_0}$). 
 %For the ASCC+SPA trajectories, we plot the crosses
@@
 from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction.
+The crosses for the ASCC+SPA trajectories are plotted every ten calculations
+($\delta q = 10dq =0.1/\sqrt{\epsilon_0}$). 
 }
@@
  \end{center}
-\caption{Occupation numbers in each single-particle level
+\caption{The occupation numbers $2j^{\alpha}$ in each single-particle level $\alpha$
 as a function of the collective coordinate $q^1$,
@@
 At the left end point of the collective coordinate in each panel,
-the configurations correspond to the ``HF-like'' states.
+the configuration corresponds to the ``HF-like'' states.
 See text for details.
@@
 by about $10\%\sim20\%$.
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
+}
+ \label{Pb_omega_sq}
+\end{figure*}
+
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
+}
+ \label{Pb_occ_number}
+\end{figure*}
 
@@
 
-\begin{figure*}[tb]
- \begin{center}
-  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
- \end{center}
-	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
-}
- \label{Pb_omega_sq}
-\end{figure*}
-
-\begin{figure*}[tb]
- \begin{center}
-  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
- \end{center}
-	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
-}
- \label{Pb_occ_number}
-\end{figure*}
 \subsection{Non-integrable case (2): Pb isotopes}
@@
 are studied.
-\begin{table}[htbp]
+\begin{table}[tb]
 \caption{Single-particle energies of Pb isotopes used in the calculation
@@
 
-\begin{figure}[htbp]
+\begin{figure}[bt]
  \begin{center}
@@
 
-\begin{table}[htbp]
+We show the calculated excitation energy of the first excited state
+in Table~\ref{Pb_ex}.
+Experimentally, this pair vibrational excited $0^+$ state is
+fragmented into several $0^+$ states due to other correlations,
+such as quadrupole correlation, not taken into account in the present model.
+%The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction. 
+We make a comparison with the exact solution of the multi-level
+pairing model.
+The ASCC+SPA method quantitatively reproduces the excitation energy of
+the exact solution.
+
+\begin{table}[bt]
 \caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
@@
 \end{table}
-We show the calculated excitation energy of the first excited state
-in Table~\ref{Pb_ex}.
-Experimentally, this pair vibrational excited $0^+$ state is
-fragmented into several $0^+$ states due to other correlations,
-such as quadrupole correlation, not taken into account in the present model.
-%The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction. 
-We make a comparison with the exact solution of the multi-level
-pairing model.
-The ASCC+SPA method quantitatively reproduces the excitation energy of
-the exact solution.
-
-\begin{figure}[htbp]
+\begin{figure}[htb]
  \begin{center}
@@
 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
- \end{center}
-	\caption{Pairing gap as a function of collective coordinate $q^1$
-	in ${}^{192}$Pb. 
-}
- \label{192Pb_gap}
-\end{figure}
 Finally, we discuss the validity of the collective model approach
@@
 
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
+ \end{center}
+	\caption{Pairing gap as a function of collective coordinate $q^1$
+	in ${}^{192}$Pb. 
+}
+ \label{192Pb_gap}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 collective subspace including the pair rotation.
-In other words, we map the non-integrable system to an approximate
-integrable system described by $(q^1,p_1;J,\Phi)$.
+In other words, we extract an approximate integrable system 
+in the non-integrable system described by $(q^1,p_1;J,\Phi)$.
 

### 2018-11-20 thesis/thesis.tex
thesis

@@
 
-\usepackage{graphicx} % support the \includegraphics command and options
+\usepackage[dvips]{graphicx} % support the \includegraphics command and options
+\usepackage[dvips]{color}
 
@@
 
+\pagenumbering{roman}
 \tableofcontents
@@
 \chapter{Introduction}
-
-\section{Pairing interaction in nuclei}
-
-Pairing correlation plays an important role near the Fermi energy.
-Pairing correlation is the two-body interaction which couples two identical nucleons into $J^{\pi}=0^+$ state.
-There are many evidences of pairing correlation detected from experiment.
-The most clear evidence is shown in Fig.
-\ref{Sn_isotope}.
-All of the ground states of even-even Sn isotopes are $J^{\pi}=0^+$ states  It indicates that the ground states consist of the $J^{\pi}=0^+$ pairs is more stable than other configurations.
+\pagenumbering{arabic}
+
+\section{Pairing correlation in theoretical and experimental aspects}
+
+\subsection{Superfluid nuclei}
+
+Mean field model is standard tool to describe the structure of atomic nuclei.
+The idea of mean field model is based on the primary theoretical framework of shell model introduced by Mayer and Jensen in 1949.
+Mean field picture indicates that the nucleon can be described in single-particle motion in the mean field potential created by the whole nucleons in the nucleus.
+Although the many-body correlation between the nucleons is extremely complicate, the single-particle motion picture can well reproduce the basic properties (e.g.
+radius, binding energy, separation energy, magic number) in most of nuclide.
+%%The most popular mean field potential is Woods-Saxon potential with spin-orbit coupling.
+Because
+
+Of course, single-particle motion picture cannot describe the nuclear system perfectly.
+To describe the nuclear structure more precisely, the residual interaction, the deviation between single-particle interaction and many body correlation, needs to be taken account.
+In 1950s, nuclear physicists found one of the most important residual interaction, pairing correlation.
+One of the clear evidences for pairing correlation detected from experiment is the separation energy difference between odd nuclei and even nuclei.
+Fig.
+\ref{S_n} shows the separation energies for Sn, Sb, and Te isotopes as a function of neutron number.
+The isotopes in even neutron number have about $2\sim3$ MeV larger separation energies than the isotopes in odd neutron number.
+It is odd-even staggering (OES) effect, which is detected in whole mass region of nuclei ( Fig.
+\ref{gap}).
+In this figure, $2\Delta$ corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei.
+The approximate value is $2\Delta \approx 24A^{-1/2}$ MeV.
+It indicates a two-body attractive interaction should be included based on single-particle motion picture.
+In addition, if we examine the spin-parity of the ground states, we can find all of the even-even nuclei are $J^{\pi}=0^+$ states and most of the odd mass number nuclei have the same spin-parity as their single-particle orbital which the last nucleon fulfills in.
+To explain these phenomena, it is natural to consider that the ground state of even-even nuclei consist of coupled $J^{\pi}=0^+$ pairs and the ground state of odd mass number nuclei consist of coupled $J^{\pi}=0^+$ pairs except one unpaired nucleon in last single-particle orbit.
+The two-body attractive interaction which couples two identical nucleons into $J^{\pi}=0^+$ state is called pairing correlation.
+\begin{figure}[htbp]
+ \begin{center}
+    \includegraphics[width=100mm]{images/S_n.eps}
+ \end{center}
+  \caption{Separation energy for Sn, Sb, Te isotopes as a function of neutron number obtained from experimental data \cite{KJJ12}.}
+  \label{S_n}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+    \includegraphics[width=120mm]{images/gap.eps}
+ \end{center}
+  \caption{The odd-even mass differences $\Delta_n$, $\Delta_p$ for neutrons and protons (Zeldes {\it et al.} {\it Mat. Fys. Skr. Dan. Vid. Selsk.}, 3, no. 5 (1967)).}
+  \label{gap}
+\end{figure}
+
+Because pairing correlation is two-body interaction, a theoretical framework beyond the mean field model seems to be necessary.
+However, there is a tricky approximated theory, BCS theory, enable us to describe pairing correlation within mean field model.
+In BCS theory, the ground state is superposed by the states with different particle number.
+It indicates that the ground state breaks symmetry in a space, namely U(1) gauge space.
+With symmetry breaking, the corresponding order parameter, pairing gap $\Delta$, has finite value.
+Based on BCS theory, because the energy of each particle in a $J^{\pi}=0^+$ pair is $E_k=\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}$, where $\epsilon_k$ is single particle energy, $\lambda$ is Fermi energy, the minimum excitation energy is $2\Delta$.
+In fact, pairing gap corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei discussed in previous paragraph.
+As same as superconductivity in condensed matter physics, the superfluid nucleus is defined when $\Delta\neq0$ in ground state.
+Thus, the OES detected from experiment caused from pairing correlation can be well explained by BCS theory.
+
+After BCS theory was firstly introduced by J.
+Bardeen, L.
+Cooper, and J.
+R.
+Schrieffer in 1957, it was immediately generalized to Hartree-Fock-Bogoliubov (HFB) theory.
+HFB theory is the naturally extension of Hartree-Fock (HF) theory by introducing Bogoliubov transformation.
+Under Bogoliubov transformation, the particles become to quasiparticles, and the mean field potential is extended to generalized form including pairing field.
+After HFB theory had been applied to nuclear physics in 1958, the structure of ground states in nuclei was examined by plenty of studies.
+Up to now, HFB theory is the standard mean field theory to describe nuclear structure including pairing correlation.
+
+% Recently, nuclear density functional theory has been developed based on HFB theory.
+and the computational codes are well developed.
+The properties of ground states in even-even nuclei are well studied by HFB theory.
+
+%BCS theory is firstly introduced by J.
+Bardeen, L.
+Cooper, and J.
+R.
+Schrieffer in 1957 \cite{} to describe .
+BCS theory can describe the superconducting state or superfluid state caused by cooper pairs.
+In nuclear physics, the  created by pairing correlation correspond to the cooper pairs.
+
+%  It indicates that the ground states consist of the $J^{\pi}=0^+$ pairs is more stable than other configurations.
 In addition, the ground states between even-even nuclei and neighborhood odd nuclei has large gaps of binding energy.
 In odd nuclei, the unpaired last neutron is the last single-particle level.
-The odd-even mass difference  To break the $J^{\pi}=0^+$ pair, we need large energy which is about $2\Delta \approx 24A^{-1/2}$ MeV.
+The odd-even mass difference  To break the $J^{\pi}=0^+$ pair, we need large energy which
+
+%Pairing correlation plays an important role near the Fermi energy.
+%\begin{figure}[htbp]
+% \begin{center}
+%    \includegraphics[width=100mm]{images/Sn_isotope.eps}
+% \end{center}
+%  \caption{Low-lying excited states in Sn isotopes \cite{}. The absolute values of binding energy are adjusted at 0 MeV in the ground state of ${}^{116}$Sn.}
+%  \label{Sn_isotope}
+%\end{figure}
+
+\subsection{Pairing collective motion}
+\label{1-1-2}
+Due to the superfluid state breaks the symmetry in U(1) gauge space, we expect that there are two types of elementary modes of excitation for pairing collective motion in nuclei.
+Two types of elementary modes of excitation are Nambu-Goldstone (NG) mode, pairing rotation, recovering the broken symmetry in U(1) gauge space, and Higgs mode, pairing vibration, fluctuating around the energy minimum point.
+
 \begin{figure}[htbp]
  \begin{center}
-    \includegraphics[width=100mm, bb=0 0 400 300]{images/Sn_isotope.png}
- \end{center}
-  \caption{Low-lying excited states in Sn isotopes \cite{}. The absolute values of binding energy are adjusted at 0 MeV in the ground state of ${}^{116}$Sn.}
-  \label{Sn_isotope}
+    \includegraphics[width=100mm]{images/pair_coll.eps}
+ \end{center}
+  \caption{Schematic picture of pairing collective motion with superfluid ground state.
+Red  bi-direction arrow indicates pairing rotation, which rotates in $\Phi$ direction along the energy minimum circle degenerating at an absolute value of pairing gap $|\Delta|\neq 0$, in U(1) gauge space.
+Green bi-direction arrow indicates pairing vibration, which vibrates in $|\Delta|$ direction around one of the degenerated energy minimum points.}
+  \label{Pair_coll}
 \end{figure}
-
-\subsection{A subsection}
-
-More text.
+First, we discuss about pairing rotation.
+In classical picture, pairing rotation is the motion which the system rotates in the U(1) gauge space (red bi-direction arrow in Fig.
+\ref{pair_rot}).
+The motion is described by the coordinate, gauge angle $\Phi$, and the corresponding momentum, total particle number $N$.
+%It is similar to normal rotation in 3D space which described by the angles ($\theta_x, \theta_y, \theta_z$) and their conjugate angular momenta ($J_x, J_y, J_z$). 
+Because the total particle number is unchanged in time evolution, the momentum $N$ is conserved quantity.
+In quantum picture, if we assume the ground state in a particle number $N_0$ as the ``ground state'', the ground states in $N=N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing rotational mode.
+The excitation energy is $E_{\rm rot}^{\rm pair}=\frac{(N-N_0)^2}{2\mathcal{J}}$, where $\mathcal{J}$ is the pairing-rotational moment of inertia which characterizes the pairing rotation.
+In experiment, the pairing rotational band is expected to be observed in even-even isotope chain or even-even isotone chain between two magic numbers.
+One clear observation is found in Sn isotopes shown in Fig.
+\ref{pair_rot}.
+Except  a constant value and linear term with respect to mass number $A$, we can find the energies of ground states consist of a parabolic line - pairing rotational band.
+Recently, the systematic study for the pairing-rotational moment of inertia has been done in Ref.
+\cite{HN16}.
+The experimental moments of inertia obtained from two neutron(proton) separation energies have excellent correspondence with the theoretical moments of inertia obtained from NG mode in quasiparticle random phase approximation (QRPA) \cite{TV61} based on HFB mean field theory, not only for the spherical nuclei, but also for the deformed nuclei.
+Because the pairing-rotational moments of inertia are free from ambiguities caused from odd-even system, they are supposed to be excellent indicators of pairing correlation rather than pairing gaps.
+
+Next, we discuss about pairing vibration.
+We emphasize that there are two types of pairing vibrations, one which vibrates around normal ground state ($\Delta\approx 0$), and another one which vibrates around superfluid ground state ($\Delta\neq 0$).
+The structures between two vibrational modes are quite different.
+%The former one is well understood because the structure of the excited $0^+$ states are $2np2nh$ configurations, detected from the energy spectra around ${}^{208}$Pb. 
+Here, we only focus on the later one.
+In classical picture, the later one vibrates around one of the degenerated energy minimum points. Depending on the intrinsic structure, various pairing vibrations can exist in one nucleus. 
+%In general, the motion is supposed to be described by the coordinate, pairing gap $\Delta$, and its corresponding momentum\footnote{Because $\Delta$ is order parameter, it is naturally supposed to be the coordinate to describe the pairing vibration in previous studies.
+However, we found $\Delta$ is not proper coordinate in most of case from our study.
+The detail is discussed in Chapter 3 and 4.}.
+In quantum picture, if we assume the ground state in a particle number $N_0$ as the ``ground state'', the excited states in $N=N_0, N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing vibrational mode.
+The excitation energy is $E_{\rm vib}^{\rm pair}=n_{\alpha}\hbar\omega$, where $n_{\alpha}$ is the number of phonon and $\alpha$ is the label to distinguish different pairing vibrational modes.
+Because $2\Delta$ is the minimum energy to break one-pair, the collectivity is supposed to be strong when $E_{\rm vib}^{\rm pair}<2\Delta$.
+Thus, low-lying excited $0^+$ states in even-even nuclei are possible to be pairing vibrational states.
+Except the region around the magic number, excited $0^+$ states below $2\Delta$ exist in most of even-even nuclei.
+However, it is difficult to observe the signatures for pairing vibration directly from experiment.
+The properties of pairing vibration in nuclei are not well understood up to now.
+
+The signatures for pairing collective motion can also be observed from the two-neutron(proton) transfer reaction \cite{BHR73}, such as $(p, t)$, $(t, p)$, and $({}^3{\rm He}, n)$.
+The cross sections of two particle transfer reaction strongly depend on the matrix elements of $J^{\pi}=0^+$ pair-transition operators (e.g.
+pair-additional transition: $\sigma( P_{ad};0_{\alpha}^+(N) \to 0_{\beta}^+(N+2))\sim |\braket{N+2,\beta|\sum_k a^{\dag}_k a^{\dag}_{\bar{k}}|N,\alpha}|^2$).
+From theoretical prediction, the pairing correlation is known to enhance $\sigma(g.s.\to g.s.)$ and decrease $\sigma(g.s.\to 0_{ex}^+)$ significantly, hence, $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)\ll 1$ is expected in superfluid system.
+One example of $(p, t)$ reactions is demonstrated in Fig.
+\ref{pair_rot}.
+As mentioned in previous paragraph, the ground states of even-even Sn isotopes consist of a pairing rotational band.
+In such situation, we can find intraband transition is dominant with respect to interband transition.
+Therefore, the cross sections of two-neutron transfer reaction is consistent with theoretical prediction.
+In general, the ratio $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)$ for two-neutron(proton) transfer reaction are excellent indicators to describe the collectivity of pairing dynamics.
+
+\begin{figure}[htbp]
+ \begin{center}
+    \includegraphics[width=100mm]{images/pair_rot.eps}
+ \end{center}
+  \caption{Experimental energies of the $J^{\pi}=0^+$ states of the Sn isotopes (ground state and pairing vibration),
+populated in $(p, t)$ reactions. The heavy drawn horizontal lines
+represent the values of the expression $E=-B({}_{50}^{A}{\rm Sn}_{N})+E_{exc}+
+8.124A+46.33$ MeV, where $B({}_{50}^{A}{\rm Sn}_{N})$ is the binding energy
+of the Sn isotopes of mass number $A$, and $E_{exc}$ is the
+weighted [with $\sigma(0_i^+)$] average energy of the excited $0^+$ states
+below 3 MeV. The dashed and dotted lines represent the parabolas
+given in the insets, corresponding to the ground state and to
+the (average) excited state-based pairing rotational bands. The
+absolute values of the $g.s.\to g.s.$ integrated cross sections (in $\mu$b units) are given (perpendicular) to the abscissa, as a function
+of $N$. The values in the shaded areas correspond to the experimental values, while the remaining values correspond to theoretical
+predictions. For the first group (experimental), the relative
+(in \%)$(p, t)$, pairing vibrational, cross sections $\sum_i\sigma(g.s.\to 0_i^+)$
+normalized with respect to the ground state cross sections are in parenthesis. The detailed information are written in \cite{PF11}.}
+  \label{pair_rot}
+\end{figure}
+
+\section{Motivation of this study}
+
+\subsection{Mysterious excited $0^+$ states and pairing dynamics}
+In most of nuclei, the structure of excited $0^+$ states is complicate and unclear.
+The reason is that not only pairing correlation but also deformations and multipole correlations influence the excited $0^+$ states significantly.
+The various correlations competing with each other construct plenty of mysterious excited $0^+$ states.
+
+After the concept of pairing vibration was introduced, it encountered the problem for the large asymmetry cross sections between $(p, t)$ and $(t, p)$ reaction in actinide region observed from experiment.
+In low-lying energy region, the cross section of $\sigma(g.s.\to 0_{ex}^+)$ is about $15\%$ of $\sigma(g.s.\to g.s.)$ for $(p, t)$ reaction \cite{MEFSS70, MEFSS72}, while the signal of $\sigma(g.s.\to 0_{ex}^+)$ is extremely weak for $(t, p)$ reaction \cite{Cas72}.
+To explain such phenomena, the coexistence of both oblate shape and prolate shape in one state, and the mixing of pairing correlations between oblate and prolate shape was suggested \cite{GJV71,RK72}.
+Another interpretation for such phenomena is using microscopic interaction, including multipole pairing correlations and quadrupole particle-hole interactions \cite{RB76}.
+Although the approaches are different, they succeeded to reproduce the asymmetry cross section of two-neutron transfer reaction in actinide region.
+
+$\beta$ vibration
+Collective motion is the essential idea to explain the excited states in nuclei.
+The quadrupole collective motion described by the quadrupole deformation parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,0)$ is known as the most typical collective motion.
+In the framework of quadrupole collective motion, the low-lying excited $0^+$ states can be roughly categorized into two types: quadrupole vibration emerging above two-phonon excitation in spherical nuclei, and $\beta$ vibration emerging in quadrupole deformed nuclei.
+The excitation energies and $B(E2)$ transition strength is well understood under harmonic approximation.
+
+\subsection{Theoretical problem}
+%As discussed in previous section, the low-lying excited $0^+$ states are not be understood in general. 
+We aim to understand the mysterious excited $0^+$ states discussed in previous section based on mean field approach.
+In low-energy region, the pairing correlation supposed to be important as the quadrupole correlation.
+The most well-known and successful model is Bohr model, which was introduced to describe low-energy nuclear collective motion in quadrupole degrees of freedom with the deformation parameters $(\beta,\gamma)$ and the Euler angles $(\phi,\theta,\psi)$.
+However, the pairing degrees of freedom is not included in the Bohr model.
+As discussed in Sec.
+\ref{1-1-2}, the pairing vibrational degrees of freedom supposed to be a key ingredient to understand the low-lying  excited $0^+$ states.
+ the pairing vibrational degrees of freedom is necessary to include in the collective model. the role of pairing correlation is hardly discussed up to now.
+The degrees of freedom for pairing collective motion are supposed to be necessary including the collective model.
+
+The study about the collective model for pairing collective motion was firstly introduced by Bes.
+et al.
+\cite{BBPK70}.
+They constructed phenomenological pairing collective model  by two degrees of freedom, the pair deformation parameter (pairing gap) $\Delta$ and the global gauge angle $\Phi$.
+After the pairing collective model was formulated, it was applied to several studies for nuclear structure \cite{GPBW85, ZPPRS99, P07}.
+In Ref.
+\cite{ZPPRS99}, the $B(E2)$ transition improved by introducing pairing degrees of freedom.
+On the other hand, the wave function of ground state from collective model looks like unusual because the pairing gap $\Delta_{vib}$ at the peak of the wave function is smaller than the pairing gap $\Delta_{eq}$ obtained from BCS equation.
+
+It is supposed to be important to find the collective coordinates describing the pairing collective motions from the microscopic degrees of freedom without any assumption.
+
+The difficult point is the requantization of the pairing collective motion. Such difficulty is not found in quadrupole collective motion.
+
+\subsection{Our idea}
+
+\subsection{Outline of this thesis}
+In this study, we concentrate in the pairing model which only contains pairing interaction in two-body interaction to construct the theoretical framework of the requantization.
 
@@
 We also define a seniority $\nu_l$, which is the number of unpaired particles in each level.
+The total number of unpaired particles is $\nu=\sum_l\nu_l$.
 The unpaired particles have no pairing interaction, and play a part in Pauli blocking effect.\par
@@
 \end{align}
-The first term is the energy of unpaird particle, and the second term is the total energy of $J^{\pi}=0^+$ pairs. The pair-energy $E_{\alpha}$ is derived from the non-linear equations
+The first term is the energy of unpaired particle, and the second term is the total energy of $J^{\pi}=0^+$ pairs. The pair-energy $E_{\alpha}$ is derived from the non-linear equations
 \begin{equation}
@@
   \delta\mathcal{S}=0, \quad 
-  \mathcal{S} \equiv \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
+  \mathcal{S} \equiv \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt ,
+  \label{variation}
 \end{equation}
@@
 \begin{align}
-	N = \sum_l \nu_l + 2J .
+	N = \nu + 2J .
 \end{align}
@@
 
-\section{TDHFB dynamics in two-level system}
-To describe the one-dimensional motion, we use the global gauge angle $\Phi$ and the relative gauge angle $\phi$ as canonical coordinates
+\section{Classical dynamics in two-level system}
+\subsection{TDHFB dynamics}
+To describe the one-dimensional motion, we introduce the global gauge angle $\Phi$ and the relative gauge angle $\phi$ as canonical coordinates
 \begin{align}
@@
 \end{align}
-The Hamiltonian in terms of these canonical variables
-$(\phi,j;\Phi,J)$ is given by
-\begin{align}
+The Lagrangian and Hamiltonian in terms of these canonical variables
+$(\phi,j;\Phi,J)$ are given by
+\begin{align}
+	\mathcal{L} =& J\dot{\Phi} + j\dot{\phi} - \mathcal{H}(\phi,j;J) \label{Lagrangian2}\\
 	\mathcal{H}(\phi,j;J)
@@
 	j_1 = \frac{J}{2} - j, \quad\quad j_2 = \frac{J}{2} + j .
-\end{align}
+	\label{j_l}
+\end{align}
+The TDHFB equation can be written in a form of
+the classical equations of motion:
+\begin{eqnarray}
+	&&\frac{d\Phi}{dt} = \frac{\partial\mathcal{H}}{\partial J} ,\quad\quad
+\frac{dJ}{dt} = -\frac{\partial\mathcal{H}}{\partial \Phi} , \\
+	&&\frac{d\phi}{dt} = \frac{\partial\mathcal{H}}{\partial j} ,\quad\quad
+\frac{dj}{dt} = -\frac{\partial\mathcal{H}}{\partial \phi} .
+\label{TDHFB_equation}
+\end{eqnarray}
 Because $J$ and the total energy $E$ constants of motion, the TDHFB trajectories with given $J$ and $E$ are determined
@@
   \mathcal{H}(\phi(t),j(t);J) = E.
-\end{equation}
-
-For convenience, we also define a dimensionless coupling constant in two-level system
-\begin{align}
-	x = \frac{\epsilon_2 - \epsilon_1}{2\Omega}
-\end{align}.
+  \label{contour}
+\end{equation}
+
+\begin{figure}[tp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
+ \end{center}
+ \caption{Energy contour plot for $\Omega_1=\Omega_2=8$ and $N=16$.
+	The lines indicate the TDHFB trajectories fulfilling
+	the EBK quantization condition of Eq. (\ref{EBK}).
+	}
+ \label{fig:phase_space}
+\end{figure}
+
+We show an example of the classical trajectories in two-level system.
+Fig.
+\ref{fig:phase_space} is the contour lines fulfilling (\ref{contour}), which correspond to the classical trajectories, with $\Omega_1=\Omega_2=\Omega=8$, $\nu=0$, and $N=2\Omega=16$ with various coupling constant $g$.
+The dimensionless coupling constant $x$ is defined as $x=2g\Omega/(\epsilon_2-\epsilon_1)$ (See Appendix \ref{two-level}).
+The phase transition from normal state to superfluid state occurs at $x=1$ in closed shell ($N=2\Omega$).
+At $x<1$ corresponding the left panel in Fig.
+\ref{fig:phase_space}, the trajectory of ground state is $j=-4$ independent from $\phi$.
+It is consistent with the fully occupied lower level $n_1=N$ and the empty upper level $n_2=0$.
+For the dynamical states, the trajectories are open with gentle slopes.
+At $x>1$ corresponding the middle and right panels in Fig.
+\ref{fig:phase_space}, the trajectory of ground state becomes a point at $\phi=0$, $j=j_0$ $(-4<j_0<4)$.
+With superfluid ground state, the dynamical states have two types, closed trajectory and open trajectory.
+The closed trajectory appears around $(\phi,j)=(0,j_0)$ at low-energy region.
+On the other hand, the open trajectory with steep slope appears at high-energy region relatively.
+The stronger pairing correlation, the higher excitation energy of the transition point from closed trajectory to open trajectory.
+The structure of the excited states between closed trajectory and open trajectory is quite different.
+They influence the matrix element of two-particle transfer reaction significantly.
+We will discuss the feature of the excited states in the following sections.
+
+\subsection{Adiabatic TDHFB (ATDHFB) dynamics}
+\label{ATDHFB}
+In general collective motion, the frequency in the collective motion is much smaller than the frequency in single particle motion ($\hbar\omega\ll\epsilon_m-\epsilon_i$).
+The slow velocity of the collective motion enable us to expand the collective Hamiltonian up to second order with respect to the collective momentum (adiabatic approximation).
+We discuss the behavior of TDHFB dynamics in adiabatic approximation.\par
+From (\ref{Hamiltonian2}), we find that the classical Hamiltonian is even function with respect to $\phi$.
+With time reversal $t\to-t$, (\ref{TDHFB_equation}) is invariant under $j\to j, \phi\to -\phi$, which indicates that $j$ is time even and $\phi$ is time odd.
+Thus, we switch the coordinate and momentum
+\begin{equation}
+	(\phi,j)\to(j,-\phi) ,
+	\label{switch}
+\end{equation}
+to make the coordinate time even. The classical Hamiltonian under adiabatic approximation becomes
+\begin{align}
+  \mathcal{H}(j,\phi) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
+  \label{ATDHFB_Hamiltonian}
+\end{align}
+where 
+\begin{align}
+	V(j) = \mathcal{H}(\phi=0,j) 
+	=& \sum_{l=1,2} \epsilon_l\nu_l + \sum_{l=1,2} 2\epsilon_lj_l - g\sum_{l=1,2} \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	&- 2g\sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})} \\
+	B^{-1}(j) = \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}
+	=& 2g\sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})} .
+	\label{mass_two_level}
+\end{align}
+It is obvious that $V(j)$ is potential and $B(j)$ is mass parameter.
+Because the closed trajectories appear around the energy minimum point $(\phi,j)=(0,j_0)$, we can expect that adiabatic approximation performs excellent for closed trajectories.
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/phase_compare.eps}
+ \end{center}
+ \caption{Energy contour plot in the same system as Fig. \ref{fig:phase_space}. Black solid lines correspond to TDHFB trajectories and gray dashed lines correspond to ATDHFB trajectories. 
+	}
+ \label{fig:phase_compare}
+\end{figure}
+
+We compare the difference of the classical trajectories between TDHFB and ATDHFB.
+Fig.
+\ref{fig:phase_compare} shows both TDHFB and ATDHFB trajectories in the same system as in Fig.
+\ref{fig:phase_space}.
+For weak pairing correlation ($x<1$), both results are similar, especially at the low-energy region.
+For strong pairing correlation ($x>1$), both results are almost identical for closed trajectories.
+The opened trajectories are also well reproduced near the closed trajectories.
+The deviation becomes large at the high-energy region.
+In conclusion, ATDHFB is excellent approximation at low-energy region, regardless of the type of the trajectories.
 
 \section{Requantization methods}
+To obtain the excited states, quantization of the TDHFB trajectory, namely, requantization is necessary procedure.
+The straightforward requantization method is canonical quantization, which is commonly applied into nuclear collective model.
+We expected canonical quantization gives reasonable result and we applied it at first.
+However, we find that canonical quantization has serious problem to describe the pairing dynamics.
+To solve or avoid the problem, alternative requantization methods, Fourier decomposition and stationary phase approximation to the path integral, are also introduced.
+In this section, we explain each requantization method in detail, respectively.
+
+\subsection{Stationary phase approximation to the path integral}
+At first, we introduce the idea of stationary phase approximation to the path integral (SPA). Starting an arbitrary state $\ket{\psi(0)}$ at time $t=0$,
+the time-dependent full quantum state can be written in the path integral form
+\begin{align}
+\ket{\psi(t)}
+	=& e^{-iHt} \ket{\psi(0)} \nonumber \\
+	=& \int d\mu(Z'') \ket{Z''} \int d\mu(Z') \int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)]
+	e^{i\mathcal{S}[Z(\tau)]} \psi(Z') ,
+\label{path_integral_expression}
+\end{align}
+where $\psi(Z)\equiv \braket{Z|\psi(0)}$ and
+the invariant measure $d\mu(Z)$ is defined by 
+the unity condition,
+\begin{equation}
+  \int d\mu(Z) \ket{Z}\bra{Z} = 1 .
+  \label{unity}
+\end{equation}
+In Eq. (\ref{path_integral_expression}),
+$\mathcal{S}[Z(\tau)]$ is the action (\ref{variation}) along a given path $Z(\tau)$
+with the initial coherent state $\ket{Z(0)}=\ket{Z'}$ and
+the final state $\ket{Z(t)}=\ket{Z''}$,
+then, the integration $\int \mathcal {D}\mu[Z(\tau)]$
+is performed over all possible paths $\ket{Z(\tau)}$ between them.
+Among all trajectories in the path integral,
+the lowest stationary-phase approximation $\delta S_{\rm cl}=0$ selects
+the TDHFB (classical) trajectories\footnote{
+In this formulation, the stationary-phase approximation agrees with
+the TDHF(B) trajectories, while that to the auxiliary-field path
+integral of Refs. \cite{Neg82,L80}
+leads to the TDH(B) without the Fock potentials.
+}.
+\begin{equation}
+	\ket{\psi(t)} \approx \int d\mu(Z') \ket{Z'_{\rm cl}(t)}
+	e^{i\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z')} \psi(Z') ,
+	\label{SPA}
+\end{equation}
+where the TDHFB trajectory starting from $\ket{Z'}$
+ends at $\ket{Z'_{\rm cl}(t)}$ at time $t$.
+The action $\mathcal{S}_{\rm cl}(Z_f,Z_i)$ is calculated along this
+classical trajectory
+connecting $Z_i=Z'_{\rm cl}(0)=Z'$ and $Z_f=Z'_{\rm cl}(t)$.
+\begin{align}
+	\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z') &\equiv \int_{0}^{t}
+\braket{Z_{\rm cl}(t)|
+	i\frac{\partial}{\partial t} - H
+	|Z_{\rm cl}(t)} dt \nonumber \\
+	&= \mathcal{T}[Z_{\rm cl}] - \mathcal{H}(Z',Z'^*) t 
+	,
+	\label{S_cl}
+\end{align}
+with the action integral $\mathcal{T}[Z_{\rm cl}]$
+\begin{align}
+\mathcal{T}[Z_{\rm cl}] &\equiv
+\int_{0}^{t} \braket{Z_{\rm cl}(t)| i\frac{\partial}{\partial t}
+	|Z_{\rm cl}(t)} dt  .
+\end{align}
+In the last equation of Eq. (\ref{S_cl}),
+we used the fact that the TDHFB trajectory conserves the energy,
+$\mathcal{H}(Z_{\rm cl}(t),Z_{\rm cl}^*(t))= \mathcal{H}(Z',Z'^*)$.
+%We assume that only classical (TDHFB) trajectory contributes to the time dependent wave function
+
+The energy eigenstates correspond to stationary states,
+$\braket{Z|\psi(t)} \propto \braket{Z|\psi(0)}=\psi(Z)$,
+which can be constructed by superposing the coherent states along
+a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{KS80,K81,SM88}
+\begin{equation}
+	\ket{\psi_k} = \oint d\mu(Z_{\rm cl}^{(k)}) \ket{Z_{\rm cl}^{(k)}}
+	e^{i\mathcal{T}[Z_{\rm cl}^{(k)}]} .
+\end{equation}
+The single-valuedness of the wave function leads to
+the quantization condition ($k$: integer)
+\begin{align}
+	\mathcal{T}_\circ[Z_{\rm cl}^{(k)}]=&
+	\oint \braket{Z_{\rm cl}(t)| i\frac{\partial}{\partial t}
+	|Z_{\rm cl}(t)} dt  \nonumber \\
+	=& 2k\pi .
+	\label{EBK}
+\end{align}
+The state evolves in time as $\ket{\psi_k(t)}=\ket{\psi_k}e^{-iE_k t}$,
+with the energy of the $k$-th periodic trajectory,
+$E_k=\mathcal{H}(Z_{\rm cl}^{(k)},Z_{\rm cl}^{(k)*})$.
+
+Finding TDHFB trajectories satisfying the quantization condition
+(\ref{EBK}) is an extremely difficult task in general.
+It is better founded and more practical
+if the classical system is completely integrable.
+In integrable systems, $M$ complex variables $Z(t)$ can be transformed into
+the action-angle variables;
+\begin{align}
+	Z(t) &= \{Z_l(t);l=1,\cdots,M \} \nonumber \\
+	&\rightarrow
+	\{E; v_1,\cdots,v_{M-1}; \theta_1(t),\cdots,\theta_M(t)\} ,
+\end{align}
+where the variables $E$ and $v$ define an invariant torus,
+while $\theta(t)$ parameterize the coordinates on the torus.
+The integration path of Eq. (\ref{EBK}) is now taken as topologically
+independent closed path on the torus,
+namely the EBK quantization condition.
+There are $M$ independent closed paths and $M$ quantum numbers,
+$k=(k_1,\cdots,k_M)$, to specify the stationary energy eigenstate.
+These are associated with $M$ invariant variables,
+$\{E_k;v_1^{(k)},\cdots,v_{M-1}^{(k)}\}$.
+Using the invariant measure
+\begin{align}
+%  d\mu(Z) = \rho(Z)dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
+  d\mu(Z) = \rho(E,v,\theta) dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
+\end{align}
+the $k$-th semiclassical wave function can be calculated as
+\begin{align}
+  \ket{\psi_k} \propto \oint d\theta_1\cdots \oint d\theta_M &\ 
+	\rho(E_k,v^{(k)},\theta)
+	\ket{E_k,v^{(k)},\theta} \nonumber \\
+	&\times e^{i\mathcal{T}[E_k,v^{(k)},\theta]} .
+  \label{semi_wave_func}
+\end{align}
+Here, we omit the integration with respect to the invariant variables,
+$E$ and $v$.
+
+We apply the SPA approach to the two-level pairing model.
+The invariant measure in SU(2)$\otimes$SU(2) is 
+\begin{align}
+%	d\mu(Z) &= \prod_{l=1,2} \frac{S_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
+%  &= \prod_l \frac{S_l+1}{4\pi}\sin{\theta_l}d\theta_ld\phi_l \\
+%  &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi .
+d\mu(Z) &= \prod_l \frac{\Omega_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
+  &= \prod_l \frac{\Omega_l+1}{4\pi}d\cos{\theta_l}d\chi_l \\
+	&= \left(\prod_{l=1,2} \frac{1+\Omega_l^{-1}}{2\pi}\right)
+             d\Phi dJ d\phi dj .
+\end{align}
+In the last equation, we transform the canonical coordinates
+by Eqs. (\ref{phi}) and (\ref{pi}).
+Since the particle number $J=N/2$ and the total energy $E$ are invariant,
+the two-level pairing model is integrable.
+Thus, we can construct the semiclassical wave function using
+Eq. (\ref{semi_wave_func}).
+From (\ref{Lagrangian2}), the action integral is given by
+\begin{align}
+	\mathcal{T}_k(\Phi,\phi;J)
+	&= J\Phi + \int^t_0
+	j(t') \frac{d\phi}{dt'} dt' \nonumber \\
+	&\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
+\end{align}
+where the integration is performed on the $k$-th
+closed trajectory of Eq. (\ref{EBK}), and
+the variables $(\phi,j)$ are transformed into $(t,E)$.
+%where $\pi(t)$ can be solved from the right side of (\ref{TDHFB_equation}). (i.e. 2D Runge-Kutta method) \par
+The semiclassical wave function fulfilling the EBK quantization condition
+becomes
+\begin{align}
+	\ket{\psi_k^J} &\propto \oint d\Phi \oint dt
+	e^{i\mathcal{T}_{J,E_k}(\Phi, t)}
+	\ket{\Phi,t}_{N,E_k} \label{semi_wave_func0} \\
+  &\propto \sum_{m=0}^{J}C_m^{(E_k,J)}\ket{S_1,-S_1+m;S_2,-S_2+(J-m)} ,
+	\label{semi_wave_func1}
+\end{align}
+with $S_l=(\Omega_l-\nu_l)/2$ and the coefficients
+\begin{align}
+  C_m^{(E_k,J)} =& \binom{J}{m}\int_0^T dt \nonumber \\
+ &\times \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)} \nonumber \\ 
+ &\times A(j_1,S_1,m)A(j_2,S_2,J-m) ,\\
+  A(j,S,m) &= \left(\frac{j}{2S}\right)^{m/2}\left(\frac{2S-j}{2S}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
+\end{align}
+where $T$ is the period of the closed trajectory.
+The TDHFB-requantized wave functions (\ref{semi_wave_func1}) are
+eigenstates of the total particle number.
+This is due to the integration over the global gauge angle $\Phi$,
+which makes the particle number projection not only for the ground state
+but also for excited states.
+See Appendix for detailed derivation of Eq.~(\ref{semi_wave_func1}).
+
+Since we obtain the microscopic wave function of every eigenstate,
+the expectation values and the transition matrix elements for any operator
+can be calculated in a straightforward manner.
+In Sec.~\ref{sec:results}, we show those of the pair-addition operator
+$S^+$ which characterize properties of the pair condensates.
+
+Before ending this section, let us note the periodic conditions
+of the coordinates and the quantization condition.
+Since the two original variables, $(\chi_1,\chi_2)$,
+are independent periodic variables of the period $2\pi$,
+in addition to the trivial periodicity of $2\pi$ for $\Phi$ and of $4\pi$
+for $\phi$,
+we have periodic conditions for
+$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\pm 2\pi)$ and
+$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\mp 2\pi)$.
+The former (latter) corresponds to $\chi_2\pm 2\pi$ ($\chi_1\pm 2\pi$)
+with $\chi_1$ ($\chi_2$) being fixed.
+For open TDHFB trajectory (e.g., Fig.~\ref{fig:phase_space}),
+the quantization condition becomes
+\begin{align}
+ \mathcal{T}_{J,E_k}(\Phi\pm\pi,\phi\pm 2\pi;J) &= \mathcal{T}_{J,E_k}(\Phi,\phi;J) + 2m\pi \nonumber \\
+	 \Leftrightarrow \quad\quad \pm J \pi + \int_{-\pi}^\pi j d\phi
+	&= 2m\pi .
+\end{align}
+This leads to the following:
+\begin{equation}
+	\int_{-\pi}^\pi j d\phi = 
+	\begin{cases}
+		2k\pi & \mbox{ for } J=2n ,\\
+		(2k+1)\pi & \mbox{ for } J=2n+1 ,
+	\end{cases}
+	\label{EBK_2}
+\end{equation}
+where $m$, $k$ and $n>0$ are integer numbers.
+
 \subsection{Canonical quantization}
+\label{sec:canonical}
+In the pairing collective model, the canonical quantization
+was adopted in previous studies \cite{BBPK70,delta1,delta3}.
+Assuming magnitude and phase of the pairing gap as collective coordinates,
+a collective Hamiltonian was constructed in the second order in momenta.
+Then, the Hamiltonian was quantized by the canonical quantization
+with Pauli's prescription.
+In this section, we apply similar quantization method to
+the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
+The main difference is that the collective canonical variables are
+not assumed in the present case, but are obtained from the TDHFB dynamics
+itself.\par
+It is not straightforward to apply Pauli's prescription
+to the present case, 
+because the TDHFB Hamiltonian (\ref{Hamiltonian2})
+is not limited to the second order in momenta.
+In the present study, 
+we adopt a simple symmetrized ordering, as
+\begin{align}
+	\mathcal{H}(\hat{\phi},\hat{j};\hat{J})
+	=& \sum_{l=1,2} \epsilon_l\nu_l + \sum_{l=1,2} 2\epsilon_lj_l - g\sum_{l=1,2} \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	&- g \left\{ \sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})}\cos{\hat{\phi}} \right. \nonumber \\
+	&\left. + \cos{\hat{\phi}}\sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})} \right\} .
+\label{canonical_quantized_H}
+\end{align}
+To fulfill the canonical quantization condition
+\begin{align}
+ [\hat{\Phi},\hat{J}]=i, \quad\quad [\hat{\phi},\hat{j}]=i ,
+\end{align}
+as in (\ref{j_l}), $j_l$ contain $J$ and $j$ which
+are replaced by
+\begin{equation}
+	\hat{J} = -i\frac{\partial}{\partial\Phi},\quad\quad
+	\hat{j} = -i\frac{\partial}{\partial\phi} .
+\end{equation}
+Since $\Phi$ is a cyclic variable, 
+we write the collective wave function $\Psi(\Phi,\phi)$ as eigenstates
+of the number of $J^{\pi}=0^+$ pairs $J$ in a separable form
+\begin{equation}
+  \Psi_k^{(J)}(\Phi,\phi) = 
+	\frac{1}{\sqrt{2\pi}}e^{iJ\Phi}\psi_k^{(J)}(\phi) .
+\end{equation}
+Then, the problem is reduced to the one-dimensional Schr\"{o}dinger
+equation for the motion in the relative angle $\phi$.
+%pairing vibrational mode can be obtained by solving
+the Schr\"{o}dinger equation is
+\begin{equation}
+	H\left( \phi,-i\frac{d}{d\phi};J \right)
+	\psi_k^{(J)}(\phi) = E_k^{(J)}\psi_k^{(J)}(\phi) .
+	\label{Schroedinger_eq}
+\end{equation}
+
+The wave function should have a periodic property with respect to
+the variable $\phi$;
+$\psi_k(\phi)=\psi_k(\phi+4\pi)$.
+For the adopted simple ordering of Eq. (\ref{canonical_quantized_H}),
+it is convenient to use the eigenstates of $\hat{j}$ as the basis
+to diagonalize the Hamiltonian.
+They are
+\begin{equation}
+%  \hat{\pi}\chi_\nu(\phi) = \nu \chi_\nu(\phi) \\
+	\chi_j(\phi) = \frac{1}{\sqrt{4\pi}} e^{i\phi j} ,
+	\quad\quad\mbox{with $j$: integer or half integer} .
+\end{equation}
+Since the Hamiltonian (\ref{canonical_quantized_H}) contains only
+terms linearly proportional to $e^{\pm i\phi}$,
+the basis states $\chi_j$ with half-integer difference in $j$
+are not coupled with each other.
+Thus, the eigenstates of Eq. (\ref{Schroedinger_eq}) can be expanded as
+\begin{equation}
+	\psi_k^{(J)}(\phi) = 
+	\sum_{j=j_{\rm min},j_{\rm min}+1,\cdots}^{j_{\rm max}}
+	c_{k,j}^{(J)} \chi_j^{(J)}(\phi) .
+	\label{CQ_eigenstate}
+\end{equation}
+According to the relation $j=(j_2-j_1)/2$ in Eq. (\ref{pi}),
+we adopt the (half-)integer values of $j$ for $J=2n$ ($J=2n+1$)
+with integer $n$.
+This is consistent with the quantization condition (\ref{EBK_2}).
+The coupling term with different $j$
+in Eq. (\ref{canonical_quantized_H}) vanishes
+for $j_l=0$ and $j_l=\Omega_l-\nu_l$,
+which restricts values of $j$ in a finite range of
+$j_{\rm min}\leq j \leq j_{\rm max}$.
+
+In order to estimate the two-particle transfer matrix elements,
+we construct the corresponding operators as follows.
+The classical form of matrix elements are obtained as
+\begin{align}
+  S^+(\Phi,J;\phi,j) &= \braket{Z|\hat{S}^+|Z} \nonumber \\
+ &= \frac{1}{2}
+\left( \sqrt{j_1(\Omega_1-\nu_1-j_1)}e^{-i\phi/2}+\sqrt{j_2(\Omega_2-\nu_2-j_2)}e^{i\phi/2} \right) e^{i\Phi}
+	\label{Sp_mean_value} \\
+  S^-(\Phi,J;\phi,j) &= \braket{Z|\hat{S}^-|Z} \nonumber \\
+ &= \frac{1}{2}
+\left( \sqrt{j_1(\Omega_1-\nu_1-j_1)}e^{i\phi/2}+\sqrt{j_2(\Omega_2-\nu_2-j_2)}e^{-i\phi/2} \right) e^{-i\Phi} .
+	\label{Sm_mean_value}
+\end{align}
+%For simplicity, we ignore the part of off-diagonal element (e.g. $\braket{Z'|\hat{S}_+|Z}$). 
+%To requantize the two-particle transition operators, 
+Again, we adopt a simple symmetrized ordering for the quantization:
+\begin{align}
+%  &S_+(\Phi,\Pi;\phi,\pi) \to S_+(\hat{\Phi},\hat{\Pi};\hat{\phi},\hat{\pi}) \nonumber \\
+  S^\pm (\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
+	=& \frac{1}{4}\left( \sqrt{j_1(\Omega_1-\nu_1-j_1)}e^{\mp i\hat{\phi}/2}
++\sqrt{j_2(\Omega_2-\nu_2-j_2)}e^{\pm i\hat{\phi}/2} \right) e^{\pm i\hat{\Phi}} \nonumber \\ 
+&+ \frac{1}{4}e^{\pm i\hat{\Phi}}\left( 
+e^{\mp i\hat{\phi}/2}\sqrt{j_1(\Omega_1-\nu_1-j_1)}
++e^{\pm i\hat{\phi}/2}\sqrt{j_2(\Omega_2-\nu_2-j_2)} \right) .
+\end{align}
+The exponential factors $e^{\pm i\Phi}$ change
+the total particle number $N\rightarrow N\pm 2$ ($J\rightarrow J\pm 1$),
+while $e^{\pm i\phi/2}$ change the relative numbers,
+$j_2-j_1 \rightarrow j_2-j_1 \pm 1$.
+%For example, the pair-additional transition strength in requantized form is
+Using these operators,
+the pair-addition transition strengths are calculated as
+\begin{align}
+B(P_{\rm ad};k\rightarrow k') &=
+|\braket{J',k'|S^+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})|J,k}|^2
+	\nonumber \\
+&= \left| \frac{1}{2\pi} \int_{0}^{2\pi}d\Phi \int_{-2\pi}^{2\pi}d\phi 
+	\psi^{(J')*}_{k'}(\phi) e^{-iJ'\Phi}
+	S^+(\hat{\Phi},\hat{J};\hat{\phi},\hat{j})
+	\psi^{(J)}_{k}(\phi)e^{iJ\Phi} \right|^2,
+\end{align}
+which automatically vanishes for $J'\neq J+1$.
 
 \subsection{Fourier decomposition}
-
-\subsection{Stationary phase to the path integral}
+\label{sec:Fourier}
+
+The requantization and calculation of the matrix elements can be also
+performed using the time-dependent solutions of the TDHFB.
+It was proposed and applied to the two-level pairing model \cite{CDS84},
+which we recapitulate in this section.
+
+The TDHFB provides a time-dependent solution $Z(t)$ starting from
+a given initial state $Z(0)$.
+The energy eigenvalues and the corresponding closed trajectories
+are determined from the EBK quantization condition (\ref{EBK}).
+The pair transfer matrix elements are evaluated as the Fourier components
+of the time-dependent mean values $S^\pm(t)=S^\pm(Z(t))$,
+Eqs. (\ref{Sp_mean_value}) and (\ref{Sm_mean_value}).
+%In the ground state, the motion in the global gauge angle $\Phi$
+%is independent from the $\phi$ motion.
+Since the global gauge angle $\Phi$ is a cyclic variable,
+the motion in the relative gauge angle $\phi$ is independent from $\Phi$.
+Thus, we calculate the time evolution of $\phi(t)$, and
+find the period of the $k$-th closed trajectory $T$
+satisfying Eq. (\ref{EBK}).
+Then, the Fourier component,
+\begin{equation}
+	\tilde{S}^\pm(E_k; \omega) = \frac{1}{T}\int_0^T dt
+	e^{i\omega t} S^\pm(t) ,
+\label{Fourier_decomposition}
+\end{equation}
+corresponds to the pair transfer matrix element from the state $k$ to $k'$
+when $\omega=2\pi (k'-k)/T$.
+The pair-addition transition strengths are calculated as
+\begin{equation}
+	B(P_{\rm ad};k\rightarrow k') 
+	= \left|\tilde{S}^+\left(E_k;\frac{2\pi}{T}\Delta k \right) \right|^2 ,
+\end{equation}
+with $\Delta k=k'-k$.
+In this approach, the transition between the ground states of
+neighboring nuclei ($N\rightarrow N+2$) corresponds to
+the stationary component ($k=0$ and $\Delta k=0$),
+namely the expectation value in the BCS approximation.
+
+The derivation  of Eq. (\ref{Fourier_decomposition})
+is based on the wave packet in the
+classical limit \cite{LL65}.
+The TDHFB state is assumed to be a superposition of eigenstates $\ket{\phi_k^N}$
+in a narrow range of energy $E_{k_0}-\Delta E<E_k<E_{k_0}+\Delta E$,
+\begin{equation}
+	\ket{Z(t)} = \sum_N \sum_k c_k^N \ket{\phi_k^N} e^{-iE_k t} ,
+	\label{superposition}
+\end{equation}
+where the eigenenergies are evenly spaced and
+the coefficients $c_k^N$ slowly vary with respect to $k$ and $N$.
+The expectation value of $S^\pm$ is
+\begin{equation}
+	S^\pm(t) = \sum_{N} \sum_{k,k'} c_{k'}^{N+2*} c_k^N 
+	\braket{\phi_{k'}^{N+2}|S^\pm|\phi_k^N} e^{i(E_{k'}-E_k)t} .
+\end{equation}
+The matrix element $\braket{\phi_{k'}^{N+2}|S^\pm|\phi_k^N}$
+quickly disappears as $|k'-k|$ increases, while it stays almost constant
+for the small change of $k$ and $N$ with $|k'-k|$ being fixed.
+Thus, we may approximate $c_{k'}^{N+2}\approx c_k^N$,
+$E_{k'}-E_k\approx \omega_0 \Delta k$, and
+that $\braket{\phi_{k'}^{N+2}|S^\pm|\phi_k^N}\approx
+\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}$ 
+\begin{align}
+	S^\pm(t) &\approx \sum_{N} \sum_{k} \left|c_k^N\right|^2
+	\sum_{\Delta k}
+	\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}
+	e^{i\omega_0 \Delta k t}  \nonumber \\
+	&= \sum_{\Delta k}
+	\braket{\phi_{k_0+\Delta k}^{N+2}|S^\pm|\phi_{k_0}^N}
+	e^{i\omega_0 \Delta k t}  ,
+\end{align}
+where $k_0$ is a representative index value of the superposition in 
+Eq. (\ref{superposition}).
+From this classical wave packet approximation,
+we obtain Eq. (\ref{Fourier_decomposition}).
+It is not trivial to justify the approximation for small values of $\Omega$
+and for transitions around the ground state.
 
 \section{Result}
+In this section, we study the seniority-zero states ($\nu_1=\nu_2=0$) in
+the two-level system with equal degeneracy, $\Omega_1=\Omega_2=\Omega$.
+Since all the properties are scaled with the ratio, $g/\Delta\epsilon$,
+where $\Delta\epsilon$ is the level spacing
+$\Delta\epsilon=\epsilon_2-\epsilon_1$,
+we use the dimensionless parameter $x$ defined in Appendix (\ref{x}) to control the strength of the pairing correlation.
+
+We apply the requantization methods in Sec.~\ref{sec:requantization}.
+In the following, the stationary-phase approximation to the path
+integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
+the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
+and the canonical quantization with periodic boundary condition 
+(Sec.~\ref{sec:canonical}) as ``CQ''.
+Note that the SPA and the FD produce the same eigenenergies which
+are based on the EBK quantization rule.
+
+\subsection{Large-$\Omega$ cases}
+
+\begin{figure}[t]
+ \begin{center}
+(a)	 \includegraphics[height=0.6\textwidth,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
+\\
+(b)	 \includegraphics[height=0.6\textwidth,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and
+$\ket{0_4^+}$ for $\Omega=50$ systems with (a) $N=50$ and (b) $N=100$
+	as functions of the dimensionless parameter $x$ of Eq. (\ref{x}).
+}
+ \label{fig:N50energy}
+\end{figure}
+
+In the limit of $\Omega\rightarrow\infty$,
+we expect that the classical approximation becomes exact.
+Here, we adopt $\Omega=50$ with $N=100$ (closed-shell configuration)
+and $N=50$ (mid-shell configuration).
+
+Calculated excitation energies are shown in Fig.~\ref{fig:N50energy}.
+The results of SPA/FD and CQ are compared with the exact values.
+At the weak pairing limit of $x\rightarrow 0$,
+the excitation energies are multiples of $2\Delta\epsilon$, 
+which correspond to pure $2n$-particle-$2n$-hole excitations.
+Both the weak and the strong pairing limits
+are nicely reproduced by all the calculations,
+while the CQ method produces excitation energies slightly lower than the
+exact values in an intermediate region around $x=1$.
+It is somewhat surprising to see that the deviation is larger for
+the case of the mid-shell configuration ($N=50$) than the closed shell
+($N=100$).
+
+The deviation in the CQ method is mainly due to the zero-point energy
+in the ground state.
+Since we solve the collective Schr\"odinger equation (\ref{Schroedinger_eq})
+with the quantized Hamiltonian of Eq. (\ref{canonical_quantized_H}),
+the zero-point energy $\Delta E>0$ is inevitable in the CQ method.
+The $\Delta E$ is associated with the degree of localization of
+the wave function.
+Thus, the magnitude of $\Delta E$ for ``bound'' states are different
+from that for ``unbound'' states.
+See Fig.~\ref{fig:phase_space}.
+In the strong pairing limit, the potential minimum is deep enough to bound
+both ground and excited states.
+Conversely, all the states are unbound in the weak limit.
+In both limits, $\Delta E$ for ground and excited states are similar,
+and they are canceled for the excitation energy.
+However, near $x=1$, the ground state is bound,
+while the excited states are unbound.
+In this case, $\Delta E$ is larger in the ground state than in the
+excited states, which makes the excitation energy smaller.
+This also explains the difference between the mid-shell and closed-shell
+configurations.
+In the closed shell, all the states are unbound for $x<1$,
+while, in the mid-shell,
+there is a region in $x<1$ where the ground state is bound but
+the excited state is unbound.
+
+The obtained wave functions in the SPA and the CQ can be decomposed in the
+$2n$-particle-$2n$-hole components in Fig.~\ref{fig:N50_occ}.
+In the SPA, it is done as Eq. (\ref{semi_wave_func1}) and
+the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
+in Fig.~\ref{fig:N50_occ}.
+For the CQ, $|c_{k,j}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
+Here, $m$ and $j$ are related to each other, $2j=J-2m$.
+They show excellent agreement with the exact results, not only for the
+ground state but for excited states.
+We find the SPA is even more precise than the CQ.
+\begin{figure}[t]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+ \caption{
+Occupation probability in excited $0^+$ states
+as a function of $j$ for $\Omega=50$ systems
+with (a) $N=50$ and (b) $N=100$.
+The upper and lower panels display the results for $x=0.5$ and $x=2$,
+respectively. 
+The three vertical bars at each $j$ from the left to the right represent
+the squared components of the wave functions
+from exact, SPA, and CQ calculations, respectively.
+The left end of the horizontal axis at $j=j_{\rm min}$
+corresponds to a component with $(n_1,n_2)=(N,0)$.
+The next at $j=j_{\rm min}+1$ corresponds to the one with
+$(n_1,n_2)=(N-2,2)$, and so on.
+}
+ \label{fig:N50_occ}
+\end{figure}
+
+Next, let us discuss the transition matrix elements.
+In this paper, we discuss only $k=0$ (ground state) and $k=1$
+(1st excited $\nu=0$ state).
+The FD calculation is based on the time evolution of the expectation 
+value $S^+(t)$ with fixed $(J,\Phi)$ in Eq. (\ref{Fourier_decomposition}).
+For $(N,k)\rightarrow (N+2,k')$ transitions,
+we basically adopt the trajectories for the initial state, namely,
+the one with $J=N/2$ satisfying the $k$-th EBK quantization condition.
+The $k\rightarrow k$ ($\Delta k = 0$)  transitions
+correspond to the intraband transitions of the
+pair-rotational band, when the state is deformed in the
+gauge space (pair deformation).
+For the ground-state band ($k=0$),
+this is nothing but the expectation value at the BCS wave function,
+with the constant value of $S^+$.
+Since the constant $S^+$ provides only $\Delta k=0$ intraband transitions,
+for the interband transition of $(N,k=0)\rightarrow (N+2,k=1)$
+transitions, the trajectory satisfying the EBK condition of $k=1$ is used to
+perform the Fourier decomposition (\ref{Fourier_decomposition})
+of $\omega=2\pi/T$.
+
+\begin{figure}[t]
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_CQ.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_FD.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N50Pad_SPA.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \caption{The strength of pair additional transition
+$B(P_{\rm ad};k\rightarrow k')$ for $\Omega=50$ systems
+from $N=48$ to 50.
+Left panels: results of the CQ method; Middle panels: FD; Right panels: SPA.
+Dashed lines represent exact calculation.
+Upper panels show the intraband transitions of
+$\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$,
+while lower panels show the interband transition of
+$\ket{0_1^+}\to\ket{0_2^+}$ and $\ket{0_2^+}\to\ket{0_1^+}$.
+}
+ \label{fig:N50Pad}
+\end{figure}
+
+\begin{figure}[t]
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_CQ.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_FD.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N100Pad_SPA.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \caption{
+The same as Fig.~\ref{fig:N50Pad} but for $N=98\rightarrow 100$.}
+ \label{fig:N100Pad}
+\end{figure}
+
+The calculated pair-addition strengths $B(P_{\rm ad})$ are shown in
+Fig.~\ref{fig:N50Pad} for $N=48\rightarrow 50$,
+and in Fig.~\ref{fig:N100Pad} for $N=98\rightarrow 100$.
+Near the closed-shell configuration ($N=98\rightarrow 100$),
+the pair-addition strengths for the intraband transitions ($\Delta k=0$)
+drastically increase around $x=1$.
+This reflects a character change from the pair vibration ($x\lesssim 1$)
+to the pair rotation ($x\gtrsim 1$).
+The $B(P_{\rm ad}; k\rightarrow k)$ in the pair-rotational transitions
+are about 20 times larger than those in the vibrational transitions.
+The interband $B(P_{\rm ad}; 0\rightarrow 1)$ are similar to
+the $B(P_{\rm ad}; 0\rightarrow 0)$ in the vibrational region
+($x\lesssim 1$), because they both change the number of pair-phonon quanta
+by one unit.
+In contrast, $B(P_{\rm ad}; 1\rightarrow 0)$, which change the phonon
+quanta by three, are almost zero.
+In the pair-rotational region ($x \gg 1$),
+$B(P_{\rm ad}; 1\rightarrow 0)$ and $B(P_{\rm ad}; 0\rightarrow 1)$
+are roughly identical. This is because both $B(P_{\rm ad}; 1\rightarrow 0)$ 
+and $B(P_{\rm ad}; 0\rightarrow 1)$ correspond to one-phonon excitation
+in ``deformed'' cases ($x \gg 1$).
+
+In the mid-shell region ($N=48\rightarrow 50$),
+the intraband $B(P_{\rm ad}; k\rightarrow k)$ are smoothly increase as
+$x$ increases.
+Their values are larger than the interband strengths by about one (two) order
+of magnitude at $x\sim 0$ ($x\sim 2.5$),
+indicating the pair-rotational character.
+The interband $B(P_{\rm ad}; 0\rightarrow 1)$ show a gradual decrease
+as a function of $x$, while
+$B(P_{\rm ad}; 1\rightarrow 0)$ are negligibly small,
+even at $x\gg 1$.
+This presents a prominent difference from the closed-shell case.
+
+All the features of the pair-transfer strengths
+are nicely reproduced in the SPA method,
+for both the closed- and mid-shell configurations.
+The CQ method qualitatively agrees with the exact calculation.
+For instance, the order-of-magnitude difference between intraband
+and interband transitions.
+However, the precision of the CQ method is not so good,
+especially around $x=1$.
+The FD method properly describes the main features
+in the superfluid phase, while it fails for the normal phase
+($x\lesssim 1$). 
+In the mid-shell configuration, the ground state is always
+in the superfluid phase at $x>0$,
+while the $k=1$ excited state corresponds to
+the open (closed) trajectory at $0<x\lesssim 1$ ($x\gtrsim 1$).
+For the open trajectory, the FD produces wrong values.
+However, somewhat surprisingly,
+the SPA, which uses these open trajectories for the construction
+of wave functions,
+reproduces main features of the exact results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsection{Small-$\Omega$ cases}
+\label{SmallOmg}
+
+Next, we discuss systems with smaller degeneracy $\Omega=8$.
+Again, we study systems near the closed-shell and the mid-shell configurations.
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[height=0.6\textwidth,angle=-90]{images/N8ex_energy_wo_adiabatic.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and
+$\ket{0_4^+}$ for $\Omega=N=8$ systems as functions of $x$.
+}
+ \label{fig:N8energy}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+   \includegraphics[height=0.45\textwidth,angle=-90]{images/N8Xeq0p5occ_wo_adiabatic.eps}
+   \includegraphics[height=0.45\textwidth,angle=-90]{images/N8Xeq2occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+ \caption{
+Occupation probability in excited $0^+$ states
+as a function of $j$ for $\Omega=N=8$ systems.
+The panels (a) and (b) display the results for $x=0.5$ and $x=2$,
+respectively. 
+See also the caption of Fig.~\ref{fig:N50_occ}.
+}
+ \label{fig:N8_occ}
+\end{figure}
+
+\subsubsection{Mid-shell configuration}
+
+The calculated excitation energies are shown in Fig.~\ref{fig:N8energy}
+for the $N=8$ case.
+The SPA/FD reproduces the exact calculation in the entire region of $x$,
+not only for the lowest but also for higher excited states.
+The CQ reproduces the exact result in a weak pairing region ($x\lesssim 1$),
+while it underestimates the excitation energies at $x\gtrsim 1$.
+Analogous to the case of $\Omega=50$,
+this is mainly due to effect of the zero-point energy $\Delta E$.
+The ground-state energy in the CQ calculation 
+is bound at $x\gtrsim 1$.
+However, because of the weak collectivity with $N=8$,
+the first excited state stays unbound even at the maximum $x$ in 
+Fig.~\ref{fig:N8energy}.
+Therefore, the energy shift $\Delta E>0$ is larger in the ground state,
+which makes the excitation energy smaller.
+
+The wave functions are plotted in Fig.~\ref{fig:N8_occ}. 
+At the weak pairing case of $x=0.5$,
+both the SPA and the CQ reproduce the exact result.
+At $x=2$, the squared coefficients of the ground state has an
+asymmetric shape peaked at the
+lowest $j$, which suggests that the state is not deeply bound in the
+potential.
+It is in contrast to the symmetric shape in Fig.~\ref{fig:N50_occ}.
+The wave functions obtained by the CQ method has noticeable deviation
+from the exact results.
+On the other hand, the SPA wave functions are almost identical to the
+exact ones.
+
+The pair-addition transition strengths from $N=6$ to $N=8$ are
+shown in Fig.~\ref{fig:N8Pad}.
+The intraband $k\rightarrow k$ transitions increase and 
+the interband $k=0\rightarrow 1$ transitions decrease as
+functions of $x$.
+Their relative difference becomes
+more than one order of magnitude at $x\gtrsim 2$.
+Thus, even at relatively small $\Omega$ and $N$,
+the intraband transitions in the pair rotation is qualitatively different
+from the interband transitions.
+
+We find the excellent agreement between the SPA and the exact calculations.
+The first excited state corresponds to the open trajectory which
+turns out to almost perfectly reproduce the exact wave function.
+In contrast, this open trajectory produces results far from the exact
+one in the FD method.
+It produces almost vanishing the intraband
+$B(P_{\rm ad}; 1\rightarrow 1)$.
+The $B(P_{\rm ad}; 0\rightarrow 0)$ shows a qualitative agreement for
+its behavior, but is significantly underestimated.
+The CQ method also underestimates the intraband transitions.
+
+For the mid-shell configurations, the SPA is dominantly superior to the
+CQ and the FD methods.
+
+\begin{figure}[t]
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N8Pad_CQ.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N8Pad_FD.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/N8Pad_SPA.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=6\rightarrow 8$
+	with $\Omega=8$.
+}
+ \label{fig:N8Pad}
+\end{figure}
+
+\begin{figure}[htb]
+ \begin{center}
+  \includegraphics[height=0.6\textwidth,,angle=-90]{images/N16ex_energy_wo_adiabatic.eps}
+ \end{center}
+	\caption{The same as Fig.~\ref{fig:N8energy} but for
+	$N=2\Omega=16$.
+}
+ \label{fig:N16energy}
+\end{figure}
+
+\begin{figure}[thb]
+ \begin{minipage}{1\hsize}
+ \begin{center}
+   \includegraphics[height=0.45\textwidth,angle=-90]{images/N16Xeq0p5occ_wo_adiabatic.eps}
+   \includegraphics[height=0.45\textwidth,angle=-90]{images/N16Xeq2occ_wo_adiabatic.eps}
+ \end{center}
+ \end{minipage}
+	\caption{The same as Fig.~\ref{fig:N8_occ} but for
+	$N=2\Omega=16$.
+}
+ \label{fig:N16_occ}
+\end{figure}
+
+\subsubsection{Closed-shell configuration}
+
+In the closed shell with $N=16$,
+the minimum-energy trajectory changes at $x=1$ from
+$j=-4$ (normal phase) to
+the BCS minimum $j>-4$ and $\phi=0$ (superfluid phase).
+At the transitional point ($x=1$), the harmonic approximation is
+known to collapse, namely to produce zero excitation energy.
+In Fig.~\ref{fig:N16energy},
+this collapsing is avoided in all the calculations (SPA/FD and CQ).
+The behaviors of the lowest excitation agree with the exact calculations,
+while the CQ method substantially underestimates those for higher states.
+This is again due to the difference in the zero-point energy in
+the ground and the excited states.
+In the CQ calculation, the first excited state is bound at $x\gtrsim 2$,
+but the second excited state is unbound for $x\lesssim 3.2$.
+
+Near the transition point from the open to closed trajectories,
+the wave functions calculated with the SPA and CQ methods somewhat differ
+from the exact ones.
+In Fig.~\ref{fig:N16_occ}, the wave functions at $x=0.5$ and 2 are presented.
+They agree with exact calculation at $x=0.5$.
+In contrast, we find some deviations for the first excited state ($k=1$)
+at $x=2$.
+This is because the $k=1$ trajectory corresponding to the first excited state
+changes its character from open to closed at $x\approx 1.8$.
+Therefore, the first excited wave function is difficult to reproduce in
+the SPA, although the wave functions for
+the ground and higher excited states show reasonable agreement.
+The similar disagreement is observed for the ground state near $x=1$.
+
+\begin{figure}[t]
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+ \includegraphics[width=70mm,angle=-90]{images/N16Pad_CQ.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+ \includegraphics[width=70mm,angle=-90]{images/N16Pad_FD.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+ \begin{minipage}{0.3\hsize}
+ \begin{center}
+ \includegraphics[width=70mm,angle=-90]{images/N16Pad_SPA.eps}
+ \end{center}
+ \captionsetup{labelformat=empty,labelsep=none}
+ \end{minipage}
+	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
+	with $\Omega=8$.
+}
+ \label{fig:N16Pad}
+\end{figure}
+
+Singular behaviors near the transition points can be also observed in
+the pair-addition transition strengths ($N=14\rightarrow 16$) shown
+in Fig.~\ref{fig:N16Pad}. 
+At $x=1$, the intraband $B(P_{\rm ad}; 0\rightarrow 0)$ shows a kink
+in the SPA,
+and $B(P_{\rm ad}; 1\rightarrow 1)$ shows another kink at $x\approx 1.8$.
+These exactly correspond to the transition points from open to closed
+trajectories.
+Nevertheless, the overall behaviors are well reproduced and
+the values at the weak and strong pairing limit are reasonably reproduced
+in the SPA.
+The CQ calculation also shows smoothed kink-like behaviors near the
+transition points.
+However, it underestimates the intraband $B(P_{\rm ad}; k\rightarrow k)$.
+The FD method does not have a kink for $B(P_{\rm ad}; 0\rightarrow 0)$,
+because $S^+(t)$ is calculated for an $N=14$ system.
+Both intraband and interband transitions in the FD calculations
+reasonably agree with the exact results at $x\gtrsim 1.8$.
+The $k=1$ state is not properly reproduced at $x\lesssim 1.8$
+with the open trajectory.
+
+For the closed-shell configurations,
+the SPA and the FD methods provide reasonable description for the
+pair-transfer transition strengths.
 
 \section{Collective model treatment} 
+The collective model has been proposed
+and utilized for the nuclear pairing dynamics
+\cite{BBPK70,delta1,delta3}.
+For those studies, the pairing gap parameter (or equivalent quantities)
+is assumed to be the collective coordinates.
+This is analogous to the five-dimensional (5D) collective (Bohr) model,
+in which the collective coordinates are assumed to be the
+quadrupole deformation parameters, $\alpha_{2\mu}$.
+The 5D collective model has been 
+extensively applied to analysis on numerous experimental data.
+On the contrary, there have been very few applications of
+the pairing collective model
+in comparison with experimental data.
+In this section, we examine the validity of
+the collective treatment of the pairing.
+
+Although the global gauge angle $\Phi$ is arbitrary,
+the deformation parameter $\alpha\equiv \braket{ \hat{S}^- }$
+in the gauge space is
+usually taken as a real value ($\Phi=0$).
+%In the superfluid phase, 
+The energy minimization with a fixed value of real $\alpha$ always
+leads to $\phi=0$.
+\begin{align}
+\alpha(j,J) = \braket{Z_0|\hat{S}^-|Z_0}
+	= \sqrt{j_1(\Omega_1-\nu_1-j_1)} +\sqrt{j_2(\Omega_2-\nu_2-j_2)}.
+ \label{Delta_BCS}
+\end{align}
+The parameter $\alpha$ is equivalent to the pairing gap $\Delta$,
+since the relation, $\Delta=G\alpha$,
+guarantees one-to-one correspondence between $\alpha$ and $\Delta$. In Sec.~\ref{sec:canonical}, we treat $\phi$ as a collective coordinate
+and $j$ as its conjugate momentum.
+The collective model treatment is based on the opposite choice,
+$j$ as a coordinate and $\phi$ as a momentum, as discussed in Sec. \ref{ATDHFB}.
+
+\begin{figure}[tb]
+ \begin{center}
+(a) \includegraphics[height=0.44\textwidth,angle=-90]{images/N8p_E.eps}
+(b) \includegraphics[height=0.44\textwidth,angle=-90]{images/N16p_E.eps}
+ \end{center}
+ \caption{Energy surfaces as functions of $j$,
+ Eq. (\ref{TDHFB_Hamiltonian_3}) with $\phi=0$,
+ for $x=0.5$, $2$, and $3.2$.
+ Dashed line is the pairing deformation parameter $\alpha$
+ of Eq.~(\ref{Delta_BCS}) as a function of $j$.
+ (a) mid-shell ($\Omega=N=8$) and (b) closed-shell ($2\Omega=N=16$).
+}
+ \label{fig:p_Delta}
+\end{figure}
+
+The problem is that
+there is no one-to-one correspondence between $j$ and $\alpha$.
+If we examine the derivative of (\ref{Delta_BCS})
+\begin{align}
+\frac{\partial\alpha}{\partial j} = \frac{-(\Omega_1-\nu_1)/2+j_1}{\sqrt{j_1(\Omega_1-\nu_1-j_1)}} + \frac{(\Omega_2-\nu_2)/2-j_2}{\sqrt{j_2(\Omega_2-\nu_2-j_2)}} ,
+ \label{dalpha}
+\end{align}
+we can find (\ref{dalpha}) is $+\infty$ for $j_{min}$ and $-\infty$ for $j_{max}$ in any two-level system.
+It indicates $\frac{\partial\alpha}{\partial j} =0$ exists at $j=j_0$ ($j_{min}<j_0<j_{max}$).
+For equal degeneracy case ($\Omega_1-\nu_1=\Omega_2-\nu_2$), $j_0=0$.
+The relation between $j$ and $\alpha$ 
+are shown by dashed lines in Fig.~\ref{fig:p_Delta} 
+for $\Omega=8$ mid-shell (a) and closed-shell (b) configurations discussed in Sec. \ref{SmallOmg}.
+The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
+and smallest at the end points of $j$.
+The constrained minimization with respect to $\alpha$ cannot 
+produce the states corresponding to $j>0$.
+Apparently, we cannot map the entire region of $j$ to $\alpha$.
+
+The collective model treatment
+requires the collective wave functions to be well localized
+in the $j<0$ region.
+The potential energy, $E(j)=\mathcal{H}(\phi=0,j;J=N/2)$ of
+Eq. (\ref{TDHFB_Hamiltonian_3}), is also shown in
+Fig.~\ref{fig:p_Delta}.
+The restriction becomes more serious for the stronger pairing cases.
+For instance, the potential with $x=3.2$ in Fig.~\ref{fig:p_Delta}(a)
+has only about 1 MeV depth at the minimum point, relative to the value
+at the boundary point ($j=0$) corresponding to
+the maximum value of $\alpha$ ($\Delta$).
+
+To simulate the result of the collective model, we requantize the ATDHFB Hamiltonian in (\ref{ATDHFB_Hamiltonian})-(\ref{mass_two_level}) by $\hat{\phi}=i\partial/\partial j$, with
+the ordering given by Pauli's prescription
+\begin{align}
+	H \left( j,i\frac{\partial}{\partial j} \right) 
+= V(j) - \frac{1}{2}\frac{1}{\sqrt{B(j)}}\frac{\partial}{\partial j}\frac{1}{\sqrt{B(j)}}\frac{\partial}{\partial j}.
+\end{align}
+The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
+with the vanishing boundary condition $\psi(j_{\rm min})=\psi(0)=0$.
+Figure~\ref{fig:Delta_E} shows two examples of the relationship 
+between excitation energies and the potential energy surface.
+In the panel (a), we show the case of large $\Omega$
+($\Omega=50$, $N=50$, and $x=2.4$),
+in which
+the excited $0^+$ states are bound up to second excitation.
+From the collective model, the energies of the ground and the first excited states
+are well described, while the deviation becomes larger for
+higher excited states.
+For very large degeneracy, the pocket of energy surface is deep, 
+hence the low-lying excited states may be described by $\alpha$. 
+However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, and $x=2.4$)
+of the panel (b), no excited states are bound by the potential
+as a function of $\alpha$.
+None of the excited $0^+$ states
+are properly described in the collective model.
+This shallow potential is a consequence of the improper
+choice of the collective coordinate $\alpha$
+which represents only the $j<0$ region.
+Therefore, the collective model treatment assuming
+$\alpha$ ($\Delta$) as the collective coordinate
+is not applicable to small-$\Omega$ and strong-pairing cases.
+
+\begin{figure}[tb]
+% \begin{minipage}{0.45\hsize}
+ \begin{center}
+(a) \includegraphics[height=0.4\textwidth,angle=-90]{images/N50Xeq2p4gap_E.eps}
+% \end{center}
+% \end{minipage}
+% \begin{minipage}{0.45\hsize}
+% \begin{center}
+(b) \includegraphics[height=0.4\textwidth,angle=-90]{images/N16Xeq2p4gap_E.eps}
+ \end{center}
+%\end{minipage}
+\caption{Potential energy surface as functions of $\alpha$ with $x=2.4$;
+(a) $\Omega=N=50$,
+(b) $2\Omega=N=16$.
+Horizontal lines 
+indicate energy spectra. Black lines are obtained
+from the potential energy surface, and green lines are 
+obtained with the CQ method
+(Sec.~\ref{sec:canonical}).
+%Left panels: $\Omega=50$, $N=50$ system;
+% Right panels: $\Omega=8$, $N=16$ system.
+}
+ \label{fig:Delta_E}
+\end{figure}
 
@@
 
-\section{Derivation of the collective subspace in adiabatic self-consistent collective coordinate method}
-
-\section{Application of SPA in non-integrable system}
+\section{Theoretical framework of ASCC+SPA in non-integrable system}
 
@@
 
-\section{Properties of the spin-coherent state}
-\label{formula}
+\section{Matrix elements of the spin-coherent state}
+\label{formula1}
 The time-dependent coherent state classified into the spin-coherent state is employed in (\ref{coherent}). We derive the necessary formula for the spin-coherent state in this subsection. \par
@@
 
-We conclude the useful formula for the spin-coherent state as follows.
+We conclude the useful formulae for the spin-coherent state as follows.
 \begin{framed}
@@
 	\label{ddt}
+\end{equation}
+\end{itemize}
+\end{framed}
+
+\section{Matrix elements in special canonical variables $(\chi,j)$ representation}
+\label{formula2}
+In the text, we mostly use the transformed formulae derived in the previous section.
+We use $(\chi,j)$ representation. which is defined from the transformation of the complex number $Z$
+\begin{align}
+  Z_l &\equiv \tan{\frac{\theta_l}{2}}e^{-i\chi_l} \\
+  j_l &\equiv S_l(1-\cos{\theta}_l) .
+\end{align}
+In such representation, most of matrix elements of spin-coherent state become concise.
+Because the derivations of the transformation for those matrix elements are simple, we omit the explanation here.
+We conclude the useful formulae as follows.
+\begin{framed}
+  \begin{itemize}
+ \item Expectation value of $\hat{S}^0$
+\begin{equation}
+     \braket{Z|\hat{S}^0|Z} = \sum_l (j_l-S_l)
+\end{equation}
+ \item Expectation value of $\hat{S}^+$
+\begin{equation}
+     \braket{Z|\hat{S}^+|Z} = \sum_l \sqrt{j_l(2S_l-j_l)}e^{-i\chi_l}
+\end{equation}
+ \item Expectation value of $\hat{S}^-$
+\begin{equation}
+     \braket{Z|\hat{S}^-|Z} = \sum_l \sqrt{j_l(2S_l-j_l)}e^{i\chi_l}
+\end{equation}
+ \item Expectation value of $\hat{S}^+\hat{S}^-$
+\begin{equation}
+    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_l \left( 2S_l j_l - j_l^2 +\frac{j_l^2}{2S_l} \right) 
++ 2\sum_{l_1\le l_2} \sqrt{j_{l_1}j_{l_2}(2S_{l_1}-j_{l_1})(2S_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   .
+\end{equation}
+ \item Expectation value of $\frac{\partial}{\partial t}$
+\begin{equation}
+       \braket{Z|\frac{\partial}{\partial t}|Z} = \frac{1}{i}\sum_l j_l \dot{\chi_l}
+	\label{ddt2}
 \end{equation}
@@
 
-\section{Action in canonical variables representation}
-We derived the action in the previous section. Using the formula in Sec. \ref{formula}, the expectation value of pairing Hamiltonian is
+\section{Action in pairing model}
+We derived the action in the previous sections. Using the formula in Sec. \ref{formula1}, the expectation value of pairing Hamiltonian is
 \begin{align}
@@
 \end{align}
-To obtain more tractable form of the action, we transform the complex variables $Z_l$ into real variables $(\theta_l,\chi_l)$
-by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$). The Lagrangian becomes
-\begin{align}
-\mathcal{L}(t) = \sum_l S_l
-	(1-\cos{\theta_l})\dot{\chi_l} - \braket{Z|H|Z} .
-\end{align}
-If we choose the $\chi_l$ as canonical coordinates, the conjugate momenta $j_l$ are given by
-\begin{align}
-  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=S_l(1-\cos{\theta}_l) .
-\end{align}
-Therefore, the Lagrangian in canonical variables representation becomes
+Using the canonical variables $(\chi,j)$, we can obtain the tractable form of the action based on Sec. \ref{formula2}. 
+The Lagrangian in $(\chi,j)$ representation becomes
 \begin{align}
@@
 	=& \sum_l \epsilon_l\nu_l + \sum_l 2\epsilon_lj_l - g\sum_l \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
-	&- g\sum_{l_1\le l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   .
-\end{align}
+	&- 2g\sum_{l_1\le l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   .
+\end{align}
+
+\chapter{Properties of superfluid ground state in pairing model}
+The superfluid ground state correspond to the local minimum point in energy surface.
+The time-dependent coherent state described in (\ref{coherent}) attributes to BCS trail wave function in $\chi_l=0$.
+For the simplicity, here, we only consider the even-particle system with $\nu=0$ (without Pauli blocking).
+
+\section{Two-level system}
+\label{two-level}
+With fixed expectation value of total particle number $N=2J$, the superfluid ground state correspond to the local minimum point in (\ref{Hamiltonian2})
+\begin{align}
+	\left. \frac{\partial\mathcal{H}(\phi,j;J)}{\partial j} \right|_{\phi=0}=0 .
+	\label{dH}
+\end{align}
+The explicit form of (\ref{dH}) is
+\begin{align}
+	\frac{2(\epsilon_2-\epsilon_1)}{g} =
+	2(S_2q_2-S_1q_1)-(q_2-q_1) + 2\left(\frac{q_2}{\sqrt{1-q_2^2}}S_1\sqrt{1-q_1^2}
+	-\frac{q_1}{\sqrt{1-q_1^2}}S_2\sqrt{1-q_2^2}\right) ,
+	\label{BCS_2level}
+\end{align}
+where 
+\begin{equation}
+	q_l=\cos{\theta_l} = \frac{\Omega_l - J -2(-1)^l j}{\Omega_l} 
+	\quad \mbox{ for } l=1,2
+	\label{q_l}
+\end{equation}
+with the range $-1\le q_l\le 1$. $q_l=1$ corresponds to empty occupation and $q_l=-1$ corresponds to full occupation.
+
+(\ref{BCS_2level}) has solution only for the superfluid state.
+In open shell, (\ref{BCS_2level}) always have solution.
+In closed shell, substituting $q_1=-1$ and $q_2=1$ into (\ref{BCS_2level}) leads the phase transition point between normal state and superfluid state.
+The last term of right side in (\ref{BCS_2level}) becomes
+\begin{align*}
+	& 2\left(\frac{q_2}{\sqrt{1-q_2^2}}S_1\sqrt{1-q_1^2}
+	-\frac{q_1}{\sqrt{1-q_1^2}}S_2\sqrt{1-q_2^2}\right) \\
+	=\ \ & 2\left(\frac{S_2-j_2}{\sqrt{j_2(2S_2-j_2)}}\sqrt{j_1(2S_1-j_1)}
+	- \frac{S_1-j_1}{\sqrt{j_1(2S_1-j_1)}}\sqrt{j_2(2S_2-j_2)}\right) \\
+	=\ \ & 2\left(\frac{S_2-j_2}{\sqrt{2S_2-j_2}}\sqrt{j_1}
+	- \frac{S_1-j_1}{\sqrt{j_1}}\sqrt{2S_2-j_2}\right) \\ 
+	\xrightarrow[j_2\to0]{j_1\to2S_1}\ \ &  4 \sqrt{S_1S_2} .
+\end{align*}
+From second line to the third line, we used the fact of closed shell $J=2S_1$. With $\Omega_l=2S_l$, the phase transition point in closed shell is
+\begin{align}
+	g_c = \frac{2\Delta\epsilon}{\Omega_1+\Omega_2+2\sqrt{\Omega_1\Omega_2}-2} ,
+	\label{g_c}
+\end{align}
+where $\Delta\epsilon=\epsilon_2-\epsilon_1$. When $\Omega_1=\Omega_2=\Omega$, (\ref{g_c}) becomes
+\begin{align}
+	g_c = \frac{\Delta\epsilon}{2\Omega-1} ,
+	\label{g_2}
+\end{align}
+In the textbook \cite{}, the dimensionless coupling constant $x$ is defined in
+\begin{align}
+	x = 2g \frac{\Omega}{\Delta\epsilon} .
+	\label{x}
+\end{align}
+We can find the phase transition occurs at
+\begin{align}
+	x_c = 2g_c \frac{\Omega}{\Delta\epsilon} = \frac{2\Omega}{2\Omega-1} \approx 1.
+	\label{x_c}
+\end{align}
+The last approximation performs well for $\Omega>>1$. We often use the dimensionless coupling constant $x$ in the text.
+
+\chapter{Adiabatic self-consistent collective coordinate method}
+
+\section{Theoretical framework}
+\section{Matrix elements of local harmonic approximation in pairing model}
 

### 2018-12-04 thesis/thesis.tex
thesis

@@
 \usepackage{braket}
+\usepackage[stable]{footmisc}
 
@@
 \pagestyle{fancy} % options: empty , plain , fancy
-\renewcommand{\headrulewidth}{0pt} % customise the layout...
-\lhead{}\chead{}\rhead{}
+\renewcommand{\headrulewidth}{1pt} % customise the layout...
+\rhead[]{\rightmark}
+\lhead[\leftmark]{}
 \lfoot{}\cfoot{\thepage}\rfoot{}
+\renewcommand{\chaptermark}[1]{\markboth{Chapter\ \thechapter\ #1}{}}
+\renewcommand{\sectionmark}[1]{\markright{Section\ \thesection\ #1}{}}
 
@@
 
+\chapter*{Absract}
+
+In most of nuclei, the structure of low-lying excited $0^+$ states, which had been called as $\beta$ vibration or two-phonon excitation, are complicate and mysterious from plenty of recent experimental data.
+The common suggestion from those experimentalists is that the pairing correlation plays an important role in such excited $0^+$ states because they found strange cross sections of two-nucleon transfer reactions.
+From theoretical viewpoint, excited $0^+$ states correspond to pairing vibrational mode, the elementary mode of excitation of pairing collective motions, in superfluid nuclei.
+Because quantum fluctuation is large in low-lying region, To understand such excited $0^+$ states, extend to the large-amplitude regime, but also pairing correlation.
+
 \pagenumbering{roman}
 \tableofcontents
+\thispagestyle{empty}
 
@@
 
-Mean field model is standard tool to describe the structure of atomic nuclei.
-The idea of mean field model is based on the primary theoretical framework of shell model introduced by Mayer and Jensen in 1949.
+Mean-field model is standard tool to describe the structure of atomic nuclei.
+The idea of mean-field model is based on the primary theoretical framework of shell model introduced by Mayer and Jensen in 1949.
 Mean field picture indicates that the nucleon can be described in single-particle motion in the mean field potential created by the whole nucleons in the nucleus.
@@
 Because
+
+\begin{figure}[tb]
+ \begin{center}
+    \includegraphics[width=100mm]{images/S_n.eps}
+ \end{center}
+  \caption{Separation energy for Sn, Sb, Te isotopes as a function of neutron number obtained from experimental data \cite{KJJ12}.}
+  \label{S_n}
+\end{figure}
 
@@
 The isotopes in even neutron number have about $2\sim3$ MeV larger separation energies than the isotopes in odd neutron number.
-It is odd-even staggering (OES) effect, which is detected in whole mass region of nuclei ( Fig.
+It is odd-even staggering (OES) effect, which is detected in whole mass region of nuclei (Fig.
 \ref{gap}).
@@
 The two-body attractive interaction which couples two identical nucleons into $J^{\pi}=0^+$ state is called pairing correlation.
-\begin{figure}[htbp]
- \begin{center}
-    \includegraphics[width=100mm]{images/S_n.eps}
- \end{center}
-  \caption{Separation energy for Sn, Sb, Te isotopes as a function of neutron number obtained from experimental data \cite{KJJ12}.}
-  \label{S_n}
-\end{figure}
-
-\begin{figure}[htbp]
+
+\begin{figure}[tb]
  \begin{center}
@@
 
-Because pairing correlation is two-body interaction, a theoretical framework beyond the mean field model seems to be necessary.
-However, there is a tricky approximated theory, BCS theory, enable us to describe pairing correlation within mean field model.
+Because pairing correlation is two-body interaction, a theoretical framework beyond the mean-field model seems to be necessary.
+However, there is a tricky approximated theory, BCS theory, enable us to describe pairing correlation within mean-field model.
 In BCS theory, the ground state is superposed by the states with different particle number.
@@
 With symmetry breaking, the corresponding order parameter, pairing gap $\Delta$, has finite value.
-Based on BCS theory, because the energy of each particle in a $J^{\pi}=0^+$ pair is $E_k=\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}$, where $\epsilon_k$ is single particle energy, $\lambda$ is Fermi energy, the minimum excitation energy is $2\Delta$.
-In fact, pairing gap corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei discussed in previous paragraph.
+Based on BCS theory, because the energy of each particle in a $J^{\pi}=0^+$ pair is $E_k=\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}$, where $\epsilon_k$ is single particle energy, $\lambda$ is Fermi energy, the lowest single-particle excited state corresponds to one-pair broken state with minimum excitation energy $2\Delta$ In fact, pairing gap corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei discussed in previous paragraph.
 As same as superconductivity in condensed matter physics, the superfluid nucleus is defined when $\Delta\neq0$ in ground state.
@@
 HFB theory is the naturally extension of Hartree-Fock (HF) theory by introducing Bogoliubov transformation.
-Under Bogoliubov transformation, the particles become to quasiparticles, and the mean field potential is extended to generalized form including pairing field.
+Under Bogoliubov transformation, the particles become to quasiparticles, and the mean-field potential is extended to generalized form including pairing field.
 After HFB theory had been applied to nuclear physics in 1958, the structure of ground states in nuclei was examined by plenty of studies.
-Up to now, HFB theory is the standard mean field theory to describe nuclear structure including pairing correlation.
+Up to now, HFB theory is the standard mean-field theory to describe nuclear structure including pairing correlation.
 
@@
 \label{1-1-2}
-Due to the superfluid state breaks the symmetry in U(1) gauge space, we expect that there are two types of elementary modes of excitation for pairing collective motion in nuclei.
-Two types of elementary modes of excitation are Nambu-Goldstone (NG) mode, pairing rotation, recovering the broken symmetry in U(1) gauge space, and Higgs mode, pairing vibration, fluctuating around the energy minimum point.
-
-\begin{figure}[htbp]
+
+\begin{figure}[bt]
  \begin{center}
@@
 \end{figure}
-First, we discuss about pairing rotation.
-In classical picture, pairing rotation is the motion which the system rotates in the U(1) gauge space (red bi-direction arrow in Fig.
-\ref{pair_rot}).
-The motion is described by the coordinate, gauge angle $\Phi$, and the corresponding momentum, total particle number $N$.
-%It is similar to normal rotation in 3D space which described by the angles ($\theta_x, \theta_y, \theta_z$) and their conjugate angular momenta ($J_x, J_y, J_z$). 
-Because the total particle number is unchanged in time evolution, the momentum $N$ is conserved quantity.
-In quantum picture, if we assume the ground state in a particle number $N_0$ as the ``ground state'', the ground states in $N=N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing rotational mode.
-The excitation energy is $E_{\rm rot}^{\rm pair}=\frac{(N-N_0)^2}{2\mathcal{J}}$, where $\mathcal{J}$ is the pairing-rotational moment of inertia which characterizes the pairing rotation.
-In experiment, the pairing rotational band is expected to be observed in even-even isotope chain or even-even isotone chain between two magic numbers.
-One clear observation is found in Sn isotopes shown in Fig.
-\ref{pair_rot}.
-Except  a constant value and linear term with respect to mass number $A$, we can find the energies of ground states consist of a parabolic line - pairing rotational band.
-Recently, the systematic study for the pairing-rotational moment of inertia has been done in Ref.
-\cite{HN16}.
-The experimental moments of inertia obtained from two neutron(proton) separation energies have excellent correspondence with the theoretical moments of inertia obtained from NG mode in quasiparticle random phase approximation (QRPA) \cite{TV61} based on HFB mean field theory, not only for the spherical nuclei, but also for the deformed nuclei.
-Because the pairing-rotational moments of inertia are free from ambiguities caused from odd-even system, they are supposed to be excellent indicators of pairing correlation rather than pairing gaps.
-
-Next, we discuss about pairing vibration.
-We emphasize that there are two types of pairing vibrations, one which vibrates around normal ground state ($\Delta\approx 0$), and another one which vibrates around superfluid ground state ($\Delta\neq 0$).
-The structures between two vibrational modes are quite different.
-%The former one is well understood because the structure of the excited $0^+$ states are $2np2nh$ configurations, detected from the energy spectra around ${}^{208}$Pb. 
-Here, we only focus on the later one.
-In classical picture, the later one vibrates around one of the degenerated energy minimum points. Depending on the intrinsic structure, various pairing vibrations can exist in one nucleus. 
-%In general, the motion is supposed to be described by the coordinate, pairing gap $\Delta$, and its corresponding momentum\footnote{Because $\Delta$ is order parameter, it is naturally supposed to be the coordinate to describe the pairing vibration in previous studies.
-However, we found $\Delta$ is not proper coordinate in most of case from our study.
-The detail is discussed in Chapter 3 and 4.}.
-In quantum picture, if we assume the ground state in a particle number $N_0$ as the ``ground state'', the excited states in $N=N_0, N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing vibrational mode.
-The excitation energy is $E_{\rm vib}^{\rm pair}=n_{\alpha}\hbar\omega$, where $n_{\alpha}$ is the number of phonon and $\alpha$ is the label to distinguish different pairing vibrational modes.
-Because $2\Delta$ is the minimum energy to break one-pair, the collectivity is supposed to be strong when $E_{\rm vib}^{\rm pair}<2\Delta$.
-Thus, low-lying excited $0^+$ states in even-even nuclei are possible to be pairing vibrational states.
-Except the region around the magic number, excited $0^+$ states below $2\Delta$ exist in most of even-even nuclei.
-However, it is difficult to observe the signatures for pairing vibration directly from experiment.
-The properties of pairing vibration in nuclei are not well understood up to now.
-
-The signatures for pairing collective motion can also be observed from the two-neutron(proton) transfer reaction \cite{BHR73}, such as $(p, t)$, $(t, p)$, and $({}^3{\rm He}, n)$.
-The cross sections of two particle transfer reaction strongly depend on the matrix elements of $J^{\pi}=0^+$ pair-transition operators (e.g.
-pair-additional transition: $\sigma( P_{ad};0_{\alpha}^+(N) \to 0_{\beta}^+(N+2))\sim |\braket{N+2,\beta|\sum_k a^{\dag}_k a^{\dag}_{\bar{k}}|N,\alpha}|^2$).
-From theoretical prediction, the pairing correlation is known to enhance $\sigma(g.s.\to g.s.)$ and decrease $\sigma(g.s.\to 0_{ex}^+)$ significantly, hence, $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)\ll 1$ is expected in superfluid system.
-One example of $(p, t)$ reactions is demonstrated in Fig.
-\ref{pair_rot}.
-As mentioned in previous paragraph, the ground states of even-even Sn isotopes consist of a pairing rotational band.
-In such situation, we can find intraband transition is dominant with respect to interband transition.
-Therefore, the cross sections of two-neutron transfer reaction is consistent with theoretical prediction.
-In general, the ratio $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)$ for two-neutron(proton) transfer reaction are excellent indicators to describe the collectivity of pairing dynamics.
-
-\begin{figure}[htbp]
+
+\begin{figure}[tb]
  \begin{center}
@@
 
-\section{Motivation of this study}
+Due to the superfluid state breaks the symmetry in U(1) gauge space, we expect that there are two types of elementary modes of excitation for pairing collective motion in nuclei.
+The elementary modes of excitation are Nambu-Goldstone (NG) mode, pairing rotational mode, recovering the broken symmetry in U(1) gauge space, and Higgs mode, pairing vibrational mode, fluctuating around the energy minimum point.
+
+First, we discuss about pairing rotation.
+In classical picture, pairing rotation is the motion which the system rotates in the U(1) gauge space (red bi-direction arrow in Fig.
+\ref{pair_rot}).
+The motion is described by the coordinate, gauge angle $\Phi$, and the corresponding momentum, total particle number $N$.
+%It is similar to normal rotation in 3D space which described by the angles ($\theta_x, \theta_y, \theta_z$) and their conjugate angular momenta ($J_x, J_y, J_z$). 
+Because the total particle number is unchanged in time evolution, pairing rotation corresponds to constant of motion.
+In quantum picture, if we assume the ground state of $N_0$ particle system as the ``ground state'', the ground states in $N=N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing rotational mode.
+The excitation energy is $E_{\rm rot}^{\rm pair}=\frac{(N-N_0)^2}{2\mathcal{J}}$, where $\mathcal{J}$ is the pairing-rotational moment of inertia.
+In experiment, the pairing rotational band is expected to be observed in even-even isotope chain or even-even isotone chain in open-shell nuclei.
+A clear observation is found in Sn isotopes shown in Fig.
+\ref{pair_rot}.
+Except a constant value and linear term with respect to mass number $A$, we can find the energies of ground states consist of a parabolic line - pairing rotational band.
+Recently, the systematic study for the pairing-rotational moment of inertia has been done in Ref.
+\cite{HN16}.
+The experimental moments of inertia obtained from two neutron(proton) separation energies have excellent correspondence with the theoretical moments of inertia obtained from NG mode in quasiparticle random phase approximation (QRPA) \cite{TV61} based on HFB mean-field theory, not only for the spherical nuclei, but also for the deformed nuclei.
+Because the pairing-rotational moments of inertia are free from ambiguities caused from odd-even system, they are supposed to be excellent indicators of pairing correlation rather than pairing gaps.
+
+Next, we discuss about pairing vibration.
+We emphasize that there are two types of pairing vibrations, one which vibrates around normal ground state ($\Delta\approx 0$), and another one which vibrates around superfluid ground state ($\Delta\neq 0$).
+The structures of two vibrational modes are quite different.
+%The former one is well understood because the structure of the excited $0^+$ states are $2np2nh$ configurations, detected from the energy spectra around ${}^{208}$Pb. 
+Here, we only focus on the later case.
+In classical picture, the system vibrates around one of the degenerated energy minimum points. Depending on the intrinsic structure, various pairing vibrations are able to exist in one nucleus. 
+%In general, the motion is supposed to be described by the coordinate, pairing gap $\Delta$, and its corresponding momentum\footnote{Because $\Delta$ is order parameter, it is naturally supposed to be the coordinate to describe the pairing vibration in previous studies.
+However, we found $\Delta$ is not proper coordinate in most of case from our study.
+The detail is discussed in Chapter 3 and 4.}.
+In quantum picture, if we assume the ground state of $N_0$ particle system as the ``ground state'', the excited states in $N=N_0, N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing vibrational mode.
+The excitation energy is $E_{\rm vib}^{\rm pair}=n_{\alpha}\hbar\omega$, where $n_{\alpha}$ is the number of phonon and $\alpha$ is the label to distinguish different pairing vibrational modes.
+Because $2\Delta$ is the minimum energy to break one-pair, the collectivity is supposed to be strong when $E_{\rm vib}^{\rm pair}<2\Delta$.
+Thus, low-lying excited $0^+$ states in even-even nuclei are possible to be pairing vibrational states.
+Except the region around the magic number, excited $0^+$ states below $2\Delta$ exist in most of even-even nuclei.
+However, it is difficult to observe the signatures for pairing vibration directly from experiment.
+The properties of pairing vibration in nuclei are not well understood up to now.
+% because the multipole correlations interfere the pairing correlation significantly
+
+The signatures for pairing collective motion can also be observed from the two-neutron(proton) transfer reaction \cite{BHR73}, such as $(p, t)$, $(t, p)$, and $({}^3{\rm He}, n)$.
+The cross sections of two particle transfer reaction strongly depend on the matrix elements of $J^{\pi}=0^+$ pair-transition operators (e.g.
+pair-additional transition: $\sigma( P_{ad};0_{\alpha}^+(N) \to 0_{\beta}^+(N+2))\sim |\braket{N+2,\beta|\sum_k a^{\dag}_k a^{\dag}_{\bar{k}}|N,\alpha}|^2$).
+From theoretical prediction, the pairing correlation is known to enhance $\sigma(g.s.\to g.s.)$ and decrease $\sigma(g.s.\to 0_{ex}^+)$ significantly, hence, $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)\ll 1$ is expected in superfluid system.
+One example of $(p, t)$ reactions is demonstrated in Fig.
+\ref{pair_rot}.
+As mentioned in previous paragraph, the ground states of even-even Sn isotopes consist of a pairing rotational band.
+In such situation, we can find intraband transition is dominant with respect to interband transition.
+Therefore, the cross sections of two-neutron transfer reaction is consistent with theoretical prediction.
+In general, the ratio $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)$ for two-neutron(proton) transfer reaction are excellent indicators to describe the collectivity of pairing dynamics.
 
 \subsection{Mysterious excited $0^+$ states and pairing dynamics}
-In most of nuclei, the structure of excited $0^+$ states is complicate and unclear.
+In most of nuclei, the structure of excited $0^+$ states in a low-lying region (a few MeV excitation) is complicate and unclear \cite{HW11}.
 The reason is that not only pairing correlation but also deformations and multipole correlations influence the excited $0^+$ states significantly.
 The various correlations competing with each other construct plenty of mysterious excited $0^+$ states.
-
-After the concept of pairing vibration was introduced, it encountered the problem for the large asymmetry cross sections between $(p, t)$ and $(t, p)$ reaction in actinide region observed from experiment.
+We present several examples for these excited $0^+$ states observed from experiment.
+
+After the concept of pairing vibration was introduced, it encountered the problem for the large asymmetry cross sections between $(p, t)$ and $(t, p)$ reaction in actinide region (e.g.
+Th, U, Pu, Cm) observed from experiment.
 In low-lying energy region, the cross section of $\sigma(g.s.\to 0_{ex}^+)$ is about $15\%$ of $\sigma(g.s.\to g.s.)$ for $(p, t)$ reaction \cite{MEFSS70, MEFSS72}, while the signal of $\sigma(g.s.\to 0_{ex}^+)$ is extremely weak for $(t, p)$ reaction \cite{Cas72}.
@@
 Another interpretation for such phenomena is using microscopic interaction, including multipole pairing correlations and quadrupole particle-hole interactions \cite{RB76}.
-Although the approaches are different, they succeeded to reproduce the asymmetry cross section of two-neutron transfer reaction in actinide region.
-
-$\beta$ vibration
-Collective motion is the essential idea to explain the excited states in nuclei.
+Although the approaches are different, they reproduced the asymmetry cross sections of two-neutron transfer reaction in actinide region.
+These studies hinted the importance of the quadrupole deformation and interactions in low-lying excited $0^+$ states.
+
+We can consider the excited $0^+$ states from common viewpoint, liquid drop with surface vibration.
+Bohr collective model, which is well-known and successful model describing the quadrupole collective motions in nuclei \cite{BM75} has been constructed based on the idea of liquid drop.
+The $0_2^+$ states in the model correspond to $\beta$ vibration and the first $2^+$ state in $K=2$ bands correspond to $\gamma$ vibration, in quadrupole deformed nuclei.
+Also, their rotational bands exist in each vibrational mode.
+The nuclei in rare earth region (e.g.
+Sm, Gd, Dy, Er, Yb, Hf, W), well deformed nuclei, had been supposed to be the typical examples of quadrupole collective motions in the early days.
+With the development for extracting $B(E2)$ values from experiment, however, the doubt whether $0_2^+$ states in rare earth region is $\beta$ vibration arose in the last decades \cite{G01, Kulp08, SS11}.
+They found that only a part of $B(E2)$ values related to the $0_2^+$ states agree with the predicted $B(E2)$ values in pure $\beta$ vibration picture.
+Moreover, for $E0$ transition, very few $0_2^+$ states satisfies the range of $\rho^2(E0)$ values which the $\beta$ vibrational picture is good.
+On the other hand, they detected strong cross sections $\sigma(g.s.\to 0_{2}^+)$ in both $(t, p)$ and $(p, t)$ reactions.
+These results suggest that $0_2^+$ states in rare earth region are not pure $\beta$ vibrational states, but some mixed states with the importance of pairing correlation.
+
+\begin{figure}[tb]
+ \begin{center}
+    \includegraphics[width=100mm]{images/phonon.eps}
+ \end{center}
+ \begin{center}
+    \includegraphics[width=100mm]{images/112Cd.eps}
+ \end{center}
+  \caption{$B(E2)$ values, relative to the $B(E2; 2_1^+\to 0_1^+)$ value, and energy spectra in phonon excitation picture.
+Upper panel: expected $B(E2)$ values for a quadrupole harmonic vibrator.
+Lower panel: data observed for ${}^{112}$Cd.
+Dashed transitions indicate an unobserved transition.
+Detailed information is discussed in Ref.
+\cite{GW10}.}
+  \label{112Cd}
+\end{figure}
+The mystery of excited $0^+$ states exist not only in deformed nuclei, but also in spherical nuclei.
+A best example is the structure of $0_2^+$ or $0_3^+$ states in Cd isotopes observed in recent experiment \cite{GW10}.
+The lower part of Fig.
+\ref{112Cd} shows the excitation energy and $B(E2)$ transition strength in ${}^{112}$Cd.
+Comparing with the typical values for the ideal quadrupole harmonic vibration in spherical nuclei shown in the upper part of Fig.
+\ref{112Cd}, we can find that the observed excitation energy spectra have good coincidence with phonon excitation picture.
+The $0_2^+$ or $0_3^+$ states seem to can be interpreted as two-phonon or three-phonon excitation.
+However, the $B(E2)$ values are very different comparing with each other, especially for the no observed decay from $0_{2ph}^+$ to $2_1^+$ state.
+Such phenomena are also seen in other Cd isotopes.
+The configuration of these $0^+$ states are supposed to be not pure phonon excitation, but proton pair-excitation between $2p_{1/2}$ and $1g_{9/2}$ orbits from the hint of the ground state configurations of Ag isotopes \cite{HW11}.
+The pairing should plays an important role if the excited $0^+$ states are described by pair-excitation.
+
+%Collective motion is the essential idea to explain the excited states in nuclei.
 The quadrupole collective motion described by the quadrupole deformation parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,0)$ is known as the most typical collective motion.
@@
 
+\section{Motivation of this study}
+We aim to understand the low-lying excited $0^+$ states ($\sim$ a few MeV excitation) from nuclear many-body theory.
+As mentioned above, pairing correlation is supposed to play a significant role in such excited $0^+$ states.
+We discuss the theoretical approach  to describe the pairing dynamics in the following.
+
 \subsection{Theoretical problem}
-%As discussed in previous section, the low-lying excited $0^+$ states are not be understood in general. 
-We aim to understand the mysterious excited $0^+$ states discussed in previous section based on mean field approach.
-In low-energy region, the pairing correlation supposed to be important as the quadrupole correlation.
-The most well-known and successful model is Bohr model, which was introduced to describe low-energy nuclear collective motion in quadrupole degrees of freedom with the deformation parameters $(\beta,\gamma)$ and the Euler angles $(\phi,\theta,\psi)$.
-However, the pairing degrees of freedom is not included in the Bohr model.
+
+Time-dependent mean-field (TDMF) theory is a standard theory to describe the nuclear dynamics.
+In principle, TDMF enables us to describe the collective motions from the microscopic degrees of freedom without any artificial parameters.
+Inclusion of the pairing correlation leads to the time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, which has been utilized for plenty of nuclear structure and reaction studies \cite{NMMY16}.
+
+%QRPA
+Quasiparticle random phase approximation (QRPA) theory, which correspond to the small amplitude approximation of TDHFB, is known as the most common approach to describe the structure of collective excited states.
+From a number of studies, we can find that the giant resonances (locating at a few MeV$\sim$dozens of MeV excitation with broad width) can be well described by the QRPA \cite{Eba10, YN11, YN13, SL13-2}.
+With density functional formalism, recently, QRPA equation can be solved in finite amplitude method (FAM) \cite{Na07}.
+FAM, which reduce the computational time significantly, enables the linear response calculation for deformed nuclei in allowable computational time.
+%and is becoming the standard way to solve the QRPA equation numerically. 
+The QRPA is not only useful to predict the collective motions which have not been observed such as exotic nuclei, but also can become the basic concept to construct a theoretical framework beyond the linear regime.
+On the other hand, the QRPA description for the low-lying collective excited states is not as good as the giant resonances.
+The effects of anharmonic vibration and shape coexistence are often important in low-energy region \cite{HW11}, while QRPA is nothing but harmonic approximation.
+For example, the excitation energies of $0_2^+$ states in rare-earth region have large deviation between QRPA calculations and experimental data \cite{TE11}.
+
+%Large amplitude motion, Adiabatic approach
+To describe the low-lying excited states, especially for the excited $0^+$ states, we need to introduce the large-amplitude motions beyond the linear regime.
+Collective model, which is designed by a couple of collective coordinates and their collective potential and mass parameters, is useful for the large-amplitude dynamics.
+The most popular phenomenological collective model is Bohr collective model, five-dimensional collective Hamiltonian (5DCH) with the quadrupole deformation parameters $(\beta,\gamma)$ and the Euler angles $(\phi,\theta,\psi)$.
+It has been applied to describe the low-lying excited states in realistic nuclei, with the construction of the collective potential and mass parameters from the microscopic degrees of freedom.
+However, the pairing degrees of freedom are not explicitly included in the Bohr collective model.
 As discussed in Sec.
 \ref{1-1-2}, the pairing vibrational degrees of freedom supposed to be a key ingredient to understand the low-lying  excited $0^+$ states.
- the pairing vibrational degrees of freedom is necessary to include in the collective model. the role of pairing correlation is hardly discussed up to now.
-The degrees of freedom for pairing collective motion are supposed to be necessary including the collective model.
-
-The study about the collective model for pairing collective motion was firstly introduced by Bes.
+We have great interest for the collective coordinates describing the pairing corrective motions.
+
+The discussion for the collective model describing the pairing collective motions is not so much.
+The first study was introduced by Bes.
 et al.
@@
 They constructed phenomenological pairing collective model by two degrees of freedom, the pair deformation parameter (pairing gap) $\Delta$ and the global gauge angle $\Phi$.
-After the pairing collective model was formulated, it was applied to several studies for nuclear structure \cite{GPBW85, ZPPRS99, P07}.
+After the pairing collective model was formulated, it was combined with the Bohr collective Hamiltonian and applied to describe the nuclear structure \cite{GPBW85, ZPPRS99, P07}.
 In Ref.
-\cite{ZPPRS99}, the $B(E2)$ transition improved by introducing pairing degrees of freedom.
-On the other hand, the wave function of ground state from collective model looks like unusual because the pairing gap $\Delta_{vib}$ at the peak of the wave function is smaller than the pairing gap $\Delta_{eq}$ obtained from BCS equation.
-
-It is supposed to be important to find the collective coordinates describing the pairing collective motions from the microscopic degrees of freedom without any assumption.
-
-The difficult point is the requantization of the pairing collective motion. Such difficulty is not found in quadrupole collective motion.
-
-\subsection{Our idea}
-
-\subsection{Outline of this thesis}
-In this study, we concentrate in the pairing model which only contains pairing interaction in two-body interaction to construct the theoretical framework of the requantization.
-
+\cite{ZPPRS99}, the excitation energy and $B(E2)$ transition are improved by introducing pairing degrees of freedom.
+On the other hand, the wave function of ground state from collective model looks like unusual because the gap parameter $\Delta_{vib}$ at the peak of the pairing collective wave function is smaller than the pairing gap $\Delta_{eq}$ obtained from BCS equation.
+%There is no further discussion about the unusual behaviors. Also, two-particle transition strength is hardly discussed in the collective model.
+%The problem is supposed to be the phenomenological degrees of freedom for pairing collective motion.
+
+The question is that whether the pair deformation parameter $\Delta$ is proper to describe the pairing vibration, as the quadrupole deformation parameters $Q_{2\mu} (\mu=\pm2,\pm1,0)$ describing the quadrupole surface vibration.
+From the nature viewpoint, the time evolution of $Q_{2\mu}$ correspond to nuclear vibrations in liquid drop picture, while the time evolution of $\Delta$ is difficult to be imagined as a shape vibration.
+We need to explore more to understand the nature of pairing dynamics in large-amplitude regime.
+
+\subsection{Our approach}
+
+To understand pairing dynamics in large-amplitude regime, we think that it is important to find the collective coordinates describing the pairing collective motions from the TDHFB dynamics itself without any assumption.
+Apart from the realistic nuclear system, as the first step, we study the pairing collective motions in pairing model, which only contains the monopole pairing correlation in two-body interaction.
+In this model, the collective motions obtained from TDHFB degrees of freedom are pure pairing collective motions.
+
+In fact, the TDHFB degrees of freedom equal to the number of single-particle levels, in pairing model.
+Furthermore, the TDHFB degrees of freedom consist of one constant of motion, pairing rotation, and other intrinsic degrees of freedom.
+One-level system, which contains only one pairing rotational mode, is well understood (seniority scheme in the textbook \cite{RS80}).
+All we have to do is to study the multi-level system.
+We categorize two types of multi-level system, two-level system and the system more than three-level.
+The former one is two-dimensional integrable system.
+We have two explicit coordinates to describe pairing rotation and pairing vibration, respectively.
+Thus, the pairing collective motions can be properly described in such coordinates.
+The later one is non-integrables system.
+The collective coordinate describing the pairing vibrational mode is not explicit.
+However, we can find such collective coordinate decoupled from other intrinsic degrees of freedom by using adiabatic self-consistent collective coordinate (ASCC) method \cite{MNM00, N2012}.
+
+With these collective coordinates, we quantize them to obtain the collective excited states.
+We call this procedure as ``requantization''.
+The typical requantization method is Pauli's prescription, a type of canonical quantization, which has been applied to requantize the collective Hamiltonian, such as 5DCH \cite{KB67} and pairing collective Hamiltonian \cite{BBPK70}.
+However, there is no guarantee whether Pauli's prescription is proper.
+In addition, Pauli's prescription is not available for the general collective Hamiltonian including the higher-oder terms of momenta.
+Such requantization problems are arisen to describe the pairing collective motions at the beginning of our study. 
+To examine the proper requantization procedure, we introduce other possible requantization methods.
+The surprising point is that the value of two-particle transition strength, a indicator of pairing collective motions, depends on the requantization method significantly (See Chap.
+\ref{integrable} for the detailed discussion).
+After trial and error, eventually, we found a reasonable requantization method, stationary-phase approximation (SPA) to the path integral to describe the pairing collective motions. 
+Actually, SPA itself is available only for the integrable system.
+In order to apply SPA to the general non-integrable system, we constructed a new requantization theoretical framework, ASCC+SPA.
+This requantization method can describe the pairing dynamics properly.
+Moreover, ASCC+SPA supposed to be available for any collective motions based on TDMF theory.
+In this thesis, the keyword ``SPA'' emerges frequently.
+
+%Based on this method, we also constructed the theoretical framework for the general TDHFB dynamics.
+
+%Because pairing model is exact solvable model, we can the collective excited states from requantization compare with the exact solution. 
+%We hope that we can understand the pairing collective motion
+
+\section{Outline of this thesis}
+This thesis is organized as follows.
+Chap.
+\ref{chap2} is the preparation for the main discussion of the thesis.
+We show the pairing model in this chapter.
+Because pairing model is exact solvable model, we give the recipe for the exact solution in the former part.
+In the later part, we derive the TDHFB equation for the pairing Hamiltonian in explicit form.
+%The constant of motion, pairing rotation, is also
+
+The main achievements of our study are shown in Chap.
+\ref{integrable} and Chap.
+\ref{non-integrable}.
+Chap.
+\ref{integrable} discuss the pairing collective motions in integrable system (two-level system).
+We applied three different requantization methods, canonical quantization, Fourier decomposition, and SPA.
+The obtained excitation energies and wave functions from each method are compared with exact solution.
+Also, we discuss the validity of pairing gap parameter as a collective coordinate.
+Chap.
+\ref{non-integrable} discuss the pairing collective motions in non-integrable system.
+We introduce a new requantization method, ASCC+SPA, proposed by us.
+We explain the theoretical framework of ASCC+SPA in the former part, and discuss the result for pairing collective motions from ASCC+SPA in the later part.
+
+There are several remaining problems from our study.
+In Chap.
+\ref{discussion}, we point out these problems and give some possible approaches for them.
+Because SPA is the theory of great elegance, we also discuss the perspective for the large-amplitude dynamics by using SPA or beyond SPA.
+We conclude our study in Chap.
+\ref{conclusion}.
+
+%The detailed derivations
+
+\clearpage{\pagestyle{empty}\cleardoublepage}
 \chapter{Pairing model}
-
-To examine the pairing dynamics influencing the structure of nuclei, we can only concentrate the nucleons near the Fermi energy. The Hamiltonian of pairing model is
+\label{chap2}
+
+We introduce the pairing model in this chapter. The Hamiltonian of pairing model is
 \begin{align}
@@
 \end{align}
-The pairing rotational band created by the pairing correlation is completely parabolic with the moment of inertia $2/g$.
+The pairing rotational band created by the pairing correlation is completely parabolic with the pairing-rotational moment of inertia $2/g$.
 Also, the excited states in a specified $N$ is only described by the quantum number $\nu$.
 For example, the first excited state in even particle system is $\nu=2$ state, which correspond to one $J^{\pi}=0^+$ pair broken state.\par
-The profound dynamics occurs in multi-level pairing model ($L\ge 2$).
-The pairing rotational mode becomes complex due to the shell effect.
+The non-explicit dynamics arises in multi-level pairing model ($L\ge 2$).
+The pairing rotational mode includes higher order terms of $N$ due to the shell effect.
 In addition, several pairing vibrational modes emerge.
-The pairing vibration is not single particle motion specified by $\nu_l$, but a collective motion with the excitation of $J^{\pi}=0^+$ pairs.
-In this chapter, we explain the numerical exact solution and derive the TDHFB dynamics in multi-level pairing Hamiltonian.
+The pairing vibration is not single particle motion specified by $\nu_l$, but a collective motion arisen from $J^{\pi}=0^+$ pairs.
+In order to solve the multi-level pairing Hamiltonian, we explain the numerical exact solution.
+Also, we derive the TDHFB equation to study the mean-field picture of pairing collective motions.
 
@@
 \end{align}
-and $S_l^+, S_l^-$ are the same as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
+and $S_l^+, S_l^-$ as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
 \begin{align}
@@
 
-We discuss the physical meaning of the quasispin space.
+We consider the physical meaning of the quasispin space.
 Because $S_l^+$ and $S_l^-$ correspond to the creation and annihilation operators with respect to the $J^{\pi}=0^+$ pairs in each level, the quasispin space is decoupled from the space which the unpaired particles belong to.
@@
 However, diagonalization is time consuming when the model space becomes large.
-The calculation time is proportional to the cubes of the dimension of the model space For example, there are 16 single particle levels between the magic number 50 and 82 in deformed nuclei.
+The calculation time is proportional to the cubes of the dimension of the model space.
+For example, there are 16 single particle levels between the magic number 50 and 82 in deformed nuclei.
 Because the dimension for the system is $D=2^{16}=65536$, the calculation time in deformed system is $\sim 10^5$ times as much as the case in spherical system.
@@
 W.
-Richardson \cite{Richardson1, Richardson2, Richardson3}.
+Richardson \cite{Richardson1, Richardson2, Richardson3, Richardson4, Richardson5}.
 We divide the total energy into two parts
@@
 $E_{\alpha}$ can become not only real numbers, but also complex conjugate pairs when $M\ge 2$.
+
+We solved the non-linear equations numerically in general.
+If we input a set of initial values $E_{\alpha}^{0}$ into the equations, the values will converge by using proper numerical algorithm such as Newton-Raphson method.
+The difficult point is that we cannot directly specify the number of excitation from the obtained excitation energy because the converged excitation energy $\sum_{\alpha=1}^M E_{\alpha}$ can be any number of excitation.
+To specify the number of excitation, we can use the idea in Ref.
+\cite{Richardson4}, which discussed the behavior of the $E_{\alpha}$ as a function of $g$ for ground and each low-lying excitation energy.
+
+The eigenvalues can be also calculated numerically by using the obtained $E_{\alpha}$.
+Actually, we need to calculate the matrix elements for specific operators we interest (e.g.
+number operator, two-particle transition operator), without obtaining the explicit eigenvectors.
+For example, the occupation number can be obtained in the following non-linear equations
+\begin{align}
+n.
+\end{align}
+%However, the equation
 
@@
 The time-dependent mean-field theory
-To understand the classical picture of the pairing dynamics, time-dependent mean-field (TDMF) theory is useful tool. With pairing correlation, TDMF theory attributes to TDHFB theory.
+We apply time-dependent mean-field (TDMF) theory to examine the classical picture of the pairing dynamics. With pairing correlation, TDMF theory attributes to TDHFB theory.
 The TDHFB equation can be derived from the time-dependent variational principle,
@@
 The number of the TDHFB degrees of freedom is same as the number of the single-particle levels.
-However, because the Hamiltonian depends only on the relative difference in the gauge angles, the global gauge angle
-\begin{align}
-	\Phi = \frac{1}{L}\sum_l \chi_l
-\end{align}
-is a cyclic variable. With the definition for relative gauge angle (e.g. $\phi_l = \chi_l-\chi_1$), we can find that the conjugate momentum of $\Phi$ is the sum of $j_l$
-\begin{align}
-	J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} = \sum_l j_l .
-\end{align}
-From (\ref{occ}), $J$ is related to the total particle number
-\begin{align}
-	N = \nu + 2J .
-\end{align}
-The Hamilton's equation for $J$
-\begin{align}
-	\dot{J} = -\frac{\partial\mathcal{H}}{\partial \dot{\Phi}} = 0, \quad J = {\rm const}
-\end{align}
-indicates that the total particle number is conserved in time evolution.
+However, there is one constant of motion, pairing rotation.
+Using (\ref{occ}), the total particle number can be written in
+\begin{align}
+	N = \braket{Z|\hat{N}|Z} = \nu + 2J ,
+\end{align}
+where $J$ is defined in
+\begin{align}
+	J \equiv \sum_l j_l .
+\end{align}
+Because $\nu$ is nothing but quantum number, the total particle number can be specified by $J$.
+We can confirm that the total particle number is conserved by checking the Poisson Bracket
+\begin{align}
+	\{\mathcal{H},J\}_{PB} &= \sum_l \left(
+	\frac{\partial\mathcal{H}}{\partial\chi_l}\frac{\partial J}{\partial j_l}
+	- \frac{\partial\mathcal{H}}{\partial j_l}\frac{\partial J}{\partial \chi_l} \right) \nonumber \\
+	&= \sum_l \frac{\partial\mathcal{H}}{\partial\chi_l} \nonumber \\
+	&= \sum_l 2g \sum_{l'\neq l} \sqrt{j_{l}j_{l'}(\Omega_{l}-\nu_{l}-j_{l})(\Omega_{l'}-\nu_{l'}-j_{l'})}\sin{(\chi_{l}-\chi_{l'})} \nonumber \\
+	&= 0 .
+\end{align} 
+Actually, $J$ correspond to a conjugate momentum with respect to a global gauge angle $\Phi$.
+We note that $\Phi$ is not necessarily becoming $\Phi=\sum_l \chi_l/L$ because the explicit form of $\Phi$ depends on the coordinate transformation.
+In other words, the condition of total particle number conservation cannot determine the form of $\Phi$ uniquely.
+
 The canonical variable $(\Phi,J)$ describes the pairing rotation.
@@
 In multi-level system, the coupling constant $g$ and single-particle energy $\epsilon_l$ affects significantly to the last term in (\ref{Hamiltonian}).
-The parabolic structure can be broken when the shell effect is strong.
-
-In the analysis of TDHFB classical Hamiltonian, we can decouple the pairing rotational mode.
+The parabolic structure will be broken when the shell effect is strong.
+
+In order to analyze the time-dependent dynamics, we decouple the pairing rotational mode.
 The degrees of freedom is $L-1$ in $L$ level system.
-Therefore, the dynamics is integrable for $L=2$ and non-integrable for $L\le 3$ in multi-level pairing model.
+In multi-level pairing model, therefore, the dynamics is integrable for $L=2$ and non-integrable for $L\le 3$.
 We discuss the integrable system and non-integrable system in Chapter \ref{integrable} and \ref{non-integrable}, respectively.
 
+\clearpage{\pagestyle{empty}\cleardoublepage}
 \chapter{Requantization of TDHFB in integrable system}
 \label{integrable}
-As discussed in Sec. \ref{constant}, the TDHFB dynamics in two-level system is one-dimensional motion. We know that one-dimensional system must be integrable system. 
-There are two new discoveries obtained from the study of the integrable system.
-First, the requantization method, stationary phase approximation to the path integral, can be applied straightforward to describe the collective excited $0^+$ states.
+As discussed in Sec. \ref{constant}, there is only one time-dependent degree of freedom in two-level system. We know that one-dimensional system must be integrable system.
+We obtained two achievements from the study for the integrable system.
+First, the requantization method, stationary-phase approximation to the path integral, can be applied straightforward to describe the collective excited $0^+$ states.
 We find that SPA is superior to the other requantization methods, especially for the calculation of two-particle transition strength.
@@
 \subsection{TDHFB dynamics}
-To describe the one-dimensional motion, we introduce the global gauge angle $\Phi$ and the relative gauge angle $\phi$ as canonical coordinates
+To describe the one-dimensional time-dependent motion, pairing vibration, by an explicit coordinate, we introduce a global gauge angle $\Phi$ and a relative gauge angle $\phi$ as canonical coordinates
 \begin{align}
@@
 \begin{align}
-  j = \frac{\nu_{2}-\nu_{1}}{2} + \frac{n_{2}-n_{1}}{4}
-\end{align}
-The Lagrangian and Hamiltonian in terms of these canonical variables
+  j = \frac{\nu_{2}-\nu_{1}}{2} + \frac{n_{2}-n_{1}}{4} .
+\end{align}
+As discussed in \ref{constant}, we note that $\Phi \equiv c_1\chi_1 + c_2\chi_2, \ \phi\equiv \chi_2 - \chi_1 \ (c_1+c_2=1,\ 0<c_1,c_2<1)$ can decouple the pairing rotational mode.
+One of the choice, $c_1=c_2=1/2$ as in (\ref{phi}), is the simplest transformation.
+After the coordinate transformation, the Lagrangian and Hamiltonian in terms of these canonical variables
 $(\phi,j;\Phi,J)$ are given by
@@
 \end{eqnarray}
-Because $J$ and the total energy $E$ constants of motion, the TDHFB trajectories with given $J$ and $E$ are determined
+Because $J$ and the total energy $E$ are constants of motion, the TDHFB trajectories with given $J$ and $E$ are determined
 in the two-dimensional phase space $(\phi,j)$ with the condition
@@
 
-\subsection{Adiabatic TDHFB (ATDHFB) dynamics}
+\subsection{TDHFB dynamics in adiabatic\footnote{In this subsection, the word ``adiabatic'' means that the collective velocity is small.} limit}
 \label{ATDHFB}
-In general collective motion, the frequency in the collective motion is much smaller than the frequency in single particle motion ($\hbar\omega\ll\epsilon_m-\epsilon_i$).
-The slow velocity of the collective motion enable us to expand the collective Hamiltonian up to second order with respect to the collective momentum (adiabatic approximation).
+In general collective motion, the frequency of the collective motion is much smaller than the frequency in single particle motion ($\hbar\omega\ll\epsilon_m-\epsilon_i$).
+The slow velocity of the collective motion enable us to expand the TDHFB Hamiltonian up to second order with respect to the collective momentum.
 We discuss the behavior of TDHFB dynamics in adiabatic approximation.\par
 From (\ref{Hamiltonian2}), we find that the classical Hamiltonian is even function with respect to $\phi$.
-With time reversal $t\to-t$, (\ref{TDHFB_equation}) is invariant under $j\to j, \phi\to -\phi$, which indicates that $j$ is time even and $\phi$ is time odd.
+With time reversal $t\to-t$, (\ref{TDHFB_equation}) is invariant under $j\to j, \phi\to -\phi$, which indicates that $j$ is time-even and $\phi$ is time-odd.
 Thus, we switch the coordinate and momentum
@@
 \end{equation}
-to make the coordinate time even. The classical Hamiltonian under adiabatic approximation becomes
+to make the coordinate time-even. The classical Hamiltonian under adiabatic approximation becomes
 \begin{align}
@@
 It is obvious that $V(j)$ is potential and $B(j)$ is mass parameter.
-Because the closed trajectories appear around the energy minimum point $(\phi,j)=(0,j_0)$, we can expect that adiabatic approximation performs excellent for closed trajectories.
-\begin{figure}[htbp]
+We define a classical trajectory obtained from (\ref{ATDHFB_Hamiltonian}) as adiabatic TDHFB (ATDHFB) trajectory.
+Because the closed trajectories appear around the energy minimum point $(\phi,j)=(0,j_0)$, we expect that adiabatic approximation performs excellent for closed trajectories.
+\begin{figure}[tb]
  \begin{center}
@@
 The deviation becomes large at the high-energy region.
-In conclusion, ATDHFB is excellent approximation at low-energy region, regardless of the type of the trajectories.
+In conclusion, ATDHFB is excellent approximation at low-energy region for both open and closed trajectories.
 
 \section{Requantization methods}
-To obtain the excited states, quantization of the TDHFB trajectory, namely, requantization is necessary procedure.
+To obtain quantum states from TDHFB dynamics, quantization of the TDHFB trajectories, namely, requantization is necessary procedure.
+We emphasize that there are infinite quantum pictures corresponding to one classical picture.
+Different quantization methods lead different quantum states.
 The straightforward requantization method is canonical quantization, which is commonly applied into nuclear collective model.
-We expected canonical quantization gives reasonable result and we applied it at first.
-However, we find that canonical quantization has serious problem to describe the pairing dynamics.
-To solve or avoid the problem, alternative requantization methods, Fourier decomposition and stationary phase approximation to the path integral, are also introduced.
+Here, we apply the canonical quantization to describe the excited states.
+However, we find that canonical quantization has serious problems to describe the pairing dynamics.
+Such problems are discussed in Sec.
+\ref{3-3}.
+To solve or avoid the problems, alternative requantization methods, Fourier decomposition and stationary-phase approximation to the path integral, are also introduced.
 In this section, we explain each requantization method in detail, respectively.
@@
 \subsection{Stationary phase approximation to the path integral}
-At first, we introduce the idea of stationary phase approximation to the path integral (SPA). Starting an arbitrary state $\ket{\psi(0)}$ at time $t=0$,
+TDHFB trajectory corresponds to a stationary-phase limit of the path integral formulation.
+The idea for constructing excited states from TDHFB trajectories based on the path integral formulation was proposed in Ref.
+\cite{Neg82,L80,LNP80,KS80,K81,Rei80}.
+It recovers quantum fluctuations missing in the mean-field
+level, and possibly enables us to describe large-amplitude collective
+tunneling phenomena.
+%such as spontaneous fission \cite{Neg82}.
+The requantization of the TDHFB is particularly feasible
+for integrable systems, because the system is described by separable
+action-angle variables $(I_k, \phi_k)$, leading to
+the Einstein-Brillouin-Keller (EBK) quantization condition.
+However, for nonintegrable systems in general, it is difficult to find
+suitable periodic orbits to quantize.
+A possible solution to this difficulty is to find a decoupled collective
+subspace spanned by
+a single coordinate and its conjugate momentum \cite{NMMY16}.
+Since the one-dimensional system is integrable, the quantization is
+practicable.
+
+Here, we formulate the stationary-phase approximation to the path integral (SPA). 
+Starting an arbitrary state $\ket{\psi(0)}$ at time $t=0$,
 the time-dependent full quantum state can be written in the path integral form
@@
 \label{sec:canonical}
-In the pairing collective model, the canonical quantization
-was adopted in previous studies \cite{BBPK70,delta1,delta3}.
+In the pairing collective model, the canonical quantization with Pauli's prescription
+was adopted in previous studies \cite{BBPK70,GPBW85, ZPPRS99, P07}.
 Assuming magnitude and phase of the pairing gap as collective coordinates,
@@
 In this section, we apply similar quantization method to
-the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
+the TDHFB Hamiltonian (\ref{Hamiltonian2}).
 The main difference is that the collective canonical variables are
@@
 is not limited to the second order in momenta.
+%We need to keep the Hamiltonian Hermitian after 
 In the present study, 
@@
 \section{Result}
+\label{3-3}
 In this section, we study the seniority-zero states ($\nu_1=\nu_2=0$) in
@@
 
-\section{Collective model treatment} 
+\clearpage{\pagestyle{empty}\cleardoublepage}
+\chapter{Requantization of TDHFB in non-integrable system}
+\label{non-integrable}
+
+\section{Theoretical framework of ASCC+SPA in non-integrable system}
+\subsection{Adiabatic self-consistent collective coordinate method and
+1D collective subspace}
+\label{sec:ASCC}
+%To discuss the application of ASCC+SPA in the later subsection, 
+In this section,
+we first recapitulate the ASCC method to find a 1D collective coordinate,
+following the notation of Ref. \cite{N2012}.
+
+As is seen in Sec.~\ref{sec3}, the TDHFB equations can be
+interpreted as the classical Hamilton's equations of motion
+%The classical Hamilton's equation which is identical to the TDHFB equation is described by
+with canonical variables $\{\xi^{\alpha},\pi_{\alpha}\}$. 
+Each point in the phase space $(\xi^{\alpha},\pi_{\alpha})$
+corresponds to a generalized Slater determinant (coherent state).
+Assuming slow collective motion,
+we expand the Hamiltonian $\mathcal{H}(\xi,\pi)$ with respect to
+the momenta $\pi$ up to second order.
+The TDHFB Hamiltonian is written as
+\begin{align}
+ \mathcal{H} &= V(\xi) + \frac{1}{2}B^{\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}
+\end{align}
+with the potential $V(\xi)$ and
+the reciprocal mass parameter $B^{\alpha\beta}(\xi)$ defined by
+\begin{align}
+  V(\xi) &= \mathcal{H}(\xi,\pi=0) , \\
+  B^{\alpha\beta}(\xi) &= \left. \frac{\partial^2\mathcal{H}(\xi,\pi)}{\partial\pi_{\alpha}\partial\pi_{\beta}} \right|_{\pi=0}.
+\end{align}
+
+For multi-level pairing models in Sec.~\ref{sec3}, 
+there is a constant of motion in the TDHFB dynamics,
+namely the average particle number $q^n\equiv \langle \hat{N} \rangle/2$.
+Since the particle number $\hat{N}$ is time-even Hermitian operator, we treat
+this as a coordinate, and its conjugate gauge angle, $p_n$,
+as a momentum.
+Since $q^n$ is a constant of motion, the Hamiltonian does not
+depend on $p_n$.
+On the other hand, the gauge angle $p_n$ changes in time,
+which corresponds to the pair rotation, a Nambu-Goldstone (NG) mode
+associated with the breaking of the gauge (particle-number) symmetry.
+We assume the existence of 2D collective subspace $\Sigma_2$
+(4D phase space),
+described by a set of canonical variable $(q^1,q^2=q^n;p_1,p_2=p_n)$,
+which is well decoupled from the rest of degrees of freedom,
+$\{q^a,p_a\}$ with $a=3,\cdots$.
+The collective Hamiltonian is given by imposing $q^a=p_a=0$,
+namely by restricting the space into the collective subspace
+\begin{equation}
+%\mathcal{H}_{\rm coll}(q,p) &= \bar{V}(q) + \frac{1}{2}\bar{B}^{-1}(q)p^2 .
+\mathcal{H}_{\rm coll}(q,p;q^n)
+= \bar{V}(q^1,q^n) + \frac{1}{2}\bar{B}^{11}(q^1,q^n)p_1^2 .
+  \label{coll}
+\end{equation}
+Since there exist two conserved quantities, $q^n$ and $\mathcal{H}_{\rm coll}$,
+this 2D system is integrable.
+We can treat the collective motion of $(q^1,p_1)$ separately from
+the pair rotation $(q^n, p_n)$.
+
+In the collective Hamiltonian (\ref{coll}), the variable $q^n$ is
+trivially given as the particle number, which is expanded up to
+second order in the momenta $\pi$,
+\begin{equation}
+q^n=\frac{\langle \hat{N} \rangle}{2} = f^n(\xi)
+	+\frac{1}{2}f^{(1)n\alpha\beta}\pi_\alpha\pi_\beta .
+	\label{q^n}
+\end{equation}
+To obtain the non-trivial collective variables
+$(q^1,p_1)$, we assume the point transformation\footnote{
+We may lift the restriction to the point transformation,
+as Eq. (\ref{q^n}) \cite{Sat18}.
+In this paper, we neglect these higher-order terms, such as
+$f^{(1)1\alpha\beta}\pi_\alpha\pi_\beta/2$.
+},
+\begin{equation}
+%  q = q^1 &= f^1(\xi) + \frac{1}{2}f^{(1)1\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}  \label{point}\\
+  q^1 = f^1(\xi) \label{point} ,
+% \xi^{\alpha} &= g^{\alpha}(q) + \frac{1}{2}g^{(1)\alpha 1 1}(\xi)p_{1}p_{1}
+\end{equation}
+and $\xi^\alpha$ on the subspace $\Sigma_2$ is given as
+$\xi^{\alpha} = g^{\alpha}(q^1,q^n,q^a=0)$.
+The momenta on $\Sigma_2$ are transformed as
+\begin{align}
+p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha,
+	\label{coll_momenta}\\
+\pi_{\alpha} &= f^1_{,\alpha}p_1 +f^n_{,\alpha}p_n,
+ \label{momenta}
+\end{align}
+where the comma indicates the partial derivative
+$(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
+The Einstein's convention for summation with respect to the repeated
+upper and lower indices is assumed hereafter.
+The canonical variable condition leads to
+\begin{align}
+ %f^1_{,\alpha}g_{,1}^{\beta} = \delta^{\beta}_{\alpha}, \quad 
+f^i_{,\alpha}g_{,j}^{\alpha} = \delta^i_j,
+  \label{canonicity}
+\end{align}
+where $i,j=1$ and $n$.
+The collective potential $\bar{V}(q^1,q^n)$ and
+the collective mass parameter
+$\bar{B}_{11}(q^1,q^n)=[\bar{B}^{11}(q^1,q^n)]^{-1}$ can be given by
+\begin{align}
+\bar{V}(q^1,q^n) &= V(\xi=g(q^1,q^n,q^a=0)), \\
+\bar{B}^{11}(q^1,q^n) &= f^1_{,\alpha}\tilde{B}^{\alpha\beta}(\xi)f^1_{,\beta} ,
+  \label{coll_mass}
+\end{align}
+where $\tilde{B}^{\alpha\beta}$ are defined as
+\begin{align}
+ \tilde{B}^{\alpha\beta}(\xi)
+%&= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
+&= B^{\alpha\beta}(\xi) - \bar{V}_{,n} f^{(1)n\alpha\beta}(\xi)
+%- \lambda_1 f^{(1)1\alpha\beta}(\xi) 
+\label{tildeB}.
+\end{align}
+
+%Before showing the ASCC basic equations, we consider the constants of motion in TDHFB dynamics.
+Since nuclei is self-bound systems without external potential, the ground state obtained from mean-field theory violates the symmetry (e.g.
+deformation, pairing).
+In such system, the constants of motion corresponding the Nambu-Goldstone (NG) mode emerges in TDHFB dynamics.
+Therefore, we are mostly interested in the systems with collective motion separated from NG mode.\par
+%We know that the most of conserved quantities, such as total angular momentum $J$ and total particle number $N$, are not only expressed by one-body Hermitian operators, but also has real matrix elements in the quasi-particle basis.
+Such classical variable $\mathcal{P}$ corresponding to the conserved quantity can be expanded as
+%\begin{align}
+%  \mathcal{P}(\xi,\pi) = f^I(\xi) + \frac{1}{2}f^{(1)I\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta} . \label{P}
+%\end{align}
+%The index $I$ indicates the degree of freedom for NG mode. Since the conserved quantity must fulfill $\{\mathcal{P},\mathcal{H}\}_{PB}=0$, it leads
+%\begin{align}
+%  f^{I}_{,\alpha}B^{\alpha\beta} - f^{(1)I\alpha\beta}V_{,\alpha} = 0.
+%  \label{P_PB}
+%\end{align}
+
+Decoupling conditions for the collective subspace $\Sigma_2$ lead to
+the basic equations of the ASCC method \cite{MNM00,N2012},
+which determine tangential vectors,
+$f^1_{,\alpha}(\xi)$ and $g_{,1}^{\alpha}(q)$.
+\begin{align}
+  \delta H_M(\xi,\pi) = 0, \label{mfHFB}
+  \end{align}\begin{align}
+%  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
+%  \tilde{B}^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
+ \mathcal{M}^\beta_\alpha f^1_{,\beta}  = \omega^2 f^1_{,\alpha},\hspace{2em} 
+\mathcal{M}^\beta_\alpha g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1} .
+  \label{mfQRPA}
+\end{align}
+The first equation (\ref{mfHFB}) is called moving-frame
+Hartree-Fock-Bogoliubov (HFB) equation.
+The moving-frame Hamiltonian $\mathcal{H}_M$
+%with constraints on collective coordinate and constant of motion
+is
+\begin{align}
+\mathcal{H}_M(\xi,\pi) &= \mathcal{H}(\xi,\pi)
+	-\lambda_{1} q^1(\xi) - \lambda_{n} q^n(\xi,\pi) .
+\label{H_M}
+\end{align}
+The second equation (\ref{mfQRPA}) is called moving-frame QRPA equation.
+%$\tilde{B}^{\alpha\beta}$ is the modified mass parameter
+%\begin{align}
+% \tilde{B}^{\alpha\beta}(\xi) &= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
+%&= B^{\alpha\beta}(\xi) - \bar{V}_{,n} f^{(1)n\alpha\beta}(\xi)
+%- \lambda_1 f^{(1)1\alpha\beta}(\xi) 
+%\label{tildeB}.
+%\end{align} 
+%and the covariant derivative $V_{;\gamma\alpha}$ is defined by
+%\begin{align}
+% V_{;\alpha\beta} = V_{,\alpha\beta} - \Gamma^{\gamma}_{\alpha\beta}V_{,\gamma} , \label{covariant}
+%\end{align}
+%where the affine connection is
+%\begin{equation}
+%\Gamma^{\alpha}_{\beta\gamma}=\frac{1}{2}B^{\alpha\delta}(B_{\delta\beta,\gamma}+B_{\delta\gamma,\beta}-B_{\beta\gamma,\delta}).
+%\end{equation}
+%If we assume that the collective coordinate $q$ is geodesic, 
+The matrix $\mathcal{M}^\beta_\alpha$ in the moving-frame QRPA
+equation (\ref{mfQRPA}) can be rewritten as 
+ \begin{align}
+\mathcal{M}^{\beta}_{\alpha} =
+	 \tilde{B}^{\beta\gamma}
+	 \left(V_{,\gamma\alpha}-\lambda_{n}f^n_{,\gamma\alpha}\right)
+	+ \frac{1}{2}\tilde{B}^{\beta\gamma}_{,\alpha}V_{,\gamma} 
+\label{M}.
+\end{align}
+The NG mode, $f^n_{,\alpha}$ and $g^\alpha_{,n}$, corresponds to
+the zero mode with $\omega^2=0$.
+Therefore, the collective mode of our interest corresponds to
+the mode with the lowest frequency squared except for the zero mode.
+
+%We discuss the practical solution to derive the one-dimensional collective coordinate.
+We neglect $f^{(1)1\alpha\beta}(\xi)$ because it is supposed to be negligibly small in the previous study.
+On the other hand, from (\ref{P_PB}) and (\ref{mfQRPA}), $f^{(1)I\alpha\beta}(\xi)$ is necessary information to promise $\tilde{B}^{\beta\gamma}V_{;\gamma\alpha}f^I_{,\beta}=0$, which means zero mode.
+In most of case, we know the explicit form of $\mathcal{P}(\xi,\pi)$.
+In practice, we obtain the collective path according to the following procedure:
+\begin{enumerate}
+\item Find the HFB minimum point $\xi^\alpha_i$ ($i=0$)
+	by solving Eq. (\ref{mfHFB}) with $\lambda_1=0$.
+	Let us assume that this corresponds to $q^1_i=0$.
+\item \label{step-2}
+	Diagonalize the matrix $\mathcal{M}^{\beta}_{\alpha}$
+to solve Eq.~(\ref{mfQRPA}) using Eq.~(\ref{M}).
+%Then, choose a mode with the lowest frequency $\omega^2$
+%as $f^1_{,\alpha}$ and $g^\alpha_{,1}$.
+%\footnote{
+%When eigenvalues cross on the collective path, the choice of adiabatic path or diabatic path is a critical problem}. 
+\item \label{step-3}
+%The right eigenvector $g^{\alpha}_{,1}$ tell us the direction which system moves in energy surface. 
+Move to the next neighboring point
+$\xi^\alpha_{i+1}=\xi^\alpha_{i}+d\xi^\alpha$
+with $d\xi^{\alpha}=g^{\alpha}_{,1}dq^1$.
+This corresponds to the collective coordinate, $q^1_{i+1}=q^1_i+dq^1$.
+\item \label{step-4}
+At $\xi_{i+1}^\alpha$ $(q^1_{i+1})$,
+obtain a self-consistent solution of
+Eqs. (\ref{mfHFB}) and (\ref{mfQRPA})
+to determine
+$\xi^\alpha_{i+1}$, $f^1_{,\alpha}$, and $g^\alpha_{,1}$.
+\item Go back to Step \ref{step-3} to determine the next point
+on the collective path.
+%\item Iterate (2)$\sim$(5) to decide the collective path under the same direction in the energy surface. 
+%\item Implement (2)$\sim$(6) for the opposite direction of the collective path in energy surface. 
+\end{enumerate}
+We repeat this procedure with $dq^1 > 0$ and $dq^1<0$, and
+construct the collective path.
+In Steps~\ref{step-2} and \ref{step-4}, we choose a mode
+with the lowest frequency squared $\omega^2$.
+Note that $\omega^2$ can be negative.
+In Step \ref{step-4}, when we solve Eq.~(\ref{mfHFB}), we use
+a constraint on the magnitude of $dq^1=f^1_{,\alpha}d\xi^{\alpha}$.
+Since the normalization of $f^1_{,\alpha}$ and $g^\alpha_{,1}$ is
+arbitrary as far as they satisfy Eq. (\ref{canonicity}),
+we fix this scale by an additional condition of $\bar{B}^{11}(q^1)=1$.
+
+%The scale of the collective coordinate is not unique because of the uncertainty of the eigenvectors in (\ref{mfQRPA}).
+To unify the scale, the simplest procedure is to keep the collective mass parameter $\bar{B}^{-1}(q)=1$ by renormalizing eigenvectors in (\ref{coll_mass}).
+
+\subsection{Stationary-phase approximation to path integral}
+\label{sec:SPA}
+
+For quantization of integrable systems,
+we can apply the stationary-phase approximation (SPA)
+to the path integral.
+In our former study \cite{NN18},
+we have proposed and tested the SPA for an integrable pairing model.
+Since the collective Hamiltonian (\ref{coll}) that is
+extracted from the TDHFB degrees of freedom is integrable,
+the SPA is applicable to it.
+In this manner, we may apply the ASCC+SPA to
+non-integrable systems in general.
+
+\subsubsection{Basic idea of ASCC+SPA}
+
+Because the Hamiltonian $\mathcal{H}_{\rm coll}$ of Eq.~(\ref{coll})
+is separable,
+it is easy to find periodic trajectories on invariant tori.
+Since the pair rotation corresponds to the motion of $p_n$
+with a constant $q^n$,
+all we need to do is to find classical periodic trajectories $C_k$ in
+the $(q^1,p_1)$ space (with a fixed $q^n$) which satisfy
+the Einstein-Brillouin-Keller (EBK) quantization rule
+with a unit of $\hbar=1$,
+\begin{equation}
+	\oint_{C_k} p_1dq^1 = 2\pi k ,
+	\label{EBK}
+\end{equation}
+where $k$ is an integer number.
+
+At each point in the space $(q^1,q^n; p_1,p_n)$ corresponds to
+a generalized Slater determinant
+$\ket{q^1,q^n;p_1,p_n}=\ket{\xi,\pi}$
+where $(\xi,\pi)$ are given as
+$\xi^\alpha=g^\alpha(q^1,q^n,q^a=0)$ and
+$\pi_\alpha=f^1_{,\alpha}p_1+f^n_{,\alpha}p_n$.
+According to the SPA, the $k$-th excited state $\ket{\psi_k}$
+is constructed from the $k$-th periodic trajectory $C_k$,
+given by $(q^1(t),p_1(t))$,
+of the Hamiltonian $\mathcal{H}_{\rm coll}$.
+\begin{equation}
+%\ket{\psi_k} = \oint_{C_k} d\mu(q,p) \ket{q,p}
+\ket{\psi_k} \propto \oint dp_n \oint_{C_k} \rho(q,p) dt \ket{q,p}
+	e^{i\mathcal{T}[q,p]} ,
+	\label{SPA}
+\end{equation}
+where $(q,p)$ means $(q^1,q^n;p_1, p_n)$, and the weight function
+$\rho(q,p)$ is given through an invariant measure $d\mu(q,p)$ as
+\begin{equation}
+d\mu(q,p)=\rho(q,p) dE dt dq^n dp_n .
+\end{equation}
+The invariant measure $d\mu(q,p)$ is defined by the unity condition
+$\int d\mu(q,p) \ket{q,p}\bra{q,p} = 1$.
+An explicit form of $d\mu(q,p)$ for the present pairing model is shown
+in Eq. (\ref{dmu}).
+The action integral $\mathcal{T}$ is defined by
+\begin{align}
+\mathcal{T}[q,p] &\equiv
+\int_{0}^{t} \braket{q(t'),p(t')| i\frac{\partial}{\partial t'}
+	|q(t'),p(t')} dt' .
+\label{tau}
+\end{align}
+
+The SPA quantization is able to provide a wave function $\ket{\psi_k}$
+in microscopic degrees of freedom, which is given as a superposition
+of generalized Slater determinants $\ket{q,p}$.
+In addition, the integration with respect to $p_n$ over a circuit on a torus
+automatically recovers the broken symmetry, namely the good particle number.
+However, it relies on the existence of invariant tori.
+In the present approach of the ASCC+SPA,
+we first derive a decoupled collective subspace $\Sigma_2$ and identify
+canonical variables $(q,p)$.
+Because of the cyclic nature of $(q^n,p_n)$, it is basically a 1D system
+and becomes integrable.
+In other words, we perform the torus quantization on
+approximate tori in the TDHFB phase space $(\xi,\pi)$,
+which is mapped from tori in the 2D collective subspace $(q,p)$.
+
+%\begin{figure}[tb]
+% \begin{center}
+%    \includegraphics[width=80mm, bb=0 0 550 180]{SPA.png}
+% \end{center}
+%  \caption{For a TDHFB trajectory, the correspondence between TDHFB phase space and collective subspace.}
+%  \label{fig:correspondence}
+%\end{figure}
+%We try to combine SPA with ASCC.
+The key point is to find the correspondence between TDHFB phase space and collective subspace in a TDHFB trajectory (See Fig.
+\ref{fig:correspondence}).
+We consider the time-dependent state vector $\ket{Z(t)}$ is in a collective subspace.
+With pairing correlation, $\ket{Z(t)}$ can be expressed as
+
+\subsubsection{Notation and practical procedure for quantization}
+\label{sec:notation}
+
+For the application of the ASCC+SPA method to the pairing model in Sec.~\ref{sec3},
+we summarize some notations and procedures to obtain quantized states.
+
+In Sec.~\ref{sec3}, the time-dependent generalized Slater determinants
+(coherent states) are written as $\ket{Z}$ with complex variables
+$Z_\alpha(t)$.
+The variables $Z_\alpha$ are transformed into real variables
+$(j^\alpha, -\chi_\alpha)$ that correspond to $(\xi^\alpha,\pi_\alpha)$
+in Sec.~\ref{sec2}.
+$\chi_\alpha$ and $j^\alpha$ correspond to
+the ``angle'' and the ``number'' variables, respectively.
+%Although it is customary to take the angle as a coordinate,
+%since the angle $\chi_\alpha$ is time-odd quantities, 
+%we switch the coordinates and the momenta with minus signs
+%in front of variables $\chi$.
+Although it is customary to take the time-odd angle $\chi_\alpha$ as a coordinate,
+we take the number $j^\alpha$ as a coordinate and the angle $-\chi_\alpha$ as a momentum with an additional minus sign.
+Similarly, the gauge angle $\Phi$ and the total particle number $J$
+correspond to variables of the pair rotation, $-p_n$ and $q^n$, respectively.
+According to the EBK quantization rule (\ref{EBK}),
+the ground state with $k=0$ corresponds to nothing but the HFB state
+with a fixed particle number $J(=q^n)$.
+For the $k$-th excited states, we perform the following calculations:
+\begin{enumerate}
+\item Obtain the 1D collective subspace with canonical variables $(q^1,p_1)$
+	according to the ASCC in Sec.~\ref{sec:ASCC}.
+\item Find a trajectory $(q^1(t),p_1(t))$ which satisfies
+the $k$-th EBK quantization condition (\ref{EBK}).
+\item Calculate the action integral (\ref{tau}) for the $k$-th trajectory.
+\item Construct the $k$-th excited state using Eq.~(\ref{SPA}).
+\end{enumerate}
+The ASCC provides the 2D collective subspace $(q^1,J)$
+and the generalized coherent states $\ket{\Phi=0,J;q,p=0}$.
+For finite values of momenta, we use Eq.~(\ref{momenta})
+to obtain the state $\ket{\Phi,J;q,p}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Application of ASCC+SPA in pairing model}
+
+\subsection{Application of ASCC}
+
+%In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec. \ref{ASCC}. 
+We construct a 2D collective subspace $\Sigma_2$ from the ASCC method.
+%Because the first order with respect to $\chi_{\alpha}$ is zero in TDHFB Hamiltonian, we assume $j^{\alpha}$ as coordinates and $\chi_{\alpha}$ as conjugate momenta.
+The canonical variables are $(j^{\alpha},-\chi_{\alpha})$ and fulfill $\{j^{\alpha},-\chi_{\beta}\}_{PB}=\delta^{\alpha}_{\beta}$.
+We expand the classical Hamiltonian up to second order with respect to
+the momenta, $-\chi_{\alpha}$
+\begin{align}
+  \mathcal{H}(j,\chi) \approx& V(j) + \frac{1}{2}B^{\alpha\beta}(j)\chi_{\alpha}\chi_{\beta},
+\end{align}
+where the potential $V(j)$ and the reciprocal mass parameter
+$B^{\alpha\beta}(j)$ are given as
+\begin{align}
+  V(j) =& \mathcal{H}(j,\chi=0) \nonumber \\
+	=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left[ \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right] \nonumber \\
+  &- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}, 	
+\end{align}
+%\begin{align}
+\begin{eqnarray}
+&&B^{\alpha\beta}(j) = \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \\
+\label{mass}
+&&=
+	\begin{cases}
+2g\sum_{\gamma\ne \alpha} \sqrt{j^{\gamma}j^{\alpha}(\Omega_{\gamma}-j^{\gamma})(\Omega_{\alpha}-j^{\alpha})}
+		& \text{for $\alpha=\beta$} \\
+-2g\sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}
+		& \text{for $\alpha\ne\beta$}
+	\end{cases}. \nonumber
+\end{eqnarray}
+%\end{align}
+We may apply the ASCC method in Sec. \ref{sec:ASCC}
+by regarding $\xi\to j$ and $\pi\to-\chi$.
+
+The TDHFB conserves the average total particle number $N$.
+We adopt 
+\begin{equation}
+	J\equiv N/2=\sum_\alpha j^\alpha, 
+  \label{J}
+\end{equation}
+as a coordinate $q^n$.
+Since this is explicitly given as the expectation value of the particle-number
+operator, curvature quantities,
+such as $f^n_{,\alpha\beta}$ and $f^{(1)n\alpha\beta}$,
+are explicitly calculable.
+On the other hand, the gauge angle $\Phi=-p_n$ is not given a priori.
+Since the ASCC solution provides $g^\alpha_{,n}$ as an eigenvector of
+Eq. (\ref{mfQRPA}),
+we may construct it as Eq. (\ref{coll_momenta}) in the first order
+in $\pi=-\chi$.
+We confirm that the pair rotation corresponds to an eigenvector
+of Eq. (\ref{mfQRPA}) with the zero frequency $\omega^2=0$.
+
+%With the properties of the constant of motion, we discuss the practical solution of ASCC in pairing model.
+If we ignore the higher order term $f^{(1)1\alpha\beta}$, we can practice local harmonic equation (LHE)
+%\begin{align}
+%  B^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
+%  B^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1},
+%  \label{LHE}
+%\end{align}
+%which simplifies the moving-frame QRPA equation (\ref{mfQRPA}) by replacing $\tilde{B}^{\beta\gamma}$ into $B^{\beta\gamma}$. Under (\ref{LHE}),
+
+In the present pairing model, 
+from Eq. (\ref{J}), we find $J$ does not depend on $\chi$.
+This means $f^{(1)n\alpha\beta}=0$ in Eq. (\ref{q^n}),
+thus, $\tilde{B}^{\alpha\beta}=B^{\alpha\beta}$.
+The second derivative of $J$ with respect to $j$ also vanishes,
+which indicates $f^n_{,\gamma\alpha}$ in Eq.~(\ref{M}) is zero. 
+%It indicates the chemical potential $\lambda_I(q)$ is not necessary information to calculate the matrix element in moving-frame QRPA equation.
+The gauge angle $\Phi$ is locally determined
+by the solution of Eq. (\ref{mfQRPA}).
+\begin{align}
+%  \Phi = \frac{1}{L}\sum_{\alpha} \chi_{\alpha},
+\Phi = g^\alpha_{,n} \chi_{\alpha},
+  \label{total_gauge}
+\end{align}
+%where $L$ is the number of available shells $\alpha=1,\cdots,L$.
+%Its conjugate variable
+%${\partial\mathcal{L}}/{\partial\dot{\Phi}}$
+%is indeed given by $J$ of Eq. (\ref{J}).
+%Again, exchanging coordinate and momentum,
+%we have $q^n=J$ and $p_n=-\Phi$.
+
+%We consider the treatment for the constant of motion in pairing model. In the TDHFB Hamiltonian, there is no dependence about the total gauge angle
+%\begin{align}
+%  J \equiv \frac{\partial\mathcal{L}}{\partial\dot{\Phi}}=\sum_{\alpha} j^{\alpha} = \frac{N}{2}
+%\end{align}
+%is conserved quantity.
+
+%%%%%% Gauge fixing %%%%%%
+It should be noted \cite{N2012} that the definition of the collective
+variables $(q^1,p_1)$ is not unique, because it can be arbitrarily mixed
+with the pair rotation $(q^n,p_n)$ as
+\begin{equation}
+	q^1 \rightarrow q^1 + c q^n,  \quad
+	p_n \rightarrow p_n -c p_1 \label{eq:pairrotmix}
+\end{equation}
+with an arbitrary constant $c$.
+Numerically, this arbitrariness sometimes leads to a problematic behavior 
+in iterative procedure of the ASCC.
+In order to fix the parameter $c$, we adopt a condition
+called ``ETOP'' in Ref.~\cite{HNMM07}.
+We require the following condition to determine $c$:
+\begin{align}
+\sum_\alpha 
+	f^1_{,\alpha} = 0 ,
+\end{align}
+where $f^1_{,\alpha}$ is replaced as
+\begin{align}
+{f}^1_{,\alpha} \to f^1_{,\alpha} + c f^n_{,\alpha}
+  \label{f}
+\end{align}
+with Eq. (\ref{eq:pairrotmix}).
+%after solving (\ref{LHE}) at each point of $q$.
+
+\subsection{Application of SPA}
+
+After deriving the collective subspace $\Sigma_2$, 
+we perform the quantization according to the SPA in Sec.~\ref{sec:SPA}.
+Calculating a trajectory in the $(q^1,p_1)$ space,
+we can identify a series of states $\{\ket{\Phi,J;q^1(t),p_1(t)}\}$
+on the trajectory,
+in the form of Eq. (\ref{coherent})
+with parameters $Z_\alpha$ given at $(\Phi,J,q^1,p_1)$ and $q^a=p_a=0$ for
+$a\geq 3$.
+%Due to $J$ is conserved quantity, the action integral can be divided into two terms
+Since the variables $(\Phi,J)$ and $(q^1,p_1)$ are separable,
+we may take closed trajectories independently in $(\Phi,J)$ and $(q^1,p_1)$
+sectors, which we denote here as $C_\Phi$ and $C_1$, respectively.
+The action integral is given by
+\begin{align}
+\mathcal{T}(\Phi,J;q^1,p_1)
+&= \int_{C_\Phi} \braket{\Phi(t),J;q^1,p_1|i\frac{\partial}{\partial t}|\Phi(t),J;q^1,p_1} dt \nonumber \\
++ \int_{C_1} &\braket{\Phi,J;q^1(t),p_1(t)|i\frac{\partial}{\partial t}|\Phi,J;q^1(t),p_1(t)} dt
+ \nonumber \\
+	&=J\Phi + \int_{C_1} \sum_\alpha j^\alpha d\chi_\alpha
+	\nonumber \\
+	&\equiv \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
+%	\label{tau}
+\end{align}
+In fact, the gauge-angle dependence is formally given as
+\begin{equation}
+  \ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1},
+\end{equation}
+where $\hat{N}=\sum_\alpha \hat{n}_\alpha$.
+Then, the action for the trajectory $C_1$ can be also expressed as
+$\mathcal{T}(q^1,p_1;J)=
+ \int_{C_1} \braket{J;q^1,p_1|i\frac{\partial}{\partial t}|J;q^1,p_1} dt$.
+%\begin{align}
+%  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
+%\end{align}
+%%where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
+%The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.
+
+In the SU(2) representation, the invariant measure is
+\begin{align}
+  d\mu(Z) &= \prod_\alpha \frac{\Omega_\alpha+1}{\pi} (1+|Z_\alpha|^2)^{-2} d({\rm Re}\,Z) d({\rm Im}\,Z) \nonumber \\
+=& \prod_\alpha \frac{-(\Omega_\alpha+1)}{4\pi} d(\cos{\theta_\alpha}) d\chi_\alpha \nonumber \\
+ =& \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} d\chi_\alpha dj^\alpha \nonumber \\
+ =& \left[ \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} \right] d\Phi dJ dq^1 dp_1 %\nonumber \\
+  \prod_a dq^a dp_a,
+% d\Phi dJ dq dp = d\Phi dJ dE dt 
+	\label{dmu}
+\end{align}
+where $(q^a,p_a)$ are the intrinsic canonical variables
+decoupled from the collective subspace $\Sigma_2$.
+In the last line in Eq. (\ref{dmu}),
+we used the invariance of the phase-space volume element
+in the canonical transformation.
+%The part of the invariant measure which contributes to the excited states is
+According to Eq. (\ref{dmu}),
+the weight function $\rho(q,p)$ in Eq. (\ref{SPA}) is just a constant,
+thus, treated as the normalization of the wave function.
+%\begin{align}
+%d\mu(\Phi,J;q,p) \propto d\Phi dJ dqdp = d\Phi dJ dE dt. 
+%\end{align}
+%Under EBK quantization condition (\ref{EBK}),
+
+%derive the explicit form of excited states in (\ref{SPA}). From (\ref{GCS}) and (\ref{J}), the state vector $\ket{\Phi,J;q,p}$ becomes
+%\begin{align}
+%  \ket{\Phi,J;q,p} &= \sum_{\{j_l\}} e^{-i\Phi \sum_l j_l} \ket{J;q,p} .
+%\end{align}
+The coherent state $\ket{\Phi,J;q^1,p_1}=\ket{Z}$ is
+expanded in the SU(2) quasispin basis as
+\begin{align}
+\ket{Z} &= 
+\sum_{\{m_\alpha\}} A_m(Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots}, \nonumber\\
+\end{align}
+where the summation is taken over all possible combinations
+of integer values of $\{ m_\alpha\}$ with
+\begin{align}
+A_m(Z) =& \prod_\alpha 
+\frac{Z_\alpha^{m_\alpha}}
+	{\left(1+|Z_\alpha|^2\right)^{\Omega_\alpha/2}m_\alpha!}
+\sqrt{\frac{\Omega_\alpha! m_\alpha!}{(\Omega_\alpha-m_\alpha)!}} \nonumber\\
+ =& \prod_\alpha \left(\frac{1-\cos{\theta}_\alpha}{2}\right)^{m_\alpha/2}\left(\frac{1+\cos{\theta}_\alpha}{2}\right)^{(\Omega_\alpha-m_\alpha)/2}
+  \nonumber \\
+  &\times\sqrt{\frac{\Omega_\alpha!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
+	\label{A_m}
+\end{align}
+where the lower index $m$ indicates a combination of $\{ m_\alpha \}$.
+The integer number $m_\alpha$ corresponds to the number of pairs
+in the level $\alpha$.
+%is in fixed gauge angle ($\Phi=0$).
+%
+
+Using Eq.~(\ref{A_m}),
+the $k$-th excited state is calculated as
+\begin{align}
+\ket{\psi_k} \propto& \oint_{C_\Phi} d\Phi \oint_{C_1} dt
+\ket{\Phi,J;q^1,p_1} e^{i\mathcal{T}(\Phi,J;q^1,p_1)}
+ \nonumber \\
+	=& \sum_{\{m_\alpha\}}
+	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \nonumber \\
+&\times \oint dt e^{i\mathcal{T}_1}(t) B_m (Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots} \nonumber \\
+ \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
+ \label{SPA2}
+\end{align}
+where $B_m(Z)$ are identical to $A_m$ in Eq.~(\ref{A_m}) except for
+replacing $\chi_\alpha$ with the relative angles
+$\phi_\alpha\equiv\chi_\alpha-\Phi$.
+The coefficients $C_m$ are given by
+\begin{align}
+C_m = \oint_{C_1} dt e^{i\mathcal{T}_1(t)} B_m(Z(t)).
+  \label{coef}
+\end{align}
+In the last line of Eq. (\ref{SPA2}), the summation is restricted to
+$\{m_\alpha\}$ that satisfy $\sum_\alpha m_\alpha=J$.
+It is easy to find that $J$ must be integer,
+according to the quantization rule (\ref{EBK}) for the $(J,\Phi)$ sector.
+
+The SPA for the ground state ($k=0$) is given by the stationary point
+in the $(q^1,p_1)$ sector,
+namely, the HFB state $\ket{\Phi,J;q,p}=e^{-i\Phi\hat{N}/2}\ket{\rm HFB}$.
+Nevertheless, the rotational motion in $\Phi(t)$ is present,
+which leads to the number quantization (projection).
+Therefore, Eq.~(\ref{SPA2}) becomes
+\begin{align}
+	\ket{\psi_{\rm g.s.}} \propto& \sum_{\{m_\alpha\}}
+	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi}
+	\ket{\rm HFB},  
+	\label{SPA3}
+\end{align}
+which is identical to the wave function of the particle-number projected HFB state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Result}
+In the pairing model in Sec.~\ref{sec3},
+the number of TDHFB degrees of freedom equals that of single-particle levels.
+% including the constant of motion (pair rotation).
+We consider various systems, two-level system, three-level system, and Pb isotope system in each subsection respectively.
+Next, we discuss the dynamics in non-integrable (more than three-level) system.
+As there are two constants of motion, that is, the particle number and 
+the energy, the system is integrable for one- and two-level models.
+We first apply the ASCC+SPA method to an integrable two-level model,
+then, to non-integrable multi-level models.
+
+\subsection{Integrable case: Two-level pairing model}
+
+\begin{figure}[thb]
+ \begin{center}
+   \includegraphics[height=0.45\textwidth,angle=-90]{images/N16X3p2trajectory.eps}
+ \end{center}
+\caption{Classical trajectories satisfying the EBK quantization condition
+(\ref{EBK}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
+%The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$. 
+The crosses, solid and dashed lines correspond to the results
+of the ASCC+SPA, TDHFB2+SPA, and TDHFB+SPA, respectively.
+The crosses for the ASCC+SPA trajectories are plotted every ten calculations
+($\delta q = 10dq =0.1/\sqrt{\epsilon_0}$). 
+%For the ASCC+SPA trajectories, we plot the crosses
+%every ten(?) points of the calculation,
+%namely $\delta q=0.1/\sqrt{\epsilon_2-\epsilon_1}$.
+}
+\label{fig:N16_traj}
+\end{figure}
+\begin{figure}[thb]
+ \begin{center}
+   \includegraphics[height=0.5\textwidth,angle=-90]{images/N16X3p2action.eps}
+ \end{center}
+\caption{Calculated action integrals for the $\ket{0_2^+}$ and $\ket{0_3^+}$ states as functions of time $t$.
+The crosses, solid and dashed lines correspond to the ASCC+SPA,
+the TDHFB2+SPA, and the TDHFB+SPA, respectively. 
+%Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
+The action integrals are calculated on each trajectory in Fig. \ref{fig:N16_traj}
+from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction.
+The crosses for the ASCC+SPA trajectories are plotted every ten calculations
+($\delta q = 10dq =0.1/\sqrt{\epsilon_0}$). 
+}
+\label{fig:N16_tau}
+\end{figure}
+\begin{figure}[thb]
+ \begin{center}
+   \includegraphics[height=0.5\textwidth,angle=-90]{images/N16X3p2occ.eps}
+ \end{center}
+\caption{
+Occupation probabilities for the $0_2^+$ and $0_3^+$ states.
+The horizontal line indicates the $j=(m_2-m_1)/2$ of the quasi-spin basis
+in Eq. (\ref{SPA2}).
+The vertical bars at each $m_2-m_1$ from left to right
+represent $|C_m|^2$ of Eq. (\ref{coef}) in
+the ASCC+SPA, TDHFB2+SPA and TDHFB+SPA calculations,
+respectively.
+}
+ \label{fig:N16_occ}
+\end{figure}
+
+The two-level pairing model corresponds to the 2D TDHFB system.
+Explicitly separating the gauge angle $\Phi$ and
+fixing the particle number $J$,
+the 2D TDHFB is reduced to the 1D system
+with the relative angle $\phi\equiv \chi_2-\chi_1$ and the relative
+occupation $j\equiv (j_2-j_1)/2$ as canonical variables.
+In Ref.~\cite{NN18}, using the explicit transformation to these
+separable variables,
+we examined the performance of the SPA requantization
+for the two-level model.
+In this section, we discuss the same model as in Ref.~\cite{NN18},
+but we determine the transformation using the ASCC method and then apply the
+SPA (ASCC+SPA).
+%In this section, we apply the ASCC+SPA method to the same model.
+%In other words, the ASCC method finds the transformation.
+
+Here, we study the system with the equal degeneracy,
+$\Omega_1=\Omega_2=8$, 
+the pairing strength $g/\epsilon_0=0.2$,
+and the particle number $N=16$. 
+In this two-level case, we use the level spacing,
+$\epsilon_0\equiv \epsilon_2-\epsilon_1$,
+as the unit of energy.
+The moving-frame QRPA produces the zero mode and another eigenvector
+with a finite frequency squared $\omega^2\neq 0$.
+We follow the latter mode to construct the collective path.
+In the ASCC calculation, we set the increment of the
+collective coordinate, $dq=0.01$,
+in units of $1/\sqrt{\epsilon_0}$.
+We confirm that the pair rotation always has a zero frequency
+on the collective path.
+On the obtained collective path, we calculate a classical trajectory
+for the Hamiltonian
+\begin{equation}
+\mathcal{H}_{\rm coll}(q^1,p_1;J)=\frac{1}{2} p_1^2 + V(q^1,J)
+\end{equation}
+with $J=N/2=8$.
+Calculated trajectories that satisfy the EBK quantization condition
+(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$)
+are mapped onto the $(\phi,j)$ plane and
+shown in Fig. \ref{fig:N16_traj}.
+We also calculate the trajectories using the explicit transformation
+of the variables to $(\Phi,J;\phi,j)$, which
+are shown by dashed lines in Fig. \ref{fig:N16_traj}.
+We call this ``TDHFB trajectories''.
+Small deviation in large $\phi$ is due to the absence of the higher-order
+terms in $\chi_\alpha$ in the ASCC.
+In fact, if we calculate the trajectories in the variables
+$(\Phi,J;\phi,j)$ using the Hamiltonian truncated up to the
+second order in $\chi_\alpha$ (``TDHFB2 trajectories''),
+we obtain the solid lines in Fig. \ref{fig:N16_traj},
+which perfectly agree with the ASCC trajectories.
+
+The action integrals $\mathcal{T}(t)$ corresponding to
+these closed trajectories are shown in Fig. \ref{fig:N16_tau}.
+For the $0_2^+$ state,
+all three calculations agree well
+with each other, while we see small deviation between the full TDHFB
+and the ASCC/TDHFB2 calculations for the $0_3^+$ state.
+
+The calculated wave functions for the excited $0^+$ states 
+are shown in Fig. \ref{fig:N16_occ}. 
+We show the occupation probabilities which are decomposed 
+into the $2n$-particle-$2n$-hole components. 
+The left end of the horizontal axis at $m_2-m_1=-8$ $(j=-4)$
+corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
+are in the lower level $\alpha=1$.
+The next one at $m_2-m_1=-6$ $(j=-3)$ corresponds to the one with
+$(m_1,m_2)=((N-2)/2,1)$, and so on.
+The results from the TDHFB2+SPA and the ASCC+SPA are identical to each other
+within numerical error, and they reproduce
+the TDHFB+SPA calculation well.
+
+%we can obtain the obvious collective path from ASCC.
+%The dynamics is exactly identical with adiabatic TDHFB (ATDHFB). We confirm that whether ASCC is identical to one-dimensional ATDHFB, and compare the difference with TDHFB, in numerical calculation.
+%
+%In two-level system, the classical Hamiltonian in (\ref{TDHFB_Hamiltonian_2}) is
+%\begin{align}
+%\mathcal{H} 
+%  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
+% &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
+%- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
+%\end{align}
+%If we define the canonical coordinate $\phi=\chi_2-\chi_1$, it attributes to one-dimensional system.
+The conjugate momentum is $j= \frac{\partial\mathcal{L}}{\partial\dot{\phi}} = \{\Omega_2(1-\cos{\theta}_2) - \Omega_1(1-\cos{\theta}_1)\}/4$.
+The ATDHFB indicates that the Hamiltonian can be expanded up to second order with respect to $\phi$
+%\begin{align}
+%  \mathcal{H}(\phi,j) &\approx V(j) + \frac{1}{2}B^{-1}(j)\phi^2,
+%\end{align}
+%where $V(j)=\mathcal{H}(\phi=0,j)$ and $B^{-1}(j)= \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2} \right|_{\phi=0}$.
+%We know that the BCS ground state corresponds to the potential minimum point with $\phi=0$.
+If the pairing correlation is strong enough to bind the excited states in the collective potential,  the adiabatic approximation is expected to be well because the states are localized in small $\phi$ region.
+%
+
+By comparing with the full TDHFB calculation with the ASCC+SPA approach
+in the two-level pairing model,
+we conclude that the ASCC is reliable for description of low-lying
+collective states, for which the adiabatic approximation is justifiable.
+In addition to that, we should note that the pair rotation is properly separated.
+%we succeed to describe the bound collective excited states by ASCC+SPA.
+For the bound states, whether the adiabatic approximation included or not hardly has influence.
+Even for the weakly bound states, the adiabatic approximation is reasonable approximation.
+
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{images/omega_sq.eps}
+ \end{center}
+ \caption{Eigenvalues of moving-frame QRPA equation as a function of
+the collective coordinate $q^1$, from $N=14$ to $N=24$.
+The thick (green) lines are the modes we choose as
+the collective coordinate $q^1$,
+while the dashed lines correspond to the zero modes ($q^n$).
+In each panel, both ends of the horizontal axis corresponds
+to the ending points of the collective path $q^1$.
+}
+ \label{omega_sq}
+\end{figure*}
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=40mm,angle=-90]{images/occ_number.eps}
+ \end{center}
+\caption{The occupation numbers $2j^{\alpha}$ in each single-particle level $\alpha$
+as a function of the collective coordinate $q^1$,
+from $N=14$ to $N=24$.
+The purple, green, and blue lines correspond to
+$\alpha=1$, 2, and 3, respectively.
+At the left end point of the collective coordinate in each panel,
+the configuration corresponds to the ``HF-like'' states.
+See text for details.
+}
+ \label{occ_number}
+\end{figure*}
+\subsection{Non-integrable case (1): Three-level pairing model}
+\label{sec:three-level-model}
+
+In contrast to the two-level model,
+the TDHFB for the three-level model is non integrable.
+%The simplest non-integrable system is three-level system. We have one trivial motion and two time-dependent degrees of freedom. 
+We set the parameters of the system as follows:
+$\Omega_1=\Omega_2=\Omega_3=\Omega=8$,
+$\epsilon_1=-\epsilon_0$, $\epsilon_2=0$, $\epsilon_3=1.5\epsilon_0$,
+and $g=0.2\epsilon_0$.
+We use the parameter $\epsilon_0$ as the unit energy.
+For the sub-shell closed configuration of $N=2\Omega=16$,
+the HFB ground state changes from the normal phase to
+the superfluid phase at $g_c=0.058\epsilon_0$.
+We calculate a chain of systems with even particle numbers
+from $N=14$ to $N=24$.
+
+We obtain three eigen frequencies for the moving-frame QRPA equation, 
+on the collective path (Fig. \ref{omega_sq}). 
+First of all, we clearly identify the zero mode with $\omega^2=0$
+everywhere along the collective path.
+This means that the pair rotation is separated from the other
+degrees of freedom in the ASCC.
+The frequency could become imaginary ($\omega^2<0$).
+Except for the case of sub-shell closure ($N=2\Omega_1=16$),
+the frequency rapidly increases near the end points.
+The end points are given by points where the search for the next point
+on the collective path in Sec.~\ref{sec:ASCC} fails.
+
+We choose the lowest frequency squared mode, except for the zero mode,
+as a generator of the collective path ($q^1$).
+Figure~\ref{occ_number} shows variation of the occupation probability
+of each single-particle state, as functions of the collective
+coordinate $q^1$ on the collective path.
+The most striking feature is that the collective path terminates
+with special configurations which are given by the integer number
+of occupation.
+This is the reason why the search for the collective path fails
+at both the ends.
+At the end points,
+the occupation of the level 3 ($\epsilon_3$) vanishes, while
+those of the levels 1 and 2 become either maximum or minimum.
+The left end of each panel in Fig.~\ref{occ_number} corresponds to 
+a kind of ``Hartree-Fock'' (HF) state which minimizes
+the single-particle-energy sum, $\sum_\alpha 2j_\alpha \epsilon_\alpha$.
+The pairing correlation is weakened in both ends of the
+collective path.
+
+The collective mass with respect to the coordinate $q^1$ is normalized
+to unity.
+The collective potential is shown in Fig.~\ref{potential}.
+The range of $q^1$ is the largest for the system with $N=16$.
+This is because the variation of $j^1$ and $j^2$ is the largest in
+this case.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/potential.eps}
+ \end{center}
+	\caption{Collective potential $V(q^1)$ obtained from the ASCC.
+	We adjust the energy minimum point as $q^1=0$ and $V=0$.
+}
+ \label{potential}
+\end{figure}
+\begin{table}[htbp]
+\caption{Calculated excitation energies of the first and the second
+excited states in units of $\epsilon_0$.
+In the exact calculation, the second excited state in the ASCC+SPA
+corresponds to the $0_4^+$ state.
+See text for details.}
+\label{ex}
+\begin{tabular}{c|cccccc}
+            $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
+ASCC+SPA (1st exc.) & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\
+    Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\ \hline
+ASCC+SPA (2nd exc.)& $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
+Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$
+\end{tabular}
+\end{table}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/intra_trans.eps}
+ \end{center}
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/inter_trans.eps}
+ \end{center}
+\caption{Calculated strength of pair-addition transition (\ref{BPad})
+from $N=14$ to $N=22$. 
+The solid (dashed) lines correspond to the ASCC+SPA (exact) calculation.
+The horizontal line indicates the particle number of the initial states.
+The upper panel shows the intraband transitions,
+$0_1^+\to 0_1^+$ and $0_2^+\to 0_2^+$,
+while the lower panel shows the interband transitions,
+$0_1^+ \to 0_2^+$ and $0_2^+\to 0_1^+$.
+}
+ \label{3levelPad}
+\end{figure}
+
+Based on the collective path determined by the ASCC calculation,
+we perform the requantization according to the SPA.
+Table \ref{ex} shows the excitation energies of the first and second
+excited states, determined by the EBK quantization condition (\ref{EBK}).
+Comparing the result of the ASCC+SPA with that of the exact calculation,
+we find that the excitation energies are reasonably well reproduced. 
+The ASCC+SPA underestimates the excitation energies only by about 5 \%.
+%The difference is that the values from ASCC+SPA are 
+%about $5\%$ smaller than exact solution.
+
+It should be noted that the second excited state in the collective path
+corresponds to the $0_4^+$ state,
+not to the $0_3^+$ state, in the exact calculation. 
+We examine the interband $(k\neq k')$ pair-addition transition,
+\begin{equation}
+B(P_{\rm ad};k\rightarrow k') \equiv 
+	\left|\bra{0_{k'}^+;N+2} \hat{S}^+ \ket{0_k^+;N}\right|^2 ,
+\label{BPad}
+\end{equation}
+in the exact solution.
+$B(P_{\rm ad};0_2^+\rightarrow 0_3^+)$ 
+is $10\sim100$ times smaller than $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$,
+while $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and
+$B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$ are in the same order.
+The ASCC+SPA produces states in the same family,
+namely, those belonging to the same collective subspace (path).
+In the phonon-like picture,
+we expect similar magnitude of the strengths for
+$B(P_{\rm ad};{\rm g.s.}\rightarrow \omega_{\rm phon})$
+and
+$B(P_{\rm ad};\omega_{\rm phon}\rightarrow 2\omega_{\rm phon})$,
+but smaller values of
+$B(P_{\rm ad};{\rm g.s.}\rightarrow 2\omega_{\rm phon})$.
+Thus, the $0_4^+$ state in the exact calculation
+corresponds to the two-phonon state in the ASCC+SPA.
+The $0_3^+$ state in the exact calculation may correspond to
+a collective path associated with another solution of the moving-frame QRPA
+(thin black line in Fig.~\ref{omega_sq}).
+
+%It indicates that $\ket{0_3^+}$ is also one-phonon state which belongs to the other collective path (black line in Fig.
+\ref{omega_sq}).
+About two-phonon states, we can easily find the candidates of two-phonon states from excitation energies and $B(P_{\rm ad};0_1^+\rightarrow 0_{ex}^+)$.
+In the candidates, $\ket{0_4^+}$ is the lowest two-phonon state and $B(P_{\rm ad};0_2^+\rightarrow 0_4^+)$ is much larger than $B(P_{\rm ad};0_3^+\rightarrow 0_4^+)$.
+Therefore, $\ket{0_4^+}$ is considered to be most appropriate corresponding to the second excited state in ASCC+SPA calculation.
+
+Next, we calculate the wave functions,
+according to Eqs.~(\ref{SPA2}) and (\ref{SPA3}).
+The ground state corresponds to the number-projected HFB state
+(variation before projection).
+In contrast, the excited states are given as superposition of
+generalized Slater determinants in the collective subspace,
+The pair-addition transition strengths
+computed using these wave functions of the excited states
+are shown in Fig. \ref{3levelPad}.
+For the intraband transition ($k=k'$ in Eq. (\ref{BPad})),
+the ASCC+SPA method well reproduces the strengths of the exact calculation.
+The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$, 
+are perfectly reproduced, while
+$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are underestimated 
+by about $10\%\sim20\%$.
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=55mm,angle=-90]{images/Pbomega_sq.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
+}
+ \label{Pb_omega_sq}
+\end{figure*}
+
+\begin{figure*}[tb]
+ \begin{center}
+  \includegraphics[width=55mm,angle=-90]{images/Pbocc_number.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
+}
+ \label{Pb_occ_number}
+\end{figure*}
+
+It is more difficult to reproduce the absolute magnitude of
+interband transitions ($k\neq k'$), 
+which are far smaller than the intraband transitions.
+Although the increasing (decreasing) trend for
+$B(P_{\rm ad};0_2^+\rightarrow 0_1^+)$
+($B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$)
+as a function of the particle number is properly reproduced,
+the absolute magnitude is significantly underestimated in the ASCC+SPA.
+This is due to extremely small collectivity in the interband transitions.
+Almost all the strengths are absorbed in the intraband transitions.
+Even in the exact calculation, the pair addition strength is
+about two orders of magnitude smaller than the intraband strength.
+Remember that the non-collective limit ($g\rightarrow 0$) of this
+value is $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)=\Omega$.
+Therefore, the pairing correlation hinders the interband transitions
+by about one order of magnitude.
+For such tiny quantities, perhaps, 
+the reduction to the 1D collective path is not well justified.
+%In our previous study on the two-level case, we found that
+%the SPA reasonably well reproduces interband transitions \cite{NN18}.
+%The present case corresponds to a strong pairing case with
+%the strongly hindered interband transitions.
+
+%It is difficult to reproduce the absolute value of exact solution.
+%However, because the pairing correlation is enough strong in this case, the strength of intraband transition is dominant compared with interband transition.
+%We can find that 
+%$B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_1^+)$ are only about $1\%$ of $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$ and $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$.
+Therefore, the interband transition can be regarded as reasonable.
+From all above results, we can conclude that ASCC+SPA reproduces exact solution quantitatively.
+
+We should remark here that there is a difficulty in the present ASCC+SPA
+requantization for weak pairing cases.
+In such cases, the potential minimum is close to the left end 
+($q^1=q_L$) of the collective path, and the potential height
+at $q^1=q_L$, $V(q_L) - V(0)$, becomes small.
+Then, a classical trajectory with $E>V(q_L)$ hits this boundary ($q^1=q_L$).
+In construction of wave functions,
+the boundary condition at $q^1=q_L$ significantly influences the result.
+In the present study, we choose a strong pairing case to avoid
+such a situation.
+As in Fig.~\ref{potential}, the potential height at $q^1=q_L$ has
+about $10\epsilon_0$ which is larger than the excitation energies
+of the second excitation.
+Therefore, all the trajectories are ``closed'' in the usual sense.
+
+%We skipped the result about $\ket{0_3^+}$.
+
+\subsection{Non-integrable case (2): Pb isotopes}
+\label{sec:Pb_isotopes}
+
+Finally, we apply our method to neutrons' pairing dynamics in 
+neutron-deficient Pb isotopes.
+The spherical single-particle levels of neutrons
+between the magic numbers 82 and 126 are adopted and
+their energies are presented in Table \ref{Pb}. 
+The coupling constant $g=0.138$ MeV is determined to reproduce
+the experimental pairing gap given by the odd-even mass difference,
+$\Delta(N)=\frac{(-1)^{N+1}}{2}[B(N+1)-2B(N)+B(N-1)]$ of ${}^{192}$Pb.
+The even-even nuclei from ${}^{188}$Pb to ${}^{194}$Pb
+are studied.
+\begin{table}[tb]
+\caption{Single-particle energies of Pb isotopes used in the calculation
+in units of MeV.
+These are obtained from the spherical Woods-Saxon potential
+with the parameters of Ref.~\cite{BM69}.
+}
+\begin{tabular}{c|cccccc}
+  orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
+  energy(MeV)& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
+\end{tabular}
+\label{Pb}
+\end{table}
+
+The TDHFB dynamics is described by six degrees of freedom.
+Figure \ref{Pb_omega_sq} shows eigenvalues of the
+moving-frame QRPA equation.
+Again, we find that there is a zero mode corresponding to
+the neutron pair rotation.
+Among the five vibrational modes, we choose the lowest one to
+construct the collective path in the ASCC.
+This lowest mode never crosses with other modes,
+though the spacing between the lowest to the next lowest mode
+can be very small, especially for ${}^{194}$Pb.
+The evolution of the occupation numbers along the collective path
+is shown in Fig. \ref{Pb_occ_number}.
+Similarly to the three-level model, 
+the end points of the collective path indicate exactly
+the integer numbers, and
+the left end of each panel corresponds to the
+``Hartree-Fock''-like state.
+On the collective path, the occupation numbers of $i_{13/2}$, $p_{3/2}$, and
+$f_{5/2}$ mainly change.
+%The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb.
+
+\begin{figure}[bt]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/Pbpotential.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{potential} but for Pb isotopes.
+}
+ \label{Pb_potential}
+\end{figure}
+The collective potentials for these isotopes are shown
+in Fig. \ref{Pb_potential}.
+The heights of the potentials at the left end, $V(q_L)-V(0)$,
+are $2\sim3.5$ MeV.
+For $^{186}$Pb, the height of the potential is not
+enough to satisfy the condition, $E<V(q_L)$,
+to have a closed trajectory for the first excited state
+(See the last paragraph in Sec.~\ref{sec:three-level-model}).
+We encounter another kind of problem for $^{196}$Pb,
+which will be discussed in Sec.~\ref{sec5}.
+Therefore, in this paper, we calculate the first excited states
+in $^{188,190,192,194}$Pb.
+
+We show the calculated excitation energy of the first excited state
+in Table~\ref{Pb_ex}.
+Experimentally, this pair vibrational excited $0^+$ state is
+fragmented into several $0^+$ states due to other correlations,
+such as quadrupole correlation, not taken into account in the present model.
+%The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction. 
+We make a comparison with the exact solution of the multi-level
+pairing model.
+The ASCC+SPA method quantitatively reproduces the excitation energy of
+the exact solution.
+
+\begin{table}[bt]
+\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
+\begin{tabular}{c|cccccc}
+   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
+ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
+Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
+\end{tabular}
+\label{Pb_ex}
+\end{table}
+\begin{figure}[htb]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/Pbintra_trans.eps}
+ \end{center}
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/Pbinter_trans.eps}
+ \end{center}
+	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
+}
+ \label{PbPad}
+\end{figure}
+The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
+The feature that is similar to the three-level case is observed:
+dominant intraband transition and very weak interband transitions.
+The accuracy from the ASCC+SPA method well reproduces
+$B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
+and qualitatively reproduces
+$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ as well.
+The deviation for the latter is about $25\%$.
+The interband transitions are smaller than the intraband transitions
+by more than two orders of magnitude.
+This is also similar to the three-level model discussed
+in Sec.~\ref{sec:three-level-model}.
+For such weak transitions, the ASCC+SPA significantly
+underestimates the strengths.
+We may say that the ASCC+SPA gives reasonable results for the intraband
+transitions in the realistic values of the pairing coupling constant $g$ and
+single-particle levels.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage{\pagestyle{empty}\cleardoublepage}
+\chapter{Collective model treatment}
+\label{collective}
+
 The collective model has been proposed
 and utilized for the nuclear pairing dynamics
-\cite{BBPK70,delta1,delta3}.
-For those studies, the pairing gap parameter (or equivalent quantities)
+\cite{BBPK70,GPBW85, ZPPRS99, P07}.
+For those studies, the pairing gap parameter $\Delta$ (or equivalent quantities)
 is assumed to be the collective coordinates.
-This is analogous to the five-dimensional (5D) collective (Bohr) model,
+This is analogous to the Bohr collective model,
 in which the collective coordinates are assumed to be the
@@
 in comparison with experimental data.
-In this section, we examine the validity of
+In this chapter, we examine the validity of
 the collective treatment of the pairing.
@@
 since the relation, $\Delta=G\alpha$,
-guarantees one-to-one correspondence between $\alpha$ and $\Delta$. In Sec.~\ref{sec:canonical}, we treat $\phi$ as a collective coordinate
+guarantees one-to-one correspondence between $\alpha$ and $\Delta$.
+
+\section{Integrable system}
+In Sec.~\ref{sec:canonical}, we treat $\phi$ as a collective coordinate
 and $j$ as its conjugate momentum.
@@
 
-\chapter{Requantization of TDHFB in non-integrable system}
-\label{non-integrable}
-
-\section{Theoretical framework of ASCC+SPA in non-integrable system}
-
-\section{Result}
-
-\chapter{Discussion}
-
+\section{non-integrable system}
+Finally, we discuss the validity of the collective model approach
+assuming the pairing gap as a collective coordinate.
+The 5D collective Hamiltonian assuming the quadrupole deformation
+parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,$ and $0)$ as the collective coordinates
+is widely utilized to analyze experimental data of quadrupole states.
+Similarly, we may construct the pairing collective Hamiltonian
+in terms of the pairing gap $\Delta$ and the gauge angle $\Phi$. 
+As far as there is a one-to-one correspondence between $\Delta$ 
+and the collective variable $q^1$ we obtained in the present study,
+we can transform the collective Hamiltonian in $(q^1,\Phi)$
+into the one in $(\Delta,\Phi)$.
+The pairing gap $\Delta$ is defined as
+\begin{align}
+  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|\hat{S}^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
+  &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
+\end{align}
+Figure \ref{192Pb_gap} shows the pairing gap $\Delta$ in ${}^{192}$Pb
+as a function of the collective coordinate $q^1$.
+The peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
+function of $q^1$, thus no one-to-one correspondence exists.
+The same behavior is observed for other Pb isotopes too.
+Therefore, the pairing gap $\Delta$ is not a suitable collective coordinate
+to describe the pairing dynamics in the multi-level model.
+
+%Because only one orbit near the Fermi energy ($i_{13/2}$ orbit for both end points) contributes the value of pairing gap, the value at both end points are small compared with the value around the ground state.
+There is no one-to-one correspondence between $\Delta$ and $q$ not only in ${}^{192}$Pb, but also in all multi-level systems.
+
+%As with the 5D collective model, pairing can also be supposed as a sort of deformation. The collective model is described by
+%the pair deformation parameters pairing gap $\Delta$ and global gauge angle $\Phi$. 
+%The utilization of the collective model for nuclear pairing dynamics was done in several references\cite{??}.
+In our previous study, however, we find that the pairing gap $\Delta$ is not proper to be the collective coordinate in two-level pairing model \cite{??}.
+In multi-level system, we can investigate the relations between the pairing gap and the collective coordinate.
+
+\begin{figure}[t]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/192Pbgap.eps}
+ \end{center}
+	\caption{Pairing gap as a function of collective coordinate $q^1$
+	in ${}^{192}$Pb. 
+}
+ \label{192Pb_gap}
+\end{figure}
+
+\clearpage{\pagestyle{empty}\cleardoublepage}
 \chapter{Conclusion}
-
+\label{conclusion}
+
+We studied the low-lying excited $0^+$ states in multi-level pairing model.
+We constructed theoretical framework to describe pairing collective motion in large-amplitude regime.
+The approach roughly consists of two steps: (1) solve the TDHFB equation to obtain the classical trajectories; (2) requantize the TDHFB trajectories to obtain the excited states.
+The TDHFB degrees of freedom equal to the number of single-particle level.
+More specifically, the TDHFB degrees of freedom consists of one constant of motion, pairing rotation, and $L-1$ time-dependent degrees of freedom in $L$ single-particle level system.
+Therefore, we divided the pairing system into two classes, two-level system corresponding to the integrable system and the system more than three-level corresponding to the non-integrable system.
+
+In two-level system, integrable system, we studied three different methods of requantization of TDHFB, the stationary-phase approximation (SPA) of the path integral, the canonical quantization (CQ), and the Fourier decomposition(FD) of the time-dependent observables.
+
+\clearpage{\pagestyle{empty}\cleardoublepage}
 \appendix
@@
 
+\clearpage{\pagestyle{empty}\cleardoublepage}
 \chapter{Properties of superfluid ground state in pairing model}
@@
 
+\clearpage{\pagestyle{empty}\cleardoublepage}
 \chapter{Adiabatic self-consistent collective coordinate method}

### 2018-12-10 thesis/thesis.tex
thesis

@@
 
-\title{Requantization of time-dependent mean field
- for pairing collective motion in superfluid nuclei}
-\author{Fang Ni}
-%\date{} % Activate to display a given date or no date (if empty),
-         % otherwise the current date is printed
-
 \begin{document}
-\maketitle
-
-\chapter*{Absract}
+\begin{titlepage}
+\begin{center}
+\vspace*{100truept}
+{\huge Requantization of time-dependent mean field}\\
+\vspace{5truept}
+{\huge for pairing collective motion in superfluid nuclei}\\
+\vspace*{120truept}
+{\LARGE Fang Ni}\\
+\vspace*{280truept}
+{\LARGE February 2019}\\ 
+\end{center}
+\end{titlepage} 
+\newpage
+
+\thispagestyle{empty}
+\newpage
+
+\begin{titlepage}
+\begin{center}
+\vspace*{100truept}
+{\huge Requantization of time-dependent mean field}\\
+\vspace{5truept}
+{\huge for pairing collective motion in superfluid nuclei}\\
+\vspace*{120truept}
+{\LARGE Fang Ni}\\
+\vspace{5truept}
+{\LARGE Doctral Program in Physics}\\
+\vspace*{200truept}
+{\LARGE Submitted to the Graduate School of}\\
+\vspace{5truept}
+{\LARGE Pure and Applied Sciences}\\
+\vspace{5truept}
+{\LARGE in Partial Fulfillment of the Requirements} \\
+\vspace{5truept}
+{\LARGE for the Degree of Doctor of Philosophy in}\\
+\vspace{5truept}
+{\LARGE Science}\\
+\vspace*{15truept}
+{\LARGE at the}\\
+\vspace{5truept}
+{\LARGE University of Tsukuba}\\ 
+\end{center}
+\end{titlepage} 
+\thispagestyle{empty}
+
+\chapter*{Abstract}
+\thispagestyle{empty}
 
@@
 The common suggestion from those experimentalists is that the pairing correlation plays an important role in such excited $0^+$ states because they found strange cross sections of two-nucleon transfer reactions.
-From theoretical viewpoint, excited $0^+$ states correspond to pairing vibrational mode, the elementary mode of excitation of pairing collective motions, in superfluid nuclei.
-Because quantum fluctuation is large in low-lying region, To understand such excited $0^+$ states, extend to the large-amplitude regime, but also pairing correlation.
+From theoretical viewpoint,
+%excited $0^+$ states in superfluid nuclei correspond to not only quadrupole vibrational mode, the elementary mode of excitation of quadrupole collective motions, but also pairing vibrational mode, the elementary mode of excitation of pairing collective motions.
+the competition between quadrupole correlation and pairing correlation causes complicate structure of low-lying excited $0^+$ states. 
+We aim to understand such excited $0^+$ states based on time-dependent mean-field (TDMF) theory.
+Because quantum fluctuation is large in low-lying excitation region, theoretical framework in large-amplitude regime is necessary.
+However, the theoretical framework to describe pairing collective motions in large-amplitude regime is not developed.
+The nature of pairing collective motions in low-lying excitation region is still unclear.
+
+We consider the theoretical framework to describe large-amplitude collective motions associated with nuclear pairing.
+In general, the low-lying excited states can be obtained in two steps: (1) solve TDMF equation to obtain classical trajectories; (2) quantize such classical trajectories to obtain the excited states.
+The step 2 is called ``requantization''.
+In this thesis, we focus on step 2 and discuss the requantization method in detail.
+To simplify the system, apart from realistic nuclear system, we consider the pairing collective motions in multi-level pairing model.
+We divide the pairing system into two classes, integrable system and non-integrable system.
+The former one corresponds to two-level system and the later one corresponds to the system more than three-level.
+Because the description of requantization is different between the two, we consider the requantization methods for each case, respectively.
+
+In integrable system, the requantization of TDMF is particular feasible because we can easily find the periodic orbits.
+We apply three different requantization methods, canonical quantization, Fourier decomposition of the time-dependent observables, and stationary phase approximation (SPA) to the path integral.
+Comparing each requantization method with exact solution in various two-level system, respectively, SPA turns out to be most accurate between the three and can describe the excited states quantitatively, especially for the calculation of two-particle transition strength.
+Because the requantized wave functions from SPA are given in terms of the microscopic degrees of freedom, the transition matrix elements can be calculated directly.
+
+Actually, SPA cannot be applied to non-integrable system straightforwardly because finding the periodic orbits is extremely difficult task.
+We propose a new theoretical approach which enables SPA to apply to non-integrable system, namely, combining SPA with adiabatic self-consistent collective coordinate (ASCC) method (ASCC+SPA).
+The concept is that we employ ASCC to extract an integrable subspace from TDMF phase space, and apply SPA to obtain the excited states.
+The detailed derivation is shown in the text.
+From the application to the low-lying excited $0^+$ states in three-level system and Pb isotopes system, we find ASCC+SPA gives a reasonable description.
+
+We also examine the performance of the pairing collective model which phenomenologically assumes pairing gap parameter and gauge angle as collective coordinates.
+We check the one-to-one correspondence between the collective coordinates from TDMF dynamics itself and those in collective model.
+We find the collective coordinate describing pairing vibration has no one-to-one correspondence between the two, in both integrable and non-integrable system.
+The applicability of the collective model is limited for the nuclear pairing.
+
+We summarize the achievements in this thesis.
+We find a reasonable requantization method, SPA, from the study in integrable system.
+Using SPA, we construct a theoretical framework of ASCC+SPA to requantize the pairing collective motions in non-integrable system.
+Also, we demonstrate that to describe pairing vibration properly, it is necessary to employ the collective coordinate extracted from TDMF degrees of freedom itself, instead of the phenomenological collective coordinate, pairing gap parameter.
+With the development of computational power, we think
+ASCC+SPA is promising tool to elucidate the structure of mysterious low-lying excited $0^+$ states in nuclei.
+
+\thispagestyle{empty}
 
 \pagenumbering{roman}
+\setcounter{page}{-1}
 \tableofcontents
-\thispagestyle{empty}
+%\thispagestyle{empty}
 
@@
 \begin{align}
-	H &= \sum_{l=1}^L \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
+	H &= \sum_{\alpha=1}^L \epsilon_{\alpha} n_{\alpha} - g \sum_{\alpha\beta} S_{\alpha}^+ S_{\beta}^- ,
 \end{align}
@@
 \begin{align}
-	n_l &= \sum_m a^{\dag}_{lm}a_{lm} \\
-        S_l^{+} &= \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
-\quad   S_l^{-} = S_l^{+\dag} .
+	n_{\alpha} &= \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m} \\
+        S_{\alpha}^{+} &= \sum_{m>0}a_{j_\alpha m}^{\dag}a_{j_\alpha \overline{m}}^{\dag} ,
+\quad   S_{\alpha}^{-} = S_{\alpha}^{+\dag} .
 \label{S_+}
 \end{align}
-In $L$ single-particle level system, each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
-degeneracy ($\Omega_l=j_l+1/2$)
-and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_l-1/2$.
+In $L$ single-particle level system, each single-particle energy $\epsilon_{\alpha}$ possesses $(2\Omega_{\alpha})$-fold
+degeneracy ($\Omega_{\alpha}=j_{\alpha}+1/2$)
+and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_{\alpha}-1/2$.
 $\overline{m}$ indicates the time reversal quantum number with respect to $m$.
 The strength of pairing correlation is represented by coupling constant $g$.
-We also define a seniority $\nu_l$, which is the number of unpaired particles in each level.
-The total number of unpaired particles is $\nu=\sum_l\nu_l$.
+We also define a seniority $\nu_{\alpha}$, which is the number of unpaired particles in each level.
+The total number of unpaired particles is $\nu=\sum_{\alpha}\nu_{\alpha}$.
 The unpaired particles have no pairing interaction, and play a part in Pauli blocking effect.\par
@@
 In addition, several pairing vibrational modes emerge.
-The pairing vibration is not single particle motion specified by $\nu_l$, but a collective motion arisen from $J^{\pi}=0^+$ pairs.
+The pairing vibration is not single particle motion specified by $\nu_{\alpha}$, but a collective motion arisen from $J^{\pi}=0^+$ pairs.
 In order to solve the multi-level pairing Hamiltonian, we explain the numerical exact solution.
@@
 \begin{equation}
-  [S_l^0,S_{l'}^{+}] = \delta_{ll'}S_{l}^{+},\hspace{20pt}[S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0}. 
+  [S_{\alpha}^0,S_{\beta}^{+}] = \delta_{\alpha\beta}S_{\alpha}^{+},\hspace{20pt}[S_{\alpha}^{+},S_{\beta}^{-}] = 2\delta_{\alpha\beta}S_{\alpha}^{0}. 
   \label{SU2commu}
@@
 \begin{align}
-  S_l^0 &= \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l)
+  S_{\alpha}^0 &= \frac{1}{2}(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_{\alpha})
   \label{S_0}
 \end{align}
-and $S_l^+, S_l^-$ as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
-\begin{align}
-	H &= \sum_l \epsilon_l (2S_l^0+\Omega_l) - g \sum_{l,l'} S_l^+ S_{l'}^- .
-\end{align}
-Therefore, any states $\ket{\psi}$ belong to SU(2)$\otimes\cdots\otimes$SU(2) Hilbert space, and can be expanded in the basis $\ket{S_1,S_1^0;\cdots;S_l,S_l^0;\cdots}$
-\begin{equation}
-  \ket{\psi} = \sum_{S_1^0,\cdots\,S_l^0,\cdots}c_{S_1^0,\cdots\,S_l^0,\cdots}\ket{S_1,S_1^0;\cdots;S_l,S_l^0;\cdots} .
+and $S_{\alpha}^+, S_{\alpha}^-$ as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
+\begin{align}
+	H &= \sum_{\alpha} \epsilon_{\alpha} (2S_{\alpha}^0+\Omega_{\alpha}) - g \sum_{\alpha\beta} S_{\alpha}^+ S_{\beta}^- .
+\end{align}
+Therefore, any states $\ket{\psi}$ belong to SU(2)$\otimes\cdots\otimes$SU(2) Hilbert space, and can be expanded in the basis $\ket{S_1,S_1^0;\cdots;S_{\alpha},S_{\alpha}^0;\cdots}$
+\begin{equation}
+  \ket{\psi} = \sum_{S_1^0,\cdots\,S_{\alpha}^0,\cdots}c_{S_1^0,\cdots\,S_{\alpha}^0,\cdots}\ket{S_1,S_1^0;\cdots;S_{\alpha},S_{\alpha}^0;\cdots} .
 \end{equation}
@@
 We consider the physical meaning of the quasispin space.
-Because $S_l^+$ and $S_l^-$ correspond to the creation and annihilation operators with respect to the $J^{\pi}=0^+$ pairs in each level, the quasispin space is decoupled from the space which the unpaired particles belong to.
-Also, $S_l^0$ is related to the occupation number in each level.
-$S_l^0=-S_l$ is the minimum value corresponding no $J^{\pi}=0^+$ pair in the level and $S_l^0=S_l$ is the maximum value corresponding full of $J^{\pi}=0^+$ pairs in the level.
-Because $\nu_l$ plays a part in Pauli blocking effect in the level, the absolute value of quasispin $S_l$ is
-\begin{equation}
-  S_l = \frac{1}{2}(\Omega_l-\nu_l).
-\end{equation}
-
-The dimension of the model space is $D=\prod_l(2S_l+1)$.
+Because $S_{\alpha}^+$ and $S_{\alpha}^-$ correspond to the creation and annihilation operators with respect to the $J^{\pi}=0^+$ pairs in each level, the quasispin space is decoupled from the space which the unpaired particles belong to.
+Also, $S_{\alpha}^0$ is related to the occupation number in each level.
+$S_{\alpha}^0=-S_{\alpha}$ is the minimum value corresponding no $J^{\pi}=0^+$ pair in the level and $S_{\alpha}^0=S_{\alpha}$ is the maximum value corresponding full of $J^{\pi}=0^+$ pairs in the level.
+Because $\nu_{\alpha}$ plays a part in Pauli blocking effect in the level, the absolute value of quasispin $S_{\alpha}$ is
+\begin{equation}
+  S_{\alpha} = \frac{1}{2}(\Omega_{\alpha}-\nu_{\alpha}).
+\end{equation}
+
+The dimension of the model space is $D=\prod_{\alpha}(2S_{\alpha}+1)$.
 However, $[H,N]=0$ indicates that the Hamiltonian is block diagonal with respect to the total particle number $N$.
-The model space can be reduced after we extract the combination of $\{S_l^0\}$ fulfilling
-\begin{equation}
-  N = \sum_l (2S_l^0+2S_l+\nu_l) .
+The model space can be reduced after we extract the combination of $\{S_{\alpha}^0\}$ fulfilling
+\begin{equation}
+  N = \sum_{\alpha} (2S_{\alpha}^0+2S_{\alpha}+\nu_{\alpha}) .
 \end{equation} 
@@
 Under spherical symmetry, we have five single particle levels, $d_{5/2}$, $g_{7/2}$, $s_{1/2}$, $d_{3/2}$, and $h_{11/2}$.
-The corresponding degeneracy is $\{\Omega_l\}=\{3,4,1,2,6\}$.
-If we only consider the case for$\nu_l=0$, the dimension for the system is $D=840$.
+The corresponding degeneracy is $\{\Omega_{\alpha}\}=\{3,4,1,2,6\}$.
+If we only consider the case for$\nu_{\alpha}=0$, the dimension for the system is $D=840$.
 On the other hand, under a specified $N$, the dimensions are 105 for $N=14$ and 91 for $N=20$.
@@
   E &= \braket{\psi|H|\psi} \\
-  &= \sum_l \epsilon_l \nu_l + \sum_{\alpha=1}^M E_{\alpha} .
+  &= \sum_{\alpha} \epsilon_{\alpha} \nu_{\alpha} + \sum_{m=1}^M E_{m} .
 \end{align}
@@
 \begin{equation}
-  1 - g\sum_l \frac{\Omega_l-\nu_l}{2\epsilon_l-E_{\alpha}} + 2g\sum_{\beta(\neq\alpha)}^M \frac{1}{E_{\beta}-E_{\alpha}} = 0 .
+  1 - g\sum_{\alpha} \frac{\Omega_{\alpha}-\nu_{\alpha}}{2\epsilon_{\alpha}-E_{\alpha}} + 2g\sum_{n(\neq m)}^M \frac{1}{E_{n}-E_{m}} = 0 .
 \end{equation}
 $M$ indicates the number of $J^{\pi}=0^+$ pairs in the system, and equals to the numbers of the non-linear equations.
-$E_{\alpha}$ can become not only real numbers, but also complex conjugate pairs when $M\ge 2$.
+$E_{m}$ can become not only real numbers, but also complex conjugate pairs when $M\ge 2$.
 
 We solved the non-linear equations numerically in general.
-If we input a set of initial values $E_{\alpha}^{0}$ into the equations, the values will converge by using proper numerical algorithm such as Newton-Raphson method.
-The difficult point is that we cannot directly specify the number of excitation from the obtained excitation energy because the converged excitation energy $\sum_{\alpha=1}^M E_{\alpha}$ can be any number of excitation.
+If we input a set of initial values $E_{m}^{0}$ into the equations, the values will converge by using proper numerical algorithm such as Newton-Raphson method.
+The difficult point is that we cannot directly specify the number of excitation from the obtained excitation energy because the converged excitation energy $\sum_{m=1}^M E_{m}$ can be any number of excitation.
 To specify the number of excitation, we can use the idea in Ref.
-\cite{Richardson4}, which discussed the behavior of the $E_{\alpha}$ as a function of $g$ for ground and each low-lying excitation energy.
-
-The eigenvalues can be also calculated numerically by using the obtained $E_{\alpha}$.
+\cite{Richardson4}, which discussed the behavior of the $E_{m}$ as a function of $g$ for ground and each low-lying excitation energy.
+
+The eigenvalues can be also calculated numerically by using the obtained $E_{m}$.
 Actually, we need to calculate the matrix elements for specific operators we interest (e.g.
@@
 \section{TDHFB dynamics}
+\label{2-2}
 %In realistic nuclear system with nuclear effective interaction, the necessary model space is huge.
@@
 \begin{equation}
-	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-S_l}
-	\exp [Z_l(t) S_l^{+}] \ket{0} .
+	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_{\alpha}(t)|^2\right)^{-S_{\alpha}}
+	\exp [Z_{\alpha}(t) S_{\alpha}^{+}] \ket{0} .
  \label{coherent}
@@
 Here, we choose $\ket{\Phi_0}=\ket{0}$ which is vacuum (zero particle) state.
-In the quasispin representation, $\ket{0}=\prod_l \ket{S_l,-S_l}$.
+In the quasispin representation, $\ket{0}=\prod_{\alpha} \ket{S_{\alpha},-S_{\alpha}}$.
 The coherent state is the extension of BCS trail wave function, which consists of the superposition of different particle number states.
-$Z_l$ are complex numbers.
-$|Z_l|=0$ corresponds to empty occupation and $|Z_l|=\infty$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.\par
- With the transformation $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$), the Lagrangian and the expectation value of Hamiltonian become
+$Z_{\alpha}$ are complex numbers.
+$|Z_{\alpha}|=0$ corresponds to empty occupation and $|Z_{\alpha}|=\infty$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.\par
+ With the transformation $Z_{\alpha} = \tan{\frac{\theta_{\alpha}}{2}}e^{-i\chi_{\alpha}}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$), the Lagrangian and the expectation value of Hamiltonian become
 \begin{align}
 	\mathcal{L}(t) =& \braket{Z(t)|i\hbar\frac{\partial}{\partial t}-H|Z(t)}
-	=\sum_l j_l\dot{\chi_l} - \mathcal{H}(\chi,j) ,\\
+	=\sum_{\alpha} j_{\alpha}\dot{\chi_{\alpha}} - \mathcal{H}(\chi,j) ,\\
 	\mathcal{H}(\chi,j) \equiv& \braket{Z(t)|H|Z(t)} \nonumber \\
-	=& \sum_l \epsilon_l\nu_l + \sum_l 2\epsilon_lj_l - g\sum_l \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
-	&- 2g\sum_{l_1<l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   ,
+	=& \sum_{\alpha} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha} 2\epsilon_{\alpha}j_{\alpha} - g\sum_{\alpha} \left( (\Omega_{\alpha}-\nu_{\alpha}) j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber \\
+	&- 2g\sum_{\alpha<\beta} \sqrt{j_{\alpha}j_{\beta}(\Omega_{\alpha}-\nu_{\alpha}-j_{\alpha})(\Omega_{\beta}-\nu_{\beta}-j_{\beta})}\cos{(\chi_{\alpha}-\chi_{\beta})}   ,
 	\label{Hamiltonian}
 \end{align}
-where $\chi_l$ are the canonical coordinates and $j_l$ are the conjugate momenta defined in
-\begin{align}
-  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=S_l(1-\cos{\theta}_l) .
+where $\chi_{\alpha}$ are the canonical coordinates and $j_{\alpha}$ are the conjugate momenta defined in
+\begin{align}
+  j_{\alpha}\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_{\alpha}}=S_{\alpha}(1-\cos{\theta}_{\alpha}) .
   \label{momenta}
@@
 The canonical variables $(\chi,j)$ have clear physical meaning.
-$\chi_l$ represent a kind of gauge angle of each level, and $j_l$ correspond to the occupation number of each level
-\begin{align}
-  \braket{Z|n_l|Z} = \nu_l + 2j_l .
+$\chi_{\alpha}$ represent a kind of gauge angle of each level, and $j_{\alpha}$ correspond to the occupation number of each level
+\begin{align}
+  \braket{Z|n_{\alpha}|Z} = \nu_{\alpha} + 2j_{\alpha} .
   \label{occ}
 \end{align}
-From (\ref{momenta}), we can find that $0\le j_l\le 2S_l$, where $j_l=0$ corresponds to empty occupation and $j_l=2S_l$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.
+From (\ref{momenta}), we can find that $0\le j_{\alpha}\le 2S_{\alpha}$, where $j_{\alpha}=0$ corresponds to empty occupation and $j_{\alpha}=2S_{\alpha}$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.
 Using canonical variables, the TDHFB equations attribute to the Hamilton's equations
 \begin{equation}
-	\dot{\chi_l} = \frac{\partial\mathcal{H}}{\partial j_l}, \quad
-	\dot{j_l} = -\frac{\partial\mathcal{H}}{\partial \chi_l} .
+	\dot{\chi_{\alpha}} = \frac{\partial\mathcal{H}}{\partial j_{\alpha}}, \quad
+	\dot{j_{\alpha}} = -\frac{\partial\mathcal{H}}{\partial \chi_{\alpha}} .
 \end{equation}
@@
 \begin{align}
-	J \equiv \sum_l j_l .
+	J \equiv \sum_{\alpha} j_{\alpha} .
 \end{align}
@@
 \begin{align}
-	\{\mathcal{H},J\}_{PB} &= \sum_l \left(
-	\frac{\partial\mathcal{H}}{\partial\chi_l}\frac{\partial J}{\partial j_l}
-	- \frac{\partial\mathcal{H}}{\partial j_l}\frac{\partial J}{\partial \chi_l} \right) \nonumber \\
-	&= \sum_l \frac{\partial\mathcal{H}}{\partial\chi_l} \nonumber \\
-	&= \sum_l 2g \sum_{l'\neq l} \sqrt{j_{l}j_{l'}(\Omega_{l}-\nu_{l}-j_{l})(\Omega_{l'}-\nu_{l'}-j_{l'})}\sin{(\chi_{l}-\chi_{l'})} \nonumber \\
+	\{\mathcal{H},J\}_{PB} &= \sum_{\alpha} \left(
+	\frac{\partial\mathcal{H}}{\partial\chi_{\alpha}}\frac{\partial J}{\partial j_{\alpha}}
+	- \frac{\partial\mathcal{H}}{\partial j_{\alpha}}\frac{\partial J}{\partial \chi_{\alpha}} \right) \nonumber \\
+	&= \sum_{\alpha} \frac{\partial\mathcal{H}}{\partial\chi_{\alpha}} \nonumber \\
+	&= \sum_{\alpha} 2g \sum_{\beta\neq \alpha} \sqrt{j_{\alpha}j_{\beta}(\Omega_{\alpha}-\nu_{\alpha}-j_{\alpha})(\Omega_{\beta}-\nu_{\beta}-j_{\beta})}\sin{(\chi_{\alpha}-\chi_{\beta})} \nonumber \\
 	&= 0 .
@@
 Actually, $J$ correspond to a conjugate momentum with respect to a global gauge angle $\Phi$.
-We note that $\Phi$ is not necessarily becoming $\Phi=\sum_l \chi_l/L$ because the explicit form of $\Phi$ depends on the coordinate transformation.
+We note that $\Phi$ is not necessarily becoming $\Phi=\sum_{\alpha} \chi_{\alpha}/L$ because the explicit form of $\Phi$ depends on the coordinate transformation.
 In other words, the condition of total particle number conservation cannot determine the form of $\Phi$ uniquely.
@@
 The pairing rotational band is exactly parabolic.
-In multi-level system, the coupling constant $g$ and single-particle energy $\epsilon_l$ affects significantly to the last term in (\ref{Hamiltonian}).
+In multi-level system, the coupling constant $g$ and single-particle energy $\epsilon_{\alpha}$ affects significantly to the last term in (\ref{Hamiltonian}).
 The parabolic structure will be broken when the shell effect is strong.
@@
 The degrees of freedom is $L-1$ in $L$ level system.
-In multi-level pairing model, therefore, the dynamics is integrable for $L=2$ and non-integrable for $L\le 3$.
+In multi-level pairing model, therefore, the dynamics is integrable for $L=2$ and non-integrable for $L\ge 3$.
 We discuss the integrable system and non-integrable system in Chapter \ref{integrable} and \ref{non-integrable}, respectively.
@@
 \begin{align}
-	J = \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} =  \sum_{l=1}^2 j_l, 
+	J = \frac{\partial\mathcal{L}}{\partial\dot{\Phi}} =  \sum_{\alpha=1}^2 j_{\alpha}, 
  \quad\quad
@@
 	\mathcal{H}(\phi,j;J)
-	=& \sum_{l=1,2} \epsilon_l\nu_l + \sum_{l=1,2} 2\epsilon_lj_l - g\sum_{l=1,2} \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	=& \sum_{\alpha=1,2} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha=1,2} 2\epsilon_{\alpha}j_{\alpha} - g\sum_{\alpha=1,2} \left( (\Omega_{\alpha}-\nu_{\alpha}) j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber \\
 	&- 2g\sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})}\cos{\phi} , 
@@
 	V(j) = \mathcal{H}(\phi=0,j) 
-	=& \sum_{l=1,2} \epsilon_l\nu_l + \sum_{l=1,2} 2\epsilon_lj_l - g\sum_{l=1,2} \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	=& \sum_{\alpha=1,2} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha=1,2} 2\epsilon_{\alpha}j_{\alpha} - g\sum_{\alpha=1,2} \left( (\Omega_{\alpha}-\nu_{\alpha}) j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber
+	\label{potential_two_level} \\
 	&- 2g\sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})} \\
@@
 \section{Requantization methods}
+\label{3-2}
 To obtain quantum states from TDHFB dynamics, quantization of the TDHFB trajectories, namely, requantization is necessary procedure.
 We emphasize that there are infinite quantum pictures corresponding to one classical picture.
-Different quantization methods lead different quantum states.
+Different quantization methods lead to different quantum states.
 The straightforward requantization method is canonical quantization, which is commonly applied into nuclear collective model.
@@
 	e^{i\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z')} \psi(Z') ,
-	\label{SPA}
+%	\label{SPA}
 \end{equation}
@@
 \begin{align}
-	Z(t) &= \{Z_l(t);l=1,\cdots,M \} \nonumber \\
+	Z(t) &= \{Z_{\alpha}(t);\alpha=1,\cdots,M \} \nonumber \\
 	&\rightarrow
@@
 \begin{align}
-%	d\mu(Z) &= \prod_{l=1,2} \frac{S_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
-%  &= \prod_l \frac{S_l+1}{4\pi}\sin{\theta_l}d\theta_ld\phi_l \\
-%  &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi .
-d\mu(Z) &= \prod_l \frac{\Omega_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
-  &= \prod_l \frac{\Omega_l+1}{4\pi}d\cos{\theta_l}d\chi_l \\
-	&= \left(\prod_{l=1,2} \frac{1+\Omega_l^{-1}}{2\pi}\right)
+d\mu(Z) &= \prod_{\alpha=1,2} \frac{\Omega_{\alpha}+1}{\pi}(1+|Z_{\alpha}|^2)^{-2}d({\rm Re}Z_{\alpha})d({\rm Im}Z_{\alpha}) \nonumber \\
+  &= \prod_{\alpha=1,2} \frac{\Omega_{\alpha}+1}{4\pi}d(\cos{\theta_{\alpha}})d\chi_{\alpha} \nonumber \\
+	&= \left(\prod_{\alpha=1,2} \frac{1+\Omega_{\alpha}^{-1}}{2\pi}\right)
              d\Phi dJ d\phi dj .
@@
 \end{align}
-with $S_l=(\Omega_l-\nu_l)/2$ and the coefficients
+with $S_{\alpha}=(\Omega_{\alpha}-\nu_{\alpha})/2$ and the coefficients
 \begin{align}
@@
 but also for excited states.
-See Appendix for detailed derivation of Eq.~(\ref{semi_wave_func1}).
+See Appendix \ref{wave_func1} for detailed derivation of Eq.~(\ref{semi_wave_func1}).
 
@@
 can be calculated in a straightforward manner.
-In Sec.~\ref{sec:results}, we show those of the pair-addition operator
+In Sec.~\ref{3-3}, we show those of the pair-addition operator
 $S^+$ which characterize properties of the pair condensates.
@@
 	\mathcal{H}(\hat{\phi},\hat{j};\hat{J})
-	=& \sum_{l=1,2} \epsilon_l\nu_l + \sum_{l=1,2} 2\epsilon_lj_l - g\sum_{l=1,2} \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
+	=& \sum_{\alpha=1,2} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha=1,2} 2\epsilon_{\alpha}j_{\alpha} - g\sum_{\alpha=1,2} \left( (\Omega_{\alpha}-\nu_{\alpha}) j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber \\
 	&- g \left\{ \sqrt{j_1j_2(\Omega_{1}-\nu_{1}-j_{1})(\Omega_{2}-\nu_{2}-j_{2})}\cos{\hat{\phi}} \right. \nonumber \\
@@
 \end{align}
-as in (\ref{j_l}), $j_l$ contain $J$ and $j$ which
+as in (\ref{j_l}), $j_{\alpha}$ contain $J$ and $j$ which
 are replaced by
@@
 in Eq. (\ref{canonical_quantized_H}) vanishes
-for $j_l=0$ and $j_l=\Omega_l-\nu_l$,
+for $j_{\alpha}=0$ and $j_{\alpha}=\Omega_{\alpha}-\nu_{\alpha}$,
 which restricts values of $j$ in a finite range of
@@
 
-We apply the requantization methods in Sec.~\ref{sec:requantization}.
+We apply the requantization methods in Sec.~\ref{3-2}.
 In the following, the stationary-phase approximation to the path
@@
 
-\subsubsection{Mid-shell configuration}
+\subsubsection{(a) Mid-shell configuration}
 
@@
 
-\subsubsection{Closed-shell configuration}
+\subsubsection{(b) Closed-shell configuration}
 
@@
 
+From the study of various requantization methods for the two-level pairing model,
+canonical quantization and Fourier decomposition often fail to produce an approximate value to the exact solution.
+In contrast,
+the stationary-phase approximation (SPA) to the path integral \cite{SM88} 
+can give quantitative results not only for the excitation energies, 
+but also for the wave functions and two-particle-transfer strengths.
+The quantized states obtained in the SPA have two advantages;
+first, the wave functions are given directly in terms of
+the microscopic degrees of freedom, and second,
+the restoration of the broken symmetries are automatic.
+In the pairing model, the quantized states are eigenstates of the particle-number
+operator.
+On the other hand, applications of the SPA have been limited to
+integrable systems.
+This is because we need to find separable periodic trajectories on a classical
+torus.
+Since the nuclear systems, of course, correspond to non-integrable systems,
+a straightforward application of the SPA is not possible.
+
+%this work
+In this chapter,
+we propose a new approach of the SPA applicable to the non-integrable systems,
+which is based on the extraction of the one-dimensional (1D)
+collective coordinate
+using the adiabatic self-consistent collective coordinate (ASCC) method.
+Since the 1D system is integrable,
+the collective subspace can be quantized with the SPA.
+The optimal degree of freedom associated with a slow collective motion
+is determined self-consistently
+inside the TDHFB space, without any assumption. 
+Thus, our approach of the ASCC+SPA to the pairing model
+basically consists of two steps:
+(1) find a decoupled 1D collective coordinate of the pair vibration,
+in addition to the pair rotational degrees of freedom.
+(2) apply the SPA independently to each collective mode.
+
+We introduce the theoretical framework of the ASCC, SPA,
+and their combination, ASCC+SPA in Sec. \ref{4-1}. 
+In Sec. \ref{4-2}, we provide some details in the application
+of the ASCC+SPA to the multi-level pairing model.
+We give the numerical results in Sec. \ref{4-3}, including
+neutron pair vibrations in Pb isotopes.
+
 \section{Theoretical framework of ASCC+SPA in non-integrable system}
+\label{4-1}
 \subsection{Adiabatic self-consistent collective coordinate method and
@@
 %To discuss the application of ASCC+SPA in the later subsection, 
-In this section,
-we first recapitulate the ASCC method to find a 1D collective coordinate,
+ASCC was developed from the basic idea of the self-consistent collective coordinate (SCC) method \cite{MMSK80}, which can maximum decouple a collective subspace from TDMF phase space.
+Because the collective coordinates are obtained from TDMF dynamics itself without any assumption in ASCC, they are superior than the phenomenological collective coordinates in the collective models.
+In this subsection,
+we recapitulate the ASCC method to find a 1D collective coordinate,
 following the notation of Ref. \cite{N2012}.
 
-As is seen in Sec.~\ref{sec3}, the TDHFB equations can be
+As is seen in Sec.~\ref{4-3}, the TDHFB equations can be
 interpreted as the classical Hamilton's equations of motion
@@
 \end{align}
-
-For multi-level pairing models in Sec.~\ref{sec3}, 
+The Einstein's convention for summation with respect to the repeated
+upper and lower indices is assumed hereafter.
+
+For multi-level pairing models in Sec.~\ref{4-2}, 
 there is a constant of motion in the TDHFB dynamics,
@@
 as Eq. (\ref{q^n}) \cite{Sat18}.
-In this paper, we neglect these higher-order terms, such as
+In this chapter, we neglect these higher-order terms, such as
 $f^{(1)1\alpha\beta}\pi_\alpha\pi_\beta/2$.
@@
 \pi_{\alpha} &= f^1_{,\alpha}p_1 +f^n_{,\alpha}p_n,
- \label{momenta}
+ \label{momenta2}
 \end{align}
@@
 $(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
-The Einstein's convention for summation with respect to the repeated
-upper and lower indices is assumed hereafter.
 The canonical variable condition leads to
@@
 to the path integral.
-In our former study \cite{NN18},
-we have proposed and tested the SPA for an integrable pairing model.
 Since the collective Hamiltonian (\ref{coll}) that is
@@
 
-\subsubsection{Basic idea of ASCC+SPA}
+\subsubsection{(a) Basic idea of ASCC+SPA}
 
@@
 	\oint_{C_k} p_1dq^1 = 2\pi k ,
-	\label{EBK}
+	\label{EBK2}
 \end{equation}
@@
 At each point in the space $(q^1,q^n; p_1,p_n)$ corresponds to
-a generalized Slater determinant
-$\ket{q^1,q^n;p_1,p_n}=\ket{\xi,\pi}$
+a generalized Slater determinant \\
+$\ket{q^1,q^n;p_1,p_n}=\ket{\xi,\pi}$, 
 where $(\xi,\pi)$ are given as
@@
 
-\subsubsection{Notation and practical procedure for quantization}
+\subsubsection{(b) Notation and practical procedure for quantization}
 \label{sec:notation}
 
-For the application of the ASCC+SPA method to the pairing model in Sec.~\ref{sec3},
+For the application of the ASCC+SPA method to the pairing model in Sec.~\ref{4-2},
 we summarize some notations and procedures to obtain quantized states.
 
-In Sec.~\ref{sec3}, the time-dependent generalized Slater determinants
+In Sec.~\ref{4-2}, the time-dependent generalized Slater determinants
 (coherent states) are written as $\ket{Z}$ with complex variables
@@
 $(j^\alpha, -\chi_\alpha)$ that correspond to $(\xi^\alpha,\pi_\alpha)$
-in Sec.~\ref{sec2}.
-$\chi_\alpha$ and $j^\alpha$ correspond to
-the ``angle'' and the ``number'' variables, respectively.
+in Sec.~\ref{4-1}.
+The definition and physical meaning of $\chi_\alpha$ and $j^\alpha$ are explained in Sec. \ref{2-2}.
 %Although it is customary to take the angle as a coordinate,
@@
 correspond to variables of the pair rotation, $-p_n$ and $q^n$, respectively.
-According to the EBK quantization rule (\ref{EBK}),
+According to the EBK quantization rule (\ref{EBK2}),
 the ground state with $k=0$ corresponds to nothing but the HFB state
@@
 \item Find a trajectory $(q^1(t),p_1(t))$ which satisfies
-the $k$-th EBK quantization condition (\ref{EBK}).
+the $k$-th EBK quantization condition (\ref{EBK2}).
 \item Calculate the action integral (\ref{tau}) for the $k$-th trajectory.
@@
 The ASCC provides the 2D collective subspace $(q^1,J)$
-and the generalized coherent states $\ket{\Phi=0,J;q,p=0}$.
-For finite values of momenta, we use Eq.~(\ref{momenta})
+and the generalized coherent states \\
+$\ket{\Phi=0,J;q,p=0}$.
+For finite values of momenta, we use Eq.~(\ref{momenta2})
 to obtain the state $\ket{\Phi,J;q,p}$.
@@
 \section{Application of ASCC+SPA in pairing model}
+\label{4-2}
 
@@
 where the potential $V(j)$ and the reciprocal mass parameter
-$B^{\alpha\beta}(j)$ are given as
-\begin{align}
-  V(j) =& \mathcal{H}(j,\chi=0) \nonumber \\
-	=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left[ \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right] \nonumber \\
-  &- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}, 	
-\end{align}
+$B^{\alpha\beta}(j)$ are given as\footnote{In this thesis, $j^{\alpha}$ and $j_{\alpha}$ are identical.
+Defining the upper index in $j^{\alpha}$ is nothing but to utilize Einstein summation convention.}
 %\begin{align}
 \begin{eqnarray}
-&&B^{\alpha\beta}(j) = \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \\
+  V(j) &=& \mathcal{H}(j,\chi=0) \nonumber \\
+	&=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left[ \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right] \nonumber \\
+  &&- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}, \\	
+B^{\alpha\beta}(j) &=& \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \\
 \label{mass}
-&&=
+&=&
 	\begin{cases}
@@
 \mathcal{T}(\Phi,J;q^1,p_1)
-&= \int_{C_\Phi} \braket{\Phi(t),J;q^1,p_1|i\frac{\partial}{\partial t}|\Phi(t),J;q^1,p_1} dt \nonumber \\
-+ \int_{C_1} &\braket{\Phi,J;q^1(t),p_1(t)|i\frac{\partial}{\partial t}|\Phi,J;q^1(t),p_1(t)} dt
+=& \int_{C_\Phi} \braket{\Phi(t),J;q^1,p_1|i\frac{\partial}{\partial t}|\Phi(t),J;q^1,p_1} dt \nonumber \\
+&+ \int_{C_1} \braket{\Phi,J;q^1(t),p_1(t)|i\frac{\partial}{\partial t}|\Phi,J;q^1(t),p_1(t)} dt
  \nonumber \\
-	&=J\Phi + \int_{C_1} \sum_\alpha j^\alpha d\chi_\alpha
+	=& J\Phi + \int_{C_1} \sum_\alpha j^\alpha d\chi_\alpha
 	\nonumber \\
-	&\equiv \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
+	\equiv& \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
 %	\label{tau}
@@
 \begin{equation}
-  \ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1},
-\end{equation}
-where $\hat{N}=\sum_\alpha \hat{n}_\alpha$.
+  \ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{J}} \ket{J;q^1,p_1},
+\end{equation}
+where 
+\begin{align}
+	\hat{J} = \frac{\hat{N}-\nu}{2} .
+\end{align}
 Then, the action for the trajectory $C_1$ can be also expressed as
@@
   d\mu(Z) &= \prod_\alpha \frac{\Omega_\alpha+1}{\pi} (1+|Z_\alpha|^2)^{-2} d({\rm Re}\,Z) d({\rm Im}\,Z) \nonumber \\
-=& \prod_\alpha \frac{-(\Omega_\alpha+1)}{4\pi} d(\cos{\theta_\alpha}) d\chi_\alpha \nonumber \\
- =& \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} d\chi_\alpha dj^\alpha \nonumber \\
- =& \left[ \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} \right] d\Phi dJ dq^1 dp_1 %\nonumber \\
+&= \prod_\alpha \frac{-(\Omega_\alpha+1)}{4\pi} d(\cos{\theta_\alpha}) d\chi_\alpha \nonumber \\
+ &= \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} d\chi_\alpha dj^\alpha \nonumber \\
+ &= \left[ \prod_\alpha \frac{1+\Omega_\alpha^{-1}}{2\pi} \right] d\Phi dJ dq^1 dp_1 %\nonumber \\
   \prod_a dq^a dp_a,
@@
 %\begin{align}
-%  \ket{\Phi,J;q,p} &= \sum_{\{j_l\}} e^{-i\Phi \sum_l j_l} \ket{J;q,p} .
+%  \ket{\Phi,J;q,p} &= \sum_{\{j_{\alpha}\}} e^{-i\Phi \sum_{\alpha} j_{\alpha}} \ket{J;q,p} .
 %\end{align}
@@
 \ket{Z} &= 
-\sum_{\{m_\alpha\}} A_m(Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots}, \nonumber\\
+\sum_{\{m_\alpha\}} A_m(Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
 \end{align}
@@
  =& \prod_\alpha \left(\frac{1-\cos{\theta}_\alpha}{2}\right)^{m_\alpha/2}\left(\frac{1+\cos{\theta}_\alpha}{2}\right)^{(\Omega_\alpha-m_\alpha)/2}
-  \nonumber \\
-  &\times\sqrt{\frac{\Omega_\alpha!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
+\sqrt{\frac{\Omega_\alpha!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
 	\label{A_m}
@@
 	=& \sum_{\{m_\alpha\}}
-	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \nonumber \\
-&\times \oint dt e^{i\mathcal{T}_1}(t) B_m (Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots} \nonumber \\
+	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \oint dt e^{i\mathcal{T}_1}(t) B_m (Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots} \nonumber \\
  \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
@@
 It is easy to find that $J$ must be integer,
-according to the quantization rule (\ref{EBK}) for the $(J,\Phi)$ sector.
+according to the quantization rule (\ref{EBK2}) for the $(J,\Phi)$ sector.
 
@@
 in the $(q^1,p_1)$ sector,
-namely, the HFB state $\ket{\Phi,J;q,p}=e^{-i\Phi\hat{N}/2}\ket{\rm HFB}$.
+namely, the HFB state $\ket{\Phi,J;q,p}=e^{-i\Phi\hat{J}}\ket{\rm HFB}$.
 Nevertheless, the rotational motion in $\Phi(t)$ is present,
@@
 \section{Result}
-In the pairing model in Sec.~\ref{sec3},
+\label{4-3}
+In the pairing model in Chap.~\ref{chap2},
 the number of TDHFB degrees of freedom equals that of single-particle levels.
@@
 \caption{Classical trajectories satisfying the EBK quantization condition
-(\ref{EBK}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
+(\ref{EBK2}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
 %The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$. 
@@
 }
- \label{fig:N16_occ}
+ \label{fig:N16_occ2}
 \end{figure}
@@
 Calculated trajectories that satisfy the EBK quantization condition
-(\ref{EBK}) for the first and second excited states ($0_2^+$ and $0_3^+$)
+(\ref{EBK2}) for the first and second excited states ($0_2^+$ and $0_3^+$)
 are mapped onto the $(\phi,j)$ plane and
@@
 The calculated wave functions for the excited $0^+$ states 
-are shown in Fig. \ref{fig:N16_occ}. 
+are shown in Fig. \ref{fig:N16_occ2}. 
 We show the occupation probabilities which are decomposed 
@@
 %\mathcal{H} 
-%  =& \sum_{l=1,2} \epsilon_l\Omega_l(1- \cos{\theta}_l)& \nonumber \\ 
-% &- \frac{g}{4}\sum_{l=1,2} \Omega_l [\Omega_l(1-\cos^2{\theta}_l)+(1-\cos{\theta}_l)^2] \nonumber \\
-%- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{l_1})(1-\cos^2{\theta}_{l_2})}\cos{(\chi_{2}-\chi_{1})}   .
+%  =& \sum_{\alpha=1,2} \epsilon_{\alpha}\Omega_{\alpha}(1- \cos{\theta}_{\alpha})& \nonumber \\ 
+% &- \frac{g}{4}\sum_{\alpha=1,2} \Omega_{\alpha} [\Omega_{\alpha}(1-\cos^2{\theta}_{\alpha})+(1-\cos{\theta}_{\alpha})^2] \nonumber \\
+%- \frac{g}{2} \Omega_{1}\Omega_{2}&\sqrt{(1-\cos^2{\theta}_{\alpha})(1-\cos^2{\theta}_{\beta})}\cos{(\chi_{2}-\chi_{1})}   .
 %\end{align}
@@
 \begin{table}[htbp]
+\begin{center}
 \caption{Calculated excitation energies of the first and the second
@@
 \begin{tabular}{c|cccccc}
+\toprule
             $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
@@
 ASCC+SPA (2nd exc.)& $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
-Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$
+Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$ \\
+\bottomrule
 \end{tabular}
+\end{center}
 \end{table}
@@
 Table \ref{ex} shows the excitation energies of the first and second
-excited states, determined by the EBK quantization condition (\ref{EBK}).
+excited states, determined by the EBK quantization condition (\ref{EBK2}).
 Comparing the result of the ASCC+SPA with that of the exact calculation,
@@
 \begin{table}[tb]
+\begin{center}
 \caption{Single-particle energies of Pb isotopes used in the calculation
@@
 \begin{tabular}{c|cccccc}
+  \toprule 
   orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
   energy(MeV)& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
+  \bottomrule 
 \end{tabular}
 \label{Pb}
+\end{center}
 \end{table}
@@
 We encounter another kind of problem for $^{196}$Pb,
-which will be discussed in Sec.~\ref{sec5}.
+which will be discussed in Chapter~\ref{??}.
 Therefore, in this paper, we calculate the first excited states
@@
 \begin{table}[bt]
+\begin{center}
 \caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
 \begin{tabular}{c|cccccc}
+  \toprule
    & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
 ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
-Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
+Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$ \\
+  \bottomrule
 \end{tabular}
 \label{Pb_ex}
+\end{center}
 \end{table}
@@
 \cite{BBPK70,GPBW85, ZPPRS99, P07}.
-For those studies, the pairing gap parameter $\Delta$ (or equivalent quantities)
-is assumed to be the collective coordinates.
+For those studies, the pairing collective Hamiltonian is constructed
+in terms of the pairing gap parameter $\Delta$ (or equivalent quantities) 
+and the gauge angle $\Phi$.  
 This is analogous to the Bohr collective model,
@@
 
-Although the global gauge angle $\Phi$ is arbitrary,
-the deformation parameter $\alpha\equiv \braket{ \hat{S}^- }$
-in the gauge space is
-usually taken as a real value ($\Phi=0$).
-%In the superfluid phase, 
-The energy minimization with a fixed value of real $\alpha$ always
-leads to $\phi=0$.
-\begin{align}
-\alpha(j,J) = \braket{Z_0|\hat{S}^-|Z_0}
-	= \sqrt{j_1(\Omega_1-\nu_1-j_1)} +\sqrt{j_2(\Omega_2-\nu_2-j_2)}.
+Because pairing rotation is trivial, we only consider the collective coordinate for pairing vibration. The deformation parameter is defined in $\alpha\equiv \braket{ \hat{S}^- }$. 
+To consider pairing vibration only, we fix the gauge angle as $\Phi=0$.
+With $\Phi=0$, the energy minimization with a fixed value of real $\alpha$ always
+leads to $\chi_{\alpha}=0$.
+\begin{align}
+\alpha(j) = \left. \braket{Z|\hat{S}^-|Z} \right|_{\chi=0}
+	= \sum_{\alpha} \sqrt{j_{\alpha}(\Omega_{\alpha}-\nu_{\alpha}-j_{\alpha})} .
+ \label{Delta}
+\end{align}
+The parameter $\alpha$ is equivalent to the pairing gap $\Delta$,
+since the relation, $\Delta=g\alpha$,
+guarantees one-to-one correspondence between $\alpha$ and $\Delta$.
+
+\section{Integrable system}
+In Chapter~\ref{integrable}, we treat $(\phi, j)$ as canonical variables to describe pairing vibration.
+The collective model treatment is based on the choice,
+$j$ as a coordinate and $\phi$ as a momentum, as discussed in Sec. \ref{ATDHFB}.
+\begin{align}
+\alpha(j) = \braket{Z|\hat{S}^-|Z}
+	= \sqrt{j_1(\Omega_1-\nu_1-j_1)} +\sqrt{j_2(\Omega_2-\nu_2-j_2)},
  \label{Delta_BCS}
 \end{align}
-The parameter $\alpha$ is equivalent to the pairing gap $\Delta$,
-since the relation, $\Delta=G\alpha$,
-guarantees one-to-one correspondence between $\alpha$ and $\Delta$.
-
-\section{Integrable system}
-In Sec.~\ref{sec:canonical}, we treat $\phi$ as a collective coordinate
-and $j$ as its conjugate momentum.
-The collective model treatment is based on the opposite choice,
-$j$ as a coordinate and $\phi$ as a momentum, as discussed in Sec. \ref{ATDHFB}.
+where $j_1$ and $j_2$ are the function of $j$ as in (\ref{j_l}).
 
@@
  \end{center}
- \caption{Energy surfaces as functions of $j$,
- Eq. (\ref{TDHFB_Hamiltonian_3}) with $\phi=0$,
- for $x=0.5$, $2$, and $3.2$.
+ \caption{Potential surfaces as functions of $j$,
+ Eq. (\ref{potential_two_level}) for $x=0.5$, $2$, and $3.2$.
  Dashed line is the pairing deformation parameter $\alpha$
@@
  \label{fig:p_Delta}
+\end{figure}
+
+\begin{figure}[tb]
+% \begin{minipage}{0.45\hsize}
+ \begin{center}
+(a) \includegraphics[height=0.4\textwidth,angle=-90]{images/N50Xeq2p4gap_E.eps}
+% \end{center}
+% \end{minipage}
+% \begin{minipage}{0.45\hsize}
+% \begin{center}
+(b) \includegraphics[height=0.4\textwidth,angle=-90]{images/N16Xeq2p4gap_E.eps}
+ \end{center}
+%\end{minipage}
+\caption{Potential energy surface as functions of $\alpha$ with $x=2.4$;
+(a) $\Omega=N=50$,
+(b) $2\Omega=N=16$.
+Horizontal lines 
+indicate energy spectra. Black lines are obtained
+from the potential energy surface, and green lines are 
+obtained with the CQ method
+(Sec.~\ref{sec:canonical}).
+%Left panels: $\Omega=50$, $N=50$ system;
+% Right panels: $\Omega=8$, $N=16$ system.
+}
+ \label{fig:Delta_E}
 \end{figure}
@@
 in the $j<0$ region.
-The potential energy, $E(j)=\mathcal{H}(\phi=0,j;J=N/2)$ of
-Eq. (\ref{TDHFB_Hamiltonian_3}), is also shown in
+The potential energy, $V(j)=\mathcal{H}(\phi=0,j;J=N/2)$ of
+Eq. (\ref{potential_two_level}), is also shown in
 Fig.~\ref{fig:p_Delta}.
@@
 
-\begin{figure}[tb]
-% \begin{minipage}{0.45\hsize}
- \begin{center}
-(a) \includegraphics[height=0.4\textwidth,angle=-90]{images/N50Xeq2p4gap_E.eps}
-% \end{center}
-% \end{minipage}
-% \begin{minipage}{0.45\hsize}
-% \begin{center}
-(b) \includegraphics[height=0.4\textwidth,angle=-90]{images/N16Xeq2p4gap_E.eps}
- \end{center}
-%\end{minipage}
-\caption{Potential energy surface as functions of $\alpha$ with $x=2.4$;
-(a) $\Omega=N=50$,
-(b) $2\Omega=N=16$.
-Horizontal lines 
-indicate energy spectra. Black lines are obtained
-from the potential energy surface, and green lines are 
-obtained with the CQ method
-(Sec.~\ref{sec:canonical}).
-%Left panels: $\Omega=50$, $N=50$ system;
-% Right panels: $\Omega=8$, $N=16$ system.
-}
- \label{fig:Delta_E}
-\end{figure}
-
-\section{non-integrable system}
-Finally, we discuss the validity of the collective model approach
-assuming the pairing gap as a collective coordinate.
-The 5D collective Hamiltonian assuming the quadrupole deformation
-parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,$ and $0)$ as the collective coordinates
-is widely utilized to analyze experimental data of quadrupole states.
-Similarly, we may construct the pairing collective Hamiltonian
-in terms of the pairing gap $\Delta$ and the gauge angle $\Phi$. 
+\section{Non-integrable system}
+In Chapter~\ref{non-integrable}, the collective canonical variables $(q^1, p_1)$ describing pairing vibration are obtained from ASCC.
 As far as there is a one-to-one correspondence between $\Delta$ 
-and the collective variable $q^1$ we obtained in the present study,
+and the collective variable $q^1$,
 we can transform the collective Hamiltonian in $(q^1,\Phi)$
 into the one in $(\Delta,\Phi)$.
-The pairing gap $\Delta$ is defined as
-\begin{align}
-  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|\hat{S}^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
-  &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
-\end{align}
-Figure \ref{192Pb_gap} shows the pairing gap $\Delta$ in ${}^{192}$Pb
-as a function of the collective coordinate $q^1$.
-The peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
+As integrable system, however, we cannot map the entire region of $q^1$ to $\Delta$ because the peak values of pairing gap parameter always appear around the middle of the collective path.
+
+%The pairing gap $\Delta$ is defined as
+%\begin{align}
+ % \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|\hat{S}^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
+%  &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
+%\end{align}
+
+In Fig. \ref{q_Delta}, we show two examples of the behavior of pairing gap parameter as a function of the collective coordinate $q^1$.
+Panel (a) corresponds to the case of $N=20$ in three-level system ($\Omega_1=\Omega_2=\Omega_3=8$,
+$\epsilon_1=-\epsilon_0$, $\epsilon_2=0$, $\epsilon_3=1.5\epsilon_0$,
+and $g=0.2\epsilon_0$), and panel (b) corresponds to the case of ${}^{192}$Pb ($g=0.138$ MeV and single-particle level shown in Table \ref{Pb}).
+In both panels, the peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
 function of $q^1$, thus no one-to-one correspondence exists. 
-The same behavior is observed for other Pb isotopes too.
-Therefore, the pairing gap $\Delta$ is not a suitable collective coordinate
-to describe the pairing dynamics in the multi-level model.
+Because the peak in $\Delta$ emerges near the energy minimum point, the potential surface of $\Delta$ is too shallow to bound first excited states. 
+The same behavior observed for all of the non-integrable systems.
+The situations are similar to the case in Fig. \ref{fig:Delta_E} (b), where the low-lying excited states cannot be properly described.
+
+We conclude that the pairing gap parameter $\Delta$ (or equivalent quantities) is not a suitable collective coordinate to describe the pairing dynamics, in the multi-level pairing model.
 
@@
 
-\begin{figure}[t]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/192Pbgap.eps}
- \end{center}
-	\caption{Pairing gap as a function of collective coordinate $q^1$
-	in ${}^{192}$Pb. 
+\begin{figure}[tb]
+ \begin{center}
+(a) \includegraphics[height=0.44\textwidth,angle=-90]{images/N20gap.eps}
+(b) \includegraphics[height=0.44\textwidth,angle=-90]{images/192Pbgap.eps}
+ \end{center}
+ \caption{Solid line is the potential surface as a function of $q^1$, and
+ dashed line is the pairing gap parameter $\Delta$
+ of Eq.~(\ref{Delta}) as a function of $q^1$.
+ (a) $N=20$ in three-level system ($\Omega_1=\Omega_2=\Omega_3=8$,
+$\epsilon_1=-\epsilon_0$, $\epsilon_2=0$, $\epsilon_3=1.5\epsilon_0$,
+and $g=0.2\epsilon_0$), (b) ${}^{192}$Pb ($g=0.138$ MeV and single-particle level shown in Table \ref{Pb}).
 }
- \label{192Pb_gap}
+ \label{q_Delta}
 \end{figure}
@@
 
-We studied the low-lying excited $0^+$ states in multi-level pairing model.
-We constructed theoretical framework to describe pairing collective motion in large-amplitude regime.
-The approach roughly consists of two steps: (1) solve the TDHFB equation to obtain the classical trajectories; (2) requantize the TDHFB trajectories to obtain the excited states.
-The TDHFB degrees of freedom equal to the number of single-particle level.
-More specifically, the TDHFB degrees of freedom consists of one constant of motion, pairing rotation, and $L-1$ time-dependent degrees of freedom in $L$ single-particle level system.
-Therefore, we divided the pairing system into two classes, two-level system corresponding to the integrable system and the system more than three-level corresponding to the non-integrable system.
-
-In two-level system, integrable system, we studied three different methods of requantization of TDHFB, the stationary-phase approximation (SPA) of the path integral, the canonical quantization (CQ), and the Fourier decomposition(FD) of the time-dependent observables.
+In order to construct a theoretical framework to describe large-amplitude collective motion associated with nuclear pairing, apart from realistic nuclear system, we studied the low-lying excited $0^+$ states in multi-level pairing model.
+Based on the time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, we constructed the pairing collective excited states in two steps: (1) solve the TDHFB equation to obtain the TDHFB classical trajectories; (2) requantize the TDHFB trajectories to obtain the excited states.
+In step 1, we found the TDHFB degrees of freedom equal to the number of single-particle level.
+More specifically, the TDHFB degrees of freedom consists of one constant of motion, pairing rotation described in variables $(\Phi, J)$, and $L-1$ time-dependent degrees of freedom in $L$ single-particle level system.
+To apply the step 2, we divided the pairing system into two classes, two-level system corresponding to the integrable system and the system more than three-level corresponding to the non-integrable system.
+
+Two-level system corresponds to integrable system because there is only one time-dependent degree of freedom.
+After the explicit coordinate transformation decoupling the constant of motion, pairing rotation described by $(\Phi, J)$, we obtain the time-dependent variables $(\phi, j)$ describing pairing vibration.
+Under the transformed canonical variables, we studied three different methods of requantization of TDHFB, the stationary-phase approximation (SPA) to the path integral, the canonical quantization (CQ), and the Fourier decomposition (FD) of the time-dependent observables.
+
+To test the performance of each requantization method, we considered two classes of systems, large systems with large degeneracy $\Omega$ and number of particles $N$, and small systems which are comparable with the valence orbits in realistic nuclear systems.
+In the former case, all the quantization methods reasonably reproduced the results of the
+exact calculation not only for excitation spectra, but also for two-particle transfer matrix elements.
+In the later case, on the other hand, the agreement is
+less quantitative for the CQ and the FD, especially for the twoparticle
+transfer matrix elements.
+In contrast, the SPA keeps its accuracy in the entire range of
+pairing strengths.
+One of the reasons of its success is due to the inclusion of the off-diagonal 
+parts of the pair transfer operator,
+by the explicit construction of the microscopic wave functions.
+The CQ and FD calculate the pair transfer matrix elements using only
+the diagonal part (expectation value) of the operator $\hat{S}^\pm$,
+based on Eqs. (\ref{Sp_mean_value}) and (\ref{Sm_mean_value}).
+This is a good approximation when the collectivity is so large that the
+diagonal parts dominate.
+However, the pairing collectivity may be too weak to justify this
+treatment.
+Thus, the SPA is the most accurate tool for description of the pairing collective motions in large-amplitude regime.
+
+The weak point of this approach is that it is applicable only to the
+integrable TDHFB system.
+To overcome this problem, we proposed the ASCC+SPA method for non-integrable systems.
+The concept is that we can employ ASCC to decouple an integrable collective subspace from original TDHFB phase space, then, the SPA is available for the collective subspace.
+In this approach, we use the ASCC method to extract the 2D
+collective subspace including the pair rotation.
+In other words, we extract an approximate integrable system 
+in the non-integrable system described by $(q^1,p_1;J,\Phi)$.
+
+We applied the ASCC+SPA method to the multi-level pairing model.
+We investigated the three-level model and 
+the multi-level model simulating Pb isotopes
+with a realistic pairing coupling constant $g$ and single-particle levels.
+In both cases, the low-lying excited $0^+$ states obtained with
+the ASCC+SPA well reproduce the exact solutions
+not only of the excitation energies but also of the wave functions.
+In the ASCC+SPA, the pair-transition calculation is straightforward,
+because we have a microscopic wave function for every quantized state.
+This overcomes a disadvantage in the conventional canonical requantization
+in which we need to construct a pair-transition operator
+in terms of the collective variables only.
+
+We also investigated the conventional treatment of the
+collective model which assumes that the collective coordinate
+is the paring gap parameter.
 
@@
   \hat{S}^0\ket{S,S^0} &= S^0\ket{S,S^0} .
-  \label{S_0}
+%  \label{S_0}
 \end{align}
@@
 \begin{align}
-  \braket{Z|\hat{S}^+\hat{S}^-|Z} &= \sum_{l_1l_2}\braket{Z|\hat{S}_{l_2}^+\hat{S}_{l_1}^-|Z} .
-\end{align}
-When $l_2=l_1$, the form is the same as in (\ref{S+S-}). When $l_2\ne l_1$, from (\ref{S+}) and (\ref{S-}),
-\begin{align}
-  \braket{Z|S_{l_2}^+S_{l_1}^-|Z} = \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2} .
+  \braket{Z|\hat{S}^+\hat{S}^-|Z} &= \sum_{\alpha\beta}\braket{Z|\hat{S}_{\beta}^+\hat{S}_{\alpha}^-|Z} .
+\end{align}
+When $\beta=\alpha$, the form is the same as in (\ref{S+S-}). When $\beta\ne \alpha$, from (\ref{S+}) and (\ref{S-}),
+\begin{align}
+  \braket{Z|S_{\beta}^+S_{\alpha}^-|Z} = \frac{2S_{\alpha}Z_{\alpha}}{1+|Z_{\alpha}|^2}\frac{2S_{\beta}Z_{\beta}^*}{1+|Z_{\beta}|^2} .
 \end{align}
@@
 \begin{align}
-    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_l 2S_l|Z_l|^2\frac{2S_l+|Z_l|^2}{(1+|Z_l|^2)^2}
-    + \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2} .
+    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_{\alpha} 2S_{\alpha}|Z_{\alpha}|^2\frac{2S_{\alpha}+|Z_{\alpha}|^2}{(1+|Z_{\alpha}|^2)^2}
+    + \sum_{\alpha \neq \beta} \frac{2S_{\alpha}Z_{\alpha}}{1+|Z_{\alpha}|^2}\frac{2S_{\beta}Z_{\beta}^*}{1+|Z_{\beta}|^2} .
 \end{align}
@@
 \begin{equation}
-	\ket{Z} = \prod_{l} \left(1+|Z_l|^2\right)^{-S_l}
-	e^{Z_l \hat{S}_l^{+}} \ket{S_l, S_l^0=-S_l} .
- \label{coherent}
+	\ket{Z} = \prod_{\alpha} \left(1+|Z_{\alpha}|^2\right)^{-S_{\alpha}}
+	e^{Z_{\alpha} \hat{S}_{\alpha}^{+}} \ket{S_{\alpha}, S_{\alpha}^0=-S_{\alpha}} .%
+% \label{coherent}
 \end{equation}
@@
 \begin{equation}
-	  \braket{\eta|Z} = \prod_l \frac{(1+\eta_l^*Z_l)^{2S_l}}{(1+|\eta_l|^2)^{S_l}(1+|Z_l|^2)^{S_l}} .
+	  \braket{\eta|Z} = \prod_{\alpha} \frac{(1+\eta_{\alpha}^*Z_{\alpha})^{2S_{\alpha}}}{(1+|\eta_{\alpha}|^2)^{S_{\alpha}}(1+|Z_{\alpha}|^2)^{S_{\alpha}}} .
   \label{overlap}
@@
 \begin{equation}
-     \braket{Z|\hat{S}^0|Z} = \sum_l S_l\left( 1-\frac{2}{1+|Z_l|^2} \right)
+     \braket{Z|\hat{S}^0|Z} = \sum_{\alpha} S_{\alpha}\left( 1-\frac{2}{1+|Z_{\alpha}|^2} \right)
 \end{equation}
@@
 \begin{equation}
-     \braket{Z|\hat{S}^+|Z} = \sum_l \frac{2S_lZ_l^*}{1+|Z_l|^2}
+     \braket{Z|\hat{S}^+|Z} = \sum_{\alpha} \frac{2S_{\alpha}Z_{\alpha}^*}{1+|Z_{\alpha}|^2}
 \end{equation}
@@
 \begin{equation}
-     \braket{Z|\hat{S}^-|Z} = \sum_l \frac{2S_lZ_l}{1+|Z_l|^2}
+     \braket{Z|\hat{S}^-|Z} = \sum_{\alpha} \frac{2S_{\alpha}Z_{\alpha}}{1+|Z_{\alpha}|^2}
 \end{equation}
@@
 \begin{equation}
-    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_l 2S_l|Z_l|^2\frac{2S_l+|Z_l|^2}{(1+|Z_l|^2)^2}
-    + \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}
+    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_{\alpha} 2S_{\alpha}|Z_{\alpha}|^2\frac{2S_{\alpha}+|Z_{\alpha}|^2}{(1+|Z_{\alpha}|^2)^2}
+    + \sum_{\alpha \neq \beta} \frac{2S_{\alpha}Z_{\alpha}}{1+|Z_{\alpha}|^2}\frac{2S_{\beta}Z_{\beta}^*}{1+|Z_{\beta}|^2}
 \end{equation}
@@
 \begin{equation}
-       \braket{Z|\frac{\partial}{\partial t}|Z} = \sum_l \frac{S_l}{1+|Z_l|^2}(Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*})
+       \braket{Z|\frac{\partial}{\partial t}|Z} = \sum_{\alpha} \frac{S_{\alpha}}{1+|Z_{\alpha}|^2}(Z_{\alpha}^*\dot{Z_{\alpha}}-Z_{\alpha}\dot{Z_{\alpha}^*})
 	\label{ddt}
@@
 \begin{align}
-  Z_l &\equiv \tan{\frac{\theta_l}{2}}e^{-i\chi_l} \\
-  j_l &\equiv S_l(1-\cos{\theta}_l) .
+  Z_{\alpha} &\equiv \tan{\frac{\theta_{\alpha}}{2}}e^{-i\chi_{\alpha}} \\
+  j_{\alpha} &\equiv S_{\alpha}(1-\cos{\theta}_{\alpha}) .
 \end{align}
@@
 \begin{equation}
-     \braket{Z|\hat{S}^0|Z} = \sum_l (j_l-S_l)
+     \braket{Z|\hat{S}^0|Z} = \sum_{\alpha} (j_{\alpha}-S_{\alpha})
 \end{equation}
@@
 \begin{equation}
-     \braket{Z|\hat{S}^+|Z} = \sum_l \sqrt{j_l(2S_l-j_l)}e^{-i\chi_l}
+     \braket{Z|\hat{S}^+|Z} = \sum_{\alpha} \sqrt{j_{\alpha}(2S_{\alpha}-j_{\alpha})}e^{-i\chi_{\alpha}}
 \end{equation}
@@
 \begin{equation}
-     \braket{Z|\hat{S}^-|Z} = \sum_l \sqrt{j_l(2S_l-j_l)}e^{i\chi_l}
+     \braket{Z|\hat{S}^-|Z} = \sum_{\alpha} \sqrt{j_{\alpha}(2S_{\alpha}-j_{\alpha})}e^{i\chi_{\alpha}}
 \end{equation}
@@
 \begin{equation}
-    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_l \left( 2S_l j_l - j_l^2 +\frac{j_l^2}{2S_l} \right) 
-+ 2\sum_{l_1\le l_2} \sqrt{j_{l_1}j_{l_2}(2S_{l_1}-j_{l_1})(2S_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   .
+    \braket{Z|\hat{S}^+\hat{S}^-|Z} = \sum_{\alpha} \left( 2S_{\alpha} j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{2S_{\alpha}} \right) 
++ 2\sum_{\alpha\le \beta} \sqrt{j_{\alpha}j_{\beta}(2S_{\alpha}-j_{\alpha})(2S_{\beta}-j_{\beta})}\cos{(\chi_{\alpha}-\chi_{\beta})}   .
 \end{equation}
@@
 \begin{equation}
-       \braket{Z|\frac{\partial}{\partial t}|Z} = \frac{1}{i}\sum_l j_l \dot{\chi_l}
+       \braket{Z|\frac{\partial}{\partial t}|Z} = \frac{1}{i}\sum_{\alpha} j_{\alpha} \dot{\chi_{\alpha}}
 	\label{ddt2}
@@
   \mathcal{S} = \int \mathcal{L}(t) dt, \quad 
-  \mathcal{L}(t) =i\hbar \sum_l \frac{S_l}{1+|Z_l|^2}
-  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{Z|H|Z}
+  \mathcal{L}(t) =i\hbar \sum_{\alpha} \frac{S_{\alpha}}{1+|Z_{\alpha}|^2}
+  (Z_{\alpha}^*\dot{Z_{\alpha}}-Z_{\alpha}\dot{Z_{\alpha}^*}) - \braket{Z|H|Z}
 \end{equation}
@@
 \begin{align}
-  \braket{Z|H|Z} =& \sum_l \epsilon_l \left\{ 2S_l\left( 1-\frac{2}{1+|Z_l|^2} \right) + \Omega_l \right\} \nonumber \\
-   &- g\sum_l 2S_l|Z_l|^2\frac{2S_l+|Z_l|^2}{(1+|Z_l|^2)^2}
-    + \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2} .
+  \braket{Z|H|Z} =& \sum_{\alpha} \epsilon_{\alpha} \left\{ 2S_{\alpha}\left( 1-\frac{2}{1+|Z_{\alpha}|^2} \right) + \Omega_{\alpha} \right\} \nonumber \\
+   &- g\sum_{\alpha} 2S_{\alpha}|Z_{\alpha}|^2\frac{2S_{\alpha}+|Z_{\alpha}|^2}{(1+|Z_{\alpha}|^2)^2}
+    + \sum_{\alpha \neq \beta} \frac{2S_{\alpha}Z_{\alpha}}{1+|Z_{\alpha}|^2}\frac{2S_{\beta}Z_{\beta}^*}{1+|Z_{\beta}|^2} .
 \end{align}
@@
 \begin{align}
-	\mathcal{L}(t) =& \sum_l j_l\dot{\chi_l} - \mathcal{H}(\chi,j) ,\\
+	\mathcal{L}(t) =& \sum_{\alpha} j_{\alpha}\dot{\chi_{\alpha}} - \mathcal{H}(\chi,j) ,\\
 	\mathcal{H}(\chi,j) \equiv& \braket{Z|H|Z} \nonumber \\
-	=& \sum_l \epsilon_l\nu_l + \sum_l 2\epsilon_lj_l - g\sum_l \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
-	&- 2g\sum_{l_1\le l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   .
+	=& \sum_{\alpha} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha} 2\epsilon_{\alpha}j_{\alpha} - g\sum_{\alpha} \left( (\Omega_{\alpha}-\nu_{\alpha}) j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber \\
+	&- 2g\sum_{\alpha\le \beta} \sqrt{j_{\alpha}j_{\beta}(\Omega_{\alpha}-\nu_{\alpha}-j_{\alpha})(\Omega_{\beta}-\nu_{\beta}-j_{\beta})}\cos{(\chi_{\alpha}-\chi_{\beta})}   .
 \end{align}
@@
 The superfluid ground state correspond to the local minimum point in energy surface.
-The time-dependent coherent state described in (\ref{coherent}) attributes to BCS trail wave function in $\chi_l=0$.
+The time-dependent coherent state described in (\ref{coherent}) attributes to BCS trail wave function in $\chi_{\alpha}=0$.
 For the simplicity, here, we only consider the even-particle system with $\nu=0$ (without Pauli blocking).
@@
 \begin{equation}
-	q_l=\cos{\theta_l} = \frac{\Omega_l - J -2(-1)^l j}{\Omega_l} 
-	\quad \mbox{ for } l=1,2
+	q_{\alpha}=\cos{\theta_{\alpha}} = \frac{\Omega_{\alpha} - J -2(-1)^l j}{\Omega_{\alpha}} 
+	\quad \mbox{ for } \alpha=1,2
 	\label{q_l}
 \end{equation}
-with the range $-1\le q_l\le 1$. $q_l=1$ corresponds to empty occupation and $q_l=-1$ corresponds to full occupation.
+with the range $-1\le q_{\alpha}\le 1$. $q_{\alpha}=1$ corresponds to empty occupation and $q_{\alpha}=-1$ corresponds to full occupation.
 
@@
 \end{align*}
-From second line to the third line, we used the fact of closed shell $J=2S_1$. With $\Omega_l=2S_l$, the phase transition point in closed shell is
+From second line to the third line, we used the fact of closed shell $J=2S_1$. With $\Omega_{\alpha}=2S_{\alpha}$, the phase transition point in closed shell is
 \begin{align}
@@
 
+%\clearpage{\pagestyle{empty}\cleardoublepage}
+%\chapter{Adiabatic self-consistent collective coordinate method}
+
+%\section{Theoretical framework}
+%\section{Matrix elements of local harmonic approximation in pairing model}
+
 \clearpage{\pagestyle{empty}\cleardoublepage}
-\chapter{Adiabatic self-consistent collective coordinate method}
-
-\section{Theoretical framework}
-\section{Matrix elements of local harmonic approximation in pairing model}
-
-\bibliographystyle{plain}
+\chapter{Detailed derivation of semiclassical wave function in SPA}
+\section{Derivation of Eq. (\ref{semi_wave_func1})}
+\label{wave_func1}
+
+We give a derivation of the semiclassical wave function
+of Eq. (\ref{semi_wave_func1}).
+The explicit form of coherent state is
+
+\begin{align}
+  \ket{Z} &= \prod_{\alpha=1}^2(1+|Z_{\alpha}|^2)^{-\Omega_{\alpha}/2}e^{Z_{\alpha}S_{\alpha}^{+}}\ket{0} \nonumber \\
+  &= \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
+  \binom{k}{m} \left(
+  \tan{\frac{\theta_1}{2}}e^{-i\phi_1}S_1^{+} \right)^m \left(
+  \tan{\frac{\theta_2}{2}}e^{-i\phi_2}S_2^{+} \right)^{k-m} \ket{0} \nonumber \\
+  &= \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
+  \binom{k}{m} \tan^m{\frac{\theta_1}{2}}\tan^{k-m}{\frac{\theta_2}{2}}e^{-ik\Phi}e^{-i(k/2-m)\phi}
+  (S_1^{+})^m(S_2^{+})^{k-m} \ket{0}
+  \label{ZZ}
+\end{align}
+Inserting (\ref{ZZ}) into (\ref{semi_wave_func0}) under fixed $N$ and $E_k$,
+it becomes
+\begin{align}
+	\ket{\psi_k^N} \propto& \oint d\Phi \oint dt
+	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
+	\ket{\Phi,t}_{N,E_k} \nonumber \\
+  \propto& \sum_k \frac{1}{k!} \sum_{m=0}^k \binom{k}{m} \int_0^{2\pi} d\Phi e^{i(N/2-k)\Phi} 
+  \int_0^T dt e^{i\int \pi(t') \dot{\phi}(t') dt'-i(k/2-m)\phi} \nonumber \\
+  &\times \left\{ \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \right\}
+\tan^m{\frac{\theta_1}{2}}\tan^{k-m}\frac{\theta_2}{2}(S_1^{+})^m(S_2^{+})^{k-m} \ket{0} \nonumber \\
+  \propto& \sum_{m=0}^{N/2} \binom{N/2}{m} \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(N/4-m)\phi \right)} \nonumber \\
+  &\times \left\{ \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \right\} 
+\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} . \label{semi_wave_func_b}
+\end{align}
+We find that the integration over $\Phi$ is nothing but the number projection.
+In SU(2) quasi-spin representation, the vacuum state is written as
+$\ket{0}=\ket{S_1,-S_1;S_2,-S_2}$, which leads to
+\begin{align}
+  (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} 
+  = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(N/2-m)!}{[2S_2-(N/2-m)]!}}
+  \ket{S_1,-S_1+m;S_2,-S_2+(N/2-m)}.
+\end{align}
+For convenience, we define coefficients
+\begin{align}
+  A(q,S,m) &\equiv 
+  \frac{\tan^m{\frac{\theta}{2}}}{\left(1+\tan^2{\frac{\theta}{2}}\right)^{-S}}
+  \sqrt{\frac{(2S)!m!}{(2S-m)!}}  \nonumber \\
+  &= \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2} \sqrt{\frac{(2S)!m!}{(2S-m)!}}
+\label{tan}
+\end{align}
+where $q=\cos{\theta}$.
+Inserting Eq. (\ref{tan}) into Eq. (\ref{semi_wave_func_b}) with $N/2=J$,
+we reach Eq. (\ref{semi_wave_func1}).
+
+\bibliographystyle{unsrt}
 \bibliography{ref}

### 2018-12-17 thesis/thesis.tex
thesis

@@
 %\usepackage{geometry} % to change the page dimensions
-\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}
+\usepackage[top=30truemm,bottom=25truemm,left=20truemm,right=20truemm]{geometry}
 \geometry{a4paper} % or letterpaper (US) or a5paper or....
@@
 
-In most of nuclei, the structure of low-lying excited $0^+$ states, which had been called as $\beta$ vibration or two-phonon excitation, are complicate and mysterious from plenty of recent experimental data.
-The common suggestion from those experimentalists is that the pairing correlation plays an important role in such excited $0^+$ states because they found strange cross sections of two-nucleon transfer reactions.
-From theoretical viewpoint,
+In early days, the low-lying excited $0^+$ states in most of nuclei had been considered as $\beta$ vibration or two-phonon excitation associated with quadrupole vibrations.
+However, plenty of recent experimental data indicate that not only quadrupole correlations but also pairing correlations play important roles in such excited $0^+$ states.
+%From theoretical viewpoint, 
 %excited $0^+$ states in superfluid nuclei correspond to not only quadrupole vibrational mode, the elementary mode of excitation of quadrupole collective motions, but also pairing vibrational mode, the elementary mode of excitation of pairing collective motions.
-the competition between quadrupole correlation and pairing correlation causes complicate structure of low-lying excited $0^+$ states. 
+The competition between quadrupole correlations and pairing correlations causes complicate and mysterious structure for the low-lying excited $0^+$ states. 
 We aim to understand such excited $0^+$ states based on time-dependent mean-field (TDMF) theory.
-Because quantum fluctuation is large in low-lying excitation region, theoretical framework in large-amplitude regime is necessary.
-However, the theoretical framework to describe pairing collective motions in large-amplitude regime is not developed.
+Because quantum fluctuation is large in low-lying excitation region, we need to consider the collective motion in large-amplitude regime.
+However, the theoretical framework to describe pairing collective motions in large-amplitude regime is not well developed.
 The nature of pairing collective motions in low-lying excitation region is still unclear.
@@
 We consider the theoretical framework to describe large-amplitude collective motions associated with nuclear pairing.
-In general, the low-lying excited states can be obtained in two steps: (1) solve TDMF equation to obtain classical trajectories; (2) quantize such classical trajectories to obtain the excited states.
+In general, the low-lying excited states can be obtained in two steps: (1) solve TDMF equation to obtain the classical trajectories; (2) quantize such classical trajectories to obtain the excited states.
 The step 2 is called ``requantization''.
-In this thesis, we focus on step 2 and discuss the requantization method in detail.
-To simplify the system, apart from realistic nuclear system, we consider the pairing collective motions in multi-level pairing model.
+Because the theoretical framework for the requantization is not well developed, we focus on the step 2 and discuss it in detail.
+%To simplify the system, 
+Apart from realistic nuclear system, 
+we consider the pairing collective motions in multi-level pairing model.
 We divide the pairing system into two classes, integrable system and non-integrable system.
@@
 We apply three different requantization methods, canonical quantization, Fourier decomposition of the time-dependent observables, and stationary phase approximation (SPA) to the path integral.
-Comparing each requantization method with exact solution in various two-level system, respectively, SPA turns out to be most accurate between the three and can describe the excited states quantitatively, especially for the calculation of two-particle transition strength.
+Comparing each requantization method with exact solution in various two-level system, respectively, SPA turns out to be most accurate between the three and can describe the excited states quantitatively, especially for the description of two-particle transition strength.
 Because the requantized wave functions from SPA are given in terms of the microscopic degrees of freedom, the transition matrix elements can be calculated directly.
@@
 Actually, SPA cannot be applied to non-integrable system straightforwardly because finding the periodic orbits is extremely difficult task.
-We propose a new theoretical approach which enables SPA to apply to non-integrable system, namely, combining SPA with adiabatic self-consistent collective coordinate (ASCC) method (ASCC+SPA).
-The concept is that we employ ASCC to extract an integrable subspace from TDMF phase space, and apply SPA to obtain the excited states.
-The detailed derivation is shown in the text.
-From the application to the low-lying excited $0^+$ states in three-level system and Pb isotopes system, we find ASCC+SPA gives a reasonable description.
-
-We also examine the performance of the pairing collective model which phenomenologically assumes pairing gap parameter and gauge angle as collective coordinates.
-We check the one-to-one correspondence between the collective coordinates from TDMF dynamics itself and those in collective model.
+We propose a new theoretical approach which enables SPA to apply to non-integrable system, that is, combining SPA with adiabatic self-consistent collective coordinate (ASCC) method (ASCC+SPA).
+The concept is that we employ ASCC to extract an integrable subspace from original TDMF phase space, and apply SPA to obtain the excited states.
+%The detailed derivation is shown in the text.
+After the application to the low-lying excited $0^+$ states in three-level system and Pb isotopes system, we find that ASCC+SPA can properly describe the pairing collective motions.
+
+We also examine the performance of the pairing collective model which assumes pairing gap parameter and gauge angle as collective coordinates.
+We check the one-to-one correspondence between the collective coordinates from TDMF dynamics itself and those in the collective model.
 We find the collective coordinate describing pairing vibration has no one-to-one correspondence between the two, in both integrable and non-integrable system.
@@
 Using SPA, we construct a theoretical framework of ASCC+SPA to requantize the pairing collective motions in non-integrable system.
-Also, we demonstrate that to describe pairing vibration properly, it is necessary to employ the collective coordinate extracted from TDMF degrees of freedom itself, instead of the phenomenological collective coordinate, pairing gap parameter.
-With the development of computational power, we think
-ASCC+SPA is promising tool to elucidate the structure of mysterious low-lying excited $0^+$ states in nuclei.
+Also, we demonstrate that it is necessary to describe the pairing vibration in the collective coordinate extracted from TDMF degrees of freedom itself, instead of the phenomenological collective coordinate, pairing gap parameter.
+With the development of computational power and numerical techniques, we think
+the ASCC+SPA is the promising tool to elucidate the structure of mysterious low-lying excited $0^+$ states in nuclei, in the near future.
 
@@
 
-Mean-field model is standard tool to describe the structure of atomic nuclei.
+Mean-field model is a standard tool to describe the structure of atomic nuclei.
 The idea of mean-field model is based on the primary theoretical framework of shell model introduced by Mayer and Jensen in 1949.
-Mean field picture indicates that the nucleon can be described in single-particle motion in the mean field potential created by the whole nucleons in the nucleus.
-Although the many-body correlation between the nucleons is extremely complicate, the single-particle motion picture can well reproduce the basic properties (e.g.
+Mean field picture indicates that the nucleus can be described in single-particle motion in the mean field potential created by the whole nucleons in the nucleus.
+Although the many-body correlations between the nucleons is extremely complicate, the single-particle motion picture can well reproduce the basic properties (e.g.
 radius, binding energy, separation energy, magic number) in most of nuclide.
@@
 Of course, single-particle motion picture cannot describe the nuclear system perfectly.
-To describe the nuclear structure more precisely, the residual interaction, the deviation between single-particle interaction and many body correlation, needs to be taken account.
-In 1950s, nuclear physicists found one of the most important residual interaction, pairing correlation.
+To describe the nuclear structure more precisely, residual interactions need to be taken account.
+In 1950s, nuclear physicists found one of the most important residual interactions, pairing correlation.
 One of the clear evidences for pairing correlation detected from experiment is the separation energy difference between odd nuclei and even nuclei.
@@
 \ref{S_n} shows the separation energies for Sn, Sb, and Te isotopes as a function of neutron number.
-The isotopes in even neutron number have about $2\sim3$ MeV larger separation energies than the isotopes in odd neutron number.
+The isotopes in even number of neutron have about $2\sim3$ MeV larger separation energies than the isotopes in odd number of neutron.
 It is odd-even staggering (OES) effect, which is detected in whole mass region of nuclei (Fig.
@@
 It indicates a two-body attractive interaction should be included based on single-particle motion picture.
-In addition, if we examine the spin-parity of the ground states, we can find all of the even-even nuclei are $J^{\pi}=0^+$ states and most of the odd mass number nuclei have the same spin-parity as their single-particle orbital which the last nucleon fulfills in.
+In addition, if we examine the spin-parity of the ground states, we can find all of the even-even nuclei are $J^{\pi}=0^+$ states and most of the odd mass number nuclei have the same spin-parity as their single-particle orbit which the last nucleon fulfills in.
 To explain these phenomena, it is natural to consider that the ground state of even-even nuclei consist of coupled $J^{\pi}=0^+$ pairs and the ground state of odd mass number nuclei consist of coupled $J^{\pi}=0^+$ pairs except one unpaired nucleon in last single-particle orbit.
@@
 However, there is a tricky approximated theory, BCS theory, enable us to describe pairing correlation within mean-field model.
-In BCS theory, the ground state is superposed by the states with different particle number.
+In BCS theory, the states with different particle number are superposed to describe the ground state.
 It indicates that the ground state breaks symmetry in a space, namely U(1) gauge space.
 With symmetry breaking, the corresponding order parameter, pairing gap $\Delta$, has finite value.
-Based on BCS theory, because the energy of each particle in a $J^{\pi}=0^+$ pair is $E_k=\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}$, where $\epsilon_k$ is single particle energy, $\lambda$ is Fermi energy, the lowest single-particle excited state corresponds to one-pair broken state with minimum excitation energy $2\Delta$ In fact, pairing gap corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei discussed in previous paragraph.
+Based on BCS theory, because the energy of each particle in a $J^{\pi}=0^+$ pair is $E_k=\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}$, where $\epsilon_k$ is single particle energy, $\lambda$ is Fermi energy, the lowest single-particle excited state corresponds to one-pair broken state with minimum excitation energy $2\Delta$.
+In fact, pairing gap corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei.
 As same as superconductivity in condensed matter physics, the superfluid nucleus is defined when $\Delta\neq0$ in ground state.
-Thus, the OES detected from experiment caused from pairing correlation can be well explained by BCS theory.
+Thus, BCS theory can explain the OES effect caused from pairing correlation.
 
@@
 HFB theory is the naturally extension of Hartree-Fock (HF) theory by introducing Bogoliubov transformation.
-Under Bogoliubov transformation, the particles become to quasiparticles, and the mean-field potential is extended to generalized form including pairing field.
+Under Bogoliubov transformation, the particles become to quasiparticles, and the mean-field is extended to generalized form including pairing field.
 After HFB theory had been applied to nuclear physics in 1958, the structure of ground states in nuclei was examined by plenty of studies.
@@
 
-Due to the superfluid state breaks the symmetry in U(1) gauge space, we expect that there are two types of elementary modes of excitation for pairing collective motion in nuclei.
+Due to the superfluid state breaks the symmetry in U(1) gauge space, there are two types of elementary modes of excitation for pairing collective motion in nuclei.
 The elementary modes of excitation are Nambu-Goldstone (NG) mode, pairing rotational mode, recovering the broken symmetry in U(1) gauge space, and Higgs mode, pairing vibrational mode, fluctuating around the energy minimum point.
 
-First, we discuss about pairing rotation.
+First, we discuss the pairing rotation.
 In classical picture, pairing rotation is the motion which the system rotates in the U(1) gauge space (red bi-direction arrow in Fig.
@@
 %It is similar to normal rotation in 3D space which described by the angles ($\theta_x, \theta_y, \theta_z$) and their conjugate angular momenta ($J_x, J_y, J_z$). 
-Because the total particle number is unchanged in time evolution, pairing rotation corresponds to constant of motion.
-In quantum picture, if we assume the ground state of $N_0$ particle system as the ``ground state'', the ground states in $N=N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' of pairing rotational mode.
+Of course, $N$ is a constant of motion.
+In quantum picture, if we assume the ground state of $N_0$ particle system as the ``ground state'', the ground states in $N=N_0\pm2, N_0\pm4,\cdots$ correspond to the ``excited states'' in the pairing rotational mode.
 The excitation energy is $E_{\rm rot}^{\rm pair}=\frac{(N-N_0)^2}{2\mathcal{J}}$, where $\mathcal{J}$ is the pairing-rotational moment of inertia.
@@
 \cite{HN16}.
-The experimental moments of inertia obtained from two neutron(proton) separation energies have excellent correspondence with the theoretical moments of inertia obtained from NG mode in quasiparticle random phase approximation (QRPA) \cite{TV61} based on HFB mean-field theory, not only for the spherical nuclei, but also for the deformed nuclei.
+The experimental moments of inertia obtained from two neutron(proton) separation energies have excellent correspondence with the theoretical moments of inertia obtained from NG mode in quasiparticle random phase approximation (QRPA) \cite{TV61}, not only for the spherical nuclei, but also for the deformed nuclei.
 Because the pairing-rotational moments of inertia are free from ambiguities caused from odd-even system, they are supposed to be excellent indicators of pairing correlation rather than pairing gaps.
 
-Next, we discuss about pairing vibration.
-We emphasize that there are two types of pairing vibrations, one which vibrates around normal ground state ($\Delta\approx 0$), and another one which vibrates around superfluid ground state ($\Delta\neq 0$).
-The structures of two vibrational modes are quite different.
+Next, we discuss the pairing vibration.
+We emphasize that there are two types of pairing vibrations, one vibrating around a normal ground state ($\Delta\approx 0$), and the other vibrating around superfluid ground state ($\Delta\neq 0$).
+The properties of the two are quite different.
 %The former one is well understood because the structure of the excited $0^+$ states are $2np2nh$ configurations, detected from the energy spectra around ${}^{208}$Pb. 
@@
 The excitation energy is $E_{\rm vib}^{\rm pair}=n_{\alpha}\hbar\omega$, where $n_{\alpha}$ is the number of phonon and $\alpha$ is the label to distinguish different pairing vibrational modes.
-Because $2\Delta$ is the minimum energy to break one-pair, the collectivity is supposed to be strong when $E_{\rm vib}^{\rm pair}<2\Delta$.
-Thus, low-lying excited $0^+$ states in even-even nuclei are possible to be pairing vibrational states.
+Because $2\Delta$ is the minimum energy to break one-pair, the collectivity is dominant when $E_{\rm vib}^{\rm pair}<2\Delta$.
+Thus, low-lying excited $0^+$ states in even-even nuclei have strong collectivity associated with pairing vibration.
 Except the region around the magic number, excited $0^+$ states below $2\Delta$ exist in most of even-even nuclei.
@@
 As mentioned in previous paragraph, the ground states of even-even Sn isotopes consist of a pairing rotational band.
-In such situation, we can find intraband transition is dominant with respect to interband transition.
+In such situation, the intraband transition is dominant with respect to the interband transition.
 Therefore, the cross sections of two-neutron transfer reaction is consistent with theoretical prediction.
@@
 In most of nuclei, the structure of excited $0^+$ states in a low-lying region (a few MeV excitation) is complicate and unclear \cite{HW11}.
-The reason is that not only pairing correlation but also deformations and multipole correlations influence the excited $0^+$ states significantly.
+The reason is that not only pairing correlations but also deformations and multipole correlations influence the excited $0^+$ states significantly.
 The various correlations competing with each other construct plenty of mysterious excited $0^+$ states.
@@
 Another interpretation for such phenomena is using microscopic interaction, including multipole pairing correlations and quadrupole particle-hole interactions \cite{RB76}.
-Although the approaches are different, they reproduced the asymmetry cross sections of two-neutron transfer reaction in actinide region.
-These studies hinted the importance of the quadrupole deformation and interactions in low-lying excited $0^+$ states.
+Although the approaches between these studies are different, they reproduced the asymmetry cross sections of two-neutron transfer reaction in actinide region.
+These studies hinted the importance of the quadrupole correlations in low-lying excited $0^+$ states.
 
@@
 They found that only a part of $B(E2)$ values related to the $0_2^+$ states agree with the predicted $B(E2)$ values in pure $\beta$ vibration picture.
-Moreover, for $E0$ transition, very few $0_2^+$ states satisfies the range of $\rho^2(E0)$ values which the $\beta$ vibrational picture is good.
+Moreover, for $E0$ transition, very few $0_2^+$ states satisfies the range of $\rho^2(E0)$ values which the $\beta$ vibrational picture predicts.
 On the other hand, they detected strong cross sections $\sigma(g.s.\to 0_{2}^+)$ in both $(t, p)$ and $(p, t)$ reactions.
-These results suggest that $0_2^+$ states in rare earth region are not pure $\beta$ vibrational states, but some mixed states with the importance of pairing correlation.
+These results suggest that $\ket{0_2^+}$ in rare earth region are not pure $\beta$ vibrational states, but some states mixing with pairing correlations.
 
@@
 \ref{112Cd}, we can find that the observed excitation energy spectra have good coincidence with phonon excitation picture.
-The $0_2^+$ or $0_3^+$ states seem to can be interpreted as two-phonon or three-phonon excitation.
-However, the $B(E2)$ values are very different comparing with each other, especially for the no observed decay from $0_{2ph}^+$ to $2_1^+$ state.
+The $0_2^+$ or $0_3^+$ states seem to be interpreted as two-phonon or three-phonon excitation.
+However, the $B(E2)$ values are quite different between the two, especially for the no observed decay from $0_{2ph}^+$ to $2_1^+$ state.
 Such phenomena are also seen in other Cd isotopes.
 The configuration of these $0^+$ states are supposed to be not pure phonon excitation, but proton pair-excitation between $2p_{1/2}$ and $1g_{9/2}$ orbits from the hint of the ground state configurations of Ag isotopes \cite{HW11}.
-The pairing should plays an important role if the excited $0^+$ states are described by pair-excitation.
+The pairing should play an important role if the excited $0^+$ states are described by pair-excitation.
 
@@
 We aim to understand the low-lying excited $0^+$ states ($\sim$ a few MeV excitation) from nuclear many-body theory.
-As mentioned above, pairing correlation is supposed to play a significant role in such excited $0^+$ states.
+As mentioned above, pairing correlation plays a significant role in such excited $0^+$ states.
+We need to understand the nature of the pairing dynamics in nuclei.
 We discuss the theoretical approach to describe the pairing dynamics in the following.
@@
 Quasiparticle random phase approximation (QRPA) theory, which correspond to the small amplitude approximation of TDHFB, is known as the most common approach to describe the structure of collective excited states.
-From a number of studies, we can find that the giant resonances (locating at a few MeV$\sim$dozens of MeV excitation with broad width) can be well described by the QRPA \cite{Eba10, YN11, YN13, SL13-2}.
+From a number of studies, the giant resonances (locating at a few MeV $\sim$ dozens of MeV excitation with broad width) can be well described by the QRPA \cite{Eba10, YN11, YN13, SL13-2}.
 With density functional formalism, recently, QRPA equation can be solved in finite amplitude method (FAM) \cite{Na07}.
@@
 %and is becoming the standard way to solve the QRPA equation numerically. 
-The QRPA is not only useful to predict the collective motions which have not been observed such as exotic nuclei, but also can become the basic concept to construct a theoretical framework beyond the linear regime.
+The QRPA is not only useful to predict the collective motions which have not been observed, such as those in exotic nuclei, but also can become the basic concept of a theoretical framework beyond the linear regime.
 On the other hand, the QRPA description for the low-lying collective excited states is not as good as the giant resonances.
@@
 To describe the low-lying excited states, especially for the excited $0^+$ states, we need to introduce the large-amplitude motions beyond the linear regime.
-Collective model, which is designed by a couple of collective coordinates and their collective potential and mass parameters, is useful for the large-amplitude dynamics.
+Collective model, which is designed by a couple of collective coordinates and their collective potential and mass parameters, is useful for describing the large-amplitude dynamics.
 The most popular phenomenological collective model is Bohr collective model, five-dimensional collective Hamiltonian (5DCH) with the quadrupole deformation parameters $(\beta,\gamma)$ and the Euler angles $(\phi,\theta,\psi)$.
-It has been applied to describe the low-lying excited states in realistic nuclei, with the construction of the collective potential and mass parameters from the microscopic degrees of freedom.
+It has been applied to describe the low-lying excited states in realistic nuclei, with the construction of the collective potential and mass parameters from the microscopic degrees of freedom \cite{NMMY16}.
 However, the pairing degrees of freedom are not explicitly included in the Bohr collective model.
@@
 
-In fact, the TDHFB degrees of freedom equal to the number of single-particle levels, in pairing model.
+In fact, the TDHFB degrees of freedom equal to the number of single-particle level, in pairing model.
 Furthermore, the TDHFB degrees of freedom consist of one constant of motion, pairing rotation, and other intrinsic degrees of freedom.
@@
 All we have to do is to study the multi-level system.
-We categorize two types of multi-level system, two-level system and the system more than three-level.
+We divide the multi-level system into two classes, two-level system and the system more than three-level.
 The former one is two-dimensional integrable system.
 We have two explicit coordinates to describe pairing rotation and pairing vibration, respectively.
-Thus, the pairing collective motions can be properly described in such coordinates.
-The later one is non-integrables system.
+The later one is non-integrable system.
 The collective coordinate describing the pairing vibrational mode is not explicit.
-However, we can find such collective coordinate decoupled from other intrinsic degrees of freedom by using adiabatic self-consistent collective coordinate (ASCC) method \cite{MNM00, N2012}.
-
-With these collective coordinates, we quantize them to obtain the collective excited states.
+However, adiabatic self-consistent collective coordinate (ASCC) method  enables us to find such collective coordinate decoupled from other intrinsic degrees of freedom, without any artificial assumption \cite{MNM00, N2012}.
+
+With the obtained collective coordinates, we quantize them to derive the collective excited states.
 We call this procedure as ``requantization''.
@@
 In addition, Pauli's prescription is not available for the general collective Hamiltonian including the higher-oder terms of momenta.
-Such requantization problems are arisen to describe the pairing collective motions at the beginning of our study. 
-To examine the proper requantization procedure, we introduce other possible requantization methods.
-The surprising point is that the value of two-particle transition strength, a indicator of pairing collective motions, depends on the requantization method significantly (See Chap.
-\ref{integrable} for the detailed discussion).
-After trial and error, eventually, we found a reasonable requantization method, stationary-phase approximation (SPA) to the path integral to describe the pairing collective motions. 
-Actually, SPA itself is available only for the integrable system.
-In order to apply SPA to the general non-integrable system, we constructed a new requantization theoretical framework, ASCC+SPA.
+Moreover, canonical quantization is not the only approach for requantization.
+Actually, the requantized results depend on the requantization methods significantly, especially for the pairing collective motions.
+%The requantization problem is serious to describe the pairing collective motions. 
+%To explore a proper requantization procedure, we introduce other possible requantization methods.
+The surprising point is that the value of two-particle transition strength, a indicator of pairing collective motions, depends on the requantization method significantly
+After trial and error, eventually, we find that the requantization approach following the path integral form is most proper.
+A stationary-phase approximation (SPA) to the path integral, one of the requantization methods, can describe the pairing collective motions quantitatively.
+The detailed information is shown in Chap.
+\ref{integrable}.
+On the other hand, SPA itself is available only for the integrable system.
+In order to apply SPA to the general non-integrable system, we construct a new requantization theoretical framework, ASCC+SPA.
 This requantization method can describe the pairing dynamics properly.
-Moreover, ASCC+SPA supposed to be available for any collective motions based on TDMF theory.
+Moreover, the ASCC+SPA is available not only for pairing collective motions, but also for any types of collective motions.
 In this thesis, the keyword ``SPA'' emerges frequently.
@@
 \ref{integrable} discuss the pairing collective motions in integrable system (two-level system).
-We applied three different requantization methods, canonical quantization, Fourier decomposition, and SPA.
+We applied three different requantization methods, canonical quantization, Fourier decomposition, and SPA to describe the pairing collective motions.
 The obtained excitation energies and wave functions from each method are compared with exact solution.
-Also, we discuss the validity of pairing gap parameter as a collective coordinate.
 Chap.
-\ref{non-integrable} discuss the pairing collective motions in non-integrable system.
-We introduce a new requantization method, ASCC+SPA, proposed by us.
+\ref{non-integrable} refers the pairing collective motions in non-integrable system.
+According to the achievement in Chap.
+\ref{integrable}, we propose a new requantization method, ASCC+SPA.
 We explain the theoretical framework of ASCC+SPA in the former part, and discuss the result for pairing collective motions from ASCC+SPA in the later part.
 
-There are several remaining problems from our study.
-In Chap.
-\ref{discussion}, we point out these problems and give some possible approaches for them.
-Because SPA is the theory of great elegance, we also discuss the perspective for the large-amplitude dynamics by using SPA or beyond SPA.
-We conclude our study in Chap.
-\ref{conclusion}.
+Also, we discuss the validity of the collective model treatment in Chap.
+\ref{collective}.
+We analyze the one-to-one correspondence between the pairing gap parameter and the collective coordinate obtained from TDHFB dynamics itself in both integrable system and non-integrable system.
+
+In Chap. \ref{conclusion}, we summarize our achievements from the study. Moreover, we discuss the remaining problems and perspective of ASCC+SPA, toward the realistic nuclear system.
 
@@
 The difficult point is that we cannot directly specify the number of excitation from the obtained excitation energy because the converged excitation energy $\sum_{m=1}^M E_{m}$ can be any number of excitation.
-To specify the number of excitation, we can use the idea in Ref.
-\cite{Richardson4}, which discussed the behavior of the $E_{m}$ as a function of $g$ for ground and each low-lying excitation energy.
-
-The eigenvalues can be also calculated numerically by using the obtained $E_{m}$.
-Actually, we need to calculate the matrix elements for specific operators we interest (e.g.
-number operator, two-particle transition operator), without obtaining the explicit eigenvectors.
-For example, the occupation number can be obtained in the following non-linear equations
-\begin{align}
-n.
-\end{align}
-%However, the equation
+After plenty of studies for the numerical techniques, recently, such difficulty was solved in Ref.
+\cite{QC15}.
+They employed a simple hybrid polynomial to simplify the guess of the initial values, and obtained the proper energies easily in very short computational time.
+This approach is useful not only for the energy in ground state, but also for the low-lying excitation energies
+
+Another challenging problem is how to calculate the wave functions.
+The eigenvectors can be also calculated numerically by using the obtained $E_{m}$.
+Because the dimension of the eigenvectors is huge in general, we need to calculate the matrix elements for a specific operator we interest (e.g.
+occupation number operator $\hat{n}_{\alpha}$, two-particle transition operator $\hat{S}^{\pm}_{\alpha}$).
+The expectation value of such operators can be obtained by solving non-linear equations for a specific operator \cite{Richardson5}.
+However, there is no general method to calculate the off-diagonal part of operators.
+The development for solving Richardson equations is still necessary.
 
@@
 \clearpage{\pagestyle{empty}\cleardoublepage}
-\chapter{Conclusion}
+\chapter{Conclusion and perspective}
 \label{conclusion}
@@
 In step 1, we found the TDHFB degrees of freedom equal to the number of single-particle level.
-More specifically, the TDHFB degrees of freedom consists of one constant of motion, pairing rotation described in variables $(\Phi, J)$, and $L-1$ time-dependent degrees of freedom in $L$ single-particle level system.
-To apply the step 2, we divided the pairing system into two classes, two-level system corresponding to the integrable system and the system more than three-level corresponding to the non-integrable system.
-
-Two-level system corresponds to integrable system because there is only one time-dependent degree of freedom.
+More specifically, the TDHFB degrees of freedom consist of one constant of motion, pairing rotation described in variables $(\Phi, J)$, and $L-1$ time-dependent degrees of freedom in $L$ single-particle level system.
+To apply the step 2, we divided the pairing system into two classes, two-level system corresponding to the integrable system, and the system more than three-level corresponding to the non-integrable system.
+
+Two-level system is integrable system because there is only one time-dependent degree of freedom.
 After the explicit coordinate transformation decoupling the constant of motion, pairing rotation described by $(\Phi, J)$, we obtain the time-dependent variables $(\phi, j)$ describing pairing vibration.
@@
 
-To test the performance of each requantization method, we considered two classes of systems, large systems with large degeneracy $\Omega$ and number of particles $N$, and small systems which are comparable with the valence orbits in realistic nuclear systems.
+To test the performance of each requantization method, we applied them to two classes of systems, large systems with large degeneracy $\Omega$ and number of particles $N$, and small systems which are comparable with the valence orbits in realistic nuclear systems.
 In the former case, all the quantization methods reasonably reproduced the results of the
@@
 In the later case, on the other hand, the agreement is
-less quantitative for the CQ and the FD, especially for the twoparticle
+less quantitative for the CQ and FD, especially for the two-particle
 transfer matrix elements.
@@
 
-The weak point of this approach is that it is applicable only to the
+The weak point of SPA is that SPA is applicable only to the
 integrable TDHFB system.
 To overcome this problem, we proposed the ASCC+SPA method for non-integrable systems.
-The concept is that we can employ ASCC to decouple an integrable collective subspace from original TDHFB phase space, then, the SPA is available for the collective subspace.
+The concept is that ASCC can decouple an integrable collective subspace from original TDHFB phase space, then, the SPA is available for the collective subspace.
 In this approach, we use the ASCC method to extract the 2D
-collective subspace including the pair rotation.
+collective subspace including the pairing rotation.
 In other words, we extract an approximate integrable system 
@@
 
-We also investigated the conventional treatment of the
+We also investigated the conventional treatment of the pairing
 collective model which assumes that the collective coordinate
-is the paring gap parameter.
+describing pairing vibration is the paring gap parameter $\Delta$.
+In integrable (two-level) system, the coordinate $j$ corresponding to TDHFB degree of freedom itself describes the pairing vibration. $\Delta$ is expressed as a function of $j$ explicitly.
+There is no
+one-to-one correspondence between $\Delta$ and $j$ in any two-level systems.
+In non-integrable system, the coordinate $q^1$ obtained from ASCC describes the pairing vibration.
+The behavior of $\Delta(q^1)$ is very similar to $\Delta(j)$ in integrable system.
+Basically, there is also no
+one-to-one correspondence between $\Delta$ and $q^1$.
+The collective
+wave functions are not necessarily bound in the region where
+the variable $\Delta$ can represent.
+Thus, $\Delta$ is improper coordinate to describe pairing vibration, at least in pairing model.
+
+It is the first attempt of the application of SPA into non-integrable system, and it is successful to describe the pairing dynamics quantitatively in large-amplitude regime. 
+In realistic nuclear system, the competition between pairing and quadrupole correlations is important.
+If there is quadrupole correlation, the single-particle level changes significantly.
+The behavior of the pairing dynamics in such system is supposed to be different from that in the pairing model we discussed in this thesis.
+
+We think the next application of SPA is valuable for the systems with pairing and quadrupole correlations, such as multi-O(4) model \cite{HNMM07} and P+Q model \cite{HNMM08}.
+Then, we need to extend ASCC+SPA to the following cases: (1) ``unbound'' trajectories in shallow potential energy surface as discussed in Sec.
+\ref{4-3}; (2) trajectories in potential energy surface with multi energy minimum pockets, such as shape coexistence.
+In the former case, we need to find a proper boundary condition to guarantee the periodicity  of the trajectories.
+We suppose that such boundary condition can be easily constructed in the same manner as in \cite{HNMM07,HNMM08}.
+In the later case, the tunneling effect between the different energy minimum pockets is important, while the SPA basically has no tunneling effect.
+However, we think it is possible to overcome the difficulty by extending the EBK quantization condition to multi-trajectories in each energy minimum pocket.
+
+Also, ASCC+SPA can be applied to the realistic nuclear system in density functional formalism.
+The numerical cost for solving ASCC basic equations is extremely large in realistic system.
+An efficient numerical algorithm is employing FAM to solve the moving-frame QRPA equation \cite{NIY07,HKN13}.
+Recently, ASCC has been started to apply to the realistic nuclear effective interaction \cite{WN16,WN17}.
+In the near future, ASCC+SPA will be able to describe the low-lying excited states in nuclei, including the mysterious $0^+$ states.
 

### 2019-01-01 thesis/thesis.tex
thesis

@@
 
-In early days, the low-lying excited $0^+$ states in most of nuclei had been considered as $\beta$ vibration or two-phonon excitation associated with quadrupole vibrations.
+The low-lying excited $0^+$ states in most of nuclei had been traditionally considered as either $\beta$ vibration or two-phonon excitation associated with quadrupole vibrations.
 However, plenty of recent experimental data indicate that not only quadrupole correlations but also pairing correlations play important roles in such excited $0^+$ states.
@@
 %excited $0^+$ states in superfluid nuclei correspond to not only quadrupole vibrational mode, the elementary mode of excitation of quadrupole collective motions, but also pairing vibrational mode, the elementary mode of excitation of pairing collective motions.
-The competition between quadrupole correlations and pairing correlations causes complicate and mysterious structure for the low-lying excited $0^+$ states. 
-We aim to understand such excited $0^+$ states based on time-dependent mean-field (TDMF) theory.
-Because quantum fluctuation is large in low-lying excitation region, we need to consider the collective motion in large-amplitude regime.
-However, the theoretical framework to describe pairing collective motions in large-amplitude regime is not well developed.
-The nature of pairing collective motions in low-lying excitation region is still unclear.
-
-We consider the theoretical framework to describe large-amplitude collective motions associated with nuclear pairing.
-In general, the low-lying excited states can be obtained in two steps: (1) solve TDMF equation to obtain the classical trajectories; (2) quantize such classical trajectories to obtain the excited states.
+The competition between quadrupole correlations and pairing correlations causes complex and mysterious structure for the low-lying excited $0^+$ states. 
+We aim to understand such excited $0^+$ states based on the time-dependent mean-field (TDMF) theory.
+Because quantum fluctuation is large in low-lying excitation region, we need to treat the collective motion in large-amplitude regime.
+However, the theoretical framework to describe pairing collective motions in the large-amplitude regime is not yet established.
+The nature of low-lying pairing collective motions is still unclear.
+
+We aim at developing a new theoretical framework to describe large-amplitude collective motions associated with nuclear pairing.
+In our approach, the low-lying excited states are obtained in two steps: (1) solve TDMF equation to obtain the classical trajectories; (2) quantize such classical trajectories to obtain the excited states.
 The step 2 is called ``requantization''.
-Because the theoretical framework for the requantization is not well developed, we focus on the step 2 and discuss it in detail.
-%To simplify the system, 
-Apart from realistic nuclear system, 
-we consider the pairing collective motions in multi-level pairing model.
-We divide the pairing system into two classes, integrable system and non-integrable system.
-The former one corresponds to two-level system and the later one corresponds to the system more than three-level.
-Because the description of requantization is different between the two, we consider the requantization methods for each case, respectively.
-
-In integrable system, the requantization of TDMF is particular feasible because we can easily find the periodic orbits.
+First, we consider the pairing collective motions in multi-level pairing model.
+The pairing models can be classified into two classes, integrable and non-integrable systems.
+The former one corresponds to the two-level system and the later one corresponds to the system with three levels or more.
+
+In the integrable system, the requantization of TDMF is particularly feasible because we can easily find the periodic orbits.
 We apply three different requantization methods, canonical quantization, Fourier decomposition of the time-dependent observables, and stationary phase approximation (SPA) to the path integral.
-Comparing each requantization method with exact solution in various two-level system, respectively, SPA turns out to be most accurate between the three and can describe the excited states quantitatively, especially for the description of two-particle transition strength.
+Comparing each requantization method with the exact solution, respectively, SPA turns out to be the most accurate among the three and can describe the excited states quantitatively, including two-particle transition strength.
 Because the requantized wave functions from SPA are given in terms of the microscopic degrees of freedom, the transition matrix elements can be calculated directly.
 
-Actually, SPA cannot be applied to non-integrable system straightforwardly because finding the periodic orbits is extremely difficult task.
-We propose a new theoretical approach which enables SPA to apply to non-integrable system, that is, combining SPA with adiabatic self-consistent collective coordinate (ASCC) method (ASCC+SPA).
-The concept is that we employ ASCC to extract an integrable subspace from original TDMF phase space, and apply SPA to obtain the excited states.
+Unfortunately, the application of the SPA to the non-integrable system is not straightforward because finding the periodic orbits is an extremely difficult task.
+We propose a new theoretical approach which makes the SPA to be applicable to non-integrable systems, that is, combining the SPA with the adiabatic self-consistent collective coordinate (ASCC) method (ASCC+SPA).
+The concept is that we employ the ASCC to extract an integrable subspace from original TDMF phase space, and apply the SPA to the integrable subspace.
 %The detailed derivation is shown in the text.
-After the application to the low-lying excited $0^+$ states in three-level system and Pb isotopes system, we find that ASCC+SPA can properly describe the pairing collective motions.
-
-We also examine the performance of the pairing collective model which assumes pairing gap parameter and gauge angle as collective coordinates.
-We check the one-to-one correspondence between the collective coordinates from TDMF dynamics itself and those in the collective model.
-We find the collective coordinate describing pairing vibration has no one-to-one correspondence between the two, in both integrable and non-integrable system.
+We apply the ASCC+SPA to the low-lying excited $0^+$ states in three-level system and Pb isotopes system. We find that the ASCC+SPA can properly describe the pairing collective motions.
+
+We also examine the validity of the pairing collective model which assumes the pairing gap parameter and gauge angle as the phenomenological collective coordinates.
+We check the one-to-one correspondence between the collective coordinates self-consistently determined with the ASCC and those assumed in the collective model.
+We find the collective coordinate describing pairing vibration has no one-to-one correspondence between the two, in both integrable and non-integrable systems.
 The applicability of the collective model is limited for the nuclear pairing.
 
-We summarize the achievements in this thesis.
+%We summarize the achievements in this thesis.
 We find a reasonable requantization method, SPA, from the study in integrable system.
@@
 Also, we demonstrate that it is necessary to describe the pairing vibration in the collective coordinate extracted from TDMF degrees of freedom itself, instead of the phenomenological collective coordinate, pairing gap parameter.
-With the development of computational power and numerical techniques, we think
-the ASCC+SPA is the promising tool to elucidate the structure of mysterious low-lying excited $0^+$ states in nuclei, in the near future.
+With the development of computational power and numerical techniques,
+the ASCC+SPA is a promising tool to elucidate the structure of mysterious low-lying excited $0^+$ states in nuclei, in near future.
 
@@
 \begin{align}
-d\mu(Z) &= \prod_{\alpha=1,2} \frac{\Omega_{\alpha}+1}{\pi}(1+|Z_{\alpha}|^2)^{-2}d({\rm Re}Z_{\alpha})d({\rm Im}Z_{\alpha}) \nonumber \\
-  &= \prod_{\alpha=1,2} \frac{\Omega_{\alpha}+1}{4\pi}d(\cos{\theta_{\alpha}})d\chi_{\alpha} \nonumber \\
-	&= \left(\prod_{\alpha=1,2} \frac{1+\Omega_{\alpha}^{-1}}{2\pi}\right)
+d\mu(Z) &= \prod_{\alpha=1,2} \frac{2S_{\alpha}+1}{\pi}(1+|Z_{\alpha}|^2)^{-2}d({\rm Re}Z_{\alpha})d({\rm Im}Z_{\alpha}) \nonumber \\
+  &= \prod_{\alpha=1,2} \frac{2S_{\alpha}+1}{4\pi}d(\cos{\theta_{\alpha}})d\chi_{\alpha} \nonumber \\
+	&= \left(\prod_{\alpha=1,2} \frac{1+(2S_{\alpha})^{-1}}{2\pi}\right)
              d\Phi dJ d\phi dj .
@@
 by Eqs. (\ref{phi}) and (\ref{pi}).
-Since the particle number $J=N/2$ and the total energy $E$ are invariant,
+Since the particle number $J=(N-\nu)/2$ and the total energy $E$ are invariant,
 the two-level pairing model is integrable.
@@
 	j(t') \frac{d\phi}{dt'} dt' \nonumber \\
-	&\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
+	&\equiv \mathcal{T}_{J,E_k}(\Phi,t) ,
 \end{align}
@@
 	e^{i\mathcal{T}_{J,E_k}(\Phi, t)}
-	\ket{\Phi,t}_{N,E_k} \label{semi_wave_func0} \\
+	\ket{\Phi,t}_{J,E_k} \label{semi_wave_func0} \\
   &\propto \sum_{m=0}^{J}C_m^{(E_k,J)}\ket{S_1,-S_1+m;S_2,-S_2+(J-m)} ,
@@
 is not limited to the second order in momenta.
-%We need to keep the Hamiltonian Hermitian after 
-In the present study, 
+The application of Pauli's prescription for the adiabatic TDHFB Hamiltonian (\ref{ATDHFB_Hamiltonian}) is discussed in Appendix \ref{can-trans}.
+Here, 
 we adopt a simple symmetrized ordering, as
@@
  \caption{
-The same as Fig.~\ref{fig:N50Pad} but for $N=98\rightarrow 100$.}
+The same as described in the caption of Fig.~\ref{fig:N50Pad} but for $N=98\rightarrow 100$.}
  \label{fig:N100Pad}
@@
  \end{minipage}
-	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=6\rightarrow 8$
+	\caption{The same as described in the caption of Fig.~\ref{fig:N50Pad} but for $N=6\rightarrow 8$
 	with $\Omega=8$.
@@
  \end{center}
-	\caption{The same as Fig.~\ref{fig:N8energy} but for
+	\caption{The same as described in the caption of Fig.~\ref{fig:N8energy} but for
 	$N=2\Omega=16$.
@@
  \end{minipage}
-	\caption{The same as Fig.~\ref{fig:N8_occ} but for
+	\caption{The same as described in the caption of Fig.~\ref{fig:N8_occ} but for
 	$N=2\Omega=16$.
@@
  \end{minipage}
-	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
+	\caption{The same as described in the caption of Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
 	with $\Omega=8$.
@@
 \begin{align}
-	\hat{J} = \frac{\hat{N}-\nu}{2} .
+	\hat{J} = \frac{\hat{N}-\nu}{2} = \sum_{\alpha} (\hat{S}_{\alpha}^0 + S_{\alpha}).
 \end{align}
 Then, the action for the trajectory $C_1$ can be also expressed as
-$\mathcal{T}(q^1,p_1;J)=
- \int_{C_1} \braket{J;q^1,p_1|i\frac{\partial}{\partial t}|J;q^1,p_1} dt$.
+\begin{align}
+\mathcal{T}(q^1,p_1;J)=
+ \int_{C_1} \braket{J;q^1,p_1|i\frac{\partial}{\partial t}|J;q^1,p_1} dt.
+\end{align}
 %\begin{align}
@@
 \begin{align}
-\ket{Z} &= 
-\sum_{\{m_\alpha\}} A_m(Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
+\ket{Z} &= e^{-i\Phi \hat{J}} \ket{J;q^1,p_1}
+ = e^{-i\Phi \hat{J}}\sum_{\{m_\alpha\}} B_m(Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
+\label{coherent2}
 \end{align}
@@
 \begin{align}
-A_m(Z) =& \prod_\alpha 
-\frac{Z_\alpha^{m_\alpha}}
-	{\left(1+|Z_\alpha|^2\right)^{\Omega_\alpha/2}m_\alpha!}
-\sqrt{\frac{\Omega_\alpha! m_\alpha!}{(\Omega_\alpha-m_\alpha)!}} \nonumber\\
- =& \prod_\alpha \left(\frac{1-\cos{\theta}_\alpha}{2}\right)^{m_\alpha/2}\left(\frac{1+\cos{\theta}_\alpha}{2}\right)^{(\Omega_\alpha-m_\alpha)/2}
-\sqrt{\frac{\Omega_\alpha!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} e^{-i m_\alpha\chi_\alpha}  ,
-	\label{A_m}
-\end{align}
-where the lower index $m$ indicates a combination of $\{ m_\alpha \}$.
+B_m(Z) 
+%=& \prod_\alpha 
+%\frac{Z_\alpha^{m_\alpha}}
+%	{\left(1+|Z_\alpha|^2\right)^{\Omega_\alpha/2}m_\alpha!}
+%\sqrt{\frac{\Omega_\alpha! m_\alpha!}{(\Omega_\alpha-m_\alpha)!}} \nonumber\\
+% =& \prod_\alpha \left(\frac{1-\cos{\theta}_\alpha}{2}\right)^{m_\alpha/2}\left(\frac{1+\cos{\theta}_\alpha}{2}\right)^{(\Omega_\alpha-m_\alpha)/2}
+%\sqrt{\frac{\Omega_\alpha!}{m_\alpha!(\Omega_\alpha-m_\alpha)!}} \\
+  =& \prod_\alpha \left(\frac{j_\alpha}{2S_\alpha}\right)^{m_\alpha/2}\left(\frac{2S_\alpha-j_\alpha}{2S_\alpha}\right)^{S_\alpha-m_\alpha/2}
+ \sqrt{\frac{(2S_\alpha)!}{m_\alpha!(2S_\alpha-m_\alpha)!}}
+e^{-i m_\alpha\phi_\alpha}  ,
+	\label{B_m}
+\end{align}
+where the relative angles are defined as
+$\phi_\alpha\equiv\chi_\alpha-\Phi$ and the lower index $m$ indicates a combination of $\{ m_\alpha \}$.
+From Eq.
+(\ref{momenta2}) in ASCC, we can directly obtain the relative angles $\phi_\alpha = -f^1_{,\alpha}p_1$.
 The integer number $m_\alpha$ corresponds to the number of pairs
@@
 
-Using Eq.~(\ref{A_m}),
+Using Eq.~(\ref{B_m}),
 the $k$-th excited state is calculated as
@@
 	\int_0^{2\pi} d\Phi e^{i(J-\sum_\alpha m_\alpha)\Phi} \oint dt e^{i\mathcal{T}_1}(t) B_m (Z) \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots} \nonumber \\
- \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots},
+ \equiv& \sum_{\{m_\alpha\}_J} C_m \ket{\cdots;S_\alpha,-S_\alpha+m_\alpha,\cdots}.
  \label{SPA2}
 \end{align}
-where $B_m(Z)$ are identical to $A_m$ in Eq.~(\ref{A_m}) except for
-replacing $\chi_\alpha$ with the relative angles
-$\phi_\alpha\equiv\chi_\alpha-\Phi$.
 The coefficients $C_m$ are given by
@@
  \begin{center}
-   \includegraphics[height=0.5\textwidth,angle=-90]{images/N16X3p2occ.eps}
+   \includegraphics[height=0.7\textwidth,angle=-90]{images/N16X3p2occ.eps}
  \end{center}
@@
 \begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/intra_trans.eps}
- \end{center}
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/inter_trans.eps}
- \end{center}
+ \begin{minipage}{1\hsize}
+ \begin{center}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/intra_trans.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/inter_trans.eps}
+ \end{center}
+ \end{minipage}
 \caption{Calculated strength of pair-addition transition (\ref{BPad})
@@
 The horizontal line indicates the particle number of the initial states.
-The upper panel shows the intraband transitions,
+The left panel shows the intraband transitions,
 $0_1^+\to 0_1^+$ and $0_2^+\to 0_2^+$,
-while the lower panel shows the interband transitions,
+while the right panel shows the interband transitions,
 $0_1^+ \to 0_2^+$ and $0_2^+\to 0_1^+$.
@@
  \end{center}
-	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
+	\caption{The same as described in the caption of Fig. \ref{omega_sq} but for Pb isotopes.
 }
@@
  \end{center}
-	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
+	\caption{The same as described in the caption of Fig. \ref{occ_number} but for Pb isotopes.
 }
@@
 \begin{center}
-\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
+\caption{The same as described in the caption of Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
 \begin{tabular}{c|cccccc}
@@
 \begin{figure}[htb]
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/Pbintra_trans.eps}
- \end{center}
- \begin{center}
-  \includegraphics[width=60mm,angle=-90]{images/Pbinter_trans.eps}
- \end{center}
-	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
+ \begin{minipage}{1\hsize}
+ \begin{center}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/Pbintra_trans.eps}
+  \includegraphics[height=0.45\textwidth,angle=-90]{images/Pbinter_trans.eps}
+ \end{center}
+ \end{minipage}
+	\caption{The same as described in the caption of Fig. \ref{3levelPad} but for Pb isotopes.
 }
@@
 
-In order to construct a theoretical framework to describe large-amplitude collective motion associated with nuclear pairing, apart from realistic nuclear system, we studied the low-lying excited $0^+$ states in multi-level pairing model.
+In order to construct a theoretical framework to describe large-amplitude collective motion associated with nuclear pairing, we studied the low-lying excited $0^+$ states in multi-level pairing model.
 Based on the time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory, we constructed the pairing collective excited states in two steps: (1) solve the TDHFB equation to obtain the TDHFB classical trajectories; (2) requantize the TDHFB trajectories to obtain the excited states.
-In step 1, we found the TDHFB degrees of freedom equal to the number of single-particle level.
-More specifically, the TDHFB degrees of freedom consist of one constant of motion, pairing rotation described in variables $(\Phi, J)$, and $L-1$ time-dependent degrees of freedom in $L$ single-particle level system.
-To apply the step 2, we divided the pairing system into two classes, two-level system corresponding to the integrable system, and the system more than three-level corresponding to the non-integrable system.
-
-Two-level system is integrable system because there is only one time-dependent degree of freedom.
-After the explicit coordinate transformation decoupling the constant of motion, pairing rotation described by $(\Phi, J)$, we obtain the time-dependent variables $(\phi, j)$ describing pairing vibration.
-Under the transformed canonical variables, we studied three different methods of requantization of TDHFB, the stationary-phase approximation (SPA) to the path integral, the canonical quantization (CQ), and the Fourier decomposition (FD) of the time-dependent observables.
-
-To test the performance of each requantization method, we applied them to two classes of systems, large systems with large degeneracy $\Omega$ and number of particles $N$, and small systems which are comparable with the valence orbits in realistic nuclear systems.
+In these models, the TDHFB degrees of freedom consist of one constant of motion, pairing rotation described in variables $(\Phi, J)$, and $L-1$ degrees of freedom in the system with $L$ single-particle levels.
+Therefore, the two-level system corresponds to the integrable system, and the system with more than two levels corresponds to the non-integrable system.
+
+In the integrable two-level case, it is easy to find the coordinates to describe two types of collective motion, pairing rotation described by $(\Phi, J)$, and pairing vibration by variables $(\phi, j)$.
+With these canonical variables, we studied three different methods of requantization of TDHFB, the stationary-phase approximation (SPA) to the path integral, the canonical quantization (CQ), and the Fourier decomposition (FD) of the time-dependent observables.
+To test the performance of each requantization method, we applied them to systems with large particle numbers, and to small systems which are comparable with the valence orbits in realistic nuclear systems.
 In the former case, all the quantization methods reasonably reproduced the results of the
@@
 transfer matrix elements.
-In contrast, the SPA keeps its accuracy in the entire range of
+In contrast, the SPA keeps its accuracy for both cases in the entire range of
 pairing strengths.
@@
 treatment.
-Thus, the SPA is the most accurate tool for description of the pairing collective motions in large-amplitude regime.
-
-The weak point of SPA is that SPA is applicable only to the
-integrable TDHFB system.
+Thus, the SPA is the most accurate tool for description of the pairing collective motions in the large-amplitude regime.
+
+The weak point of SPA is that the SPA is applicable only to the
+integrable TDHFB systems.
 To overcome this problem, we proposed the ASCC+SPA method for non-integrable systems.
-The concept is that ASCC can decouple an integrable collective subspace from original TDHFB phase space, then, the SPA is available for the collective subspace.
+The concept is that the ASCC can decouple an integrable collective subspace from the original TDHFB phase space, then, the SPA is available for the collective subspace.
 In this approach, we use the ASCC method to extract the 2D
@@
 not only of the excitation energies but also of the wave functions.
-In the ASCC+SPA, the pair-transition calculation is straightforward,
+In the ASCC+SPA, the calculation of any matrix elements is straightforward,
 because we have a microscopic wave function for every quantized state.
 This overcomes a disadvantage in the conventional canonical requantization
-in which we need to construct a pair-transition operator
+in which we need to construct an effective expression of a given operator
 in terms of the collective variables only.
 
-We also investigated the conventional treatment of the pairing
+We also investigated the validity of the conventional treatment of the pairing
 collective model which assumes that the collective coordinate
 describing pairing vibration is the paring gap parameter $\Delta$.
-In integrable (two-level) system, the coordinate $j$ corresponding to TDHFB degree of freedom itself describes the pairing vibration. $\Delta$ is expressed as a function of $j$ explicitly.
-There is no
+In integrable (two-level) systems, the coordinate $j$ describes the pairing vibration.
+We have found that there is no
 one-to-one correspondence between $\Delta$ and $j$ in any two-level systems.
-In non-integrable system, the coordinate $q^1$ obtained from ASCC describes the pairing vibration.
-The behavior of $\Delta(q^1)$ is very similar to $\Delta(j)$ in integrable system.
-Basically, there is also no
+In non-integrable systems, the coordinate $q^1$ obtained from ASCC describes the pairing vibration. The behavior of $\Delta(q^1)$ is very similar to $\Delta(j)$ in integrable systems. There is no
 one-to-one correspondence between $\Delta$ and $q^1$.
@@
 the variable $\Delta$ can represent.
-Thus, $\Delta$ is improper coordinate to describe pairing vibration, at least in pairing model.
-
-It is the first attempt of the application of SPA into non-integrable system, and it is successful to describe the pairing dynamics quantitatively in large-amplitude regime. 
-In realistic nuclear system, the competition between pairing and quadrupole correlations is important.
-If there is quadrupole correlation, the single-particle level changes significantly.
-The behavior of the pairing dynamics in such system is supposed to be different from that in the pairing model we discussed in this thesis.
-
-We think the next application of SPA is valuable for the systems with pairing and quadrupole correlations, such as multi-O(4) model \cite{HNMM07} and P+Q model \cite{HNMM08}.
-Then, we need to extend ASCC+SPA to the following cases: (1) ``unbound'' trajectories in shallow potential energy surface as discussed in Sec.
+Thus, $\Delta$ is not a suitable coordinate to describe pairing vibration, at least in the pairing model.
+
+This is the first attempt of the application of SPA into non-integrable systems, and we succeeded to describe the pairing dynamics quantitatively in the large-amplitude regime. 
+In realistic nuclear systems, the competition between pairing and quadrupole correlations is important.
+The behavior of the pairing dynamics in such systems may be different from that in the pairing model we discussed in this thesis.
+
+Thus, it is of significant interest to apply the SPA to systems with pairing and quadrupole correlations, such as multi-O(4) model \cite{HNMM07} and P+Q model \cite{HNMM08}.
+It is also important to extend the ASCC+SPA to the following cases: (1) ``unbound'' trajectories in shallow potential energy surface as discussed in Sec.
 \ref{4-3}; (2) trajectories in potential energy surface with multi energy minimum pockets, such as shape coexistence.
 In the former case, we need to find a proper boundary condition to guarantee the periodicity  of the trajectories.
-We suppose that such boundary condition can be easily constructed in the same manner as in \cite{HNMM07,HNMM08}.
-In the later case, the tunneling effect between the different energy minimum pockets is important, while the SPA basically has no tunneling effect.
-However, we think it is possible to overcome the difficulty by extending the EBK quantization condition to multi-trajectories in each energy minimum pocket.
-
-Also, ASCC+SPA can be applied to the realistic nuclear system in density functional formalism.
-The numerical cost for solving ASCC basic equations is extremely large in realistic system.
-An efficient numerical algorithm is employing FAM to solve the moving-frame QRPA equation \cite{NIY07,HKN13}.
-Recently, ASCC has been started to apply to the realistic nuclear effective interaction \cite{WN16,WN17}.
-In the near future, ASCC+SPA will be able to describe the low-lying excited states in nuclei, including the mysterious $0^+$ states.
+In the later case, the tunneling effect between the different energy minimum pockets is important, while the current version of SPA is based on classical trajectories which cannot take into account tunneling effect.
+Perhaps, it is possible to overcome the difficulty by extending the EBK quantization condition to multi-trajectories in each energy minimum pocket and imaginary-time trajectories in the classically forbidden region.
+
+Ultimately, we aim at applying the ASCC+SPA to the realistic nuclear system with the density functional formalism.
+The numerical cost for solving the ASCC basic equations is extremely large in realistic systems.
+Recently, the ASCC has been applied to the realistic nuclear effective interaction \cite{WN16,WN17} employing an efficient method, finite amplitude method (FAM) \cite{NIY07,HKN13}, in solution of the moving-frame QRPA equation.
+We expect in the near future, ASCC+SPA will be able to describe the low-lying excited states in nuclei, including the mysterious $0^+$ states.
 
@@
 \clearpage{\pagestyle{empty}\cleardoublepage}
-\chapter{Properties of superfluid ground state in pairing model}
-The superfluid ground state correspond to the local minimum point in energy surface.
-The time-dependent coherent state described in (\ref{coherent}) attributes to BCS trail wave function in $\chi_{\alpha}=0$.
-For the simplicity, here, we only consider the even-particle system with $\nu=0$ (without Pauli blocking).
-
-\section{Two-level system}
+\chapter{Extra discussion in two-level pairing model}
+
+\section{Phase transition point}
 \label{two-level}
-With fixed expectation value of total particle number $N=2J$, the superfluid ground state correspond to the local minimum point in (\ref{Hamiltonian2})
+We consider the phase transition point between the superfluid state and the normal state.
+The superfluid ground state corresponds to the local minimum point in potential energy surface.
+The time-dependent coherent state (\ref{coherent}) attributes to BCS trail wave function in $\chi_{\alpha}=0$.
+For the sake of simplicity, here, we only consider the even-particle system with $\nu=0$ (without Pauli blocking).
+
+With fixed expectation value of the total particle number $N=2J$, the superfluid ground state correspond to the local minimum point in (\ref{Hamiltonian2})
 \begin{align}
@@
 
+\section{Canonical quantization in Pauli's prescription}
+\label{can-trans}
+
+In Sec. \ref{integrable}, we derived the TDHFB Hamiltonian in adiabatic approximation. 
+The canonical quantization in Pauli's prescription is available for Eq. (\ref{ATDHFB_Hamiltonian}). Using Pauli's prescription, Eq. (\ref{ATDHFB_Hamiltonian}) becomes
+\begin{align}
+   H \left( j,i\frac{\partial}{\partial j} \right) = V(j) - \frac{1}{2}\sqrt{B^{-1}(j)}\frac{\partial}{\partial j}\sqrt{B^{-1}(j)}\frac{\partial}{\partial j},
+\end{align}
+and we can obtain the requantized states by solving the Schr\"{o}dinger equation
+\begin{align}
+   H \left( j,i\frac{\partial}{\partial j} \right) \psi(j) = E \psi(j).
+\end{align}
+
+Because the range of $j$ is limited $(j_{\rm min}\le j \le j_{\rm max})$, we have to care about the boundary condition for the end points $j_{\rm min}$ and $j_{\rm max}$.
+As shown in Fig.
+??, the boundary condition is negligible for the strong pairing correlation.
+On the other hand, the boundary condition is important for the weak pairing correlation because the potential cannot bind the states at $j_{\rm min}$.
+
+We reconsider the coordinate system for the phase space $(\phi,j)$ (Fig. \ref{coordinate}). It is natural to utilize 
+a cylindrical coordinate system because $\phi$ is periodic.
+In cylindrical coordinate system, the points at $j_{\rm min}$ and $j_{\rm max}$ are singular.
+Instead of the cylindrical coordinate system, we bring an another coordinate system, geographic coordinate system, which assumes the phase space collapsing at $j_{\rm min}$ and  $j_{\rm max}$, such as north pole and south pole.
+This assumption is available because the (adiabatic) TDHFB Hamiltonian is independent of $\phi$ at $j_{\rm min}$ and $j_{\rm max}$.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=100mm]{images/can-trans.eps}
+ \end{center}
+ \caption{Coordinate systems of the phase space $(\phi,j)$ in two-level pairing model. Left figure: cylindrical coordinate system; right figure: geographic coordinate system.}
+ \label{coordinate}
+\end{figure}
+
+Under the geographic coordinate system, we try to find a new set of canonical variables to obtain the requantized states in weak pairing correlation. 
+In $x\to 0$ limit, the excitation energies are $2n\Delta\epsilon$ with equivalent energy spacing because the excited states are pure $2n$-particle-$2n$-hole 
+configurations. 
+We aim to obtain harmonic oscillator Hamiltonian by canonical transformation 
+from $(\phi,j)$ to $(Q,P)$ at $x=0$. We utilize Type III generating function
+\begin{align}
+G_3(P,\phi) = \frac{P^2}{2\tan{\phi}} - \phi j_{\rm min} .
+\end{align}
+The first term is known as the harmonic oscillator generating function, 
+and the second term is to determine the original point $(q,p)=(0,0)$ at $j=j_{\rm min}$. 
+The new canonical variables can be straightforward derived from
+\begin{align}
+  Q &= -\frac{\partial G_3}{\partial P} = -\frac{P}{2\tan{\phi}} \\
+  j &= -\frac{\partial G_3}{\partial \phi} = \frac{P^2}{2\sin{\phi}} + j_{\rm min},
+\end{align}
+which lead to
+\begin{align}
+  Q &= \pm \sqrt{2}\sqrt{j-j_{\rm min}} \cos{\phi} \\
+  P &= \mp \sqrt{2}\sqrt{j-j_{\rm min}} \sin{\phi}.
+\end{align}
+Under the new canonical variables, 
+we can avoid the singularity at $j=j_{\rm min}$.
+Especially at $x=0$, the original classical Hamiltonian becomes
+\begin{align}
+  \mathcal{H}(\phi,j;J) &= (\epsilon_1+\epsilon_2)J + 2(\epsilon_2-\epsilon_1)j \nonumber \\
+  	&= (\epsilon_1+\epsilon_2)J + 2\Delta\epsilon j_{\rm min}
+	+ \Delta\epsilon(Q^2+P^2),
+\end{align}
+which perfectly reproduce the excitation energies $2n\Delta\epsilon$.
+
 %\clearpage{\pagestyle{empty}\cleardoublepage}
@@
 of Eq. (\ref{semi_wave_func1}).
-The explicit form of coherent state is
-
-\begin{align}
-  \ket{Z} &= \prod_{\alpha=1}^2(1+|Z_{\alpha}|^2)^{-\Omega_{\alpha}/2}e^{Z_{\alpha}S_{\alpha}^{+}}\ket{0} \nonumber \\
-  &= \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
+The explicit form of coherent state in two-level system is
+
+\begin{align}
+  \ket{Z} &= \prod_{\alpha=1}^2(1+|Z_{\alpha}|^2)^{-S_{\alpha}}e^{Z_{\alpha}S_{\alpha}^{+}}\ket{0} \nonumber \\
+  &= \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \sum_k \frac{1}{k!} \sum_{m=0}^k
   \binom{k}{m} \left(
@@
   \tan{\frac{\theta_2}{2}}e^{-i\phi_2}S_2^{+} \right)^{k-m} \ket{0} \nonumber \\
-  &= \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \sum_k \frac{1}{k!} \sum_{m=0}^k
+  &= \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \sum_k \frac{1}{k!} \sum_{m=0}^k
   \binom{k}{m} \tan^m{\frac{\theta_1}{2}}\tan^{k-m}{\frac{\theta_2}{2}}e^{-ik\Phi}e^{-i(k/2-m)\phi}
@@
 \end{align}
-Inserting (\ref{ZZ}) into (\ref{semi_wave_func0}) under fixed $N$ and $E_k$,
+Inserting (\ref{ZZ}) into (\ref{semi_wave_func0}) under fixed $J$ and $E_k$,
 it becomes
 \begin{align}
-	\ket{\psi_k^N} \propto& \oint d\Phi \oint dt
-	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
-	\ket{\Phi,t}_{N,E_k} \nonumber \\
-  \propto& \sum_k \frac{1}{k!} \sum_{m=0}^k \binom{k}{m} \int_0^{2\pi} d\Phi e^{i(N/2-k)\Phi} 
+	\ket{\psi_k^J} \propto& \oint d\Phi \oint dt
+	e^{i\mathcal{T}_{J,E_k}(\Phi, t)}
+	\ket{\Phi,t}_{J,E_k} \nonumber \\
+  \propto& \sum_k \frac{1}{k!} \sum_{m=0}^k \binom{k}{m} \int_0^{2\pi} d\Phi e^{i(J-k)\Phi} 
   \int_0^T dt e^{i\int \pi(t') \dot{\phi}(t') dt'-i(k/2-m)\phi} \nonumber \\
-  &\times \left\{ \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \right\}
+  &\times \left\{ \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \right\}
 \tan^m{\frac{\theta_1}{2}}\tan^{k-m}\frac{\theta_2}{2}(S_1^{+})^m(S_2^{+})^{k-m} \ket{0} \nonumber \\
-  \propto& \sum_{m=0}^{N/2} \binom{N/2}{m} \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(N/4-m)\phi \right)} \nonumber \\
-  &\times \left\{ \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-\Omega_{\alpha}/2} \right\} 
-\tan^m{\frac{\theta_1}{2}}\tan^{N/2-m}\frac{\theta_2}{2} (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} . \label{semi_wave_func_b}
+  \propto& \sum_{m=0}^{J} \binom{J}{m} \int_0^T dt \exp{\left( i\int \pi(t') \dot{\phi}(t') dt'-i(J/2-m)\phi \right)} \nonumber \\
+  &\times \left\{ \prod_{\alpha=1}^2\left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \right\} 
+\tan^m{\frac{\theta_1}{2}}\tan^{J-m}\frac{\theta_2}{2} (S_1^{+})^m(S_2^{+})^{J-m} \ket{0} . \label{semi_wave_func_b}
 \end{align}
@@
 \begin{align}
-  (S_1^{+})^m(S_2^{+})^{N/2-m} \ket{0} 
-  = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(N/2-m)!}{[2S_2-(N/2-m)]!}}
-  \ket{S_1,-S_1+m;S_2,-S_2+(N/2-m)}.
+  (S_1^{+})^m(S_2^{+})^{J-m} \ket{0} 
+  = \sqrt{\frac{(2S_1)!m!}{(2S_1-m)!}} \sqrt{\frac{(2S_2)!(J-m)!}{[2S_2-(J-m)]!}}
+  \ket{S_1,-S_1+m;S_2,-S_2+(J-m)}.
 \end{align}
@@
   \sqrt{\frac{(2S)!m!}{(2S-m)!}}  \nonumber \\
-  &= \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2} \sqrt{\frac{(2S)!m!}{(2S-m)!}}
+  &= \left(\frac{j}{2S}\right)^{m/2}\left(\frac{2S-j}{2S}\right)^{S-m/2}
+ \sqrt{\frac{(2S)!m!}{(2S-m)!}}
 \label{tan}
 \end{align}
-where $q=\cos{\theta}$.
-Inserting Eq. (\ref{tan}) into Eq. (\ref{semi_wave_func_b}) with $N/2=J$,
+where $j=S(1-\cos{\theta})$.
+Inserting Eq. (\ref{tan}) into Eq. (\ref{semi_wave_func_b}),
 we reach Eq. (\ref{semi_wave_func1}).
+
+\section{Derivation of Eq. (\ref{coherent2})}
+\label{wave_func2}
+
+To obtain the semiclassical wave function Eq. (\ref{SPA2}) via ASCC, we give the derivation of Eq. (\ref{coherent2}).
+%First, we derive the explicit form of coherent state (\ref{coherent2})
+\begin{align}
+\ket{Z} &= \prod_{\alpha} (1+|Z_{\alpha}|^2)^{-S_{\alpha}}e^{Z_{\alpha}S_{\alpha}^{\dag}}\ket{0} \nonumber \\
+&= \prod_{\alpha} \left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \sum_{m_{\alpha}=0}^{2S_{\alpha}} \frac{1}{m_{\alpha}!}
+  \left(
+  \tan{\frac{\theta_{\alpha}}{2}}e^{-i\chi_{\alpha}}S_{\alpha}^{\dag} \right)^{m_{\alpha}} \ket{0} \nonumber \\
+&= \left[ \prod_{\alpha} \left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \right] 
+\sum_{\{m_{\alpha}\}} \prod_{\alpha} \frac{1}{m_{\alpha}!} 
+  \left(
+  \tan{\frac{\theta_{\alpha}}{2}}e^{-i\chi_{\alpha}}S_{\alpha}^{\dag} \right)^{m_{\alpha}} \ket{0} \nonumber \\
+&= \left[ \prod_{\alpha} \left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \right] 
+\sum_{\{m_{\alpha}\}} \prod_{\alpha} \left(
+  \tan{\frac{\theta_{\alpha}}{2}}e^{-i\chi_{\alpha}} \right)^{m_{\alpha}} \sqrt{\frac{(2S_{\alpha})!}{m_{\alpha}!(2S_{\alpha}-m_{\alpha})!}}
+  \ket{\cdots;S_{\alpha},-S_{\alpha}+m_{\alpha},\cdots}, 
+\label{ZZZ}
+\end{align}
+where the summation is taken over all possible combinations
+of integer values of $\{ m_\alpha\}$. For convenience, we define coefficients
+\begin{align}
+B_{m_{\alpha}}(q,p) &= \prod_{\alpha} \left(1+\tan^2{\frac{\theta_{\alpha}}{2}}\right)^{-S_{\alpha}} \left(
+  \tan{\frac{\theta_{\alpha}}{2}}e^{-i(\chi_{\alpha}-\Phi)} \right)^{m_{\alpha}} \sqrt{\frac{(2S_{\alpha})!}{m_{\alpha}!(2S_{\alpha}-m_{\alpha})!}} \nonumber \\
+ &=\prod_\alpha \left(\frac{j_\alpha}{2S_\alpha}\right)^{m_\alpha/2}\left(\frac{2S_\alpha-j_\alpha}{2S_\alpha}\right)^{S_\alpha-m_\alpha/2}
+ \sqrt{\frac{(2S_\alpha)!}{m_\alpha!(2S_\alpha-m_\alpha)!}}
+e^{-i m_\alpha\phi_\alpha} ,
+\end{align}
+where $\phi_\alpha \equiv\chi_{\alpha}-\Phi$ and $j_\alpha=S_\alpha(1-\cos{\theta_\alpha})$. Using the coefficients $B_{m_{\alpha}}(q,p)$, Eq. (\ref{ZZZ}) becomes
+\begin{align}
+  \ket{Z} &= \sum_{\{m_{\alpha}\}} e^{-i\Phi \sum_\alpha m_{\alpha}} B_{m_{\alpha}}(q,p) \ket{\cdots;S_{\alpha},-S_{\alpha}+m_{\alpha},\cdots}.
+\label{ZZZ1}
+\end{align}
+Also, 
+\begin{align}
+ \ket{Z} &= e^{-i\Phi \hat{J}} \sum_{\{m_{\alpha}\}} B_{m_{\alpha}}(q,p) \ket{\cdots;S_{\alpha},-S_{\alpha}+m_{\alpha},\cdots} \nonumber \\
+ &= e^{-i\Phi \sum_{\alpha} (\hat{S}_{\alpha}^0 + S_{\alpha})} \sum_{\{m_{\alpha}\}} B_{m_{\alpha}}(q,p) \ket{\cdots;S_{\alpha},-S_{\alpha}+m_{\alpha},\cdots} \nonumber \\
+  &= \sum_{\{m_{\alpha}\}} e^{-i\Phi \sum_\alpha m_{\alpha}} B_{m_{\alpha}}(q,p) \ket{\cdots;S_{\alpha},-S_{\alpha}+m_{\alpha},\cdots}.
+\label{ZZZ2}
+\end{align}
+Comparing Eq. (\ref{ZZZ1}) with (\ref{ZZZ2}), therefore, we reach Eq. (\ref{coherent2}).
+
+\clearpage{\pagestyle{empty}\cleardoublepage}
+\chapter{Exact energy spectra in multi-level pairing model}
+\section{Two-level system}
+We give the energy spectra with various coupling constant $g$ in $\Omega_1=\Omega_2=8$, $\epsilon_1=-\epsilon_0$, and $\epsilon_2=0\epsilon_0$.
+We fix the seniority as $\nu=0$.
+The level spacing is $\Delta\epsilon = \epsilon_2-\epsilon_1 = \epsilon_0$.
+We use a dimensionless coupling constant $x$ as in Eq.
+(\ref{x}) instead of $g$.
+$N=16$ corresponds to the closed shell.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/spectra_x0.eps}
+ \end{center}
+ \caption{Energy spectra in $x=0$ (no pairing correlation).
+Horizontal line is total particle number and Vertical line is total energy in units of $\epsilon_0$.
+Green, light blue, orange, yellow, and deep blue dots correspond to $\ket{0_1^+}\sim\ket{0_5^+}$, respectively.
+	}
+ \label{x0}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/spectra_x0p5.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $x=0.5$.
+	}
+ \label{x0p5}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/spectra_x1.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $x=1$.
+	}
+ \label{x1}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/spectra_x2.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $x=2$.
+	}
+ \label{x2}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/spectra_x3p2.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $x=3.2$.
+	}
+ \label{x3p2}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/spectra_x8.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $x=8$.
+	}
+ \label{x8}
+\end{figure}
+
+\newpage
+
+\section{Three-level system}
+We give the energy spectra with various coupling constant $g$ in $\Omega_1=\Omega_2=\Omega_3=8$, $\epsilon_1=-\epsilon_0$, $\epsilon_2=0\epsilon_0$, and $\epsilon_3=1.5\epsilon_0$.
+We fix the seniority as $\nu=0$.
+$N=16$ and $N=32$ correspond to the closed shell.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=85mm,angle=-90]{images/spectra_g0.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0\epsilon_0$.
+	}
+ \label{g0}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=90mm,angle=-90]{images/spectra_g0p05.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.05\epsilon_0$.
+	}
+ \label{g0p05}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=90mm,angle=-90]{images/spectra_g0p1.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.1\epsilon_0$.
+	}
+ \label{g0p1}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=90mm,angle=-90]{images/spectra_g0p15.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.15\epsilon_0$.
+	}
+ \label{g0p15}
+\end{figure}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=90mm,angle=-90]{images/spectra_g0p2.eps}
+ \end{center}
+ \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.2\epsilon_0$.
+	}
+ \label{g0p2}
+\end{figure}
 

### 2019-01-09 thesis/thesis.tex
thesis

@@
 One of the clear evidences for pairing correlation detected from experiment is the separation energy difference between odd nuclei and even nuclei.
-Fig.
-\ref{S_n} shows the separation energies for Sn, Sb, and Te isotopes as a function of neutron number.
+Fig.~\ref{S_n} shows the separation energies for Sn, Sb, and Te isotopes as a function of neutron number.
 The isotopes in even number of neutron have about $2\sim3$ MeV larger separation energies than the isotopes in odd number of neutron.
-It is odd-even staggering (OES) effect, which is detected in whole mass region of nuclei (Fig.
-\ref{gap}).
+It is odd-even staggering (OES) effect, which is detected in whole mass region of nuclei (Fig.~\ref{gap}).
 In this figure, $2\Delta$ corresponds to the separation energy difference between even-even nuclei and odd mass number nuclei.
@@
 First, we discuss the pairing rotation.
-In classical picture, pairing rotation is the motion which the system rotates in the U(1) gauge space (red bi-direction arrow in Fig.
-\ref{pair_rot}).
+In classical picture, pairing rotation is the motion which the system rotates in the U(1) gauge space (red bi-direction arrow in Fig.~\ref{pair_rot}).
 The motion is described by the coordinate, gauge angle $\Phi$, and the corresponding momentum, total particle number $N$.
@@
 In experiment, the pairing rotational band is expected to be observed in even-even isotope chain or even-even isotone chain in open-shell nuclei.
-A clear observation is found in Sn isotopes shown in Fig.
-\ref{pair_rot}.
+A clear observation is found in Sn isotopes shown in Fig.~\ref{pair_rot}.
 Except a constant value and linear term with respect to mass number $A$, we can find the energies of ground states consist of a parabolic line - pairing rotational band.
@@
 From theoretical prediction, the pairing correlation is known to enhance $\sigma(g.s.\to g.s.)$ and decrease $\sigma(g.s.\to 0_{ex}^+)$ significantly, hence, $\sigma(g.s.\to 0_{ex}^+)/\sigma(g.s.\to g.s.)\ll 1$ is expected in superfluid system.
-One example of $(p, t)$ reactions is demonstrated in Fig.
-\ref{pair_rot}.
+One example of $(p, t)$ reactions is demonstrated in Fig.~\ref{pair_rot}.
 As mentioned in previous paragraph, the ground states of even-even Sn isotopes consist of a pairing rotational band.
@@
 A best example is the structure of $0_2^+$ or $0_3^+$ states in Cd isotopes observed in recent experiment \cite{GW10}.
-The lower part of Fig.
-\ref{112Cd} shows the excitation energy and $B(E2)$ transition strength in ${}^{112}$Cd.
-Comparing with the typical values for the ideal quadrupole harmonic vibration in spherical nuclei shown in the upper part of Fig.
-\ref{112Cd}, we can find that the observed excitation energy spectra have good coincidence with phonon excitation picture.
+The lower part of Fig.~\ref{112Cd} shows the excitation energy and $B(E2)$ transition strength in ${}^{112}$Cd.
+Comparing with the typical values for the ideal quadrupole harmonic vibration in spherical nuclei shown in the upper part of Fig.~\ref{112Cd}, we can find that the observed excitation energy spectra have good coincidence with phonon excitation picture.
 The $0_2^+$ or $0_3^+$ states seem to be interpreted as two-phonon or three-phonon excitation.
@@
 However, the pairing degrees of freedom are not explicitly included in the Bohr collective model.
-As discussed in Sec.
-\ref{1-1-2}, the pairing vibrational degrees of freedom supposed to be a key ingredient to understand the low-lying  excited $0^+$ states.
+As discussed in Sec.~\ref{1-1-2}, the pairing vibrational degrees of freedom supposed to be a key ingredient to understand the low-lying  excited $0^+$ states.
 We have great interest for the collective coordinates describing the pairing corrective motions.
@@
 \label{integrable}
-As discussed in Sec. \ref{constant}, there is only one time-dependent degree of freedom in two-level system. We know that one-dimensional system must be integrable system.
+As discussed in Sec.~\ref{constant}, there is only one time-dependent degree of freedom in two-level system. We know that one-dimensional system must be integrable system.
 We obtained two achievements from the study for the integrable system.
@@
 We show an example of the classical trajectories in two-level system.
-Fig.
-\ref{fig:phase_space} is the contour lines fulfilling (\ref{contour}), which correspond to the classical trajectories, with $\Omega_1=\Omega_2=\Omega=8$, $\nu=0$, and $N=2\Omega=16$ with various coupling constant $g$.
+Fig.~\ref{fig:phase_space} is the contour lines fulfilling (\ref{contour}), which correspond to the classical trajectories, with $\Omega_1=\Omega_2=\Omega=8$, $\nu=0$, and $N=2\Omega=16$ with various coupling constant $g$.
 The dimensionless coupling constant $x$ is defined as $x=2g\Omega/(\epsilon_2-\epsilon_1)$ (See Appendix \ref{two-level}).
 The phase transition from normal state to superfluid state occurs at $x=1$ in closed shell ($N=2\Omega$).
-At $x<1$ corresponding the left panel in Fig.
-\ref{fig:phase_space}, the trajectory of ground state is $j=-4$ independent from $\phi$.
+At $x<1$ corresponding the left panel in Fig.~\ref{fig:phase_space}, the trajectory of ground state is $j=-4$ independent from $\phi$.
 It is consistent with the fully occupied lower level $n_1=N$ and the empty upper level $n_2=0$.
 For the dynamical states, the trajectories are open with gentle slopes.
-At $x>1$ corresponding the middle and right panels in Fig.
-\ref{fig:phase_space}, the trajectory of ground state becomes a point at $\phi=0$, $j=j_0$ $(-4<j_0<4)$.
+At $x>1$ corresponding the middle and right panels in Fig.~\ref{fig:phase_space}, the trajectory of ground state becomes a point at $\phi=0$, $j=j_0$ $(-4<j_0<4)$.
 With superfluid ground state, the dynamical states have two types, closed trajectory and open trajectory.
@@
  \end{center}
- \caption{Energy contour plot in the same system as Fig. \ref{fig:phase_space}. Black solid lines correspond to TDHFB trajectories and gray dashed lines correspond to ATDHFB trajectories. 
+ \caption{Energy contour plot in the same system as Fig.~\ref{fig:phase_space}. Black solid lines correspond to TDHFB trajectories and gray dashed lines correspond to ATDHFB trajectories. 
 	}
@@
 We compare the difference of the classical trajectories between TDHFB and ATDHFB.
-Fig.
-\ref{fig:phase_compare} shows both TDHFB and ATDHFB trajectories in the same system as in Fig.
-\ref{fig:phase_space}.
+Fig.~\ref{fig:phase_compare} shows both TDHFB and ATDHFB trajectories in the same system as in Fig.~\ref{fig:phase_space}.
 For weak pairing correlation ($x<1$), both results are similar, especially at the low-energy region.
@@
 However, we find that canonical quantization has serious problems to describe the pairing dynamics.
-Such problems are discussed in Sec.
-\ref{3-3}.
+Such problems are discussed in Sec.~\ref{3-3}.
 To solve or avoid the problems, alternative requantization methods, Fourier decomposition and stationary-phase approximation to the path integral, are also introduced.
@@
 
-Before ending this section, let us note the periodic conditions
+Let us note the periodic conditions
 of the coordinates and the quantization condition.
-Since the two original variables, $(\chi_1,\chi_2)$,
+We have three types of periodic conditions. (1) $\Phi\rightarrow \Phi\pm 2\pi$ with fixed $\phi$. The quantization condition (\ref{EBK}) becomes
+\begin{equation}
+	2\pi J = 2k \pi ,
+\end{equation}
+which determines nothing but the total particle number $J$. (2) $\phi\rightarrow \phi$ with fixed $\Phi$. The quantization condition (\ref{EBK}) becomes
+\begin{align}
+	\oint j d\phi = 2k \pi ,
+\end{align}
+which determines the excited states for closed TDHFB trajectories (e.g., 
+\ref{fig:phase_space}). (3) $(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\pm 2\pi)$ and
+$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\mp 2\pi)$.
+because the two original variables, $(\chi_1,\chi_2)$,
 are independent periodic variables of the period $2\pi$,
 in addition to the trivial periodicity of $2\pi$ for $\Phi$ and of $4\pi$
-for $\phi$,
-we have periodic conditions for
-$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\pm 2\pi)$ and
-$(\Phi,\phi)\rightarrow (\Phi\pm \pi,\phi\mp 2\pi)$.
+for $\phi$.
 The former (latter) corresponds to $\chi_2\pm 2\pi$ ($\chi_1\pm 2\pi$)
 with $\chi_1$ ($\chi_2$) being fixed.
-For open TDHFB trajectory (e.g., Fig.~\ref{fig:phase_space}),
-the quantization condition becomes
+The quantization condition (\ref{EBK}) becomes
 \begin{align}
@@
 	 \Leftrightarrow \quad\quad \pm J \pi + \int_{-\pi}^\pi j d\phi
-	&= 2m\pi .
-\end{align}
+	&= 2m\pi ,
+\end{align}
+which determines the excited states for open TDHFB trajectories (e.g., Fig.~\ref{fig:phase_space}).
 This leads to the following:
@@
 From the study of various requantization methods for the two-level pairing model,
-canonical quantization and Fourier decomposition often fail to produce an approximate value to the exact solution.
-In contrast,
 the stationary-phase approximation (SPA) to the path integral \cite{SM88} 
-can give quantitative results not only for the excitation energies, 
+gives quantitative results not only for the excitation energies, 
 but also for the wave functions and two-particle-transfer strengths.
@@
 We introduce the theoretical framework of the ASCC, SPA,
-and their combination, ASCC+SPA in Sec. \ref{4-1}. 
-In Sec. \ref{4-2}, we provide some details in the application
+and their combination, ASCC+SPA in Sec.~\ref{4-1}. 
+In Sec.~\ref{4-2}, we provide some details in the application
 of the ASCC+SPA to the multi-level pairing model.
-We give the numerical results in Sec. \ref{4-3}, including
+We give the numerical results in Sec.~\ref{4-3}, including
 neutron pair vibrations in Pb isotopes.
@@
 %We try to combine SPA with ASCC.
-The key point is to find the correspondence between TDHFB phase space and collective subspace in a TDHFB trajectory (See Fig.
-\ref{fig:correspondence}).
+The key point is to find the correspondence between TDHFB phase space and collective subspace in a TDHFB trajectory (See Fig.~\ref{fig:correspondence}).
 We consider the time-dependent state vector $\ket{Z(t)}$ is in a collective subspace.
@@
 in Sec.~\ref{4-1}.
-The definition and physical meaning of $\chi_\alpha$ and $j^\alpha$ are explained in Sec. \ref{2-2}.
+The definition and physical meaning of $\chi_\alpha$ and $j^\alpha$ are explained in Sec.~\ref{2-2}.
 %Although it is customary to take the angle as a coordinate,
@@
 
-%In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec. \ref{ASCC}. 
+%In this subsection, we use ($\alpha, \beta, \cdots$) to describe the degrees of freedom instead of $l$ to synchronize the notation with in Sec.~\ref{ASCC}. 
 We construct a 2D collective subspace $\Sigma_2$ from the ASCC method.
@@
 Defining the upper index in $j^{\alpha}$ is nothing but to utilize Einstein summation convention.}
-%\begin{align}
-\begin{eqnarray}
-  V(j) &=& \mathcal{H}(j,\chi=0) \nonumber \\
-	&=& \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left[ \Omega_{\alpha}j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}} \right] \nonumber \\
-  &&- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}, \\	
-B^{\alpha\beta}(j) &=& \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \\
+\begin{align}
+  V(j) =& \mathcal{H}(j,\chi=0) \nonumber \\
+  =& \sum_{\alpha} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha} 2\epsilon_{\alpha}j^{\alpha} - g\sum_{\alpha} \left( (\Omega_{\alpha}-\nu_{\alpha}) j^{\alpha} - (j^{\alpha})^2 +\frac{(j^{\alpha})^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber \\
+	&- g\sum_{\alpha\ne \beta} \sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-\nu_{\alpha}-j^{\alpha})(\Omega_{\beta}-\nu_{\beta}-j^{\beta})}, \\
+B^{\alpha\beta}(j) =& \left. \frac{\partial^2\mathcal{H}}{\partial\chi_{\alpha}\partial\chi_{\beta}} \right|_{\chi=0} \\
 \label{mass}
-&=&
+=&
 	\begin{cases}
-2g\sum_{\gamma\ne \alpha} \sqrt{j^{\gamma}j^{\alpha}(\Omega_{\gamma}-j^{\gamma})(\Omega_{\alpha}-j^{\alpha})}
+2g\sum_{\gamma\ne \alpha} \sqrt{j^{\gamma}j^{\alpha}(\Omega_{\gamma}-\nu_{\gamma}-j^{\gamma})(\Omega_{\alpha}-\nu_{\alpha}-j^{\alpha})}
 		& \text{for $\alpha=\beta$} \\
--2g\sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-j^{\alpha})(\Omega_{\beta}-j^{\beta})}
+-2g\sqrt{j^{\alpha}j^{\beta}(\Omega_{\alpha}-\nu_{\alpha}-j^{\alpha})(\Omega_{\beta}-\nu_{\beta}-j^{\beta})}
 		& \text{for $\alpha\ne\beta$}
 	\end{cases}. \nonumber
-\end{eqnarray}
+\end{align}
 %\end{align}
-We may apply the ASCC method in Sec. \ref{sec:ASCC}
+We may apply the ASCC method in Sec.~\ref{sec:ASCC}
 by regarding $\xi\to j$ and $\pi\to-\chi$.
@@
 \begin{equation}
-	J\equiv N/2=\sum_\alpha j^\alpha, 
+	J = \frac{N-\nu}{2}=\sum_\alpha j^\alpha, 
   \label{J}
@@
 where the relative angles are defined as
-$\phi_\alpha\equiv\chi_\alpha-\Phi$ and the lower index $m$ indicates a combination of $\{ m_\alpha \}$.
-From Eq.
-(\ref{momenta2}) in ASCC, we can directly obtain the relative angles $\phi_\alpha = -f^1_{,\alpha}p_1$.
+\begin{align}
+  \phi_\alpha\equiv\chi_\alpha-\Phi
+  \label{phi_multi}
+\end{align}
+ and the lower index $m$ indicates a combination of $\{ m_\alpha \}$. From Eq. (\ref{momenta2}) in ASCC, we can directly obtain the relative angles $\phi_\alpha = -f^1_{,\alpha}p_1$.
 The integer number $m_\alpha$ corresponds to the number of pairs
@@
 \label{4-3}
-In the pairing model in Chap.~\ref{chap2},
-the number of TDHFB degrees of freedom equals that of single-particle levels.
-% including the constant of motion (pair rotation).
-We consider various systems, two-level system, three-level system, and Pb isotope system in each subsection respectively.
-Next, we discuss the dynamics in non-integrable (more than three-level) system.
-As there are two constants of motion, that is, the particle number and 
-the energy, the system is integrable for one- and two-level models.
 We first apply the ASCC+SPA method to an integrable two-level model,
@@
 
-\begin{figure}[thb]
+\begin{figure}[tb]
  \begin{center}
@@
 \end{figure}
-\begin{figure}[thb]
+\begin{figure}[tb]
  \begin{center}
@@
 %Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
-The action integrals are calculated on each trajectory in Fig. \ref{fig:N16_traj}
+The action integrals are calculated on each trajectory in Fig.~\ref{fig:N16_traj}
 from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction.
@@
 
-The two-level pairing model corresponds to the 2D TDHFB system.
-Explicitly separating the gauge angle $\Phi$ and
-fixing the particle number $J$,
-the 2D TDHFB is reduced to the 1D system
-with the relative angle $\phi\equiv \chi_2-\chi_1$ and the relative
-occupation $j\equiv (j_2-j_1)/2$ as canonical variables.
-In Ref.~\cite{NN18}, using the explicit transformation to these
+In Sec.~\ref{3-3}, using the explicit transformation to these
 separable variables,
@@
 for the two-level model.
-In this section, we discuss the same model as in Ref.~\cite{NN18},
+In this section, we discuss the same model as in Sec.~\ref{3-3},
 but we determine the transformation using the ASCC method and then apply the
@@
 \end{equation}
-with $J=N/2=8$.
+with $N=16$, $\nu=0$.
 Calculated trajectories that satisfy the EBK quantization condition
@@
 are mapped onto the $(\phi,j)$ plane and
-shown in Fig. \ref{fig:N16_traj}.
+shown in Fig.~\ref{fig:N16_traj}.
 We also calculate the trajectories using the explicit transformation
-of the variables to $(\Phi,J;\phi,j)$, which
-are shown by dashed lines in Fig. \ref{fig:N16_traj}.
+of the variables to $(\Phi,J;\phi,j)$, Eq. (\ref{Hamiltonian2}), which
+are shown by dashed lines in Fig.~\ref{fig:N16_traj}.
 We call this ``TDHFB trajectories''.
@@
 In fact, if we calculate the trajectories in the variables
-$(\Phi,J;\phi,j)$ using the Hamiltonian truncated up to the
-second order in $\chi_\alpha$ (``TDHFB2 trajectories''),
-we obtain the solid lines in Fig. \ref{fig:N16_traj},
+$(\Phi,J;\phi,j)$ using the adiabatic TDHFB Hamiltonian Eq. (\ref{ATDHFB_Hamiltonian}) (``TDHFB2 trajectories''),
+we obtain the solid lines in Fig.~\ref{fig:N16_traj},
 which perfectly agree with the ASCC trajectories.
@@
 The action integrals $\mathcal{T}(t)$ corresponding to
-these closed trajectories are shown in Fig. \ref{fig:N16_tau}.
+these closed trajectories are shown in Fig.~\ref{fig:N16_tau}.
 For the $0_2^+$ state,
@@
 The calculated wave functions for the excited $0^+$ states 
-are shown in Fig. \ref{fig:N16_occ2}. 
+are shown in Fig.~\ref{fig:N16_occ2}. 
 We show the occupation probabilities which are decomposed 
@@
 %The simplest non-integrable system is three-level system. We have one trivial motion and two time-dependent degrees of freedom. 
-We set the parameters of the system as follows:
+We set the parameters of the system as follows: $\nu=0$,
 $\Omega_1=\Omega_2=\Omega_3=\Omega=8$,
@@
 We obtain three eigen frequencies for the moving-frame QRPA equation, 
-on the collective path (Fig. \ref{omega_sq}). 
+on the collective path (Fig.~\ref{omega_sq}). 
 First of all, we clearly identify the zero mode with $\omega^2=0$
@@
 
-%It indicates that $\ket{0_3^+}$ is also one-phonon state which belongs to the other collective path (black line in Fig.
-\ref{omega_sq}).
+%It indicates that $\ket{0_3^+}$ is also one-phonon state which belongs to the other collective path (black line in Fig.~\ref{omega_sq}).
 About two-phonon states, we can easily find the candidates of two-phonon states from excitation energies and $B(P_{\rm ad};0_1^+\rightarrow 0_{ex}^+)$.
@@
 computed using these wave functions of the excited states
-are shown in Fig. \ref{3levelPad}.
+are shown in Fig.~\ref{3levelPad}.
 For the intraband transition ($k=k'$ in Eq. (\ref{BPad})),
@@
  \end{center}
-	\caption{The same as described in the caption of Fig. \ref{omega_sq} but for Pb isotopes.
+	\caption{The same as described in the caption of Fig.~\ref{omega_sq} but for Pb isotopes.
 }
@@
  \end{center}
-	\caption{The same as described in the caption of Fig. \ref{occ_number} but for Pb isotopes.
+	\caption{The same as described in the caption of Fig.~\ref{occ_number} but for Pb isotopes.
 }
@@
 
-We should remark here that there is a difficulty in the present ASCC+SPA
+We remark here that there is a difficulty in the present ASCC+SPA
 requantization for weak pairing cases.
@@
 Therefore, all the trajectories are ``closed'' in the usual sense.
+We discuss the possible approach for the weak pairing cases in Sec.~\ref{4-4}.
 
@@
 
-Finally, we apply our method to neutrons' pairing dynamics in 
+We also apply our method to neutrons' pairing dynamics in 
 neutron-deficient Pb isotopes.
@@
 The evolution of the occupation numbers along the collective path
-is shown in Fig. \ref{Pb_occ_number}.
+is shown in Fig.~\ref{Pb_occ_number}.
 Similarly to the three-level model, 
@@
  \end{center}
-	\caption{The same as Fig. \ref{potential} but for Pb isotopes.
+	\caption{The same as Fig.~\ref{potential} but for Pb isotopes.
 }
@@
 The collective potentials for these isotopes are shown
-in Fig. \ref{Pb_potential}.
+in Fig.~\ref{Pb_potential}.
 The heights of the potentials at the left end, $V(q_L)-V(0)$,
@@
 (See the last paragraph in Sec.~\ref{sec:three-level-model}).
-We encounter another kind of problem for $^{196}$Pb,
-which will be discussed in Chapter~\ref{??}.
-Therefore, in this paper, we calculate the first excited states
-in $^{188,190,192,194}$Pb.
+We obtain the excited state for $^{186}$Pb in a special boundary condition 
+discussed in Sec.~\ref{4-4}. We encounter another kind of problem for $^{196}$Pb,
+which will be discussed in Sec.~\ref{4-4}.
+Therefore, we calculate the first excited states
+in $^{188,190,192,194}$Pb in the manner of the ASCC+SPA without any artificial assumption.
 
@@
 \begin{center}
-\caption{The same as described in the caption of Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
+\caption{The same as described in the caption of Table \ref{ex} but for Pb isotopes.
+The energies are given in units of MeV.
+The value in parenthesis () is obtained in a special boundary condition discussed in Sec.~\ref{4-4}.}
 \begin{tabular}{c|cccccc}
@@
    & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
-ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
+ASCC+SPA & $(2.36)$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
 Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$ \\
@@
 \end{table}
-\begin{figure}[htb]
+\begin{figure}[tb]
  \begin{minipage}{1\hsize}
@@
  \end{minipage}
-	\caption{The same as described in the caption of Fig. \ref{3levelPad} but for Pb isotopes.
+	\caption{The same as described in the caption of Fig.~\ref{3levelPad} but for Pb isotopes. The value in parenthesis () is obtained in a special boundary condition discussed in Sec.~\ref{4-4}.
 }
@@
 \end{figure}
-The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
+The pair-addition transition strengths are shown in Fig.~\ref{PbPad}.
 The feature that is similar to the three-level case is observed:
@@
 $B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ as well.
-The deviation for the latter is about $25\%$.
+The deviation for the latter is about $25\%$, except the value in the parenthesis.
 The interband transitions are smaller than the intraband transitions
@@
 single-particle levels.
+The value of $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ for ${}^{186}$Pb $\to$ ${}^{188}$Pb, which is not shown in the Fig.~\ref{PbPad}, is $6.30$, much larger than the exact value.
+We still need to develop the boundary condition for ``unbound'' states discussed in Sec.~\ref{4-4}.
+
+\section{Remaining problems}
+\label{4-4}
+Although we have constructed the basic framework of ASCC+SPA, there are two remaining problems for the non-integrable pairing models.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=140mm]{images/open_traj.eps}
+ \end{center}
+ \caption{Schematic image for the open trajectory ($E_k > V(q_L)$).
+Left: schematic excitation energy and collective potential.
+Right: schematic classical trajectory in collective phase space.
+Red line represents a virtual boundary which connects the points $s$ and $f$ for the open trajectory.}
+ \label{open-traj}
+\end{figure}
+
+First problem is the application of the ASCC+SPA to the open trajectories corresponding to the weak pairing case, as shown in Fig.~\ref{open-traj}.
+Because SPA is only available for the periodic trajectories, we need to assume that the collective momentum $p_1$ has a periodicity.
+Following the periodicity $0\le\chi_{\alpha}\le 2\pi$ for the original variables $\chi_{\alpha}$, we may construct an approximate periodic boundary condition for $p_1$.
+
+We remember the open trajectories in two-level pairing models.
+As shown in Fig.~\ref{fig:phase_space}, these open trajectories are connected at $\phi=\pm\pi$.
+From Eq.
+(\ref{phi}), the boundary with respect to $\chi_1$, $\chi_2$ becomes
+\begin{align}
+  \chi_1 - \Phi = \pm \frac{\pi}{2}, \quad\quad \chi_2 - \Phi = \mp \frac{\pi}{2},
+\end{align}
+which lead to
+\begin{align}
+  e^{i\sum_{\alpha=1,2}|\chi_{\alpha} - \Phi|} = -1.
+  \label{boundary_two_level}
+\end{align}
+
+A possible construction of the approximate boundary for the multi-level pairing models is extending Eq. (\ref{boundary_two_level}) to 
+\begin{align}
+  e^{i\sum_{\alpha=1}^{L}|\phi_{\alpha}|} = -1,
+\end{align}
+where $\phi_{\alpha}$ is defined in Eq. (\ref{phi_multi}). Then, the boundary for $p_1$ is determined by
+\begin{align}
+  e^{i|p_1|\sum_{\alpha=1}^{L}|f^1_{,\alpha}|} = -1,
+  \label{boundary_multi}
+\end{align}
+where $f^1_{,\alpha}$ is obtained from ASCC.
+
+Using the above boundary condition, we try to calculate the excited states for open trajectories.  We choose the same three-level system as discussed in Sec.~\ref{4-3}, $\nu=0$,
+$\Omega_1=\Omega_2=\Omega_3=\Omega=8$,
+$\epsilon_1=-\epsilon_0$, $\epsilon_2=0$, $\epsilon_3=1.5\epsilon_0$,
+but with small coupling constant $g=0.05\epsilon_0$.
+We discuss the result for $N=18$.
+Fig.~\ref{open-potential} shows the collective potential obtained from ASCC.
+The shallow energy minimum pocket cannot bind any excited states, $E_k > V(q_L)$.
+Next, we need to apply the EBK quantization condition.
+We assume the quantization condition for both open trajectory and closed trajectory as
+\begin{align}
+  \mathcal{T}_{\rm tot} &= \mathcal{T}_\circ + \mathcal{T}_{\rm corr} \nonumber \\
+  &= \int_s^f \sum_\alpha j^\alpha d\chi_\alpha + \mathcal{T}_{\rm corr} = 2\pi k, 
+  \label{tau_tot}
+\end{align}
+where $s$ and $f$ are the starting and ending points for the open trajectory, respectively, as shown in Fig.~\ref{open-traj} ($\int_s^f\to\oint$ for closed trajectory), and $\mathcal{T}_{\rm corr}$ is the correction to make the smooth change of $\mathcal{T}_{\rm tot}$ from closed to open trajectory by increasing the excitation energy.
+In closed trajectory, $\mathcal{T}_{\rm corr}=0$.
+Calculated $\mathcal{T}_{\rm tot}$ is shown in Fig.~\ref{E-tau}.
+The trajectory changes from closed to open at the excitation energy from $0.2$ to $0.3$.
+To cancel the large jump of $\mathcal{T}_\circ$ between closed and open trajectory the $\mathcal{T}_{\rm corr}$ has finite value for open trajectory.
+The classical trajectory of $\ket{0_2^+}$ fulfilling the Eq.~(\ref{tau_tot}) are shown in Fig.~\ref{open-trajectory}.
+Integrating the classical trajectory, we obtain the excited states.
+The excitation energy for $\ket{0_2^+}$ is $1.36$, while $1.46$ for exact solution, in units of $\epsilon_0$.
+The occupation probability expanded in the SU(2) quasispin basis is represented in Fig.~\ref{N18occ}.
+We can find the result from ASCC+SPA with the boundary condition reasonably reproduce the exact solution.
+
+\begin{figure}[bt]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/N18potential.eps}
+ \end{center}
+	\caption{Collective potential $V(q^1)$ for $N=18$ obtained from the ASCC.
+	We adjust the energy minimum point as $q^1=0$ and $V=0$.
+}
+ \label{open-potential}
+\end{figure}
+
+\begin{figure}[bt]
+ \begin{center}
+  \includegraphics[width=80mm,angle=-90]{images/N18E_tau.eps}
+ \end{center}
+	\caption{Action integral $\mathcal{T}_\circ$ and $\mathcal{T}_{\rm corr}$ for $N=18$ in the EBK quantization condition Eq.
+(\ref{tau_tot}) as a function of excitation energy $E_{\rm ex}$ below $2\epsilon_0$.
+See text for the definition of the two quantities.
+}
+ \label{E-tau}
+\end{figure}
+
+\begin{figure}[bt]
+ \begin{center}
+  \includegraphics[width=60mm,angle=-90]{images/N18trajectory.eps}
+ \end{center}
+	\caption{Classical trajectory for the $\ket{0_2^+}$, $N=18$ in phase space. Black dashed lines are the approximate boundary defined in Eq.~(\ref{boundary_multi}).
+}
+ \label{open-trajectory}
+\end{figure}
+
+\begin{figure}[bt]
+ \begin{center}
+  \includegraphics[width=80mm,angle=-90]{images/N18g0p05occ.eps}
+ \end{center}
+	\caption{Occupation probability for $\ket{0_2^+}$, $N=18$ in logarithmic scale as a function of $\{m_{\alpha}\}\equiv9m_3+m_2$.
+For example, $(m_1,m_2,m_3)=(8,1,0)$ at $1$, $(m_1,m_2,m_3)=(7,2,0)$ at $2$ in horizontal axis.
+The vertical bars and the circles at each $\{m_{\alpha}\}$ represent the squared components of the wave function from the ASCC+SPA and exact calculation, respectively.
+}
+ \label{N18occ}
+\end{figure}
+
+We cannot convince that the boundary condition (\ref{boundary_multi}) well works in all multi-level pairing models.
+Actually, there is a certain deviation for the $\ket{0_2^+}$ in ${}^{186}$Pb shown in Fig.~\ref{PbPad}.
+We need to consider more about the boundary condition.
+Moreover, we cannot calculate the excited states with normal ground state because the moving-frame QRPA equation in ASCC cannot give the eigenvectors associated with pairing vibrations at normal state.
+
+Another problem occurs in the calculation of ${}^{196}$Pb, in which we have encountered complex eigenvalues and eigenvectors of the moving-frame QRPA equation.
+This happens at $q\approx0.1$ where the two eigen frequencies become identical, $\omega_1^2=\omega_2^2$, as shown in Fig.~\ref{196Pbomega-sq}.
+Because the complex values of $f^1_{\alpha}$ the ASCC cannot determine the next point of the collective coordinate $q^1$.
+We do not have a problem for the crossing between the pairing rotational mode and the other modes.
+Currently, we do not know exactly when the complex solutions emerge.
+
+\begin{figure}[bt]
+ \begin{center}
+  \includegraphics[width=70mm,angle=-90]{images/196Pbomega_sq.eps}
+ \end{center}
+	\caption{The same as described in the caption of Fig.~\ref{omega_sq} but for ${}^{196}$ Pb.
+}
+ \label{196Pbomega-sq}
+\end{figure}
 
@@
 The collective model treatment is based on the choice,
-$j$ as a coordinate and $\phi$ as a momentum, as discussed in Sec. \ref{ATDHFB}.
+$j$ as a coordinate and $\phi$ as a momentum, as discussed in Sec.~\ref{ATDHFB}.
 \begin{align}
@@
 are shown by dashed lines in Fig.~\ref{fig:p_Delta} 
-for $\Omega=8$ mid-shell (a) and closed-shell (b) configurations discussed in Sec. \ref{SmallOmg}.
+for $\Omega=8$ mid-shell (a) and closed-shell (b) configurations discussed in Sec.~\ref{SmallOmg}.
 The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
@@
 To simulate the result of the collective model, we requantize the ATDHFB Hamiltonian in (\ref{ATDHFB_Hamiltonian})-(\ref{mass_two_level}) by $\hat{\phi}=i\partial/\partial j$, with
-the ordering given by Pauli's prescription
-\begin{align}
-	H \left( j,i\frac{\partial}{\partial j} \right) 
-= V(j) - \frac{1}{2}\frac{1}{\sqrt{B(j)}}\frac{\partial}{\partial j}\frac{1}{\sqrt{B(j)}}\frac{\partial}{\partial j}.
-\end{align}
+the ordering given by Pauli's prescription in Eq. (\ref{Pauli}).
 The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
@@
 
-In Fig. \ref{q_Delta}, we show two examples of the behavior of pairing gap parameter as a function of the collective coordinate $q^1$.
+In Fig.~\ref{q_Delta}, we show two examples of the behavior of pairing gap parameter as a function of the collective coordinate $q^1$.
 Panel (a) corresponds to the case of $N=20$ in three-level system ($\Omega_1=\Omega_2=\Omega_3=8$,
@@
 The same behavior observed for all of the non-integrable systems.
-The situations are similar to the case in Fig. \ref{fig:Delta_E} (b), where the low-lying excited states cannot be properly described.
+The situations are similar to the case in Fig.~\ref{fig:Delta_E} (b), where the low-lying excited states cannot be properly described.
 
@@
 Thus, it is of significant interest to apply the SPA to systems with pairing and quadrupole correlations, such as multi-O(4) model \cite{HNMM07} and P+Q model \cite{HNMM08}.
-It is also important to extend the ASCC+SPA to the following cases: (1) ``unbound'' trajectories in shallow potential energy surface as discussed in Sec.
-\ref{4-3}; (2) trajectories in potential energy surface with multi energy minimum pockets, such as shape coexistence.
+It is also important to extend the ASCC+SPA to the following cases: (1) ``unbound'' trajectories in shallow potential energy surface as discussed in Sec.~\ref{4-3}; (2) trajectories in potential energy surface with multi energy minimum pockets, such as shape coexistence.
 In the former case, we need to find a proper boundary condition to guarantee the periodicity  of the trajectories.
@@
 \begin{equation}
-       \braket{Z|\frac{\partial}{\partial t}|Z} = \frac{1}{i}\sum_{\alpha} j_{\alpha} \dot{\chi_{\alpha}}
+       \braket{Z|\frac{\partial}{\partial t}|Z} = \frac{1}{i}\sum_{\alpha} j_{\alpha} \dot{\chi}_{\alpha}
 	\label{ddt2}
@@
 \section{Action in pairing model}
-We derived the action in the previous sections. Using the formula in Sec. \ref{formula1}, the expectation value of pairing Hamiltonian is
+We derived the action in the previous sections. Using the formula in Sec.~\ref{formula1}, the expectation value of pairing Hamiltonian is
 \begin{align}
@@
 \end{align}
-Using the canonical variables $(\chi,j)$, we can obtain the tractable form of the action based on Sec. \ref{formula2}. 
+Using the canonical variables $(\chi,j)$, we can obtain the tractable form of the action based on Sec.~\ref{formula2}. 
 The Lagrangian in $(\chi,j)$ representation becomes
@@
 
-In Sec. \ref{integrable}, we derived the TDHFB Hamiltonian in adiabatic approximation. 
+In Sec.~\ref{ATDHFB}, we derived the TDHFB Hamiltonian in adiabatic approximation. 
 The canonical quantization in Pauli's prescription is available for Eq. (\ref{ATDHFB_Hamiltonian}). Using Pauli's prescription, Eq. (\ref{ATDHFB_Hamiltonian}) becomes
@@
    H \left( j,i\frac{\partial}{\partial j} \right) = V(j) - \frac{1}{2}\sqrt{B^{-1}(j)}\frac{\partial}{\partial j}\sqrt{B^{-1}(j)}\frac{\partial}{\partial j},
+\label{Pauli}
 \end{align}
@@
 Because the range of $j$ is limited $(j_{\rm min}\le j \le j_{\rm max})$, we have to care about the boundary condition for the end points $j_{\rm min}$ and $j_{\rm max}$.
-As shown in Fig.
-??, the boundary condition is negligible for the strong pairing correlation.
+We show the potential surfaces in the range of $j_{\rm min}\le j \le j_{\rm max}$ in Fig.~\ref{PES}.
+The boundary condition is negligible for the strong pairing correlation.
 On the other hand, the boundary condition is important for the weak pairing correlation because the potential cannot bind the states at $j_{\rm min}$.
-
-We reconsider the coordinate system for the phase space $(\phi,j)$ (Fig. \ref{coordinate}). It is natural to utilize 
+Actually, we obtain proper states in strong pairing correlations and improper states in weak correlations from Pauli's prescription for the canonical variables $(\phi, j)$ (Fig.~\ref{CQ-energy}).
+
+\begin{figure}[tb]
+ \begin{center}
+(a) \includegraphics[height=0.44\textwidth,angle=-90]{images/N50potential.eps}
+(b) \includegraphics[height=0.44\textwidth,angle=-90]{images/N16potential.eps}
+ \end{center}
+ \caption{Potential surfaces as functions of $j$,
+ Eq. (\ref{potential_two_level}) for $x=0.5$, $1$, and $2$.
+ (a) mid-shell in large degeneracy ($\Omega=50$, $N=50$) and (b) closed-shell in small degeneracy ($\Omega=8$, $N=16$).
+}
+ \label{PES}
+\end{figure}
+
+We reconsider the coordinate system for the phase space $(\phi,j)$ (Fig.~\ref{coordinate}). It is natural to utilize 
 a cylindrical coordinate system because $\phi$ is periodic.
@@
 Instead of the cylindrical coordinate system, we bring an another coordinate system, geographic coordinate system, which assumes the phase space collapsing at $j_{\rm min}$ and  $j_{\rm max}$, such as north pole and south pole.
-This assumption is available because the (adiabatic) TDHFB Hamiltonian is independent of $\phi$ at $j_{\rm min}$ and $j_{\rm max}$.
+We think this assumption is correct from the following reason.
+The (adiabatic) TDHFB Hamiltonian is independent of $\phi$ at $j_{\rm min}$ and $j_{\rm max}$.
+In addition, we can white down the coherent state as $\ket{Z}=e^{i\Theta \hat{J}}\ket{Z_0}$, where $\Theta$ is an arbitrary phase depends on $\phi$ and $\ket{Z_0}$ is independent of $\phi$, at $j_{\rm min}$ and $j_{\rm max}$.
 
@@
 The first term is known as the harmonic oscillator generating function, 
-and the second term is to determine the original point $(q,p)=(0,0)$ at $j=j_{\rm min}$. 
+and the second term is to determine the original point $(Q,P)=(0,0)$ at $j=j_{\rm min}$. 
 The new canonical variables can be straightforward derived from
 \begin{align}
-  Q &= -\frac{\partial G_3}{\partial P} = -\frac{P}{2\tan{\phi}} \\
-  j &= -\frac{\partial G_3}{\partial \phi} = \frac{P^2}{2\sin{\phi}} + j_{\rm min},
+  Q &= -\frac{\partial G_3}{\partial P} = -\frac{P}{2\tan{\phi}} \nonumber \\
+  j &= -\frac{\partial G_3}{\partial \phi} = \frac{P^2}{2\sin{\phi}} + j_{\rm min}, \nonumber 
 \end{align}
@@
 \begin{align}
-  Q &= \pm \sqrt{2}\sqrt{j-j_{\rm min}} \cos{\phi} \\
-  P &= \mp \sqrt{2}\sqrt{j-j_{\rm min}} \sin{\phi}.
+  Q(\phi, j) &= \pm \sqrt{2}\sqrt{j-j_{\rm min}} \cos{\phi} \nonumber \\
+  P(\phi, j) &= \mp \sqrt{2}\sqrt{j-j_{\rm min}} \sin{\phi},
+\label{QP}
+\end{align}
+and
+\begin{align}
+  j(Q,P) &= \frac{Q^2 + P^2}{2} + j_{\rm min} \nonumber \\
+  \phi(Q,P) &= \arccos{\left( \frac{Q^2}{\sqrt{Q^2 + P^2}} \right)}.
+\label{phij}
 \end{align}
 Under the new canonical variables, 
-we can avoid the singularity at $j=j_{\rm min}$.
-Especially at $x=0$, the original classical Hamiltonian becomes
+we can avoid the singularity at $j=j_{\rm min}$. The transformed TDHFB Hamiltonian $\tilde{\mathcal{H}}(Q,P;J)$ is
+\begin{align}
+  \tilde{\mathcal{H}}(Q,P;J) = \tilde{V}(Q) + \frac{1}{2}\tilde{B}^{-1}(Q)P^2, 
+\end{align}
+where
+\begin{align}
+  \tilde{V}(Q) &= \tilde{\mathcal{H}}(Q,P=0;J) = \mathcal{H}(\phi(Q,P=0), j(Q,P=0);J) \\
+  \tilde{B}^{-1}(Q) &= \left. \frac{\partial^2 \tilde{\mathcal{H}}}{\partial P^2} \right|_{P=0} .
+\end{align}
+We can also utilize the Pauli's prescription (\ref{Pauli}) for the transformed TDHFB Hamiltonian. Especially at $x=0$, the TDHFB Hamiltonian becomes
 \begin{align}
@@
 which perfectly reproduce the excitation energies $2n\Delta\epsilon$.
+
+We apply the canonical quantization in Pauli's prescription for both canonical variables $(j, -\phi)$ and $(Q, P)$.
+The boundary conditions are determined in $\psi'(j_{\rm min})=0$ and $\psi(j_{\rm max})=0$ for $(j, -\phi)$, and $\psi(Q_{\rm min})=\psi(Q_{\rm max})=0$ for $(Q, P)$.
+Calculated excitation energies are shown in Fig.~\ref{CQ-energy}.
+For the canonical variables $(j, -\phi)$, the requantized energies well reproduce the exact solution in strong pairing correlation, while the deviation becomes larger and larger toward $x=0$.
+The reason is that the singular point $j_{\rm min}$ influences the requantized states significantly.
+However, it may be difficult to know the proper boundary condition at $j_{\rm min}$.
+For the canonical variables $(Q, P)$, on the other hand, the requantized energies well reproduce the exact solution in weak pairing correlation, while the deviation becomes larger and larger toward the strong pairing correlation in the panel (b).
+We cannot obtain the result after a certain $x$ because the mass parameter $\tilde{B}^{-1}(Q)$ have the negative signs.
+
+We find that the canonical variables $(j, -\phi)$ can well describe the strong pairing systems, while $(Q, P)$ can well describe the weak pairing systems.
+We think that the choice of canonical coordinates is especially important for the canonical quantization in Pauli's prescription.
+In a sense, $(j, -\phi)$ is the best canonical variables in $x\to\infty$, and $(Q, P)$ is the best canonical variables in $x\to 0$.
+Best canonical variables in the intermediate pairing correlation should also exist in proper canonical transformations.
+We need to be careful for this problem if we choose the canonical quantization in Pauli's prescription for the requantization of TDHFB.
+
+\begin{figure}[t]
+ \begin{center}
+(a)	 \includegraphics[height=0.6\textwidth,angle=-90]{images/N50can_trans.eps}
+\\
+(b)	 \includegraphics[height=0.6\textwidth,angle=-90]{images/N16can_trans.eps}
+ \end{center}
+ \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and
+$\ket{0_4^+}$ in canonical quantization with Pauli's prescription. (a) $\Omega=50$, $N=50$ and (b) $\Omega=8$, $N=16$ 
+	as functions of the dimensionless parameter $x$ of Eq.
+(\ref{x}).
+Open circles correspond to the canonical variables $(j, -\phi)$ and filled circles correspond to the transformed canonical variables $(Q, P)$ in (\ref{QP}).
+}
+ \label{CQ-energy}
+\end{figure}
 
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $x=0.5$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $x=0.5$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $x=1$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $x=1$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $x=2$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $x=2$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $x=3.2$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $x=3.2$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $x=8$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $x=8$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0\epsilon_0$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $g=0\epsilon_0$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.05\epsilon_0$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $g=0.05\epsilon_0$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.1\epsilon_0$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $g=0.1\epsilon_0$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.15\epsilon_0$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $g=0.15\epsilon_0$.
 	}
@@
  \end{center}
- \caption{The same as described in the caption of Fig. \ref{x0} but for $g=0.2\epsilon_0$.
+ \caption{The same as described in the caption of Fig.~\ref{x0} but for $g=0.2\epsilon_0$.
 	}
